### 2015-06-03 SobolIndices.tex
Some examples for Sobol indices

\documentclass[]{amsart}

\usepackage{array,colortbl}
\usepackage{amsmath,amsfonts,amssymb,bm,listings} % no amsthm, Springer defines Theorem, Lemma, etc themselves
\usepackage{xspace}
\usepackage[autolinebreaks]{mcode}
\input FJHDef
\newcommand{\oerr}{e}

\begin{document}
\title{Adaptive Computation of Sobol' Indices}
\maketitle

\noindent To:  Cl\'ementine Prieur (U. Josef Fourier), Llu\'is Antoni Jim\'enez Rugama (IIT)

\bigskip

Today Cl\'ementine discussed the possibility of using \texttt{cubSobol\_g} to calculate Sobol sensitivity indices for functions $f : [0,1]^d \to \reals$.  Here is some sample code where we showed proof of concept.

\lstinputlisting{ProgramsImages/SobolIndexExample.m}

There are a few next steps:

\begin{enumerate}
\item Sobol' indices can be written in terms of $2d-1$-dimensional integrals.   Cl\'ementine will work out what those integrals are.

\item The problem that we want to solve is to find $s_1, \ldots, s_p$ such that 
\[
\max_{j=1, \ldots, p} \abs{S_j(I_1(f), \ldots, I_q(f)) - s_j} \le \varepsilon,
\]
 where the $I_\ell$ are integrals of $f$ or maybe powers of $f$ or something that Cl\'ementine will work out.  Tony and I need to think about how to modify \texttt{cubSobol\_g}.

My suggestion is that for each $m = m_{\min}, m_{\min}+1, \ldots$ we compute our data-based error bounds for the Sobol' cubatures $\hI_{\ell,m}(f)$ using $n=2^m$ points, i.e., 
\[
\abs{I_\ell(f) - \hI_{\ell,m}(f)} \le \oerr_{\ell,m}(f).
\]
We also identify $\hS$ such that 
\[
\hS_j(b_1, \ldots, b_q, c_1, \ldots, c_q) \le S(a_1, \ldots, a_q) \le \hS_j(c_1, \ldots, c_q, b_1, \ldots, b_q) 
\]
for all $b_\ell \le a_\ell \le c_\ell$.  When we get 
\begin{multline*}
\hS_j(\hI_{1,m}(f) + \oerr_{1,m}(f), \ldots,\hI_{q,m}(f) + \oerr_{q,m}(f), \ldots \\
\hI_{1,m}(f) - \oerr_{1,m}(f), \ldots,\hI_{q,m}(f) - \oerr_{q,m}(f)) \\
 - \hS_j(\hI_{1,m}(f) - \oerr_{1,m}(f), \ldots,\hI_{q,m}(f) - \oerr_{q,m}(f), \ldots \\
 \hI_{1,m}(f) + \oerr_{1,m}(f), \ldots,\hI_{q,m}(f) + \oerr_{q,m}(f))   \le 2\varepsilon, \quad j = 1, \ldots, p
\end{multline*}
we may stop and choose 
\begin{multline*}
s_j = \frac{1}{2}\Bigl[\hS_j(\hI_{1,m}(f) + \oerr_{1,m}(f), \ldots,\hI_{q,m}(f) + \oerr_{q,m}(f), \ldots \\
\hI_{1,m}(f) - \oerr_{1,m}(f), \ldots,\hI_{q,m}(f) - \oerr_{q,m}(f)) \\
+ \hS_j(\hI_{1,m}(f) - \oerr_{1,m}(f), \ldots,\hI_{q,m}(f) - \oerr_{q,m}(f), \ldots \\
 \hI_{1,m}(f) + \oerr_{1,m}(f), \ldots,\hI_{q,m}(f) + \oerr_{q,m}(f)) \Bigr]
 \end{multline*}

\item Cl\'ementine will talk to her student to involve him in this project.

\end{enumerate}

\bigskip

Any questions, clarifications, or comments?

\end{document}

### 2015-06-03 ProgramsImages/SobolIndexExample.m

@@ -1,0 +1,38 @@
+% Sobol Index Example
+
+d=4;
+%a=0.5*(1:d).^2; %the a_j decay more quickly
+a=0.5*(1:d)/d; %the a_j decay less quickly
+
+%% True answers for the test function
+partialvariance = 1./(3.*(1+a).^2)
+variance = prod(partialvariance+1)-1
+sobol = partialvariance/variance
+
+f = @(x) prod(bsxfun(@times,bsxfun(@plus,abs(4*x-2),a),1./(1+a)),2);
+nval = zeros(1,d+2);
+timeval = zeros(1,d+2);
+[mu,out] = cubSobol_g(f,[zeros(1,d);ones(1,d)],'abstol',1e-4,'reltol',0);
+mu
+nval(1) = out.n;
+timeval(1) = out.time;
+[Efsq,out] = cubSobol_g(@(x) f(x).*f(x),[zeros(1,d);ones(1,d)], ...
+   'abstol',1e-4,'reltol',0);
+nval(2) = out.n;
+timeval(2) = out.time;
+varf = Efsq - mu^2
+Emujsq = zeros(1,d);
+for j = 1:d
+   gj = @(x) f(x(:,1:d)).*f(x(:,[d+1:d+j-1 j d+j:2*d-1]));
+   [Emujsq(j),out] = cubSobol_g(gj, ...
+      [zeros(1,2*d-1);ones(1,2*d-1)],'abstol',1e-4,'reltol',0);
+   nval(j+2) = out.n;
+   timeval(j+2) = out.time;
+end
+varj = Efsq - Emujsq;
+sobolind = (varf - varj)/varf
+sobolerr = abs(sobol - sobolind)
+nval
+timeval
+   
+

### 2015-06-15 FunctionsTest/bratley.m
First commit

@@ -1,0 +1,52 @@
+
+
+function [y] = bratleyetal92(xx)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% BRATLEY ET AL. (1992) FUNCTION
+%
+% Authors: Sonja Surjanovic, Simon Fraser University
+%          Derek Bingham, Simon Fraser University
+% Questions/Comments: Please email Derek Bingham at dbingham@stat.sfu.ca.
+%
+% Copyright 2013. Derek Bingham, Simon Fraser University.
+%
+% THERE IS NO WARRANTY, EXPRESS OR IMPLIED. WE DO NOT ASSUME ANY LIABILITY
+% FOR THE USE OF THIS SOFTWARE.  If software is modified to produce
+% derivative works, such modified software should be clearly marked.
+% Additionally, this program is free software; you can redistribute it 
+% and/or modify it under the terms of the GNU General Public License as 
+% published by the Free Software Foundation; version 2.0 of the License. 
+% Accordingly, this program is distributed in the hope that it will be 
+% useful, but WITHOUT ANY WARRANTY; without even the implied warranty 
+% of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU 
+% General Public License for more details.
+%
+% For function details and reference information, see:
+% http://www.sfu.ca/~ssurjano/
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% INPUT:
+%
+% xx = [x1, x2, ..., xd]
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+d = length(xx);
+sum = 0;
+
+for ii = 1:d
+    prod = 1;
+    for jj = 1:ii
+        xj = xx(jj);
+        prod = prod * xj;
+    end
+    sum = sum + prod*(-1)^ii;
+end
+
+y = sum;
+
+end
+

### 2015-06-15 FunctionsTest/gfunction.m

@@ -1,0 +1,57 @@
+function [y] = gfunc(xx, a)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% G-FUNCTION
+%
+% Authors: Sonja Surjanovic, Simon Fraser University
+%          Derek Bingham, Simon Fraser University
+% Questions/Comments: Please email Derek Bingham at dbingham@stat.sfu.ca.
+%
+% Copyright 2013. Derek Bingham, Simon Fraser University.
+%
+% THERE IS NO WARRANTY, EXPRESS OR IMPLIED. WE DO NOT ASSUME ANY LIABILITY
+% FOR THE USE OF THIS SOFTWARE.  If software is modified to produce
+% derivative works, such modified software should be clearly marked.
+% Additionally, this program is free software; you can redistribute it 
+% and/or modify it under the terms of the GNU General Public License as 
+% published by the Free Software Foundation; version 2.0 of the License. 
+% Accordingly, this program is distributed in the hope that it will be 
+% useful, but WITHOUT ANY WARRANTY; without even the implied warranty 
+% of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU 
+% General Public License for more details.
+%
+% For function details and reference information, see:
+% http://www.sfu.ca/~ssurjano/
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% INPUTS:
+%
+% xx = [x1, x2, ..., xd]
+% a = [a1, a2, ..., ad] (optional), with default values given by Crestaux
+%     et al. (2007)
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+d = length(xx);
+
+if (nargin == 1)
+    a = zeros(1, d);
+    for ii = 1:d
+        a(ii) = (ii-1) / 2;
+    end
+end
+
+prod = 1;
+for ii = 1:d
+    xi = xx(ii);
+    ai = a(ii);
+    new1 = abs(4*xi-2) + ai;
+    new2 = 1 + ai;
+    prod = prod * new1/new2;
+end
+
+y = prod;
+
+end

### 2015-06-15 FunctionsTest/ishigami.m

@@ -1,0 +1,56 @@
+
+
+function [y] = ishigami(xx, a, b)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% ISHIGAMI FUNCTION
+%
+% Authors: Sonja Surjanovic, Simon Fraser University
+%          Derek Bingham, Simon Fraser University
+% Questions/Comments: Please email Derek Bingham at dbingham@stat.sfu.ca.
+%
+% Copyright 2013. Derek Bingham, Simon Fraser University.
+%
+% THERE IS NO WARRANTY, EXPRESS OR IMPLIED. WE DO NOT ASSUME ANY LIABILITY
+% FOR THE USE OF THIS SOFTWARE.  If software is modified to produce
+% derivative works, such modified software should be clearly marked.
+% Additionally, this program is free software; you can redistribute it 
+% and/or modify it under the terms of the GNU General Public License as 
+% published by the Free Software Foundation; version 2.0 of the License. 
+% Accordingly, this program is distributed in the hope that it will be 
+% useful, but WITHOUT ANY WARRANTY; without even the implied warranty 
+% of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU 
+% General Public License for more details.
+%
+% For function details and reference information, see:
+% http://www.sfu.ca/~ssurjano/
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% INPUTS:
+%
+% xx = [x1, x2, x3]
+% a = coefficient (optional), with default value 7
+% b = coefficient (optional), with default value 0.1
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+x1 = xx(1) * 2 * pi - pi;
+x2 = xx(2) * 2 * pi - pi;
+x3 = xx(3) * 2 * pi - pi;
+
+if (nargin == 1)
+	a = 7;
+	b = 0.1;
+elseif (nargin == 2)
+	b = 0.1;
+end
+
+term1 = sin(x1);
+term2 = a * (sin(x2))^2;
[…]

### 2015-06-15 FunctionsTest/morokoff.m

@@ -1,0 +1,49 @@
+
+
+function [y] = morcaf95a(xx)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% MOROKOFF & CAFLISCH (1995) FUNCTION 1
+%
+% Authors: Sonja Surjanovic, Simon Fraser University
+%          Derek Bingham, Simon Fraser University
+% Questions/Comments: Please email Derek Bingham at dbingham@stat.sfu.ca.
+%
+% Copyright 2013. Derek Bingham, Simon Fraser University.
+%
+% THERE IS NO WARRANTY, EXPRESS OR IMPLIED. WE DO NOT ASSUME ANY LIABILITY
+% FOR THE USE OF THIS SOFTWARE.  If software is modified to produce
+% derivative works, such modified software should be clearly marked.
+% Additionally, this program is free software; you can redistribute it 
+% and/or modify it under the terms of the GNU General Public License as 
+% published by the Free Software Foundation; version 2.0 of the License. 
+% Accordingly, this program is distributed in the hope that it will be 
+% useful, but WITHOUT ANY WARRANTY; without even the implied warranty 
+% of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU 
+% General Public License for more details.
+%
+% For function details and reference information, see:
+% http://www.sfu.ca/~ssurjano/
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% INPUT:
+%
+% xx = [x1, x2, ..., xd]
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+d = length(xx);
+fact1 = (1 + 1/d)^d;
+
+prod = 1;
+for ii = 1:d
+    xi = xx(ii);
+    prod = prod * (xi)^(1/d);
+end
+
+y = fact1 * prod;
+
+end
+

### 2015-06-15 FunctionsTest/bratley.m
First commit

@@ -1,5 +1,4 @@
 
-
 function [y] = bratleyetal92(xx)
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-06-15 FunctionsTest/bratley.m
Some examples of functions test

@@ -1,4 +1,5 @@
 
+
 function [y] = bratleyetal92(xx)
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@ -48,4 +49,6 @@ end
 y = sum;
 
 end
+
+
 

### 2015-06-15 FunctionsTest/gfunction.m

@@ -1,3 +1,5 @@
+
+
 function [y] = gfunc(xx, a)
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@ -55,3 +57,5 @@ end
 y = prod;
 
 end
+
+

### 2015-06-15 FunctionsTest/ishigami.m

@@ -54,3 +54,5 @@ term3 = b * x3^4 * sin(x1);
 y = term1 + term2 + term3;
 
 end
+
+

### 2015-06-15 FunctionsTest/morokoff.m

@@ -47,3 +47,5 @@ y = fact1 * prod;
 
 end
 
+
+

### 2015-07-16 SobolIndices.tex
Update SobolIndices.tex
Adding some more notes and starting code for the computations.

@@
 for all $b_\ell \le a_\ell \le c_\ell$.  When we get 
-\begin{multline*}
+\begin{multline}\label{stopping_crit}
 \hS_j(\hI_{1,m}(f) + \oerr_{1,m}(f), \ldots,\hI_{q,m}(f) + \oerr_{q,m}(f), \ldots \\
@@
  \hI_{1,m}(f) + \oerr_{1,m}(f), \ldots,\hI_{q,m}(f) + \oerr_{q,m}(f))   \le 2\varepsilon, \quad j = 1, \ldots, p
-\end{multline*}
+\end{multline}
 we may stop and choose 
@@
 
+$$\mu=\mathbb{E}\left[f(\underline{X})\right]=\int_{[0,1]^d} f(\underline{x}) d \underline{x} \, .$$
+$$\Var \left(f(\underline{X})\right)=\int_{[0,1]^d}\left(f(\underline{x})-\mu\right)^2d \underline{x} =\int_{[0,1]^d}\left(f(\underline{x})\right)^2d \underline{x} - \mu^2 \, .$$
+$$\mu_j(x)=\mathbb{E}\left[f(\underline{X})|X_j=x\right]=\int_{[0,1]^{d-1}} f(\underline{t}_{-j},x)d\underline{t}_{-j} \, .$$
+$$\begin{array}{rcl}
+\mathbb{E}\left\{ \Var \left(f(\underline{X})|X_j\right)\right\} & = &\int_{0,1]^d}\left[f(\underline{x}\right]^2 d \underline{x} - \int_0^1 \mu_j^2(x) dx  \\
+&=& \int_{[0,1]^d}\left[f(\underline{x}\right]^2 d \underline{x} - \int_{[0,1]^{2d-1}}f(\underline{x})f(\underline{x}'_{-j},x_j)d \underline{x} d \underline{x}'_{-j} \, . 
+\end{array}$$
+
+$$\mu_{-j}(\underline{x}_{-j})=\mathbb{E}\left[f(\underline{X})|X_{-j}=\underline{x}_{-j}\right]=\int_0^1 f({t}_{j},\underline{x}_{-j})d {t}_{j} \, .$$
+$$\begin{array}{rcl}
+\mathbb{E}\left\{ \Var \left(f(\underline{X})|\underline{X}_{-j}\right)\right\} & = &\int_{[0,1]^d}\left[f(\underline{x}\right]^2 d \underline{x} - \int_{[0,1]^{d-1}} \mu_{-j}^2(\underline{x}_{-j}) d \underline{x}_{-j}  \\
+&=& \int_{[0,1]^d}\left[f(\underline{x}\right]^2 d \underline{x} - \int_{[0,1]^{d+1}}f(\underline{x})f(x'_{j},\underline{x}_{-j})d \underline{x} d {x}'_{j} \, . 
+\end{array}$$
+
+\bigskip
+
+$$S_{j}=1-\frac{\mathbb{E}\left\{ \Var \left(f(\underline{X})|X_j\right)\right\}}{\Var\left(f(\underline{X})\right)}= \frac{N_j}{D}\, .$$
+$$S_{j}^{\textup{tot}}=\frac{\mathbb{E}\left\{ \Var \left(f(\underline{X})|\underline{X}_{-j}\right)\right\} }{\Var\left(f(\underline{X})\right)}=\frac{N_j^{\textup{tot}}}{D}\, .$$
+
+As $N_j$, $N_j^{\textup{tot}}$ and $D$ can be written as sums of integrals,
+one can guarantee with the existing code the existence of error terms $\tilde{\oerr}_{j,m}(f)$, $\tilde{\oerr}_{j,m}^{\textup{tot}}(f)$ and $\tilde{\oerr}_m(f)$ such that
+
+$$\hat{N}_{j,m}-\tilde{\oerr}_{j,m}(f) \leq N_j \leq \hat{N}_{j,m}+\tilde{\oerr}_{j,m}(f)  \, ,$$
+$$\hat{N}_{j,m}^{\textup{tot}}-\tilde{\oerr}_{j,m}^{\textup{tot}}(f) \leq N_j^{\textup{tot}} \leq \hat{N}_{j,m}^{\textup{tot}}+\tilde{\oerr}_{j,m}^{\textup{tot}}(f) \, ,$$
+$$\hat{D}_{m}-\tilde{\oerr}_{m}(f) \leq D \leq \hat{D}_{m}+\tilde{\oerr}_{m}(f)  \, .$$
+
+Thus
+
+\begin{equation}\label{err_bound_j}
+\frac{\hat{N}_{j,m}-\tilde{\oerr}_{j,m}(f)}{\hat{D}_{m}+\tilde{\oerr}_{m}(f) } \leq \frac{N_j}{D} \leq \frac{\hat{N}_{j,m}+\tilde{\oerr}_{j,m}(f)}{\hat{D}_{m}-\tilde{\oerr}_{m}(f) }\, ,
+\end{equation}
+\begin{equation}\label{err_bound_jtot}
+\frac{\hat{N}_{j,m}^{\textup{tot}}-\tilde{\oerr}_{j,m}^{\textup{tot}}(f) }{\hat{D}_{m}+\tilde{\oerr}_{m}(f)} \leq \frac{N_{j}^{\textup{tot}}}{D} \leq \frac{ \hat{N}_{j,m}^{\textup{tot}}+\tilde{\oerr}_{j,m}^{\textup{tot}}(f)}{\hat{D}_{m}-\tilde{\oerr}_{m}(f)} \, .
+\end{equation}
+
 \bigskip
@@
 
+Domains for integrals $N_j$ and $N_j^{\textup{tot}}$ can be rearranged to consider them as a single integral:
+\begin{align*}
+\mathbb{E}\left[ \Var \left(f(\underline{X})|X_j\right)\right] & = \int_{[0,1)^d}f(\underline{x})^2 d \underline{x} - \int_{[0,1)^{2d-1}}f(\underline{x})f(\underline{x}'_{-j},x_j)d \underline{x} d \underline{x}'_{-j} \\
+& = \int_{[0,1)^{2d-1}}\left(f(\underline{x})^2-f(\underline{x})\right)f(\underline{x}'_{-j},x_j)d \underline{x} d \underline{x}'_{-j} \, . 
+\end{align*}
+
+\begin{align*}
+\mathbb{E}\left[ \Var \left(f(\underline{X})|\underline{X}_{-j}\right)\right] & = \int_{[0,1)^d}f(\underline{x})^2 d \underline{x} - \int_{[0,1)^{d+1}}f(\underline{x})f(x'_{j},\underline{x}_{-j})d \underline{x} d {x}'_{j} \\
+& = \int_{[0,1)^{d+1}}\left(f(\underline{x})^2-f(\underline{x})\right)f(x'_{j},\underline{x}_{-j})d \underline{x} d {x}'_{j} \, . 
+\end{align*}
+
+However, because $D$ is a nonlinear combination of integrals over different domains, it needs to be split into 2 parts:
+
+\begin{align*}
+\Var \left(f(\underline{X})\right) & = \int_{[0,1)^d}f(\underline{x})^2 d \underline{x} - \left(\int_{[0,1)^d}f(\underline{x}) d \underline{x}\right)^2 \\
+& = D_1 - D_2^2 \, .
+\end{align*}
+
+Namely $a_1^{(j)} :=\mathbb{E}\left[ \Var \left(f(\underline{X})|X_j\right)\right]$, $a_2^{(j)} := \mathbb{E}\left[ \Var \left(f(\underline{X})|\underline{X}_{-j}\right)\right]$, $a_3^{(j)} := D_1$ and $a_4^{(j)} := D_2$ (we will spare the ${(j)}$ notation for simplicity), we have:
+
+\begin{equation}
+S(a_1,\dots,a_4)=1-\frac{a_1}{a_3-a_4^2} \; , \qquad S^\textup{tot}(a_1,\dots,a_4)=\frac{a_2}{a_3-a_4^2} \, .
+\end{equation}
+that directly leads to,
+\begin{equation}\label{functionals_stop_criteria}
+\hS(b_1,\dots,b_4,c_1,\dots,c_4)=1-\frac{c_1}{b_3-c_4^2} \; , \qquad \hS^\textup{tot}(b_1,\dots,b_4,c_1,\dots,c_4)=\frac{b_2}{c_3-b_4^2} \, .
+\end{equation}
+Remark that if we have some a priori knowledge of $a_4$, $c_4^2$ can be replaced by $c_4$ and $b_4^2$ by $b_4$ depending on whether $a_4 \leq 1$ or $a_4 \geq 1$ respectively.
+This would provide tighter bounds.
+
+According to \eqref{functionals_stop_criteria},
+\begin{equation}
+\hS^\textup{tot}(b_1,b_2,b_3,b_4,c_1,c_2,c_3,c_4) = 1 - \hS(b_1,c_1,c_3,c_4,b_2,c_2,b_3,b_4) \, .
+\end{equation}
+Hence, we do not really need a second estimator $\hS^\textup{tot}$.
+For further clarity, we can also set to $0$ the variables not affecting our estimators, $\hS(b_1,0,b_3,b_4,c_1,0,c_3,c_4)$ and $1-\hS(0,0,c_3,c_4,b_2,c_2,b_3,b_4)$.
+
+From here, we can use the stopping criteria proposed in \eqref{stopping_crit}.
+
 \end{document}

### 2015-07-16 FunctionsTest/cubSobol_SI_g.m

@@ -1,0 +1,682 @@
+function [q,out_param] = cubSobol_SI_g(varargin)
+%CUBSOBOL_G Quasi-Monte Carlo method using Sobol' cubature over the
+%d-dimensional region to integrate within a specified generalized error
+%tolerance with guarantees under Walsh-Fourier coefficients cone decay
+%assumptions
+%
+%   [q,out_param] = CUBSOBOL_SI_G(f,hyperbox,u) estimates the integral of f
+%   over the d-dimensional region described by hyperbox, and with an error
+%   guaranteed not to be greater than a specific generalized error tolerance,
+%   tolfun:=max(abstol,reltol*| integral(f) |). Input f is a function handle. f should
+%   accept an n x d matrix input, where d is the dimension and n is the 
+%   number of points being evaluated simultaneously. The input hyperbox is
+%   a 2 x d matrix, where the first row corresponds to the lower limits 
+%   and the second row corresponds to the upper limits of the integral.
+%   Given the construction of Sobol' sequences, d must be a positive 
+%   integer with 1<=d<=1111.
+%
+%   q = CUBSOBOL_G(f,hyperbox,measure,abstol,reltol)
+%   estimates the integral of f over the hyperbox. The answer
+%   is given within the generalized error tolerance tolfun. All parameters
+%   should be input in the order specified above. If an input is not specified,
+%   the default value is used. Note that if an input is not specified,
+%   the remaining tail cannot be specified either. Inputs f and hyperbox 
+%   are required. The other optional inputs are in the correct order:
+%   measure,abstol,reltol,mmin,mmax,fudge,toltype and
+%   theta.
+%
+%   q = CUBSOBOL_G(f,hyperbox,'measure',measure,'abstol',abstol,'reltol',reltol)
+%   estimates the integral of f over the hyperbox. The answer
+%   is given within the generalized error tolerance tolfun. All the field-value
+%   pairs are optional and can be supplied in any order. If an input is not
+%   specified, the default value is used.
+%
+%   q = CUBSOBOL_G(f,hyperbox,in_param) estimates the integral of f over the
+%   hyperbox. The answer is given within the generalized error tolerance tolfun.
+% 
+%   Input Arguments
+%
[…]

### 2015-07-17 FunctionsTest/cubSobol_SI_g.m
Finishing the algorithm for the Sobol Indices with examples and fixing a few typos.

@@ -1,13 +1,13 @@
 function [q,out_param] = cubSobol_SI_g(varargin)
-%CUBSOBOL_G Quasi-Monte Carlo method using Sobol' cubature over the
-%d-dimensional region to integrate within a specified generalized error
+%cubSobol_SI_g Quasi-Monte Carlo method using Sobol' cubature over the
+%d-dimensional region to compute the Sobol Index within a specified generalized error
 %tolerance with guarantees under Walsh-Fourier coefficients cone decay
 %assumptions
 %
-%   [q,out_param] = CUBSOBOL_SI_G(f,hyperbox,u) estimates the integral of f
-%   over the d-dimensional region described by hyperbox, and with an error
+%   [q,out_param] = CUBSOBOL_SI_G(f,hyperbox,u) estimates the Sobol Index of f
+%   over dimension u and region described by hyperbox, and with an error
 %   guaranteed not to be greater than a specific generalized error tolerance,
-%   tolfun:=max(abstol,reltol*| integral(f) |). Input f is a function handle. f should
+%   tolfun:=max(abstol,reltol*| SI(f) |). Input f is a function handle. f should
 %   accept an n x d matrix input, where d is the dimension and n is the 
 %   number of points being evaluated simultaneously. The input hyperbox is
 %   a 2 x d matrix, where the first row corresponds to the lower limits 
@@ -15,8 +15,8 @@ function [q,out_param] = cubSobol_SI_g(varargin)
 %   Given the construction of Sobol' sequences, d must be a positive 
 %   integer with 1<=d<=1111.
 %
-%   q = CUBSOBOL_G(f,hyperbox,measure,abstol,reltol)
-%   estimates the integral of f over the hyperbox. The answer
+%   q = CUBSOBOL_SI_G(f,hyperbox,u,measure,abstol,reltol)
+%   estimates the Sobol Index of f over dimension u and hyperbox. The answer
 %   is given within the generalized error tolerance tolfun. All parameters
 %   should be input in the order specified above. If an input is not specified,
[…]

### 2015-09-10 FunctionsTest/cubSobol_SI_g.m
Fixing nec conditions cubSobol_SI_g

@@ -228,12 +228,15 @@ function [q,int,out_param] = cubSobol_SI_g(varargin)
 %   above papers, software, and materials.
 %
 
-tic
+t_start = tic;
 %% Initial important cone factors and Check-initialize parameters
 r_lag = 4; %distance between coefficients summed and those computed
 [f,hyperbox,out_param] = cubSobol_SI_g_param(r_lag,varargin{:});
 u = out_param.u;
 l_star = out_param.mmin - r_lag; % Minimum gathering of points for the sums of DFWT
+omg_circ = @(m) 2.^(-m);
+omg_hat = @(m) out_param.fudge(m)/((1+out_param.fudge(r_lag))*omg_circ(r_lag));
+
 if u > 0
     S = @(b,c) 1 - c(:,1)./(b(:,2)-c(:,3).^2);
 else
@@ -315,14 +318,16 @@ int = est_int_k(1,3);
 % Necessary conditions for all three integrals
 for k = 1:size(y,2)
     for l = l_star:out_param.mmin % Storing the information for the necessary conditions
-        C_low = (1+out_param.fudge(out_param.mmin-l))/(1+2*out_param.fudge(out_param.mmin-l));
-        C_up = (1+out_param.fudge(out_param.mmin-l));
-        CStilde_low(l-l_star+1,k) = C_low*sum(abs(y(kappanumap(2^(l-1)+1:2^l,k),k)));
-        CStilde_up(l-l_star+1,k) = C_up*sum(abs(y(kappanumap(2^(l-1)+1:2^l,k),k)));
-    end
-    if any(CStilde_low(:,k) > CStilde_up(:,k))
-       out_param.exit(2) = true;
-    end
+        C_low = 1/(1+omg_hat(out_param.mmin-l)*omg_circ(out_param.mmin-l));
+    	C_up = 1/(1-omg_hat(out_param.mmin-l)*omg_circ(out_param.mmin-l));
+	CStilde_low(l-l_star+1,k) = max(CStilde_low(l-l_star+1,k),C_low*sum(abs(y(kappanumap(2^(l-1)+1:2^l)))));
+	if (omg_hat(out_param.mmin-l)*omg_circ(out_param.mmin-l) < 1)
+		CStilde_up(l-l_star+1,k) = min(CStilde_up(l-l_star+1,k),C_up*sum(abs(y(kappanumap(2^(l-1)+1:2^l)))));
+	end
+     end
[…]

### 2016-02-16 SobolIndices.tex
Finishing the algorithm for the Sobol Indices with examples and fixing a few typos.
small change
Fixing nec conditions cubSobol_SI_g
Adding old examples and the beginning of the article

@@
 \newcommand{\oerr}{e}
+\newcommand{\verr}{\boldsymbol{\varepsilon}}
+\newcommand{\tverr}{\tilde{\boldsymbol{\varepsilon}}}
+\newcommand{\terr}{\tilde{\varepsilon}}
+\newcommand{\vI}{\bvec{I}}
+\newcommand{\tx}{\tilde{x}}
 
@@
 \mathbb{E}\left[ \Var \left(f(\underline{X})|X_j\right)\right] & = \int_{[0,1)^d}f(\underline{x})^2 d \underline{x} - \int_{[0,1)^{2d-1}}f(\underline{x})f(\underline{x}'_{-j},x_j)d \underline{x} d \underline{x}'_{-j} \\
-& = \int_{[0,1)^{2d-1}}\left(f(\underline{x})^2-f(\underline{x})\right)f(\underline{x}'_{-j},x_j)d \underline{x} d \underline{x}'_{-j} \, . 
+& = \int_{[0,1)^{2d-1}}\left[f(\underline{x})^2-f(\underline{x})f(\underline{x}'_{-j},x_j)\right] d \underline{x} d \underline{x}'_{-j} \, . 
 \end{align*}
@@
 \mathbb{E}\left[ \Var \left(f(\underline{X})|\underline{X}_{-j}\right)\right] & = \int_{[0,1)^d}f(\underline{x})^2 d \underline{x} - \int_{[0,1)^{d+1}}f(\underline{x})f(x'_{j},\underline{x}_{-j})d \underline{x} d {x}'_{j} \\
-& = \int_{[0,1)^{d+1}}\left(f(\underline{x})^2-f(\underline{x})\right)f(x'_{j},\underline{x}_{-j})d \underline{x} d {x}'_{j} \, . 
+& = \int_{[0,1)^{d+1}}\left[f(\underline{x})^2-f(\underline{x})f(x'_{j},\underline{x}_{-j})\right] d \underline{x} d {x}'_{j} \, . 
 \end{align*}
@@
 
+\section{Improving Error Bounds for Stopping Criteria}
+Consider the previous function ($\vx:=\vI$)
+\[
+f(\vx)=1-\frac{x_1}{x_2-x_3^2},\quad \vx\in[\tvx-\tverr,\tvx+\tverr].
+\]
+If our estimator is 
+\[
+\tf(\tvx)=\frac{1}{2}\left(f(\tx_1+\terr_1,\tx_2-\terr_2,\tx_3+\terr_3)+f(\tx_1-\terr_1,\tx_2+\terr_2,\tx_3-\terr_3)\right),
+\]
+we know that the error bound is clearly
+\begin{align*}
+\abs{f(\vx)-\tf(\tvx)}\leq\frac{1}{2} \abs{\frac{\tx_1+\terr_1}{\tx_2-\terr_2-\left(\tx_3+\terr_3\right)^2}-\frac{\tx_1-\terr_1}{\tx_2+\terr_2-\left(\tx_3-\terr_3\right)^2} }.
+\end{align*}
+If $\varepsilon_2=\varepsilon_3=0$, this error bound would directly be linear on $\varepsilon_1$. However, the difference in the denominators makes this error bound not clearly linearly convergent.
+
+If we consider the Taylor expansion of our function with $\vx-\tvx=\verr$ (the difference is the real error $\verr\in[-\tverr,\tverr]$):
+\begin{equation}
+f(\vx)=f(\tvx)+\nabla f(\tvx)^t\verr+\frac{1}{2}\verr^t Hf(\tvx) \verr + \mathcal{O}(\norm{\verr}^3),
+\end{equation}
+we can take the following estimator,
+\begin{align*}
+\tf(\tvx)&=\frac{1}{2}\left(f(\tvx)+\nabla f(\tvx)^t\tverr+\frac{1}{2}\tverr^t Hf(\tvx) \tverr + f(\tvx)+\nabla f(\tvx)^t(-\tverr)+\frac{1}{2}(-\tverr)^t Hf(\tvx) (-\tverr) \right)\\
+&=f(\tvx)+\frac{1}{2}\tverr^t Hf(\tvx) \tverr
+\end{align*}
+Thus, given that $Hf$ is symmetric, differentiable in the region of interest (denominator always positive), the error will be bounded by
+\begin{align*}
+\abs{f(\vx)-\tf(\tvx)}&=\abs{\nabla f(\tvx)^t\verr+\frac{1}{2}\left(\verr+\tverr\right)^t Hf(\tvx) \left(\verr-\tverr\right) + \mathcal{O}(\norm{\verr}^3)} \\
+&\leq \max_{\vy\in[\tvx-\tverr,\tvx+\tverr], \vz\in[-\tverr,\tverr]}\abs{\nabla f(\tvx)^t\vz+\frac{1}{2}(\vz+\tverr)^t Hf(\vy)(\vz-\tverr)}
+\end{align*}
+
+Clearly, because of signs the maximum $\vz$ is for $\vz=\{-\tilde{\varepsilon_1},\tilde{\varepsilon_2},-\tilde{\varepsilon_3}\}$.
+
 \end{document}

### 2016-02-16 article.tex
Adding old examples and the beginning of the article

% !TEX TS-program = PDFLatexBibtex
%&LaTeX
\documentclass[]{elsarticle}
\setlength{\marginparwidth}{0.5in}
\usepackage{amsmath,amssymb,amsthm,natbib,mathtools,bbm,extraipa,mathabx,graphicx}
%accents,

\newtheorem{lem}{Lemma}
\newtheorem{remark}{Remark}
\theoremstyle{definition}
\newtheorem{defin}{Definition}
\newtheorem{algo}{Algorithm}

\newcommand{\fudge}{\fC}
\newcommand{\dtf}{\textit{\doubletilde{f}}}
\newcommand{\cube}{[0,1)^d}
%\renewcommand{\bbK}{\natzero^d}
\newcommand{\rf}{\mathring{f}}
\newcommand{\rnu}{\mathring{\nu}}
\newcommand{\natm}{\naturals_{0,m}}
\newcommand{\wcS}{\widecheck{S}}
\newcommand{\tol}{\text{tol}}
\newcommand{\e}{\text{e}}
\newcommand{\bvec}[1]{\boldsymbol{#1}}
\newcommand{\vx}{\bvec{x}}
\newcommand{\vk}{\bvec{k}}
\newcommand{\vz}{\bvec{z}}
\newcommand{\dif}{\mathsf{d}}
\newcommand{\hf}{\hat{f}}
\newcommand{\hS}{\widehat{S}}
\newcommand{\tS}{\widetilde{S}}
\newcommand{\tf}{\tilde{f}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\homega}{\widehat{\omega}}
\newcommand{\wcomega}{\mathring{\omega}}
\newcommand{\vzero}{\bvec{0}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\naturals}{\mathbb{N}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}

\def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}

\begin{document}

\begin{frontmatter}

\title{Reliable error estimation for Sobol' indices}

\author{Cl\'ementine Prieur, Elise Arnaud, Laurent Gilquin, Fred J. Hickernell, Llu\'{i}s Antoni Jim\'{e}nez Rugama}
\address{U. Josef Fourier, Illinois Institute of Technology}
\begin{abstract}
\end{abstract}

\end{frontmatter}

\section{Introduction}

\section{Sensibility Analysis}
\subsection{Background}
\subsection{Replication Method}
\subsection{Sobol' Indices}

\section{Reliable Error Estimation for Cubatures}

\section{Sobol' Sequences and Permuted Points}

\end{document}

### 2016-02-16 FunctionsTest/SI_example.m

@@ -1,6 +1,6 @@
 clearvars
 
-abstol = 1e-3;
+abstol = 1e-4;
 reltol = 0; % Pure absolute tolerance
 mmax = 22; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
 
@@ -36,6 +36,7 @@ hyperbox = [zeros(1,d) ; ones(1,d)];
 
 exitflag = [];
 exitflagt = [];
+tic
 for j = 1:d
     [q,app_int,out_param] = cubSobol_SI_g(f,hyperbox,j,'abstol',abstol,'reltol',reltol,'mmax',mmax);
     exitflag = [exitflag out_param.exitflag];
@@ -44,6 +45,7 @@ for j = 1:d
     exitflagt = [exitflagt out_param.exitflag];
     SI(2,j) = q;
 end
+toc
 disp(SI)
 if any(exitflag > 0) || any(exitflagt > 0)
     warning('Results cannot be guaranteed due to reaching maximum budget or failing necessary conditions.')

### 2016-02-16 FunctionsTest/SI_finance_example.m

@@ -5,27 +5,8 @@ reltol = 0; % Pure absolute tolerance
 mmax = 22; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
 
 
-%% European Call with PCA
-S0 = 100; K = 100; sgma = 0.05; r = sgma^2/2; T = 1; price = normcdf((log(S0/K)+(r+sgma^2/2)*T)/(sgma*sqrt(T)))*S0 - normcdf((log(S0/K)+(r-sgma^2/2)*T)/(sgma*sqrt(T)))*K*exp(-r*T);
-
-d = 8;
-time_disc = linspace(T/d,T,d);
-Sigma=bsxfun(@min,time_disc',time_disc);  % Sigma(i,j) = min(time_disc(i),time_disc(j))
-[Evec,Eval]=eig(Sigma,'vector'); % Jordan decomposition of Sigma
-[~,order] = sort(Eval,'descend');
-A = Evec(:,order)*diag(Eval(order).^(1/2)); % A*A' = Sigma. PCA substitution
-
-
-f = @(x) max(0,(S0*exp((r-sgma^2/2)*bsxfun(@plus,time_disc,zeros(size(x,1),1))+sgma*norminv(x)*A'))*[zeros(d-1,1);1]-K);
-hyperbox = [zeros(1,d) ; ones(1,d)];
-
-j = 1;
-[SI, approx_price, out_param] = cubSobol_SI_g(f,hyperbox,j,'abstol',abstol,'reltol',reltol,'mmax',mmax);
-SI
-approx_price
-
-% %% Geometric Asian Option with PCA
-% S0 = 100; K = 100; sgma = 0.05; r = sgma^2/2; T = 1; price = 000;
+% %% European Call with PCA
+% S0 = 100; K = 100; sgma = 0.05; r = sgma^2/2; T = 1; price = normcdf((log(S0/K)+(r+sgma^2/2)*T)/(sgma*sqrt(T)))*S0 - normcdf((log(S0/K)+(r-sgma^2/2)*T)/(sgma*sqrt(T)))*K*exp(-r*T);
 % 
 % d = 8;
 % time_disc = linspace(T/d,T,d);
@@ -34,10 +15,34 @@ approx_price
 % [~,order] = sort(Eval,'descend');
 % A = Evec(:,order)*diag(Eval(order).^(1/2)); % A*A' = Sigma. PCA substitution
[…]

### 2016-03-10 article.tex
Updating all changes so far. Includes both articles as article.tex and replicated_sobol.tex

@@
 
+\section{Estimators---> Correlation 2 Oracle 2}
+\subsection{Choice and parameters (threshold small)}
+\subsection{Cost discussion ---> Consider or not total order}
+Cost small:\[n(d+1)+d_sn+n\]
+Cost pas small:\[\alpha n d_s +n+(d-d_s)n\]
+Cost small - cost pas small: \[n\sum_{i=1}^{s}(2-\alpha_i+1)\] $s$ number of small indices, $alhpa_i$ proportion of how many more points if not pas small
+
 \section{Sensibility Analysis}
@@
 \section{Reliable Error Estimation for Cubatures}
+\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
 
 \section{Sobol' Sequences and Permuted Points}
+7 digits $L$ bi/tri diagonal but $L'$ identity up 7 digits.
+Fix $L_j$ for each dimension differently?
+If we fix the initial number of digits to 7, we have $7!$ different permutations of the points or Owen scramblings which means that if we take $d$ such that $2d>7!$, some dimensions will share the same points.
+Therefore, we need to scramble each dimension differently ($L'$).
 

### 2016-03-10 replicated_sobol.tex
Updating all changes so far. Includes both articles as article.tex and replicated_sobol.tex

% !TEX TS-program = PDFLatexBibtex
%&LaTeX
\documentclass[]{elsarticle}
\setlength{\marginparwidth}{0.5in}
\usepackage{amsmath,amssymb,amsthm,natbib,mathtools,bbm,extraipa,mathabx,graphicx}
%accents,

\newtheorem{lem}{Lemma}
\newtheorem{remark}{Remark}
\theoremstyle{definition}
\newtheorem{defin}{Definition}
\newtheorem{algo}{Algorithm}

\newcommand{\fudge}{\fC}
\newcommand{\dtf}{\textit{\doubletilde{f}}}
\newcommand{\cube}{[0,1)^d}
%\renewcommand{\bbK}{\natzero^d}
\newcommand{\rf}{\mathring{f}}
\newcommand{\rnu}{\mathring{\nu}}
\newcommand{\natm}{\naturals_{0,m}}
\newcommand{\wcS}{\widecheck{S}}
\newcommand{\tol}{\text{tol}}
\newcommand{\e}{\text{e}}
\newcommand{\bvec}[1]{\boldsymbol{#1}}
\newcommand{\vx}{\bvec{x}}
\newcommand{\vk}{\bvec{k}}
\newcommand{\vz}{\bvec{z}}
\newcommand{\dif}{\mathsf{d}}
\newcommand{\hf}{\hat{f}}
\newcommand{\hS}{\widehat{S}}
\newcommand{\tS}{\widetilde{S}}
\newcommand{\tf}{\tilde{f}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\homega}{\widehat{\omega}}
\newcommand{\wcomega}{\mathring{\omega}}
\newcommand{\vzero}{\bvec{0}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\naturals}{\mathbb{N}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}

\def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}

\begin{document}

\begin{frontmatter}

\title{}

\author{Cl\'ementine Prieur, Elise Arnaud, Herv\'{e} Monod, Laurent Gilquin, Fred J. Hickernell, Llu\'{i}s Antoni Jim\'{e}nez Rugama}
\address{U. Josef Fourier, Illinois Institute of Technology}
\begin{abstract}
\end{abstract}

\end{frontmatter}

\section{Problem Statement}
Denote by $\vx \in [0,1)^d$ a point with components $x_1,\dots,x_d$. Let $u$ be a subset of $\{1,\dots,d\}$, $-u$ its complement and $|u|$ its cardinality. $\vx_u$ represents a point in $[0,1)^u$ with components $x_j, j \in u$. Given two points $\vx$ and $\vx'$, we define the following hybrid point: 
\[(\vx_u:{\vx'}_{-u}) := ({x'}_1,\dots,{x'}_{u-1},x_u,{x'}_{u+1},\dots,{x'}_d).\]
Let $f$ be the symbol representing the numerical model considered. We assume $f \in \mathcal{L}^2[0,1]^d$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
%These two quantities can be expressed as the following integrals:
%\[\mu= \frac{1}{2} \int_{[0,1)^{2d-1}}f(\vx)+f(\vx_u:{\vx'}_{-u}) d\vx d{\vx'}_{-u}, \]
%\[\sigma^2= \int_{[0,1)^{d}}f(\vx)^2 d\vx - \Big{(}\int_{[0,1)^{d}}f(\vx) d\vx\Big{)}^2 .\]
The uncertainty on $\vx$ is modeled by random variables such that $\vx \sim \mathcal{U}[0,1]^d$. Recall the Hoeffding decomposition of $f$:
\begin{equation}
f(\vx)=\mu+\sum \limits_{u \subseteq \{1,\dots,d\}} f_u(\vx),
\label{anova}
\end{equation}
where:
\[f_u(\vx)= \int_{[0,1)^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).\]
Due to orthogonality, by taking the variance of each side in Equation \ref{anova} we obtain the following decomposition of the variance:
\[ \sigma^2 = \sum \limits_{u \subseteq \{1,\dots,d\}} \sigma_v^2.\]
The problem of interest is the estimation of the quantities:
\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad \text{ for } u = 1,\dots,d.\]
These quantities correspond to the partial sensitivity Sobol' indices often found written in the literature in their normalized form: $\underline{\tau}_u^2/\sigma^2$. When, $|u|=1$, $\underline{\tau}_u^2$ corresponds to the first-order Sobol' index that evaluate the main effect of the variable $\vx_u$. In \cite{}, Owen proposed to use the following expression for $\underline{\tau}_u^2$:
\[\underline{\tau}_u^2  =\int_{[0,1)^{2d-1}}(f(\vx) - \mu) (f(\vx_u:{\vx'}_{-u})-\mu) d\vx d{\vx'}_{-u},\]
taking $\mu$ as introduced in Janon \textit{et al.}:
\[\mu= \frac{1}{2} \int_{[0,1)^{2d-1}}f(\vx)+f(\vx_u:{\vx'}_{-u}) d\vx d{\vx'}_{-u}. \]
The natural way to estimate these two quantities is for $(\vx_i,\vx'_i) \stackrel{iid}{\sim} [0,1)^{2d}$ via:
\begin{align*}
\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=1}^n (f(\vx_i) - \mu) (f(\vx_{i,u}:{\vx'}_{i,-u})-\mu),\\
\widehat{\mu} & = \frac{1}{2n} \sum \limits_{i=1}^n f(\vx_i) +f(\vx_{i,u}:{\vx'}_{i,-u}).
\end{align*}
\bigskip

We consider here a quasi-Monte Carlo sampling strategy to evaluate these two estimators. We focus on the estimation of all first-order Sobol' indices. The classical estimation procedure introduced by Sobol' requires to evaluate the quantity $f(\vx_u:{\vx'}_{-u})$ $n$ times for each $u \in \{1,\dots,d\}$ while the quantity $f(\vx)$ is only evaluated $n$ times once for all $u$. The total cost sums up to $n(d+1)$ evaluations of $f$. This cost can rapidly becomes prohibitive for expansive models involving an important number of parameters. An improvement to reduces this cost lies in the use of replicated designs. The notion of replicated designs was first introduced by McKay. It is defined as follows:
\begin{defin}[Replicated designs]
Let $X$ and $X'$ be two designs defined as follow:
\[\arraycolsep=1.3pt
X=\left(\begin{array}{ccccc}
x_{1,1} & ... & x_{1,j} & ... & x_{1,d} \\
\vdots &  & \vdots & & \vdots \\
x_{i,1} & ... & x_{i,j} & ... & x_{i,d} \\
\vdots &  & \vdots & & \vdots \\
x_{n,1} & ... & x_{n,j} & ... & x_{n,d} \\
\end{array} \right), \ X'=\left(\begin{array}{ccccc}
{x'}_{1,1} & ... & {x'}_{1,j} & ... & {x'}_{1,d} \\
\vdots &  & \vdots & & \vdots \\
{x'}_{i,1} & ... & {x'}_{i,j} & ... & {x'}_{i,d} \\
\vdots &  & \vdots & & \vdots \\
{x'}_{n,1} & ... & {x'}_{n,j} & ... & {x'}_{n,d} \\
\end{array} \right) 
\]
Let the symbol $X_u$ (resp. $X'_u$), $u \subsetneq \{1,\dots,d-1\}$, denotes a subset of $u$ columns of $X$ (resp. $X'$). We say that $X$ and $X'$ are two replicated designs of order $r \in \{1,\dots,d-1\}$ if:

$\forall \ u \subsetneq \{1,\dots,d\}$ such that $|u|=r$, $X_u$ and $X'_u$ represent the same point sets.
\end{defin}
The replication procedure introduced in \cite{} allows to estimate all first-order Sobol' indices with two replicated designs of order $1$. In this procedure, the quantity $f(\vx_u:{\vx'}_{-u})$ is only evaluated $n$ times once for all $u$ resulting in a total of $2n$ evaluations of $f$. Denote by $X$,$X'$ the two replicated designs of order $1$ required by the replication procedure, $X'$ is constructed from $X$ as follows:
\[{x'}_{i,j}=x_{\pi_j(i),j}, \qquad \forall \ (i,j) \in \{1,\dots,n\} \times \{1,\dots,d\},\]
where $\pi_1,\dots,\pi_d$ are $d$ permutations on $\{1,\dots,n\}$.
\bigskip

Our objective is to combine the use of Sobol' sequence with the replication method to estimate all quantities $\underline{\tau}_u^2, u \in \{1,\dots,d\}$ with only $2n$ evaluations of $f$. This translates to construct two Sobol' sequence that identify as two replicated designs of order $1$.

\section{Sobol' sequence background}
Obviously, we do not need to evaluate $f(\vx)$ $d$ times. But we can do event better than that, and evaluate $f(\vx_u:{\vx'}_{-u})$ only one time. This is the replication method....

$X$,$X'$ are two sequences such that,
\[
X = \begin{pmatrix}
x_1^1,\dots,x_1^d \\
x_2^1,\dots,x_2^d \\
x_3^1,\dots,x_3^d \\
\end{pmatrix} \\
X' = \begin{pmatrix}
\pi_1(x_1^1),\dots,\pi_d(x_1^d) \\
\pi_1(x_2^1),\dots,\pi_d(x_2^d) \\
\pi_1(x_3^1),\dots,\pi_d(x_3^d) \\
\end{pmatrix}
\]

These sequences can be generated indeed with Owen scramblings, or which is equivalent, matrix generators $C_i$

Be $U_m(\mathbb{F}_b)$ the multiplicative group of all invertible triangular matrices of size $m\times m$ over $\mathbb{F}_b$ ($GF(b)$). We have that $\abs{U_m(\mathbb{F}_b)}=(b-1)^m b^{(m-1)m/2}$.

We consider the (infinite) set all possible generating matrices $C_1,C_2,\dots$. We also define the class

Indeed, we inherit all the group properties from the Permuatations group... because it is equivalent....

Not all choices are possible, for instance order 2 and higher Sobol' indices.

\section{There Is The Addition Method I Do Not Know}

\section{L Matrices Fred Method Too Restrictive}

\end{document}

### 2016-03-10 FunctionsTest/SI_all_example.m

@@ -1,0 +1,208 @@
+clearvars
+
+abstol = 1e-3;
+reltol = 0e-2; % Pure absolute tolerance
+mmin = 10;
+mmax = 22; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
+wronga = 0; % Wrong estimates with all indices method
+wrong = 0; % Wrong estimates using the one by one algo
+s = .0; %time in seconds used delay each function evaluation
+
+fudge = @(m,d) 5*2.^-(m);
+
+%% Ishigami
+disp('Running Ishigami example ...')
+d = 3;
+f = @(x) sin(x(:,1)).*(1+1/10*(x(:,3).^4))+7*sin(x(:,2)).^2 +  pause_t(s);
+hyperbox = pi*[-ones(1,d) ; ones(1,d)];
+
+R = [.3139051827, .4424111333, 0.; .5575888667, .4424111326, .2436836832];
+[q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d));
+SI = q;
+SI_n = out_param.n;
+SI_t = out_param.time;
+SI_s = out_param.small;
+disp(SI)
+disp(out_param.bound_err)
+% disp(SI_n)
+% disp(SI_s)
+% disp(abs(R-SI) > max(abstol,R*reltol))
+% disp(out_param.exitflag)
+% wronga = wronga + sum(sum(abs(R-SI) > max(abstol,R*reltol)));
+% disp(['Time:' num2str(SI_t)])
+
+% disp('Running Ishigami example ...')
+% exitflag = [];
+% exitflagt = [];
+% for j = 1:d
+%     [q,app_int,out_param] = cubSobol_SI_g(f,hyperbox,j,'measure','uniform','abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',fudge);
+%     exitflag = [exitflag out_param.exitflag];
+%     SI(1,j) = q;
+%     SI_n(1,j) = out_param.n;
+%     SI_t(1,j) = out_param.time;
+%     SI_s(1,j) = out_param.small;
[…]

### 2016-03-10 FunctionsTest/SI_example.m

@@ -1,101 +1,0 @@
-clearvars
-
-abstol = 1e-4;
-reltol = 0; % Pure absolute tolerance
-mmax = 22; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
-
-%% Ishigami
-disp('Running Ishigami example ...')
-d = 3;
-f = @(x) sin(x(:,1)).*(1+1/10*(x(:,3).^4))+7*sin(x(:,2)).^2;
-hyperbox = pi*[-ones(1,d) ; ones(1,d)];
-
-exitflag = [];
-exitflagt = [];
-for j = 1:d
-    [q,app_int,out_param] = cubSobol_SI_g(f,hyperbox,j,'abstol',abstol,'reltol',reltol,'mmax',mmax);
-    exitflag = [exitflag out_param.exitflag];
-    SI(1,j) = q;
-    [q,app_int,out_param] = cubSobol_SI_g(f,hyperbox,-j,'abstol',abstol,'reltol',reltol,'mmax',mmax);
-    exitflagt = [exitflagt out_param.exitflag];
-    SI(2,j) = q;
-end
-disp(SI)
-if any(exitflag > 0) || any(exitflagt > 0)
-    warning('Results cannot be guaranteed due to reaching maximum budget or failing necessary conditions.')
-end
-    
-
-
-
-%% Bratley et al.
-disp('Running Bratley et al. example ...')
-d = 6;
-f = @(x) sum(bsxfun(@times, cumprod(x,2), (-1).^(1:d)),2);
-hyperbox = [zeros(1,d) ; ones(1,d)];
-
-exitflag = [];
-exitflagt = [];
-tic
-for j = 1:d
-    [q,app_int,out_param] = cubSobol_SI_g(f,hyperbox,j,'abstol',abstol,'reltol',reltol,'mmax',mmax);
-    exitflag = [exitflag out_param.exitflag];
-    SI(1,j) = q;
-    [q,app_int,out_param] = cubSobol_SI_g(f,hyperbox,-j,'abstol',abstol,'reltol',reltol,'mmax',mmax);
-    exitflagt = [exitflagt out_param.exitflag];
-    SI(2,j) = q;
-end
-toc
-disp(SI)
-if any(exitflag > 0) || any(exitflagt > 0)
-    warning('Results cannot be guaranteed due to reaching maximum budget or failing necessary conditions.')
-end
-    
-
-
-
[…]

### 2016-03-10 FunctionsTest/cubSobol_SI_all_g.m

@@ -1,56 +1,51 @@
-function [q,int,out_param] = cubSobol_SI_g(varargin)
-%CUBSOBOL_SI_G Quasi-Monte Carlo method using Sobol' cubatures
-%to compute first order or total effect Sobol Indices
+function [q,int,out_param] = cubSobol_SI_all_g(varargin)
+%CUBSOBOL_SI_ALL_G Quasi-Monte Carlo method using Sobol' cubatures
+%to compute all first order and total effect Sobol Indices
 %within a specified generalized error tolerance with guarantees under
 %Walsh-Fourier coefficients cone decay assumptions.
 %
-%   [q,out_param] = CUBSOBOL_SI_G(f,hyperbox,u) estimates the first order
-%   Sobol Indices of f if u > 0, or the total effect Indice u otherwise,
-%   where hyperbox is the sample space of the uniform distribution
-%   (the distribution can also be set to normal), and the error guaranteed
-%   not to be greater than a specific generalized error tolerance
-%   tolfun:=max(abstol,reltol*| SI(f) |). Input f is a function handle. f should
-%   accept an n x d matrix input, where d is the dimension and n is the 
-%   number of points being evaluated simultaneously. The input hyperbox is
-%   a 2 x d matrix, where the first row corresponds to the lower limits 
-%   and the second row corresponds to the upper limits of the integral.
-%   Given the construction of Sobol' sequences, d must be a positive 
-%   integer with 1<=d<=1111.
+%   [q,out_param] = CUBSOBOL_SI_ALL_G(f,hyperbox) estimates all first order
+%   and total effect Sobol Indices of f, where hyperbox is the sample space
+%   of the uniform distribution (the distribution can also be set to normal),
+%   and the estimation error is guaranteed not to be greater than a specific
+%   generalized error tolerance tolfun:=max(abstol,reltol*| SI(f) |).
+%   Input f is a function handle. f should accept an n x d matrix input,
+%   where d is the dimension and n is the number of points being evaluated
+%   simultaneously. The input hyperbox is a 2 x d matrix, where the first
+%   row corresponds to the lower limits and the second row corresponds to
[…]

### 2016-03-10 FunctionsTest/cubSobol_SI_fo_g.m

@@ -1,25 +1,24 @@
-function [q,int,out_param] = cubSobol_SI_g(varargin)
-%CUBSOBOL_SI_G Quasi-Monte Carlo method using Sobol' cubatures
-%to compute first order or total effect Sobol Indices
-%within a specified generalized error tolerance with guarantees under
-%Walsh-Fourier coefficients cone decay assumptions.
+function [q,int,out_param] = cubSobol_SI_fo_g(varargin)
+%CUBSOBOL_SI_FO_G Quasi-Monte Carlo method using Sobol' cubatures
+%to compute all first order Sobol Indices whitin a specified
+%generalized error tolerance with guarantees under Walsh-Fourier
+%coefficients cone decay assumptions.
 %
-%   [q,out_param] = CUBSOBOL_SI_G(f,hyperbox,u) estimates the first order
-%   Sobol Indices of f if u > 0, or the total effect Indice u otherwise,
-%   where hyperbox is the sample space of the uniform distribution
-%   (the distribution can also be set to normal), and the error guaranteed
-%   not to be greater than a specific generalized error tolerance
-%   tolfun:=max(abstol,reltol*| SI(f) |). Input f is a function handle. f should
-%   accept an n x d matrix input, where d is the dimension and n is the 
-%   number of points being evaluated simultaneously. The input hyperbox is
-%   a 2 x d matrix, where the first row corresponds to the lower limits 
-%   and the second row corresponds to the upper limits of the integral.
-%   Given the construction of Sobol' sequences, d must be a positive 
-%   integer with 1<=d<=1111.
+%   [q,out_param] = CUBSOBOL_SI_FO_G(f,hyperbox) estimates all first order
+%   Sobol Indices of f, where hyperbox is the sample space
+%   of the uniform distribution (the distribution can also be set to normal),
+%   and the estimation error is guaranteed not to be greater than a specific
+%   generalized error tolerance tolfun:=max(abstol,reltol*| SI(f) |).
+%   Input f is a function handle. f should accept an n x d matrix input,
+%   where d is the dimension and n is the number of points being evaluated
+%   simultaneously. The input hyperbox is a 2 x d matrix, where the first
[…]

### 2016-03-10 FunctionsTest/finding_permutations_replication.m

@@ -1,0 +1,16 @@
+tic
+n = 2^17;
+d = 100;
+sob = sobolset(d);
+
+x = net(sob,n);
+perm = zeros(n,d);
+perm_inv = perm;
+for i = 1:d
+    [~, perm(:,i)] = sort(x(:,i));
+    [~, perm_inv(:,i)] = sort(perm(:,i));
+end
+toc
+tic
+save('perm.mat','perm','perm_inv','-v7.3')
+toc

### 2016-03-10 FunctionsTest/loading_test.m

@@ -1,0 +1,5 @@
+
+tic
+example = matfile('perm.mat')
+firstColB = example.perm(:,1);
+toc

### 2016-03-10 FunctionsTest/pause_t.m

@@ -1,0 +1,4 @@
+function y = pause_t(s)
+    pause(s)
+    y = 0;
+end

### 2016-03-10 kuo_code/bitxor_toni.m

@@ -1,0 +1,7 @@
+function y = bitxor_toni( array )
+
+if size(array,2) == 1
+    y = array;
+else
+    y = bitxor(array(1),bitxor_toni(array(2:end)));
+end

### 2016-03-10 kuo_code/generating_C_Sobol.m

@@ -1,0 +1,54 @@
+s = 6;
+m = 4;
+
+% Polynomial degree, coefficients a, and direction vector m
+C(2).d = 1; C(2).a = [];  C(2).m = [1];
+C(3).d = 2; C(3).a = 1; C(3).m = [1 1];
+C(4).d = 3; C(4).a = 1; C(4).m = [1 3 7];
+C(5).d = 3; C(5).a = 2; C(5).m = [1 1 5];
+C(6).d = 4; C(6).a = 1; C(6).m = [1 3 1 1];
+
+
+
+C(1).C = eye(m);
+C(2).C = C(1).C;
+for i = 2:m
+    C(2).m = [C(2).m bitxor(2*C(2).m(end),C(2).m(end))];
+    aa = (dec2bin(C(2).m(i))- '0')';
+    empty = i - size(aa,1);
+    C(2).C(1:i,i) = [zeros(empty,1); aa];
+end
+
+% Assuming a = a_d-1 * 2^0 + a_d-2 * 2^1 + ... + a_1 2^d-2
+for j = 3:s
+    C(j).C = C(1).C;
+    for i = 2:m
+        if i > size(C(j).m,2)
+            vec_a = dec2bin(C(j).a)- '0';
+            if size(vec_a,2) < C(j).d - 1
+                vec_a = [zeros(1,C(j).d-size(vec_a,2)-1), vec_a];
+            end
+            vec_a = [(vec_a), 1, 1].*[2.^(1:C(j).d), 1]; % Matlab mistake: [fliplr(vec_a), 1, 1].*[2.^(1:C(j).d), 1]
+            vec_a = vec_a.*[C(j).m(size(C(j).m,2):-1:size(C(j).m,2)-C(j).d+1), C(j).m(size(C(j).m,2)-C(j).d+1)];
+            C(j).m = [C(j).m, bitxor_toni(vec_a)];
+        end
+        aa = (dec2bin(C(j).m(i))- '0')';
+        empty = i - size(aa,1);
+        C(j).C(1:i,i) = [zeros(empty,1);aa];
+    end
+end
+
+x = zeros(2^m,s);
+for n = 1:2^m-1
+    vec_n = (dec2bin(n)- '0');
+    vec_n = fliplr(vec_n)';
+    for j = 1:s
+        x(n+1,j) = 2.^-(1:m)*mod(C(j).C*[vec_n;zeros(m-size(vec_n,1),1)],2);
[…]

### 2016-03-10 kuo_code/sobol.cc

@@ -1,0 +1,199 @@
+// Frances Y. Kuo
+//
+// Email: <f.kuo@unsw.edu.au>
+// School of Mathematics and Statistics
+// University of New South Wales
+// Sydney NSW 2052, Australia
+// 
+// Last updated: 21 October 2008
+//
+//   You may incorporate this source code into your own program 
+//   provided that you
+//   1) acknowledge the copyright owner in your program and publication
+//   2) notify the copyright owner by email
+//   3) offer feedback regarding your experience with different direction numbers
+//
+//
+// -----------------------------------------------------------------------------
+// Licence pertaining to sobol.cc and the accompanying sets of direction numbers
+// -----------------------------------------------------------------------------
+// Copyright (c) 2008, Frances Y. Kuo and Stephen Joe
+// All rights reserved.
+// 
+// Redistribution and use in source and binary forms, with or without
+// modification, are permitted provided that the following conditions are met:
+// 
+//     * Redistributions of source code must retain the above copyright
+//       notice, this list of conditions and the following disclaimer.
+// 
+//     * Redistributions in binary form must reproduce the above copyright
+//       notice, this list of conditions and the following disclaimer in the
+//       documentation and/or other materials provided with the distribution.
+// 
+//     * Neither the names of the copyright holders nor the names of the
+//       University of New South Wales and the University of Waikato
+//       and its contributors may be used to endorse or promote products derived
+//       from this software without specific prior written permission.
+// 
+// THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS ``AS IS'' AND ANY
+// EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+// WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
[…]

### 2016-03-10 replicated_sobol.tex
added Section 3 + end of Section 1

@@
 {x'}_{n,1} & ... & {x'}_{n,j} & ... & {x'}_{n,d} \\
-\end{array} \right) 
+\end{array} \right).
 \]
@@
 
-Our objective is to combine the use of Sobol' sequence with the replication method to estimate all quantities $\underline{\tau}_u^2, u \in \{1,\dots,d\}$ with only $2n$ evaluations of $f$.
-This translates to construct two Sobol' sequence that identify as two replicated designs of order $1$.
+Our objective is to combine the use of Sobol' sequences with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \{1,\dots,d\}$.
+This would reduce the method to constructing two replicated designs of order $1$ that are iteratively augmented with new point sets.
+Two approaches are considered: one multiplicative and one additive.
+The first one uses the innate nested structure of a Sobol' sequence.
+The size of each replicated design is doubled at each step.
+The additive approach consists first of constructing a Sobol' sequence then shifting and scrambling it to form the new point sets.
+These new point sets are then added to the initial Sobol' sequence to form the two replicated designs.
+In this case, the size of each replicated design at step $k$ is $ k \times 2^m$ where $2^m$ is the size of the initial Sobol' sequence.
 
@@
 
+\section{Matrix generators group $U_m$}
+
 Be $U_m(\mathbb{F}_b)$ the multiplicative group of all invertible triangular matrices of size $m\times m$ over $\mathbb{F}_b$ ($GF(b)$). We have that $\abs{U_m(\mathbb{F}_b)}=(b-1)^m b^{(m-1)m/2}$.

### 2016-03-10 replicated_sobol.tex
filled Section 4 + modifs Section 1

@@
 \usepackage{amsmath,amssymb,amsthm,natbib,mathtools,bbm,extraipa,mathabx,graphicx}
+\usepackage[ruled,vlined]{algorithm2e}
 %accents,
@@
 \newcommand{\vx}{\bvec{x}}
+\newcommand{\vi}{\bvec{i}}
+\newcommand{\ve}{\bvec{e}}
 \newcommand{\vk}{\bvec{k}}
@@
 
-\section{There Is The Addition Method I Do Not Know}
+\section{Additive Approach}
+Notations:
+\begin{itemize}
+\item[.] $m$ denote the number of digits
+\item[.] $C_{m,1},\dots,C_{m,d}$: $d$ generator matrices of size $m \times m$ over the finite field $\mathcal{Z}_2$
+\item[.] $\vi$: base-$2$ representation of the integer $i$: $\vi=(i_1,\dots,i_m)^T$
+\item[.] $L_{m,l}$: nonsingular $m \times m$ lower triangular matrix over the finite field $\mathcal{Z}_2$
+\item[.] $\ve_{m,l}$: $m \times 1$ vector with elements from $\mathcal{Z}_2$
+\end{itemize}
+
+Denote by $X$ and $X'$ the two replicated designs of order $1$.
+A row of $X$ or $X'$ is a point in $[0,1]^d$.
+The symbol $x_i^j$ (resp.
+${x'}_i^j$) corresponds to  the element of row $i$ and column $j$ of $X$ (resp.
+$X'$).
+The additive approach is described by Algorithm \ref{additive}.
+All operations are carried on the finite field $\mathcal{Z}_2$.
+\begin{algorithm}[!ht]
+
+\begin{center}
+\begin{minipage}{10cm}
+\begin{enumerate}
+\item[Step 1.] Instantiation: $X \leftarrow \emptyset$, $X' \leftarrow \emptyset$, $l \leftarrow 1$, $\widehat{\underline{\tau}_u^2}^{(0)} \leftarrow 0$.
+\item[Step 4.] $while$ ($!$ stopping criterion):
+\begin{enumerate}
+\item[4.1] Construct $L_{m,l}$ and $\ve_{m,l}$.
+\item[4.2] Augment both $X$ and $X'$:\\
+for $j=1,\dots,d$:\\
+for $i=1+2^{m+l-1},\dots,2^{m+l}$:
+\begin{flalign*}
+x_i^j & = C_{m,j} . \vi + \ve_{m,l} && \\
+{x'}_i^j & = L_{m,l} . (C_{m,j} . \vi +  \ve_{m,l})&&
+\end{flalign*}
+\item[4.3] For $u=1,\dots,d$: evaluate $\widehat{\underline{\tau}_u^2}^{(l)}.$ 
+\item[4.4.]  $l \leftarrow l+1.$
+\end{enumerate}
+\item[Step 5.] Return: $\widehat{\underline{\tau}_u^2}, \ u \in \{1,\dots,d\}.$ 
+\end{enumerate}
+\end{minipage}
+\end{center}
+\label{additive}
+\caption{Additive approach}
+\end{algorithm}
 

### 2016-03-10 replicated_sobol.tex
Adding definition of Sobol' sequence in replicated Sobol article

--- 2016-03-10 replicated_sobol.tex
@@
 \section{Sobol' sequence background}
+
+We are interested in digital nets which are constructed as point sets in $\cube$.
+
+For $d\geq 1$, $b\geq 2$, and $0\geq t\geq m$, the set of points $\mathcal{P}\in\cube$, with $|\mathcal{P}|=b^m$, is a $(t,m,d)-net$ in base $b$ if for every $A\in\mathcal{A}$ with volume $b^{t-m}$, $|A\cap\mathcal{P}|=b^t$ ($A$ contains exactly $b^t$ points of $\mathcal{P}$).
+
+A Sobol' sequence in dimension $d$ is a $(t,d)-sequence$ in base 2.
+
 Obviously, we do not need to evaluate $f(\vx)$ $d$ times. But we can do event better than that, and evaluate $f(\vx_u:{\vx'}_{-u})$ only one time. This is the replication method....

### 2016-03-10 kuo_code/generating_C_Sobol.m
Adding last changes on computing t_values, testing group structure of generating matrices,and creating generating matrices from Kuo-Joe files

@@ -1,54 +1,90 @@
-s = 6;
-m = 4;
+%% Construction of C generating matrices
+s = 28; % Number of matrices for which we generate the Sobol' seq generator
+m = 12; % Number of digits used to generate the seq up to 2^m points
+entry_file = 'new-joe-kuo-6.21201';
+% A = txt2mat(entry_file);
 
-% Polynomial degree, coefficients a, and direction vector m
-C(2).d = 1; C(2).a = [];  C(2).m = [1];
-C(3).d = 2; C(3).a = 1; C(3).m = [1 1];
-C(4).d = 3; C(4).a = 1; C(4).m = [1 3 7];
-C(5).d = 3; C(5).a = 2; C(5).m = [1 1 5];
-C(6).d = 4; C(6).a = 1; C(6).m = [1 3 1 1];
+% for k = 1:size(A,1)
+%     C(k + 1).d = A(k,1); % Dimension
+%     C(k + 1).s = A(k,2); % Polynomial degree
+%     C(k + 1).a = A(k,3); % Polynomial coefficients assuming a = a_d-1 * 2^0 + a_d-2 * 2^1 + ... + a_1 2^d-2
+%     aa = find(isnan(A(k,:))==1);
+%     if ~isempty(aa)
+%         C(k + 1).m = A(k,4:aa(1) - 1); % Initial directional numbers m_i
+%     else
+%         C(k + 1).m = A(k,4:end);
+%     end
+% end
+% 
+% C(1).C = eye(m); C(1).d = 1; C(1).s = 0; C(1).a = []; C(1).m = 1;
+% C(2).C = C(1).C;
+% % I generate C(2).C manually
+% for i = 2:m
+%     C(2).m = [C(2).m bitxor(2*C(2).m(end),C(2).m(end))];
+%     aa = (dec2bin(C(2).m(i))- '0')';
+%     empty = i - size(aa,1);
+%     C(2).C(1:i,i) = [zeros(empty,1); aa];
+% end
+% 
+% % Generate C(j).C matrices for j = 3:s
+% for j = 3:s % For each dimension
+%     C(j).C = C(1).C;
+%     for i = 2:m % for each column of C(j).C
+%         if i > size(C(j).m,2)
+%             vec_a = dec2bin(C(j).a)- '0';
+%             if size(vec_a,2) < C(j).s - 1
[…]

### 2016-03-10 kuo_code/t_value.m

@@ -1,0 +1,24 @@
+function y = t_value(j, C_j, d, C_d, m)
+% T_VALUE gives the t-value between C_j and C_d when m is fixed
+y = -1;
+    for t = 0:m - 1
+        if t == m - 1
+            y = t;
+            break
+        end
+        for r_j = 0:m - t
+            r_d = m - t - r_j;
+            M = [C_j(1:r_j,1:m); C_d(1:r_d,1:m)];
+            M = mod(rref(M),2);
+            if ~any(M(end,:)) % Matrix M is not full rank (echelon matrix last row is 0)
+                break
+            elseif r_j == m - t
+                y = t;
+                break
+            end
+        end
+        if y > -1
+            break
+        end
+    end
+end

### 2016-03-10 kuo_code/test_group.m

@@ -1,0 +1,31 @@
+m = 6;
+
+aux = eye(m);
+for i = 0:2^(m*(m-1)/2)-1
+    a = dec2bin(i) - '0';
+    empty = m*(m-1)/2 - size(a,2);
+    if empty
+        a = [zeros(1,empty) a];
+    end
+    ind = [];
+    for j = 2:m
+        ind = [ind j+m*(j-2):m*(j-1)];
+    end
+    A = aux;
+    A(ind) = a;
+    A = A';
+    for k = 0:m-2
+        if mod(A^(2^k),2) == aux
+            GROUP.order(i+1) = 2^k;
+            GROUP.element(i+1).matrix = A;
+            break
+        elseif k == m-2
+            GROUP.order(i+1) = 2^(m-1);
+            GROUP.element(i+1).matrix = A;
+        end
+    end
+end
+
+disp(max(GROUP.order))
+    
+    

### 2016-03-10 kuo_code/generating_C_Sobol.m
Fixing problems with the t_value computation of the function t_value

@@ -1,51 +1,54 @@
 %% Construction of C generating matrices
 s = 28; % Number of matrices for which we generate the Sobol' seq generator
 m = 12; % Number of digits used to generate the seq up to 2^m points
-entry_file = 'new-joe-kuo-6.21201';
-% A = txt2mat(entry_file);
+entry_file = 'joe-kuo-old.1111'; % joe-kuo-old.1111 new-joe-kuo-6.21201
+A = txt2mat(entry_file);
 
-% for k = 1:size(A,1)
-%     C(k + 1).d = A(k,1); % Dimension
-%     C(k + 1).s = A(k,2); % Polynomial degree
-%     C(k + 1).a = A(k,3); % Polynomial coefficients assuming a = a_d-1 * 2^0 + a_d-2 * 2^1 + ... + a_1 2^d-2
-%     aa = find(isnan(A(k,:))==1);
-%     if ~isempty(aa)
-%         C(k + 1).m = A(k,4:aa(1) - 1); % Initial directional numbers m_i
-%     else
-%         C(k + 1).m = A(k,4:end);
-%     end
-% end
-% 
-% C(1).C = eye(m); C(1).d = 1; C(1).s = 0; C(1).a = []; C(1).m = 1;
-% C(2).C = C(1).C;
-% % I generate C(2).C manually
-% for i = 2:m
-%     C(2).m = [C(2).m bitxor(2*C(2).m(end),C(2).m(end))];
-%     aa = (dec2bin(C(2).m(i))- '0')';
-%     empty = i - size(aa,1);
-%     C(2).C(1:i,i) = [zeros(empty,1); aa];
-% end
-% 
-% % Generate C(j).C matrices for j = 3:s
-% for j = 3:s % For each dimension
-%     C(j).C = C(1).C;
-%     for i = 2:m % for each column of C(j).C
-%         if i > size(C(j).m,2)
-%             vec_a = dec2bin(C(j).a)- '0';
-%             if size(vec_a,2) < C(j).s - 1
-%                 vec_a = [zeros(1,C(j).s-size(vec_a,2)-1), vec_a];
-%             end
-%             vec_a = [(vec_a), 1, 1].*[2.^(1:C(j).s), 1]; % Matlab mistake: [fliplr(vec_a), 1, 1].*[2.^(1:C(j).s), 1]
[…]

### 2016-03-10 kuo_code/rref_toni.m

@@ -1,0 +1,41 @@
+function rrA = rref_toni(A, zeroThresh)
+
+%  On entry: A is a square matrix,
+%            b is a column vector of the same dimension,
+%            display is 1 if step-by-step display desired, 0 otherwise.
+%  On exit:  U and f are the result of applying Gaussian elimination
+%            with partial pivoting to the system Ax=b.
+
+[m, n] = size(A);
+if (nargin == 1)
+  zeroThresh = n*eps;
+end
+
+currRow = 1;
+for j=1:n
+  if (currRow <= m)
+	[cmax,relPos] = max(abs(A(currRow:m,j)));  % index of max element in col j.
+	temp = A(currRow,:);                     % Exchange rows j and j+jmax-1.
+	A(currRow,:) = A(currRow + relPos - 1,:);
+	A(currRow + relPos - 1,:) = temp;
+
+	if (abs(A(currRow,j)) > zeroThresh)
+	  A(currRow,:) = A(currRow,:)/A(currRow,j);
+	  A(currRow,1:j-1) = zeros(1,j-1);
+	  for i=1:currRow - 1                 % Eliminate in column j using currRow.
+		mult = A(i,j);
+		A(i,j:n) = mod(A(i,j:n) - mult*A(currRow,j:n),2);
+	  end
+	  for i=currRow + 1:m                 % Eliminate in column j using currRow.
+		mult = A(i,j);
+		A(i,j:n) = mod(A(i,j:n) - mult*A(currRow,j:n),2);
+	  end
+	  A([1:currRow-1 currRow+1:m],j) = zeros(m-1,1);
+	  currRow = currRow + 1;
+	else
+	  A(currRow:m,j) = 0;
+    end
+  end
+end
+rrA = A;
+end

### 2016-03-10 kuo_code/t_value.m

@@ -9,7 +9,7 @@ y = -1;
         for r_j = 0:m - t
             r_d = m - t - r_j;
             M = [C_j(1:r_j,1:m); C_d(1:r_d,1:m)];
-            M = mod(rref(M),2);
+            M = mod(rref_toni(M),2);
             if ~any(M(end,:)) % Matrix M is not full rank (echelon matrix last row is 0)
                 break
             elseif r_j == m - t

### 2016-03-10 replicated_sobol.tex
Adding more on Sobol background and definition of replicated sequences

--- 2016-03-10 replicated_sobol.tex
@@
 \newcommand{\cube}{[0,1)^d}
+\newcommand{\cubes}{[0,1)^s}
 %\renewcommand{\bbK}{\natzero^d}
@@
 In \cite{}, Owen proposed to use the following expression for $\underline{\tau}_u^2$:
-\[\underline{\tau}_u^2  =\int_{[0,1)^{2d-1}}(f(\vx) - \mu) (f(\vx_u:{\vx'}_{-u})-\mu) d\vx d{\vx'}_{-u},\]
+\begin{equation}\label{first_order_indice}
+\underline{\tau}_u^2  =\int_{[0,1)^{2d-1}}(f(\vx) - \mu) (f(\vx_u:{\vx'}_{-u})-\mu) d\vx d{\vx'}_{-u},
+\end{equation}
 taking $\mu$ as introduced in Janon \textit{et al.}:
@@
 The natural way to estimate these two quantities is for $(\vx_i,\vx'_i) \stackrel{iid}{\sim} [0,1)^{2d}$ via:
-\begin{align*}
-\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=1}^n (f(\vx_i) - \mu) (f(\vx_{i,u}:{\vx'}_{i,-u})-\mu),\\
+\begin{align}
+\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=1}^n (f(\vx_i) - \widehat{\mu}) (f(\vx_{i,u}:{\vx'}_{i,-u})-\widehat{\mu}),\label{first_order_indice_estimator}\\
+\nonumber
 \widehat{\mu} & = \frac{1}{2n} \sum \limits_{i=1}^n f(\vx_i) +f(\vx_{i,u}:{\vx'}_{i,-u}).
-\end{align*}
+\end{align}
 \bigskip
@@
 \end{defin}
-The replication procedure introduced in \cite{} allows to estimate all first-order Sobol' indices with two replicated designs of order $1$.
+The replication procedure introduced in \cite{•} allows to estimate all first-order Sobol' indices with two replicated designs of order $1$.
 In this procedure, the quantity $f(\vx_u:{\vx'}_{-u})$ is only evaluated $n$ times once for all $u$ resulting in a total of $2n$ evaluations of $f$.
@@
 
-\section{Sobol' sequence background}
-Obviously, we do not need to evaluate $f(\vx)$ $d$ times. But we can do event better than that, and evaluate $f(\vx_u:{\vx'}_{-u})$ only one time. This is the replication method....
+\section{Digital Nets Background}
+
+In this section we introduce a particular type of quasi-Monte Carlo points to estimate $\eqref{first_order_indice}$, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{2^m}$ only one time to estimate all $d$ indices.
+
+The concept of $(t,m,s)$-net and $(t,s)$-sequence was first introduced and studied by Niederreiter in \cite{•}.
+These are points sets in $\cubes$ whose quality is measured by the parameter $t$.
+Because this parameter is the criterion we use to construct our new sequences, we provide the key definitions below.
+
+Let $\mathcal{A}$ be the set of all $A\in\cubes$ such that $A:=\prod_{i=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $0\leq\gamma_j$ and $0\leq\alpha_j<b^{\gamma_j}$ for all $j=1,\dots,s$.
+
+\begin{defin}
+For integers $s\geq 1$, $b\geq 2$, and $m\geq t\geq 0$, the set of points $\mathcal{P}\in\cubes$, with $|\mathcal{P}|=b^m$, is a $(t,m,d)-net$ in base $b$ if for every $A\in\mathcal{A}$ with volume $b^{t-m}$, $|A\cap\mathcal{P}|=b^t$ ($A$ contains exactly $b^t$ points of $\mathcal{P}$).
+\end{defin}
+
+In other words, any box of ... contains a proport
+....
+This definition is linked to the star discrepancy...
+The smaller the t value, the better.
+
+\begin{defin}
+For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if every set $\mathcal{P}_{l,m}:=\{\vx_i\}_{i=lb^m}^{(l+1)b^m-1}$ with $l\geq 0$ and $m\geq t$, $\mathcal{P}_{l,m}$ is a $(t,m,s)$-net in base $b$.
+\end{defin}
+
+Digital nets are usually computed with the generating matrices $C_1,\dots,C_s$ in $\mathbb{F}_b$, whose size $\infty\times\infty$.
+However, to construct the first $b^m$ points, one only needs the knowledge of $C_1^{\infty\times m},\dots,C_s^{\infty\times m}$.
+For each $i=0,\dots,b^m-1$, the points $\vx_i = (x_{i,j},\dots,x_{i,s})^\intercal$ of the sequence can be constructed as follows:
+\begin{equation}
+(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^{\infty\times m}(i_{0},\dots,i_{m-1})^\intercal,\qquad j= 1,\dots,s\, ,
+\end{equation}
+where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ and $i = \sum_{k=0}^{m-1}i_kb^{k}$.
+
+Our goal is to generate two sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ such that for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$.
+For that purpose, $C_j'$ depend on the choice of $C_j$.
+
+Although the choices of $C_j$ and $C_j'$ are many, there is a special case interesting for its construction simplicity, and with a wide range of possible $C_j'$ choices given $C_j$.
+
+Considering the generating matrices to be upper triangular full rank (no zeros on the diagonal), one ensures that $x_{i,j,k}=0$, for $k>m$ and $b^m-1\geq i \geq 0$.
+Since the block $C_j^{m\times m}$ is full rank, each $x_{i,j}\neq x_{r,j}$ when $i\neq j$.
+Therefore, excluding the case ${\vx}_i={\vx'}_i$ for all $i\in\mathbb{N}_0$, it is enough to choose $C_j\neq C_j'$ for at least one dimension $j$.
+When $b=2$, this is the case of Sobol' sequences and one could simply consider $C_{j+d},\dots,C_{2d}$ to generate the replicated sequence.
+
+Because we are estimating the integral \eqref{first_order_indice}, we want to minimize the t-value of the following $d$ sequences at the same time............
+
+According to \eqref{first_order_indice}, our dimension of study is $s = 2d-1$.
 
@@
 
-\section{Matrix generators group $U_m$}
+\subsection{Matrix generators group $U_m$}
 
@@
 Not all choices are possible, for instance order 2 and higher Sobol' indices.
+
+\subsection{Owen Scrambling To The New Sequence}
 

### 2016-03-10 replicated_sobol.tex
Adding definition of replicated digital net

@@
 
-Our goal is to generate two sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ such that for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$.
-For that purpose, $C_j'$ depend on the choice of $C_j$.
+\subsection{Replicated Digital Sequences}
+Here recall the link with the replicated method....
+\begin{defin}
+A digital sequence $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ is the replicated digital sequence of $\{\vx_i\}_{i\in\mathbb{N}_0}$ if for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$.
+\end{defin}
+In this case, $C_j'$ will depend on the choice of $C_j$.
 
-Although the choices of $C_j$ and $C_j'$ are many, there is a special case interesting for its construction simplicity, and with a wide range of possible $C_j'$ choices given $C_j$.
+Although the choices of $C_j$ and $C_j'$ are many, there is a special case interesting for its construction simplicity, and wide range of $C_j'$ choices.
 
-Considering the generating matrices to be upper triangular full rank (no zeros on the diagonal), one ensures that $x_{i,j,k}=0$, for $k>m$ and $b^m-1\geq i \geq 0$.
+Considering the generating matrices to be upper triangular and without zeros on the diagonal, one ensures that $x_{i,j,k}=0$, for $m<k$ and $0 \leq i \leq b^m-1$.
 Since the block $C_j^{m\times m}$ is full rank, each $x_{i,j}\neq x_{r,j}$ when $i\neq j$.
-Therefore, excluding the case ${\vx}_i={\vx'}_i$ for all $i\in\mathbb{N}_0$, it is enough to choose $C_j\neq C_j'$ for at least one dimension $j$.
+Therefore, excluding the case ${\vx}_i={\vx'}_i$ for all $i\in\mathbb{N}_0$, it is enough to choose $C_j\neq C_j'$ for at least $d-1$ dimension.
 When $b=2$, this is the case of Sobol' sequences and one could simply consider $C_{j+d},\dots,C_{2d}$ to generate the replicated sequence.
@@
 
-\subsection{Owen Scrambling To The New Sequence}
+\subsection{Owen Scrambling To Replicated Digital Sequences}
 

### 2016-03-11 replicated_sobol.tex
Adding more changes to Sobol background in replicated Sobol article

@@
 
-In this section we introduce a particular type of quasi-Monte Carlo points to estimate $\eqref{first_order_indice}$, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{2^m}$ only one time to estimate all $d$ indices.
+In this section we introduce a particular type of quasi-Monte Carlo points to estimate $\eqref{first_order_indice}$, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{b^m}$ only one time to estimate all $d$ indices.
 
@@
 \begin{defin}
-A digital sequence $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ is the replicated digital sequence of $\{\vx_i\}_{i\in\mathbb{N}_0}$ if for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$.
+A digital sequence $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ is the \emph{replicated digital} sequence of $\{\vx_i\}_{i\in\mathbb{N}_0}$ if for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$.
 \end{defin}
@@
 
+If we do higher order Sobol' indices, we can easily show that $C'_{i}=AC_{i}$ for $i = 1,\dots,d$, and this does not work because this means having the same function values for each $u$, with a unique ordering given by $A$.
+
 Although the choices of $C_j$ and $C_j'$ are many, there is a special case interesting for its construction simplicity, and wide range of $C_j'$ choices.
 
-Considering the generating matrices to be upper triangular and without zeros on the diagonal, one ensures that $x_{i,j,k}=0$, for $m<k$ and $0 \leq i \leq b^m-1$.
-Since the block $C_j^{m\times m}$ is full rank, each $x_{i,j}\neq x_{r,j}$ when $i\neq j$.
-Therefore, excluding the case ${\vx}_i={\vx'}_i$ for all $i\in\mathbb{N}_0$, it is enough to choose $C_j\neq C_j'$ for at least $d-1$ dimension.
-When $b=2$, this is the case of Sobol' sequences and one could simply consider $C_{j+d},\dots,C_{2d}$ to generate the replicated sequence.
+For this special case, we consider the generating matrices to be upper triangular.
+This ensures that $x_{i,j,k}=0$, for $m<k$ and $0 \leq i \leq b^m-1$.
+If we also assume that there are no zeros on the diagonal, the block $C_j^{m\times m}$ is full rank and each $x_{i,j}\neq x_{r,j}$ when $i\neq r$.
+Therefore, excluding the trivial case, it is enough to choose $C_j\neq C_j'$ for at least $d-1$ dimensions to obtain a \emph{replicated digital sequence}.
+When $b=2$, these are Sobol' sequences.
 
-Because we are estimating the integral \eqref{first_order_indice}, we want to minimize the t-value of the following $d$ sequences at the same time............
+For quasi-Monte Carlo integration purposes, given $\{{\vx}_i\}_{i\in\mathbb{N}_0}$ generated by $C_{1},\dots,C_{d}$, and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ generated by $C'_{1},\dots,C'_{d}$, the $d$ sequences in dimension $2d-1$ used to estimate all $\underline{\tau}_u^2$ are generated by
+\begin{equation}\label{ordered_sequence}
+\underbrace{C_{1},\dots,C_{d}}_{\text{First }d\text{ dimensions}},\underbrace{C_{\alpha(u,1)},\dots,C_{\alpha(u,u-1)},C_{\alpha(u,u+1)},\dots,C_{\alpha(u,d)}}_{\text{Next }d-1\text{ dimensions}},\quad 1\leq u \leq d\, ,
+\end{equation}
+where $C_{\alpha(u,i)}:=C_u(C'_{u})^{-1}C'_{i}$.
+Note that for $i=u$, one has $C_{\alpha(u,u)}=C_u$.
+This is in fact forcing $C_u = C'_{u}$, as desired to apply the replicated method.
+Therefore, our goal is to find a good choice of $C_{1},\dots,C_{d},C'_{1},\dots,C'_{d}$ such that for all $u=1,\dots,d$, the sequence used to estimate $\underline{\tau}_u^2$ has a low $t$-value.
 
-According to \eqref{first_order_indice}, our dimension of study is $s = 2d-1$.
+The best choice of primitive polynomials and directional numbers to generate good quality Sobol' sequences is deeply discussed in \cite{•}.
+We are going to take Kuo and Joe results to find  good \emph{replicated Sobol'} sequences.
 
-$X$,$X'$ are two sequences such that,
-\[
-X = \begin{pmatrix}
-x_1^1,\dots,x_1^d \\
-x_2^1,\dots,x_2^d \\
-x_3^1,\dots,x_3^d \\
-\end{pmatrix} \\
-X' = \begin{pmatrix}
-\pi_1(x_1^1),\dots,\pi_d(x_1^d) \\
-\pi_1(x_2^1),\dots,\pi_d(x_2^d) \\
-\pi_1(x_3^1),\dots,\pi_d(x_3^d) \\
-\end{pmatrix}
-\]
-
-These sequences can be generated indeed with Owen scramblings, or which is equivalent, matrix generators $C_i$
+Pairwise projections are already well optimized (see\cite[Table 2.1]{•}).
+Thus, our starting point will be using the $C_1,\dots,C_d$ found in \cite{•} to generate the sequence $\{{\vx}_i\}_{i\in\mathbb{N}_0}$.
+Hence, we will focus on finding the optimal $C'_{1},\dots,C'_{d}$ such that we minimize a $t$-value criteria (to specify, perhaps the max of all) over all $d$ sequences described in \eqref{ordered_sequence}.
 
@@
 
-Not all choices are possible, for instance order 2 and higher Sobol' indices.
+\subsection{Owen Scrambling To Replicated Digital Sequences}
 
-\subsection{Owen Scrambling To Replicated Digital Sequences}
+It will be easy to write that we can apply an Owen scrambling to each dimension separately, and we only need to keep the same scrambling for $C_j$ and $C'_j$.
 

### 2016-03-11 kuo_code/generating_C_Sobol.m
Minor changes and computation of max order of groups U_m up to m=7

@@ -1,7 +1,7 @@
 %% Construction of C generating matrices
 s = 28; % Number of matrices for which we generate the Sobol' seq generator
 m = 12; % Number of digits used to generate the seq up to 2^m points
-entry_file = 'joe-kuo-old.1111'; % joe-kuo-old.1111 new-joe-kuo-6.21201
+entry_file = 'new-joe-kuo-6.21201'; % joe-kuo-old.1111 new-joe-kuo-6.21201
 A = txt2mat(entry_file);
 
 

### 2016-03-11 kuo_code/test_group.m

@@ -1,4 +1,11 @@
-m = 6;
+clearvars
+m = 7;
+% m:2   max group order:2   group size:2       2^1
+% m:3   max group order:4   group size:8       2^3
+% m:4   max group order:4   group size:64      2^6
+% m:5   max group order:8   group size:1024    2^10
+% m:6   max group order:8   group size:32768   2^15
+% m:7   max group order:8   group size:2097152 2^21
 
 aux = eye(m);
 for i = 0:2^(m*(m-1)/2)-1
@@ -24,8 +31,9 @@ for i = 0:2^(m*(m-1)/2)-1
             GROUP.element(i+1).matrix = A;
         end
     end
+    disp(['Done: ' num2str(i/(2^(m*(m-1)/2)-1))])
 end
 
-disp(max(GROUP.order))
+disp(['m:' num2str(m) '   max group order:' num2str(max(GROUP.order)) '   group size:' num2str(2^(m*(m-1)/2))])
     
     

### 2016-03-11 kuo_code/cpp/main.cc
Coding the t-value function in c++

@@ -1,0 +1,62 @@
+#include <iostream>
+#include <fstream>
+#include <vector>
+#include "rref.h"
+
+
+int main(){
+  ifstream infile("joe-kuo-old.1111",ios::in);
+  if (!infile) {
+    cout << "Input file containing direction numbers cannot be found!\n";
+    exit(1);
+  }
+  char buffer[1000];
+  infile.getline(buffer,1000,'\n');
+
+  for (unsigned j=1;j<=D-1;j++) {
+
+    // Read in parameters from file 
+    unsigned d, s;
+    unsigned a;
+    infile >> d >> s >> a;
+    unsigned *m = new unsigned [s+1];
+    for (unsigned i=1;i<=s;i++) infile >> m[i];
+}
+
+
+
+
+}
+
+
+/*
+    bool M1[3][3] = {   {1, 0, 1},
+                {0, 1, 1},
+                {1, 1, 0}   };
+    BooleanMatrix booleanMatrix1(M1, 3, 3);
+    std::cout << booleanMatrix1.getRank() << std::endl;
+
+    bool M2[4][4] = {   {1,1,1,0},
+                {0,1,1,0},
+                {0,1,0,0},
+                {1,1,1,1}   };
+    BooleanMatrix booleanMatrix2(M2, 4, 4);
+    std::cout << booleanMatrix2.getRank() << std::endl;
+
+    std::vector< std::vector<bool> > MM(5);
+    for (unsigned i = 0; i < 5; i++){
+        for (unsigned j = 0; j < 5; j++){
+                MM[i].push_back((i*j)%2);
+        }
+    }
+    for (unsigned i = 0; i < 5; i++){
+        for (unsigned j = 0; j < 5; j++){
+                std::cout << MM[i][j] << " ";
+        }
+    std::cout << std::endl;
+    }
+    MM[4][4] = 1;
+    BooleanMatrix booleanMatrix3(MM, 5, 5);
+    std::cout << booleanMatrix3.getRank() << std::endl;
+*/
+

### 2016-03-11 kuo_code/cpp/rref.h

@@ -1,0 +1,69 @@
+#include <vector>
+
+class BooleanMatrix{
+    std::vector< std::vector<bool> > mat; //boolean matrix
+    int n, m;           //size of matrix nxm
+    int rank;           //rank of the matrix
+
+    public:
+
+    /*Constructor
+     * Required Parameters:
+     * M ==> boolean matrix
+     * n ==> number of rows
+     * m ==> number of columns
+     */
+
+    BooleanMatrix(std::vector< std::vector<bool> > M, int n, int m){
+        this -> n = n;
+        this -> m = m;
+	this -> mat = M;
+        gaussElimination();
+    }
+    template <size_t size_m>
+    BooleanMatrix(bool M[][size_m], int n, int m){
+        this -> n = n;
+        this -> m = m;
+        for (int i = 0; i < n; i++){
+            std::vector<bool> row(m);
+            for (int j = 0; j < m; j++) row[j] = M[i][j];
+            mat.push_back(row);         
+        }
+        gaussElimination();
+    }
+
+    /* Does Gauss Elimination with partial pivoting on the matrix */
+     void gaussElimination(){
+        rank = n;
+        for (int i = 0; i < n; i++){
+            if (!mat[i][i]){
+                int j;
+                for (j = i+1; j < n && !mat[j][i]; j++);
+                if (j == n){
+                       rank--;
+                       continue;
+                }
+                else
+                    for (int k = i; k < m; k++){
+                        bool t = mat[i][k];
+                        mat[i][k] = mat[j][k];
+                        mat[j][k] = t;
+                    }
+            }
+            for (int j = i+1; j < n; j++){
+                if (mat[j][i]){
+                    for (int k = i; k < m; k++)
+                        mat[j][k] = mat[j][k] - mat[i][k];
+                }
+            }
+        }
+    }
+
+    /* Get the row rank of the boolean matrix
+     * If you require the rank of the matrix, make sure that n > m.
+     * i.e. if n < m, call the constructor over the transpose.
+     */
+    int getRank(){
+        return rank;
+    }
+};

### 2016-03-30 replicated_sobol.tex
changes: definitions,sections,notations

@@
 \newtheorem{defin}{Definition}
+\newtheorem{prop}{Proposition}
 \newtheorem{algo}{Algorithm}
@@
 \section{Problem Statement}
-Denote by $\vx \in [0,1)^d$ a point with components $x_1,\dots,x_d$.
-Let $u$ be a subset of $\{1,\dots,d\}$, $-u$ its complement and $|u|$ its cardinality.
+Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$.
+We set $\mathcal{D}=\{1,\dots,s\}$.
+Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality.
 $\vx_u$ represents a point in $[0,1)^u$ with components $x_j, j \in u$.
 Given two points $\vx$ and $\vx'$, we define the following hybrid point:
-\[(\vx_u:{\vx'}_{-u}) := ({x'}_1,\dots,{x'}_{u-1},x_u,{x'}_{u+1},\dots,{x'}_d).\]
-Let $f$ be the symbol representing the numerical model considered. We assume $f \in \mathcal{L}^2[0,1]^d$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
+\[\vz_u=(\vx_u:{\vx'}_{-u}), \text{ where: } \left\{
+      \begin{aligned}
+        z_j &= x_j, & \text{ if } j \in u\\
+        z_j &= {x'}_j, & \text{ if } j \in -u\\
+      \end{aligned}
+    \right.  \]
+Let $f$ be the symbol representing the numerical model considered. We assume $f \in \mathcal{L}^2[0,1]^s$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
 %These two quantities can be expressed as the following integrals:
@@
 %\[\sigma^2= \int_{[0,1)^{d}}f(\vx)^2 d\vx - \Big{(}\int_{[0,1)^{d}}f(\vx) d\vx\Big{)}^2 .\]
-The uncertainty on $\vx$ is modeled by random variables such that $\vx \sim \mathcal{U}[0,1]^d$. Recall the Hoeffding decomposition of $f$:
+The uncertainty on $\vx$ is modeled by random variables such that $\vx \stackrel{iid}{\sim} \mathcal{U}[0,1)^s$. Recall the Hoeffding decomposition of $f$:
 \begin{equation}
-f(\vx)=\mu+\sum \limits_{u \subseteq \{1,\dots,d\}} f_u(\vx),
+f(\vx)=\mu+\sum_{\substack{u \subseteq \{1,\dots,s\} \\ u \neq \emptyset}} f_u(\vx_u),
 \label{anova}
 \end{equation}
-where:
-\[f_u(\vx)= \int_{[0,1)^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).\]
+where: $\mu$ is a constant and $\forall \ u \subseteq \mathcal{D}, \ u \neq \emptyset, \ \forall \ j \in u: \int_{[0,1]} f_u(\vx_u) d{x_j}=0$.
 Due to orthogonality, by taking the variance of each side in Equation \ref{anova} we obtain the following decomposition of the variance:
-\[ \sigma^2 = \sum \limits_{u \subseteq \{1,\dots,d\}} \sigma_v^2.\]
+\[ \sigma^2 = \sum_{\substack{u \subseteq \{1,\dots,s\} \\ u \neq \emptyset}} \sigma_v^2.\]
 The problem of interest is the estimation of the quantities:
-\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad \text{ for } u = 1,\dots,d.\]
+\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad u \in \mathcal{D}.\]
 These quantities correspond to the partial sensitivity Sobol' indices often found written in the literature in their normalized form: $\underline{\tau}_u^2/\sigma^2$.
 When, $|u|=1$, $\underline{\tau}_u^2$ corresponds to the first-order Sobol' index that evaluate the main effect of the variable $\vx_u$.
+Higher order indices evaluate higher order interactions between variables.
 In \cite{}, Owen proposed to use the following expression for $\underline{\tau}_u^2$:
 \begin{equation}\label{first_order_indice}
-\underline{\tau}_u^2  =\int_{[0,1)^{2d-1}}(f(\vx) - \mu) (f(\vx_u:{\vx'}_{-u})-\mu) d\vx d{\vx'}_{-u},
+\underline{\tau}_u^2  =\int_{[0,1)^{2s-1}}(f(\vx) - \mu) (f(\vx_u:{\vx'}_{-u})-\mu) d\vx d{\vx'}_{-u},
 \end{equation}
 taking $\mu$ as introduced in Janon \textit{et al.}:
-\[\mu= \frac{1}{2} \int_{[0,1)^{2d-1}}f(\vx)+f(\vx_u:{\vx'}_{-u}) d\vx d{\vx'}_{-u}. \]
-The natural way to estimate these two quantities is for $(\vx_i,\vx'_i) \stackrel{iid}{\sim} [0,1)^{2d}$ via:
+\[\mu= \frac{1}{2} \int_{[0,1)^{2s-1}}f(\vx)+f(\vx_u:{\vx'}_{-u}) d\vx d{\vx'}_{-u}. \]
+The natural way to estimate these two quantities is for $(\vx_i,\vx'_i) \stackrel{iid}{\sim} [0,1)^{2s}$ via:
 \begin{align}
@@
 \end{align}
-\bigskip
 
 We consider here a quasi-Monte Carlo sampling strategy to evaluate these two estimators.
-We focus on the estimation of all first-order Sobol' indices.
-The classical estimation procedure introduced by Sobol' requires to evaluate the quantity $f(\vx_u:{\vx'}_{-u})$ $n$ times for each $u \in \{1,\dots,d\}$ while the quantity $f(\vx)$ is only evaluated $n$ times once for all $u$.
+We focus on the estimation of all first-order Sobol' indices, $u \in \mathcal{D}$.
+The classical estimation procedure introduced by Sobol' requires to evaluate the quantity $f(\vx_u:{\vx'}_{-u})$ $n$ times for each $u$ while the quantity $f(\vx)$ is only evaluated $n$ times once for all $u$.
 The total cost sums up to $n(d+1)$ evaluations of $f$.
 This cost can rapidly becomes prohibitive for expansive models involving an important number of parameters.
+
 An improvement to reduces this cost lies in the use of replicated designs.
-The notion of replicated designs was first introduced by McKay.
-It is defined as follows:
+The notion of replicated designs was first introduced by McKay through the introduction of replicated Latin Hypercubes samples.
+Here, we define replicated designs in a wider framework:
 \begin{defin}[Replicated designs]
-Let $X$ and $X'$ be two designs defined as follow:
-\[\arraycolsep=1.3pt
-X=\left(\begin{array}{ccccc}
-x_{1,1} & ... & x_{1,j} & ... & x_{1,d} \\
-\vdots &  & \vdots & & \vdots \\
-x_{i,1} & ... & x_{i,j} & ... & x_{i,d} \\
-\vdots &  & \vdots & & \vdots \\
-x_{n,1} & ... & x_{n,j} & ... & x_{n,d} \\
-\end{array} \right), \ X'=\left(\begin{array}{ccccc}
-{x'}_{1,1} & ... & {x'}_{1,j} & ... & {x'}_{1,d} \\
-\vdots &  & \vdots & & \vdots \\
-{x'}_{i,1} & ... & {x'}_{i,j} & ... & {x'}_{i,d} \\
-\vdots &  & \vdots & & \vdots \\
-{x'}_{n,1} & ... & {x'}_{n,j} & ... & {x'}_{n,d} \\
-\end{array} \right).
-\]
-Let the symbol $X_u$ (resp.
-$X'_u$), $u \subsetneq \{1,\dots,d-1\}$, denotes a subset of $u$ columns of $X$ (resp.
-$X'$).
-We say that $X$ and $X'$ are two replicated designs of order $r \in \{1,\dots,d-1\}$ if:
-
-$\forall \ u \subsetneq \{1,\dots,d\}$ such that $|u|=r$, $X_u$ and $X'_u$ represent the same point sets.
+Let $\mathcal{P}$ and $\mathcal{P}'$ be two points sets defined as follow:
+%\[\arraycolsep=1.3pt
+%D=\left(\begin{array}{ccccc}
+%x_{1,1} & ... & x_{1,j} & ... & x_{1,s} \\
+%\vdots &  & \vdots & & \vdots \\
+%x_{i,1} & ... & x_{i,j} & ... & x_{i,s} \\
+%\vdots &  & \vdots & & \vdots \\
+%x_{n,1} & ... & x_{n,j} & ... & x_{n,s} \\
+%\end{array} \right), \ D'=\left(\begin{array}{ccccc}
+%{x'}_{1,1} & ... & {x'}_{1,j} & ... & {x'}_{1,s} \\
+%\vdots &  & \vdots & & \vdots \\
+%{x'}_{i,1} & ... & {x'}_{i,j} & ... & {x'}_{i,s} \\
+%\vdots &  & \vdots & & \vdots \\
+%{x'}_{n,1} & ... & {x'}_{n,j} & ... & {x'}_{n,s} \\
+%\end{array} \right).
+%\]
+$\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$, $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$, $(\vx_i,\vx'_i) \stackrel{iid}{\sim} [0,1)^{2s}$.
+Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp.
+$\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of columns of $\mathcal{P}$ (resp.
+$\mathcal{P}'$) indexed by $u$.
+We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $r$ if:\\
+$\forall \ u \subsetneq \mathcal{D}$ such that $|u|=r$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ represent the same points set in $[0,1)^r$.
 \end{defin}
 The replication procedure introduced in \cite{•} allows to estimate all first-order Sobol' indices with two replicated designs of order $1$.
-In this procedure, the quantity $f(\vx_u:{\vx'}_{-u})$ is only evaluated $n$ times once for all $u$ resulting in a total of $2n$ evaluations of $f$.
-Denote by $X$,$X'$ the two replicated designs of order $1$ required by the replication procedure, $X'$ is constructed from $X$ as follows:
-\[{x'}_{i,j}=x_{\pi_j(i),j}, \qquad \forall \ (i,j) \in \{1,\dots,n\} \times \{1,\dots,d\},\]
-where $\pi_1,\dots,\pi_d$ are $d$ permutations on $\{1,\dots,n\}$.
-\bigskip
+In this procedure, the quantity $f(\vx_u:{\vx'}_{-u})$ is only evaluated $n$ times once for all $u$, resulting in a total of $2n$ evaluations of $f$.
+%Denote by $D$,$D'$ the two replicated designs of order $1$ required by the replication procedure, $D'$ is constructed from $D$ as follows:
+%\[{x'}_{i,j}=x_{\pi_j(i),j}, \qquad \forall \ (i,j) \in \{1,\dots,n\} \times \{1,\dots,d\},\]
+%where $\pi_1,\dots,\pi_d$ are $d$ permutations on $\{1,\dots,n\}$ selected randomly and independently.
 
-Our objective is to combine the use of Sobol' sequences with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \{1,\dots,d\}$.
-This would reduce the method to constructing two replicated designs of order $1$ that are iteratively augmented with new point sets.
-Two approaches are considered: one multiplicative and one additive.
-The first one uses the innate nested structure of a Sobol' sequence.
-The size of each replicated design is doubled at each step.
-The additive approach consists first of constructing a Sobol' sequence then shifting and scrambling it to form the new point sets.
-These new point sets are then added to the initial Sobol' sequence to form the two replicated designs.
-In this case, the size of each replicated design at step $k$ is $ k \times 2^m$ where $2^m$ is the size of the initial Sobol' sequence.
+Our objective here is to combine the use of Sobol' sequences with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \mathcal{D}$.
+This approach reduces to construct two replicated Sobol' sequences iteratively refined with new point sets.
+In this fashion, two approaches are considered: one multiplicative and one additive.
+In the next section, we provide some background on digital nets and sequences.
+The two approaches are detailed in Section \ref{sobol.seq.cons}.
 
@@
 
-In this section we introduce a particular type of quasi-Monte Carlo points to estimate $\eqref{first_order_indice}$, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{b^m}$ only one time to estimate all $d$ indices.
+In this section we introduce a particular type of quasi-Monte Carlo points called digital nets to estimate the quantities $\eqref{first_order_indice}$. 
+%, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{b^m}$ only one time to estimate all $d$ indices.
+ The concept of $(t,m,s)$-net and $(t,s)$-sequence was first introduced and studied by Niederreiter in \cite{•}.
+$(t,m,s)$-nets are digital nets in $\cubes$ whose quality is measured by the parameter $t$ called $t$-value.
+%Because this parameter is the criterion we use to construct our new sequences, we provide the key definitions below.
+ $(t,m,s)$-net and and $(t,s)$-sequence are strongly linked to the concept of star discrepancy \cite{.} and defined as follows:
+\begin{defin}[$(t,m,s)-net$]
+Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cubes$ where $A=\prod_{i=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $0\leq\gamma_j$ and $0\leq\alpha_j<b^{\gamma_j}$ for all $j=1,\dots,s$.
+For integers $s\geq 1$, $b\geq 2$, and $m\geq t\geq 0$, the points set $\mathcal{P}=\{\vx_i\}_{i=0}^{b^m-1}$, $\vx_i\in\cubes$, with $|\mathcal{P}|=b^m$, is a $(t,m,s)-net$ in base $b$ if:
 
-The concept of $(t,m,s)$-net and $(t,s)$-sequence was first introduced and studied by Niederreiter in \cite{•}.
-These are points sets in $\cubes$ whose quality is measured by the parameter $t$.
-Because this parameter is the criterion we use to construct our new sequences, we provide the key definitions below.
+for every $A\in\mathcal{A}$ with volume $b^{t-m}$, $|A\cap\mathcal{P}|=b^t$ ($A$ contains exactly $b^t$ points of $\mathcal{P}$).
+\end{defin}
+%In other words, any box of ... contains a proport
+%....
+%This definition is linked to the star discrepancy...
+%The smaller the t value, the better.
+\begin{defin}[$(t,s)$-sequence]
+For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i=1}^{\infty}$ is a $(t,s)$-sequence in base $b$, if every set $\mathcal{P}_{l,m}=\{\vx_i\}_{i=lb^m}^{(l+1)b^m-1}$ with $l\geq 0$ and $m\geq t$, $\mathcal{P}_{l,m}$ is a $(t,m,s)$-net in base $b$.
+\end{defin}
+In other words, the points set $\mathcal{P}$ is a $(t,m,s)$-net if its points are apportioned equally on all elementary intervals $A\in\mathcal{A}$.
+The smaller the $t$-value, the better the scattering of $\mathcal{P}$ in $\cubes$.
+\bigskip
 
-Let $\mathcal{A}$ be the set of all $A\in\cubes$ such that $A:=\prod_{i=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $0\leq\gamma_j$ and $0\leq\alpha_j<b^{\gamma_j}$ for all $j=1,\dots,s$.
+Digital nets are usually computed with square matrices $C_1^{\infty},\dots,C_s^{\infty}$ in $\mathbb{F}_b$ of size $\infty\times\infty$ often referred in the literature as generating matrices.
+However, to construct the first $b^m$ points, one only needs the knowledge of $C_1^m,\dots,C_s^m$.
+For each $i=0,\dots,b^m-1$, the points $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence can be constructed as follows:
+\begin{equation}
+\label{dig.net.eq.}
+(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^m (i_{0},\dots,i_{m-1})^\intercal,\qquad j= 1,\dots,s\, ,
+\end{equation}
+where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ is the radical inverse $b$-ary decomposition of point $x_{i,j}$ and $i = \sum_{k=0}^{m-1}i_kb^{k}$ is the $b$-ary decomposition of $i$.
+For $m' < m$ the matrices $C_j^{m'}$ are embedded in the upper left corners of matrices $C_j^{m}$.
+Thus, the digital nets possess an innate nested structure resulting from this embedding.
+That is $\mathcal{P}_{m'} \subset \mathcal{P}_m \subset \dots \subset \mathcal{P}_{\infty}$.
 
+Sobol' sequences are digital nets defined in base $b=2$.
+They are attractive due to their efficient implementation through the use of Gray code.
+In our scope, their attractiveness comes from their low growing rate (factor $2$).
+\bigskip
+
+In the next section, we present two approaches to construct two replicated Sobol' sequences iteratively refined with new points sets.
+The multiplicative approach uses the innate nested structure of a Sobol' sequence.
+The size of each replicated Sobol' sequence is doubled at each step.
+The additive approach combines digital shifting and scrambling operations to form the new points set.
+In this case, at step $k$ the size of each replicated Sobol' sequence is $ k \times 2^m$ where $2^m$ is the size of the initial Sobol' sequence.
+
+\section{Iterative constructions of replicated Sobol' sequence}
+\label{sobol.seq.cons}
+
+\subsection{Replicated Sobol' sequences}
+
+We start by introducing some useful definitions for the rest of the paper.
+We note by $\vi=(i_{0},\dots,i_{m-1})^T$ the vector resulting from the binary decomposition $\eqref{dig.net.eq.}$ of integer $i$.
+We also note by $U_m(\mathbb{F}_2)$ the multiplicative group of all invertible triangular matrices of size $m\times m$ over the Galois field $\mathbb{F}_2$.
+Consider the following application:
+\begin{equation*}
+ \Diamond \colon \left\lbrace \begin{array}{ccccc} (\mathbb{F}_2)^m \times U_m(\mathbb{F}_2) & \to & (\mathbb{F}_2)^m \\
+  (\vi,C) & \mapsto &  C . \vi \\
+\end{array} \right.
+\label{model}
+\end{equation*}
+The application $\Diamond$ consists in the operation carried on in Equation $\eqref{dig.net.eq.}$.
+It is easy to see that for $C \in U_m(\mathbb{F}_2)$ fixed, $\Diamond$ is a bijection of $(\mathbb{F}_2)^m$.
+As a results, applying $\Diamond$ for all $\vi \in (\mathbb{F}_2)^m$ with any generating matrix $C_j^m$ give the same points set.
+This leads to the following definition of replicated Sobol' sequences:
 \begin{defin}
-For integers $s\geq 1$, $b\geq 2$, and $m\geq t\geq 0$, the set of points $\mathcal{P}\in\cubes$, with $|\mathcal{P}|=b^m$, is a $(t,m,d)-net$ in base $b$ if for every $A\in\mathcal{A}$ with volume $b^{t-m}$, $|A\cap\mathcal{P}|=b^t$ ($A$ contains exactly $b^t$ points of $\mathcal{P}$).
+Let $C_j^m$, $C_{j'}^m$ be two generating matrices.
+The corresponding Sobol' sequences $\{\vx_i\}_{i=0}^{b^m-1}$ and $\{\vx'_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $1$.
+Furthermore, the digital sequences $\{{\vx}_i\}_{i=0}^{\infty}$ and $\{{\vx'}_i\}_{i=0}^{\infty}$ are two replicated Sobol' sequence, that is for all $m \geq 0$, $\{{\vx}_i\}_{i=b^{m-1}}^{b^m-1}$ and $\{{\vx'}_i\}_{i=b^{m-1}}^{b^m-1}$ are two replicated designs of order $1$.
 \end{defin}
+In other worlds, Sobol' sequences are innate replicated designs of order $1$ possessing a nested structure.
 
-In other words, any box of ... contains a proport
-....
-This definition is linked to the star discrepancy...
-The smaller the t value, the better.
+\subsection{Multiplicative approach}
+%
+%\begin{defin}
+%A digital sequence $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ is the \emph{replicated digital} sequence of $\{\vx_i\}_{i\in\mathbb{N}_0}$ if for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$.
+%\end{defin}
+%In this case, $C_j'$ will depend on the choice of $C_j$.
 
-\begin{defin}
-For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if every set $\mathcal{P}_{l,m}:=\{\vx_i\}_{i=lb^m}^{(l+1)b^m-1}$ with $l\geq 0$ and $m\geq t$, $\mathcal{P}_{l,m}$ is a $(t,m,s)$-net in base $b$.
-\end{defin}
-
-Digital nets are usually computed with the generating matrices $C_1,\dots,C_s$ in $\mathbb{F}_b$, whose size $\infty\times\infty$.
-However, to construct the first $b^m$ points, one only needs the knowledge of $C_1^{\infty\times m},\dots,C_s^{\infty\times m}$.
-For each $i=0,\dots,b^m-1$, the points $\vx_i = (x_{i,j},\dots,x_{i,s})^\intercal$ of the sequence can be constructed as follows:
-\begin{equation}
-(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^{\infty\times m}(i_{0},\dots,i_{m-1})^\intercal,\qquad j= 1,\dots,s\, ,
-\end{equation}
-where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ and $i = \sum_{k=0}^{m-1}i_kb^{k}$.
-
-\subsection{Replicated Digital Sequences}
-Here recall the link with the replicated method....
-\begin{defin}
-A digital sequence $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ is the \emph{replicated digital} sequence of $\{\vx_i\}_{i\in\mathbb{N}_0}$ if for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$.
-\end{defin}
-In this case, $C_j'$ will depend on the choice of $C_j$.
-
-If we do higher order Sobol' indices, we can easily show that $C'_{i}=AC_{i}$ for $i = 1,\dots,d$, and this does not work because this means having the same function values for each $u$, with a unique ordering given by $A$.
+%If we do higher order Sobol' indices, we can easily show that $C'_{i}=AC_{i}$ for $i = 1,\dots,d$, and this does not work because this means having the same function values for each $u$, with a unique ordering given by $A$.
 
@@
 Therefore, excluding the trivial case, it is enough to choose $C_j\neq C_j'$ for at least $d-1$ dimensions to obtain a \emph{replicated digital sequence}.
-When $b=2$, these are Sobol' sequences.
+%When $b=2$, these are Sobol' sequences.
 
@@
 
-\subsection{Matrix generators group $U_m$}
+%\subsection{Matrix generators group $U_m$}
+%
+%Be $U_m(\mathbb{F}_b)$ the multiplicative group of all invertible triangular matrices of size $m\times m$ over $\mathbb{F}_b$ ($GF(b)$). We have that $\abs{U_m(\mathbb{F}_b)}=(b-1)^m b^{(m-1)m/2}$.
+%
+%We consider the (infinite) set all possible generating matrices $C_1,C_2,\dots$. We also define the class 
+%
+%Indeed, we inherit all the group properties from the Permuatations group... because it is equivalent....
 
-Be $U_m(\mathbb{F}_b)$ the multiplicative group of all invertible triangular matrices of size $m\times m$ over $\mathbb{F}_b$ ($GF(b)$). We have that $\abs{U_m(\mathbb{F}_b)}=(b-1)^m b^{(m-1)m/2}$.
+%\subsection{Owen Scrambling To Replicated Digital Sequences}
+%
+%It will be easy to write that we can apply an Owen scrambling to each dimension separately, and we only need to keep the same scrambling for $C_j$ and $C'_j$.
 
-We consider the (infinite) set all possible generating matrices $C_1,C_2,\dots$. We also define the class
-
-Indeed, we inherit all the group properties from the Permuatations group... because it is equivalent....
-
-\subsection{Owen Scrambling To Replicated Digital Sequences}
-
-It will be easy to write that we can apply an Owen scrambling to each dimension separately, and we only need to keep the same scrambling for $C_j$ and $C'_j$.
-
-\section{Additive Approach}
-Notations:
-\begin{itemize}
-\item[.] $m$ denote the number of digits
-\item[.] $C_{m,1},\dots,C_{m,d}$: $d$ generator matrices of size $m \times m$ over the finite field $\mathcal{Z}_2$
-\item[.] $\vi$: base-$2$ representation of the integer $i$: $\vi=(i_1,\dots,i_m)^T$
-\item[.] $L_{m,l}$: nonsingular $m \times m$ lower triangular matrix over the finite field $\mathcal{Z}_2$
-\item[.] $\ve_{m,l}$: $m \times 1$ vector with elements from $\mathcal{Z}_2$
-\end{itemize}
-
-Denote by $X$ and $X'$ the two replicated designs of order $1$.
-A row of $X$ or $X'$ is a point in $[0,1]^d$.
+\subsection{Additive Approach}
+%Notations:
+%\begin{itemize}
+%\item[.] $m$ denote the number of digits
+%\item[.] $C_{m,1},\dots,C_{m,d}$: $d$ generator matrices of size $m \times m$ over the finite field $\mathcal{Z}_2$
+%\item[.] $\vi$: base-$2$ representation of the integer $i$: $\vi=(i_1,\dots,i_m)^T$
+%\item[.] $L_{m,l}$: nonsingular $m \times m$ lower triangular matrix over the finite field $\mathcal{Z}_2$
+%\item[.] $\ve_{m,l}$: $m \times 1$ vector with elements from $\mathcal{Z}_2$
+%\end{itemize}
+%
+%Denote by $X$ and $X'$ the two replicated designs of order $1$.
+%A row of $X$ or $X'$ is a point in $[0,1]^d$.
 The symbol $x_i^j$ (resp.
@@
 All operations are carried on the finite field $\mathcal{Z}_2$.
-\begin{algorithm}[!ht]
-
-\begin{center}
-\begin{minipage}{10cm}
-\begin{enumerate}
-\item[Step 1.] Instantiation: $X \leftarrow \emptyset$, $X' \leftarrow \emptyset$, $l \leftarrow 1$, $\widehat{\underline{\tau}_u^2}^{(0)} \leftarrow 0$.
-\item[Step 4.] $while$ ($!$ stopping criterion):
-\begin{enumerate}
-\item[4.1] Construct $L_{m,l}$ and $\ve_{m,l}$.
-\item[4.2] Augment both $X$ and $X'$:\\
-for $j=1,\dots,d$:\\
-for $i=1+2^{m+l-1},\dots,2^{m+l}$:
-\begin{flalign*}
-x_i^j & = C_{m,j} . \vi + \ve_{m,l} && \\
-{x'}_i^j & = L_{m,l} . (C_{m,j} . \vi +  \ve_{m,l})&&
-\end{flalign*}
-\item[4.3] For $u=1,\dots,d$: evaluate $\widehat{\underline{\tau}_u^2}^{(l)}.$ 
-\item[4.4.]  $l \leftarrow l+1.$
-\end{enumerate}
-\item[Step 5.] Return: $\widehat{\underline{\tau}_u^2}, \ u \in \{1,\dots,d\}.$ 
-\end{enumerate}
-\end{minipage}
-\end{center}
-\label{additive}
-\caption{Additive approach}
-\end{algorithm}
-
-\section{L Matrices Fred Method Too Restrictive}
+%\begin{algorithm}[!ht]
+%
+%\begin{center}
+%\begin{minipage}{10cm}
+%\begin{enumerate}
+%\item[Step 1.] Instantiation: $X \leftarrow \emptyset$, $X' \leftarrow \emptyset$, $l \leftarrow 1$, $\widehat{\underline{\tau}_u^2}^{(0)} \leftarrow 0$.
+%\item[Step 4.] $while$ ($!$ stopping criterion):
+%\begin{enumerate}
+%\item[4.1] Construct $L_{m,l}$ and $\ve_{m,l}$.
+%\item[4.2] Augment both $X$ and $X'$:\\
+%for $j=1,\dots,d$:\\
+%for $i=1+2^{m+l-1},\dots,2^{m+l}$:
+%\begin{flalign*}
+%x_i^j & = C_{m,j} . \vi + \ve_{m,l} && \\
+%{x'}_i^j & = L_{m,l} . (C_{m,j} . \vi +  \ve_{m,l})&&
+%\end{flalign*}
+%\item[4.3] For $u=1,\dots,d$: evaluate $\widehat{\underline{\tau}_u^2}^{(l)}.$ 
+%\item[4.4.]  $l \leftarrow l+1.$
+%\end{enumerate}
+%\item[Step 5.] Return: $\widehat{\underline{\tau}_u^2}, \ u \in \{1,\dots,d\}.$ 
+%\end{enumerate}
+%\end{minipage}
+%\end{center}
+%\label{additive}
+%\caption{Additive approach}
+%\end{algorithm}
 

### 2016-03-31 replicated_sobol.tex
Changes to commit to replicated Sobol

--- 2016-03-11 replicated_sobol.tex
@@
 where:
-\[f_u(\vx)= \int_{[0,1)^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).\]
+\[f_u(\vx)= \int_{[0,1)^{d-|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).\]
 Due to orthogonality, by taking the variance of each side in Equation \ref{anova} we obtain the following decomposition of the variance:

### 2016-04-01 replicated_sobol.tex
filled subsection additive approach

--- 2016-03-30 replicated_sobol.tex
@@
 
-\title{}
+\title{On the replication of Sobol' sequences to estimate main effects of model inputs}
 
 \author{Cl\'ementine Prieur, Elise Arnaud, Herv\'{e} Monod, Laurent Gilquin, Fred J. Hickernell, Llu\'{i}s Antoni Jim\'{e}nez Rugama}
-\address{U. Josef Fourier, Illinois Institute of Technology}
-\begin{abstract}
-\end{abstract}
+\address{University Grenoble Alpes, Illinois Institute of Technology, INRA Jouy-en-Josas}
+%\begin{abstract}
+%\end{abstract}
 
@@
 %\[\sigma^2= \int_{[0,1)^{d}}f(\vx)^2 d\vx - \Big{(}\int_{[0,1)^{d}}f(\vx) d\vx\Big{)}^2 .\]
-The uncertainty on $\vx$ is modeled by random variables such that $\vx \stackrel{iid}{\sim} \mathcal{U}[0,1)^s$. Recall the Hoeffding decomposition of $f$:
+The uncertainty on $\vx$ is modeled by random variables such that $\vx \stackrel{iid}{\sim} \mathcal{U}[0,1)^s$. Recall the Hoeffding cite{hoeffding} decomposition of $f$:
 \begin{equation}
@@
 \[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad u \in \mathcal{D}.\]
-These quantities correspond to the partial sensitivity Sobol' indices often found written in the literature in their normalized form: $\underline{\tau}_u^2/\sigma^2$.
+These quantities correspond to the partial sensitivity Sobol' indices \cite{sobol} often found written in the literature in their normalized form: $\underline{\tau}_u^2/\sigma^2$.
 When, $|u|=1$, $\underline{\tau}_u^2$ corresponds to the first-order Sobol' index that evaluate the main effect of the variable $\vx_u$.
 Higher order indices evaluate higher order interactions between variables.
-In \cite{}, Owen proposed to use the following expression for $\underline{\tau}_u^2$:
+In \cite{owen}, Owen proposed to use the following expression for $\underline{\tau}_u^2$:
 \begin{equation}\label{first_order_indice}
@@
 \end{equation}
-taking $\mu$ as introduced in Janon \textit{et al.}:
+taking $\mu$ as introduced in \cite{monod,janon}:
 \[\mu= \frac{1}{2} \int_{[0,1)^{2s-1}}f(\vx)+f(\vx_u:{\vx'}_{-u}) d\vx d{\vx'}_{-u}. \]
@@
 An improvement to reduces this cost lies in the use of replicated designs.
-The notion of replicated designs was first introduced by McKay through the introduction of replicated Latin Hypercubes samples.
+The notion of replicated designs was first introduced by McKay \cite{mckay} through the introduction of replicated Latin Hypercubes samples.
 Here, we define replicated designs in a wider framework:
@@
 \end{defin}
-The replication procedure introduced in \cite{•} allows to estimate all first-order Sobol' indices with two replicated designs of order $1$.
+The replication procedure introduced and studied in \cite{mara,tissot} allows to estimate all first-order Sobol' indices with two replicated designs of order $1$.
 In this procedure, the quantity $f(\vx_u:{\vx'}_{-u})$ is only evaluated $n$ times once for all $u$, resulting in a total of $2n$ evaluations of $f$.
@@
 
-Our objective here is to combine the use of Sobol' sequences with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \mathcal{D}$.
+Our objective here is to combine the use of Sobol' sequences \cite{sobolseq} with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \mathcal{D}$.
 This approach reduces to construct two replicated Sobol' sequences iteratively refined with new point sets.
@@
 %, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{b^m}$ only one time to estimate all $d$ indices.
- The concept of $(t,m,s)$-net and $(t,s)$-sequence was first introduced and studied by Niederreiter in \cite{•}.
+ The concept of $(t,m,s)$-net and $(t,s)$-sequence was first introduced and studied by Niederreiter in \cite{niederreiter}.
 $(t,m,s)$-nets are digital nets in $\cubes$ whose quality is measured by the parameter $t$ called $t$-value.
 %Because this parameter is the criterion we use to construct our new sequences, we provide the key definitions below.
- $(t,m,s)$-net and and $(t,s)$-sequence are strongly linked to the concept of star discrepancy \cite{.} and defined as follows:
+ $(t,m,s)$-net and and $(t,s)$-sequence are strongly linked to the concept of star discrepancy \cite{star} and defined as follows:
 \begin{defin}[$(t,m,s)-net$]
@@
 Thus, the digital nets possess an innate nested structure resulting from this embedding.
-That is $\mathcal{P}_{m'} \subset \mathcal{P}_m \subset \dots \subset \mathcal{P}_{\infty}$.
+%That is $\mathcal{P}_{m'} \subset \mathcal{P}_m \subset \dots \subset \mathcal{P}_{\infty}$.
 
@@
 We start by introducing some useful definitions for the rest of the paper.
-We note by $\vi=(i_{0},\dots,i_{m-1})^T$ the vector resulting from the binary decomposition $\eqref{dig.net.eq.}$ of integer $i$.
-We also note by $U_m(\mathbb{F}_2)$ the multiplicative group of all invertible triangular matrices of size $m\times m$ over the Galois field $\mathbb{F}_2$.
+We note by $\vi=(i_{0},\dots,i_{m-1})^\intercal$ the vector resulting from the binary decomposition $\eqref{dig.net.eq.}$ of integer $i$.
+We note by $\mathbb{N}_0$ the integer space.
+We also note by $U_m(\mathbb{F}_2)$ the multiplicative group of all invertible upper triangular matrices of size $m\times m$ over the Galois field $\mathbb{F}_2$.
 Consider the following application:
@@
 \end{array} \right.
-\label{model}
 \end{equation*}
@@
 The corresponding Sobol' sequences $\{\vx_i\}_{i=0}^{b^m-1}$ and $\{\vx'_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $1$.
-Furthermore, the digital sequences $\{{\vx}_i\}_{i=0}^{\infty}$ and $\{{\vx'}_i\}_{i=0}^{\infty}$ are two replicated Sobol' sequence, that is for all $m \geq 0$, $\{{\vx}_i\}_{i=b^{m-1}}^{b^m-1}$ and $\{{\vx'}_i\}_{i=b^{m-1}}^{b^m-1}$ are two replicated designs of order $1$.
+Furthermore, the digital sequences $\{{\vx}_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are two replicated Sobol' sequence, that is for all $m \geq 0$, $\{{\vx}_i\}_{i=b^{m-1}}^{b^m-1}$ and $\{{\vx'}_i\}_{i=b^{m-1}}^{b^m-1}$ are two replicated designs of order $1$.
 \end{defin}
@@
 
-The best choice of primitive polynomials and directional numbers to generate good quality Sobol' sequences is deeply discussed in \cite{•}.
+The best choice of primitive polynomials and directional numbers to generate good quality Sobol' sequences is deeply discussed in \cite{kuo}.
 We are going to take Kuo and Joe results to find  good \emph{replicated Sobol'} sequences.
 
-Pairwise projections are already well optimized (see\cite[Table 2.1]{•}).
-Thus, our starting point will be using the $C_1,\dots,C_d$ found in \cite{•} to generate the sequence $\{{\vx}_i\}_{i\in\mathbb{N}_0}$.
+Pairwise projections are already well optimized (see\cite[Table 2.1]{kuo2}).
+Thus, our starting point will be using the $C_1,\dots,C_d$ found in \cite{kuo2} to generate the sequence $\{{\vx}_i\}_{i\in\mathbb{N}_0}$.
 Hence, we will focus on finding the optimal $C'_{1},\dots,C'_{d}$ such that we minimize a $t$-value criteria (to specify, perhaps the max of all) over all $d$ sequences described in \eqref{ordered_sequence}.
@@
 \subsection{Additive Approach}
+
+Denote by $\mathcal{P}$ and $\mathcal{P}'$ the two replicated designs iteratively refined with new points sets using the additive approach. These two designs possess a block structure:
+$$\mathcal{P}= B_0 \cup B_1 \cup B_2 \dots $$
+$$\mathcal{P}'= {B'}_0 \cup {B'}_1 \cup {B'}_2 \dots $$
+We detail below the steps of the construction of these two designs.
+\begin{enumerate}
+\item[Step 1.] We start by fixing $m$ and choosing a set $C_1^{m},\dots,C_s^{m}$ of generating matrices to construct an initial Sobol' sequence $\{\vx_i\}_{i=0}^{2^m-1}$ of $2^m$ points. \\
+
+\item[Step 2.] At step $l$ of the recursive estimation, $l \geq 0$, a new points set $B_l=\{\vx_i^{(l)}\}_{i=0}^{2^m-1}$ of $2^m$ points is added to $\mathcal{P}$.
+$B_l$ is obtained by applying a digital shift to the initial Sobol' sequence.
+The digital shift operation is applied as follows:
+
+for each $i=0,\dots,2^m-1$, the points $\vx_i^{(l)} = (x_{i,1}^{(l)},\dots,x_{i,s}^{(l)})^\intercal$ is obtained by:
+\begin{equation}
+\label{dig.shift}
+(x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal = C_j^m \vi^\intercal+\ve_j,\qquad j= 1,\dots,s\, ,
+\end{equation}
+where $ x_{i,j}^{(l)}=\sum_{k = 1}^mx_{i,j,k}^{(l)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{m-1}})^\intercal \in (\mathbb{F}_2)^m$.\\
+
+\item[Step 3.] Then, the points set ${B'}_l=\{{\vx'}_i^{(l)}\}_{i=0}^{2^m-1}$ is obtained from $B_l$ by applying Tezuka's i-binomial scrambling \cite{tezuka}. This operation consists in the following:
+
+for each $i=0,\dots,2^m-1$, the points ${\vx'}_i^{(l)} = ({x'}_{i,1}^{(l)},\dots,{x'}_{i,s}^{(l)})^\intercal$ is obtained by:
+\begin{equation}
+\label{ibinom.scrambling}
+({x'}_{i,j,1}^{(l)},\dots,{x'}_{i,j,m}^{(l)})^\intercal = L_j^m (x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal,
+\end{equation}
+where $ {x'}_{i,j}^{(l)}=\sum_{k = 1}^m{x'}_{i,j,k}^{(l)}2^{-k}$ and $L_j^m$ is an invertible lower triangular matrix of size $m \times m$ over the Galois field $\mathbb{F}_2$.\\
+
+\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomised using a same Owen's scrambling \cite{owen.scrambl}
+
+\item[Step 5.] $B_l$ and ${B'}_l$ are used to estimate all first-order indices $\underline{\tau}_u^2, u \in \mathcal{D}$.
+\end{enumerate}
+Steps $2$ to $5$ are iterated until a stopping criterion is reached.
+There is a finite choice for the vector $\ve_j$ and matrix $L_j^m$ respectively constructed in Steps $2$ and $3$.
+Once $m$ is fixed, one can build up to $2^m$ different $\ve_j$ and $2^{m(m-1)/2}$ different $L_j^m$.
+The choice of $m$ must take into account these limitations.
+
+ At each step $l$, $B_l$ and ${B'}_l$ are two replicated designs of order $1$ thus enabling the estimation of all first-order indices.
+Denote by $K$ the step at which the recursive estimation stopped.
+The total cost of the additive approach to estimate all first-order indices equals $2 \times K \times 2^m$.
+
+The additive approach is attractive due to the slow growing size of the two replicated designs $\mathcal{P}$ and $\mathcal{P}'$.
+At the opposite of the multiplicative approach, the main drawback is that $\mathcal{P}$ and $\mathcal{P}'$ does not possess the structure of a Sobol' sequence but each block $B_l$ (resp.
+$B'_l$) composing them does.
+
 %Notations:
@@
 %\end{algorithm}
+\section*{References}
+\bibliographystyle{elsarticle-num-names} 
+\bibliography{bib}
 

### 2016-04-01 replicated_sobol.tex
Changes in replicated_sobol.tex

--- 2016-03-30 replicated_sobol.tex
@@
 \newcommand{\dtf}{\textit{\doubletilde{f}}}
-\newcommand{\cube}{[0,1)^d}
-\newcommand{\cubes}{[0,1)^s}
+\newcommand{\cube}{[0,1)^s}
 %\renewcommand{\bbK}{\natzero^d}
@@
 where: $\mu$ is a constant and $\forall \ u \subseteq \mathcal{D}, \ u \neq \emptyset, \ \forall \ j \in u: \int_{[0,1]} f_u(\vx_u) d{x_j}=0$.
+
 Due to orthogonality, by taking the variance of each side in Equation \ref{anova} we obtain the following decomposition of the variance:
@@
 The total cost sums up to $n(d+1)$ evaluations of $f$.
-This cost can rapidly becomes prohibitive for expansive models involving an important number of parameters.
+This cost can rapidly become prohibitive for models whose evaluation is time consuming, as such involve an important number of parameters.
 
-An improvement to reduces this cost lies in the use of replicated designs.
+An improvement to reduce this cost lies in the use of replicated designs.
 The notion of replicated designs was first introduced by McKay through the introduction of replicated Latin Hypercubes samples.
@@
 \begin{defin}[Replicated designs]
-Let $\mathcal{P}$ and $\mathcal{P}'$ be two points sets defined as follow:
+Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets,
 %\[\arraycolsep=1.3pt
@@
 %\]
-$\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$, $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$, $(\vx_i,\vx'_i) \stackrel{iid}{\sim} [0,1)^{2s}$.
+$\vx_i,\vx'_i\in[0,1)^{s}$.
 Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp.
-$\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of columns of $\mathcal{P}$ (resp.
+$\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp.
 $\mathcal{P}'$) indexed by $u$.
 We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $r$ if:\\
-$\forall \ u \subsetneq \mathcal{D}$ such that $|u|=r$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ represent the same points set in $[0,1)^r$.
+$\forall \ u \subsetneq \mathcal{D}$ such that $|u|=r$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^r$.
 \end{defin}
@@
 
-Our objective here is to combine the use of Sobol' sequences with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \mathcal{D}$.
+Our objective here is to combine the use of Sobol' sequences with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \mathcal{D}$, $\abs{u}=1$.
 This approach reduces to construct two replicated Sobol' sequences iteratively refined with new point sets.
@@
 
-In this section we introduce a particular type of quasi-Monte Carlo points called digital nets to estimate the quantities $\eqref{first_order_indice}$. 
+In this section we introduce a particular type of quasi-Monte Carlo points to estimate the quantities in $\eqref{first_order_indice}$ for $\abs{u}=1$, according to the replication method. 
 %, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{b^m}$ only one time to estimate all $d$ indices.
- The concept of $(t,m,s)$-net and $(t,s)$-sequence was first introduced and studied by Niederreiter in \cite{•}.
-$(t,m,s)$-nets are digital nets in $\cubes$ whose quality is measured by the parameter $t$ called $t$-value.
+The concepts of $(t,m,s)$-net and $(t,s)$-sequence were first introduced by Niederreiter in \cite{•}.
+Digital nets are accurately defined as $(t,m,s)$-nets in $\cube$ whose quality is measured by the parameter $t$, called $t$-value.
 %Because this parameter is the criterion we use to construct our new sequences, we provide the key definitions below.
- $(t,m,s)$-net and and $(t,s)$-sequence are strongly linked to the concept of star discrepancy \cite{.} and defined as follows:
+%$(t,m,s)$-net and and $(t,s)$-sequence are strongly linked to the concept of star discrepancy \cite{.} and defined as follows:
 \begin{defin}[$(t,m,s)-net$]
-Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cubes$ where $A=\prod_{i=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $0\leq\gamma_j$ and $0\leq\alpha_j<b^{\gamma_j}$ for all $j=1,\dots,s$.
-For integers $s\geq 1$, $b\geq 2$, and $m\geq t\geq 0$, the points set $\mathcal{P}=\{\vx_i\}_{i=0}^{b^m-1}$, $\vx_i\in\cubes$, with $|\mathcal{P}|=b^m$, is a $(t,m,s)-net$ in base $b$ if:
+Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cube$ where $A=\prod_{j=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $s\geq 1$, $b\geq 2$, $\gamma_j\geq 0$, and $b^{\gamma_j}>\alpha_j\geq 0$.
+For $m\geq t\geq 0$, the point set $\mathcal{P}\in\cube$ with $b^m$ points is a $(t,m,s)-net$ in base $b$ if every $A$ with volume $b^{t-m}$ contains $b^t$ points of $\mathcal{P}$.
+\end{defin}
 
-for every $A\in\mathcal{A}$ with volume $b^{t-m}$, $|A\cap\mathcal{P}|=b^t$ ($A$ contains exactly $b^t$ points of $\mathcal{P}$).
+A $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points.
+The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest size possible, $b^{-m}$, contains exactly one point.
+Note that if $t'>t$, $(t,m,s)$-nets are always $(t',m,s)$-nets.
+
+\begin{defin}[$(t,s)$-sequence]
+For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
 \end{defin}
-%In other words, any box of ... contains a proport
-%....
-%This definition is linked to the star discrepancy...
-%The smaller the t value, the better.
-\begin{defin}[$(t,s)$-sequence]
-For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i=1}^{\infty}$ is a $(t,s)$-sequence in base $b$, if every set $\mathcal{P}_{l,m}=\{\vx_i\}_{i=lb^m}^{(l+1)b^m-1}$ with $l\geq 0$ and $m\geq t$, $\mathcal{P}_{l,m}$ is a $(t,m,s)$-net in base $b$.
-\end{defin}
-In other words, the points set $\mathcal{P}$ is a $(t,m,s)$-net if its points are apportioned equally on all elementary intervals $A\in\mathcal{A}$.
-The smaller the $t$-value, the better the scattering of $\mathcal{P}$ in $\cubes$.
-\bigskip
 
-Digital nets are usually computed with square matrices $C_1^{\infty},\dots,C_s^{\infty}$ in $\mathbb{F}_b$ of size $\infty\times\infty$ often referred in the literature as generating matrices.
-However, to construct the first $b^m$ points, one only needs the knowledge of $C_1^m,\dots,C_s^m$.
-For each $i=0,\dots,b^m-1$, the points $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence can be constructed as follows:
+Digital sequences are usually computed with $\infty\times\infty$-matrices $C_1,\dots,C_s$ over $\mathbb{F}_b$, often referred in the literature as generating matrices.
+However, to construct the first $b^m$ points, one only needs the knowledge of the blocks $C_1^{\infty\times m},\dots,C_s^{\infty\times m}$.
+This is due to its construction, described as follows.
+For each $i=0,\dots,b^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension per dimension:
 \begin{equation}
 \label{dig.net.eq.}
-(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^m (i_{0},\dots,i_{m-1})^\intercal,\qquad j= 1,\dots,s\, ,
+(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^{\infty\times m} (i_{0},\dots,i_{m-1})^\intercal,\qquad j= 1,\dots,s\, ,
 \end{equation}
-where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ is the radical inverse $b$-ary decomposition of point $x_{i,j}$ and $i = \sum_{k=0}^{m-1}i_kb^{k}$ is the $b$-ary decomposition of $i$.
+where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ and $i = \sum_{k=0}^{m-1}i_kb^{k}$.
 For $m' < m$ the matrices $C_j^{m'}$ are embedded in the upper left corners of matrices $C_j^{m}$.

### 2016-04-01 replicated_sobol.tex

--- 2016-04-01 replicated_sobol.tex
@@
 The total cost sums up to $n(d+1)$ evaluations of $f$.
-This cost can rapidly becomes prohibitive for expansive models involving an important number of parameters.
+This cost can rapidly become prohibitive for models whose evaluation is time consuming, as such involve an important number of parameters.
 
-An improvement to reduces this cost lies in the use of replicated designs.
+An improvement to reduce this cost lies in the use of replicated designs.
 The notion of replicated designs was first introduced by McKay \cite{mckay} through the introduction of replicated Latin Hypercubes samples.
@@
 
-Our objective here is to combine the use of Sobol' sequences \cite{sobolseq} with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \mathcal{D}$.
+Our objective here is to combine the use of Sobol' sequences \cite{sobolseq} with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \mathcal{D}$, $\abs{u}=1$.
 This approach reduces to construct two replicated Sobol' sequences iteratively refined with new point sets.
@@
 
-In this section we introduce a particular type of quasi-Monte Carlo points called digital nets to estimate the quantities $\eqref{first_order_indice}$. 
+In this section we introduce a particular type of quasi-Monte Carlo points to estimate the quantities in $\eqref{first_order_indice}$ for $\abs{u}=1$, according to the replication method. 
 %, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{b^m}$ only one time to estimate all $d$ indices.
- The concept of $(t,m,s)$-net and $(t,s)$-sequence was first introduced and studied by Niederreiter in \cite{niederreiter}.
-$(t,m,s)$-nets are digital nets in $\cubes$ whose quality is measured by the parameter $t$ called $t$-value.
+
+The concepts of $(t,m,s)$-net and $(t,s)$-sequence were first introduced by Niederreiter in \cite{niederreiter}.
+Digital nets are accurately defined as $(t,m,s)$-nets in $\cube$ whose quality is measured by the parameter $t$, called $t$-value.
 %Because this parameter is the criterion we use to construct our new sequences, we provide the key definitions below.
- $(t,m,s)$-net and and $(t,s)$-sequence are strongly linked to the concept of star discrepancy \cite{star} and defined as follows:
+%$(t,m,s)$-net and and $(t,s)$-sequence are strongly linked to the concept of star discrepancy \cite{.} and defined as follows:
 \begin{defin}[$(t,m,s)-net$]
-Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cubes$ where $A=\prod_{i=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $0\leq\gamma_j$ and $0\leq\alpha_j<b^{\gamma_j}$ for all $j=1,\dots,s$.
-For integers $s\geq 1$, $b\geq 2$, and $m\geq t\geq 0$, the points set $\mathcal{P}=\{\vx_i\}_{i=0}^{b^m-1}$, $\vx_i\in\cubes$, with $|\mathcal{P}|=b^m$, is a $(t,m,s)-net$ in base $b$ if:
+Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cube$ where $A=\prod_{j=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $s\geq 1$, $b\geq 2$, $\gamma_j\geq 0$, and $b^{\gamma_j}>\alpha_j\geq 0$.
+For $m\geq t\geq 0$, the point set $\mathcal{P}\in\cube$ with $b^m$ points is a $(t,m,s)-net$ in base $b$ if every $A$ with volume $b^{t-m}$ contains $b^t$ points of $\mathcal{P}$.
+\end{defin}
 
-for every $A\in\mathcal{A}$ with volume $b^{t-m}$, $|A\cap\mathcal{P}|=b^t$ ($A$ contains exactly $b^t$ points of $\mathcal{P}$).
+A $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points.
+The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest size possible, $b^{-m}$, contains exactly one point.
+Note that if $t'>t$, $(t,m,s)$-nets are always $(t',m,s)$-nets.
+
+\begin{defin}[$(t,s)$-sequence]
+For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
 \end{defin}
-%In other words, any box of ... contains a proport
-%....
-%This definition is linked to the star discrepancy...
-%The smaller the t value, the better.
-\begin{defin}[$(t,s)$-sequence]
-For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i=1}^{\infty}$ is a $(t,s)$-sequence in base $b$, if every set $\mathcal{P}_{l,m}=\{\vx_i\}_{i=lb^m}^{(l+1)b^m-1}$ with $l\geq 0$ and $m\geq t$, $\mathcal{P}_{l,m}$ is a $(t,m,s)$-net in base $b$.
-\end{defin}
-In other words, the points set $\mathcal{P}$ is a $(t,m,s)$-net if its points are apportioned equally on all elementary intervals $A\in\mathcal{A}$.
-The smaller the $t$-value, the better the scattering of $\mathcal{P}$ in $\cubes$.
-\bigskip
 
-Digital nets are usually computed with square matrices $C_1^{\infty},\dots,C_s^{\infty}$ in $\mathbb{F}_b$ of size $\infty\times\infty$ often referred in the literature as generating matrices.
-However, to construct the first $b^m$ points, one only needs the knowledge of $C_1^m,\dots,C_s^m$.
-For each $i=0,\dots,b^m-1$, the points $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence can be constructed as follows:
+Digital sequences are usually computed with $\infty\times\infty$-matrices $C_1,\dots,C_s$ over $\mathbb{F}_b$, often referred in the literature as generating matrices.
+However, to construct the first $b^m$ points, one only needs the knowledge of the blocks $C_1^{\infty\times m},\dots,C_s^{\infty\times m}$.
+This is due to its construction, described as follows.
+For each $i=0,\dots,b^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension per dimension:
 \begin{equation}
 \label{dig.net.eq.}
-(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^m (i_{0},\dots,i_{m-1})^\intercal,\qquad j= 1,\dots,s\, ,
+(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^{\infty\times m} (i_{0},\dots,i_{m-1})^\intercal,\qquad j= 1,\dots,s\, ,
 \end{equation}
-where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ is the radical inverse $b$-ary decomposition of point $x_{i,j}$ and $i = \sum_{k=0}^{m-1}i_kb^{k}$ is the $b$-ary decomposition of $i$.
+where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ and $i = \sum_{k=0}^{m-1}i_kb^{k}$.
 For $m' < m$ the matrices $C_j^{m'}$ are embedded in the upper left corners of matrices $C_j^{m}$.

### 2016-04-02 replicated_sobol.tex
Adding all changes to the multiplicative method

@@
 \newcommand{\vi}{\bvec{i}}
+\newcommand{\vj}{\bvec{j}}
 \newcommand{\ve}{\bvec{e}}
@@
 A $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points.
-The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest size possible, $b^{-m}$, contains exactly one point.
+The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest volume possible, $b^{-m}$, contains exactly one point.
 Note that if $t'>t$, $(t,m,s)$-nets are always $(t',m,s)$-nets.
@@
 \begin{defin}[$(t,s)$-sequence]
-For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
+For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if for every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
 \end{defin}
@@
 This is due to its construction, described as follows.
-For each $i=0,\dots,b^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension per dimension:
+For each $i=0,\dots,b^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise:
 \begin{equation}
 \label{dig.net.eq.}
-(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^{\infty\times m} (i_{0},\dots,i_{m-1})^\intercal,\qquad j= 1,\dots,s\, ,
+(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^{\infty\times m} \vi,\qquad j= 1,\dots,s\, ,
 \end{equation}
-where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ and $i = \sum_{k=0}^{m-1}i_kb^{k}$.
-For $m' < m$ the matrices $C_j^{m'}$ are embedded in the upper left corners of matrices $C_j^{m}$.
+where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ is the b-ary decomposition of $i$.
+%For $m' < m$ the matrices $C_j^{m'}$ are embedded in the upper left corners of matrices $C_j^{m}$.
 Thus, the digital nets possess an innate nested structure resulting from this embedding.
-%That is $\mathcal{P}_{m'} \subset \mathcal{P}_m \subset \dots \subset \mathcal{P}_{\infty}$.
+That is $\mathcal{P}_{m'} \subset \mathcal{P}_m \subset \dots \subset \mathcal{P}_{\infty}$.
 
-Sobol' sequences are digital nets defined in base $b=2$.
-They are attractive due to their efficient implementation through the use of Gray code.
-In our scope, their attractiveness comes from their low growing rate (factor $2$).
+In order to relate digital nets and sequences to the definition of replicated design, we introduce the following concept.
+\begin{defin}
+Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are \emph{digitally replicated} of order $r$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $r$.
+\end{defin}
+
 \bigskip
 
-In the next section, we present two approaches to construct two replicated Sobol' sequences iteratively refined with new points sets.
-The multiplicative approach uses the innate nested structure of a Sobol' sequence.
-The size of each replicated Sobol' sequence is doubled at each step.
-The additive approach combines digital shifting and scrambling operations to form the new points set.
+Sobol' sequences are digital sequences attractive for their easy implementation and optimized properties \cite{kuo2}.
+% In our scope, their attractiveness comes from their low growing rate (factor $2$).
+In section \ref{sobol.seq.cons}, we present two approaches to construct replicated point sets based on Sobol' sequences.
+The multiplicative approach uses two Sobol' sequences that are replicated by construction, while the additive approach takes an initial number of points of two Sobol' sequences and applies digital shifts and scramblings to extend the point set.
 In this case, at step $k$ the size of each replicated Sobol' sequence is $ k \times 2^m$ where $2^m$ is the size of the initial Sobol' sequence.
 
-\section{Iterative constructions of replicated Sobol' sequence}
+\section{Iterative constructions of replicated point sets}
 \label{sobol.seq.cons}
 
-\subsection{Replicated Sobol' sequences}
+Sobol' sequences are particularly interesting for having unitriangular generating matrices over $\mathbb{F}_2$. This property leads to the result below,
 
-We start by introducing some useful definitions for the rest of the paper.
+\begin{lem}\label{Sobol_replicated}
+All Sobol' sequences are digitally replicated of order 1.
+\end{lem}
+\begin{proof}
+Consider any two s-dimensional Sobol' sequences generated by $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$.
+Since these matrices are upper triangular, to compute the first $2^m$ points one only needs the knowledge of the $m\times m$ blocks.
+Because any two matrices $C^{m\times m}_j$ and $C'^{\,m\times m}_j$ are square and full rank, the products $C^{m\times m}_j\vi$ and $C'^{\,m\times m}_j\vi$ are one-to one and onto, for all $i=0,\dots,2^m-1$.
+Therefore, they generate the same point sets.
+\end{proof}
+
+%We start by introducing some useful definitions for the rest of the paper.
 We note by $\vi=(i_{0},\dots,i_{m-1})^\intercal$ the vector resulting from the binary decomposition $\eqref{dig.net.eq.}$ of integer $i$.
@@
 Consider the following application:
-\begin{equation*}
- \Diamond \colon \left\lbrace \begin{array}{ccccc} (\mathbb{F}_2)^m \times U_m(\mathbb{F}_2) & \to & (\mathbb{F}_2)^m \\
-  (\vi,C) & \mapsto &  C . \vi \\
-\end{array} \right.
-\end{equation*}
-The application $\Diamond$ consists in the operation carried on in Equation $\eqref{dig.net.eq.}$.
+%\begin{equation*}
+% \Diamond \colon \left\lbrace \begin{array}{ccccc} (\mathbb{F}_2)^m \times U_m(\mathbb{F}_2) & \to & (\mathbb{F}_2)^m \\
+%  (\vi,C) & \mapsto &  C . \vi \\
+%\end{array} \right.
+%\end{equation*}
+%The application $\Diamond$ consists in the operation carried on in Equation $\eqref{dig.net.eq.}$.
 It is easy to see that for $C \in U_m(\mathbb{F}_2)$ fixed, $\Diamond$ is a bijection of $(\mathbb{F}_2)^m$.
@@
 This leads to the following definition of replicated Sobol' sequences:
-\begin{defin}
-Let $C_j^m$, $C_{j'}^m$ be two generating matrices.
+%\begin{defin}
+%Let $C_j^m$, $C_{j'}^m$ be two generating matrices.
 The corresponding Sobol' sequences $\{\vx_i\}_{i=0}^{b^m-1}$ and $\{\vx'_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $1$.
 Furthermore, the digital sequences $\{{\vx}_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are two replicated Sobol' sequence, that is for all $m \geq 0$, $\{{\vx}_i\}_{i=b^{m-1}}^{b^m-1}$ and $\{{\vx'}_i\}_{i=b^{m-1}}^{b^m-1}$ are two replicated designs of order $1$.
-\end{defin}
-In other worlds, Sobol' sequences are innate replicated designs of order $1$ possessing a nested structure.
+%\end{defin}
+%In other worlds, Sobol' sequences are innate replicated designs of order $1$ possessing a nested structure.
+
+Two different matrices $C^{m\times m}$ and $C'^{\,m\times m}$ produce the same set of $2^m$ values.
+However, they will appear in different order.
+It is possible to generate them in the same order using the corresponding upper triangular matrix $U^{m\times m}$, such that $C^{m\times m}=C'^{\,m\times m}U^{m\times m}$.
+This matrix can be thought as permutation of the input binary vectors $\vi$.
 
 \subsection{Multiplicative approach}
-%
-%\begin{defin}
-%A digital sequence $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ is the \emph{replicated digital} sequence of $\{\vx_i\}_{i\in\mathbb{N}_0}$ if for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$.
-%\end{defin}
-%In this case, $C_j'$ will depend on the choice of $C_j$.
 
-%If we do higher order Sobol' indices, we can easily show that $C'_{i}=AC_{i}$ for $i = 1,\dots,d$, and this does not work because this means having the same function values for each $u$, with a unique ordering given by $A$.
+The goal of this method is to generate a $2s$-dimensional Sobol' sequence with good properties to estimate all first order Sobol' indices.
+As shown in Lemma \ref{Sobol_replicated}, for any $m\geq 0$ and $2^m$ points, each dimension of the sequence will have exactly the same values, although probably with different order.
 
-Although the choices of $C_j$ and $C_j'$ are many, there is a special case interesting for its construction simplicity, and wide range of $C_j'$ choices.
+The only constraint we have is that for each $u=1,\dots,s$, the $2s$-dimensional Sobol' sequence must ensure that $x_{i,u}=x_{i,u}$ for $i\in\mathbb{N}_0$.
+Therefore, we will need $s$ different $2s$-dimensional sequences.
+These sequences can be constructed using a single $2s$-dimensional sequence and considering the corresponding upper triangular matrices $U_u$.
 
-For this special case, we consider the generating matrices to be upper triangular.
-This ensures that $x_{i,j,k}=0$, for $m<k$ and $0 \leq i \leq b^m-1$.
-If we also assume that there are no zeros on the diagonal, the block $C_j^{m\times m}$ is full rank and each $x_{i,j}\neq x_{r,j}$ when $i\neq r$.
-Therefore, excluding the trivial case, it is enough to choose $C_j\neq C_j'$ for at least $d-1$ dimensions to obtain a \emph{replicated digital sequence}.
-%When $b=2$, these are Sobol' sequences.
+Given the generators $C_1,\dots,C_s,C'_1,\dots,C'_s$, we  define the $U_u$ matrices such that $C_u=C'_uU_u$.
+Then, each sequence generated by $C_1,\dots,C_s,C'_1U_u,\dots,C'_sU_u$ will satisfy $x_{i,u}=x_{i,u}$, for all $i\in\mathbb{N}_0$.
 
-For quasi-Monte Carlo integration purposes, given $\{{\vx}_i\}_{i\in\mathbb{N}_0}$ generated by $C_{1},\dots,C_{d}$, and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ generated by $C'_{1},\dots,C'_{d}$, the $d$ sequences in dimension $2d-1$ used to estimate all $\underline{\tau}_u^2$ are generated by
-\begin{equation}\label{ordered_sequence}
-\underbrace{C_{1},\dots,C_{d}}_{\text{First }d\text{ dimensions}},\underbrace{C_{\alpha(u,1)},\dots,C_{\alpha(u,u-1)},C_{\alpha(u,u+1)},\dots,C_{\alpha(u,d)}}_{\text{Next }d-1\text{ dimensions}},\quad 1\leq u \leq d\, ,
-\end{equation}
-where $C_{\alpha(u,i)}:=C_u(C'_{u})^{-1}C'_{i}$.
-Note that for $i=u$, one has $C_{\alpha(u,u)}=C_u$.
-This is in fact forcing $C_u = C'_{u}$, as desired to apply the replicated method.
-Therefore, our goal is to find a good choice of $C_{1},\dots,C_{d},C'_{1},\dots,C'_{d}$ such that for all $u=1,\dots,d$, the sequence used to estimate $\underline{\tau}_u^2$ has a low $t$-value.
+\begin{prop}
+For any $m\geq 0$, and $t_m$ depending on $m$, if the Sobol' $(t_m,m,s)$-nets are generated by $C_1,\dots,C_s$, then $C_1U,\dots,C_sU$, where $U$ is an upper triangular matrix, generate exactly the same $(t_m,m,s)$-nets.
+\end{prop}
+\begin{proof}
+For any $m$ and $2^{m-1}\leq i < 2^m$, the image by $U$, $\vj=U\vi$, will also satisfy $2^{m-1}\leq j < 2^m$.
+The reason is because $U$ is upper triangular, therefore $j_{m-1}=i_{m-1}$.
+Thus, by induction on $m$, the $(t_m,m,s)$-nets generated after applying the permutation $U$ contain exactly the same points.
+\end{proof}
 
-The best choice of primitive polynomials and directional numbers to generate good quality Sobol' sequences is deeply discussed in \cite{kuo}.
-We are going to take Kuo and Joe results to find  good \emph{replicated Sobol'} sequences.
+This means that the use of these matrices $U_u$ do not affect the quality of our initial sequence.
 
-Pairwise projections are already well optimized (see\cite[Table 2.1]{kuo2}).
-Thus, our starting point will be using the $C_1,\dots,C_d$ found in \cite{kuo2} to generate the sequence $\{{\vx}_i\}_{i\in\mathbb{N}_0}$.
-Hence, we will focus on finding the optimal $C'_{1},\dots,C'_{d}$ such that we minimize a $t$-value criteria (to specify, perhaps the max of all) over all $d$ sequences described in \eqref{ordered_sequence}.
+Sobol' generating matrices $C$ are constructed through primitive polynomials and initial directional numbers.
+How to choose them is deeply discussed in \cite{kuo}.
+The $t$-values of pairwise projections are already optimized in \cite{kuo2}.
+Thus, we will consider the $2s$-dimensional Sobol' sequence described by them to construct the other $s$ $2s$-dimensional sequences.
+
+We still can optimize the quality of the $s$ sequences together by taking a different order of the generating matrices of the initial sequence.
+Given the generators $C_1,\dots,C_{2s}$, for all $s$ reordered sequences, the projections $C_i-C_j$ appear $s$ times when $0<i<j\leq s$, $s-1$ times when $0<i\leq s<j\leq 2s$, and $s-2$ times if $s<i<j\leq 2s$.
+Hence, we can sort the matrices such that sets of bad $C_{\pi(i)}-C_{\pi(j)}$ projections are mostly for $s<{\pi(i)}<{\pi(j)}\leq 2s$.
+
+In addition to it, one can still randomize the initial Sobol' sequence using Owen's scrambling \cite{owen.scrambl}.
+The only requirement to keep the replication property is to apply the same scrambling to dimensions that differ by $s$ positions, i.e., same scrambling to $C_j$ and $C_{j+s}$ for all $j=1,\dots,s$.
 
@@
 \label{dig.shift}
-(x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal = C_j^m \vi^\intercal+\ve_j,\qquad j= 1,\dots,s\, ,
+(x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal = C_j^m \vi+\ve_j,\qquad j= 1,\dots,s\, ,
 \end{equation}

### 2016-04-02 replicated_sobol.tex
Fixing typo x_{i,u}=x_{i,u+s}

@@
 
-The only constraint we have is that for each $u=1,\dots,s$, the $2s$-dimensional Sobol' sequence must ensure that $x_{i,u}=x_{i,u}$ for $i\in\mathbb{N}_0$.
+The only constraint we have is that for each $u=1,\dots,s$, the $2s$-dimensional Sobol' sequence must ensure that $x_{i,u}=x_{i,u+s}$ for $i\in\mathbb{N}_0$.
 Therefore, we will need $s$ different $2s$-dimensional sequences.
@@
 Given the generators $C_1,\dots,C_s,C'_1,\dots,C'_s$, we  define the $U_u$ matrices such that $C_u=C'_uU_u$.
-Then, each sequence generated by $C_1,\dots,C_s,C'_1U_u,\dots,C'_sU_u$ will satisfy $x_{i,u}=x_{i,u}$, for all $i\in\mathbb{N}_0$.
+Then, each sequence generated by $C_1,\dots,C_s,C'_1U_u,\dots,C'_sU_u$ will satisfy $x_{i,u}=x_{i,u+s}$, for all $i\in\mathbb{N}_0$.
 

### 2016-04-02 replicated_sobol.tex
link multiplicative approach, replicated designs

@@
 \subsection{Multiplicative approach}
+Denote by $\mathcal{P}$ and $\mathcal{P}'$ the two designs iteratively refined with new points sets using the multiplicative approach.
+%Based on Lemma \ref{Sobol_replicated}, by taking $\mathcal{P}$ and $\mathcal{P}'$ to be two $s$-dimensional Sobol' sequences we obtain two replicated designs or order $1$ with an innate nested structure.
+The goal of this approach is to generate a $2s$-dimensional Sobol' sequence with good properties to estimate all first order Sobol' indices.
+Design $\mathcal{P}$ is formed with the first $s$ dimensions of the sequence and design $\mathcal{P}'$ with the $s$ reminding ones.
+As shown in Lemma \ref{Sobol_replicated}, for any $m\geq 0$ and $2^m$ points, each dimension of the sequence will have exactly the same values, although probably with different order.
+Thus, designs $\mathcal{P}$ and $\mathcal{P}'$ are nested replicated designs of order $1$ and both are $s$-dimensional Sobol' sequences.
 
-The goal of this method is to generate a $2s$-dimensional Sobol' sequence with good properties to estimate all first order Sobol' indices.
-As shown in Lemma \ref{Sobol_replicated}, for any $m\geq 0$ and $2^m$ points, each dimension of the sequence will have exactly the same values, although probably with different order.
-
-The only constraint we have is that for each $u=1,\dots,s$, the $2s$-dimensional Sobol' sequence must ensure that $x_{i,u}=x_{i,u+s}$ for $i\in\mathbb{N}_0$.
+The only constraint we have is that for each $u=1,\dots,s$, to estimate the quantity $\underline{\tau}_u^2$ the $2s$-dimensional Sobol' sequence must ensure that $x_{i,u}=x_{i,u+s}$ for $i\in\mathbb{N}_0$.
 Therefore, we will need $s$ different $2s$-dimensional sequences.
@@
 \end{equation}
-where $ x_{i,j}^{(l)}=\sum_{k = 1}^mx_{i,j,k}^{(l)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{m-1}})^\intercal \in (\mathbb{F}_2)^m$.\\
+where $ x_{i,j}^{(l)}=\sum_{k = 1}^mx_{i,j,k}^{(l)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{m-1}})^\intercal \in ker(C_j^m)$ the kernel of $C_j^m$.\\
 
@@
 
-\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomised using a same Owen's scrambling \cite{owen.scrambl}
+\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomized using the same Owen's scrambling column-wise.
 
@@
 There is a finite choice for the vector $\ve_j$ and matrix $L_j^m$ respectively constructed in Steps $2$ and $3$.
-Once $m$ is fixed, one can build up to $2^m$ different $\ve_j$ and $2^{m(m-1)/2}$ different $L_j^m$.
-The choice of $m$ must take into account these limitations.
+%Once $m$ is fixed, one can build up to $2^m$ different $\ve_j$ and $2^{m(m-1)/2}$ different $L_j^m$.
+The choice of $m$ must take into account this limitation.
 

### 2016-05-09 crass/crass.tex
crass repository

% Template article for preprint document class `elsart'
% SP 2001/01/05
% Modified CG (ESME) for Model 3, single column, 2 titles, abstract/résumé,
%  and 2 sets of keywords - 07.01.03 - file called Maths-English.tex
% English Version for Mathematics (CRAS series 1)
% Revamped, CG, 17.08.04, adding header, dates, and presenter

\documentclass{elsart3-1}

% Use the option doublespacing or reviewcopy to obtain double line spacing
% \documentclass[doublespacing]{elsart}

% if you use PostScript figures in your article
% use the graphics package for simple commands
% \usepackage{graphics}
% or use the graphicx package for more complicated commands
% \usepackage{graphicx}
% or use the epsfig package if you prefer to use the old commands
% \usepackage{epsfig}

% The amssymb package provides various useful mathematical symbols
\usepackage{amsmath,amssymb}

\usepackage[english,francais]{babel}

%ENVIRONMENTS THEOREMS...
% These are predefined, and follow the numbering system used in the journal!
%English
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{e-proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{e-definition}[theorem]{Definition\rm}
\newtheorem{remark}{\it Remark\/}
\newtheorem{example}{\it Example\/}
%French
\newtheorem{theoreme}{Th\'eor\`eme}[section]
\newtheorem{lemme}[theoreme]{Lemme}
\newtheorem{proposition}[theoreme]{Proposition}
\newtheorem{corollaire}[theoreme]{Corollaire}
\newtheorem{definition}[theoreme]{D\'efinition\rm}
\newtheorem{remarque}{\it Remarque}
\newtheorem{exemple}{\it Exemple\/}
\renewcommand{\theequation}{\arabic{equation}}
\setcounter{equation}{0}

\newcommand{\fudge}{\fC}
\newcommand{\dtf}{\textit{\doubletilde{f}}}
\newcommand{\cube}{[0,1)^s}
\newcommand{\rf}{\mathring{f}}
\newcommand{\rnu}{\mathring{\nu}}
\newcommand{\natm}{\naturals_{0,m}}
\newcommand{\wcS}{\widecheck{S}}
\newcommand{\tol}{\text{tol}}
\newcommand{\bvec}[1]{\boldsymbol{#1}}
\newcommand{\vx}{\bvec{x}}
\newcommand{\vi}{\bvec{i}}
\newcommand{\vj}{\bvec{j}}
\newcommand{\ve}{\bvec{e}}
\newcommand{\vk}{\bvec{k}}
\newcommand{\vz}{\bvec{z}}
\newcommand{\dif}{\mathsf{d}}
\newcommand{\hf}{\hat{f}}
\newcommand{\hS}{\widehat{S}}
\newcommand{\tS}{\widetilde{S}}
\newcommand{\tf}{\tilde{f}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\homega}{\widehat{\omega}}
\newcommand{\wcomega}{\mathring{\omega}}
\newcommand{\vzero}{\bvec{0}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\naturals}{\mathbb{N}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}

\def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% GUILLEMETS (FRENCH QUOTES) %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\og{\leavevmode\raise.3ex\hbox{$\scriptscriptstyle\langle\!\langle$~}}
\def\fg{\leavevmode\raise.3ex\hbox{~$\!\scriptscriptstyle\,\rangle\!\rangle$}}

\journal{the Acad\'emie des sciences}
\begin{document}
% place in the next line the header (rubrique) chosen for your article,
% if you know it (you can also have 2, format : Header1/Header2
\centerline{}
\begin{frontmatter}

% Title, authors and addresses

% use the thanksref command within \title, \author or \address for footnotes;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
% \title{Title\thanksref{label1}}
% \thanks[label1]{}
% \author{Name\thanksref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \thanks[label2]{}
% \address{Address\thanksref{label3}}
% \thanks[label3]{}
\selectlanguage{english}
\title{On the replication of Sobol' sequences to estimate main effects of model inputs}

% use optional labels to link authors explicitly to addresses:
% \author[label1,label2]{}
% \address[label1]{}
% \address[label2]{}
% The [label1] can be suppressed if there is only one address for all authors

\selectlanguage{english}
\author[authorlabel1]{Laurent Gilquin},
\ead{laurent.gilquin@inria.fr}
\author[authorlabel2]{Llu\'{i}s Antoni Jim\'{e}nez Rugama},
%\ead{ljimene1@hawk.iit.edu}
\author[authorlabel3]{Elise Arnaud},
\author[authorlabel2]{Fred J. Hickernell},
\author[authorlabel4]{Herv\'{e} Monod},
\author[authorlabel3]{Cl\'{e}mentine Prieur}

\address[authorlabel1]{Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 655 avenue de l'Europe, 38330 Montbonnot}
\address[authorlabel2]{TO FILL}
\address[authorlabel3]{Univ. Grenoble Alpes, Jean Kunzmann Laboratory, F-38000 Grenoble, France \\
CNRS, LJK, F-38000 Grenoble, France, Inria}
\address[authorlabel4]{MaIAGE, INRA, Universit\'{e} Paris-Saclay, 78350 Jouy-En-Josas, France}

% If you know the dates of reception, and acceptation you can put them now;
%  idem the name of the person presenting the Note

\medskip
\begin{center}
{\small Received *****; accepted after revision +++++\\
Presented by £££££}
\end{center}

\begin{abstract}
\selectlanguage{english}
% Text of abstract in English
Your abstract in English here.
{\it To cite this article: A.
Name1, A. Name2, C. R. Acad. Sci. Paris, Ser. I 340 (2005).}

\vskip 0.5\baselineskip

\selectlanguage{francais}
% Text of abstract in French
\noindent{\bf R\'esum\'e} \vskip 0.5\baselineskip \noindent
{\bf Here is the title in French. }
Your resume in French here.
{\it Pour citer cet article~: A. Name1, A. Name2, C. R. Acad. Sci.
Paris, Ser. I 340 (2005).}

\end{abstract}
\end{frontmatter}

\selectlanguage{english}

\section{Introduction}
Mathematical models used in various fields often involve a substantial number of poorly known parameters. The effect of these parameters on the output of the model can be assessed through sensitivity analysis. Global sensitivity analysis methods are useful tools to identify the parameters having the most influence on the output. A well known approach is the variance based method introduced by Sobol' \cite{sobol'}. This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model's input. In particular, one can distinguish first-order indices that estimate the main effect of each input.

The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) all suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension. %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.  
 An elegant solution to reduce this cost relies on the construction of particular designs of experiments called replicated designs. The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes \cite{mckay}. 
Here, replicated designs are defined in a wider framework:

\begin{definition}%[Replicated designs]
\label{rep.designs}
Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$. Set $\mathcal{D}=\{1,\dots,s\}$. Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets,
$\vx_i,\vx'_i\in[0,1)^{s}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $r$ if:\\
$\forall \ u \subsetneq \mathcal{D}$ such that $|u|=r$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^r$.
\end{definition}

With the construction of only two replicated designs of order $1$, the replication procedure introduced and studied in \cite{mara,tissot} allows to estimate all first-order Sobol' indices. This procedure has the major advantage of reducing drastically the estimation cost as the number of runs (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension. However, if the input space is not properly explored the Sobol' indices estimates may still not be accurate enough. 
\bigskip

In this note, we propose to construct replicated point sets based on Sobol' sequences to generate two space-filling replicated designs of order $1$. These two designs insure that the input space is properly explored and can then be used within the replication procedure to estimate all main-effects of a numerical model. We first provide backgrounds on digital sequences, then we present two iterative approaches to construct replicated point sets based on Sobol' sequences.

\section{Digital sequences background}

\subsection{Preliminaries}

The introduction of digital nets and sequences has its origin in numerical integration and uniform distribution. Explicit constructions of digital sequences have been developed notably by Sobol' and Niederreiter \cite{niderreiter} into the overarching notion of $(t,m,s)$-nets and $(t,s)$-sequences. A comprehensive theory of $(t,m,s)$-net and $(t,s)$-sequences was first formulate by Niederreiter.

$(t,m,s)$-nets are defined as point sets in $\cube$ whose quality is measured by the parameter $t$, called $t$-value. They are defined as follows:
\begin{definition}%[$(t,m,s)-net$]
Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cube$ where $A=\prod_{j=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $s\geq 1$, $b\geq 2$, $\gamma_j\geq 0$, and $b^{\gamma_j}>\alpha_j\geq 0$. For $m\geq t\geq 0$, the point set $\mathcal{P}\in\cube$ with $b^m$ points is a $(t,m,s)-net$ in base $b$ if every $A$ with volume $b^{t-m}$ contains $b^t$ points of $\mathcal{P}$.
\end{definition}

A $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points. The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest volume possible, $b^{-m}$, contains exactly one point. %Note that if $t'>t$, $(t,m,s)$-nets are always $(t',m,s)$-nets.

$(t,s)$-sequences are the infinite analogues of $(t,m,s)$-nets. They are defined as follows:
\begin{definition}%[$(t,s)$-sequence]
For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if for every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
\end{definition}
\bigskip

All $(t,m,s)$-nets and $(t,s)$-sequences relevant for applications are based on a digital construction scheme over a finite field $\mathbb{F}_b$ with $b$ a prime power number. Digital nets and sequences referred to these structures. 
\bigskip

The construction scheme of a $s$-dimensional digital sequence requires the knowledge of the base $b$ and a set of $s$ full rank upper triangular matrices of infinite size called generating matrices. These generating matrices are recursively constructed through primitive polynomials and initial directional numbers (see \cite{niederreiter} for further details). Denote by $C_1,\dots,C_s$ $s$ generating matrices over $\mathbb{F}_b$. For $m>0$ and $j \in \{1,\dots,s\}$, we note $C_j^{m}$ the $m \times m$ upper left block of $C_j$. The first $b^m$ points $\{\vx_0,\dots,\vx_{b^m-1}\}$ of the digital sequence are constructed as follows:\\

For each $i=0,\dots,b^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise by:
\begin{equation}
\label{dig.net.eq.}
(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^{m} \vi,\qquad j= 1,\dots,s\, ,
\end{equation}
where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ is the b-ary decomposition of $i$.
\bigskip

For $m' > m$ the matrix $C_j^m$ is embedded in the upper left of matrices $C_j^{m'}$. Resulting from this embedding, the construction of a digital sequence can be performed iteratively. To link digital sequences to the definition of replicated designs, we introduce the following concept:
\begin{definition}
Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are said \emph{digitally replicated} of order $r$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $r$.
\end{definition}

\subsection{Sobol' sequences}

Sobol' sequences are digital sequences constructed in base $2$. These sequences are attractive for their easy implementation and optimized properties \cite{kuo2}. Sobol' sequences are particularly interesting for having full rank upper triangular generating matrices over $\mathbb{F}_2$. This property leads to the following lemma:
\begin{lemma}\label{Sobol_replicated}
All Sobol' sequences are digitally replicated of order 1.
\end{lemma}
\begin{pf*}{\textit{Proof}.}
Consider any two s-dimensional Sobol' sequences generated respectively by the matrices $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$. Since these matrices are upper triangular, to compute the first $2^m$ points one only needs the knowledge of the $m\times m$ upper left blocks $C_j^m$ and ${C'}_j^m$, $j \in \{1,\dots,s\}$. Because any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the products $C^{m}_j\vi$ and ${C'}^{m}_j\vi$ are one-to one and onto, for all $i=0,\dots,2^m-1$. Therefore, they generate the same point sets.
\end{pf*} 
For $j \in \{1,\dots,s\}$, using two different generating matrices $C^{m}_j$ and $C'^{m}_j$ in equation (\ref{dig.net.eq.}) produce the same set of $2^m$ values $\{x_{0,j},\dots,x_{2^m-1,j}\}$ but ordered differently. It is possible to go from an order to the other by using the corresponding full rank upper triangular matrix $U^{m}_j$, such that $C^{m}_j=C'^{m}U^{m}_j$. This matrix can be thought as a permutation of the input binary vectors $\vi$.

\section{Iterative construction of replicated point sets}

%In section \ref{sobol.seq.cons}, we present two approaches to construct replicated point sets based on Sobol' sequences. The multiplicative approach uses two Sobol' sequences that are replicated by construction, while the additive approach takes an initial number of points of two Sobol' sequences and applies digital shifts and scramblings to extend the point set. In this case, at step $k$ the size of each replicated Sobol' sequence is $ k \times 2^m$ where $2^m$ is the size of the initial Sobol' sequence.

\subsection{Multiplicative approach}
Denote by $\mathcal{P}$ and $\mathcal{P}'$ the two designs iteratively refined with new points sets using the multiplicative approach. %Based on Lemma \ref{Sobol_replicated}, by taking $\mathcal{P}$ and $\mathcal{P}'$ to be two $s$-dimensional Sobol' sequences we obtain two replicated designs or order $1$ with an innate nested structure.
The goal of this approach is to generate a $2s$-dimensional Sobol' sequence with good properties to estimate all first order Sobol' indices. Design $\mathcal{P}$ is formed with the first $s$ dimensions of the sequence and design $\mathcal{P}'$ with the $s$ remaining ones. As shown in Lemma \ref{Sobol_replicated}, for any $m\geq 0$ and $2^m$ points, each dimension of the sequence will have exactly the same values, although probably with different order. Thus, designs $\mathcal{P}$ and $\mathcal{P}'$ are nested replicated designs of order $1$ and both are $s$-dimensional Sobol' sequences.

The only constraint we have is that for each $u=1,\dots,s$, to estimate the quantity $\underline{\tau}_u^2$ the $2s$-dimensional Sobol' sequence must ensure that $x_{i,u}=x_{i,u+s}$ for $i\in\mathbb{N}_0$. Therefore, we will need $s$ different $2s$-dimensional sequences. These sequences can be constructed using a single $2s$-dimensional sequence and considering the corresponding upper triangular matrices $U_u$.

Given the generators $C_1,\dots,C_s,C'_1,\dots,C'_s$, we define the $U_u$ matrices such that $C_u=C'_uU_u$. Then, each sequence generated by $C_1,\dots,C_s,C'_1U_u,\dots,C'_sU_u$ will satisfy $x_{i,u}=x_{i,u+s}$, for all $i\in\mathbb{N}_0$.

\begin{proposition}
For any $m\geq 0$, and $t_m$ depending on $m$, if the Sobol' $(t_m,m,s)$-nets are generated by $C_1,\dots,C_s$, then $C_1U,\dots,C_sU$, where $U$ is an upper triangular matrix, generate exactly the same $(t_m,m,s)$-nets.
\end{proposition}
\begin{pf*}{Proof.}
For any $m$ and $2^{m-1}\leq i < 2^m$, the image by $U$, $\vj=U\vi$, will also satisfy $2^{m-1}\leq j < 2^m$. The reason is because $U$ is upper triangular, therefore $j_{m-1}=i_{m-1}$. Thus, by induction on $m$, the $(t_m,m,s)$-nets generated after applying the permutation $U$ contain exactly the same points.
\end{pf*}

This means that the use of these matrices $U_u$ do not affect the quality of our initial sequence.

Sobol' generating matrices $C$ are constructed through primitive polynomials and initial directional numbers. How to choose them is deeply discussed in \cite{kuo}. The $t$-values of pairwise projections are already optimized in \cite{kuo2}. Thus, we will consider the $2s$-dimensional Sobol' sequence described by them to construct the other $s$ $2s$-dimensional sequences.

We still can optimize the quality of the $s$ sequences together by taking a different order of the generating matrices of the initial sequence. Given the generators $C_1,\dots,C_{2s}$, for all $s$ reordered sequences, the projections $C_i-C_j$ appear $s$ times when $0<i<j\leq s$, $s-1$ times when $0<i\leq s<j\leq 2s$, and $s-2$ times if $s<i<j\leq 2s$. Hence, we can sort the matrices such that sets of bad $C_{\pi(i)}-C_{\pi(j)}$ projections are mostly for $s<{\pi(i)}<{\pi(j)}\leq 2s$.

In addition to it, one can still randomize the initial Sobol' sequence using Owen's scrambling \cite{owen.scrambl}. The only requirement to keep the replication property is to apply the same scrambling to dimensions that differ by $s$ positions, i.e., same scrambling to $C_j$ and $C_{j+s}$ for all $j=1,\dots,s$.

\subsection{Additive Approach}

Denote by $\mathcal{P}$ and $\mathcal{P}'$ the two replicated designs iteratively refined with new points sets using the additive approach. These two designs possess a block structure:
$$\mathcal{P}= B_0 \cup B_1 \cup B_2 \dots $$
$$\mathcal{P}'= {B'}_0 \cup {B'}_1 \cup {B'}_2 \dots $$
We detail below the steps of the construction of these two designs.
\begin{enumerate}
\item[Step 1.] We start by fixing $m$ and choosing a set $C_1^{m},\dots,C_s^{m}$ of generating matrices to construct an initial Sobol' sequence $\{\vx_i\}_{i=0}^{2^m-1}$ of $2^m$ points. \\

\item[Step 2.] At step $l$ of the recursive estimation, $l \geq 0$, a new points set $B_l=\{\vx_i^{(l)}\}_{i=0}^{2^m-1}$ of $2^m$ points is added to $\mathcal{P}$. $B_l$ is obtained by applying a digital shift to the initial Sobol' sequence. The digital shift operation is applied as follows:

for each $i=0,\dots,2^m-1$, the points $\vx_i^{(l)} = (x_{i,1}^{(l)},\dots,x_{i,s}^{(l)})^\intercal$ is obtained by:
\begin{equation}
\label{dig.shift}
(x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal = C_j^m \vi+\ve_j,\qquad j= 1,\dots,s\, ,
\end{equation}
where $ x_{i,j}^{(l)}=\sum_{k = 1}^mx_{i,j,k}^{(l)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{m-1}})^\intercal \in ker(C_j^m)$ the kernel of $C_j^m$.\\

\item[Step 3.] Then, the points set ${B'}_l=\{{\vx'}_i^{(l)}\}_{i=0}^{2^m-1}$ is obtained from $B_l$ by applying Tezuka's i-binomial scrambling \cite{tezuka}. This operation consists in the following:

for each $i=0,\dots,2^m-1$, the points ${\vx'}_i^{(l)} = ({x'}_{i,1}^{(l)},\dots,{x'}_{i,s}^{(l)})^\intercal$ is obtained by:
\begin{equation}
\label{ibinom.scrambling}
({x'}_{i,j,1}^{(l)},\dots,{x'}_{i,j,m}^{(l)})^\intercal = L_j^m (x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal,
\end{equation}
where $ {x'}_{i,j}^{(l)}=\sum_{k = 1}^m{x'}_{i,j,k}^{(l)}2^{-k}$ and $L_j^m$ is an invertible lower triangular matrix of size $m \times m$ over the Galois field $\mathbb{F}_2$.\\

\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomized using the same Owen's scrambling column-wise.

\item[Step 5.] $B_l$ and ${B'}_l$ are used to estimate all first-order indices $\underline{\tau}_u^2, u \in \mathcal{D}$.
\end{enumerate}
Steps $2$ to $5$ are iterated until a stopping criterion is reached. There is a finite choice for the vector $\ve_j$ and matrix $L_j^m$ respectively constructed in Steps $2$ and $3$. %Once $m$ is fixed, one can build up to $2^m$ different $\ve_j$ and $2^{m(m-1)/2}$ different $L_j^m$. 
The choice of $m$ must take into account this limitation.

 At each step $l$, $B_l$ and ${B'}_l$ are two replicated designs of order $1$ thus enabling the estimation of all first-order indices. Denote by $K$ the step at which the recursive estimation stopped. The total cost of the additive approach to estimate all first-order indices equals $2 \times K \times 2^m$.

The additive approach is attractive due to the slow growing size of the two replicated designs $\mathcal{P}$ and $\mathcal{P}'$. At the opposite of the multiplicative approach, the main drawback is that $\mathcal{P}$ and $\mathcal{P}'$ does not possess the structure of a Sobol' sequence but each block $B_l$ (resp. $B'_l$) composing them does.

%\label{}
% etc, etc

% The Appendices part is started with the command \appendix;
% appendix sections are then done as normal sections
% \appendix

% \section{}
% \label{}

% The Acknowledgements are an un-numbered section
%\section*{Acknowledgements}
% Acknowledgements text here

\begin{thebibliography}{00}
% please try to use the bibitem system -
% the references should be in alphabetical order of authors' names.
% Articles with a single author first, author will 1 co-author next,
% then author with several co-authors;

% \bibitem{label}
% Text of bibliographic item

\bibitem{label}

\end{thebibliography}

\end{document}

### 2016-05-10 crass/crass.tex
changes crass.tex

@@
 \selectlanguage{english}
-\title{On the replication of Sobol' sequences to estimate main effects of model inputs}
+\title{Replicated designs based on Sobol' sequences to estimate main effects of model inputs}
+%\title{On the replication of Sobol' sequences to estimate main effects of model inputs}
 
@@
 The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes \cite{mckay}.
-Here, replicated designs are defined in a wider framework:
+Here, we define replicated designs in a wider framework:
 
@@
 With the construction of only two replicated designs of order $1$, the replication procedure introduced and studied in \cite{mara,tissot} allows to estimate all first-order Sobol' indices.
+
 This procedure has the major advantage of reducing drastically the estimation cost as the number of runs (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension.
-However, if the input space is not properly explored the Sobol' indices estimates may still not be accurate enough.
+However, Sobol' indices estimates may still not be accurate enough if the input space is not properly explored.
 \bigskip
 
-In this note, we propose to construct replicated point sets based on Sobol' sequences to generate two space-filling replicated designs of order $1$.
+In this note, we propose to construct two replicated point sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$.
 These two designs insure that the input space is properly explored and can then be used within the replication procedure to estimate all main-effects of a numerical model.
-We first provide backgrounds on digital sequences, then we present two iterative approaches to construct replicated point sets based on Sobol' sequences.
+We first provide backgrounds on digital sequences, then we present two iterative approaches to construct the two replicated point sets.
 
@@
 The introduction of digital nets and sequences has its origin in numerical integration and uniform distribution.
-Explicit constructions of digital sequences have been developed notably by Sobol' and Niederreiter \cite{niderreiter} into the overarching notion of $(t,m,s)$-nets and $(t,s)$-sequences.
+Explicit constructions of digital nets and sequences have been developed notably by Sobol' and Niederreiter \cite{niderreiter} into the overarching notion of $(t,m,s)$-nets and $(t,s)$-sequences.
 A comprehensive theory of $(t,m,s)$-net and $(t,s)$-sequences was first formulate by Niederreiter.
@@
 These generating matrices are recursively constructed through primitive polynomials and initial directional numbers (see \cite{niederreiter} for further details).
-Denote by $C_1,\dots,C_s$ $s$ generating matrices over $\mathbb{F}_b$.
+We denote by $C_1,\dots,C_s$ the $s$ generating matrices over $\mathbb{F}_b$ of the $s$-dimensional digital sequence.
 For $m>0$ and $j \in \{1,\dots,s\}$, we note $C_j^{m}$ the $m \times m$ upper left block of $C_j$.
@@
 
-For $m' > m$ the matrix $C_j^m$ is embedded in the upper left of matrices $C_j^{m'}$.
+Remark that for any $m' > m$, the matrix $C_j^m$ is embedded in the upper left of matrices $C_j^{m'}$.
 Resulting from this embedding, the construction of a digital sequence can be performed iteratively.
-To link digital sequences to the definition of replicated designs, we introduce the following concept:
+
+The concept of digital sequences can be linked to the definition of replicated designs. To do so, we introduce the following notion:
 \begin{definition}
@@
 \end{pf*}
-For $j \in \{1,\dots,s\}$, using two different generating matrices $C^{m}_j$ and $C'^{m}_j$ in equation (\ref{dig.net.eq.}) produce the same set of $2^m$ values $\{x_{0,j},\dots,x_{2^m-1,j}\}$ but ordered differently.
+
+%\begin{remark}
+%For any $j \in \{1,\dots,s\}$, using two different generating matrices $C^{m}_j$ and $C'^{m}_j$ in equation (\ref{dig.net.eq.}) produce the same set of $2^m$ values $\{x_{0,j},\dots,x_{2^m-1,j}\}$ but ordered differently.
 It is possible to go from an order to the other by using the corresponding full rank upper triangular matrix $U^{m}_j$, such that $C^{m}_j=C'^{m}U^{m}_j$.
 This matrix can be thought as a permutation of the input binary vectors $\vi$.
+%\end{remark}
 
@@
 
-%In section \ref{sobol.seq.cons}, we present two approaches to construct replicated point sets based on Sobol' sequences.
-The multiplicative approach uses two Sobol' sequences that are replicated by construction, while the additive approach takes an initial number of points of two Sobol' sequences and applies digital shifts and scramblings to extend the point set.
-In this case, at step $k$ the size of each replicated Sobol' sequence is $ k \times 2^m$ where $2^m$ is the size of the initial Sobol' sequence.
+We propose here two approaches to construct two replicated point sets $\mathcal{P}$ and $\mathcal{P}'$ based on Sobol' sequences.
+These two constructions are iterative that is the two points sets constructed possess the following structure:
+$$\mathcal{P}= B_1 \cup B_2 \cup B_3 \dots $$
+$$\mathcal{P}'= {B'}_1 \cup {B'}_2 \cup {B'}_3 \dots $$
+where each $B_l$ (resp.
+$B'_l$), $l\geq1$, is a new set of points added at step $l$ to refine $\mathcal{P}$ (resp.
+$\mathcal{P}'$).
+At each step $l$ and for each approach, $\mathcal{P}$ and $\mathcal{P'}$ are two replicated designs of order $1$.
+
+The first approach is called multiplicative approach and simply consists in generating two different Sobol' sequences.
+This approach exploits the result of Lemma \ref{Sobol_replicated}.
+The second approach is called additive approach.
+It takes an initial number of points of a Sobol' sequence and applies to it digital shift and scrambling operations to generate the two replicated points sets.
 
 \subsection{Multiplicative approach}
-Denote by $\mathcal{P}$ and $\mathcal{P}'$ the two designs iteratively refined with new points sets using the multiplicative approach.
-%Based on Lemma \ref{Sobol_replicated}, by taking $\mathcal{P}$ and $\mathcal{P}'$ to be two $s$-dimensional Sobol' sequences we obtain two replicated designs or order $1$ with an innate nested structure.
-The goal of this approach is to generate a $2s$-dimensional Sobol' sequence with good properties to estimate all first order Sobol' indices.
-Design $\mathcal{P}$ is formed with the first $s$ dimensions of the sequence and design $\mathcal{P}'$ with the $s$ remaining ones.
-As shown in Lemma \ref{Sobol_replicated}, for any $m\geq 0$ and $2^m$ points, each dimension of the sequence will have exactly the same values, although probably with different order.
-Thus, designs $\mathcal{P}$ and $\mathcal{P}'$ are nested replicated designs of order $1$ and both are $s$-dimensional Sobol' sequences.
 
-The only constraint we have is that for each $u=1,\dots,s$, to estimate the quantity $\underline{\tau}_u^2$ the $2s$-dimensional Sobol' sequence must ensure that $x_{i,u}=x_{i,u+s}$ for $i\in\mathbb{N}_0$.
+The two replicated points sets $\mathcal{P}$ and $\mathcal{P}'$ constructed with the multiplicative approach are two $s$-dimensional Sobol' sequences constructed with different sets of generating matrices.
+We note $C_1,\dots,C_s$ the generating matrices used to generate design $\mathcal{P}$ and ${C'}_1,\dots,{C'}_s$ those used to generate design $\mathcal{P}'$.
+Our choice of the $2s$ generating matrices $C_1,\dots,C_S,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{kuo2}.
+These two authors proposed a set of generating matrices optimized based on the $t$-value of pairwise projections.
+We select $2s$ generating matrices of this set to generate our two designs $\mathcal{P}$ and $\mathcal{P}'$.
+\bigskip
+
+The iterative construction of designs $\mathcal{P}$ and $\mathcal{P}'$ proceed as follows:
+
+at step $l$, $l \geq 1$, design $\mathcal{P}$ is refined with a set of $2^l$ points $B_l=\{\vx_{2^{l-1}},\dots,\vx_{2^l-1}\}$ obtained through equation (\ref{dig.net.eq.}) with $C_1^l,\dots,C_s^l$.
+Likewise, design $\mathcal{P}'$ is refined with ${B'}_l=\{\vx'_{2^{l-1}},\dots,\vx'_{2^l-1}\}$ obtained through equation (\ref{dig.net.eq.}) with ${C'}_1^l,\dots,{C'}_s^l$.
+
+As a direct consequence of Lemma \ref{Sobol_replicated}, at each step $l$ the designs $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $1$.
+Furthermore, they both inherit the space-filling properties of $(t,l,s)$-nets.
+
+%The only constraint we have is that for each $u=1,\dots,s$, to estimate the quantity $\underline{\tau}_u^2$ the $2s$-dimensional Sobol' sequence must ensure that $x_{i,u}=x_{i,u+s}$ for $i\in\mathbb{N}_0$.
 Therefore, we will need $s$ different $2s$-dimensional sequences.
@@
 
-Given the generators $C_1,\dots,C_s,C'_1,\dots,C'_s$, we define the $U_u$ matrices such that $C_u=C'_uU_u$.
+%Given the generators $C_1,\dots,C_s,C'_1,\dots,C'_s$, we define the $U_u$ matrices such that $C_u=C'_uU_u$.
 Then, each sequence generated by $C_1,\dots,C_s,C'_1U_u,\dots,C'_sU_u$ will satisfy $x_{i,u}=x_{i,u+s}$, for all $i\in\mathbb{N}_0$.
 
-\begin{proposition}
-For any $m\geq 0$, and $t_m$ depending on $m$, if the Sobol' $(t_m,m,s)$-nets are generated by $C_1,\dots,C_s$, then $C_1U,\dots,C_sU$, where $U$ is an upper triangular matrix, generate exactly the same $(t_m,m,s)$-nets.
-\end{proposition}
-\begin{pf*}{Proof.}
-For any $m$ and $2^{m-1}\leq i < 2^m$, the image by $U$, $\vj=U\vi$, will also satisfy $2^{m-1}\leq j < 2^m$.
+%\begin{proposition}
+%For any $m\geq 0$, and $t_m$ depending on $m$, if the Sobol' $(t_m,m,s)$-nets are generated by $C_1,\dots,C_s$, then $C_1U,\dots,C_sU$, where $U$ is an upper triangular matrix, generate exactly the same $(t_m,m,s)$-nets.
+%\end{proposition}
+%\begin{pf*}{Proof.}
+%For any $m$ and $2^{m-1}\leq i < 2^m$, the image by $U$, $\vj=U\vi$, will also satisfy $2^{m-1}\leq j < 2^m$.
 The reason is because $U$ is upper triangular, therefore $j_{m-1}=i_{m-1}$.
 Thus, by induction on $m$, the $(t_m,m,s)$-nets generated after applying the permutation $U$ contain exactly the same points.
-\end{pf*}
+%\end{pf*}
 
-This means that the use of these matrices $U_u$ do not affect the quality of our initial sequence.
+%This means that the use of these matrices $U_u$ do not affect the quality of our initial sequence.
 
-Sobol' generating matrices $C$ are constructed through primitive polynomials and initial directional numbers.
-How to choose them is deeply discussed in \cite{kuo}.
-The $t$-values of pairwise projections are already optimized in \cite{kuo2}.
-Thus, we will consider the $2s$-dimensional Sobol' sequence described by them to construct the other $s$ $2s$-dimensional sequences.
-
-We still can optimize the quality of the $s$ sequences together by taking a different order of the generating matrices of the initial sequence.
+%We still can optimize the quality of the $s$ sequences together by taking a different order of the generating matrices of the initial sequence.
 Given the generators $C_1,\dots,C_{2s}$, for all $s$ reordered sequences, the projections $C_i-C_j$ appear $s$ times when $0<i<j\leq s$, $s-1$ times when $0<i\leq s<j\leq 2s$, and $s-2$ times if $s<i<j\leq 2s$.
@@
 
-In addition to it, one can still randomize the initial Sobol' sequence using Owen's scrambling \cite{owen.scrambl}.
-The only requirement to keep the replication property is to apply the same scrambling to dimensions that differ by $s$ positions, i.e., same scrambling to $C_j$ and $C_{j+s}$ for all $j=1,\dots,s$.
-
 \subsection{Additive Approach}
 
-Denote by $\mathcal{P}$ and $\mathcal{P}'$ the two replicated designs iteratively refined with new points sets using the additive approach. These two designs possess a block structure:
-$$\mathcal{P}= B_0 \cup B_1 \cup B_2 \dots $$
-$$\mathcal{P}'= {B'}_0 \cup {B'}_1 \cup {B'}_2 \dots $$
-We detail below the steps of the construction of these two designs.
-\begin{enumerate}
-\item[Step 1.] We start by fixing $m$ and choosing a set $C_1^{m},\dots,C_s^{m}$ of generating matrices to construct an initial Sobol' sequence $\{\vx_i\}_{i=0}^{2^m-1}$ of $2^m$ points. \\
+The two replicated points sets $\mathcal{P}$ and $\mathcal{P}'$ constructed with the additive approach are iteratively refined with points sets $B_l$ and ${B'}_l$ that each possesses the structure of a $(t,m,s)$-net.
 
-\item[Step 2.] At step $l$ of the recursive estimation, $l \geq 0$, a new points set $B_l=\{\vx_i^{(l)}\}_{i=0}^{2^m-1}$ of $2^m$ points is added to $\mathcal{P}$.
-$B_l$ is obtained by applying a digital shift to the initial Sobol' sequence.
-The digital shift operation is applied as follows:
+First, an initial set of $2^m$ points $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^m-1}$ of a $s$-dimensional Sobol' sequence is generated by fixing $m >0$ and selecting $s$ generating matrices $C_1,\dots,C_s$ from the set obtained in \cite{kuo2}.
+Then, $B_l$ and ${B'}_l$ are obtained from $B_0$ by carrying out digital shift and scrambling operations.
+These operations guarantee that both $B_l$ and ${B'}_l$ inherit the $(t,m,s)$-net structure of the starting set $B_0$.
+\bigskip
+
+We detail below the construction of $B_l$ and ${B'}_l$:
+
+At step $l$, $l \geq 1$, design $\mathcal{P}$ is refined with a set of $2^m$ points $B_l=\{\vx_i^{(l)}\}_{i=0}^{2^m-1}$. $B_l$ is a digitally shifted version of $B_0$:
 
@@
 \label{dig.shift}
-(x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal = C_j^m \vi+\ve_j,\qquad j= 1,\dots,s\, ,
+(x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal = (x_{i,j,1}^{(0)},\dots,x_{i,j,m}^{(0)})^\intercal+\ve_j,\qquad j= 1,\dots,s\, ,
 \end{equation}
-where $ x_{i,j}^{(l)}=\sum_{k = 1}^mx_{i,j,k}^{(l)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{m-1}})^\intercal \in ker(C_j^m)$ the kernel of $C_j^m$.\\
+where $ x_{i,j}^{(l)}=\sum_{k = 1}^mx_{i,j,k}^{(l)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{m-1}})^\intercal \in ker(C_j^m)$ the kernel of $C_j^m$.
+\bigskip
 
-\item[Step 3.] Then, the points set ${B'}_l=\{{\vx'}_i^{(l)}\}_{i=0}^{2^m-1}$ is obtained from $B_l$ by applying Tezuka's i-binomial scrambling \cite{tezuka}. This operation consists in the following:
+Then, design $\mathcal{P}'$ is refined with a set of $2^m$ points ${B'}_l=\{{\vx'}_i^{(l)}\}_{i=0}^{2^m-1}$.
+${B'}_l$ is obtained from $B_l$ by applying Tezuka's i-binomial scrambling \cite{tezuka}.
+This scrambling operation writes as follows:
 
@@
 \end{equation}
-where $ {x'}_{i,j}^{(l)}=\sum_{k = 1}^m{x'}_{i,j,k}^{(l)}2^{-k}$ and $L_j^m$ is an invertible lower triangular matrix of size $m \times m$ over the Galois field $\mathbb{F}_2$.\\
+where $ {x'}_{i,j}^{(l)}=\sum_{k = 1}^m{x'}_{i,j,k}^{(l)}2^{-k}$ and $L_j^m$ is a full rank lower triangular matrix of size $m \times m$ over the Galois field $\mathbb{F}_2$.
+\bigskip
 
-\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomized using the same Owen's scrambling column-wise.
+%\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomized using the same Owen's scrambling column-wise.
 
-\item[Step 5.] $B_l$ and ${B'}_l$ are used to estimate all first-order indices $\underline{\tau}_u^2, u \in \mathcal{D}$.
-\end{enumerate}
-Steps $2$ to $5$ are iterated until a stopping criterion is reached.
-There is a finite choice for the vector $\ve_j$ and matrix $L_j^m$ respectively constructed in Steps $2$ and $3$.
-%Once $m$ is fixed, one can build up to $2^m$ different $\ve_j$ and $2^{m(m-1)/2}$ different $L_j^m$.
-The choice of $m$ must take into account this limitation.
+%\item[Step 5.] $B_l$ and ${B'}_l$ are used to estimate all first-order indices $\underline{\tau}_u^2, u \in \mathcal{D}$.
+%There is a finite choice for the vector $\ve_j$ and matrix $L_j^m$ respectively constructed in Steps $2$ and $3$. The choice of $m$ must take into account this limitation.
 
- At each step $l$, $B_l$ and ${B'}_l$ are two replicated designs of order $1$ thus enabling the estimation of all first-order indices.
-Denote by $K$ the step at which the recursive estimation stopped.
-The total cost of the additive approach to estimate all first-order indices equals $2 \times K \times 2^m$.
+\begin{lemma}
+At each step $l$, $l\geq1$, the digital shift and scrambling operations carried out in equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) ensure that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $1$.
+\end{lemma}
 
-The additive approach is attractive due to the slow growing size of the two replicated designs $\mathcal{P}$ and $\mathcal{P}'$.
-At the opposite of the multiplicative approach, the main drawback is that $\mathcal{P}$ and $\mathcal{P}'$ does not possess the structure of a Sobol' sequence but each block $B_l$ (resp.
-$B'_l$) composing them does.
+\begin{pf*}{Proof.}
+This is a direct consequence of the following result: at each step $l$, $B_l$ and ${B'}_l$ are two replicated designs of order $1$.
+Indeed, since digital shift and i-binomial scrambling operations are bijections from $\mathbb{F}_2^m$ to $\mathbb{F}_2^m$, each dimension of $B_l$ and ${B'}_l$ contains the same set of $2^m$ values.
+\end{pf*}
+
+In the multiplicative approach, at each step $l$, $l \geq 1$ the sizes of designs $\mathcal{P}$ and $\mathcal{P}'$ are multiplied by $2$.
+This relatively fast growing size may be inadequate for some applications.
+The additive approach presented here is attractive due to the slow growing size of the two replicated designs $\mathcal{P}$ and $\mathcal{P}'$.
+At each step $l$, only $2^m$ points are added to both designs.
+However, the main drawback is that $\mathcal{P}$ and $\mathcal{P}'$ each as a whole does not possess the structure of a Sobol' sequence anymore.
+
+%In addition to it, one can still randomize the initial Sobol' sequence using Owen's scrambling \cite{owen.scrambl}.
+The only requirement to keep the replication property is to apply the same scrambling to dimensions that differ by $s$ positions, i.e., same scrambling to $C_j$ and $C_{j+s}$ for all $j=1,\dots,s$.
 

### 2016-05-10 article.tex
Minor changes

@@
 Cost pas small:\[\alpha n d_s +n+(d-d_s)n\]
-Cost small - cost pas small: \[n\sum_{i=1}^{s}(2-\alpha_i+1)\] $s$ number of small indices, $alhpa_i$ proportion of how many more points if not pas small
+Cost small - cost pas small: \[n\sum_{i=1}^{s}(2-\alpha_i+1)\] $s$ number of small indices, $\alhpa_i$ proportion of how many more points if not pas small
 
@@
 \section{Reliable Error Estimation for Cubatures}
+
+We assume that we have an algorithm $\widehat{I}(f;\varepsilon)$ such that $\abs{I(f)-\widehat{I}(f;\varepsilon)}\leq \varepsilon$.
+For instance, the guaranteed quasi-Monte Carlo cubatures described in \cite{-} and \cite{-}.
+Therefore, we will always assume that the true integral $I(f)$ lies in $[\widehat{I}(f;\varepsilon)-\varepsilon,\widehat{I}(f;\varepsilon)+\varepsilon]$.
+
+Sobol' indices can be seen as operators over functions that can be simplified as functions whose entries are integrals.
+
+The case of $correlation 2$
+Je viens de comprendre, prendre S(LB,UB) comme le minimum (LowerBound, UpperBound) et S(UB,LB) comme le maximum est trop simple. Il faut construire le S_max et S_min en fonction du cas.
+Pour nous, a - b*c + c^2 est un paraboloïde hyperbolique.
+La droite avec plus de décroissement est 0+lambda(2,1) [prends la dérivée par rapport à c et l'on a c=b/2] et la perpendiculaire, celle de plus accroissement (symmetrie).
+Sur notre région carré, le point de max valeur de S sera le point le plus eloignée de la droite 0+lambda(2,1), et le minimum, sera sur cette droite le plus eloignée de b = 0 (si l'on substitue c=b/2, on obtient que restreint à cette droite, la fonction est a-b^2/4).
+
+- Max at = hat{a} + e_a  ,  hat{b} - sign(hat{c}-hat{b}/2) e_b  ,  hat{c} + sign(hat{c}-hat{b}/2) e_c
+- Min at = hat{a} - e_a  ,  hat{b} + sign(hat{b}) e_b  ,  (hat{b} + sign(hat{b}) e_b)/2
+
 \subsection{Definition of $\widehat{S}$ (fix it with max and min)}

### 2016-05-11 crass/crass.tex
Minor changes
Changes in CRASS section 2

@@
 
-The introduction of digital nets and sequences has its origin in numerical integration and uniform distribution.
-Explicit constructions of digital nets and sequences have been developed notably by Sobol' and Niederreiter \cite{niderreiter} into the overarching notion of $(t,m,s)$-nets and $(t,s)$-sequences.
-A comprehensive theory of $(t,m,s)$-net and $(t,s)$-sequences was first formulate by Niederreiter.
+Digital nets and sequences were first introduced by Niederreiter \cite{SIAM92book} in the numerical integration framework to define good uniformly distributed points in $\cube$.
+They can also appear in the literature as digital $(t,m,s)$-nets and digital $(t,s)$-sequences, or simply $(t,m,s)$-nets and $(t,s)$-sequences.
+Sobol' \cite{Sobol} and Niederreiter-Xing sequences are two examples whose explicit constructions are detailed in \cite{Niederreiter, Sobol, DickPhilischammer,DickKritzer,KuoJoe}.
 
-$(t,m,s)$-nets are defined as point sets in $\cube$ whose quality is measured by the parameter $t$, called $t$-value. They are defined as follows:
+The quality of any $(t,m,s)$-net or $(t,s)$-sequence is measured by $t$, called the $t$-value. The $t$-value is introduced in the $(t,m,s)$-net definition as follows:
+
 \begin{definition}%[$(t,m,s)-net$]
@@
 
-A $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points.
+Thus, a $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points of $\mathcal{P}$, namely $b^{t-m}|\mathcal{P}|$ points.
 The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest volume possible, $b^{-m}$, contains exactly one point.
-%Note that if $t'>t$, $(t,m,s)$-nets are always $(t',m,s)$-nets.
 
-$(t,s)$-sequences are the infinite analogues of $(t,m,s)$-nets. They are defined as follows:
+By increasing $m$, we increase the number of points of the $(t,m,s)$-net. If one considers the limit for $m\rightarrow\infty$, $(t,s)$-sequences are defined as:
 \begin{definition}%[$(t,s)$-sequence]
@@
 
-All $(t,m,s)$-nets and $(t,s)$-sequences relevant for applications are based on a digital construction scheme over a finite field $\mathbb{F}_b$ with $b$ a prime power number.
+All $(t,m,s)$-nets and $(t,s)$-sequences relevant for applications are based on a digital construction scheme over a finite field $\mathbb{F}_b:=\{0,\dots,b-1\}$ with $b$ a prime power number.
 Digital nets and sequences referred to these structures.

### 2016-05-11 crass/crass.tex
changes crass.tex

@@
 \selectlanguage{english}
-\title{Replicated designs based on Sobol' sequences to estimate main effects of model inputs}
+\title{Construction of replicated designs based on Sobol' sequences}
+%\title{Replicated designs based on Sobol' sequences to estimate main effects of model inputs}
 %\title{On the replication of Sobol' sequences to estimate main effects of model inputs}
@@
 \address[authorlabel1]{Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 655 avenue de l'Europe, 38330 Montbonnot}
-\address[authorlabel2]{TO FILL}
+\address[authorlabel2]{Illinois Institute of Technology}
 \address[authorlabel3]{Univ. Grenoble Alpes, Jean Kunzmann Laboratory, F-38000 Grenoble, France \\
@@
 % Text of abstract in English
-Your abstract in English here.
-{\it To cite this article: A.
-Name1, A. Name2, C. R. Acad. Sci. Paris, Ser. I 340 (2005).}
+In the perspective of estimating main effects of model inputs, two approaches are studied to construct replicated designs based on Sobol' sequences.
+{\it To cite this article: L.
+Gilquin, L. A. J. Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci. Paris, Ser. I 340 (2005).}
 
@@
 \noindent{\bf R\'esum\'e} \vskip 0.5\baselineskip \noindent
-{\bf Here is the title in French. }
-Your resume in French here.
-{\it Pour citer cet article~: A. Name1, A. Name2, C. R. Acad. Sci.
+{ \bf Construction de plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.}
+%{\bf Plans r\'epliqu\'es \`a base de s\'equences de Sobol' pour estimer les effets principaux des param\`etres d'un mod\`ele. }
+Dans le contexte d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches pour construire des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.
+{\it Pour citer cet article~: L. Gilquin, L. A. J. Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
 Paris, Ser. I 340 (2005).}
@@
 Global sensitivity analysis methods are useful tools to identify the parameters having the most influence on the output.
-A well known approach is the variance based method introduced by Sobol' \cite{sobol'}.
-This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model's input.
+A well known approach is the variance based method introduced by Sobol' \cite{Sobol2}.
+This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model input.
 In particular, one can distinguish first-order indices that estimate the main effect of each input.
@@
 %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.
- An elegant solution to reduce this cost relies on the construction of particular designs of experiments called replicated designs.
-The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes \cite{mckay}.
+ An elegant solution to reduce this cost relies on the construction of particular design of experiments called replicated designs.
+The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes \cite{Mckay}.
 Here, we define replicated designs in a wider framework:
@@
 \label{rep.designs}
-Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$.
-Set $\mathcal{D}=\{1,\dots,s\}$.
+Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$ and $\mathcal{D}=\{1,\dots,s\}$.
 Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets,
@@
 
-With the construction of only two replicated designs of order $1$, the replication procedure introduced and studied in \cite{mara,tissot} allows to estimate all first-order Sobol' indices.
-
+With the construction of only two replicated designs of order $1$, the replication procedure introduced and studied in \cite{Mara,Tissot} allows to estimate all first-order Sobol' indices.
 This procedure has the major advantage of reducing drastically the estimation cost as the number of runs (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension.
@@
 
-In this note, we propose to construct two replicated point sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$.
+In this note, we propose to construct two replicated points sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$.
 These two designs insure that the input space is properly explored and can then be used within the replication procedure to estimate all main-effects of a numerical model.
@@
 
-Digital nets and sequences were first introduced by Niederreiter \cite{SIAM92book} in the numerical integration framework to define good uniformly distributed points in $\cube$.
+Digital nets and sequences were first introduced by Niederreiter \cite{Niederreiter} in the numerical integration framework to define good uniformly distributed points in $\cube$.
 They can also appear in the literature as digital $(t,m,s)$-nets and digital $(t,s)$-sequences, or simply $(t,m,s)$-nets and $(t,s)$-sequences.
-Sobol' \cite{Sobol} and Niederreiter-Xing sequences are two examples whose explicit constructions are detailed in \cite{Niederreiter, Sobol, DickPhilischammer,DickKritzer,KuoJoe}.
+Sobol' and Niederreiter-Xing sequences are two examples whose explicit constructions are detailed in \cite{Niederreiter} and \cite{Sobol1}.
+%\cite{Niederreiter, Sobol, DickPhilischammer,DickKritzer,KuoJoe}.
 
@@
 Digital nets and sequences referred to these structures.
-\bigskip
 
 The construction scheme of a $s$-dimensional digital sequence requires the knowledge of the base $b$ and a set of $s$ full rank upper triangular matrices of infinite size called generating matrices.
-These generating matrices are recursively constructed through primitive polynomials and initial directional numbers (see \cite{niederreiter} for further details).
-We denote by $C_1,\dots,C_s$ the $s$ generating matrices over $\mathbb{F}_b$ of the $s$-dimensional digital sequence.
+These generating matrices are recursively constructed through primitive polynomials and initial directional numbers (see \cite{Niederreiter} for further details).
+We detail below the construction scheme.
+
+Denote by $C_1,\dots,C_s$ the $s$ generating matrices over $\mathbb{F}_b$ of a $s$-dimensional digital sequence.
 For $m>0$ and $j \in \{1,\dots,s\}$, we note $C_j^{m}$ the $m \times m$ upper left block of $C_j$.
-The first $b^m$ points $\{\vx_0,\dots,\vx_{b^m-1}\}$ of the digital sequence are constructed as follows:\\
+The first $b^m$ points $\{\vx_0,\dots,\vx_{b^m-1}\}$ of the digital sequence are constructed as follows:
 
@@
 
-Remark that for any $m' > m$, the matrix $C_j^m$ is embedded in the upper left of matrices $C_j^{m'}$.
-Resulting from this embedding, the construction of a digital sequence can be performed iteratively.
+Remark that for any $m' > m$, the matrix $C_j^m$ is embedded in the upper left of matrix $C_j^{m'}$.
+Resulting from this embedding, the next $2^m$ points of the digital sequence are constructed by increasing $m$ by one in equation (\ref{dig.net.eq.}).
+The process is iterated as many times as needed.
 
@@
 Sobol' sequences are digital sequences constructed in base $2$.
-These sequences are attractive for their easy implementation and optimized properties \cite{kuo2}.
+These sequences are attractive for their easy implementation and optimized properties \cite{Kuo}.
 Sobol' sequences are particularly interesting for having full rank upper triangular generating matrices over $\mathbb{F}_2$.
@@
 \end{lemma}
-\begin{pf*}{\textit{Proof}.}
-Consider any two s-dimensional Sobol' sequences generated respectively by the matrices $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$.
+\begin{pf*}{Proof.}
+Consider any two s-dimensional Sobol' sequences generated respectively by the generating matrices $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$.
 Since these matrices are upper triangular, to compute the first $2^m$ points one only needs the knowledge of the $m\times m$ upper left blocks $C_j^m$ and ${C'}_j^m$, $j \in \{1,\dots,s\}$.
@@
 $$\mathcal{P}'= {B'}_1 \cup {B'}_2 \cup {B'}_3 \dots $$
-where each $B_l$ (resp.
+where $B_l$ (resp.
 $B'_l$), $l\geq1$, is a new set of points added at step $l$ to refine $\mathcal{P}$ (resp.
 $\mathcal{P}'$).
-At each step $l$ and for each approach, $\mathcal{P}$ and $\mathcal{P'}$ are two replicated designs of order $1$.
+For each approach and at each step, $\mathcal{P}$ and $\mathcal{P'}$ are two replicated designs of order $1$.
 
@@
 We note $C_1,\dots,C_s$ the generating matrices used to generate design $\mathcal{P}$ and ${C'}_1,\dots,{C'}_s$ those used to generate design $\mathcal{P}'$.
-Our choice of the $2s$ generating matrices $C_1,\dots,C_S,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{kuo2}.
-These two authors proposed a set of generating matrices optimized based on the $t$-value of pairwise projections.
-We select $2s$ generating matrices of this set to generate our two designs $\mathcal{P}$ and $\mathcal{P}'$.
+Our choice of the $2s$ generating matrices $C_1,\dots,C_S,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}.
+These two authors proposed a set of generating matrices optimized based on the $t$-value of pairwise projections of the corresponding digital sequence.
+Here, we select $2s$ generating matrices from this set to generate our two designs $\mathcal{P}$ and $\mathcal{P}'$.
 \bigskip
@@
 
-The two replicated points sets $\mathcal{P}$ and $\mathcal{P}'$ constructed with the additive approach are iteratively refined with points sets $B_l$ and ${B'}_l$ that each possesses the structure of a $(t,m,s)$-net.
-
-First, an initial set of $2^m$ points $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^m-1}$ of a $s$-dimensional Sobol' sequence is generated by fixing $m >0$ and selecting $s$ generating matrices $C_1,\dots,C_s$ from the set obtained in \cite{kuo2}.
-Then, $B_l$ and ${B'}_l$ are obtained from $B_0$ by carrying out digital shift and scrambling operations.
-These operations guarantee that both $B_l$ and ${B'}_l$ inherit the $(t,m,s)$-net structure of the starting set $B_0$.
+With the multiplicative approach, the sizes of designs $\mathcal{P}$ and $\mathcal{P}'$ are multiplied by $2$ at each step.
+This growth rate may be inadequate for some applications.
+The additive approach presented here is attractive due to the slow growing size of the two replicated designs $\mathcal{P}$ and $\mathcal{P}'$ constructed.
+At each step, only $2^m$ points are added to both designs.
+However, the main drawback is that $\mathcal{P}$ and $\mathcal{P}'$ each as a whole does not possess the structure of a Sobol' sequence anymore.
 \bigskip
 
-We detail below the construction of $B_l$ and ${B'}_l$:
+The two replicated points sets $\mathcal{P}$ and $\mathcal{P}'$ constructed with the additive approach are iteratively refined with new points sets $B_l$ and ${B'}_l$ that each possesses the structure of a $(t,m,s)$-net.
 
-At step $l$, $l \geq 1$, design $\mathcal{P}$ is refined with a set of $2^m$ points $B_l=\{\vx_i^{(l)}\}_{i=0}^{2^m-1}$. $B_l$ is a digitally shifted version of $B_0$:
+First, an initial set $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^m-1}$ of $2^m$ points of a $s$-dimensional Sobol' sequence is generated by fixing $m >0$ and choosing $s$ generating matrices $C_1,\dots,C_s$.
+These matrices are selected from the set obtained in \cite{Kuo}.
+Then, at step $l$, $B_l$ and ${B'}_l$ are obtained from $B_0$ by carrying out digital shift and scrambling operations.
+These operations guarantee that both $B_l$ and ${B'}_l$ inherit the $(t,m,s)$-net structure of the initial set $B_0$.
+We detail below the construction of $B_l$ and ${B'}_l$.
+\bigskip
+
+At step $l$, $l \geq 1$, $B_l=\{\vx_i^{(l)}\}_{i=0}^{2^m-1}$ is generated by applying a digital shift to $B_0$:
 
@@
 
-Then, design $\mathcal{P}'$ is refined with a set of $2^m$ points ${B'}_l=\{{\vx'}_i^{(l)}\}_{i=0}^{2^m-1}$.
-${B'}_l$ is obtained from $B_l$ by applying Tezuka's i-binomial scrambling \cite{tezuka}.
-This scrambling operation writes as follows:
+Then, ${B'}_l=\{{\vx'}_i^{(l)}\}_{i=0}^{2^m-1}$ is obtained from $B_l$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows:
 
@@
 This is a direct consequence of the following result: at each step $l$, $B_l$ and ${B'}_l$ are two replicated designs of order $1$.
-Indeed, since digital shift and i-binomial scrambling operations are bijections from $\mathbb{F}_2^m$ to $\mathbb{F}_2^m$, each dimension of $B_l$ and ${B'}_l$ contains the same set of $2^m$ values.
+Indeed, since digital shift and i-binomial scrambling operations are bijections from ${\mathbb{F}_2}^m$ to ${\mathbb{F}_2}^m$, each dimension of $B_l$ and ${B'}_l$ contains the same set of $2^m$ values.
 \end{pf*}
-
-In the multiplicative approach, at each step $l$, $l \geq 1$ the sizes of designs $\mathcal{P}$ and $\mathcal{P}'$ are multiplied by $2$.
-This relatively fast growing size may be inadequate for some applications.
-The additive approach presented here is attractive due to the slow growing size of the two replicated designs $\mathcal{P}$ and $\mathcal{P}'$.
-At each step $l$, only $2^m$ points are added to both designs.
-However, the main drawback is that $\mathcal{P}$ and $\mathcal{P}'$ each as a whole does not possess the structure of a Sobol' sequence anymore.
 
@@
 % Text of bibliographic item
+\bibitem{Kuo} S. Joe, F. Y. Kuo, Constructing Sobol Sequences with Better Two-Dimensional Projections, \emph{SIAM J. Sci. Comput.} 30(8), 2008, pp. 2635--2654.
 
-\bibitem{label}
+\bibitem{Mara} T.
+A.
+Mara, O.
+R.
+Joseph, Comparison of some efficient methods to evaluate the main effect of computer model factors, \emph{Journal of Statistical Computation and Simulation} 78(2), 2008, pp.
+167--178.
+
+\bibitem{Mckay} M.
+D.
+McKay, W.
+J.
+Conover, R.
+J.
+Beckman, A comparison of three methods for selecting values of input variables in the analysis of output from a computer code, \emph{Technometrics} 21, 1979, pp.
+239--245.
+
+\bibitem{Niederreiter} 	H. Niederreiter, Random Number Generation and Quasi-Monte Carlo Methods, \emph{CBMS-NSF Regional Conference Series in Applied Math.} 63, SIAM,Philadelphia, PA, 1992.
+
+\bibitem{Saltelli} A. Saltelli, Making best use of model evaluations to compute sensitivity indices, \emph{Computer Physics Communications} 145(2), 2002, pp. 280?-297.
+
+\bibitem{Sobol1} I.
+M.
+Sobol', On the distribution of points in a cube and the approximate evaluation of integrals, \emph{USSR Computational Mathematics and Mathematical Physics} 7(4), 1967, pp.
+86--112.
+
+\bibitem{Sobol2} I. M. Sobol', Sensitivity indices for nonlinear mathematical models, \emph{Mathematical Modeling and Computational Experiment} 1, 1993, pp. 407--414.
+
+\bibitem{Tezuka} S. Tezuka, H. Faure, I-binomial scrambling of digital nets and sequences, \emph{J. Complexity} 19(6),2003, pp. 744--757.
+
+\bibitem{Tissot} J.
+Y.
+Tissot, C.
+Prieur, A randomized orthogonal array-based procedure for the estimation of first- and second-order Sobol' indices, \emph{J.
+Statist.
+Comput.
+Simulation} 85, 2014, pp.
+1358--1381.
 

### 2016-05-12 crass/crass.tex
Most of section 2 reviewed

@@
 {\it To cite this article: L.
-Gilquin, L. A. J. Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci. Paris, Ser. I 340 (2005).}
+Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci. Paris, Ser. I 340 (2005).}
 
@@
 They can also appear in the literature as digital $(t,m,s)$-nets and digital $(t,s)$-sequences, or simply $(t,m,s)$-nets and $(t,s)$-sequences.
-Sobol' and Niederreiter-Xing sequences are two examples whose explicit constructions are detailed in \cite{Niederreiter} and \cite{Sobol1}.
-%\cite{Niederreiter, Sobol, DickPhilischammer,DickKritzer,KuoJoe}.
+Sobol' and Niederreiter-Xing sequences are two examples of digital sequences detailed in \cite{Sobol1} and \cite{NiederreiterXing}.
 
@@
 
-By increasing $m$, we increase the number of points of the $(t,m,s)$-net. If one considers the limit for $m\rightarrow\infty$, $(t,s)$-sequences are defined as:
+By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limit case where $m\rightarrow\infty$, we can define $(t,s)$-sequences as:
 \begin{definition}%[$(t,s)$-sequence]
@@
 \end{definition}
-\bigskip
 
-All $(t,m,s)$-nets and $(t,s)$-sequences relevant for applications are based on a digital construction scheme over a finite field $\mathbb{F}_b:=\{0,\dots,b-1\}$ with $b$ a prime power number.
-Digital nets and sequences referred to these structures.
+Replicated design properties can apply to digital sequences. Therefore, we introduce the definition,
+\begin{definition}
+Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are said \emph{digitally replicated} of order $r$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $r$.
+\end{definition}
 
-The construction scheme of a $s$-dimensional digital sequence requires the knowledge of the base $b$ and a set of $s$ full rank upper triangular matrices of infinite size called generating matrices.
-These generating matrices are recursively constructed through primitive polynomials and initial directional numbers (see \cite{Niederreiter} for further details).
-We detail below the construction scheme.
+\subsection{Sobol' sequences}
 
-Denote by $C_1,\dots,C_s$ the $s$ generating matrices over $\mathbb{F}_b$ of a $s$-dimensional digital sequence.
-For $m>0$ and $j \in \{1,\dots,s\}$, we note $C_j^{m}$ the $m \times m$ upper left block of $C_j$.
-The first $b^m$ points $\{\vx_0,\dots,\vx_{b^m-1}\}$ of the digital sequence are constructed as follows:
+$s$-dimensional Sobol' sequences are designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices defined over $\mathbb{F}_2:=\{0,1\}$.
+In \cite{Kuo}, Kuo and Joe suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.
 
-For each $i=0,\dots,b^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise by:
+We denote these matrices by $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$.
+Although $C_1,\dots,C_s$ have infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points.
+
+For each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise by:
 \begin{equation}
@@
 \end{equation}
-where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ is the b-ary decomposition of $i$.
+where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}2^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ the binary decomposition of $i$. Below we show how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$
+
+\begin{equation*}
+\begin{pmatrix}
+x_{11,1,1} \\
+x_{11,1,2} \\
+x_{11,1,3} \\
+x_{11,1,4}
+\end{pmatrix} =
+\begin{pmatrix}
+1 \\
+1 \\
+0 \\
+1
+\end{pmatrix} = 
+\overbrace{
+\begin{pmatrix}
+1 & 0 & 0 & 0 \\
+0 & 1 & 0 & 0 \\
+0 & 0 & 1 & 0 \\
+0 & 0 & 0 & 1
+\end{pmatrix}}^{C_1^4}
+\overbrace{
+\begin{pmatrix}
+1 \\
+1 \\
+0 \\
+1
+\end{pmatrix}}^{\bvec{11}},\qquad
+\begin{pmatrix}
+x_{9,2,1} \\
+x_{9,2,2} \\
+x_{9,2,3} \\
+x_{9,2,4}
+\end{pmatrix} =
+\begin{pmatrix}
+0 \\
+1 \\
+1 \\
+1
+\end{pmatrix} = 
+\overbrace{\begin{pmatrix}
+1 & 1 & 1 & 1 \\
+0 & 1 & 0 & 1 \\
+0 & 0 & 1 & 1 \\
+0 & 0 & 0 & 1
+\end{pmatrix}}^{C_2^4}
+\overbrace{\begin{pmatrix}
+1 \\
+0 \\
+0 \\
+1
+\end{pmatrix}}^{\bvec{9}}
+\end{equation*}
 \bigskip
@@
 
-The concept of digital sequences can be linked to the definition of replicated designs. To do so, we introduce the following notion:
-\begin{definition}
-Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are said \emph{digitally replicated} of order $r$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $r$.
-\end{definition}
-
-\subsection{Sobol' sequences}
-
-Sobol' sequences are digital sequences constructed in base $2$.
-These sequences are attractive for their easy implementation and optimized properties \cite{Kuo}.
-Sobol' sequences are particularly interesting for having full rank upper triangular generating matrices over $\mathbb{F}_2$.
-This property leads to the following lemma:
 \begin{lemma}\label{Sobol_replicated}
@@
 \begin{pf*}{Proof.}
-Consider any two s-dimensional Sobol' sequences generated respectively by the generating matrices $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$.
+Consider any two $s$-dimensional Sobol' sequences generated by the generating matrices $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$ respectively.
 Since these matrices are upper triangular, to compute the first $2^m$ points one only needs the knowledge of the $m\times m$ upper left blocks $C_j^m$ and ${C'}_j^m$, $j \in \{1,\dots,s\}$.
-Because any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the products $C^{m}_j\vi$ and ${C'}^{m}_j\vi$ are one-to one and onto, for all $i=0,\dots,2^m-1$.
+Because any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the operations $C^{m}_j\vi$ and ${C'}^{m}_j\vi$ are one-to one and onto, for all $i=0,\dots,2^m-1$.
 Therefore, they generate the same point sets.
@@
 \section{Iterative construction of replicated point sets}
-
+SCRAMBLING
 We propose here two approaches to construct two replicated point sets $\mathcal{P}$ and $\mathcal{P}'$ based on Sobol' sequences.
@@
 
+\bibitem{NiederreiterXing} H.
+Niederreiter, C.
+Xing, Low-Discrepancy Sequences and Global Function Fields with Many Rational Places, \emph{Finite Fields and Their Applications} 2(3), 1996, pp.
+241--273.
+
 \end{thebibliography}

### 2016-05-12 crass/crass.tex
changes crass.tex

@@
 
-\address[authorlabel1]{Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 655 avenue de l'Europe, 38330 Montbonnot}
-\address[authorlabel2]{Illinois Institute of Technology}
+\address[authorlabel1]{Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 38330 Montbonnot, France}
+\address[authorlabel2]{Illinois Institute of Technology, 3300 S Federal St, Chicago, IL 60616, United States}
 \address[authorlabel3]{Univ. Grenoble Alpes, Jean Kunzmann Laboratory, F-38000 Grenoble, France \\
@@
 % Text of abstract in English
-In the perspective of estimating main effects of model inputs, two approaches are studied to construct replicated designs based on Sobol' sequences.
+In the perspective of estimating main effects of model inputs, two iterative approaches are studied to construct replicated designs based on Sobol' sequences.
 {\it To cite this article: L.
@@
 %{\bf Plans r\'epliqu\'es \`a base de s\'equences de Sobol' pour estimer les effets principaux des param\`etres d'un mod\`ele. }
-Dans le contexte d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches pour construire des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.
+Dans le contexte d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches it\'eratives pour construire des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.
 {\it Pour citer cet article~: L. Gilquin, L. A. J. Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
@@
 
-The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) all suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension.
+The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) all suffer from a prohibitive cost of model evaluations that increases depending on the input space dimension.
 %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.
@@
 
-In this note, we propose to construct two replicated points sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$.
-These two designs insure that the input space is properly explored and can then be used within the replication procedure to estimate all main-effects of a numerical model.
-We first provide backgrounds on digital sequences, then we present two iterative approaches to construct the two replicated point sets.
+In this note, we propose to construct two point sets $\mathcal{P}$ and $\mathcal{P}'$ based on Sobol' sequences that identify as two space-filling replicated designs of order $1$.
+These two designs ensure that the input space is properly explored and can be used within the replication procedure to estimate all main-effects of a numerical model.
+We first provide background on digital sequences, then we present two iterative approaches to construct the two point sets.
 
@@
 They can also appear in the literature as digital $(t,m,s)$-nets and digital $(t,s)$-sequences, or simply $(t,m,s)$-nets and $(t,s)$-sequences.
-Sobol' and Niederreiter-Xing sequences are two examples of digital sequences detailed in \cite{Sobol1} and \cite{NiederreiterXing}.
+Sobol' and Niederreiter-Xing sequences are two examples of digital sequences whose explicit constructions are detailed in \cite{Sobol1} and \cite{NiederreiterXing}.
 
-The quality of any $(t,m,s)$-net or $(t,s)$-sequence is measured by $t$, called the $t$-value. The $t$-value is introduced in the $(t,m,s)$-net definition as follows:
+The quality of any $(t,m,s)$-net or $(t,s)$-sequence is measured by $t$, called the $t$-value. The $t$-value is introduced in the following $(t,m,s)$-net definition:
 
@@
 
-By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limit case where $m\rightarrow\infty$, we can define $(t,s)$-sequences as:
+By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limit case where $m\rightarrow\infty$, we can define $(t,s)$-sequences as follows:
 \begin{definition}%[$(t,s)$-sequence]
-For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if for every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
+For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, %if for every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
+if every subset $\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, is a $(t,m,s)$-net in base $b$.
 \end{definition}
+\bigskip
 
-Replicated design properties can apply to digital sequences. Therefore, we introduce the definition,
+The concept of digital sequences can be linked to the definition of replicated designs. To do so, we introduce the following notion:
 \begin{definition}
-Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are said \emph{digitally replicated} of order $r$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $r$.
+Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are said \emph{digitally replicated} of order $r$ if for all $m\geq 0$, the subsets $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $r$.
 \end{definition}
@@
 
-$s$-dimensional Sobol' sequences are designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices defined over $\mathbb{F}_2:=\{0,1\}$.
+Sobol' sequences are digital sequences designed in base $2$.
+These sequences can be computed based on a digital construction scheme over the finite field $\mathbb{F}_2=\{0,1\}$.
+The construction scheme of a $s$-dimensional Sobol' sequence requires a set of $s$ full rank upper triangular matrices of infinite size called generating matrices.
+These generating matrices are recursively constructed through primitive polynomials and initial directional numbers (see \cite{Niederreiter} for further details).
+We detail below the construction scheme of a $s$-dimensional Sobol' sequence.
+%using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices defined over $\mathbb{F}_2:=\{0,1\}$.
 In \cite{Kuo}, Kuo and Joe suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.
 
-We denote these matrices by $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$.
-Although $C_1,\dots,C_s$ have infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points.
+Denote by $C_1,\dots,C_s$ a set of $s$ generating matrices, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$.
+Although $C_1,\dots,C_s$ have infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points of a Sobol' sequence:
 
@@
 \end{equation}
-where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}2^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ the binary decomposition of $i$. Below we show how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$
+where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}2^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ the binary decomposition of $i$. 
+\bigskip
+
+As an example, the points $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$ are computed below for an arbitrary choice of matrices $C_1$, $C_2$:
 
@@
 \end{equation*}
+
+For any $m' > m$, the matrix $C_j^m$ is embedded in the upper left of matrix $C_j^{m'}$.
+Resulting from this embedding, the next $2^m$ points of the digital sequence are constructed by increasing $m$ by one and considering the next $2^m$ integers $i=2^m,\dots,2^{m+1}-1$ in (\ref{dig.net.eq.}).
 \bigskip
 
-Remark that for any $m' > m$, the matrix $C_j^m$ is embedded in the upper left of matrix $C_j^{m'}$.
-Resulting from this embedding, the next $2^m$ points of the digital sequence are constructed by increasing $m$ by one in equation (\ref{dig.net.eq.}).
-The process is iterated as many times as needed.
-
-\begin{lemma}\label{Sobol_replicated}
+In our framework, Sobol' sequences are particularly attractive for their following property:
+\begin{lemma}
+\label{Sobol_replicated}
 All Sobol' sequences are digitally replicated of order 1.
 \end{lemma}
-\begin{pf*}{Proof.}
+\textit{Proof}:
 Consider any two $s$-dimensional Sobol' sequences generated by the generating matrices $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$ respectively.
@@
 Therefore, they generate the same point sets.
-\end{pf*}
 
@@
 
-\section{Iterative construction of replicated point sets}
-SCRAMBLING
-We propose here two approaches to construct two replicated point sets $\mathcal{P}$ and $\mathcal{P}'$ based on Sobol' sequences.
-These two constructions are iterative that is the two points sets constructed possess the following structure:
+\section{Iterative construction}
+
+We present here two approaches to construct two point sets $\mathcal{P}$ and $\mathcal{P}'$ based on Sobol' sequences.
+These two constructions are iterative that is the two point sets constructed possess the following structure:
 $$\mathcal{P}= B_1 \cup B_2 \cup B_3 \dots $$
 $$\mathcal{P}'= {B'}_1 \cup {B'}_2 \cup {B'}_3 \dots $$
-where $B_l$ (resp.
-$B'_l$), $l\geq1$, is a new set of points added at step $l$ to refine $\mathcal{P}$ (resp.
-$\mathcal{P}'$).
-For each approach and at each step, $\mathcal{P}$ and $\mathcal{P'}$ are two replicated designs of order $1$.
+where $B_l$ (resp. $B'_l$), $l\geq1$, is a new set of points added at step $l$ to refine $\mathcal{P}$ (resp. $\mathcal{P}'$).
 
@@
 The second approach is called additive approach.
-It takes an initial number of points of a Sobol' sequence and applies to it digital shift and scrambling operations to generate the two replicated points sets.
+It takes an initial number of points of a Sobol' sequence and applies to it digital operations to generate the two point sets $\mathcal{P}$ and $\mathcal{P}'$.
+For each approach, we show that at each step $\mathcal{P}$ and $\mathcal{P'}$ are two replicated designs of order $1$.
+
+Remark that at each step $l$, the new set of points added $B_l$ and ${B'}_l$ can further be randomized using a scrambling.
+We choose to not detail this aspect, a concise survey on scrambling methods can be found in \cite{Lemieux}.
 
@@
 
-The two replicated points sets $\mathcal{P}$ and $\mathcal{P}'$ constructed with the multiplicative approach are two $s$-dimensional Sobol' sequences constructed with different sets of generating matrices.
-We note $C_1,\dots,C_s$ the generating matrices used to generate design $\mathcal{P}$ and ${C'}_1,\dots,{C'}_s$ those used to generate design $\mathcal{P}'$.
-Our choice of the $2s$ generating matrices $C_1,\dots,C_S,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}.
+The two point sets $\mathcal{P}$ and $\mathcal{P}'$ constructed with the multiplicative approach are two $s$-dimensional Sobol' sequences generated with different sets of generating matrices.
+We note $C_1,\dots,C_s$ the set used to generate $\mathcal{P}$ and ${C'}_1,\dots,{C'}_s$ the set used to generate $\mathcal{P}'$.
+
+Our choice of the $2s$ generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}.
 These two authors proposed a set of generating matrices optimized based on the $t$-value of pairwise projections of the corresponding digital sequence.
-Here, we select $2s$ generating matrices from this set to generate our two designs $\mathcal{P}$ and $\mathcal{P}'$.
+Our $2s$ generating matrices are selected from this set.
+
+The iterative construction of $\mathcal{P}$ and $\mathcal{P}'$ proceed as follows:
+
+at step $l$, $l \geq 1$, $\mathcal{P}$ is refined with a set of $2^l$ points $B_l=\{\vx_{2^{l-1}},\dots,\vx_{2^l-1}\}$ obtained through (\ref{dig.net.eq.}) with $C_1^l,\dots,C_s^l$.
+Likewise, $\mathcal{P}'$ is refined with ${B'}_l=\{\vx'_{2^{l-1}},\dots,\vx'_{2^l-1}\}$ obtained through (\ref{dig.net.eq.}) with ${C'}_1^l,\dots,{C'}_s^l$.
 \bigskip
 
-The iterative construction of designs $\mathcal{P}$ and $\mathcal{P}'$ proceed as follows:
-
-at step $l$, $l \geq 1$, design $\mathcal{P}$ is refined with a set of $2^l$ points $B_l=\{\vx_{2^{l-1}},\dots,\vx_{2^l-1}\}$ obtained through equation (\ref{dig.net.eq.}) with $C_1^l,\dots,C_s^l$.
-Likewise, design $\mathcal{P}'$ is refined with ${B'}_l=\{\vx'_{2^{l-1}},\dots,\vx'_{2^l-1}\}$ obtained through equation (\ref{dig.net.eq.}) with ${C'}_1^l,\dots,{C'}_s^l$.
-
-As a direct consequence of Lemma \ref{Sobol_replicated}, at each step $l$ the designs $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $1$.
+As a direct consequence of Lemma \ref{Sobol_replicated}, at each step $l$ the point sets $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $1$.
 Furthermore, they both inherit the space-filling properties of $(t,l,s)$-nets.
@@
 
-With the multiplicative approach, the sizes of designs $\mathcal{P}$ and $\mathcal{P}'$ are multiplied by $2$ at each step.
+With the multiplicative approach, the sizes of $\mathcal{P}$ and $\mathcal{P}'$ are both multiplied by $2$ at each step.
 This growth rate may be inadequate for some applications.
-The additive approach presented here is attractive due to the slow growing size of the two replicated designs $\mathcal{P}$ and $\mathcal{P}'$ constructed.
-At each step, only $2^m$ points are added to both designs.
+The additive approach presented here is attractive due to the slow growing size of the point sets $\mathcal{P}$ and $\mathcal{P}'$ constructed.
+At each step, a same fixed number of points is added to each point sets.
 However, the main drawback is that $\mathcal{P}$ and $\mathcal{P}'$ each as a whole does not possess the structure of a Sobol' sequence anymore.
@@
 
-The two replicated points sets $\mathcal{P}$ and $\mathcal{P}'$ constructed with the additive approach are iteratively refined with new points sets $B_l$ and ${B'}_l$ that each possesses the structure of a $(t,m,s)$-net.
+Within the additive approach, the two point sets $\mathcal{P}$ and $\mathcal{P}'$ are iteratively refined with new set of points $B_l$ and ${B}'_l$ that each possesses the structure of a $(t,m,s)$-net.
 
-First, an initial set $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^m-1}$ of $2^m$ points of a $s$-dimensional Sobol' sequence is generated by fixing $m >0$ and choosing $s$ generating matrices $C_1,\dots,C_s$.
+First, an initial set $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^m-1}$ of $2^m$ points of a $s$-dimensional Sobol' sequence is generated through (\ref{dig.net.eq.}) by fixing $m >0$ and choosing $s$ generating matrices $C_1,\dots,C_s$.
 These matrices are selected from the set obtained in \cite{Kuo}.
-Then, at step $l$, $B_l$ and ${B'}_l$ are obtained from $B_0$ by carrying out digital shift and scrambling operations.
+Then, at step $l$, $B_l$ and ${B'}_l$ are obtained from $B_0$ by respectively carrying out a digital shift and a random linear scrambling.
 These operations guarantee that both $B_l$ and ${B'}_l$ inherit the $(t,m,s)$-net structure of the initial set $B_0$.
@@
 \end{equation}
-where $ x_{i,j}^{(l)}=\sum_{k = 1}^mx_{i,j,k}^{(l)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{m-1}})^\intercal \in ker(C_j^m)$ the kernel of $C_j^m$.
+where $ x_{i,j}^{(l)}=\sum_{k = 1}^mx_{i,j,k}^{(l)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{m-1}})^\intercal \in {\mathbb{F}_2}^m$.
 \bigskip
 
-Then, ${B'}_l=\{{\vx'}_i^{(l)}\}_{i=0}^{2^m-1}$ is obtained from $B_l$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows:
+Then, ${B'}_l=\{{\vx'}_i^{(l)}\}_{i=0}^{2^m-1}$ is obtained from $B_l$ by applying Matousek's random linear scrambling \cite{Matousek}. This scrambling writes as follows:
 
@@
 \end{equation}
-where $ {x'}_{i,j}^{(l)}=\sum_{k = 1}^m{x'}_{i,j,k}^{(l)}2^{-k}$ and $L_j^m$ is a full rank lower triangular matrix of size $m \times m$ over the Galois field $\mathbb{F}_2$.
+where $ {x'}_{i,j}^{(l)}=\sum_{k = 1}^m{x'}_{i,j,k}^{(l)}2^{-k}$ and $L_j^m$ is a full rank lower triangular matrix of size $m \times m$ over $\mathbb{F}_2$.
 \bigskip
@@
 \begin{lemma}
-At each step $l$, $l\geq1$, the digital shift and scrambling operations carried out in equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) ensure that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $1$.
+At each step $l$, $l\geq1$, the digital shift and scrambling performed in (\ref{dig.shift}) and (\ref{ibinom.scrambling}) ensure that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $1$.
 \end{lemma}
-
-\begin{pf*}{Proof.}
+\textit{Proof:}
 This is a direct consequence of the following result: at each step $l$, $B_l$ and ${B'}_l$ are two replicated designs of order $1$.
-Indeed, since digital shift and i-binomial scrambling operations are bijections from ${\mathbb{F}_2}^m$ to ${\mathbb{F}_2}^m$, each dimension of $B_l$ and ${B'}_l$ contains the same set of $2^m$ values.
-\end{pf*}
+Indeed, since digital shift and random linear scrambling are bijections from ${\mathbb{F}_2}^m$ to ${\mathbb{F}_2}^m$, each dimension of $B_l$ and ${B'}_l$ contains the same set of $2^m$ values.
 
@@
 
+\bibitem{Lemieux} C. Lemieux, Monte Carlo and Quasi-Monte Carlo Sampling, \emph{Springer Ser. Statist.}, New York: Springer, 2009.
+
 \bibitem{Mara} T.
@@
 
-\bibitem{Mckay} M.
-D.
-McKay, W.
-J.
-Conover, R.
-J.
-Beckman, A comparison of three methods for selecting values of input variables in the analysis of output from a computer code, \emph{Technometrics} 21, 1979, pp.
-239--245.
+\bibitem{Matousek} J. Matousek, On the $L^2$-discrepancy  for anchored boxes, \emph{Journal of Complexity} 14(4), pp.527--556.
+
+\bibitem{Mckay} M. D. McKay, Evaluating prediction uncertainty, Discussion paper, \emph{Los Alamos National
+Laboratory Report NUREG/CR- 6311}, LA-12915-MS, 1995.
 
 \bibitem{Niederreiter} 	H. Niederreiter, Random Number Generation and Quasi-Monte Carlo Methods, \emph{CBMS-NSF Regional Conference Series in Applied Math.} 63, SIAM,Philadelphia, PA, 1992.
+
+\bibitem{NiederreiterXing} H.
+Niederreiter, C.
+Xing, Low-Discrepancy Sequences and Global Function Fields with Many Rational Places, \emph{Finite Fields and Their Applications} 2(3), 1996, pp.
+241--273.
 
@@
 
-\bibitem{Tezuka} S. Tezuka, H. Faure, I-binomial scrambling of digital nets and sequences, \emph{J. Complexity} 19(6),2003, pp. 744--757.
-
 \bibitem{Tissot} J.
@@
 
-\bibitem{NiederreiterXing} H.
-Niederreiter, C.
-Xing, Low-Discrepancy Sequences and Global Function Fields with Many Rational Places, \emph{Finite Fields and Their Applications} 2(3), 1996, pp.
-241--273.
-
 \end{thebibliography}

### 2016-05-13 crass/crass.tex
Finshing to review crass

--- 2016-05-12 crass/crass.tex
@@
 \author[authorlabel2]{Llu\'{i}s Antoni Jim\'{e}nez Rugama},
-%\ead{ljimene1@hawk.iit.edu}
+\ead{ljimene1@hawk.iit.edu}
 \author[authorlabel3]{Elise Arnaud},
@@
 \address[authorlabel1]{Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 655 avenue de l'Europe, 38330 Montbonnot}
-\address[authorlabel2]{Illinois Institute of Technology}
+\address[authorlabel2]{Illinois Institute of Technology, Rettaliata Engineering Center, 10 W 32st, Chicago, IL 60616}
 \address[authorlabel3]{Univ. Grenoble Alpes, Jean Kunzmann Laboratory, F-38000 Grenoble, France \\
@@
 Dans le contexte d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches pour construire des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.
-{\it Pour citer cet article~: L. Gilquin, L. A. J. Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
+{\it Pour citer cet article~: L. Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
 Paris, Ser. I 340 (2005).}
@@
 \section{Introduction}
-Mathematical models used in various fields often involve a substantial number of poorly known parameters.
-The effect of these parameters on the output of the model can be assessed through sensitivity analysis.
+Mathematical models often involve a substantial number of poorly known parameters.
+The effect of these parameters to the output of the model can be assessed through sensitivity analysis.
 Global sensitivity analysis methods are useful tools to identify the parameters having the most influence on the output.
-A well known approach is the variance based method introduced by Sobol' \cite{Sobol2}.
+A well known approach is the variance based method introduced by Sobol' in \cite{Sobol2}.
 This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model input.
@@
 
-The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) all suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension.
+The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension.
 %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.
  An elegant solution to reduce this cost relies on the construction of particular design of experiments called replicated designs.
-The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes \cite{Mckay}.
-Here, we define replicated designs in a wider framework:
+The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes in \cite{Mckay}.
+Below we define replicated designs in a wider framework:
 
@@
 Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$ and $\mathcal{D}=\{1,\dots,s\}$.
-Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets,
-$\vx_i,\vx'_i\in[0,1)^{s}$.
+Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
+$[0,1)^{s}$.
 Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp.
@@
 $\mathcal{P}'$) indexed by $u$.
-We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $r$ if:\\
-$\forall \ u \subsetneq \mathcal{D}$ such that $|u|=r$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^r$.
+We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a$ if $\forall \ u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
 \end{definition}
 
-With the construction of only two replicated designs of order $1$, the replication procedure introduced and studied in \cite{Mara,Tissot} allows to estimate all first-order Sobol' indices.
-This procedure has the major advantage of reducing drastically the estimation cost as the number of runs (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension.
+The replication procedure introduced by \cite{Mara,Tissot} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$.
+This procedure has the major advantage of reducing the estimation cost as the number of model evaluations (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension.
 However, Sobol' indices estimates may still not be accurate enough if the input space is not properly explored.
@@
 
-In this note, we propose to construct two replicated points sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$.
-These two designs insure that the input space is properly explored and can then be used within the replication procedure to estimate all main-effects of a numerical model.
-We first provide backgrounds on digital sequences, then we present two iterative approaches to construct the two replicated point sets.
+In this note, we propose the construction of two replicated point sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$.
+These two designs ensure that the input space is properly explored and can be used within the replication procedure to estimate all main-effects of a numerical model.
+We first provide a brief introduction on digital sequences and then present two iterative approaches to construct the two replicated point sets.
 
@@
 \begin{definition}
-Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are said \emph{digitally replicated} of order $r$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $r$.
+Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are \emph{digitally replicated} of order $a$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $a$.
 \end{definition}
@@
 
-$s$-dimensional Sobol' sequences are designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices defined over $\mathbb{F}_2:=\{0,1\}$.
+$s$-dimensional Sobol' sequences are designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over $\mathbb{F}_2:=\{0,1\}$.
+We will denote by $\oplus$ the addition in $\mathbb{F}_2:=\{0,1\}$.
 In \cite{Kuo}, Kuo  and Joe suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.
 
-We denote these matrices by $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$.
-Although $C_1,\dots,C_s$ have infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points.
-
-For each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise by:
+Consider the generating matrices $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$.
+Although $C_1,\dots,C_s$ are of infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points: for each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise:
 \begin{equation}
 \label{dig.net.eq.}
-(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^{m} \vi,\qquad j= 1,\dots,s\, ,
+(x_{i,j,1},\dots,x_{i,j,m})^\intercal = C_j^{m} \vi,\qquad j= 1,\dots,s\, ,
 \end{equation}
-where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}2^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ the binary decomposition of $i$. Below we show how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$
-
+where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}2^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ are the binary decompositions of $x_{i,j}$ and $i$, and matrix operations are performed in $\mathbb{F}_2$.
+Below we provide an example on how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$,
 \begin{equation*}
@@
 x_{11,1,4}
-\end{pmatrix} =
-\begin{pmatrix}
-1 \\
-1 \\
-0 \\
-1
 \end{pmatrix} = 
@@
 1
-\end{pmatrix}}^{\bvec{11}},\qquad
+\end{pmatrix}}^{\bvec{11}}=
+\begin{pmatrix}
+1 \\
+1 \\
+0 \\
+1
+\end{pmatrix}
+,\qquad
 \begin{pmatrix}
@@
 x_{9,2,4}
-\end{pmatrix} =
-\begin{pmatrix}
-0 \\
-1 \\
-1 \\
-1
 \end{pmatrix} = 
@@
 1
-\end{pmatrix}}^{\bvec{9}}
+\end{pmatrix}}^{\bvec{9}} =
+\begin{pmatrix}
+0 \\
+1 \\
+1 \\
+1
+\end{pmatrix}
 \end{equation*}
@@
 
-Remark that for any $m' > m$, the matrix $C_j^m$ is embedded in the upper left of matrix $C_j^{m'}$.
-Resulting from this embedding, the next $2^m$ points of the digital sequence are constructed by increasing $m$ by one in equation (\ref{dig.net.eq.}).
-The process is iterated as many times as needed.
+To compute the next $2^m$ points of the sequence, one can infer from equation (\ref{dig.net.eq.}) that \\$(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m+1})^\intercal=(x_{i,j,1},\dots,x_{i+2^m,j,m},0)^\intercal\oplus {(c_j^{m+1})}^\intercal$, where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.
 
@@
 \begin{pf*}{Proof.}
-Consider any two $s$-dimensional Sobol' sequences generated by the generating matrices $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$ respectively.
-Since these matrices are upper triangular, to compute the first $2^m$ points one only needs the knowledge of the $m\times m$ upper left blocks $C_j^m$ and ${C'}_j^m$, $j \in \{1,\dots,s\}$.
-Because any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the operations $C^{m}_j\vi$ and ${C'}^{m}_j\vi$ are one-to one and onto, for all $i=0,\dots,2^m-1$.
+Consider any two $s$-dimensional Sobol' sequences generated by $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$ respectively.
+Since any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the operations $C^{m}_j\vi$ and ${C'}^{m}_j\vi$ are one-to one and onto for all $i=0,\dots,2^m-1$.
 Therefore, they generate the same point sets.
@@
 
-\section{Iterative construction of replicated point sets}
-SCRAMBLING
-We propose here two approaches to construct two replicated point sets $\mathcal{P}$ and $\mathcal{P}'$ based on Sobol' sequences.
-These two constructions are iterative that is the two points sets constructed possess the following structure:
-$$\mathcal{P}= B_1 \cup B_2 \cup B_3 \dots $$
-$$\mathcal{P}'= {B'}_1 \cup {B'}_2 \cup {B'}_3 \dots $$
-where $B_l$ (resp.
-$B'_l$), $l\geq1$, is a new set of points added at step $l$ to refine $\mathcal{P}$ (resp.
-$\mathcal{P}'$).
-For each approach and at each step, $\mathcal{P}$ and $\mathcal{P'}$ are two replicated designs of order $1$.
+\section{Iterative constructions of extensible replicated point sets of order 1}
 
-The first approach is called multiplicative approach and simply consists in generating two different Sobol' sequences.
-This approach exploits the result of Lemma \ref{Sobol_replicated}.
-The second approach is called additive approach.
-It takes an initial number of points of a Sobol' sequence and applies to it digital shift and scrambling operations to generate the two replicated points sets.
+In this section we propose two different approaches to construct extensible replicated point sets of order 1, $\mathcal{P}_m$ and $\mathcal{P}'_m$, based on Sobol' sequences.
+These two constructions are iteratively extended according to:
+$$\mathcal{P}_m= B_0 \cup \dots \cup B_m\, ,$$
+$$\mathcal{P}'_m= {B'}_0 \cup \dots \cup {B'}_m\, ,$$
+where $B_m$ and $B'_m$, $m \geq 0$, are new sets of points added at step $m$ to refine $\mathcal{P}_{m-1}$ and $\mathcal{P}'_{m-1}$.
+For all $m$, $\mathcal{P}_m$ and $\mathcal{P'}_m$ are two replicated designs of order $1$.
+
+The first approach is called multiplicative because $|P_m|=2^m$ while the second one with $|P_m|=m|B_0|$ is called additive.
+In the multiplicative case, we will directly use $2$ $s$-dimensional sequences as a result from Lemma \ref{Sobol_replicated}.
+However, for the additive case, we will consider an initial set of Sobol' points and apply different scramblings and digital shifts to extend the point sets.
+Additionally, in both cases one can randomize the points with Owen's scrambling \cite{OwenScrambling} as long as equal dimensions between $\mathcal{P}_m$ and $\mathcal{P}'_m$ share the same scrambling.
 
@@
 
-The two replicated points sets $\mathcal{P}$ and $\mathcal{P}'$ constructed with the multiplicative approach are two $s$-dimensional Sobol' sequences constructed with different sets of generating matrices.
-We note $C_1,\dots,C_s$ the generating matrices used to generate design $\mathcal{P}$ and ${C'}_1,\dots,{C'}_s$ those used to generate design $\mathcal{P}'$.
-Our choice of the $2s$ generating matrices $C_1,\dots,C_S,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}.
+Two replicated point sets of order 1 $\mathcal{P}_m$ and $\mathcal{P}'_m$ can be constructed using two $s$-dimensional Sobol' sequences.
+We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_m$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_m$.
+All these matrices need to be different.
+% Our choice of the $2s$ generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}.
 These two authors proposed a set of generating matrices optimized based on the $t$-value of pairwise projections of the corresponding digital sequence.
@@
 
-The iterative construction of designs $\mathcal{P}$ and $\mathcal{P}'$ proceed as follows:
+In order to iteratively construct designs $\mathcal{P}_m$ and $\mathcal{P}'_m$, one just needs to compute $B_\ell=\{\vx_{2^{\ell-1}},\dots,\vx_{2^\ell-1}\}$ and ${B'}_\ell=\{\vx'_{2^{\ell-1}},\dots,\vx'_{2^\ell-1}\}$ for all $\ell=1,\dots,m$, with $B_0=B'_0=\{\bvec{0}\}$.
+Each set $B_\ell$ can be obtained applying equation (\ref{dig.net.eq.}) to $C_1,\dots,C_s$, and $B'_\ell$ using $C'_1,\dots,C'_s$.
 
-at step $l$, $l \geq 1$, design $\mathcal{P}$ is refined with a set of $2^l$ points $B_l=\{\vx_{2^{l-1}},\dots,\vx_{2^l-1}\}$ obtained through equation (\ref{dig.net.eq.}) with $C_1^l,\dots,C_s^l$.
-Likewise, design $\mathcal{P}'$ is refined with ${B'}_l=\{\vx'_{2^{l-1}},\dots,\vx'_{2^l-1}\}$ obtained through equation (\ref{dig.net.eq.}) with ${C'}_1^l,\dots,{C'}_s^l$.
-
-As a direct consequence of Lemma \ref{Sobol_replicated}, at each step $l$ the designs $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $1$.
-Furthermore, they both inherit the space-filling properties of $(t,l,s)$-nets.
+As a direct consequence of Lemma \ref{Sobol_replicated}, at each step $\ell$ designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are two replicated designs of order $1$.
+Furthermore, they both inherit the space-filling properties of $(t,\ell,s)$-nets.
 
@@
 
-With the multiplicative approach, the sizes of designs $\mathcal{P}$ and $\mathcal{P}'$ are multiplied by $2$ at each step.
+With the multiplicative approach, the size of designs $\mathcal{P}_m$ and $\mathcal{P}'_m$ is multiplied by $2$ each time $m$ is increased by one.
 This growth rate may be inadequate for some applications.
-The additive approach presented here is attractive due to the slow growing size of the two replicated designs $\mathcal{P}$ and $\mathcal{P}'$ constructed.
-At each step, only $2^m$ points are added to both designs.
-However, the main drawback is that $\mathcal{P}$ and $\mathcal{P}'$ each as a whole does not possess the structure of a Sobol' sequence anymore.
+The additive approach presented in this section is attractive due to a slower size growth.
+Given a particular choice of $r\geq 1$, only $|B_0|=2^r$ points are added to both designs at each step.
+However, the main drawback is that $\mathcal{P}_m$ and $\mathcal{P}'_m$ do not possess the structure of a Sobol' sequence when $m\geq 1$.
 \bigskip
 
-The two replicated points sets $\mathcal{P}$ and $\mathcal{P}'$ constructed with the additive approach are iteratively refined with new points sets $B_l$ and ${B'}_l$ that each possesses the structure of a $(t,m,s)$-net.
+The two replicated point sets $\mathcal{P}_m$ and $\mathcal{P}'_m$ constructed with the additive approach are iteratively refined with $B_{m+1}$ and ${B'}_{m+1}$.
+Each $B_{m+1}$ and ${B'}_{m+1}$ are $(t,r,s)$-nets.
 
-First, an initial set $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^m-1}$ of $2^m$ points of a $s$-dimensional Sobol' sequence is generated by fixing $m >0$ and choosing $s$ generating matrices $C_1,\dots,C_s$.
-These matrices are selected from the set obtained in \cite{Kuo}.
-Then, at step $l$, $B_l$ and ${B'}_l$ are obtained from $B_0$ by carrying out digital shift and scrambling operations.
-These operations guarantee that both $B_l$ and ${B'}_l$ inherit the $(t,m,s)$-net structure of the initial set $B_0$.
-We detail below the construction of $B_l$ and ${B'}_l$.
+First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ is set to be the first $2^r$ Sobol' points of a $s$-dimensional sequence.
+Then, $B_0'$, $B_\ell$ and ${B'}_\ell$, for $\ell\geq 1$, are obtained from $B_0$ by carrying out digital shifts and scrambling operations.
+These operations guarantee that both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of the initial set $B_0$.
+We detail below the construction of $B_\ell$ and ${B'}_\ell$.
 \bigskip
 
-At step $l$, $l \geq 1$, $B_l=\{\vx_i^{(l)}\}_{i=0}^{2^m-1}$ is generated by applying a digital shift to $B_0$:
+At step $\ell$, $\ell \geq 1$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated by applying a digital shift to $B_0$:
 
-for each $i=0,\dots,2^m-1$, the points $\vx_i^{(l)} = (x_{i,1}^{(l)},\dots,x_{i,s}^{(l)})^\intercal$ is obtained by:
+for each $i=0,\dots,2^r-1$, points $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ are obtained by:
 \begin{equation}
 \label{dig.shift}
-(x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal = (x_{i,j,1}^{(0)},\dots,x_{i,j,m}^{(0)})^\intercal+\ve_j,\qquad j= 1,\dots,s\, ,
+(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = (x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
 \end{equation}
-where $ x_{i,j}^{(l)}=\sum_{k = 1}^mx_{i,j,k}^{(l)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{m-1}})^\intercal \in ker(C_j^m)$ the kernel of $C_j^m$.
+where $ x_{i,j}^{(\ell)}=\sum_{k = 1}^r x_{i,j,k}^{(\ell)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$.
 \bigskip
 
-Then, ${B'}_l=\{{\vx'}_i^{(l)}\}_{i=0}^{2^m-1}$ is obtained from $B_l$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows:
+Then, ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained from $B_\ell$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows:
 
-for each $i=0,\dots,2^m-1$, the points ${\vx'}_i^{(l)} = ({x'}_{i,1}^{(l)},\dots,{x'}_{i,s}^{(l)})^\intercal$ is obtained by:
+for each $i=0,\dots,2^r-1$, points ${\vx'}_i^{(\ell)} = ({x'}_{i,1}^{(\ell)},\dots,{x'}_{i,s}^{(\ell)})^\intercal$ are obtained by:
 \begin{equation}
 \label{ibinom.scrambling}
-({x'}_{i,j,1}^{(l)},\dots,{x'}_{i,j,m}^{(l)})^\intercal = L_j^m (x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal,
+({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = L_j^r (x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal,
 \end{equation}
-where $ {x'}_{i,j}^{(l)}=\sum_{k = 1}^m{x'}_{i,j,k}^{(l)}2^{-k}$ and $L_j^m$ is a full rank lower triangular matrix of size $m \times m$ over the Galois field $\mathbb{F}_2$.
+where $ {x'}_{i,j}^{(\ell)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(\ell)}2^{-k}$ and each $L_j^r$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
 \bigskip
@@
 \begin{lemma}
-At each step $l$, $l\geq1$, the digital shift and scrambling operations carried out in equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) ensure that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $1$.
+Using the additive construction, $\mathcal{P}_m$ and $\mathcal{P}'_m$ are two replicated designs of order $1$ for $m\geq 0$.
 \end{lemma}
@@
 \begin{pf*}{Proof.}
-This is a direct consequence of the following result: at each step $l$, $B_l$ and ${B'}_l$ are two replicated designs of order $1$.
-Indeed, since digital shift and i-binomial scrambling operations are bijections from ${\mathbb{F}_2}^m$ to ${\mathbb{F}_2}^m$, each dimension of $B_l$ and ${B'}_l$ contains the same set of $2^m$ values.
+For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) are bijections from $\mathbb{F}^r_2$ to $\mathbb{F}^r_2$.
+Hence, equal dimensions of $B_\ell$ and ${B'}_\ell$ will contain the same set of $2^m$ values.
 \end{pf*}
@@
 
+\bibitem{OwenScrambling} A. B. Owen, Scrambling Sobol' and Niederreiter-xing points, \emph{J. Complexity}, 14(4), 1998, pp. 466--489.
+
 \end{thebibliography}

### 2016-05-30 crass/crass.tex
changes crass.tex + graphes

@@
 \usepackage{amsmath,amssymb}
+\usepackage{graphicx}
 
@@
 \newcommand{\bvec}[1]{\boldsymbol{#1}}
-\newcommand{\vx}{\bvec{x}}
 \newcommand{\vi}{\bvec{i}}
@@
 \newcommand{\vk}{\bvec{k}}
+\newcommand{\vv}{\bvec{v}}
+\newcommand{\vx}{\bvec{x}}
 \newcommand{\vz}{\bvec{z}}
@@
 \selectlanguage{english}
-\title{Construction of replicated designs based on Sobol' sequences}
+\title{Iterative construction of replicated designs based on Sobol' sequences}
 %\title{Replicated designs based on Sobol' sequences to estimate main effects of model inputs}
@@
 % Text of abstract in English
-In the perspective of estimating main effects of model inputs, two approaches are studied to construct replicated designs based on Sobol' sequences.
+In the perspective of estimating main effects of model inputs, two approaches are studied to iteratively construct replicated designs based on Sobol' sequences.
+Space-filling properties of the resulting designs are studied based on two criteria.
 {\it To cite this article: L.
@@
 %{\bf Plans r\'epliqu\'es \`a base de s\'equences de Sobol' pour estimer les effets principaux des param\`etres d'un mod\`ele. }
-Dans le contexte d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches pour construire des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.
+Dans l'objectif d'estimer les effets principaux des param\`etres d'un mod\`ele, nous proposons d'\'etudier deux approches pour construire it\'erativement des plans r\'epliqu\'es \`a partir de s\'equences de Sobol'.
+Les propri\'et\'es de remplissement de l'espace des plans construits sont \'etudi\'ees sur la base de deux crit\`eres.
 {\it Pour citer cet article~: L. Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
@@
 Mathematical models often involve a substantial number of poorly known parameters.
-The effect of these parameters to the output of the model can be assessed through sensitivity analysis.
+The effect of these parameters on the output of the model can be assessed through sensitivity analysis.
 Global sensitivity analysis methods are useful tools to identify the parameters having the most influence on the output.
@@
 This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model input.
-In particular, one can distinguish first-order indices that estimate the main effect of each input.
+Among all Sobol' indices, one can distinguish first-order indices that estimate the main effect of each input.
 
-The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension.
+The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) all suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension.
 %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.
- An elegant solution to reduce this cost relies on the construction of particular design of experiments called replicated designs.
+ An elegant solution to reduce this cost relies on the construction of particular designs of experiments called replicated designs.
 The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes in \cite{Mckay}.
@@
 $\mathcal{P}'$) indexed by $u$.
-We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a$ if $\forall \ u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
+We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a$ if $\forall \ u \subsetneq \mathcal{D}$ of cardinality $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
 \end{definition}
 
-The replication procedure introduced by \cite{Mara,Tissot} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$.
+The replication procedure introduced in \cite{Mara,Tissot} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$.
 This procedure has the major advantage of reducing the estimation cost as the number of model evaluations (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension.
 However, Sobol' indices estimates may still not be accurate enough if the input space is not properly explored.
+
 \bigskip
@@
 These two designs ensure that the input space is properly explored and can be used within the replication procedure to estimate all main-effects of a numerical model.
+The construction of the two replicated designs is recursive, at each step each design is refined with a new set of points.
+
 We first provide a brief introduction on digital sequences and then present two iterative approaches to construct the two replicated point sets.
+We end this note by studying the space-filling aspect of the two designs constructed.
 
@@
 
-The quality of any $(t,m,s)$-net or $(t,s)$-sequence is measured by $t$, called the $t$-value. The $t$-value is introduced in the $(t,m,s)$-net definition as follows:
+%The quality of any $(t,m,s)$-net or $(t,s)$-sequence is measured by $t$, called the $t$-value. The $t$-value is introduced in the $(t,m,s)$-net definition as follows:
+$(t,m,s)$-nets are defined as follows:
 
@@
 The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest volume possible, $b^{-m}$, contains exactly one point.
+The quality of any $(t,m,s)$-net is therefore measured by the parameter $t$, called $t$-value.
 
@@
 
-$s$-dimensional Sobol' sequences are designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over $\mathbb{F}_2:=\{0,1\}$.
-We will denote by $\oplus$ the addition in $\mathbb{F}_2:=\{0,1\}$.
-In \cite{Kuo}, Kuo  and Joe suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.
+$s$-dimensional Sobol' sequences are digital sequences designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over the Galois field $\mathbb{F}_2:=\{0,1\}$.
+We will denote by $\oplus$ the addition in $\mathbb{F}_2$.
+These generating matrices are recursively constructed through primitive polynomials and initial directional numbers.
+In \cite{Kuo}, Kuo and Joe detail this construction and also suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.
 
 Consider the generating matrices $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$.
-Although $C_1,\dots,C_s$ are of infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points: for each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise:
+Although $C_1,\dots,C_s$ are of infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points: for each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise by:
 \begin{equation}
@@
 \end{equation}
-where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}2^{-k}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ are the binary decompositions of $x_{i,j}$ and $i$, and matrix operations are performed in $\mathbb{F}_2$.
+where $x_{i,j} = \sum_{k \geq 1}^m x_{i,j,k}2^{-k}$ is the binary expansion of $x_{i,j}$ and $\vi = (i_{0},\dots,i_{m-1})^\intercal$ is the vector obtained from the binary expansion of $i= \sum_{k \geq 0}^{m-1} i_{k}2^{k}$.
+All matrix operations are performed in $\mathbb{F}_2$.
 Below we provide an example on how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$,
@@
 
-To compute the next $2^m$ points of the sequence, one can infer from equation (\ref{dig.net.eq.}) that \\$(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m+1})^\intercal=(x_{i,j,1},\dots,x_{i+2^m,j,m},0)^\intercal\oplus {(c_j^{m+1})}^\intercal$, where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.
+To compute the next $2^m$ points of the sequence, one can infer from Equation (\ref{dig.net.eq.}) that \\$(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m+1})^\intercal=(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m},0)^\intercal\oplus {(c_j^{m+1})}^\intercal$, where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.
 
@@
 Consider any two $s$-dimensional Sobol' sequences generated by $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$ respectively.
-Since any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the operations $C^{m}_j\vi$ and ${C'}^{m}_j\vi$ are one-to one and onto for all $i=0,\dots,2^m-1$.
+Since any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the operations $\vi \mapsto C^{m}_j\vi$ and $\vi \mapsto {C'}^{m}_j\vi$ are one-to one and onto for all $i=0,\dots,2^m-1$.
 Therefore, they generate the same point sets.
@@
 
-\section{Iterative constructions of extensible replicated point sets of order 1}
+%\section{Iterative constructions of extensible replicated point sets of order 1}
+\section{Iterative constructions of replicated point sets}
 
-In this section we propose two different approaches to construct extensible replicated point sets of order 1, $\mathcal{P}_m$ and $\mathcal{P}'_m$, based on Sobol' sequences.
-These two constructions are iteratively extended according to:
-$$\mathcal{P}_m= B_0 \cup \dots \cup B_m\, ,$$
-$$\mathcal{P}'_m= {B'}_0 \cup \dots \cup {B'}_m\, ,$$
-where $B_m$ and $B'_m$, $m \geq 0$, are new sets of points added at step $m$ to refine $\mathcal{P}_{m-1}$ and $\mathcal{P}'_{m-1}$.
-For all $m$, $\mathcal{P}_m$ and $\mathcal{P'}_m$ are two replicated designs of order $1$.
+In this section we propose two different approaches to iteratively construct two replicated point sets, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, based on Sobol' sequences.
+These two constructions are carried out according to the following recursive scheme :
+$$\left\lbrace \begin{array}{l}
+\mathcal{P}_0= B_0 \\
+\mathcal{P}_\ell= \mathcal{P}_{\ell-1} \cup B_\ell \end{array}\right. \,
+\hspace*{0.5cm}
+\left\lbrace \begin{array}{l}
+\mathcal{P}'_0= {B'}_0 \\
+\mathcal{P}'_\ell= \mathcal{P}'_{\ell-1} \cup {B'}_\ell \end{array}\right. 
+$$
+%$$\mathcal{P}_m= B_0 \cup \dots \cup B_m\, ,$$
+%$$\mathcal{P}'_m= {B'}_0 \cup \dots \cup {B'}_m\, ,$$
+where $B_\ell$ and $B'_\ell$, $\ell \geq 0$, are new sets of points added at step $\ell$ to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$.
+For all $\ell$, $\mathcal{P}_\ell$ and $\mathcal{P'}_\ell$ are two replicated designs of order $1$.
 
-The first approach is called multiplicative because $|P_m|=2^m$ while the second one with $|P_m|=m|B_0|$ is called additive.
+The first approach is called multiplicative because $|P_\ell|=2^\ell$ while the second one with $|P_\ell|=\ell|B_0|$ is called additive.
 In the multiplicative case, we will directly use $2$ $s$-dimensional sequences as a result from Lemma \ref{Sobol_replicated}.
 However, for the additive case, we will consider an initial set of Sobol' points and apply different scramblings and digital shifts to extend the point sets.
-Additionally, in both cases one can randomize the points with Owen's scrambling \cite{OwenScrambling} as long as equal dimensions between $\mathcal{P}_m$ and $\mathcal{P}'_m$ share the same scrambling.
+Additionally, in both cases one can randomize the points with Owen's scrambling \cite{OwenScrambling} as long as same coordinates of $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ share the same scrambling.
 
@@
 
-Two replicated point sets of order 1 $\mathcal{P}_m$ and $\mathcal{P}'_m$ can be constructed using two $s$-dimensional Sobol' sequences.
-We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_m$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_m$.
+Two replicated point sets of order 1 $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ can be constructed using two $s$-dimensional Sobol' sequences.
+We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_\ell$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_\ell$.
 All these matrices need to be different.
@@
 
-In order to iteratively construct designs $\mathcal{P}_m$ and $\mathcal{P}'_m$, one just needs to compute $B_\ell=\{\vx_{2^{\ell-1}},\dots,\vx_{2^\ell-1}\}$ and ${B'}_\ell=\{\vx'_{2^{\ell-1}},\dots,\vx'_{2^\ell-1}\}$ for all $\ell=1,\dots,m$, with $B_0=B'_0=\{\bvec{0}\}$.
-Each set $B_\ell$ can be obtained applying equation (\ref{dig.net.eq.}) to $C_1,\dots,C_s$, and $B'_\ell$ using $C'_1,\dots,C'_s$.
+In order to recursively construct designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, one just needs to compute $B_\ell=\{\vx_{2^{\ell-1}},\dots,\vx_{2^\ell-1}\}$ and ${B'}_\ell=\{\vx'_{2^{\ell-1}},\dots,\vx'_{2^\ell-1}\}$ at each step $\ell \geq 1$ to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$, starting with $B_0=B'_0=\{\bvec{0}\}$ where $\bvec{0}$ denotes the null vector.
+Each set $B_\ell$ can be obtained applying equation (\ref{dig.net.eq.}) to $C_1,\dots,C_s$ and likewise for ${B'}_\ell$ using $C'_1,\dots,C'_s$.
 
@@
 
-With the multiplicative approach, the size of designs $\mathcal{P}_m$ and $\mathcal{P}'_m$ is multiplied by $2$ each time $m$ is increased by one.
+With the multiplicative approach, the size of designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ is multiplied by $2$ each time $\ell$ is increased by one.
 This growth rate may be inadequate for some applications.
 The additive approach presented in this section is attractive due to a slower size growth.
-Given a particular choice of $r\geq 1$, only $|B_0|=2^r$ points are added to both designs at each step.
-However, the main drawback is that $\mathcal{P}_m$ and $\mathcal{P}'_m$ do not possess the structure of a Sobol' sequence when $m\geq 1$.
+Given an initial choice of $r\geq 1$ that specifies the size of $B_0$ and ${B'}_0$, only $|B_0|=2^r$ points are added to both designs at each step.
+
+The main drawback of this approach is that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ do not possess the structure of a Sobol' sequence anymore when $m\geq 1$.
+Still, both designs display good space-filling properties as shown in the next section.
+
 \bigskip
 
-The two replicated point sets $\mathcal{P}_m$ and $\mathcal{P}'_m$ constructed with the additive approach are iteratively refined with $B_{m+1}$ and ${B'}_{m+1}$.
-Each $B_{m+1}$ and ${B'}_{m+1}$ are $(t,r,s)$-nets.
+The two replicated point sets $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ constructed with the additive approach are iteratively refined with $B_\ell$ and ${B'}_\ell$.
+Each $B_\ell$ and ${B'}_\ell$ are $(t,r,s)$-nets.
 
-First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ is set to be the first $2^r$ Sobol' points of a $s$-dimensional sequence.
-Then, $B_0'$, $B_\ell$ and ${B'}_\ell$, for $\ell\geq 1$, are obtained from $B_0$ by carrying out digital shifts and scrambling operations.
-These operations guarantee that both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of the initial set $B_0$.
+First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are set to be the first $2^r$ Sobol' points of two $s$-dimensional sequences.
+Then, $B_\ell$ (resp.
+${B'}_\ell$), for $\ell \geq 1$, is obtained from $B_0$ (resp.
+${B'}_0$) by carrying out digital shifts and scrambling operations.
+These operations guarantee that both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of the initial sets $B_0$ and ${B'}_0$.
 We detail below the construction of $B_\ell$ and ${B'}_\ell$.
@@
 
-At step $\ell$, $\ell \geq 1$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated by applying a digital shift to $B_0$:
+At step $\ell$, $\ell \geq 1$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated as follows:
 
@@
 \label{dig.shift}
-(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = (x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
+(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = L (x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
 \end{equation}
-where $ x_{i,j}^{(\ell)}=\sum_{k = 1}^r x_{i,j,k}^{(\ell)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$.
+where $ x_{i,j}^{(\ell)}=\sum_{k = 1}^r x_{i,j,k}^{(\ell)}2^{-k}$, $\ve_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and $L$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
 \bigskip
 
-Then, ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained from $B_\ell$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows:
+Likewise ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained as follows: 
+%from $B_\ell$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows
 
@@
 \label{ibinom.scrambling}
-({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = L_j^r (x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal,
+({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = {L'} ({x'}_{i,j,1}^{(0)},\dots,{x'}_{i,j,r}^{(0)})^\intercal\oplus {\ve'}_j,\qquad j= 1,\dots,s\, ,
 \end{equation}
-where $ {x'}_{i,j}^{(\ell)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(\ell)}2^{-k}$ and each $L_j^r$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
+where $ {x'}_{i,j}^{(\ell)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(\ell)}2^{-k}$, ${\ve'}_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and ${L'}$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
 \bigskip
 
+The left multiplications carried out in Equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) by matrices $L$ and $L'$ are referred as random linear scrambling \cite{Matousek} while the additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts.
+There are exactly $2^r$ different choices for vectors $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices for matrices $L$ and $L'$.
+
+The vectors $\ve_j$ (resp.
+${\ve}'_j$) are selected to guarantee that the set $\{\ve_1,\dots,\ve_s\}$ (resp.
+$\{{\ve}'_1,\dots,{\ve}'_s\}$) is different at each step $\ell$.
+There exists exactly $2^{r s}$ combinations of this set which leaves us with a large panel of choice.
+
+\bigskip
+
+We have the following result:
 %\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomized using the same Owen's scrambling column-wise.
@@
 \begin{lemma}
-Using the additive construction, $\mathcal{P}_m$ and $\mathcal{P}'_m$ are two replicated designs of order $1$ for $m\geq 0$.
+Using the additive construction, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are two replicated designs of order $1$ for $\ell \geq 0$.
 \end{lemma}
@@
 For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) are bijections from $\mathbb{F}^r_2$ to $\mathbb{F}^r_2$.
-Hence, equal dimensions of $B_\ell$ and ${B'}_\ell$ will contain the same set of $2^m$ values.
+Hence, same coordinates of $B_\ell$ and ${B'}_\ell$ will contain the same set of $2^r$ values.
 \end{pf*}
+
+\section{Space-filling properties}
+
+It has already been pointed out in the previous section that the two replicated designs constructed with the additive approach loose their $(t,m,s)$-net properties once a new set of points is added.
+Nonetheless, they still retain space-filling properties that combined with the low cost of the additive approach make their use appealing.
+We propose two study the space-filling properties of the two designs constructed with both approaches: multiplicative and additive, based on two criteria.
+
+The first one is the $L_2$ star discrepancy that measures the uniformity of a points set.
+This criterion can easily be computed through an analytical expression \cite{Morokoff}.
+The lower the criterion, the more uniform the points set.
+Sobol' sequences were originally constructed to be low discrepancy sequences and so behave well with regards to this criterion.
+
+The second criterion is called maximin distance criterion and measures the regularity of a points set.
+It returns the minimum of distances between all pairs of a points set.
+The higher the criterion, the more spread the points set.
+
+\bigskip
+
+We denote by design $A$ (resp. design $B$) the design constructed with the multiplicative (resp. additive) approach. Values of maximin and discrepancy criteria are computed for designs $A$ and $B$.
+
+For design $A$, the design constructed is refined in four steps, starting from $2^8$ points.
+For design $B$, we chose a starting value $r=8$ and refine the design $15$ times.
+To highlight the performance of design $B$, the results are compared to those obtained with a Latin Hypercube design.
+Average results over $100$ repeats are presented in Figure \ref{results.crit}.
+The x-axis represent the growing size of the design from $2^8$ points to $2^{12}$ points.
+
+As expected design $A$ performs the best.
+However, we observe that design $B$ outperforms a classic Latin Hypercube design in both criteria while allowing $15$ construction steps instead of $4$ for design $A$.
+
+\begin{figure}
+\label{results.crit}
+\includegraphics[scale=0.43]{discrep.pdf}
+\hspace*{0.1cm}
+\includegraphics[scale=0.43]{mindist.pdf}
+\end{figure}
 
@@
 
+\bibitem{Matousek} J. Matou$\check{s}$ek, On the $L2$-discrepancy for anchored boxes, \emph{Journal of Complexity} 14, 1998, pp. 527?-556.
+
 \bibitem{Mckay} M.
@@
 
+\bibitem{Morokoff} W. J. Morokoff, R. E. Caflisch, Quasi-random sequences and their discrepancies, \emph{SIAM Journal on Scientific Computing} 15, 1994, pp.1251?-1279.
+
 \bibitem{Niederreiter} 	H. Niederreiter, Random Number Generation and Quasi-Monte Carlo Methods, \emph{CBMS-NSF Regional Conference Series in Applied Math.} 63, SIAM,Philadelphia, PA, 1992.
 
-\bibitem{Saltelli} A. Saltelli, Making best use of model evaluations to compute sensitivity indices, \emph{Computer Physics Communications} 145(2), 2002, pp. 280?-297.
+\bibitem{NiederreiterXing} H.
+Niederreiter, C.
+Xing, Low-Discrepancy Sequences and Global Function Fields with Many Rational Places, \emph{Finite Fields and Their Applications} 2(3), 1996, pp.
+241--273.
+
+\bibitem{OwenScrambling} A. B. Owen, Scrambling Sobol' and Niederreiter-xing points, \emph{J. Complexity}, 14(4), 1998, pp. 466--489.
+
+\bibitem{Saltelli} A. Saltelli, Making best use of model evaluations to compute sensitivity indices, \emph{Computer Physics Communications} 145(2), 2002, pp. 280--297.
 
@@
 
-\bibitem{Tezuka} S. Tezuka, H. Faure, I-binomial scrambling of digital nets and sequences, \emph{J. Complexity} 19(6),2003, pp. 744--757.
+%\bibitem{Tezuka} S. Tezuka, H. Faure, I-binomial scrambling of digital nets and sequences, \emph{J. Complexity} 19(6),2003, pp. 744--757.
 
@@
 
-\bibitem{NiederreiterXing} H.
-Niederreiter, C.
-Xing, Low-Discrepancy Sequences and Global Function Fields with Many Rational Places, \emph{Finite Fields and Their Applications} 2(3), 1996, pp.
-241--273.
-
-\bibitem{OwenScrambling} A. B. Owen, Scrambling Sobol' and Niederreiter-xing points, \emph{J. Complexity}, 14(4), 1998, pp. 466--489.
-
 \end{thebibliography}

### 2016-06-06 article.tex
changes main paper

--- 2016-02-16 article.tex
@@
 \newtheorem{remark}{Remark}
+\newtheorem{theorem}{Theorem}
 \theoremstyle{definition}
@@
 \newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
+\newcommand\iid{\stackrel{iid}{\sim}}
+
+\makeatletter
+\newcommand*{\ov}[1]{
+  \m@th\overline{\mbox{#1}\raisebox{2mm}{}}
+}
 
 \def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}
+
+\let\oldemptyset\emptyset
+\let\emptyset\varnothing
 
@@
 
-\section{Sensibility Analysis}
-\subsection{Background}
-\subsection{Replication Method}
-\subsection{Sobol' Indices}
+\begin{itemize}
+\item[$\bullet$] introduction sensitivity analysis + estimation methods
+\item[$\bullet$] importance of sampling $\rightarrow$ sobol' sequences
+\item[$\bullet$] problem: when to stop? $\rightarrow$ reliable error estimation 
+\end{itemize}
+
+\section{Estimation of Sobol' indices}
+\subsection{Definition of Sobol' indices}
+We follow the same notations introduced by Owen in \cite{Owen}.
+Denote by $\vx \in [0,1)^d$ a point with components $x_1,\dots,x_d$ and $\mathcal{D}=\{1,\dots,d\}$.
+Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality.
+$\vx_u$ represents a point in $[0,1)^u$ with components $x_j, j \in u$.
+Given two points $\vx$ and $\vx'$, the hybrid point $\vz=(\vx_u:{\vx'}_{-u})$ is defined as $z_j=x_j$ if $j \in u$ and $z_j={x'}_j$ if $j \notin u$.
+
+Let $f$ be the symbol representing the numerical model considered. We assume $f \in \mathcal{L}^2[0,1]^d$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
+The uncertainty on $\vx$ is modeled by random variables such that $\vx \iid \mathcal{U}[0,1)^d$. Recall the Hoeffding decomposition \cite{Hoeffding} of $f$:
+\begin{equation}
+f(\vx)=\mu+\sum \limits_{u \subseteq \mathcal{D}} f_u(\vx),
+\label{anova}
+\end{equation}
+where:
+\[f_u(\vx)= \int_{[0,1)^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).\]
+Due to orthogonality, taking the variance of each side in equation (\ref{anova}) leads to the variance decomposition of $f$:
+\[ \sigma^2 = \sum \limits_{u \subseteq \{1,\dots,d\}} \sigma_v^2, \ \text{ with } \ \sigma_v^2=\int_{[0,1)^{|v|}} f_v(\vx)^2 d{\vx}.\]
+The problem of interest is the estimation of the quantities:
+\begin{align*}
+\underline{\tau}_u^2 &= \sum \limits_{v \subseteq u} \sigma_v^2, \\
+\ov{$\tau$}_u^2 &= \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2.
+\end{align*}
+
+For $u \subsetneq \mathcal{D}$, the two quantities $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ both measure the importance of the variables in $\vx_u$.
+$\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$ that corresponds to the effect of all interactions between variables in $\vx_u$.
+$\ov{$\tau$}_u^2$ quantifies the main effect of $\vx_u$ plus all interactions between variables in $\vx_u$ and variables in $\vx_{-u}$.
+
+These two measure satisfy the following relations: $ 0 \leq  \underline{\tau}_u^2 \leq \ov{$\tau$}_u^2$ and $\underline{\tau}_u^2 = \sigma^2 - \ov{$\tau$}_{-u}^2$.
+These two measure are commonly found in the litterature in their normalized form: $\underline{S}_u = \underline{\tau}_u^2 / \sigma^2$ is the closed $|u|$-order Sobol' index for the set $u$, while $\ov{$S$}_u = \ov{$\tau$}_u^2 / \sigma^2$ is the total effect Sobol' index for the set $u$.
+\bigskip
+
+We focus here on the evaluation of first-order and total effect Sobol' indices. The computation of these indices is performed based on the following identities:
+\begin{align}
+\label{first.order}
+\underline{\tau}_u^2  &= \int_{[0,1)^{2d-1}} f(\vx) f(\vx_u:{\vx'}_{-u})d\vx d{\vx'}-\mu^2 , \\
+\label{total.effect}
+\ov{$\tau$}_u^2 &= \int_{[0,1)^{d+1}}f(\vx)^2-f(\vx)f({\vx'}_u:\vx_{-u})d\vx d{\vx'},
+\end{align}
+where mean and variance of $f$ respectively writes as:
+\[ \mu = \int_{[0,1)^{2d}} f(\vx) d{\vx}, \ \qquad
+\sigma^2 = \int_{[0,1)^{2d}} f(\vx)^2d{\vx} - \mu^2 .\]
+Most of the time, the complexity of $f$ causes the computation of $\mu$, $\sigma^2$ and integrals (\ref{first.order}) and (\ref{total.effect}) to be intractable.
+In such case, one needs to rely on an estimation of these quantities.
+
+We define by design a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ obtained by sampling each variable $x_j$ $n$ times.
+Each row of the design is a point $\vx_i$ in $[0,1)^d$.
+Each column of the design refers to a variable $x_j$.
+The strategy proposed by Sobol' to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
+\begin{align}
+\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-\hat{\mu}^2,\\
+\widehat{\ov{$\tau$}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i)^2 - f(\vx_i)f({\vx'}_{i,u}:\vx_{i,-u}),
+\end{align}
+where $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ are two designs and $(\vx_i,{\vx'}_i) \iid [0,1)^{2d}$.
+The estimation of a single pair ($\underline{\tau}_u^2$, $\ov{$\tau$}_u^2$) requires $3n$ evaluations of the model $f$.
+Using a combinatorial formalism, Saltelli \cite{Saltelli} proposed the following strategy to reduce the estimation cost:
+\begin{theorem}
+\label{saltelli.theorem}
+The $d+2$ designs $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allows to estimate all first-order and all total effect Sobol' indices at a cost of $n(d+2)$ evaluations of the model.
+\end{theorem}
+The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P'}$ in $\mathcal{P}$.
+While elegant, this approach still requires a number of model evaluations that grows linearly with respect to the input space dimension.
+
+An efficient alternative was proposed by Mara \textit{et al.} \cite{Mara} to evaluate all first-order indices with only $2n$ model evaluations.
+This alternative has been further deeply studied and generalized in Tissot
+et al. \cite{Mara} to the estimation of closed second-order indices. The estimation procedure introduced in \cite{Mara} relies on the construction of two replicated designs.
+
+\subsection{Two iterative estimation procedures}
+
+In this section we propose two iterative estimation procedures to evaluate first-order and total-effect Sobol' indices.
+The first procedure combine the strategy proposed by Saltelli with quasi-Monte Carlo sampling.
+The second is the procedure proposed by Mara
+
+The first approach is called multiplicative because $|P_\ell|=2^\ell$ while the second one with $|P_\ell|=\ell|B_0|$ is called additive.
+In the multiplicative case, we will directly use $2$ $s$-dimensional sequences as a result from Lemma \ref{Sobol_replicated}.
+However, for the additive case, we will consider an initial set of Sobol' points and apply different scramblings and digital shifts to extend the point sets.
+Additionally, in both cases one can randomize the points with Owen's scrambling \cite{OwenScrambling} as long as same coordinates of $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ share the same scrambling.
+
+$\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, based on Sobol' sequences. These two constructions are carried out according to the following recursive scheme :
+$$\left\lbrace \begin{array}{l}
+\mathcal{P}_0= B_0 \\
+\mathcal{P}_\ell= \mathcal{P}_{\ell-1} \cup B_\ell \end{array}\right. \,
+\hspace*{0.5cm}
+\left\lbrace \begin{array}{l}
+\mathcal{P}'_0= {B'}_0 \\
+\mathcal{P}'_\ell= \mathcal{P}'_{\ell-1} \cup {B'}_\ell \end{array}\right. 
+$$
+
+%where expressions for $\mu$ and $\sigma^2$ are taken as introduced in Janon \textit{et al.} \cite{Janon}:
+%\begin{align*}
+%\mu &= \frac{1}{2} \int_{[0,1)^{2d-1}}f(\vx)+f(\vx_u:{\vx'}_{-u}) d\vx d{\vx'}, \\
+%\sigma^2 &= \frac{1}{2} \int_{[0,1)^{2d-1}}(f(\vx)+f(\vx_u:{\vx'}_{-u}))^2 d\vx d{\vx'} - \mu^2.
+%\end{align*}
+
+\subsection{Improvements}
+Cost small:\[n(d+1)+d_sn+n\]
+Cost pas small:\[\alpha n d_s +n+(d-d_s)n\]
+Cost small - cost pas small: \[n\sum_{i=1}^{s}(2-\alpha_i+1)\] $s$ number of small indices, $\alpha_i$ proportion of how many more points if not pas small
+
+%\section{Estimators: Correlation 2 Oracle 2}
+%\subsection{Choice and parameters (threshold small?)}
+%\subsection{Cost discussion: for first-order Consider or not total order}
 
 \section{Reliable Error Estimation for Cubatures}
+We assume that we have an algorithm $\widehat{I}(f;\varepsilon)$ such that $\abs{I(f)-\widehat{I}(f;\varepsilon)}\leq \varepsilon$.
+For instance, the guaranteed quasi-Monte Carlo cubatures described in \cite{-} and \cite{-}.
+Therefore, we will always assume that the true integral $I(f)$ lies in $[\widehat{I}(f;\varepsilon)-\varepsilon,\widehat{I}(f;\varepsilon)+\varepsilon]$.
 
-\section{Sobol' Sequences and Permuted Points}
+Sobol' indices can be seen as operators over functions that can be simplified as functions whose entries are integrals.
+
+The case of $correlation 2$
+Je viens de comprendre, prendre S(LB,UB) comme le minimum (LowerBound, UpperBound) et S(UB,LB) comme le maximum est trop simple. Il faut construire le $S_{max}$ et $S_{min}$ en fonction du cas.
+Pour nous, $a - b*c + c^2$ est un paraboloïde hyperbolique.
+La droite avec plus de décroissement est $0+\lambda(2,1)$ [prends la dérivée par rapport à $c$ et l'on a $c=b/2$] et la perpendiculaire, celle de plus accroissement (symmetrie).
+Sur notre région carré, le point de max valeur de $S$ sera le point le plus eloignée de la droite $0+\lambda(2,1)$, et le minimum, sera sur cette droite le plus eloignée de $b = 0$ (si l'on substitue $c=b/2$, on obtient que restreint à cette droite, la fonction est $a-b^2/4$).
+
+$\bullet$ Max at $= \hat{a} + e_a$  ,  $\hat{b} - sign(\hat{c}-\hat{b}/2) e_b$,  $\hat{c} + sign(\hat{c}-\hat{b}/2) e_c$
+
+$\bullet$ Min at $= \hat{a} - e_a$  ,  $\hat{b} + sign(\hat{b}) e_b$  ,  $(\hat{b} + sign(\hat{b}) e_b)/2$
+\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
+
+\section{Applications}
+\subsection{Classical test functions}
+\subsection{Real case model}
 

### 2016-06-06 FunctionsTest/SI_all_example.m
Updating code for (d+1)n

@@ -23,8 +23,8 @@ SI_n = out_param.n;
 SI_t = out_param.time;
 SI_s = out_param.small;
 disp(SI)
-disp(out_param.bound_err)
-% disp(SI_n)
+% disp(out_param.bound_err)
+disp(SI_n)
 % disp(SI_s)
 % disp(abs(R-SI) > max(abstol,R*reltol))
 % disp(out_param.exitflag)
@@ -72,8 +72,8 @@ SI_n = out_param.n;
 SI_t = out_param.time;
 SI_s = out_param.small;
 disp(SI)
-disp(out_param.bound_err)
-% disp(SI_n)
+% disp(out_param.bound_err)
+disp(SI_n)
 % disp(SI_s)
 % disp(abs(R-SI) > max(abstol,R*reltol))
 % wronga = wronga + sum(sum(abs(R-SI) > max(abstol,R*reltol)));
@@ -122,8 +122,8 @@ SI_n = out_param.n;
 SI_t = out_param.time;
 SI_s = out_param.small;
 disp(SI)
-disp(out_param.bound_err)
-% disp(SI_n)
+% disp(out_param.bound_err)
+disp(SI_n)
 % disp(SI_s)
 % disp(abs(R-SI) > max(abstol,R*reltol))
 % wronga = wronga + sum(sum(abs(R-SI) > max(abstol,R*reltol)));
@@ -171,8 +171,8 @@ SI_n = out_param.n;
 SI_t = out_param.time;
 SI_s = out_param.small;
 disp(SI)
-disp(out_param.bound_err)
-% disp(SI_n)
+% disp(out_param.bound_err)
+disp(SI_n)
 % disp(SI_s)
 % disp(abs(R-SI) > max(abstol,R*reltol))
 % wronga = wronga + sum(sum(abs(R-SI) > max(abstol,R*reltol)));

### 2016-06-06 FunctionsTest/cubSobol_SI_all_g.m

@@ -244,7 +244,8 @@ end
 
 % First and total order indices estimators and function evaluations
 Sfo  = @(b,c) min(max(max(b(:,1),0)./max((c(:,2)-b(:,3).^2),0),0),1); % S function for first order
-ffo = @(xpts,u,fx,fy,fxy) (fx - 1/2*mean(fx + fxy)).*(fxy - 1/2*mean(fx + fxy));
+% ffo = @(xpts,u,fx,fy,fxy) (fx - 1/2*mean(fx + fxy)).*(fxy - 1/2*mean(fx + fxy));
+ffo = @(xpts,u,fx,fy,fxy) fx.*(fxy - fy);
 Sfo_s = Sfo; % S function for first order small
 ffo_s = @(xpts,u,fx,fy,fxy) (fx - f([xpts(:,1:u-1) xpts(:,2*out_param.d + u) xpts(:,u+1:out_param.d)])).*(fxy - fy); % We redefine the non normalized estimator
 Stot = Sfo; % S function for total effect
@@ -253,7 +254,7 @@ ftot = @(xpts,u,fx,fy,fxy) 1/2*(fy - fxy).^2;
 
 %% Main algorithm (we added 2xd dimensions for each index and and additional 2 for mean of f and f^2)
 sobstr = sobolset(3*out_param.d); %generate a Sobol' sequence 3*d to consider the changing to the estimator for some smaller size indices
-sobstr = scramble(sobstr,'MatousekAffineOwen'); %scramble it
+% sobstr = scramble(sobstr,'MatousekAffineOwen'); %scramble it
 kappanumap_fx2_fx = bsxfun(@times,(1:2^out_param.mmin)', [1 1]); %initialize map
 Stilde_fx2_fx = zeros(out_param.mmax-out_param.mmin+1, 2); %initialize sum of DFWT terms for fx2 and fx
 CStilde_low_fx2_fx = -inf(out_param.mmax-l_star+1, 2); %initialize various sums of DFWT terms for necessary conditions for fx2 and fx
@@ -886,5 +887,11 @@ if (strcmp(out_param.measure,'normal')) && (any(hyperbox(1,:)==hyperbox(2,:)) ||
     disp([-inf*ones(1,out_param.d);inf*ones(1,out_param.d)])
     hyperbox = [-inf*ones(1,out_param.d);inf*ones(1,out_param.d)];
 end
+
+end
+
+function y = phyp_minmax(b,c)
+
+
 
 end

### 2016-06-08 article.tex
crass + article changes

@@
 \setlength{\marginparwidth}{0.5in}
-\usepackage{amsmath,amssymb,amsthm,natbib,mathtools,bbm,extraipa,mathabx,graphicx}
+\usepackage{amsmath,amssymb,amsthm,natbib,
+mathtools,bbm,extraipa,mathabx,graphicx,algorithm}
+\usepackage{algpseudocode}
 %accents,
@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{definition}{Definition}
 \theoremstyle{definition}
-\newtheorem{defin}{Definition}
 \newtheorem{algo}{Algorithm}
@@
 \subsection{Definition of Sobol' indices}
-We follow the same notations introduced by Owen in \cite{Owen}.
-Denote by $\vx \in [0,1)^d$ a point with components $x_1,\dots,x_d$ and $\mathcal{D}=\{1,\dots,d\}$.
+We adopt the same notations introduced by Owen in \cite{Owen}.
+Denote by $\vx \in [0,1)^d$ a point with components $x_1,\dots,x_d$ and set $\mathcal{D}=\{1,\dots,d\}$.
 Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality.
@@
 
-Let $f$ be the symbol representing the numerical model considered. We assume $f \in \mathcal{L}^2[0,1]^d$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
+Let $f$ be the symbol representing the numerical model studied. We assume $f \in \mathcal{L}^2[0,1)^d$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
 The uncertainty on $\vx$ is modeled by random variables such that $\vx \iid \mathcal{U}[0,1)^d$. Recall the Hoeffding decomposition \cite{Hoeffding} of $f$:
@@
 \[ \sigma^2 = \sum \limits_{u \subseteq \{1,\dots,d\}} \sigma_v^2, \ \text{ with } \ \sigma_v^2=\int_{[0,1)^{|v|}} f_v(\vx)^2 d{\vx}.\]
-The problem of interest is the estimation of the quantities:
-\begin{align*}
-\underline{\tau}_u^2 &= \sum \limits_{v \subseteq u} \sigma_v^2, \\
-\ov{$\tau$}_u^2 &= \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2.
-\end{align*}
+From the variance decomposition of $f$, on can express the following two quantities:
+\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
+\ov{$\tau$}_u^2 = \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2, \qquad u \subsetneq \mathcal{D}.\]
 
 For $u \subsetneq \mathcal{D}$, the two quantities $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ both measure the importance of the variables in $\vx_u$.
-$\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$ that corresponds to the effect of all interactions between variables in $\vx_u$.
+$\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$ that is the effect of all interactions between variables in $\vx_u$.
 $\ov{$\tau$}_u^2$ quantifies the main effect of $\vx_u$ plus all interactions between variables in $\vx_u$ and variables in $\vx_{-u}$.
 
-These two measure satisfy the following relations: $ 0 \leq  \underline{\tau}_u^2 \leq \ov{$\tau$}_u^2$ and $\underline{\tau}_u^2 = \sigma^2 - \ov{$\tau$}_{-u}^2$.
+$\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ satisfy the following relations: $ 0 \leq  \underline{\tau}_u^2 \leq \ov{$\tau$}_u^2$ and $\underline{\tau}_u^2 = \sigma^2 - \ov{$\tau$}_{-u}^2$.
 These two measure are commonly found in the litterature in their normalized form: $\underline{S}_u = \underline{\tau}_u^2 / \sigma^2$ is the closed $|u|$-order Sobol' index for the set $u$, while $\ov{$S$}_u = \ov{$\tau$}_u^2 / \sigma^2$ is the total effect Sobol' index for the set $u$.
@@
 
-We focus here on the evaluation of first-order and total effect Sobol' indices. The computation of these indices is performed based on the following identities:
+The problem of interest here is the evaluation of first-order and total effect Sobol' indices. The computation of these indices is performed based on the following integral formula:
 \begin{align}
@@
 \label{total.effect}
-\ov{$\tau$}_u^2 &= \int_{[0,1)^{d+1}}f(\vx)^2-f(\vx)f({\vx'}_u:\vx_{-u})d\vx d{\vx'},
+\ov{$\tau$}_u^2 &= \int_{[0,1)^{d+1}}(f(\vx)-f({\vx'}_u:\vx_{-u}))^2d\vx d{\vx'},
 \end{align}
@@
 In such case, one needs to rely on an estimation of these quantities.
+In the following, we propose two iterative estimation procedures to evaluate first-order and total-effect Sobol' indices.
+
+\subsection{Estimation of Sobol' indices}
 
@@
 Each column of the design refers to a variable $x_j$.
-The strategy proposed by Sobol' to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
+Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid [0,1)^{2d}$.
+One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
 \begin{align}
-\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-\hat{\mu}^2,\\
-\widehat{\ov{$\tau$}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i)^2 - f(\vx_i)f({\vx'}_{i,u}:\vx_{i,-u}),
+\label{first.order.est}
+\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-\hat{\mu})(f(\vx_{i,u}:{\vx'}_{i,-u})-\hat{\mu}),\\
+\label{total.effect.est}
+\widehat{\ov{$\tau$}_u^2} & = \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f(\vx_i) - f({\vx'}_{i,u}:\vx_{i,-u}))^2,
 \end{align}
-where $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ are two designs and $(\vx_i,{\vx'}_i) \iid [0,1)^{2d}$.
+using for $\mu$ the efficient estimator introduced in \cite{Monod, Janon}:
+\[ \hat{\mu} = \frac{1}{2n} \sum \limits_{i=0}^{n-1} f(\vx_i) + f({\vx'}_{i,u}:\vx_{i,-u}). \]
 The estimation of a single pair ($\underline{\tau}_u^2$, $\ov{$\tau$}_u^2$) requires $3n$ evaluations of the model $f$.
-Using a combinatorial formalism, Saltelli \cite{Saltelli} proposed the following strategy to reduce the estimation cost:
+Using a combinatorial formalism, Saltelli \cite[Theorem 1]{Saltelli} proposed the following strategy to reduce the estimation cost:
 \begin{theorem}
@@
 \end{theorem}
-The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P'}$ in $\mathcal{P}$.
+The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ accordingly to subset $u$.
 While elegant, this approach still requires a number of model evaluations that grows linearly with respect to the input space dimension.
 
-An efficient alternative was proposed by Mara \textit{et al.} \cite{Mara} to evaluate all first-order indices with only $2n$ model evaluations.
-This alternative has been further deeply studied and generalized in Tissot
-et al. \cite{Mara} to the estimation of closed second-order indices. The estimation procedure introduced in \cite{Mara} relies on the construction of two replicated designs.
+An efficient alternative to evaluate all first-order indices was proposed by Mara \textit{et al.} \cite{Mara}  requiring only $2n$ model evaluations.
+This alternative relies on the construction of two replicated designs.
+The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes in \cite{Mckay}.
+The definition we give here introduce the structure in a wider context:
+\begin{definition}
+\label{rep.designs}
+Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
+$[0,1)^{d}$.
+Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp.
+${\mathcal{P}'}^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp.
+$\mathcal{P}'$) indexed by $u$.
+We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a$ if $\forall \ u \subsetneq \mathcal{D}$ of cardinality $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1)^a$.
+We note $\pi_u$ the permutation reordering the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
+\end{definition}
+The method introduced in \cite{Mara} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$.
+The key point of this method is to use the permutations resulting from the structure of the two replicated designs to mimic the hybrid points in formula (\ref{first.order.est}).
 
-\subsection{Two iterative estimation procedures}
+Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$.
+Denote by $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$.
+Consider $u \subsetneq \mathcal{D}$, from Definition \ref{rep.designs} there exists a permutation $\pi_u$ such that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$.
+Then, remark that $\forall i \in \{0,\dots,n-1\}$:
+\[\pi_u(f({\vx'}_i))=f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u})=f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u})\]
+%\pi_u(f({\vx'}_{i,u}:{\vx'}_{i,-u}))
+Hence, $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) with $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{\pi_u(f({\vx'}_i))\}_{i=0}^{n-1}$.
+This estimation method has been further studied and generalized in Tissot et al.
+\cite{Mara} to the case of closed second-order indices.
+\bigskip
 
-In this section we propose two iterative estimation procedures to evaluate first-order and total-effect Sobol' indices.
-The first procedure combine the strategy proposed by Saltelli with quasi-Monte Carlo sampling.
-The second is the procedure proposed by Mara
+\subsection{Iterative estimation procedures}
+We propose here two iterative procedures two estimate first-order and total effect Sobol' indices.
+Each procedure combines quasi-Monte Carlo sampling with respectively the estimation strategy proposed by Saltelli (Theorem \ref{saltelli.theorem}) and the estimation strategy based on replicated designs.
+In the following, we refer to these two iterative procedures as procedure $A$ and $B$.
+\bigskip
 
-The first approach is called multiplicative because $|P_\ell|=2^\ell$ while the second one with $|P_\ell|=\ell|B_0|$ is called additive.
-In the multiplicative case, we will directly use $2$ $s$-dimensional sequences as a result from Lemma \ref{Sobol_replicated}.
-However, for the additive case, we will consider an initial set of Sobol' points and apply different scramblings and digital shifts to extend the point sets.
-Additionally, in both cases one can randomize the points with Owen's scrambling \cite{OwenScrambling} as long as same coordinates of $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ share the same scrambling.
-
-$\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, based on Sobol' sequences. These two constructions are carried out according to the following recursive scheme :
+Both procedures require to iteratively construct two points sets $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$ that identify as two Sobol' sequences.
+Background on Sobol' sequences are provided in \cite{crass}.
+The construction of these two points sets is carried out according to the following recursive scheme :
 $$\left\lbrace \begin{array}{l}
 \mathcal{P}_0= B_0 \\
-\mathcal{P}_\ell= \mathcal{P}_{\ell-1} \cup B_\ell \end{array}\right. \,
+\mathcal{P}_\ell= \mathcal{P}_{\ell-1} \cup B_\ell \end{array}\right. ,\qquad
 \hspace*{0.5cm}
@@
 \mathcal{P}'_0= {B'}_0 \\
-\mathcal{P}'_\ell= \mathcal{P}'_{\ell-1} \cup {B'}_\ell \end{array}\right. 
+\mathcal{P}'_\ell= \mathcal{P}'_{\ell-1} \cup {B'}_\ell \end{array}\right.,
 $$
+where at step $\ell\geq0$, $B_\ell$ and $B'_\ell$ are new sets of $2^{\ell-1}$ points added to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$.
+In the following, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ refer to the two Sobol' sequences constructed following the multiplicative approach presented in \cite{crass}.
+This approach guarantee that at each step $\ell\geq0$, $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ are two replicated designs of order $1$.
 
-%where expressions for $\mu$ and $\sigma^2$ are taken as introduced in Janon \textit{et al.} \cite{Janon}:
-%\begin{align*}
-%\mu &= \frac{1}{2} \int_{[0,1)^{2d-1}}f(\vx)+f(\vx_u:{\vx'}_{-u}) d\vx d{\vx'}, \\
-%\sigma^2 &= \frac{1}{2} \int_{[0,1)^{2d-1}}(f(\vx)+f(\vx_u:{\vx'}_{-u}))^2 d\vx d{\vx'} - \mu^2.
-%\end{align*}
+$\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can either be used with procedure $A$ to estimate all first-order and all total effect Sobol' indices or with procedure $B$ to estimate all first-order Sobol' indices.
+Algorithms \ref{procedureA} and \ref{procedureB} summarize the main steps of each iterative estimation procedure.
+\begin{algorithm}[!ht]
+\caption{Iterative estimation: procedure $A$}
+\begin{algorithmic}[1]
+\vspace*{0.2cm}
+\State Set: $\ell \leftarrow 1$, $\mathcal{P}_{0} \leftarrow B_0$, ${\mathcal{P}'}_{0} \leftarrow {B'}_0$
+\While {stopping criterion}
+\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
+
+\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
+\For {$u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$}
+\State Construct design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=0}^{2^{\ell}-1}$
+\State Compute $\{f(\vx_i)\}_{i=0}^{2^\ell-1}$ and $\{f(\vx_{i,u},{\vx'}_{i,-u})\}_{i=0}^{2^\ell-1}$
+\State Estimate $\widehat{\underline{\tau}_u^2}$ and $\widehat{\ov{$\tau$}_u^2}$ with formula (\ref{first.order.est}) and (\ref{total.effect.est})
+\EndFor
+\State $\ell \leftarrow \ell + 1$
+\EndWhile
+\State Return $\widehat{\underline{\tau}_u^2}$ and $\widehat{\ov{$\tau$}_u^2}$ for all $u \in \mathcal{D}$.
+\end{algorithmic}
+\label{procedureA}
+\end{algorithm}
+\begin{algorithm}[!ht]
+\caption{Iterative estimation: procedure $B$}
+\begin{algorithmic}[1]
+\vspace*{0.2cm}
+\State Set: $\ell \leftarrow 1$, $\mathcal{P}_{0} \leftarrow B_0$, ${\mathcal{P}'}_{0} \leftarrow {B'}_0$
+\While {stopping criterion}
+\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
+
+\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
+\State Compute $\{f(\vx_i)\}_{i=0}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=0}^{2^\ell-1}$
+\For {$u \in \mathcal{D}$}
+\State  $\{f({\vx'}_i)\}_{i=0}^{2^\ell-1}$ into $\{\pi_u(f({\vx'}_i))\}_{i=0}^{2^\ell-1}$
+\State Estimate $\widehat{\underline{\tau}_u^2}$ with formula (\ref{first.order.est})
+\EndFor
+\State $\ell \leftarrow \ell + 1$
+\EndWhile
+\State Return $\widehat{\underline{\tau}_u^2}$ for all $u \in \mathcal{D}$.
+\end{algorithmic}
+\label{procedureB}
+\end{algorithm}
+
+The choice of the stopping criterion is the key point of this paper.
+In most iterative approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly from the estimates.
+For example, an absolute difference between estimates obtained on consecutive steps.
+Such stopping criteria are often hard to tweak but above all fail to guarantee any error bounds on the Sobol' indices.
+Our stopping criterion is presented and discussed in Section \ref{section.error}.
+The criterion is an error bound based on the discrete Walsh decomposition of the integral formula of the first-order and total effect Sobol' index.
+The formulation of this error bound makes use of the closed set property of Sobol' sequences.
 
 \subsection{Improvements}
-Cost small:\[n(d+1)+d_sn+n\]
-Cost pas small:\[\alpha n d_s +n+(d-d_s)n\]
-Cost small - cost pas small: \[n\sum_{i=1}^{s}(2-\alpha_i+1)\] $s$ number of small indices, $\alpha_i$ proportion of how many more points if not pas small
+This section provide two improvements to ease the estimation of Sobol' indices with procedures $A$ and $B$.
+The first improvement focus on the use of a better estimator to evaluate small first-order Sobol' indices with procedure $A$.
+The second improvement focus on the choice of the $2d$ generating matrices that generate the two Sobol' sequences $\mathcal{P}_\ell$  and ${\mathcal{P}'}_\ell$ in procedure $B$.
+
+\bigskip
+
+This estimator called ``Correlation 2" was introduced by Owen in \cite{Owen}.
+Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small closed Sobol' indices.
+Our aim is to show that using ``Correlation 2" to estimate small first-order Sobol' indices in procedure $A$  reduces the total number of model evaluations required while reaching the same accuracy on the estimates.
+
+Cost small: $n(d+1)+d_sn+n$
+
+Cost pas small: $\alpha n d_s +n+(d-d_s)n$
+
+Cost small - cost pas small: $n\sum_{i=1}^{s}(2-\alpha_i+1)$ $s$ number of small indices, $\alpha_i$ proportion of how many more points if not pas small
+\bigskip
+
+The choice of the $2d$ generating matrices that generate the two Sobol' sequences $\mathcal{P}_\ell$ and ${\mathcal{P}'}_\ell$ in the multiplicative approach \cite{crass}.
+These generating matrices are selected from the set found by Kuo and Joe in \cite{Kuo}.
+This set is composed of generating matrices that optimize the $2$-dimensional projection $t$-values.
+Elements of the set are ordered based on the best optimized $t$-values.
 
@@
 \section{Reliable Error Estimation for Cubatures}
+\label{section.error} 
 We assume that we have an algorithm $\widehat{I}(f;\varepsilon)$ such that $\abs{I(f)-\widehat{I}(f;\varepsilon)}\leq \varepsilon$.

### 2016-06-08 crass/crassnew.tex
crass + article changes

--- 2016-05-30 crass/crass.tex
@@
 Paris, Ser. I 340 (2005).}
-
 \end{abstract}
 \end{frontmatter}
-
 \selectlanguage{english}
-
 \section{Introduction}
@@
 \subsection{Preliminaries}
-
 Digital nets and sequences were first introduced by Niederreiter \cite{Niederreiter} in the numerical integration framework to define good uniformly distributed points in $\cube$.
@@
 \end{equation*}
+
 \bigskip
@@
 \end{lemma}
-\begin{pf*}{Proof.}
-Consider any two $s$-dimensional Sobol' sequences generated by $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$ respectively.
+\textit{Proof}: Consider any two $s$-dimensional Sobol' sequences generated by $C_1,\dots,C_s$ and $C'_1,\dots,C'_s$ respectively.
 Since any two matrices $C^{m}_j$ and ${C'}^{m}_j$ are square and full rank, the operations $\vi \mapsto C^{m}_j\vi$ and $\vi \mapsto {C'}^{m}_j\vi$ are one-to one and onto for all $i=0,\dots,2^m-1$.
 Therefore, they generate the same point sets.
-\end{pf*}
 
@@
 We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_\ell$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_\ell$.
-All these matrices need to be different.
-% Our choice of the $2s$ generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}.
-These two authors proposed a set of generating matrices optimized based on the $t$-value of pairwise projections of the corresponding digital sequence.
-Here, we select $2s$ generating matrices from this set to generate our two designs $\mathcal{P}$ and $\mathcal{P}'$.
+To insure that $2$-dimensional projections between $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other.
+Our choice of the $2s$ generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}.
 \bigskip
@@
 Given an initial choice of $r\geq 1$ that specifies the size of $B_0$ and ${B'}_0$, only $|B_0|=2^r$ points are added to both designs at each step.
-
 The main drawback of this approach is that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ do not possess the structure of a Sobol' sequence anymore when $m\geq 1$.
@@
 Each $B_\ell$ and ${B'}_\ell$ are $(t,r,s)$-nets.
-
 First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are set to be the first $2^r$ Sobol' points of two $s$-dimensional sequences.
+The generating matrices of these two sequences are selected as in the multiplicative approach.
 Then, $B_\ell$ (resp.
@@
 There are exactly $2^r$ different choices for vectors $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices for matrices $L$ and $L'$.
-
 The vectors $\ve_j$ (resp.
-${\ve}'_j$) are selected to guarantee that the set $\{\ve_1,\dots,\ve_s\}$ (resp.
-$\{{\ve}'_1,\dots,{\ve}'_s\}$) is different at each step $\ell$.
-There exists exactly $2^{r s}$ combinations of this set which leaves us with a large panel of choice.
-
-\bigskip
+${\ve}'_j$) are selected as follows:
+\begin{itemize}
+\item[i)] for the first coordinate, the same vector $\ve_1$ (resp. ${\ve}'_1$) is selected at each iteration $\ell$,
+\item[ii)] for the others coordinates, the vectors $\ve_2,\dots,\ve_s$ (resp.
+${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$.
+There exists exactly $2^{r (s-1)}$ combinations of this set which leaves us with a large panel of choice.
+\end{itemize}
 
@@
 \end{lemma}
-
-\begin{pf*}{Proof.}
-For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) are bijections from $\mathbb{F}^r_2$ to $\mathbb{F}^r_2$.
+\textit{Proof}:For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) are bijections from $\mathbb{F}^r_2$ to $\mathbb{F}^r_2$.
 Hence, same coordinates of $B_\ell$ and ${B'}_\ell$ will contain the same set of $2^r$ values.
-\end{pf*}
 
@@
 
-We denote by design $A$ (resp. design $B$) the design constructed with the multiplicative (resp. additive) approach. Values of maximin and discrepancy criteria are computed for designs $A$ and $B$.
-
-For design $A$, the design constructed is refined in four steps, starting from $2^8$ points.
+We denote by design $A$ (resp.
+design $B$) one of the two replicated designs constructed with the multiplicative (resp.
+additive) approach.
+Values of maximin and discrepancy criteria are computed for designs $A$ and $B$.
+For design $A$, the design constructed is refined until reaching $2^{12}$ points.
 For design $B$, we chose a starting value $r=8$ and refine the design $15$ times.
 To highlight the performance of design $B$, the results are compared to those obtained with a Latin Hypercube design.
-Average results over $100$ repeats are presented in Figure \ref{results.crit}.
-The x-axis represent the growing size of the design from $2^8$ points to $2^{12}$ points.
+Averaged results over $100$ repeats are presented in Figure \ref{results.crit}.
+The x-axis corresponds to the growing size of the designs from $2^8$ points to $2^{12}$ points.
 
 As expected design $A$ performs the best.
-However, we observe that design $B$ outperforms a classic Latin Hypercube design in both criteria while allowing $15$ construction steps instead of $4$ for design $A$.
+However, we observe that design $B$ outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points instead of $4$ steps for design $A$.
 
 \begin{figure}
+\caption{Averaged $L_2$ star discrepancy (left figure) and maximin (right figure) values for designs $A$ and $B$ over $100$ repeats.}
 \label{results.crit}
-\includegraphics[scale=0.43]{discrep.pdf}
+\centering
+\includegraphics[scale=0.4]{discrep.pdf}
 \hspace*{0.1cm}
-\includegraphics[scale=0.43]{mindist.pdf}
+\includegraphics[scale=0.4]{mindist.pdf}
 \end{figure}

### 2016-06-10 crass/crassnew.tex
Changes in crassnew.tex

@@
 % The amssymb package provides various useful mathematical symbols
-\usepackage{amsmath,amssymb}
+\usepackage{amsmath,amssymb,color}
 \usepackage{graphicx}
@@
 This method estimates sensitivity indices called Sobol' indices that summarize the influence of each model input.
-Among all Sobol' indices, one can distinguish first-order indices that estimate the main effect of each input.
+Among all Sobol' indices, one can distinguish the first-order indices that estimate the main effect of each input.
 
-The procedure proposed by Sobol' to estimate first-order Sobol' indices and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) all suffer from a prohibitive cost of model evaluations that grows with respect to the input space dimension.
+The procedure to estimate first-order Sobol' indices proposed by Sobol' and its improvements (see Saltelli \cite{Saltelli} for an exhaustive survey) all suffer from a prohibitive number of model evaluations that grows with respect to the input space dimension.
 %An elegant solution to reduce this cost relies on the construction of replicated designs introduced by McKay \cite{mckay}.
- An elegant solution to reduce this cost relies on the construction of particular designs of experiments called replicated designs.
-The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes in \cite{Mckay}.
-Below we define replicated designs in a wider framework:
+ An elegant solution to reduce this number relies on the construction of particular designs of experiments called replicated designs.
+The notion of replicated designs was first introduced by McKay through its definition of replicated Latin Hypercubes in \cite{Mckay}.
+Below we provide this definition in a more general framework:
 
@@
 \label{rep.designs}
-Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$ and $\mathcal{D}=\{1,\dots,s\}$.
-Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
-$[0,1)^{s}$.
-Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp.
-$\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp.
+Consider $\vx \in [0,1)^s$, and $\vx_u \in [0,1)^{s-|u|}$ the subset of dimensions of $\vx$ given by $u\subsetneq \{1,\dots,s\}$, where $|u|$ is the cardinality of $u$.
+Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1)^{s}$, and denote by $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp.
+$\mathcal{P}'^u$) the subset of dimensions of points in $\mathcal{P}$ (resp.
 $\mathcal{P}'$) indexed by $u$.
-We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a$ if $\forall \ u \subsetneq \mathcal{D}$ of cardinality $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
+We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a=1,\dots,s-1$, if for any $u\subsetneq \{1,\dots,s\}$ with $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
 \end{definition}
 
-The replication procedure introduced in \cite{Mara,Tissot} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$.
-This procedure has the major advantage of reducing the estimation cost as the number of model evaluations (one design $\mathcal{P}$ of size $n$  and its replication $\mathcal{P}'$) becomes independent of the input space dimension.
-However, Sobol' indices estimates may still not be accurate enough if the input space is not properly explored.
+The replication procedure described in \cite{Mara,Tissot} allows the estimation of all first-order Sobol' indices with only two replicated designs of order $1$.
+This procedure has the major advantage of reducing the number of model evaluations, evaluating only on designs $\mathcal{P}$ and $\mathcal{P}'$ regardless of the input space dimension.
+However, Sobol' indices estimates may still not be accurate enough if designs $\mathcal{P}$ and $\mathcal{P}'$ do not explore the input space properly.
 
@@
 
-In this note, we propose the construction of two replicated point sets based on Sobol' sequences that identify as two space-filling replicated designs of order $1$.
-These two designs ensure that the input space is properly explored and can be used within the replication procedure to estimate all main-effects of a numerical model.
-The construction of the two replicated designs is recursive, at each step each design is refined with a new set of points.
+In this note, we propose two different constructions of replicated designs of order $1$ based on Sobol' sequences.
+These two constructions ensure that the input space is properly explored and can be used within the replication procedure to estimate all first order Sobol' indices.
+The definition of these constructions is recursive, therefore one can iteratively refine the replicated designs by adding the corresponding new set of points.
 
 We first provide a brief introduction on digital sequences and then present two iterative approaches to construct the two replicated point sets.
-We end this note by studying the space-filling aspect of the two designs constructed.
+We end this note by analyzing the space-filling properties of the two designs constructed.
 
@@
 %The quality of any $(t,m,s)$-net or $(t,s)$-sequence is measured by $t$, called the $t$-value. The $t$-value is introduced in the $(t,m,s)$-net definition as follows:
-$(t,m,s)$-nets are defined as follows:
 
@@
 
-By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limit case where $m\rightarrow\infty$, we can define $(t,s)$-sequences as:
+By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limit case where $m\rightarrow\infty$, we can define the $(t,s)$-sequence as:
 \begin{definition}%[$(t,s)$-sequence]
@@
 
-Replicated design properties can apply to digital sequences. Therefore, we introduce the definition,
+The replicated design properties can also apply to digital sequences. Hence, we introduce the following definition,
 \begin{definition}
@@
 
-$s$-dimensional Sobol' sequences are digital sequences designed in base $b=2$ and can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over the Galois field $\mathbb{F}_2:=\{0,1\}$.
+$s$-dimensional Sobol' sequences are digital sequences in base $b=2$ that can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over the Galois field $\mathbb{F}_2:=\{0,1\}$.
 We will denote by $\oplus$ the addition in $\mathbb{F}_2$.
-These generating matrices are recursively constructed through primitive polynomials and initial directional numbers.
+These generating matrices are recursively constructed given some primitive polynomials and initial directional numbers.
 In \cite{Kuo}, Kuo and Joe detail this construction and also suggest a particular choice for these matrices that optimize the 2 dimensional projection $t$-values.
@@
 Consider the generating matrices $C_1,\dots,C_s$, and $C_1^m,\dots,C_s^m$ their upper left corner blocks of size $m\times m$.
-Although $C_1,\dots,C_s$ are of infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ points: for each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise by:
+Although $C_1,\dots,C_s$ are of infinite size, one only requires the knowledge of $C_1^m,\dots,C_s^m$ to construct the first $2^m$ Sobol' points: for each $i=0,\dots,2^m-1$, the point $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence is obtained dimension-wise by:
 \begin{equation}
@@
 All matrix operations are performed in $\mathbb{F}_2$.
-Below we provide an example on how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$,
+Below we provide an example of how to compute $x_{11,1}=0.8125$ and $x_{9,2}=0.4375$,
 \begin{equation*}
@@
 \end{pmatrix} = 
-\overbrace{
+\underbrace{
 \begin{pmatrix}
@@
 0 & 0 & 0 & 1
-\end{pmatrix}}^{C_1^4}
-\overbrace{
+\end{pmatrix}}_{C_1^4}
+\underbrace{
 \begin{pmatrix}
@@
 1
-\end{pmatrix}}^{\bvec{11}}=
+\end{pmatrix}}_{\bvec{11}}=
 \begin{pmatrix}
@@
 \end{pmatrix} = 
-\overbrace{\begin{pmatrix}
+\underbrace{\begin{pmatrix}
 1 & 1 & 1 & 1 \\
@@
 0 & 0 & 0 & 1
-\end{pmatrix}}^{C_2^4}
-\overbrace{\begin{pmatrix}
+\end{pmatrix}}_{C_2^4}
+\underbrace{\begin{pmatrix}
 1 \\
@@
 1
-\end{pmatrix}}^{\bvec{9}} =
+\end{pmatrix}}_{\bvec{9}} =
 \begin{pmatrix}
@@
 
-\bigskip
+%\bigskip
 
-To compute the next $2^m$ points of the sequence, one can infer from Equation (\ref{dig.net.eq.}) that \\$(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m+1})^\intercal=(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m},0)^\intercal\oplus {(c_j^{m+1})}^\intercal$, where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.
+To compute the next $2^m$ points of the sequence, one can infer from \eqref{dig.net.eq.} that
+\begin{equation}\label{Sobol_iter_constr}
+(x_{i+2^m,j,1},\dots,x_{i+2^m,j,m+1})^\intercal=(x_{i,j,1},\dots,x_{i,j,m},0)^\intercal\oplus {(c_j^{m+1})}^\intercal,\quad i=0,\dots,2^m-1,
+\end{equation}
+where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.
 
@@
 \mathcal{P}'_0= {B'}_0 \\
-\mathcal{P}'_\ell= \mathcal{P}'_{\ell-1} \cup {B'}_\ell \end{array}\right. 
+\mathcal{P}'_\ell= \mathcal{P}'_{\ell-1} \cup {B'}_\ell \end{array}\right. , 
+\hspace*{0.5cm} \ell \geq 1,
 $$
@@
 %$$\mathcal{P}'_m= {B'}_0 \cup \dots \cup {B'}_m\, ,$$
-where $B_\ell$ and $B'_\ell$, $\ell \geq 0$, are new sets of points added at step $\ell$ to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$.
-For all $\ell$, $\mathcal{P}_\ell$ and $\mathcal{P'}_\ell$ are two replicated designs of order $1$.
+where $B_\ell$ and $B'_\ell$ are new sets of points added at step $\ell$ to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$.
+For all $\ell\geq 0$, $\mathcal{P}_\ell$ and $\mathcal{P'}_\ell$ are two replicated designs of order $1$.
 
-The first approach is called multiplicative because $|P_\ell|=2^\ell$ while the second one with $|P_\ell|=\ell|B_0|$ is called additive.
+The first approach is called multiplicative because $|P_\ell|=2^\ell$ while the second one is called additive and $|P_\ell|=\ell|B_0|$.
 In the multiplicative case, we will directly use $2$ $s$-dimensional sequences as a result from Lemma \ref{Sobol_replicated}.
 However, for the additive case, we will consider an initial set of Sobol' points and apply different scramblings and digital shifts to extend the point sets.
-Additionally, in both cases one can randomize the points with Owen's scrambling \cite{OwenScrambling} as long as same coordinates of $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ share the same scrambling.
+Additionally, in both cases one can randomize the points using Owen's scrambling \cite{OwenScrambling} as long as same coordinates of $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ share the same scrambling.
 
@@
 
-Two replicated point sets of order 1 $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ can be constructed using two $s$-dimensional Sobol' sequences.
+Two replicated point sets of order 1, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, can be constructed using two $s$-dimensional Sobol' sequences.
 We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_\ell$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_\ell$.
-To insure that $2$-dimensional projections between $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other.
-Our choice of the $2s$ generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ follows the results obtained by Joe and Kuo in \cite{Kuo}.
+To ensure that the $2$-dimensional projections between $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other.
+Our choice of generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ is based on the results obtained by Joe and Kuo in \cite{Kuo}.
 \bigskip
 
-In order to recursively construct designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, one just needs to compute $B_\ell=\{\vx_{2^{\ell-1}},\dots,\vx_{2^\ell-1}\}$ and ${B'}_\ell=\{\vx'_{2^{\ell-1}},\dots,\vx'_{2^\ell-1}\}$ at each step $\ell \geq 1$ to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$, starting with $B_0=B'_0=\{\bvec{0}\}$ where $\bvec{0}$ denotes the null vector.
-Each set $B_\ell$ can be obtained applying equation (\ref{dig.net.eq.}) to $C_1,\dots,C_s$ and likewise for ${B'}_\ell$ using $C'_1,\dots,C'_s$.
+In order to iteratively extend designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, one just needs to compute $B_\ell=\{\vx_{2^{\ell-1}},\dots,\vx_{2^\ell-1}\}$ and ${B'}_\ell=\{\vx'_{2^{\ell-1}},\dots,\vx'_{2^\ell-1}\}$, starting with $B_0=B'_0=\{\bvec{0}\}$, with $\bvec{0}$ the null vector.
+Each set $B_\ell$ and ${B'}_\ell$ can be constructed using \eqref{Sobol_iter_constr} applied to $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$.
 
@@
 Given an initial choice of $r\geq 1$ that specifies the size of $B_0$ and ${B'}_0$, only $|B_0|=2^r$ points are added to both designs at each step.
-The main drawback of this approach is that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ do not possess the structure of a Sobol' sequence anymore when $m\geq 1$.
-Still, both designs display good space-filling properties as shown in the next section.
+The main drawback of this approach is that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ do not inherit the structure of a Sobol' sequence when $\ell\geq 1$.
+Nevertheless, both designs display good space-filling properties as shown in the next section.
 
@@
 
-The two replicated point sets $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ constructed with the additive approach are iteratively refined with $B_\ell$ and ${B'}_\ell$.
-Each $B_\ell$ and ${B'}_\ell$ are $(t,r,s)$-nets.
-First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are set to be the first $2^r$ Sobol' points of two $s$-dimensional sequences.
+Analogously to the multiplicative case, the two replicated point sets $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ constructed with the additive approach are iteratively refined with $B_\ell$ and ${B'}_\ell$.
+First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are set to be the first $2^r$ points of two $s$-dimensional Sobol' sequences.
 The generating matrices of these two sequences are selected as in the multiplicative approach.
@@
 ${B'}_0$) by carrying out digital shifts and scrambling operations.
-These operations guarantee that both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of the initial sets $B_0$ and ${B'}_0$.
-We detail below the construction of $B_\ell$ and ${B'}_\ell$.
+Therefore, both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of the initial sets $B_0$ and ${B'}_0$.
+%We detail below the construction of $B_\ell$ and ${B'}_\ell$.
 \bigskip
 
-At step $\ell$, $\ell \geq 1$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated as follows:
-
-for each $i=0,\dots,2^r-1$, points $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ are obtained by:
+At step $\ell$, $\ell \geq 1$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated as follows: for each $i=0,\dots,2^r-1$, point $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ is obtained by linearly transforming $\vx_i^{(0)}$,
 \begin{equation}
@@
 
-Likewise ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained as follows: 
+Likewise, ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained as follows: for each $i=0,\dots,2^r-1$, point ${\vx'}_i^{(\ell)} = ({x'}_{i,1}^{(\ell)},\dots,{x'}_{i,s}^{(\ell)})^\intercal$ is obtained by linearly transforming ${\vx'}_i^{(0)}$,
 %from $B_\ell$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows
 
-for each $i=0,\dots,2^r-1$, points ${\vx'}_i^{(\ell)} = ({x'}_{i,1}^{(\ell)},\dots,{x'}_{i,s}^{(\ell)})^\intercal$ are obtained by:
 \begin{equation}
@@
 
-The left multiplications carried out in Equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) by matrices $L$ and $L'$ are referred as random linear scrambling \cite{Matousek} while the additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts.
-There are exactly $2^r$ different choices for vectors $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices for matrices $L$ and $L'$.
-The vectors $\ve_j$ (resp.
+Left multiplications by matrices $L$ and $L'$ in \eqref{dig.shift} and \eqref{ibinom.scrambling}  are called linear scramblings \cite{Matousek} while additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts.
+There are exactly $2^r$ different choices of $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices of $L$ and $L'$ {\color{blue} although .......
+Because......., (I think it would be good to give the reason why a particular choice of $\ve_j$ needs to be made.
+Then, how)} vectors $\ve_j$ (resp.
 ${\ve}'_j$) are selected as follows:
 \begin{itemize}
-\item[i)] for the first coordinate, the same vector $\ve_1$ (resp. ${\ve}'_1$) is selected at each iteration $\ell$,
-\item[ii)] for the others coordinates, the vectors $\ve_2,\dots,\ve_s$ (resp.
+\item[i)] for the first dimension, the same vector $\ve_1$ (resp. ${\ve}'_1$) is selected at each iteration $\ell$,
+\item[ii)] for the other dimensions, vectors $\ve_2,\dots,\ve_s$ (resp.
 ${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$.
@@
 
-We have the following result:
+%We have the following result:
 %\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomized using the same Owen's scrambling column-wise.
@@
 \begin{lemma}
-Using the additive construction, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are two replicated designs of order $1$ for $\ell \geq 0$.
+Under the additive construction $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are two replicated designs of order $1$, $\ell \geq 0$.
 \end{lemma}
@@
 
-It has already been pointed out in the previous section that the two replicated designs constructed with the additive approach loose their $(t,m,s)$-net properties once a new set of points is added.
-Nonetheless, they still retain space-filling properties that combined with the low cost of the additive approach make their use appealing.
-We propose two study the space-filling properties of the two designs constructed with both approaches: multiplicative and additive, based on two criteria.
+%In the previous section we showed how two replicated designs constructed with the additive approach are not $(t,m,s)$-nets after refinement.
+Nonetheless, they still retain space-filling properties that combined with the low iterative growth make their use appealing.
 
-The first one is the $L_2$ star discrepancy that measures the uniformity of a points set.
-This criterion can easily be computed through an analytical expression \cite{Morokoff}.
-The lower the criterion, the more uniform the points set.
-Sobol' sequences were originally constructed to be low discrepancy sequences and so behave well with regards to this criterion.
-
-The second criterion is called maximin distance criterion and measures the regularity of a points set.
-It returns the minimum of distances between all pairs of a points set.
-The higher the criterion, the more spread the points set.
+To analyze the space-filling properties of both approaches we will use two criteria.
+The first one is the $L_2$ star discrepancy that measures the uniformity of a point set.
+This criterion can be easily computed through an analytical expression provided by \cite{Morokoff}.
+The lower the criterion, the more uniform the point set is.
+Sobol' sequences were originally constructed to be low discrepancy sequences and therefore, behave well under this criterion.
+The second criterion is called maximin distance and measures the regularity of a point set.
+It returns the minimum of all {\color{blue} euclidean?} distances between pairs of points in the set.
+The higher the criterion, the more spread the point set is.
 
@@
 
-We denote by design $A$ (resp.
-design $B$) one of the two replicated designs constructed with the multiplicative (resp.
-additive) approach.
-Values of maximin and discrepancy criteria are computed for designs $A$ and $B$.
-For design $A$, the design constructed is refined until reaching $2^{12}$ points.
-For design $B$, we chose a starting value $r=8$ and refine the design $15$ times.
-To highlight the performance of design $B$, the results are compared to those obtained with a Latin Hypercube design.
-Averaged results over $100$ repeats are presented in Figure \ref{results.crit}.
-The x-axis corresponds to the growing size of the designs from $2^8$ points to $2^{12}$ points.
+We name by $A$ (resp.
+$B$) one of the two replicated designs constructed with the multiplicative (resp.
+additive) approach {\color{blue} In which dimension?}.
+We also sampled {\color{blue} how?
+randomly?
+IID?
+the Sobol' seq is fixed, did you sample it?} $100$ designs of $A$ and $B$ whose average criteria are presented in Figure \ref{results.crit} below.
+Design $A$ is refined until $\ell=12$, and design $B$ is constructed with an initial value $r=8$ and refined 15 times {\color{blue} for each $B$, how are $L$ and $\ve_j$ chosen?}.
+The x-axis corresponds to the number of points of the design.
 
-As expected design $A$ performs the best.
-However, we observe that design $B$ outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points instead of $4$ steps for design $A$.
+As expected, design $A$ performs the best.
+However, we observe that design $B$ outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $A$.
 
 \begin{figure}
-\caption{Averaged $L_2$ star discrepancy (left figure) and maximin (right figure) values for designs $A$ and $B$ over $100$ repeats.}
+\caption{Averaged $L_2$ star discrepancy (left) and maximin (right) for designs $A$ and $B$ over $100$ repetitions.}
 \label{results.crit}

### 2016-06-10 crass/crassnew.tex
blue changes + graphs

@@
 In this note, we propose two different constructions of replicated designs of order $1$ based on Sobol' sequences.
-These two constructions ensure that the input space is properly explored and can be used within the replication procedure to estimate all first order Sobol' indices.
-The definition of these constructions is recursive, therefore one can iteratively refine the replicated designs by adding the corresponding new set of points.
+These two constructions ensure that the input space is properly explored and can be used within the replication procedure to estimate all first-order Sobol' indices.
+The definition of these constructions is recursive, therefore one can iteratively refine each replicated design by adding the corresponding new set of points.
 
@@
 Left multiplications by matrices $L$ and $L'$ in \eqref{dig.shift} and \eqref{ibinom.scrambling}  are called linear scramblings \cite{Matousek} while additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts.
-There are exactly $2^r$ different choices of $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices of $L$ and $L'$ {\color{blue} although .......
-Because......., (I think it would be good to give the reason why a particular choice of $\ve_j$ needs to be made.
-Then, how)} vectors $\ve_j$ (resp.
+There are exactly $2^r$ different choices of $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices of $L$ and $L'$.
+To guarantee that new points added will fill unexplored regions of the input space, the vectors $\ve_j$ (resp.
 ${\ve}'_j$) are selected as follows:
@@
 ${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$.
-There exists exactly $2^{r (s-1)}$ combinations of this set which leaves us with a large panel of choice.
+There exists exactly $2^{r (s-1)}$ combinations of this set.
+At each step $\ell$, one combination is sampled without replacement.
 \end{itemize}
-
+The maximum number of iterations $\ell$ that can be performed equals the number of combinations of the set $\{\ve_2,\dots,\ve_s\}$.
+If this maximum is reached, designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ both correspond to a full grid design of $2^{rs}$ points.
 %We have the following result:
@@
 The second criterion is called maximin distance and measures the regularity of a point set.
-It returns the minimum of all {\color{blue} euclidean?} distances between pairs of points in the set.
+It returns the minimum of all euclidean distances between pairs of points in the set.
 The higher the criterion, the more spread the point set is.
@@
 $B$) one of the two replicated designs constructed with the multiplicative (resp.
-additive) approach {\color{blue} In which dimension?}.
-We also sampled {\color{blue} how?
-randomly?
-IID?
-the Sobol' seq is fixed, did you sample it?} $100$ designs of $A$ and $B$ whose average criteria are presented in Figure \ref{results.crit} below.
-Design $A$ is refined until $\ell=12$, and design $B$ is constructed with an initial value $r=8$ and refined 15 times {\color{blue} for each $B$, how are $L$ and $\ve_j$ chosen?}.
-The x-axis corresponds to the number of points of the design.
+additive) approach.
+We set the input space dimension $s$ equals to $6$.
+We also sampled $100$ designs of $A$ and $B$ whose average criteria are presented in Figure \ref{results.crit}.
+Each of the $100$ designs $A$ is independently randomized by applying Owen's scrambling.
+Each of the $100$ designs $B$ is sampled by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and by selecting the vectors $\ve_j$ following steps i) and ii).
+Design $A$ is refined until $\ell=12$, and design $B$ is constructed with an initial value $r=8$ and refined 15 times.
+The x-axis corresponds to the number of points $N$ of the design.
+THe y-axis corresponds to the value of the criterion.
+Logarithmic scale is used for both axis.
 
-As expected, design $A$ performs the best.
+As expected, design $A$ performs the best and the estimated slope of the discrepancy curve ($-0.67$) falls within the expected range for Sobol' sequences \cite{Morokoff}.
 However, we observe that design $B$ outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $A$.
@@
 \begin{figure}
-\caption{Averaged $L_2$ star discrepancy (left) and maximin (right) for designs $A$ and $B$ over $100$ repetitions.}
+\caption{Log-log graph of averaged $L_2$ star discrepancy (left) and maximin (right) for designs $A$ and $B$ over $100$ repetitions.}
 \label{results.crit}

### 2016-06-10 article.tex
changes article.tex: annesection 1 + annexe

@@
 using for $\mu$ the efficient estimator introduced in \cite{Monod, Janon}:
-\[ \hat{\mu} = \frac{1}{2n} \sum \limits_{i=0}^{n-1} f(\vx_i) + f({\vx'}_{i,u}:\vx_{i,-u}). \]
+\begin{equation}
+ \hat{\mu} = \frac{1}{2n} \sum \limits_{i=0}^{n-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}).
+\label{mu.est}
+\end{equation}
 The estimation of a single pair ($\underline{\tau}_u^2$, $\ov{$\tau$}_u^2$) requires $3n$ evaluations of the model $f$.
@@
 
-\subsection{Iterative estimation procedures}
-We propose here two iterative procedures two estimate first-order and total effect Sobol' indices.
+\subsection{Recursive estimation procedures}
+We propose here two recursive procedures two estimate first-order and total effect Sobol' indices.
 Each procedure combines quasi-Monte Carlo sampling with respectively the estimation strategy proposed by Saltelli (Theorem \ref{saltelli.theorem}) and the estimation strategy based on replicated designs.
-In the following, we refer to these two iterative procedures as procedure $A$ and $B$.
+In the following, we refer to these two procedures as procedure $A$ and $B$.
 \bigskip
 
-Both procedures require to iteratively construct two points sets $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$ that identify as two Sobol' sequences.
+Using a recursive estimation procedure requires to write a recursive formula for estimators (\ref{first.order.est}) and (\ref{total.effect.est}).
+For the sake of readability of the paper, the corresponding recursive formulas are detailed in equations (\ref{first.order.est.rec}) and (\ref{total.effect.est.rec}) in the Annexe.
+
+Procedures $A$ and $B$ also require to iteratively construct two designs $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$.
+These two designs are two Sobol' sequences.
 Background on Sobol' sequences are provided in \cite{crass}.
-The construction of these two points sets is carried out according to the following recursive scheme :
-$$\left\lbrace \begin{array}{l}
+The construction of $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ is carried out according to the following recursive scheme :
+\begin{equation}
+\left\lbrace \begin{array}{l}
 \mathcal{P}_0= B_0 \\
@@
 \mathcal{P}'_\ell= \mathcal{P}'_{\ell-1} \cup {B'}_\ell \end{array}\right.,
-$$
+\label{rec.scheme}
+\end{equation}
 where at step $\ell\geq0$, $B_\ell$ and $B'_\ell$ are new sets of $2^{\ell-1}$ points added to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$.
@@
 $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can either be used with procedure $A$ to estimate all first-order and all total effect Sobol' indices or with procedure $B$ to estimate all first-order Sobol' indices.
-Algorithms \ref{procedureA} and \ref{procedureB} summarize the main steps of each iterative estimation procedure.
+Algorithms \ref{procedureA} and \ref{procedureB} summarize the main steps of each recursive estimation procedure.
 \begin{algorithm}[!ht]
-\caption{Iterative estimation: procedure $A$}
+\caption{Procedure $A$}
 \begin{algorithmic}[1]
@@
 \State Compute $\{f(\vx_i)\}_{i=0}^{2^\ell-1}$ and $\{f(\vx_{i,u},{\vx'}_{i,-u})\}_{i=0}^{2^\ell-1}$
-\State Estimate $\widehat{\underline{\tau}_u^2}$ and $\widehat{\ov{$\tau$}_u^2}$ with formula (\ref{first.order.est}) and (\ref{total.effect.est})
+\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ with formula (\ref{first.order.est}) and (\ref{total.effect.est})
 \EndFor
@@
 \EndWhile
-\State Return $\widehat{\underline{\tau}_u^2}$ and $\widehat{\ov{$\tau$}_u^2}$ for all $u \in \mathcal{D}$.
+\State Return $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ for all $u \in \mathcal{D}$.
 \end{algorithmic}
@@
 \begin{algorithm}[!ht]
-\caption{Iterative estimation: procedure $B$}
+\caption{Procedure $B$}
 \begin{algorithmic}[1]
@@
 \State  $\{f({\vx'}_i)\}_{i=0}^{2^\ell-1}$ into $\{\pi_u(f({\vx'}_i))\}_{i=0}^{2^\ell-1}$
-\State Estimate $\widehat{\underline{\tau}_u^2}$ with formula (\ref{first.order.est})
+\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ with formula (\ref{first.order.est})
 \EndFor
@@
 \EndWhile
-\State Return $\widehat{\underline{\tau}_u^2}$ for all $u \in \mathcal{D}$.
+\State Return $\widehat{\underline{\tau}_u^2}^{(\ell)}$ for all $u \in \mathcal{D}$.
 \end{algorithmic}
@@
 The choice of the stopping criterion is the key point of this paper.
-In most iterative approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly from the estimates.
-For example, an absolute difference between estimates obtained on consecutive steps.
-Such stopping criteria are often hard to tweak but above all fail to guarantee any error bounds on the Sobol' indices.
+In most recursive approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly from the estimates.
+For example, an absolute difference between estimates computed on consecutive steps.
+Such stopping criteria are often hard to tweak but above all fail to guarantee any error bounds on the estimation.
 Our stopping criterion is presented and discussed in Section \ref{section.error}.
-The criterion is an error bound based on the discrete Walsh decomposition of the integral formula of the first-order and total effect Sobol' index.
-The formulation of this error bound makes use of the closed set property of Sobol' sequences.
+The criterion is an error bound based on the discrete Walsh decomposition of the integral formulas of first-order and total effect Sobol' indices.
 
 \subsection{Improvements}
-This section provide two improvements to ease the estimation of Sobol' indices with procedures $A$ and $B$.
-The first improvement focus on the use of a better estimator to evaluate small first-order Sobol' indices with procedure $A$.
-The second improvement focus on the choice of the $2d$ generating matrices that generate the two Sobol' sequences $\mathcal{P}_\ell$  and ${\mathcal{P}'}_\ell$ in procedure $B$.
+This section discusses two improvements to ease the estimation of Sobol' indices with procedures $A$ and $B$.
 
@@
 
-This estimator called ``Correlation 2" was introduced by Owen in \cite{Owen}.
+The first improvement focus on the use of a better estimator to evaluate small first-order Sobol' indices with procedure $A$.
+This estimator is called ``Correlation 2" and was introduced by Owen in \cite{Owen}.
 Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small closed Sobol' indices.
-Our aim is to show that using ``Correlation 2" to estimate small first-order Sobol' indices in procedure $A$  reduces the total number of model evaluations required while reaching the same accuracy on the estimates.
+
+Our aim is to show that using ``Correlation 2" in procedure $A$ may reduces the total number of model evaluations required while reaching the same accuracy on the estimates.
 
@@
 Cost small - cost pas small: $n\sum_{i=1}^{s}(2-\alpha_i+1)$ $s$ number of small indices, $\alpha_i$ proportion of how many more points if not pas small
+
 \bigskip
 
-The choice of the $2d$ generating matrices that generate the two Sobol' sequences $\mathcal{P}_\ell$ and ${\mathcal{P}'}_\ell$ in the multiplicative approach \cite{crass}.
-These generating matrices are selected from the set found by Kuo and Joe in \cite{Kuo}.
+The second improvement focus on the choice of the $2d$ generating matrices that generate the two Sobol' sequences $\mathcal{P}_\ell$  and ${\mathcal{P}'}_\ell$ in procedure $B$.
+
+In the multiplicative approach \cite{crass}, these $2d$ generating matrices are selected as the first $2d$ elements of the set found by Kuo and Joe in \cite{Kuo}.
 This set is composed of generating matrices that optimize the $2$-dimensional projection $t$-values.
-Elements of the set are ordered based on the best optimized $t$-values.
+For procedure $A$ this choice of these $2d$ generating matrices is logical.
+Each of the $d+2$ designs constructed following Theorem \ref{saltelli.theorem} is a Sobol' sequence generated by a subset of $d$ matrices among the initial $2d$ ones.
+Therefore, $2$-dimensional projection $t$-values are not changed.
+
+That is not the case for procedure $B$.
+(introduire les matrices $C_j$ et ecrire les relations).
+The permutations applied in step $6$ of Algorithm \ref{procedureB} modify the $2$-dimensional projection $t$-values of the underlying designs.
 
@@
 
+\newpage
+\section{Annexe: recursive formulas}
+
+Let $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$ be the two points sets constructed with the recursive scheme (\ref{rec.scheme}).
+
+\subsection{Recursive formula for $\hat{\mu}$}
+
+The quantity $\hat{\mu}$ defined by formula (\ref{mu.est}) can be recursively estimated by:
+\[\left \lbrace\begin{array}{l}
+\hat{\mu}^{(0)} = \dfrac{1}{2} \Big{(} f(\vx_0)+f(\vx_{0,u}:{\vx'}_{0,-u}) \Big{)} \\
+\\
+\hat{\mu}^{(\ell+1)} = \dfrac{1}{2} \Big{(} \hat{\mu}^{(\ell)} + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}
+\end{array}\right.\]
+\begin{proof}
+By developing $\hat{\mu}^{(\ell+1)}$:
+\begin{align*}
+\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \\
+\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \Big{(} \sum \limits_{i=0}^{2^{\ell}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
+\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \Big{(} 2 \times 2^{\ell}\hat{\mu}^{(\ell)} + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
+\end{align*}
+\end{proof}
+
+\subsection{Recursive formula for $\widehat{\underline{\tau}_u^2}$}
+
+The quantity $\widehat{\underline{\tau}_u^2}$ defined by formula (\ref{first.order.est}) can be recursively estimated by:
+\begin{equation}
+\left\lbrace \begin{array}{l}
+\widehat{\underline{\tau}_u^2}^{(0)}= (f(\vx_0)-\hat{\mu}^{(0)})(f(\vx_{0,u}:{\vx'}_{0,-u})-\hat{\mu}^{(0)}) \\
+\\
+\widehat{\underline{\tau}_u^2}^{(\ell+1)} =  \dfrac{1}{2} \widehat{\underline{\tau}_u^2}^{(\ell)} - \dfrac{1}{2} (\hat{\mu}^{(\ell)})^2 - (\hat{\mu}^{(\ell+1)})^2 + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}+1}^{2^{\ell+1}-1} f(\vx_i) f(\vx_{i,u}:{\vx'}_{i,-u})
+\end{array}\right.
+\label{first.order.est.rec}
+\end{equation}
+\begin{proof}
+By developing $\widehat{\underline{\tau}_u^2}^{(\ell+1)}$:
+\begin{align*}
+\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} (f(\vx_i)-\hat{\mu}^{(\ell+1)})(f(\vx_{i,u}:{\vx'}_{i,-u})-\hat{\mu}^{(\ell+1)}) \\
+\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(\ell+1)})^2 \\
+\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \Big{(}\sum \limits_{i=0}^{2^{\ell}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})\Big{)} -(\hat{\mu}^{(\ell+1)})^2 \\
+\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \dfrac{1}{2}\Big{(}\widehat{\underline{\tau}_u^2}^{(\ell)}-(\hat{\mu}^{(\ell)})^2\Big{)} + \frac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(\ell+1)})^2 \\
+\end{align*}
+\end{proof}
+
+\subsection{Recursive formula for} 
+%$\widehat{\ov{$\tau$}_u^2}$}
+
+The quantity $\widehat{\underline{\tau}_u^2}$ defined by formula (\ref{total.effect.est}) can be recursively estimated by:
+\begin{equation}
+\left\lbrace \begin{array}{l}
+\widehat{\ov{$\tau$}_u^2}^{(0)}= \dfrac{1}{2} \Big{(} f(\vx_0)-(f({\vx'}_{0,u}:\vx_{0,-u}) \Big{)}^2 \\
+\\
+\widehat{\ov{$\tau$}_u^2}^{(\ell+1)} = \dfrac{1}{2} \widehat{\ov{$\tau$}_u^2}^{(\ell)} + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}+1}^{2^{\ell+1}-1} \Big{(}f(\vx_i)- f({\vx'}_{i,u}:\vx_{i,-u})\Big{)}^2
+\end{array}\right.
+\label{total.effect.est.rec}
+\end{equation}
+\begin{proof}
+Straightforward by developing $\widehat{\ov{$\tau$}_u^2}^{(\ell+1)}$.
+\end{proof}
+
 \end{document}

### 2016-06-10 crass/crassnew.tex
modifications section 4

@@
 
-We name by $A$ (resp.
+We name by design $A$ (resp.
 $B$) one of the two replicated designs constructed with the multiplicative (resp.
@@
 We set the input space dimension $s$ equals to $6$.
-We also sampled $100$ designs of $A$ and $B$ whose average criteria are presented in Figure \ref{results.crit}.
+Design $A$ is refined until $\ell=12$, and design $B$ is constructed with an initial value $r=8$ and refined 15 times.
+We construct $100$ designs $A$ and $B$ whose average criteria are presented in Figure \ref{results.crit}.
 Each of the $100$ designs $A$ is independently randomized by applying Owen's scrambling.
-Each of the $100$ designs $B$ is sampled by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and by selecting the vectors $\ve_j$ following steps i) and ii).
-Design $A$ is refined until $\ell=12$, and design $B$ is constructed with an initial value $r=8$ and refined 15 times.
+Each of the $100$ designs $B$ is constructed by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and by selecting the vectors $\ve_j$ following steps i) and ii).
+We also represent  in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points of design $B$.
 The x-axis corresponds to the number of points $N$ of the design.
-THe y-axis corresponds to the value of the criterion.
-Logarithmic scale is used for both axis.
+The y-axis corresponds to the value of the criterion.
+A logarithmic scale is used for both axis.
 
@@
 However, we observe that design $B$ outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $A$.
-
 \begin{figure}

### 2016-06-10 crass/crassnew.tex
changes vectors e_j

@@
 % The amssymb package provides various useful mathematical symbols
-\usepackage{amsmath,amssymb,color}
+\usepackage{amsmath,amssymb}
 \usepackage{graphicx}
@@
 There are exactly $2^r$ different choices of $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices of $L$ and $L'$.
-To guarantee that new points added will fill unexplored regions of the input space, the vectors $\ve_j$ (resp.
+To guarantee that new points added will fill unexplored regions of the input space, vectors $\ve_j$ (resp.
 ${\ve}'_j$) are selected as follows:
 \begin{itemize}
-\item[i)] for the first dimension, the same vector $\ve_1$ (resp. ${\ve}'_1$) is selected at each iteration $\ell$,
+\item[i)] for the first dimension, the same vector $\ve_1=(0,\dots,0)$ (resp. ${\ve}'_1=(0,\dots,0)$) is selected at each iteration $\ell$,
 \item[ii)] for the other dimensions, vectors $\ve_2,\dots,\ve_s$ (resp.
-${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$.
+${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$ and different from $\{\ve_1,\dots,\ve_1\}$.
 There exists exactly $2^{r (s-1)}$ combinations of this set.
@@
 additive) approach.
-We set the input space dimension $s$ equals to $6$.
+We set the input space dimension $s$ to $6$.
 Design $A$ is refined until $\ell=12$, and design $B$ is constructed with an initial value $r=8$ and refined 15 times.
@@
 We also represent  in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points of design $B$.
-The x-axis corresponds to the number of points $N$ of the design.
+The x-axis corresponds to the number of points N of the design.
 The y-axis corresponds to the value of the criterion.
@@
 As expected, design $A$ performs the best and the estimated slope of the discrepancy curve ($-0.67$) falls within the expected range for Sobol' sequences \cite{Morokoff}.
-However, we observe that design $B$ outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $A$.
+Although design $B$ does not perform as well as design $A$, it outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $A$.
 \begin{figure}

### 2016-06-13 crass/crassnew.tex
changes choice vectors e_j

@@
 Analogously to the multiplicative case, the two replicated point sets $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ constructed with the additive approach are iteratively refined with $B_\ell$ and ${B'}_\ell$.
-First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are set to be the first $2^r$ points of two $s$-dimensional Sobol' sequences.
+%First, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are set to be the first $2^r$ points of two $s$-dimensional Sobol' sequences.
+First $\{\vx_i\}_{i=0}^{2^r-1}$ and $\{{\vx'}_i\}_{i=0}^{2^r-1}$ are set to be the first $2^r$ points of two $s$-dimensional Sobol' sequences.
 The generating matrices of these two sequences are selected as in the multiplicative approach.
 Then, $B_\ell$ (resp.
-${B'}_\ell$), for $\ell \geq 1$, is obtained from $B_0$ (resp.
-${B'}_0$) by carrying out digital shifts and scrambling operations.
-Therefore, both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of the initial sets $B_0$ and ${B'}_0$.
+${B'}_\ell$), for $\ell \geq 0$, is obtained from $\{\vx_i\}_{i=0}^{2^r-1}$ (resp.
+$\{{\vx'}_i\}_{i=0}^{2^r-1}$) by carrying out digital shifts and scrambling operations.
+Therefore, both $B_\ell$ and ${B'}_\ell$ inherit the $(t,r,s)$-net structure of these initial sets.
 %We detail below the construction of $B_\ell$ and ${B'}_\ell$.
@@
 
-At step $\ell$, $\ell \geq 1$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated as follows: for each $i=0,\dots,2^r-1$, point $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ is obtained by linearly transforming $\vx_i^{(0)}$,
+At step $\ell$, $\ell \geq 0$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated as follows: for each $i=0,\dots,2^r-1$, point $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ is obtained by linearly transforming $\vx_i$,
 \begin{equation}
 \label{dig.shift}
-(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = L (x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
+(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = L (x_{i,j,1},\dots,x_{i,j,r})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
 \end{equation}
@@
 Likewise, ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained as follows: for each $i=0,\dots,2^r-1$, point ${\vx'}_i^{(\ell)} = ({x'}_{i,1}^{(\ell)},\dots,{x'}_{i,s}^{(\ell)})^\intercal$ is obtained by linearly transforming ${\vx'}_i^{(0)}$,
-%from $B_\ell$ by applying Tezuka's i-binomial scrambling \cite{Tezuka}. This scrambling operation writes as follows
-
 \begin{equation}
 \label{ibinom.scrambling}
-({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = {L'} ({x'}_{i,j,1}^{(0)},\dots,{x'}_{i,j,r}^{(0)})^\intercal\oplus {\ve'}_j,\qquad j= 1,\dots,s\, ,
+({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = {L'} ({x'}_{i,j,1},\dots,{x'}_{i,j,r})^\intercal\oplus {\ve'}_j,\qquad j= 1,\dots,s\, ,
 \end{equation}
@@
 There are exactly $2^r$ different choices of $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices of $L$ and $L'$.
-To guarantee that new points added will fill unexplored regions of the input space, vectors $\ve_j$ (resp.
-${\ve}'_j$) are selected as follows:
+To guarantee that new points added will fill unexplored regions of the input space, the vectors $\ve_j$ are selected as follows:
 \begin{itemize}
-\item[i)] for the first dimension, the same vector $\ve_1=(0,\dots,0)$ (resp. ${\ve}'_1=(0,\dots,0)$) is selected at each iteration $\ell$,
-\item[ii)] for the other dimensions, vectors $\ve_2,\dots,\ve_s$ (resp.
+\item[i)] at iteration $\ell=0$, the vectors $\ve_j$ are all equal to the zero of $\mathbb{F}_2^r$,
+\item[ii)] for $\ell \geq1$, we use the following result:
+$(B_0,\oplus)$ is a subgroup in $\mathbb{F}_2^{rs}$.
+From Lagrange's Theorem, the left cosets $\ve \oplus B_0$, $\ve \in \mathbb{F}_2^{rs}$, form a partition of $\mathbb{F}_2^{rs}$.
+At iteration $\ell \geq1$, we select $\ve \in \mathbb{F}_2^{rs}$ such that $\ve \oplus B_0$ is a left coset different from $\{B_0,\dots,B_{\ell-1}\}$.
+Then, the vectors $\ve_j$ are extracted from $\ve=(\ve_1,\dots,\ve_s)$.
+By identification we have $B_{\ell}=\ve \oplus B_0$ ensuring that the new points added are all different.
+
+%\item[i)] for the first dimension, the same vector $\ve_1=(0,\dots,0)$ (resp. ${\ve}'_1=(0,\dots,0)$) is selected at each iteration $\ell$,
+%\item[ii)] for the other dimensions, vectors $\ve_2,\dots,\ve_s$ (resp.
 ${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$ and different from $\{\ve_1,\dots,\ve_1\}$.
@@
 \end{itemize}
-The maximum number of iterations $\ell$ that can be performed equals the number of combinations of the set $\{\ve_2,\dots,\ve_s\}$.
+The same reasoning is made with $({B'}_0,\oplus)$ to select the vectors $\ve'_j$.
+The maximum number of iterations $\ell$ that can be performed equals the number of unique left cosets that is $2^{s}$.
 If this maximum is reached, designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ both correspond to a full grid design of $2^{rs}$ points.

### 2016-06-13 crass/crassnew.tex
Solving conflicts changes choice vectors e_j
Revert "Merge branch 'master' of https://github.com/fjhickernell/SobolIndices"
This reverts commit cbdb7ad57a772cf1e429b2c5c10c103e85a7da9a, reversing
changes made to 5d6d73d7005a6f882b5cd52485642ae80295075b.
Revert "changes vectors e_j"
This reverts commit de9a54ecb6a39d0b851b7457804889c4fb70baf7.

--- 2016-06-10 crass/crassnew.tex
@@
 \begin{itemize}
-\item[i)] for the first dimension, the same vector $\ve_1=(0,\dots,0)$ (resp. ${\ve}'_1=(0,\dots,0)$) is selected at each iteration $\ell$,
+\item[i)] for the first dimension, the same vector $\ve_1$ (resp. ${\ve}'_1$) is selected at each iteration $\ell$,
 \item[ii)] for the other dimensions, vectors $\ve_2,\dots,\ve_s$ (resp.
-${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$ and different from $\{\ve_1,\dots,\ve_1\}$.
+${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$.
 There exists exactly $2^{r (s-1)}$ combinations of this set.
@@
 We also represent  in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points of design $B$.
-The x-axis corresponds to the number of points N of the design.
+The x-axis corresponds to the number of points $N$ of the design.
 The y-axis corresponds to the value of the criterion.

### 2016-06-13 crass/crassnew.tex
Changes crassnew.tex, additive method, choice of shift

--- 2016-06-13 crass/crassnew.tex
@@
 \begin{itemize}
-\item[i)] at iteration $\ell=0$, the vectors $\ve_j$ are all equal to the zero of $\mathbb{F}_2^r$,
+\item[i)] at iteration $\ell=0$, vectors $\ve_j$ are all equal to the zero of $\mathbb{F}_2^r$,
 \item[ii)] for $\ell \geq1$, we use the following result:
-$(B_0,\oplus)$ is a subgroup in $\mathbb{F}_2^{rs}$.
-From Lagrange's Theorem, the left cosets $\ve \oplus B_0$, $\ve \in \mathbb{F}_2^{rs}$, form a partition of $\mathbb{F}_2^{rs}$.
-At iteration $\ell \geq1$, we select $\ve \in \mathbb{F}_2^{rs}$ such that $\ve \oplus B_0$ is a left coset different from $\{B_0,\dots,B_{\ell-1}\}$.
-Then, the vectors $\ve_j$ are extracted from $\ve=(\ve_1,\dots,\ve_s)$.
-By identification we have $B_{\ell}=\ve \oplus B_0$ ensuring that the new points added are all different.
+$(B_0,\oplus)$ is a subgroup of $\left(\mathbb{F}_2^{r}\right)^{s}$.
+From Lagrange's Theorem, we can construct cosets $B_\ell$ as $B_0 \oplus \ve$, $\ve=(\ve_1,\dots,\ve_s) \in \left(\mathbb{F}_2^{r}\right)^{s}$
+%, which form a partition of $\left(\mathbb{F}_2^{r}\right)^{s}$
+.
+At iteration $\ell \geq1$, we select $\ve$ such that $B_0 \oplus \ve$ is a new coset different from $\{B_0,\dots,B_{\ell-1}\}$, and it will be enough to choose $\ve\notin\mathcal{P}_{\ell-1}$.
+By identification we have $B_{\ell}=B_0 \oplus \ve$ ensuring that the new points added are all different.
 
@@
 \end{itemize}
-The same reasoning is made with $({B'}_0,\oplus)$ to select the vectors $\ve'_j$.
-The maximum number of iterations $\ell$ that can be performed equals the number of unique left cosets that is $2^{s}$.
+The same reasoning to select vectors $\ve'_j$ is made for $({B'}_0,\oplus)$.
+The maximum number of iterations $\ell$ that can be performed equals the number of cosets, $2^{s}$.
 If this maximum is reached, designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ both correspond to a full grid design of $2^{rs}$ points.

### 2016-06-13 crass/crassnew.tex
Adding the choice of shift e for additive approach

@@
 .
-At iteration $\ell \geq1$, we select $\ve$ such that $B_0 \oplus \ve$ is a new coset different from $\{B_0,\dots,B_{\ell-1}\}$, and it will be enough to choose $\ve\notin\mathcal{P}_{\ell-1}$.
-By identification we have $B_{\ell}=B_0 \oplus \ve$ ensuring that the new points added are all different.
+At iteration $\ell \geq1$, we select $\ve$ such that $B_{\ell}=B_0 \oplus \ve$ is a new coset different from $\{B_0,\dots,B_{\ell-1}\}$.
+It will be enough to choose $\ve$ such that $\ve\notin\mathcal{P}_{\ell-1}$.
+%By identification we have $B_{\ell}=B_0 \oplus \ve$ ensuring that the new points added are all different.
 

### 2016-06-14 crass/crassnew.tex
Big changes in definition of oplus and algo additive approach

--- 2016-06-13 crass/crassnew.tex
@@
 
+Each
+
 \subsection{Sobol' sequences}
 
-$s$-dimensional Sobol' sequences are digital sequences in base $b=2$ that can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over the Galois field $\mathbb{F}_2:=\{0,1\}$.
-We will denote by $\oplus$ the addition in $\mathbb{F}_2$.
+Sobol' sequences in dimension $s$ are digital sequences in base $b=2$ that can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over the Galois field $\mathbb{F}_2:=\{0,1\}$.
+%We will denote by $\oplus$ the addition in $\mathbb{F}_2$.
 These generating matrices are recursively constructed given some primitive polynomials and initial directional numbers.
@@
 where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.
+
+Sobol' sequences also have good group structure properties. For any $m\geq 1$, the first $2^m$ points of the sequence form an Abelian group under the following operation $\oplus$,
+\begin{gather*}
+\vx = \left(\sum_{k=1}^m x_{1,k}2^{-k},\dots,\sum_{k=1}^m x_{s,k}2^{-k}\right)^\intercal\; , \qquad \vz = \left(\sum_{k=1}^m z_{1,k}2^{-k},\dots,\sum_{k=1}^m z_{s,k}2^{-k}\right)^\intercal, \\
+\vx\oplus\vz := \left(\sum_{k=1}^m (x_{1,k}+z_{1,k}\mod 2)2^{-k},\dots,\sum_{k=1}^m (x_{s,k}+z_{s,k}\mod 2)2^{-k}\right)^\intercal.
+\end{gather*}
 
@@
 
-At step $\ell$, $\ell \geq 0$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated as follows: for each $i=0,\dots,2^r-1$, point $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ is obtained by linearly transforming $\vx_i$,
-\begin{equation}
-\label{dig.shift}
-(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = L (x_{i,j,1},\dots,x_{i,j,r})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
-\end{equation}
-where $ x_{i,j}^{(\ell)}=\sum_{k = 1}^r x_{i,j,k}^{(\ell)}2^{-k}$, $\ve_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and $L$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
-\bigskip
+%At step $\ell$, $\ell \geq 0$, $B_\ell=\{\vx_i^{(\ell)}\}_{i=0}^{2^r-1}$ is generated as follows: for each $i=0,\dots,2^r-1$, point $\vx_i^{(\ell)} = (x_{i,1}^{(\ell)},\dots,x_{i,s}^{(\ell)})^\intercal$ is obtained by linearly transforming $\vx_i$,
+%\begin{equation}
+%\label{dig.shift}
+%(x_{i,j,1}^{(\ell)},\dots,x_{i,j,r}^{(\ell)})^\intercal = L (x_{i,j,1},\dots,x_{i,j,r})^\intercal\oplus \ve_j,\qquad j= 1,\dots,s\, ,
+%\end{equation}
+%where $ x_{i,j}^{(\ell)}=\sum_{k = 1}^r x_{i,j,k}^{(\ell)}2^{-k}$, $\ve_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and $L$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
+%\bigskip
+%
+%Likewise, ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained as follows: for each $i=0,\dots,2^r-1$, point ${\vx'}_i^{(\ell)} = ({x'}_{i,1}^{(\ell)},\dots,{x'}_{i,s}^{(\ell)})^\intercal$ is obtained by linearly transforming ${\vx'}_i^{(0)}$,
+%\begin{equation}
+%\label{ibinom.scrambling}
+%({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = {L'} ({x'}_{i,j,1},\dots,{x'}_{i,j,r})^\intercal\oplus {\ve'}_j,\qquad j= 1,\dots,s\, ,
+%\end{equation}
+%where $ {x'}_{i,j}^{(\ell)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(\ell)}2^{-k}$, ${\ve'}_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and ${L'}$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
+%\bigskip
 
-Likewise, ${B'}_\ell=\{{\vx'}_i^{(\ell)}\}_{i=0}^{2^r-1}$ is obtained as follows: for each $i=0,\dots,2^r-1$, point ${\vx'}_i^{(\ell)} = ({x'}_{i,1}^{(\ell)},\dots,{x'}_{i,s}^{(\ell)})^\intercal$ is obtained by linearly transforming ${\vx'}_i^{(0)}$,
-\begin{equation}
-\label{ibinom.scrambling}
-({x'}_{i,j,1}^{(\ell)},\dots,{x'}_{i,j,r}^{(\ell)})^\intercal = {L'} ({x'}_{i,j,1},\dots,{x'}_{i,j,r})^\intercal\oplus {\ve'}_j,\qquad j= 1,\dots,s\, ,
-\end{equation}
-where $ {x'}_{i,j}^{(\ell)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(\ell)}2^{-k}$, ${\ve'}_j=(e_{j,{0}},\dots,e_{j,{r-1}})^\intercal\in\mathbb{F}_2^r$ and ${L'}$ is a full rank lower triangular matrix of size $r \times r$ over $\mathbb{F}_2$.
-\bigskip
+Initial sets are $B_0=\{\vx_i\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i\}_{i=0}^{2^r-1}$.
+Then, one may take $B_\ell=\{\vx_i\oplus\ve_\ell\}_{i=0}^{2^r-1}$ and ${B'}_\ell=\{{\vx'}_i\oplus{\ve'}_\ell\}_{i=0}^{2^r-1}$ such that $\ve_\ell\notin\mathcal{P}_{\ell-1}$ and ${\ve'}_\ell\notin\mathcal{P'}_{\ell-1}$.
+Indeed, $B_0$ is a subgroup of $\left(\mathbb{F}_2^{r}\right)^{s}$.
+Therefore, we can construct cosets $B_\ell$ as $B_0 \oplus \ve$, under the right $\ve \in \left(\mathbb{F}_2^{r}\right)^{s}$.
+After that, we may also apply linear scramblings \cite{Matousek} using lower triangular matrices $L$ and $L'$ ......
+There are exactly $2^{rs}$ different choices of $\ve$ and ${\ve'}$, and $2^{r(r-1)/2}$ choices of $L$ and $L'$.
+The maximum number of iterations $\ell$ that can be performed equals the number of cosets, $2^{s}$.
+If this maximum is reached, designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ both correspond to a full grid design of $2^{rs}$ points.
 
-Left multiplications by matrices $L$ and $L'$ in \eqref{dig.shift} and \eqref{ibinom.scrambling}  are called linear scramblings \cite{Matousek} while additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts.
+%Left multiplications by matrices $L$ and $L'$ in \eqref{dig.shift} and \eqref{ibinom.scrambling}  are called linear scramblings \cite{Matousek} while additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts.
 There are exactly $2^r$ different choices of $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices of $L$ and $L'$.
 To guarantee that new points added will fill unexplored regions of the input space, the vectors $\ve_j$ are selected as follows:
-\begin{itemize}
-\item[i)] at iteration $\ell=0$, vectors $\ve_j$ are all equal to the zero of $\mathbb{F}_2^r$,
-\item[ii)] for $\ell \geq1$, we use the following result:
-$(B_0,\oplus)$ is a subgroup of $\left(\mathbb{F}_2^{r}\right)^{s}$.
+%\begin{itemize}
+%\item[i)] at iteration $\ell=0$, vectors $\ve_j$ are all equal to the zero of $\mathbb{F}_2^r$,
+%\item[ii)] for $\ell \geq1$, we use the following result:
+%$(B_0,\oplus)$ is a subgroup of $\left(\mathbb{F}_2^{r}\right)^{s}$.
 From Lagrange's Theorem, we can construct cosets $B_\ell$ as $B_0 \oplus \ve$, $\ve=(\ve_1,\dots,\ve_s) \in \left(\mathbb{F}_2^{r}\right)^{s}$
-%, which form a partition of $\left(\mathbb{F}_2^{r}\right)^{s}$
-.
-At iteration $\ell \geq1$, we select $\ve$ such that $B_0 \oplus \ve$ is a new coset different from $\{B_0,\dots,B_{\ell-1}\}$, and it will be enough to choose $\ve\notin\mathcal{P}_{\ell-1}$.
-By identification we have $B_{\ell}=B_0 \oplus \ve$ ensuring that the new points added are all different.
+%%, which form a partition of $\left(\mathbb{F}_2^{r}\right)^{s}$
+%.
+At iteration $\ell \geq1$, we select $\ve$ such that $B_{\ell}=B_0 \oplus \ve$ is a new coset different from $\{B_0,\dots,B_{\ell-1}\}$.
+It will be enough to choose $\ve$ such that $\ve\notin\mathcal{P}_{\ell-1}$.
+%By identification we have $B_{\ell}=B_0 \oplus \ve$ ensuring that the new points added are all different.
 
@@
 At each step $\ell$, one combination is sampled without replacement.
-\end{itemize}
-The same reasoning to select vectors $\ve'_j$ is made for $({B'}_0,\oplus)$.
+%\end{itemize}
+%The same reasoning to select vectors $\ve'_j$ is made for $({B'}_0,\oplus)$.
 The maximum number of iterations $\ell$ that can be performed equals the number of cosets, $2^{s}$.

### 2016-06-14 crass/crassnew.tex
hopefully last changes

@@
 \end{equation}
-where $c_j^{m+1}$ is the last column of $C_j^{m+1}$.
+where $c_j^{m+1}$ is the last column of $C_j^{m+1}$ and $\oplus$ is the addition in $\mathbb{F}_2$.
 
-Sobol' sequences also have good group structure properties. For any $m\geq 1$, the first $2^m$ points of the sequence form an Abelian group under the following operation $\oplus$,
-\begin{gather*}
+Sobol' sequences also have good group structure properties. For any $m\geq 1$, the first $2^m$ points of the sequence form an Abelian group under $\oplus$:
+\begin{equation}
+\begin{gathered}
 \vx = \left(\sum_{k=1}^m x_{1,k}2^{-k},\dots,\sum_{k=1}^m x_{s,k}2^{-k}\right)^\intercal\; , \qquad \vz = \left(\sum_{k=1}^m z_{1,k}2^{-k},\dots,\sum_{k=1}^m z_{s,k}2^{-k}\right)^\intercal, \\
 \vx\oplus\vz := \left(\sum_{k=1}^m (x_{1,k}+z_{1,k}\mod 2)2^{-k},\dots,\sum_{k=1}^m (x_{s,k}+z_{s,k}\mod 2)2^{-k}\right)^\intercal.
-\end{gather*}
+\end{gathered}
+\label{group.operation}
+\end{equation}
 
@@
 
-Initial sets are $B_0=\{\vx_i\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i\}_{i=0}^{2^r-1}$.
-Then, one may take $B_\ell=\{\vx_i\oplus\ve_\ell\}_{i=0}^{2^r-1}$ and ${B'}_\ell=\{{\vx'}_i\oplus{\ve'}_\ell\}_{i=0}^{2^r-1}$ such that $\ve_\ell\notin\mathcal{P}_{\ell-1}$ and ${\ve'}_\ell\notin\mathcal{P'}_{\ell-1}$.
+At step $\ell=0$, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are generated as follows:
+
+for each $i=0,\dots,2^r-1$, point $\vx_i^{(0)} = (x_{i,1}^{(0)},\dots,x_{i,s}^{(0)})^\intercal$ and ${\vx'}_i^{(0)} = ({x'}_{i,1}^{(0)},\dots,{x'}_{i,s}^{(0)})^\intercal$ are obtained by linearly transforming $\vx_i$,
+\begin{equation}
+\label{linear.scrambl}
+\begin{aligned}
+(x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal &= L (x_{i,j,1},\dots,x_{i,j,r})^\intercal,\\
+({x'}_{i,j,1}^{(0)},\dots,{x'}_{i,j,r}^{(0)})^\intercal &= L' (x_{i,j,1},\dots,x_{i,j,r})^\intercal,\qquad j= 1,\dots,s\,
+\end{aligned}
+\end{equation}
+where $ x_{i,j}^{(0)}=\sum_{k = 1}^r x_{i,j,k}^{(0)}2^{-k}$, $ {x'}_{i,j}^{(0)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(0)}2^{-k}$ and $L$, $L'$ are two full rank lower triangular matrices of size $r \times r$ over $\mathbb{F}_2$.
+Left multiplications by matrices $L$ and $L'$ in \eqref{linear.scrambl} are called linear scramblings \cite{Matousek}.
+
+At step $\ell \geq 1$, using formula (\ref{group.operation}) we construct:
+\begin{equation}
+B_\ell=\{\vx_i^{(0)}\oplus\ve_\ell\}_{i=0}^{2^r-1}, \qquad {B'}_\ell=\{{\vx'}_i^{(0)}\oplus{\ve'}_\ell\}_{i=0}^{2^r-1}
+\label{dig.shift}
+\end{equation}
+where $\ve_\ell \in \left(\mathbb{F}_2^{r}\right)^{s} \setminus \mathcal{P}_{\ell-1}$ and ${\ve'}_\ell \in \left(\mathbb{F}_2^{r}\right)^{s} \setminus \mathcal{P'}_{\ell-1}$.
 Indeed, $B_0$ is a subgroup of $\left(\mathbb{F}_2^{r}\right)^{s}$.
-Therefore, we can construct cosets $B_\ell$ as $B_0 \oplus \ve$, under the right $\ve \in \left(\mathbb{F}_2^{r}\right)^{s}$.
-After that, we may also apply linear scramblings \cite{Matousek} using lower triangular matrices $L$ and $L'$ ......
-There are exactly $2^{rs}$ different choices of $\ve$ and ${\ve'}$, and $2^{r(r-1)/2}$ choices of $L$ and $L'$.
-The maximum number of iterations $\ell$ that can be performed equals the number of cosets, $2^{s}$.
+Therefore, we construct $B_\ell=B_0 \oplus \ve_\ell$ as a coset of $B_0$ under the right $\ve_\ell$.
+The same reasoning applies to ${B'}_0$.
+Additions by vectors $\ve_j$ and ${\ve'}_j$ in (\ref{dig.shift}) are referred as digital shifts.
+
+There are exactly $2^{rs}$ different choices of $\ve_\ell$ and ${\ve'}_\ell$, and $2^{r(r-1)/2}$ choices of $L$ and $L'$.
+The maximum number of iterations $\ell$ that can be performed equals the number of cosets, $2^{r(s-1)}$.
 If this maximum is reached, designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ both correspond to a full grid design of $2^{rs}$ points.
 
+\bigskip
 %Left multiplications by matrices $L$ and $L'$ in \eqref{dig.shift} and \eqref{ibinom.scrambling}  are called linear scramblings \cite{Matousek} while additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts.
@@
 \end{lemma}
-\textit{Proof}:For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{dig.shift}) and (\ref{ibinom.scrambling}) are bijections from $\mathbb{F}^r_2$ to $\mathbb{F}^r_2$.
+\textit{Proof}:For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{linear.scrambl}) and (\ref{dig.shift}) are bijections.
 Hence, same coordinates of $B_\ell$ and ${B'}_\ell$ will contain the same set of $2^r$ values.

### 2016-06-14 crass/crassnew.tex
hopefully last changes

@@
 
-\bigskip
 %Left multiplications by matrices $L$ and $L'$ in \eqref{dig.shift} and \eqref{ibinom.scrambling}  are called linear scramblings \cite{Matousek} while additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts.
@@
 \end{lemma}
-\textit{Proof}:For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{linear.scrambl}) and (\ref{dig.shift}) are bijections.
+\textit{Proof}:For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{linear.scrambl}) and (\ref{dig.shift}) are bijections from $\mathbb{F}_2^r$ and $\left(\mathbb{F}_2^{r}\right)^{s}$.
 Hence, same coordinates of $B_\ell$ and ${B'}_\ell$ will contain the same set of $2^r$ values.
@@
 Each of the $100$ designs $A$ is independently randomized by applying Owen's scrambling.
-Each of the $100$ designs $B$ is constructed by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and by selecting the vectors $\ve_j$ following steps i) and ii).
+Each of the $100$ designs $B$ is constructed by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and the vectors $\ve_\ell$ as in equation (\ref{dig.shift}).
 We also represent in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points of design $B$.

### 2016-06-14 crass/crassnew.tex
Final changes to crassnew according to new definition of oplus

@@
 
-Sobol' sequences in dimension $s$ are digital sequences in base $b=2$ that can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over the Galois field $\mathbb{F}_2:=\{0,1\}$.
+Sobol' sequences in dimension $s$ are digital sequences in base $b=2$ that can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over $\mathbb{F}_2$.
 %We will denote by $\oplus$ the addition in $\mathbb{F}_2$.
@@
 
-Sobol' sequences also have good group structure properties. For any $m\geq 1$, the first $2^m$ points of the sequence form an Abelian group under $\oplus$:
+In addition, Sobol' sequences have good group structure properties. For any $m\geq 1$, the first $2^m$ points of the sequence form an Abelian group under $\oplus$:
 \begin{equation}
@@
 \end{equation}
+From definition \eqref{group.operation} above, one may see that the first $2^m$ points of the sequence are elements of $\left(\mathbb{F}_2^m\right)^s$, with $\mathbb{F}_2:=\{0,1\}$ the Galois field.
 
@@
 \begin{aligned}
-(x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal &= L (x_{i,j,1},\dots,x_{i,j,r})^\intercal,\\
-({x'}_{i,j,1}^{(0)},\dots,{x'}_{i,j,r}^{(0)})^\intercal &= L' (x_{i,j,1},\dots,x_{i,j,r})^\intercal,\qquad j= 1,\dots,s\,
+(x_{i,j,1}^{(0)},\dots,x_{i,j,r}^{(0)})^\intercal &= L (x_{i,j,1},\dots,x_{i,j,r})^\intercal,\qquad j= 1,\dots,s\, , \\
+({x'}_{i,j,1}^{(0)},\dots,{x'}_{i,j,r}^{(0)})^\intercal &= L' (x_{i,j,1},\dots,x_{i,j,r})^\intercal,\qquad j= 1,\dots,s\, , 
 \end{aligned}
@@
 \begin{equation}
-B_\ell=\{\vx_i^{(0)}\oplus\ve_\ell\}_{i=0}^{2^r-1}, \qquad {B'}_\ell=\{{\vx'}_i^{(0)}\oplus{\ve'}_\ell\}_{i=0}^{2^r-1}
+B_\ell=\{\vx_i^{(0)}\oplus\ve_\ell\}_{i=0}^{2^r-1}, \qquad {B'}_\ell=\{{\vx'}_i^{(0)}\oplus{\ve'}_\ell\}_{i=0}^{2^r-1}.
 \label{dig.shift}
@@
 Indeed, $B_0$ is a subgroup of $\left(\mathbb{F}_2^{r}\right)^{s}$.
-Therefore, we construct $B_\ell=B_0 \oplus \ve_\ell$ as a coset of $B_0$ under the right $\ve_\ell$.
+Therefore, we construct $B_\ell=B_0 \oplus \ve_\ell$ as a coset of $B_0$ under the right choice of $\ve_\ell$.
 The same reasoning applies to ${B'}_0$.
@@
 There are exactly $2^{rs}$ different choices of $\ve_\ell$ and ${\ve'}_\ell$, and $2^{r(r-1)/2}$ choices of $L$ and $L'$.
-The maximum number of iterations $\ell$ that can be performed equals the number of cosets, $2^{r(s-1)}$.
+The maximum number of iterations $\ell$ that can be performed equals the number of cosets, $2^s$.
 If this maximum is reached, designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ both correspond to a full grid design of $2^{rs}$ points.

### 2016-06-14 crass/crassnew.tex
Small typos

@@
 
-At step $\ell \geq 1$, using formula (\ref{group.operation}) we construct:
+At step $\ell \geq 1$, using definition \eqref{group.operation} we construct:
 \begin{equation}
@@
 The same reasoning applies to ${B'}_0$.
-Additions by vectors $\ve_j$ and ${\ve'}_j$ in (\ref{dig.shift}) are referred as digital shifts.
+Additions by vectors $\ve_j$ and ${\ve'}_j$ in \eqref{dig.shift} are referred as digital shifts.
 

### 2016-06-17 article.tex
article last changes

@@
 \newtheorem{definition}{Definition}
+\newtheorem{proposition}{Proposition}
 \theoremstyle{definition}
@@
 \label{first.order}
-\underline{\tau}_u^2  &= \int_{[0,1)^{2d-1}} f(\vx) f(\vx_u:{\vx'}_{-u})d\vx d{\vx'}-\mu^2 , \\
+\underline{\tau}_u^2  &= \int_{[0,1)^{2d-1}} (f(\vx)-\mu)(f(\vx_{u}:{\vx'}_{-u})-\mu), \\
 \label{total.effect}
-\ov{$\tau$}_u^2 &= \int_{[0,1)^{d+1}}(f(\vx)-f({\vx'}_u:\vx_{-u}))^2d\vx d{\vx'},
+\ov{$\tau$}_u^2 &= \int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}, \qquad u \in \mathcal{D},
 \end{align}
@@
 \label{total.effect.est}
-\widehat{\ov{$\tau$}_u^2} & = \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f(\vx_i) - f({\vx'}_{i,u}:\vx_{i,-u}))^2,
+\widehat{\ov{$\tau$}_u^2} & = \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D}
 \end{align}
@@
 \end{theorem}
-The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ accordingly to subset $u$.
+The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ accordingly to $u$.
 While elegant, this approach still requires a number of model evaluations that grows linearly with respect to the input space dimension.
@@
 
-Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$.
+More specifically, let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$.
 Denote by $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$.
-Consider $u \subsetneq \mathcal{D}$, from Definition \ref{rep.designs} there exists a permutation $\pi_u$ such that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$.
+Consider $u \in \mathcal{D}$, from Definition \ref{rep.designs} there exists a permutation $\pi_u$ such that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$.
 Then, remark that $\forall i \in \{0,\dots,n-1\}$:
-\[\pi_u(f({\vx'}_i))=f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u})=f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u})\]
+\[\pi_u(f({\vx'}_i))=f({\vx'}_{\pi_u(i)})=f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u})=f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u})\]
 %\pi_u(f({\vx'}_{i,u}:{\vx'}_{i,-u}))
-Hence, $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) with $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{\pi_u(f({\vx'}_i))\}_{i=0}^{n-1}$.
-This estimation method has been further studied and generalized in Tissot et al.
+Each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) with $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{\pi_u(f({\vx'}_i))\}_{i=0}^{n-1}$ without requiring further model evaluations.
+This estimation method has been deeply studied and generalized in Tissot et al.
 \cite{Mara} to the case of closed second-order indices.
@@
 Using a recursive estimation procedure requires to write a recursive formula for estimators (\ref{first.order.est}) and (\ref{total.effect.est}).
-For the sake of readability of the paper, the corresponding recursive formulas are detailed in equations (\ref{first.order.est.rec}) and (\ref{total.effect.est.rec}) in the Annexe.
+For the sake of readability of the paper, the corresponding recursive formulas are detailed in equations (\ref{first.order.est.rec}) and (\ref{total.effect.est.rec}) in the Annexe \ref{recursive.formulas}.
 
@@
 Background on Sobol' sequences are provided in \cite{crass}.
+We recall here that a $d$-dimensional Sobol' sequence is generated with a set of $d$ generating matrices (one per coordinate).
 The construction of $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ is carried out according to the following recursive scheme :
@@
 $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can either be used with procedure $A$ to estimate all first-order and all total effect Sobol' indices or with procedure $B$ to estimate all first-order Sobol' indices.
-Algorithms \ref{procedureA} and \ref{procedureB} summarize the main steps of each recursive estimation procedure.
+Algorithms \ref{procedureA} and \ref{procedureB} summarize the main steps of each procedure.
 \begin{algorithm}[!ht]
@@
 \hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
+\State Compute $\{f(\vx_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$
 \For {$u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$}
-\State Construct design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=0}^{2^{\ell}-1}$
-\State Compute $\{f(\vx_i)\}_{i=0}^{2^\ell-1}$ and $\{f(\vx_{i,u},{\vx'}_{i,-u})\}_{i=0}^{2^\ell-1}$
-\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ with formula (\ref{first.order.est}) and (\ref{total.effect.est})
+\State Construct design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=2^{\ell-1}}^{2^{\ell}-1}$
+\State Compute  $\{f(\vx_{i,u},{\vx'}_{i,-u})\}_{i=2^{\ell-1}}^{2^\ell-1}$
+\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ with formula (\ref{first.order.est.rec}) and (\ref{total.effect.est.rec})
 \EndFor
@@
 \hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
-\State Compute $\{f(\vx_i)\}_{i=0}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=0}^{2^\ell-1}$
+\State Compute $\{f(\vx_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$
 \For {$u \in \mathcal{D}$}
-\State  $\{f({\vx'}_i)\}_{i=0}^{2^\ell-1}$ into $\{\pi_u(f({\vx'}_i))\}_{i=0}^{2^\ell-1}$
-\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ with formula (\ref{first.order.est})
+\State  order $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ into $\{\pi_u(f({\vx'}_i))\}_{i=2^{\ell-1}}^{2^\ell-1}$
+\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ with formula (\ref{first.order.est.rec})
 \EndFor
@@
 For example, an absolute difference between estimates computed on consecutive steps.
-Such stopping criteria are often hard to tweak but above all fail to guarantee any error bounds on the estimation.
+Such stopping criteria are often hard to tweak but above all fail to guarantee any error bound on the estimation.
 Our stopping criterion is presented and discussed in Section \ref{section.error}.
-The criterion is an error bound based on the discrete Walsh decomposition of the integral formulas of first-order and total effect Sobol' indices.
+The criterion is an error bound based on the discrete Walsh decomposition of integrals (\ref{first.order}) and (\ref{total.effect}).
 
@@
 Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small closed Sobol' indices.
+Our aim is to show that using ``Correlation 2" in procedure $A$ may reduces the total number of model evaluations.
+``Correlation 2" formula writes as follows:
+\begin{equation}
+\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i))
+\label{correlation2}
+\end{equation}
+It uses an extra set of $n$ model evaluations to estimate $\widehat{\underline{\tau}_u^2}$.
+Owen explains the effectiveness of ``Correlation 2" as follows.
+If the main effect of $\vx_u$ is small then $f(\vx)$ will be almost entirely explained by $\vx_{-u}$.
+The two terms $(f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))$ and $(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i))$ should then be small quantities as well as (\ref{correlation2}).
 
-Our aim is to show that using ``Correlation 2" in procedure $A$ may reduces the total number of model evaluations required while reaching the same accuracy on the estimates.
-
-Cost small: $n(d+1)+d_sn+n$
-
-Cost pas small: $\alpha n d_s +n+(d-d_s)n$
-
-Cost small - cost pas small: $n\sum_{i=1}^{s}(2-\alpha_i+1)$ $s$ number of small indices, $\alpha_i$ proportion of how many more points if not pas small
+We discuss now the potential improvement brought by the use of ``Correlation 2".
+Assume that the number of small first-order indices is known and equals $\alpha$.
+Then, the cost of procedure $A$ including ``Correlation 2" to estimate small indices writes:
+\[ n(d-\alpha) + 2 n'\alpha + 2\max(n,n'),\]
+where: \begin{itemize}
+\item[$\bullet$] $n(d-\alpha)$ is the number of evaluations induced by the $d-\alpha$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i\geq0}$ to estimate all non small indices, 
+\item[$\bullet$] $2 n'\alpha$ is the number of evaluations induced by the $2\alpha$ designs $\{\vz_{i,u}:\vx_{i,-u}\}_{i\geq0}$ and $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i\geq0}$ to estimate all small indices,
+\item[$\bullet$] $2\max(n,n')$ is the number of evaluations  induced by the $2$ designs $\{\vx_{i}\}_{i\geq0}$ and $\{{\vx'}_{i}\}_{i\geq0}$.
+\end{itemize}
+At the opposite, the cost of procedure $A$ excluding ``Correlation 2" writes: 
+\[ n(d-\alpha) + n\alpha + 2n.\]
+It is straightforward that procedure $A$ including ``Correlation 2" performs equally well or better when $n' \leq 2n$.
+Furthermore, since we are working with Sobol' sequences $n'=2^{k'}$ and $n=2^{k}$.
+Hence, procedure $A$ including ``Correlation 2" performs equally well or better when the recursive estimation procedure finished at least one step sooner.
+Illustrations of this improvement will be provided in Section \ref{appli}.
 
@@
 
-In the multiplicative approach \cite{crass}, these $2d$ generating matrices are selected as the first $2d$ elements of the set found by Kuo and Joe in \cite{Kuo}.
+We note by $C_1,\dots,C_d$ the matrices generating $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and ${C'}_1,\dots,{C'}_d$ those generating $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$.
+In the multiplicative approach \cite{crass}, these $2d$ matrices are selected as the first $2d$ elements of the set found by Kuo and Joe in \cite{Kuo}.
 This set is composed of generating matrices that optimize the $2$-dimensional projection $t$-values.
-For procedure $A$ this choice of these $2d$ generating matrices is logical.
-Each of the $d+2$ designs constructed following Theorem \ref{saltelli.theorem} is a Sobol' sequence generated by a subset of $d$ matrices among the initial $2d$ ones.
-Therefore, $2$-dimensional projection $t$-values are not changed.
 
-That is not the case for procedure $B$.
-(introduire les matrices $C_j$ et ecrire les relations).
-The permutations applied in step $6$ of Algorithm \ref{procedureB} modify the $2$-dimensional projection $t$-values of the underlying designs.
+%In procedure $A$, each design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i\geq0}$ constructed in step $6$ of Algorithm \ref{procedureA} is a $d$-dimensional Sobol' sequence generated by the $d$-subset: $${C'}_1,\dots,{C'}_{u-1},C_u,{C'}_{u+1},\dots,C_d.$$ Therefore, $2$-dimensional projection $t$-values are still optimized.
+
+In procedure $B$, each permutation $\pi_u$ applied in step $6$ of Algorithm \ref{procedureB} results in a design $\{\vx_{i,u}:{\vx'}_{\pi_u(i),-u}\}_{i=0}^{2^\ell-1}$.
+The $d$ generating matrices corresponding to this design are:
+$${C'}_1U_u,\dots,{C'}_{u-1}U_u,C_u,{C'}_{u+1}U_u,{C'}_dU_u$$ where $U_u$ is a a full rank upper triangular matrix verifying $C_u={C'}_uU_u$.
+The right multiplication by $U_u$ is the digital representation of the ordering by $\pi_u$.
 
@@
 \section{Applications}
+\label{appli}
 \subsection{Classical test functions}
@@
 \newpage
-\section{Annexe: recursive formulas}
+\section{Annexes}
+
+\subsection{recursive formulas}
+\label{recursive.formulas}
 
@@
 
+\subsection{Proof proposition \ref{right.multi}}
+\label{proof.prop}
+
 \end{document}

### 2016-06-17 crass/crassnew.tex
last and final small changes

@@
 
-Each
-
 \subsection{Sobol' sequences}
 
-Sobol' sequences in dimension $s$ are digital sequences in base $b=2$ that can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over $\mathbb{F}_2$.
+Sobol' sequences in dimension $s$ are digital sequences in base $b=2$ that can be computed using the \emph{generating matrices}, a set of $s$ full rank infinite dimensional upper triangular matrices over the Galois field $\mathbb{F}_2:=\{0,1\}$.
 %We will denote by $\oplus$ the addition in $\mathbb{F}_2$.
@@
 \end{equation}
-From definition \eqref{group.operation} above, one may see that the first $2^m$ points of the sequence are elements of $\left(\mathbb{F}_2^m\right)^s$, with $\mathbb{F}_2:=\{0,1\}$ the Galois field.
+From equation \eqref{dig.net.eq.} above, one may see that the first $2^m$ points of the sequence are elements of $\left(\mathbb{F}_2^m\right)^s$, with $\mathbb{F}_2:=\{0,1\}$ the Galois field.
 
@@
 
-The first approach is called multiplicative because $|P_\ell|=2^\ell$ while the second one is called additive and $|P_\ell|=\ell|B_0|$.
+The first approach is called multiplicative because $|\mathcal{P}_\ell|=2^\ell$ while the second one is called additive and $|\mathcal{P}_\ell|=\ell|B_0|$.
 In the multiplicative case, we will directly use $2$ $s$-dimensional sequences as a result from Lemma \ref{Sobol_replicated}.
@@
 \end{equation}
-where $ x_{i,j}^{(0)}=\sum_{k = 1}^r x_{i,j,k}^{(0)}2^{-k}$, $ {x'}_{i,j}^{(0)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(0)}2^{-k}$ and $L$, $L'$ are two full rank lower triangular matrices of size $r \times r$ over $\mathbb{F}_2$.
+where $ x_{i,j}^{(0)}=\sum_{k = 1}^r x_{i,j,k}^{(0)}2^{-k}$, $ {x'}_{i,j}^{(0)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(0)}2^{-k}$ and $L$, $L'$ are two distinct full rank lower triangular matrices of size $r \times r$ over $\mathbb{F}_2$.
 Left multiplications by matrices $L$ and $L'$ in \eqref{linear.scrambl} are called linear scramblings \cite{Matousek}.
@@
 
-There are exactly $2^{rs}$ different choices of $\ve_\ell$ and ${\ve'}_\ell$, and $2^{r(r-1)/2}$ choices of $L$ and $L'$.
-The maximum number of iterations $\ell$ that can be performed equals the number of cosets, $2^s$.
+There are exactly $2^{rs}$ different choices of $\ve_\ell$ and ${\ve'}_\ell$ in $\left(\mathbb{F}_2^{r}\right)^{s}$, and $2^{r(r-1)/2}$ choices of $L$ and $L'$.
+The maximum number of iterations $\ell$ that can be performed equals the number of cosets, $2^{r(s-1)}$.
 If this maximum is reached, designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ both correspond to a full grid design of $2^{rs}$ points.
@@
 
-We name by design $A$ (resp.
-$B$) one of the two replicated designs constructed with the multiplicative (resp.
+We name by design $M$ (resp.
+$A$) one of the two replicated designs constructed with the multiplicative (resp.
 additive) approach.
 We set the input space dimension $s$ to $6$.
-Design $A$ is refined until $\ell=12$, and design $B$ is constructed with an initial value $r=8$ and refined 15 times.
-We construct $100$ designs $A$ and $B$ whose average criteria are presented in Figure \ref{results.crit}.
-Each of the $100$ designs $A$ is independently randomized by applying Owen's scrambling.
-Each of the $100$ designs $B$ is constructed by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and the vectors $\ve_\ell$ as in equation (\ref{dig.shift}).
-We also represent in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points of design $B$.
+Design $M$ is refined until $\ell=12$, and design $A$ is constructed with an initial value $r=8$ and refined 15 times.
+We construct $100$ designs $M$ and $A$ whose average criteria are presented in Figure \ref{results.crit}.
+Each of the $100$ designs $M$ is independently randomized by applying Owen's scrambling \cite{OwenScrambling}.
+Each of the $100$ designs $A$ is constructed by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and the vectors $\ve_\ell$ as in equation (\ref{dig.shift}).
+We also represent in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points of design $A$.
 The x-axis corresponds to the number of points $N$ of the design.
@@
 
-As expected, design $A$ performs the best and the estimated slope of the discrepancy curve ($-0.67$) falls within the expected range for Sobol' sequences \cite{Morokoff}.
-Although design $B$ does not perform as well as design $A$, it outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $A$.
+As expected, design $M$ performs the best and the estimated slope of the discrepancy curve ($-0.67$) falls within the expected range for Sobol' sequences \cite{Morokoff}.
+Although design $A$ does not perform as well as design $M$, it outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $M$.
 \begin{figure}
-\caption{Log-log graph of averaged $L_2$ star discrepancy (left) and maximin (right) for designs $A$ and $B$ over $100$ repetitions.}
+\caption{Log-log graph of averaged $L_2$ star discrepancy (left) and maximin (right) for designs $M$ and $A$ over $100$ repetitions.}
 \label{results.crit}

### 2016-06-24 crass/crassnew.tex
Fixing some comments from Fred to crassnew

@@
 \label{rep.designs}
-Consider $\vx \in [0,1)^s$, and $\vx_u \in [0,1)^{s-|u|}$ the subset of dimensions of $\vx$ given by $u\subsetneq \{1,\dots,s\}$, where $|u|$ is the cardinality of $u$.
+Consider $\vx \in [0,1)^s$, and $\vx_u \in [0,1)^{s-|u|}$ the subset of elements of $\vx$ given by $u\subsetneq \{1,\dots,s\}$, where $|u|$ is the cardinality of $u$.
 Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1)^{s}$, and denote by $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp.
-$\mathcal{P}'^u$) the subset of dimensions of points in $\mathcal{P}$ (resp.
+$\mathcal{P}'^u$) the subset of elements of points in $\mathcal{P}$ (resp.
 $\mathcal{P}'$) indexed by $u$.
@@
 
-Thus, a $(t,m,s)$-net is defined such that all elementary intervals of volume at least $b^{t-m}$ will enclose a proportional number of points of $\mathcal{P}$, namely $b^{t-m}|\mathcal{P}|$ points.
+Thus, a $(t,m,s)$-net is defined such that all elementary intervals of volume $b^{t-m}$ will enclose the same proportion of points of $\mathcal{P}$, namely $b^{t-m}|\mathcal{P}|$ points.
 The most evenly spread nets are $(0,m,s)$-nets, since each elementary interval of the smallest volume possible, $b^{-m}$, contains exactly one point.
@@
 \end{equation}
-From equation \eqref{dig.net.eq.} above, one may see that the first $2^m$ points of the sequence are elements of $\left(\mathbb{F}_2^m\right)^s$, with $\mathbb{F}_2:=\{0,1\}$ the Galois field.
+From equation \eqref{dig.net.eq.} above, one may see that the first $2^m$ points of the sequence are elements of $\left(\mathbb{F}_2^m\right)^s$.
 
@@
 The second criterion is called maximin distance and measures the regularity of a point set.
-It returns the minimum of all euclidean distances between pairs of points in the set.
+It returns the minimum of all Euclidean distances between pairs of points in the set.
 The higher the criterion, the more spread the point set is.
@@
 $A$) one of the two replicated designs constructed with the multiplicative (resp.
-additive) approach.
-We set the input space dimension $s$ to $6$.
-Design $M$ is refined until $\ell=12$, and design $A$ is constructed with an initial value $r=8$ and refined 15 times.
-We construct $100$ designs $M$ and $A$ whose average criteria are presented in Figure \ref{results.crit}.
-Each of the $100$ designs $M$ is independently randomized by applying Owen's scrambling \cite{OwenScrambling}.
-Each of the $100$ designs $A$ is constructed by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and the vectors $\ve_\ell$ as in equation (\ref{dig.shift}).
-We also represent in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points of design $A$.
-The x-axis corresponds to the number of points $N$ of the design.
-The y-axis corresponds to the value of the criterion.
-A logarithmic scale is used for both axis.
+additive) approach, and set the input space dimension $s$ to $6$.
+For design $M$, we study the properties of $\mathcal{P}_8,\dots,\mathcal{P}_{12}$, and for design $A$, we set the initial value to $r=8$ and study the properties of $\mathcal{P}_0,\dots,\mathcal{P}_{15}$.
+For both $M$ and $A$ we generate $100$ random designs whose average criteria are presented in Figure \ref{results.crit}.
+While each of the $100$ designs $M$ is independently randomized applying Owen's scrambling \cite{OwenScrambling}, designs $A$ are constructed by randomly selecting matrix $L$ (uniformly among all $2^{r(r-1)/2}$ choices) and vectors $\ve_\ell$ used in equation (\ref{dig.shift}).
+In addition, we also show in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points as in design $A$.
+The x-axis corresponds to the number of design points $N$ and the y-axis to the value of the criterion.
 

### 2016-06-27 crass/crassnew.tex
changes according to Fred comments

@@
 {\it To cite this article: L.
-Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci. Paris, Ser. I 340 (2005).}
+Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci. Paris, Ser. I 340 (2016).}
 
@@
 {\it Pour citer cet article~: L. Gilquin, Ll. A. Jim\'enez Rugama, E. Arnaud, F. J. Hickernell, H. Monod, C. Prieur, C. R. Acad. Sci.
-Paris, Ser. I 340 (2005).}
+Paris, Ser. I 340 (2016).}
 \end{abstract}
@@
 
-\begin{definition}%[Replicated designs]
+\begin{e-definition}%[Replicated designs]
 \label{rep.designs}
@@
 We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a=1,\dots,s-1$, if for any $u\subsetneq \{1,\dots,s\}$ with $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
-\end{definition}
+\end{e-definition}
 
@@
 
-\begin{definition}%[$(t,m,s)-net$]
+\begin{e-definition}%[$(t,m,s)-net$]
 Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cube$ where $A=\prod_{j=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $s\geq 1$, $b\geq 2$, $\gamma_j\geq 0$, and $b^{\gamma_j}>\alpha_j\geq 0$.
 For $m\geq t\geq 0$, the point set $\mathcal{P}\in\cube$ with $b^m$ points is a $(t,m,s)-net$ in base $b$ if every $A$ with volume $b^{t-m}$ contains $b^t$ points of $\mathcal{P}$.
-\end{definition}
+\end{e-definition}
 
@@
 By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limit case where $m\rightarrow\infty$, we can define the $(t,s)$-sequence as:
-\begin{definition}%[$(t,s)$-sequence]
+\begin{e-definition}%[$(t,s)$-sequence]
 For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if for every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
-\end{definition}
+\end{e-definition}
 
 The replicated design properties can also apply to digital sequences. Hence, we introduce the following definition,
-\begin{definition}
+\begin{e-definition}
 Two digital sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are \emph{digitally replicated} of order $a$ if for all $m\geq 0$, $\{{\vx}_i\}_{i=0}^{b^m-1}$ and $\{{\vx'}_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $a$.
-\end{definition}
+\end{e-definition}
 
@@
 The higher the criterion, the more spread the point set is.
-
 \bigskip
@@
 While each of the $100$ designs $M$ is independently randomized applying Owen's scrambling \cite{OwenScrambling}, designs $A$ are constructed by randomly selecting matrix $L$ (uniformly among all $2^{r(r-1)/2}$ choices) and vectors $\ve_\ell$ used in equation (\ref{dig.shift}).
-In addition, we also show in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points as in design $A$.
+In addition, we also show in Figure \ref{results.crit} the results obtained with a Latin Hypercube design (LH design) with an equal number of points as in design $A$.
 The x-axis corresponds to the number of design points $N$ and the y-axis to the value of the criterion.

### 2016-06-28 crass/crassnew.tex
Fixing slope L2 discrepancy Sobol' seq

@@
 
-As expected, design $M$ performs the best and the estimated slope of the discrepancy curve ($-0.67$) falls within the expected range for Sobol' sequences \cite{Morokoff}.
+As expected, design $M$ performs the best and the estimated slope of the discrepancy curve ($-0.72$) falls within the expected range for Sobol' sequences \cite{Morokoff}.
 Although design $A$ does not perform as well as design $M$, it outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $M$.

### 2016-06-29 FunctionsTest/cubSobol_SI_all_g.m
Fixing a problem with cubSobol_SI_all: for small indices, we evaluated fzx each time for each small indice

@@ -244,12 +244,16 @@ end
 
 % First and total order indices estimators and function evaluations
 Sfo  = @(b,c) min(max(max(b(:,1),0)./max((c(:,2)-b(:,3).^2),0),0),1); % S function for first order
-% ffo = @(xpts,u,fx,fy,fxy) (fx - 1/2*mean(fx + fxy)).*(fxy - 1/2*mean(fx + fxy));
-ffo = @(xpts,u,fx,fy,fxy) fx.*(fxy - fy);
+% ffo = @(xpts,u,fx,fy,fxy,fzx) (fx - 1/2*mean(fx + fxy)).*(fxy - 1/2*mean(fx + fxy));
+ffo = @(xpts,u,fx,fy,fxy,fzx) fx.*(fxy - fy);
 Sfo_s = Sfo; % S function for first order small
-ffo_s = @(xpts,u,fx,fy,fxy) (fx - f([xpts(:,1:u-1) xpts(:,2*out_param.d + u) xpts(:,u+1:out_param.d)])).*(fxy - fy); % We redefine the non normalized estimator
+ffo_s = @(xpts,u,fx,fy,fxy,fzx) (fx - fzx).*(fxy - fy); % We redefine the non normalized estimator
+    % fzx is only used for the small indices. But we needed as input for
+    % all estimators to generalize the algorithm. If we give it as an
+    % input, we can only evaluate it one time and use it to several small
+    % indices.
 Stot = Sfo; % S function for total effect
-ftot = @(xpts,u,fx,fy,fxy) 1/2*(fy - fxy).^2;
+ftot = @(xpts,u,fx,fy,fxy,fzx) 1/2*(fy - fxy).^2;
 
 
 %% Main algorithm (we added 2xd dimensions for each index and and additional 2 for mean of f and f^2)
@@ -265,7 +269,7 @@ exit_len = 2;
 out_param.exit = false(exit_len, 2, out_param.d); %we start the algorithm with all warning flags down
 
 for u = 1:out_param.d
-    for r = 1:2
+    for r = 1:2 % r = 1 for first order, r = 2 for total effect
         INDICES(r,u).kappanumap = kappanumap_fx2_fx(:,1);
         INDICES(r,u).Stilde = zeros(out_param.mmax-out_param.mmin+1,1);
         INDICES(r,u).CStilde_low = CStilde_low_fx2_fx(:,1);
@@ -293,18 +297,22 @@ fx2 = fx.^2; %evaluate integrands y2
[…]

### 2016-06-29 crass/crassnew.tex
Fixing crass according to Herve comments

@@
 In this note, we propose two different constructions of replicated designs of order $1$ based on Sobol' sequences.
-These two constructions ensure that the input space is properly explored and can be used within the replication procedure to estimate all first-order Sobol' indices.
+Both constructions ensure that the input space is properly explored and can be used within the replication procedure to estimate all first-order Sobol' indices.
 The definition of these constructions is recursive, therefore one can iteratively refine each replicated design by adding the corresponding new set of points.
@@
 \begin{e-definition}%[$(t,m,s)-net$]
-Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cube$ where $A=\prod_{j=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $s\geq 1$, $b\geq 2$, $\gamma_j\geq 0$, and $b^{\gamma_j}>\alpha_j\geq 0$.
+Let $\mathcal{A}$ be the set of all subintervals $A\subset\cube$ where $A=\prod_{j=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $s\geq 1$, $b\geq 2$, $\gamma_j\geq 0$, and $b^{\gamma_j}>\alpha_j\geq 0$.
 For $m\geq t\geq 0$, the point set $\mathcal{P}\in\cube$ with $b^m$ points is a $(t,m,s)-net$ in base $b$ if every $A$ with volume $b^{t-m}$ contains $b^t$ points of $\mathcal{P}$.

### 2016-06-29 crass/crassnew.tex

@@
 However, Sobol' indices estimates may still not be accurate enough if designs $\mathcal{P}$ and $\mathcal{P}'$ do not explore the input space properly.
-
 \bigskip
@@
 \begin{e-definition}%[$(t,m,s)-net$]
-Let $\mathcal{A}$ be the set of all subintervals $A\subset\cube$ where $A=\prod_{j=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $s\geq 1$, $b\geq 2$, $\gamma_j\geq 0$, and $b^{\gamma_j}>\alpha_j\geq 0$.
+Let $\mathcal{A}$ be the set of all elementary intervals $A\subset \cube$ where $A=\prod_{j=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $s\geq 1$, $b\geq 2$, $\gamma_j\geq 0$, and $b^{\gamma_j}>\alpha_j\geq 0$.
 For $m\geq t\geq 0$, the point set $\mathcal{P}\in\cube$ with $b^m$ points is a $(t,m,s)-net$ in base $b$ if every $A$ with volume $b^{t-m}$ contains $b^t$ points of $\mathcal{P}$.
@@
 Nevertheless, both designs display good space-filling properties as shown in the next section.
-
 \bigskip
@@
 
-At step $\ell=0$, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are generated as follows:
-
-for each $i=0,\dots,2^r-1$, point $\vx_i^{(0)} = (x_{i,1}^{(0)},\dots,x_{i,s}^{(0)})^\intercal$ and ${\vx'}_i^{(0)} = ({x'}_{i,1}^{(0)},\dots,{x'}_{i,s}^{(0)})^\intercal$ are obtained by linearly transforming $\vx_i$,
+At step $\ell=0$, $B_0=\{\vx_i^{(0)}\}_{i=0}^{2^r-1}$ and ${B'}_0=\{{\vx'}_i^{(0)}\}_{i=0}^{2^r-1}$ are generated as follows: for each $i=0,\dots,2^r-1$, points $\vx_i^{(0)} = (x_{i,1}^{(0)},\dots,x_{i,s}^{(0)})^\intercal$ and ${\vx'}_i^{(0)} = ({x'}_{i,1}^{(0)},\dots,{x'}_{i,s}^{(0)})^\intercal$ are obtained by linearly transforming $\vx_i$,
 \begin{equation}
@@
 where $ x_{i,j}^{(0)}=\sum_{k = 1}^r x_{i,j,k}^{(0)}2^{-k}$, $ {x'}_{i,j}^{(0)}=\sum_{k = 1}^r {x'}_{i,j,k}^{(0)}2^{-k}$ and $L$, $L'$ are two distinct full rank lower triangular matrices of size $r \times r$ over $\mathbb{F}_2$.
-Left multiplications by matrices $L$ and $L'$ in \eqref{linear.scrambl} are called linear scramblings \cite{Matousek}.
+Left multiplications by $L$ and $L'$ in \eqref{linear.scrambl} are called linear scramblings \cite{Matousek}.
 
-At step $\ell \geq 1$, using definition \eqref{group.operation} we construct:
+At step $\ell \geq 1$, using addition as defined in \eqref{group.operation} we construct:
 \begin{equation}
@@
 The maximum number of iterations $\ell$ that can be performed equals the number of cosets, $2^{r(s-1)}$.
-If this maximum is reached, designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ both correspond to a full grid design of $2^{rs}$ points.
+If this maximum is reached, designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ both correspond to a full grid design of $2^{rs}$ points with $2^r$ distinct values per input.
 
@@
 \end{lemma}
-\textit{Proof}:For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{linear.scrambl}) and (\ref{dig.shift}) are bijections from $\mathbb{F}_2^r$ and $\left(\mathbb{F}_2^{r}\right)^{s}$.
-Hence, same coordinates of $B_\ell$ and ${B'}_\ell$ will contain the same set of $2^r$ values.
+\textit{Proof}: For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{linear.scrambl}) and (\ref{dig.shift}) are bijections from $\mathbb{F}_2^r$ and $\left(\mathbb{F}_2^{r}\right)^{s}$.
+Hence, the same coordinates of $B_\ell$ and ${B'}_\ell$ will contain the same set of $2^r$ values.
 
@@
 For design $M$, we study the properties of $\mathcal{P}_8,\dots,\mathcal{P}_{12}$, and for design $A$, we set the initial value to $r=8$ and study the properties of $\mathcal{P}_0,\dots,\mathcal{P}_{15}$.
-For both $M$ and $A$ we generate $100$ random designs whose average criteria are presented in Figure \ref{results.crit}.
+For both $M$ and $A$ we generate $100$ designs whose average criteria are presented in Figure \ref{results.crit}.
 While each of the $100$ designs $M$ is independently randomized applying Owen's scrambling \cite{OwenScrambling}, designs $A$ are constructed by randomly selecting matrix $L$ (uniformly among all $2^{r(r-1)/2}$ choices) and vectors $\ve_\ell$ used in equation (\ref{dig.shift}).
 In addition, we also show in Figure \ref{results.crit} the results obtained with a Latin Hypercube design (LH design) with an equal number of points as in design $A$.
+LH designs are the standard designs used in the replication procedure to estimate first-order indices.
 The x-axis corresponds to the number of design points $N$ and the y-axis to the value of the criterion.
@@
 As expected, design $M$ performs the best and the estimated slope of the discrepancy curve ($-0.72$) falls within the expected range for Sobol' sequences \cite{Morokoff}.
-Although design $A$ does not perform as well as design $M$, it outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $M$.
+Although design $A$ does not perform as well as design $M$, it outperforms a classic LH design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $M$.
 \begin{figure}
@@
 \centering
-\includegraphics[scale=0.4]{discrep.pdf}
+\includegraphics[scale=0.38]{discrep.pdf}
 \hspace*{0.1cm}
-\includegraphics[scale=0.4]{mindist.pdf}
+\includegraphics[scale=0.38]{mindist.pdf}
 \end{figure}

### 2016-06-29 crass/crassnew.tex
Adding a little more explanatio in section 3.1 (CRASS)

@@
 We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_\ell$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_\ell$.
-To ensure that the $2$-dimensional projections between $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other.
-Our choice of generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ is based on the results obtained by Joe and Kuo in \cite{Kuo}.
+To ensure that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other.
+We choose $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ to be the first $2s$ generating matrices suggested by Joe and Kuo in \cite{Kuo}, where they minimized the $t$-value for all $2$ dimensional projections.
 \bigskip

### 2016-06-30 FunctionsTest/cubSobol_SI_all_g.m
First changes to fix estimator in cubSobol_g_SI_all

@@ -243,9 +243,9 @@ elseif strcmp(out_param.measure,'uniform')
 end
 
 % First and total order indices estimators and function evaluations
-Sfo  = @(b,c) min(max(max(b(:,1),0)./max((c(:,2)-b(:,3).^2),0),0),1); % S function for first order
-% ffo = @(xpts,u,fx,fy,fxy,fzx) (fx - 1/2*mean(fx + fxy)).*(fxy - 1/2*mean(fx + fxy));
+Sfo  = @(down,up) min(max(max(down(:,1),0)./max((up(:,2)-down(:,3).^2),0),0),1); % S function for first order
 ffo = @(xpts,u,fx,fy,fxy,fzx) fx.*(fxy - fy);
+% ffo = @(xpts,u,fx,fy,fxy,fzx) (fx - 1/2*mean(fx + fxy)).*(fxy - 1/2*mean(fx + fxy));
 Sfo_s = Sfo; % S function for first order small
 ffo_s = @(xpts,u,fx,fy,fxy,fzx) (fx - fzx).*(fxy - fy); % We redefine the non normalized estimator
     % fzx is only used for the small indices. But we needed as input for
@@ -275,10 +275,12 @@ for u = 1:out_param.d
         INDICES(r,u).CStilde_low = CStilde_low_fx2_fx(:,1);
         INDICES(r,u).CStilde_up = CStilde_up_fx2_fx(:,1);
         if r == 1
-            INDICES(r,u).S = Sfo;
+            INDICES(r,u).Smin = @(down,up) Sfo(down,up);
+            INDICES(r,u).Smax = @(down,up) Sfo(up,down);
             INDICES(r,u).f = ffo;
         else
-            INDICES(r,u).S = Stot;
+            INDICES(r,u).Smin = @(down,up) Stot(down,up);
+            INDICES(r,u).Smax = @(down,up) Stot(up,down);
             INDICES(r,u).f = ftot;
         end
         INDICES(r,u).est_int = est_int_fx2_fx(:,1); %initialize mean estimates for each integral in the numerator
@@ -302,7 +304,7 @@ fzx = []; % We set it empty. So if it is empty, we only evaluate it 1 time.
 for u = 1:out_param.d
[…]

### 2016-06-30 crass/crassnew.tex
Last typos in crassnew.tex

@@
 \label{rep.designs}
-Consider $\vx \in [0,1)^s$, and $\vx_u \in [0,1)^{s-|u|}$ the subset of elements of $\vx$ given by $u\subsetneq \{1,\dots,s\}$, where $|u|$ is the cardinality of $u$.
+Consider $\vx \in [0,1)^s$, and $\vx_u \in [0,1)^{|u|}$ the subset of elements of $\vx$ given by $u\subsetneq \{1,\dots,s\}$, where $|u|$ is the cardinality of $u$.
 Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1)^{s}$, and denote by $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp.
@@
 $\mathcal{P}'$) indexed by $u$.
-We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a=1,\dots,s-1$, if for any $u\subsetneq \{1,\dots,s\}$ with $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
+We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a=1,\dots,s-1$, if for any $u\subsetneq \{1,\dots,s\}$ with $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$, perhaps in a different order.
 \end{e-definition}
@@
 
-By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limit case where $m\rightarrow\infty$, we can define the $(t,s)$-sequence as:
+By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limiting case where $m\rightarrow\infty$, we can define the $(t,s)$-sequence as:
 \begin{e-definition}%[$(t,s)$-sequence]
@@
 To ensure that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other.
-We choose $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ to be the first $2s$ generating matrices suggested by Joe and Kuo in \cite{Kuo}, where they minimized the $t$-value for all $2$ dimensional projections.
+We choose $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ to be the first $2s$ generating matrices suggested by Joe and Kuo in \cite{Kuo}, not necessarily in this order.
+In \cite{Kuo}, Joe and Kuo minimized the $t$-value for all $2$ dimensional projections.
 \bigskip

### 2016-07-29 FunctionsTest/SI_all_example.m
Adding last changes in code for all indices and changes in example files

@@ -1,6 +1,6 @@
 clearvars
 
-abstol = 1e-3;
+abstol = 1*1e-3;
 reltol = 0e-2; % Pure absolute tolerance
 mmin = 10;
 mmax = 24; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
@@ -165,6 +165,56 @@ f = @(x) (1+1/d)^d*prod(x,2).^(1/d) +  pause_t(s);
 hyperbox = [zeros(1,d) ; ones(1,d)];
 
 R = [.1581948744, .1581948744, .1581948744, .1581948744, .1581948744, .1581948744; .1753745708, .1753745708, .1753745708, .1753745708, .1753745708, .1753745708];
+[q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d));
+SI = q;
+SI_n = out_param.n;
+SI_t = out_param.time;
+SI_s = out_param.small;
+disp(SI)
+% disp(out_param.bound_err)
+disp(SI_n)
+% disp(SI_s)
+% disp(abs(R-SI) > max(abstol,R*reltol))
+% wronga = wronga + sum(sum(abs(R-SI) > max(abstol,R*reltol)));
+% disp(['Time:' num2str(SI_t)])
+% disp(['Wrong estimates with all:' num2str(wronga)]);
+
+% disp('Running Morokoff and Caflish example ...')
+% exitflag = [];
+% exitflagt = [];
+% for j = 1:d
+%     [q,app_int,out_param] = cubSobol_SI_g(f,hyperbox,j,'measure','uniform','abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',fudge);
+%     exitflag = [exitflag out_param.exitflag];
+%     SI(1,j) = q;
+%     SI_n(1,j) = out_param.n;
+%     SI_t(1,j) = out_param.time;
+%     SI_s(1,j) = out_param.small;
+%     [q,app_int,out_param] = cubSobol_SI_g(f,hyperbox,-j,'measure','uniform','abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',fudge);
+%     exitflagt = [exitflagt out_param.exitflag];
+%     SI(2,j) = q;
[…]

### 2016-07-29 FunctionsTest/SI_fo_example.m

@@ -1,6 +1,6 @@
 clearvars
 
-abstol = 1e-3;
+abstol = 2*1e-2;
 reltol = 0e-2; % Pure absolute tolerance
 mmin = 10;
 mmax = 20; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
@@ -162,6 +162,54 @@ f = @(x) (1+1/d)^d*prod(x,2).^(1/d) +  pause_t(s);
 hyperbox = [zeros(1,d) ; ones(1,d)];
 
 R = [.1581948744, .1581948744, .1581948744, .1581948744, .1581948744, .1581948744; .1753745708, .1753745708, .1753745708, .1753745708, .1753745708, .1753745708];
+[q,app_int,out_param] = cubSobol_SI_fo_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d));
+SI = q;
+SI_n = out_param.n;
+SI_t = out_param.time;
+disp(SI)
+% disp(out_param.bound_err)
+disp(SI_n)
+% disp(SI_s)
+% disp(abs(R-SI) > max(abstol,R*reltol))
+% wronga = wronga + sum(sum(abs(R-SI) > max(abstol,R*reltol)));
+% disp(['Time:' num2str(SI_t)])
+% disp(['Wrong estimates with all:' num2str(wronga)]);
+
+% disp('Running Morokoff and Caflish example ...')
+% exitflag = [];
+% exitflagt = [];
+% for j = 1:d
+%     [q,app_int,out_param] = cubSobol_SI_g(f,hyperbox,j,'measure','uniform','abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',fudge);
+%     exitflag = [exitflag out_param.exitflag];
+%     SI(1,j) = q;
+%     SI_n(1,j) = out_param.n;
+%     SI_t(1,j) = out_param.time;
+%     SI_s(1,j) = out_param.small;
+%     [q,app_int,out_param] = cubSobol_SI_g(f,hyperbox,-j,'measure','uniform','abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',fudge);
+%     exitflagt = [exitflagt out_param.exitflag];
+%     SI(2,j) = q;
[…]

### 2016-07-29 FunctionsTest/cubSobol_SI_all_g.m

@@ -255,9 +255,12 @@ numerator_size = 1;
 % Sfo_max = @(down, up) estimate_max(down, up); % S function for first order
 % ffo1 = @(xpts,u,fx,fy,fxy,fzx) fx.*fxy;
 % ffo2 = @(xpts,u,fx,fy,fxy,fzx) 1/2*(fx + fxy);
-Sfo_min = @(down, up) estimate_min([down(1) 0 down(2:end)], [up(1) 0 up(2:end)]); % S function for first order
-Sfo_max = @(down, up) estimate_max([down(1) 0 down(2:end)], [up(1) 0 up(2:end)]); % S function for first order
-ffo = @(xpts,u,fx,fy,fxy,fzx) fx.*(fxy - fy); % ffo = @(xpts,u,fx,fy,fxy,fzx) (fx - 1/2*mean(fx + fxy)).*(fxy - 1/2*mean(fx + fxy));
+Sfo_min = @(down, up) estimate_min([down(1) down(end) down(2:end)], [up(1) up(end) up(2:end)]); % S function for first order
+Sfo_max = @(down, up) estimate_max([down(1) down(end) down(2:end)], [up(1) up(end) up(2:end)]); % S function for first order
+ffo = @(xpts,u,fx,fy,fxy,fzx) fx.*fxy;
+% Sfo_min = @(down, up) estimate_min([down(1) 0 down(2:end)], [up(1) 0 up(2:end)]); % S function for first order
+% Sfo_max = @(down, up) estimate_max([down(1) 0 down(2:end)], [up(1) 0 up(2:end)]); % S function for first order
+% ffo = @(xpts,u,fx,fy,fxy,fzx) fx.*(fxy - fy); % ffo = @(xpts,u,fx,fy,fxy,fzx) (fx - 1/2*mean(fx + fxy)).*(fxy - 1/2*mean(fx + fxy));
 
 Sfo_s_min = @(down,up) estimate_min([down(1) 0 down(2:end)], [up(1) 0 up(2:end)]); % S function for first order small
 Sfo_s_max = @(down,up) estimate_max([down(1) 0 down(2:end)], [up(1) 0 up(2:end)]); % S function for first order small

### 2016-07-29 article.tex
Changes in article.tex and file containing the Brownian motion example

@@
 \newcommand{\vx}{\bvec{x}}
+\newcommand{\vI}{\bvec{I}}
 \newcommand{\vk}{\bvec{k}}
@@
 \label{first.order}
-\underline{\tau}_u^2  &= \int_{[0,1)^{2d-1}} (f(\vx)-\mu)(f(\vx_{u}:{\vx'}_{-u})-\mu), \\
+\underline{\tau}_u^2  &= \int_{[0,1)^{2d-1}} (f(\vx)-\mu)(f(\vx_{u}:{\vx'}_{-u})-\mu)d\vx d{\vx'}, \\
 \label{total.effect}
-\ov{$\tau$}_u^2 &= \int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}, \qquad u \in \mathcal{D},
+\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}, \qquad u \in \mathcal{D},
 \end{align}
 where mean and variance of $f$ respectively writes as:
-\[ \mu = \int_{[0,1)^{2d}} f(\vx) d{\vx}, \ \qquad
-\sigma^2 = \int_{[0,1)^{2d}} f(\vx)^2d{\vx} - \mu^2 .\]
+\[ \mu = \int_{[0,1)^{d}} f(\vx) d{\vx}, \ \qquad
+\sigma^2 = \int_{[0,1)^{d}} f(\vx)^2d{\vx} - \mu^2 .\]
 Most of the time, the complexity of $f$ causes the computation of $\mu$, $\sigma^2$ and integrals (\ref{first.order}) and (\ref{total.effect}) to be intractable.
@@
 \label{section.error} 
-We assume that we have an algorithm $\widehat{I}(f;\varepsilon)$ such that $\abs{I(f)-\widehat{I}(f;\varepsilon)}\leq \varepsilon$.
-For instance, the guaranteed quasi-Monte Carlo cubatures described in \cite{-} and \cite{-}.
-Therefore, we will always assume that the true integral $I(f)$ lies in $[\widehat{I}(f;\varepsilon)-\varepsilon,\widehat{I}(f;\varepsilon)+\varepsilon]$.
+\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
+In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$.
+In both cases, regular and normalized indices can be approximated by estimating some integrals,
+\begin{align*}
+S_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
+\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
+\end{align*}
+Therefore, we can define $S_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
+If we can estimate $\vI$ such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$, then we can define the following estimators for the Sobol' indices:
+\begin{align*}
+\widehat{S}_u & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right) \\
+\varepsilon_{S_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right)
+\end{align*}
+where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
 
-Sobol' indices can be seen as operators over functions that can be simplified as functions whose entries are integrals.
+\subsection{Reliable Estimation Using Quasi-Monte Carlo}
+In \cite{HicJim} we proposed an algorithm based on digital nets that estimates hight dimensional integrals whose error lies within a user-input error tolerance.
+This algorithm finds the number of data points automatically.
+We will refer to it as $\widehat{I}(f;\varepsilon)$, where $f$ is the function to integrate and $\varepsilon$ the user-input error tolerance.
 
-The case of $correlation 2$
-Je viens de comprendre, prendre S(LB,UB) comme le minimum (LowerBound, UpperBound) et S(UB,LB) comme le maximum est trop simple. Il faut construire le $S_{max}$ et $S_{min}$ en fonction du cas.
-Pour nous, $a - b*c + c^2$ est un paraboloïde hyperbolique.
-La droite avec plus de décroissement est $0+\lambda(2,1)$ [prends la dérivée par rapport à $c$ et l'on a $c=b/2$] et la perpendiculaire, celle de plus accroissement (symmetrie).
-Sur notre région carré, le point de max valeur de $S$ sera le point le plus eloignée de la droite $0+\lambda(2,1)$, et le minimum, sera sur cette droite le plus eloignée de $b = 0$ (si l'on substitue $c=b/2$, on obtient que restreint à cette droite, la fonction est $a-b^2/4$).
-
-$\bullet$ Max at $= \hat{a} + e_a$  ,  $\hat{b} - sign(\hat{c}-\hat{b}/2) e_b$,  $\hat{c} + sign(\hat{c}-\hat{b}/2) e_c$
-
-$\bullet$ Min at $= \hat{a} - e_a$  ,  $\hat{b} + sign(\hat{b}) e_b$  ,  $(\hat{b} + sign(\hat{b}) e_b)/2$
-\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
+The main result from the article if that for all $f\in\mathcal{C}$,
+\[
+\abs{\int_{\cube} f(\vx)\,d\vx - \widehat{I}(f;\varepsilon)}\leq a(r,m)\sum_{\kappa=\left \lfloor 2^{m-r-1}\right \rfloor}^{2^{m-r}-1} \abs{\tf_{m,\kappa}}\leq \varepsilon.
+\]
+\begin{itemize}
+\item $\tf_{m,\kappa}=$ discrete Fourier Walsh coefficients of $f$.
+\item $a(r,m)=$ inflation factor that depends on $\mathcal{C}$.
+\end{itemize}
 
@@
 \subsection{Real case model}
+The Brownian motion is widely used in many applications.
+Thus, the following example might be interesting to understand what Sobol' indices can explain in some of these applications.
+For instance, if we want to estimate the expected value of the maximum of a discretized Brownian motion whose covariance matrix is $\Sigma$, our goal is to estimate
+\begin{align*}
+\mathbb{E} \left[\max(\bvec{B}_t)\right] &= \int_{\mathbb{R}^d} \max(\bvec{B}_t) \frac{{\rm e}^{\bvec{B}_t^T\Sigma^{-1}\bvec{B}_t}}{(2\pi)^{d/2}|\Sigma|^{1/2}}\,d\bvec{B}_t \\
+&= \int_{[0,1]^d} \max(f_{\rm Chol}(\vx)) \,d\vx \\
+&= \int_{[0,1]^d} \max(f_{\rm PCA}(\vx)) \,d\vx.
+\end{align*}
+The last two equalities are obtained through two different subsitutions corresponding to the \textit{Cholesky} construction of the Brownian motion, and the \textit{PCA} construction.
+For instance, if we take 10 dimensions and $t_i=i/10$, using the Cholesky construction $S_{1} = 24\%$, $S_{2} = 16\%$, $S_{3} = 13\%$, $S_{4} = 10\%$, and $\overline{S}_{1}=24\%$, $\overline{S}_{2}=18\%$, $\overline{S}_{3}=15\%$, $\overline{S}_{4} = 13\%$.
+However, using the PCA construction, $S_{1} = 89\%$, $S_{2} = 2\%$, $S_{3} = 1\%$, $S_{4} = 0\%$, and $\overline{S}_{1}=94\%$, $\overline{S}_{2}=7\%$, $\overline{S}_{3}=3\%$, $\overline{S}_{4} = 2\%$.
+This shows that the PCA construction will be better to estimate the above expectation using quasi-Monte Carlo methods since it has a lower effective dimensionality.
+
+For those who were curious about the actual value of $\mathbb{E} \left[\max(\bvec{B}_t)\right]$, it is approximately 0.5935.
+Nevertheless, the Brownian Motion is a continuous time process.
+Thus, in order to estimate the expected value on a continuous time Browninan motion, one could either use a multilevel method, or a multivariate decomposition method to estimate this infinite dimensional integral.
 

### 2016-07-29 FunctionsTest/article_examples_brownian_motion.m

@@ -1,0 +1,23 @@
+d = 2;
+time_vec = (1:d)/d;
+Sigma=bsxfun(@min, time_vec', time_vec);
+
+% % Time differencing
+fTD = @(x) max(sqrt(1/d)*cumsum(gail.stdnorminv(x'), 2))';
+% Cholesky
+A = chol(Sigma,'lower'); % A*A' = Sigma
+fChol = @(x) max((A*(gail.stdnorminv(x)')))';
+%PCA
+[Eigenvectors,Eigenvalues]=eig(Sigma,'vector');
+[~, order] = sort(Eigenvalues, 'descend');
+A = Eigenvectors(:,order)*diag(Eigenvalues(order).^(1/2));% A*A' = Sigma
+fPCA = @(x) max((A*(gail.stdnorminv(x)')))';
+
+% Sobol indices estimation
+hyperbox = [zeros(1,d) ; ones(1,d)];
+abstol = 1e-3;
+reltol = 0;
+mmin = 22;
+mmax = 22;
+[q,app_int,out_param] = cubSobol_SI_all_g(fPCA,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax);
+round(q*100)

### 2016-08-06 article.tex
Adding more about reliable cubatures in article.tex

@@
 \subsection{Reliable Estimation Using Quasi-Monte Carlo}
+
+We assume we have an embedded sequence of digital nets in base $b$,
+\[
+\mathcal{P}_0=\{\bvec{0}\}\subset\dots\subset\mathcal{P}_m=\{\vx_i\}_{i=0}^{b^m}\subset\dots\subset\mathcal{P}_\infty=\{\vx_i\}_{i=0}^{\infty}.
+\]
+
+Each $\mathcal{P}_m$ has a group structure under the digit wise addition.
+Analogously, we can also define the dual nets as $\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vx}{\vk}=0,\, \vx\in\mathcal{P}_m\}$,
+\[
+\mathcal{P}_0^\perp=\left\{\mathbb{N}_0^d\right\}\supset\dots\supset\mathcal{P}_\infty=\{\bvec{0}\}.
+\]
+
+An important property is that for any Walsh basis $\phi_{\vk}(\vx)$
+\[
+\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\phi_{\vk}(\vx)=
+\begin{cases}
+1,\quad \vk\in\mathcal{P}_m^\perp, \\
+0,\quad \vk\notin\mathcal{P}_m^\perp
+\end{cases}
+\]
+
+Therefore,
+\[
+\abs{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}=\abs{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}}
+\]
+
 In \cite{HicJim} we proposed an algorithm based on digital nets that estimates hight dimensional integrals whose error lies within a user-input error tolerance.

### 2016-08-06 article.tex
changes Laurenté

@@
 
-\section{Estimation of Sobol' indices}
+\section{Backgrounds on Sobol' indices}
+
 \subsection{Definition of Sobol' indices}
 We adopt the same notations introduced by Owen in \cite{Owen}.
-Denote by $\vx \in [0,1)^d$ a point with components $x_1,\dots,x_d$ and set $\mathcal{D}=\{1,\dots,d\}$.
+Denote by $f$ a numerical model, by $\vx=(x_1,\dots,x_d)$ its vector of inputs and set $\mathcal{D}=\{1,\dots,d\}$.
+The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
 Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality.
@@
 
-The problem of interest here is the evaluation of first-order and total effect Sobol' indices. The computation of these indices is performed based on the following integral formula:
+The problem of interest here is the evaluation of first-order and total effect Sobol' indices.
+The computation of these indices is performed based on the following integral formula for their numerators:
 \begin{align}
 \label{first.order}
-\underline{\tau}_u^2  &= \int_{[0,1)^{2d-1}} (f(\vx)-\mu)(f(\vx_{u}:{\vx'}_{-u})-\mu)d\vx d{\vx'}, \\
+\underline{\tau}_u^2  &= \int_{[0,1)^{2d-1}} \left(f(\vx)-
+f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}, \\
 \label{total.effect}
@@
 \end{align}
-where mean and variance of $f$ respectively writes as:
-\[ \mu = \int_{[0,1)^{d}} f(\vx) d{\vx}, \ \qquad
-\sigma^2 = \int_{[0,1)^{d}} f(\vx)^2d{\vx} - \mu^2 .\]
+The variance of $f$ is evaluated by:
+\[ \sigma^2 = \int_{[0,1)^{d}} f(\vx)^2d{\vx} - \mu^2, \text{ with } \ \mu = \int_{[0,1)^{d}} f(\vx) d{\vx}.\]
 Most of the time, the complexity of $f$ causes the computation of $\mu$, $\sigma^2$ and integrals (\ref{first.order}) and (\ref{total.effect}) to be intractable.
 In such case, one needs to rely on an estimation of these quantities.
-In the following, we propose two iterative estimation procedures to evaluate first-order and total-effect Sobol' indices.
 
 \subsection{Estimation of Sobol' indices}
-
+In this section we review two Monte Carlo procedures for the estimation of Sobol' indices.
 We define by design a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ obtained by sampling each variable $x_j$ $n$ times.
@@
 Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid [0,1)^{2d}$.
+\bigskip
+
 One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
@@
 \label{first.order.est}
-\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-\hat{\mu})(f(\vx_{i,u}:{\vx'}_{i,-u})-\hat{\mu}),\\
+\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_i)-f(\vx_{i,u}:{\vx'}_{i,-u}\right)f(\vx'_i),\\
 \label{total.effect.est}
-\widehat{\ov{$\tau$}_u^2} & = \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D}
+\widehat{\ov{$\tau$}_u^2} & = \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
 \end{align}
-using for $\mu$ the efficient estimator introduced in \cite{Monod, Janon}:
+using for $\sigma^2$ the classic estimator:
 \begin{equation}
- \hat{\mu} = \frac{1}{2n} \sum \limits_{i=0}^{n-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}).
+ \widehat{\sigma}^2 = \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i)^2 - \widehat{\mu}^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
 \label{mu.est}
@@
 The estimation of a single pair ($\underline{\tau}_u^2$, $\ov{$\tau$}_u^2$) requires $3n$ evaluations of the model $f$.
-Using a combinatorial formalism, Saltelli \cite[Theorem 1]{Saltelli} proposed the following strategy to reduce the estimation cost:
+Using a combinatorial formalism, in \cite[Theorem 1]{Saltelli} Saltelli proposes the following estimation strategy:
 \begin{theorem}
@@
 $\mathcal{P}'$) indexed by $u$.
-We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a$ if $\forall \ u \subsetneq \mathcal{D}$ of cardinality $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1)^a$.
+We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if $\forall \ u \subsetneq \mathcal{D}$ of cardinality $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1)^a$.
 We note $\pi_u$ the permutation reordering the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
@@
 \cite{Mara} to the case of closed second-order indices.
+In the following we refer to this method as replication procedure.
 \bigskip
 
-\subsection{Recursive estimation procedures}
-We propose here two recursive procedures two estimate first-order and total effect Sobol' indices.
-Each procedure combines quasi-Monte Carlo sampling with respectively the estimation strategy proposed by Saltelli (Theorem \ref{saltelli.theorem}) and the estimation strategy based on replicated designs.
-In the following, we refer to these two procedures as procedure $A$ and $B$.
+\subsection{Towards a robust estimation}
+The aim of this paper is to propose a recursive estimation procedure to estimate Sobol' indices.
+The choice of the stopping criterion is the key point of this paper.
+The two estimation procedures reviewed in the previous section can be rendered recursive.
+In \cite{Gilquin16}, the authors propose a recursive version of the replication procedure.
+The stopping criterion of the recursive algorithm is an absolute difference between estimates computed on consecutive steps.
+
+More generally, in most recursive approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly upon the estimates.
+Such stopping criteria often involved hyperparameters hard to tweak but above all fail to guarantee any error bound on the estimation.
 \bigskip
 
-Using a recursive estimation procedure requires to write a recursive formula for estimators (\ref{first.order.est}) and (\ref{total.effect.est}).
-For the sake of readability of the paper, the corresponding recursive formulas are detailed in equations (\ref{first.order.est.rec}) and (\ref{total.effect.est.rec}) in the Annexe \ref{recursive.formulas}.
+Our recursive procedure stands apart from others approaches by the construction of a robust stopping criterion.
+This criterion is an error bound based on the discrete Walsh decomposition of integrals (\ref{first.order}) and (\ref{total.effect}).
+This decomposition use the close set property of digital sequences.
+As such, our recursive procedure relies on the iterative construction of Sobol' sequence.
 
-Procedures $A$ and $B$ also require to iteratively construct two designs $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$.
-These two designs are two Sobol' sequences.
 Background on Sobol' sequences are provided in \cite{crass}.
-We recall here that a $d$-dimensional Sobol' sequence is generated with a set of $d$ generating matrices (one per coordinate).
-The construction of $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ is carried out according to the following recursive scheme :
-\begin{equation}
-\left\lbrace \begin{array}{l}
-\mathcal{P}_0= B_0 \\
-\mathcal{P}_\ell= \mathcal{P}_{\ell-1} \cup B_\ell \end{array}\right. ,\qquad
-\hspace*{0.5cm}
-\left\lbrace \begin{array}{l}
-\mathcal{P}'_0= {B'}_0 \\
-\mathcal{P}'_\ell= \mathcal{P}'_{\ell-1} \cup {B'}_\ell \end{array}\right.,
-\label{rec.scheme}
-\end{equation}
-where at step $\ell\geq0$, $B_\ell$ and $B'_\ell$ are new sets of $2^{\ell-1}$ points added to refine $\mathcal{P}_{\ell-1}$ and $\mathcal{P}'_{\ell-1}$.
-In the following, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ refer to the two Sobol' sequences constructed following the multiplicative approach presented in \cite{crass}.
-This approach guarantee that at each step $\ell\geq0$, $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ are two replicated designs of order $1$.
-
-$\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can either be used with procedure $A$ to estimate all first-order and all total effect Sobol' indices or with procedure $B$ to estimate all first-order Sobol' indices.
-Algorithms \ref{procedureA} and \ref{procedureB} summarize the main steps of each procedure.
-\begin{algorithm}[!ht]
-\caption{Procedure $A$}
-\begin{algorithmic}[1]
-\vspace*{0.2cm}
-\State Set: $\ell \leftarrow 1$, $\mathcal{P}_{0} \leftarrow B_0$, ${\mathcal{P}'}_{0} \leftarrow {B'}_0$
-\While {stopping criterion}
-\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
-
-\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
-\State Compute $\{f(\vx_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$
-\For {$u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$}
-\State Construct design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=2^{\ell-1}}^{2^{\ell}-1}$
-\State Compute  $\{f(\vx_{i,u},{\vx'}_{i,-u})\}_{i=2^{\ell-1}}^{2^\ell-1}$
-\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ with formula (\ref{first.order.est.rec}) and (\ref{total.effect.est.rec})
-\EndFor
-\State $\ell \leftarrow \ell + 1$
-\EndWhile
-\State Return $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ for all $u \in \mathcal{D}$.
-\end{algorithmic}
-\label{procedureA}
-\end{algorithm}
-\begin{algorithm}[!ht]
-\caption{Procedure $B$}
-\begin{algorithmic}[1]
-\vspace*{0.2cm}
-\State Set: $\ell \leftarrow 1$, $\mathcal{P}_{0} \leftarrow B_0$, ${\mathcal{P}'}_{0} \leftarrow {B'}_0$
-\While {stopping criterion}
-\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
-
-\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
-\State Compute $\{f(\vx_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$
-\For {$u \in \mathcal{D}$}
-\State  order $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ into $\{\pi_u(f({\vx'}_i))\}_{i=2^{\ell-1}}^{2^\ell-1}$
-\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ with formula (\ref{first.order.est.rec})
-\EndFor
-\State $\ell \leftarrow \ell + 1$
-\EndWhile
-\State Return $\widehat{\underline{\tau}_u^2}^{(\ell)}$ for all $u \in \mathcal{D}$.
-\end{algorithmic}
-\label{procedureB}
-\end{algorithm}
-
-The choice of the stopping criterion is the key point of this paper.
-In most recursive approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly from the estimates.
-For example, an absolute difference between estimates computed on consecutive steps.
-Such stopping criteria are often hard to tweak but above all fail to guarantee any error bound on the estimation.
-Our stopping criterion is presented and discussed in Section \ref{section.error}.
-The criterion is an error bound based on the discrete Walsh decomposition of integrals (\ref{first.order}) and (\ref{total.effect}).
-
-\subsection{Improvements}
-This section discusses two improvements to ease the estimation of Sobol' indices with procedures $A$ and $B$.
-
-\bigskip
-
-The first improvement focus on the use of a better estimator to evaluate small first-order Sobol' indices with procedure $A$.
-This estimator is called ``Correlation 2" and was introduced by Owen in \cite{Owen}.
-Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small closed Sobol' indices.
-Our aim is to show that using ``Correlation 2" in procedure $A$ may reduces the total number of model evaluations.
-``Correlation 2" formula writes as follows:
-\begin{equation}
-\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i))
-\label{correlation2}
-\end{equation}
-It uses an extra set of $n$ model evaluations to estimate $\widehat{\underline{\tau}_u^2}$.
-Owen explains the effectiveness of ``Correlation 2" as follows.
-If the main effect of $\vx_u$ is small then $f(\vx)$ will be almost entirely explained by $\vx_{-u}$.
-The two terms $(f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))$ and $(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i))$ should then be small quantities as well as (\ref{correlation2}).
-
-We discuss now the potential improvement brought by the use of ``Correlation 2".
-Assume that the number of small first-order indices is known and equals $\alpha$.
-Then, the cost of procedure $A$ including ``Correlation 2" to estimate small indices writes:
-\[ n(d-\alpha) + 2 n'\alpha + 2\max(n,n'),\]
-where: \begin{itemize}
-\item[$\bullet$] $n(d-\alpha)$ is the number of evaluations induced by the $d-\alpha$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i\geq0}$ to estimate all non small indices, 
-\item[$\bullet$] $2 n'\alpha$ is the number of evaluations induced by the $2\alpha$ designs $\{\vz_{i,u}:\vx_{i,-u}\}_{i\geq0}$ and $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i\geq0}$ to estimate all small indices,
-\item[$\bullet$] $2\max(n,n')$ is the number of evaluations  induced by the $2$ designs $\{\vx_{i}\}_{i\geq0}$ and $\{{\vx'}_{i}\}_{i\geq0}$.
-\end{itemize}
-At the opposite, the cost of procedure $A$ excluding ``Correlation 2" writes: 
-\[ n(d-\alpha) + n\alpha + 2n.\]
-It is straightforward that procedure $A$ including ``Correlation 2" performs equally well or better when $n' \leq 2n$.
-Furthermore, since we are working with Sobol' sequences $n'=2^{k'}$ and $n=2^{k}$.
-Hence, procedure $A$ including ``Correlation 2" performs equally well or better when the recursive estimation procedure finished at least one step sooner.
-Illustrations of this improvement will be provided in Section \ref{appli}.
-
-\bigskip
-
-The second improvement focus on the choice of the $2d$ generating matrices that generate the two Sobol' sequences $\mathcal{P}_\ell$  and ${\mathcal{P}'}_\ell$ in procedure $B$.
-
-We note by $C_1,\dots,C_d$ the matrices generating $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and ${C'}_1,\dots,{C'}_d$ those generating $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$.
-In the multiplicative approach \cite{crass}, these $2d$ matrices are selected as the first $2d$ elements of the set found by Kuo and Joe in \cite{Kuo}.
-This set is composed of generating matrices that optimize the $2$-dimensional projection $t$-values.
-
-%In procedure $A$, each design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i\geq0}$ constructed in step $6$ of Algorithm \ref{procedureA} is a $d$-dimensional Sobol' sequence generated by the $d$-subset: $${C'}_1,\dots,{C'}_{u-1},C_u,{C'}_{u+1},\dots,C_d.$$ Therefore, $2$-dimensional projection $t$-values are still optimized.
-
-In procedure $B$, each permutation $\pi_u$ applied in step $6$ of Algorithm \ref{procedureB} results in a design $\{\vx_{i,u}:{\vx'}_{\pi_u(i),-u}\}_{i=0}^{2^\ell-1}$.
-The $d$ generating matrices corresponding to this design are:
-$${C'}_1U_u,\dots,{C'}_{u-1}U_u,C_u,{C'}_{u+1}U_u,{C'}_dU_u$$ where $U_u$ is a a full rank upper triangular matrix verifying $C_u={C'}_uU_u$.
-The right multiplication by $U_u$ is the digital representation of the ordering by $\pi_u$.
-
-%\section{Estimators: Correlation 2 Oracle 2}
-%\subsection{Choice and parameters (threshold small?)}
-%\subsection{Cost discussion: for first-order Consider or not total order}
+The iterative construction of the Sobol' sequences is performed accordingly to the multiplicative  approach presented in \cite{crass}.
+The construction of our stopping criterion is the subject of the next section \ref{section.error}.
+Our recursive estimation procedure is presented in section \ref{section.recursive.procedure}.
 
@@
 
+\section{Recursive estimation procedure}
+\label{section.recursive.procedure}
+%
+%$\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can either be used with procedure $A$ to estimate all first-order and all total effect Sobol' indices or with procedure $B$ to estimate all first-order Sobol' indices.
+Algorithms \ref{procedureA} and \ref{procedureB} summarize the main steps of each procedure.
+%\begin{algorithm}[!ht]
+%\caption{Procedure $A$}
+%\begin{algorithmic}[1]
+%\vspace*{0.2cm}
+%\State Set: $\ell \leftarrow 1$, $\mathcal{P}_{0} \leftarrow B_0$, ${\mathcal{P}'}_{0} \leftarrow {B'}_0$
+%\While {stopping criterion}
+%\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
+%
+%\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
+%\State Compute $\{f(\vx_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$
+%\For {$u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$}
+%\State Construct design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=2^{\ell-1}}^{2^{\ell}-1}$
+%\State Compute  $\{f(\vx_{i,u},{\vx'}_{i,-u})\}_{i=2^{\ell-1}}^{2^\ell-1}$
+%\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ with formula (\ref{first.order.est.rec}) and (\ref{total.effect.est.rec})
+%\EndFor
+%\State $\ell \leftarrow \ell + 1$
+%\EndWhile
+%\State Return $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ for all $u \in \mathcal{D}$.
+%\end{algorithmic}
+%\label{procedureA}
+%\end{algorithm}
+%\begin{algorithm}[!ht]
+%\caption{Procedure $B$}
+%\begin{algorithmic}[1]
+%\vspace*{0.2cm}
+%\State Set: $\ell \leftarrow 1$, $\mathcal{P}_{0} \leftarrow B_0$, ${\mathcal{P}'}_{0} \leftarrow {B'}_0$
+%\While {stopping criterion}
+%\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
+%
+%\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
+%\State Compute $\{f(\vx_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$
+%\For {$u \in \mathcal{D}$}
+%\State  order $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ into $\{\pi_u(f({\vx'}_i))\}_{i=2^{\ell-1}}^{2^\ell-1}$
+%\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ with formula (\ref{first.order.est.rec})
+%\EndFor
+%\State $\ell \leftarrow \ell + 1$
+%\EndWhile
+%\State Return $\widehat{\underline{\tau}_u^2}^{(\ell)}$ for all $u \in \mathcal{D}$.
+%\end{algorithmic}
+%\label{procedureB}
+%\end{algorithm}
+%
+%\subsection{Improvements}
+%This section discusses two improvements to ease the estimation of Sobol' indices with procedures $A$ and $B$. 
+%
+%\bigskip
+%
+%The first improvement focus on the use of a better estimator to evaluate small first-order Sobol' indices with procedure $A$.
+This estimator is called ``Correlation 2" and was introduced by Owen in \cite{Owen}.
+Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small closed Sobol' indices.
+Our aim is to show that using ``Correlation 2" in procedure $A$ may reduces the total number of model evaluations.
+``Correlation 2" formula writes as follows:
+%\begin{equation}
+%\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i))
+%\label{correlation2}
+%\end{equation}
+%It uses an extra set of $n$ model evaluations to estimate $\widehat{\underline{\tau}_u^2}$.
+Owen explains the effectiveness of ``Correlation 2" as follows.
+If the main effect of $\vx_u$ is small then $f(\vx)$ will be almost entirely explained by $\vx_{-u}$.
+The two terms $(f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))$ and $(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i))$ should then be small quantities as well as (\ref{correlation2}).
+%
+%We discuss now the potential improvement brought by the use of ``Correlation 2".
+Assume that the number of small first-order indices is known and equals $\alpha$.
+Then, the cost of procedure $A$ including ``Correlation 2" to estimate small indices writes:
+%\[ n(d-\alpha) + 2 n'\alpha + 2\max(n,n'),\]
+%where: \begin{itemize}
+%\item[$\bullet$] $n(d-\alpha)$ is the number of evaluations induced by the $d-\alpha$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i\geq0}$ to estimate all non small indices, 
+%\item[$\bullet$] $2 n'\alpha$ is the number of evaluations induced by the $2\alpha$ designs $\{\vz_{i,u}:\vx_{i,-u}\}_{i\geq0}$ and $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i\geq0}$ to estimate all small indices,
+%\item[$\bullet$] $2\max(n,n')$ is the number of evaluations  induced by the $2$ designs $\{\vx_{i}\}_{i\geq0}$ and $\{{\vx'}_{i}\}_{i\geq0}$.
+%\end{itemize}
+%At the opposite, the cost of procedure $A$ excluding ``Correlation 2" writes: 
+%\[ n(d-\alpha) + n\alpha + 2n.\]
+%It is straightforward that procedure $A$ including ``Correlation 2" performs equally well or better when $n' \leq 2n$.
+Furthermore, since we are working with Sobol' sequences $n'=2^{k'}$ and $n=2^{k}$.
+Hence, procedure $A$ including ``Correlation 2" performs equally well or better when the recursive estimation procedure finished at least one step sooner.
+Illustrations of this improvement will be provided in Section \ref{appli}.
+%
+%\bigskip
+%
+%The second improvement focus on the choice of the $2d$ generating matrices that generate the two Sobol' sequences $\mathcal{P}_\ell$  and ${\mathcal{P}'}_\ell$ in procedure $B$.
+%
+%We note by $C_1,\dots,C_d$ the matrices generating $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and ${C'}_1,\dots,{C'}_d$ those generating $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$.
+%In the multiplicative approach \cite{crass}, these $2d$ matrices are selected as the first $2d$ elements of the set found by Kuo and Joe in \cite{Kuo}.
+This set is composed of generating matrices that optimize the $2$-dimensional projection $t$-values.
+%
+%%In procedure $A$, each design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i\geq0}$ constructed in step $6$ of Algorithm \ref{procedureA} is a $d$-dimensional Sobol' sequence generated by the $d$-subset: $${C'}_1,\dots,{C'}_{u-1},C_u,{C'}_{u+1},\dots,C_d.$$ Therefore, $2$-dimensional projection $t$-values are still optimized.
+%
+%In procedure $B$, each permutation $\pi_u$ applied in step $6$ of Algorithm \ref{procedureB} results in a design $\{\vx_{i,u}:{\vx'}_{\pi_u(i),-u}\}_{i=0}^{2^\ell-1}$.
+The $d$ generating matrices corresponding to this design are:
+%$${C'}_1U_u,\dots,{C'}_{u-1}U_u,C_u,{C'}_{u+1}U_u,{C'}_dU_u$$ where $U_u$ is a a full rank upper triangular matrix verifying $C_u={C'}_uU_u$.
+The right multiplication by $U_u$ is the digital representation of the ordering by $\pi_u$.
+
+%\section{Estimators: Correlation 2 Oracle 2}
+%\subsection{Choice and parameters (threshold small?)}
+%\subsection{Cost discussion: for first-order Consider or not total order}
+
 \section{Applications}
@@
 
-\newpage
-\section{Annexes}
+%\newpage
+%\section{Annexes}
 
-\subsection{recursive formulas}
-\label{recursive.formulas}
-
-Let $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$ be the two points sets constructed with the recursive scheme (\ref{rec.scheme}).
-
-\subsection{Recursive formula for $\hat{\mu}$}
-
-The quantity $\hat{\mu}$ defined by formula (\ref{mu.est}) can be recursively estimated by:
-\[\left \lbrace\begin{array}{l}
-\hat{\mu}^{(0)} = \dfrac{1}{2} \Big{(} f(\vx_0)+f(\vx_{0,u}:{\vx'}_{0,-u}) \Big{)} \\
-\\
-\hat{\mu}^{(\ell+1)} = \dfrac{1}{2} \Big{(} \hat{\mu}^{(\ell)} + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}
-\end{array}\right.\]
-\begin{proof}
-By developing $\hat{\mu}^{(\ell+1)}$:
-\begin{align*}
-\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \\
-\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \Big{(} \sum \limits_{i=0}^{2^{\ell}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
-\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \Big{(} 2 \times 2^{\ell}\hat{\mu}^{(\ell)} + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
-\end{align*}
-\end{proof}
-
-\subsection{Recursive formula for $\widehat{\underline{\tau}_u^2}$}
-
-The quantity $\widehat{\underline{\tau}_u^2}$ defined by formula (\ref{first.order.est}) can be recursively estimated by:
-\begin{equation}
-\left\lbrace \begin{array}{l}
-\widehat{\underline{\tau}_u^2}^{(0)}= (f(\vx_0)-\hat{\mu}^{(0)})(f(\vx_{0,u}:{\vx'}_{0,-u})-\hat{\mu}^{(0)}) \\
-\\
-\widehat{\underline{\tau}_u^2}^{(\ell+1)} =  \dfrac{1}{2} \widehat{\underline{\tau}_u^2}^{(\ell)} - \dfrac{1}{2} (\hat{\mu}^{(\ell)})^2 - (\hat{\mu}^{(\ell+1)})^2 + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}+1}^{2^{\ell+1}-1} f(\vx_i) f(\vx_{i,u}:{\vx'}_{i,-u})
-\end{array}\right.
-\label{first.order.est.rec}
-\end{equation}
-\begin{proof}
-By developing $\widehat{\underline{\tau}_u^2}^{(\ell+1)}$:
-\begin{align*}
-\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} (f(\vx_i)-\hat{\mu}^{(\ell+1)})(f(\vx_{i,u}:{\vx'}_{i,-u})-\hat{\mu}^{(\ell+1)}) \\
-\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(\ell+1)})^2 \\
-\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \Big{(}\sum \limits_{i=0}^{2^{\ell}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})\Big{)} -(\hat{\mu}^{(\ell+1)})^2 \\
-\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \dfrac{1}{2}\Big{(}\widehat{\underline{\tau}_u^2}^{(\ell)}-(\hat{\mu}^{(\ell)})^2\Big{)} + \frac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(\ell+1)})^2 \\
-\end{align*}
-\end{proof}
-
-\subsection{Recursive formula for} 
-%$\widehat{\ov{$\tau$}_u^2}$}
-
-The quantity $\widehat{\underline{\tau}_u^2}$ defined by formula (\ref{total.effect.est}) can be recursively estimated by:
-\begin{equation}
-\left\lbrace \begin{array}{l}
-\widehat{\ov{$\tau$}_u^2}^{(0)}= \dfrac{1}{2} \Big{(} f(\vx_0)-(f({\vx'}_{0,u}:\vx_{0,-u}) \Big{)}^2 \\
-\\
-\widehat{\ov{$\tau$}_u^2}^{(\ell+1)} = \dfrac{1}{2} \widehat{\ov{$\tau$}_u^2}^{(\ell)} + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}+1}^{2^{\ell+1}-1} \Big{(}f(\vx_i)- f({\vx'}_{i,u}:\vx_{i,-u})\Big{)}^2
-\end{array}\right.
-\label{total.effect.est.rec}
-\end{equation}
-\begin{proof}
-Straightforward by developing $\widehat{\ov{$\tau$}_u^2}^{(\ell+1)}$.
-\end{proof}
-
-\subsection{Proof proposition \ref{right.multi}}
-\label{proof.prop}
-
+%\subsection{recursive formulas}
+%\label{recursive.formulas}
+%
+%Let $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$ be the two points sets constructed with the recursive scheme (\ref{rec.scheme}).  
+%
+%\subsection{Recursive formula for $\hat{\mu}$}
+%
+%The quantity $\hat{\mu}$ defined by formula (\ref{mu.est}) can be recursively estimated by:
+%\[\left \lbrace\begin{array}{l}
+%\hat{\mu}^{(0)} = \dfrac{1}{2} \Big{(} f(\vx_0)+f(\vx_{0,u}:{\vx'}_{0,-u}) \Big{)} \\
+%\\
+%\hat{\mu}^{(\ell+1)} = \dfrac{1}{2} \Big{(} \hat{\mu}^{(\ell)} + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}
+%\end{array}\right.\]
+%\begin{proof}
+%By developing $\hat{\mu}^{(\ell+1)}$:
+%\begin{align*}
+%\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \\
+%\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \Big{(} \sum \limits_{i=0}^{2^{\ell}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
+%\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \Big{(} 2 \times 2^{\ell}\hat{\mu}^{(\ell)} + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
+%\end{align*}
+%\end{proof}
+%
+%
+%\subsection{Recursive formula for $\widehat{\underline{\tau}_u^2}$}
+%
+%The quantity $\widehat{\underline{\tau}_u^2}$ defined by formula (\ref{first.order.est}) can be recursively estimated by:
+%\begin{equation}
+%\left\lbrace \begin{array}{l}
+%\widehat{\underline{\tau}_u^2}^{(0)}= (f(\vx_0)-\hat{\mu}^{(0)})(f(\vx_{0,u}:{\vx'}_{0,-u})-\hat{\mu}^{(0)}) \\
+%\\
+%\widehat{\underline{\tau}_u^2}^{(\ell+1)} =  \dfrac{1}{2} \widehat{\underline{\tau}_u^2}^{(\ell)} - \dfrac{1}{2} (\hat{\mu}^{(\ell)})^2 - (\hat{\mu}^{(\ell+1)})^2 + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}+1}^{2^{\ell+1}-1} f(\vx_i) f(\vx_{i,u}:{\vx'}_{i,-u})
+%\end{array}\right.
+%\label{first.order.est.rec}
+%\end{equation}
+%\begin{proof}
+%By developing $\widehat{\underline{\tau}_u^2}^{(\ell+1)}$:
+%\begin{align*}
+%\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} (f(\vx_i)-\hat{\mu}^{(\ell+1)})(f(\vx_{i,u}:{\vx'}_{i,-u})-\hat{\mu}^{(\ell+1)}) \\
+%\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(\ell+1)})^2 \\
+%\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \Big{(}\sum \limits_{i=0}^{2^{\ell}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})\Big{)} -(\hat{\mu}^{(\ell+1)})^2 \\
+%\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \dfrac{1}{2}\Big{(}\widehat{\underline{\tau}_u^2}^{(\ell)}-(\hat{\mu}^{(\ell)})^2\Big{)} + \frac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(\ell+1)})^2 \\
+%\end{align*}
+%\end{proof}
+%
+%\subsection{Recursive formula for} 
+%%$\widehat{\ov{$\tau$}_u^2}$}
+%
+%The quantity $\widehat{\underline{\tau}_u^2}$ defined by formula (\ref{total.effect.est}) can be recursively estimated by:
+%\begin{equation}
+%\left\lbrace \begin{array}{l}
+%\widehat{\ov{$\tau$}_u^2}^{(0)}= \dfrac{1}{2} \Big{(} f(\vx_0)-(f({\vx'}_{0,u}:\vx_{0,-u}) \Big{)}^2 \\
+%\\
+%\widehat{\ov{$\tau$}_u^2}^{(\ell+1)} = \dfrac{1}{2} \widehat{\ov{$\tau$}_u^2}^{(\ell)} + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}+1}^{2^{\ell+1}-1} \Big{(}f(\vx_i)- f({\vx'}_{i,u}:\vx_{i,-u})\Big{)}^2
+%\end{array}\right.
+%\label{total.effect.est.rec}
+%\end{equation}
+%\begin{proof}
+%Straightforward by developing $\widehat{\ov{$\tau$}_u^2}^{(\ell+1)}$.
+%\end{proof}
+%
+%\subsection{Proof proposition \ref{right.multi}}
+%\label{proof.prop}
+%
 \end{document}

### 2016-08-08 article.tex
Swapping section 3.1 with section 3.2
changes L, sections 2.3, 4.1, 4.2 and 3.1 (b^m-1)

@@
 \newcommand{\vk}{\bvec{k}}
+\newcommand{\vw}{\bvec{w}}
 \newcommand{\vz}{\bvec{z}}
@@
 \subsection{Definition of Sobol' indices}
-We adopt the same notations introduced by Owen in \cite{Owen}.
+%We adopt the same notations introduced by Owen in \cite{Owen}. 
 Denote by $f$ a numerical model, by $\vx=(x_1,\dots,x_d)$ its vector of inputs and set $\mathcal{D}=\{1,\dots,d\}$.
@@
 $\vx_u$ represents a point in $[0,1)^u$ with components $x_j, j \in u$.
-Given two points $\vx$ and $\vx'$, the hybrid point $\vz=(\vx_u:{\vx'}_{-u})$ is defined as $z_j=x_j$ if $j \in u$ and $z_j={x'}_j$ if $j \notin u$.
+Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j={x'}_j$ if $j \notin u$.
 
@@
 \subsection{Estimation of Sobol' indices}
+\label{estimation.strategies}
 In this section we review two Monte Carlo procedures for the estimation of Sobol' indices.
@@
 
-\subsection{Towards a robust estimation}
-The aim of this paper is to propose a recursive estimation procedure to estimate Sobol' indices.
-The choice of the stopping criterion is the key point of this paper.
+\subsection{Towards a reliable estimation}
+The aim of this paper is to propose a recursive estimation procedure to estimate Sobol' indices. The choice of the stopping criterion is the key point of this paper.
+
 The two estimation procedures reviewed in the previous section can be rendered recursive.
 In \cite{Gilquin16}, the authors propose a recursive version of the replication procedure.
-The stopping criterion of the recursive algorithm is an absolute difference between estimates computed on consecutive steps.
-
+In this recursive version, the stopping criterion is an absolute difference between estimates computed on consecutive steps.
 More generally, in most recursive approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly upon the estimates.
@@
 This decomposition use the close set property of digital sequences.
-As such, our recursive procedure relies on the iterative construction of Sobol' sequence.
+As such, our recursive procedure relies on the iterative construction of Sobol' sequences.
+The iterative construction of the Sobol' sequences is performed accordingly to the multiplicative  approach presented in \cite{crass}.
 
-Background on Sobol' sequences are provided in \cite{crass}.
-The iterative construction of the Sobol' sequences is performed accordingly to the multiplicative  approach presented in \cite{crass}.
-The construction of our stopping criterion is the subject of the next section \ref{section.error}.
-Our recursive estimation procedure is presented in section \ref{section.recursive.procedure}.
+The construction of our stopping criterion is the subject of the next section \ref{section.error}. Our recursive estimation procedure is presented in section \ref{section.recursive.procedure}.
 
@@
 \label{section.error}
-\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
-In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$.
-In both cases, regular and normalized indices can be approximated by estimating some integrals,
-\begin{align*}
-S_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
-\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
-\end{align*}
-Therefore, we can define $S_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
-If we can estimate $\vI$ such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$, then we can define the following estimators for the Sobol' indices:
-\begin{align*}
-\widehat{S}_u & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right) \\
-\varepsilon_{S_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right)
-\end{align*}
-where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
 
@@
 \[
-\mathcal{P}_0=\{\bvec{0}\}\subset\dots\subset\mathcal{P}_m=\{\vx_i\}_{i=0}^{b^m}\subset\dots\subset\mathcal{P}_\infty=\{\vx_i\}_{i=0}^{\infty}.
+\mathcal{P}_0=\{\bvec{0}\}\subset\dots\subset\mathcal{P}_m=\{\vx_i\}_{i=0}^{b^m-1}\subset\dots\subset\mathcal{P}_\infty=\{\vx_i\}_{i=0}^{\infty}.
 \]
@@
 
+\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
+In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$.
+In both cases, regular and normalized indices can be approximated by estimating some integrals,
+\begin{align*}
+S_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
+\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
+\end{align*}
+Therefore, we can define $S_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
+If we can estimate $\vI$ such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$, then we can define the following estimators for the Sobol' indices:
+\begin{align*}
+\widehat{S}_u & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right) \\
+\varepsilon_{S_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right)
+\end{align*}
+where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
+
 \section{Recursive estimation procedure}
 \label{section.recursive.procedure}
+
+The recursive estimation procedure we propose combine the error bound presented in the previous section with one of the two estimation strategies of section \ref{estimation.strategies}.
+Namely, Saltelli's strategy and the one based on replicated designs.
+The form of the error bound is the same for both strategies and is given by equation \ref{}.
+
+We start be detailing our recursive procedure in the form of an algorithm.
+Then, we discuss a possible improvement by considering an estimator recently introduced by Owen improving the estimation of small first-order indices.
+
+\subsection{Main algorithm}
 %
@@
 %
-%\subsection{Improvements}
-%This section discusses two improvements to ease the estimation of Sobol' indices with procedures $A$ and $B$. 
-%
-%\bigskip
-%
-%The first improvement focus on the use of a better estimator to evaluate small first-order Sobol' indices with procedure $A$.
+\subsection{Improvements}
+
+We focus on the use of a better estimator to evaluate small first-order Sobol' indices in Variant $A$.
 This estimator is called ``Correlation 2" and was introduced by Owen in \cite{Owen}.
 Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small closed Sobol' indices.
-Our aim is to show that using ``Correlation 2" in procedure $A$ may reduces the total number of model evaluations.
-``Correlation 2" formula writes as follows:
-%\begin{equation}
-%\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i))
-%\label{correlation2}
-%\end{equation}
-%It uses an extra set of $n$ model evaluations to estimate $\widehat{\underline{\tau}_u^2}$.
-Owen explains the effectiveness of ``Correlation 2" as follows.
+Our aim is to show that using ``Correlation 2" in procedure $A$ may reduce the total number of model evaluations.
+Its formula writes as follows:
+\begin{equation}
+\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)),
+\label{correlation2}
+\end{equation}
+It uses an extra set of $n$ model evaluations to estimate $\widehat{\underline{\tau}_u^2}$.
+%Owen explains the effectiveness of (\ref{correlation2}) as follows.
 If the main effect of $\vx_u$ is small then $f(\vx)$ will be almost entirely explained by $\vx_{-u}$.
 The two terms $(f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))$ and $(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i))$ should then be small quantities as well as (\ref{correlation2}).
-%
-%We discuss now the potential improvement brought by the use of ``Correlation 2".
-Assume that the number of small first-order indices is known and equals $\alpha$.
-Then, the cost of procedure $A$ including ``Correlation 2" to estimate small indices writes:
-%\[ n(d-\alpha) + 2 n'\alpha + 2\max(n,n'),\]
-%where: \begin{itemize}
-%\item[$\bullet$] $n(d-\alpha)$ is the number of evaluations induced by the $d-\alpha$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i\geq0}$ to estimate all non small indices, 
-%\item[$\bullet$] $2 n'\alpha$ is the number of evaluations induced by the $2\alpha$ designs $\{\vz_{i,u}:\vx_{i,-u}\}_{i\geq0}$ and $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i\geq0}$ to estimate all small indices,
-%\item[$\bullet$] $2\max(n,n')$ is the number of evaluations  induced by the $2$ designs $\{\vx_{i}\}_{i\geq0}$ and $\{{\vx'}_{i}\}_{i\geq0}$.
-%\end{itemize}
-%At the opposite, the cost of procedure $A$ excluding ``Correlation 2" writes: 
-%\[ n(d-\alpha) + n\alpha + 2n.\]
-%It is straightforward that procedure $A$ including ``Correlation 2" performs equally well or better when $n' \leq 2n$.
-Furthermore, since we are working with Sobol' sequences $n'=2^{k'}$ and $n=2^{k}$.
-Hence, procedure $A$ including ``Correlation 2" performs equally well or better when the recursive estimation procedure finished at least one step sooner.
-Illustrations of this improvement will be provided in Section \ref{appli}.
-%
-%\bigskip
-%
+\bigskip
+
+We discuss now the potential improvement brought by the use of ``Correlation 2" in Variant $A$.
+The idea is to replace the current estimator (\ref{first.order.est}) by (\ref{correlation2}) for each small first-order index.
+Assume that the number of small first-order indices is known and equals $\gamma$.
+We denote by $u_1,\dots,u_{\gamma}$ the indexes of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$.
+The cost of Variant $A$ including ``Correlation 2" writes:
+\begin{equation}
+2 \sum \limits_{j \in \Gamma} n'_{u_j} + \sum \limits_{j \in \mathcal{D}/\Gamma} n'_{u_j} + 2 \ n'_{\max},
+\label{cost.improvement}
+\end{equation}
+where: \begin{itemize}
+\item[$\bullet$] $2 \sum \limits_{j \in \Gamma} n'_{u_j}$ is the number of evaluations induces by the $\gamma$ sets \\ $\{f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)\}_{i=0}^{n'_{u_j}-1}$ and $\gamma$ sets $\{f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)\}_{i=0}^{n'_{u_j}-1}$,
+\item[$\bullet$] $\sum \limits_{j \in \mathcal{D}/\Gamma} n'_{u_j}$ is the number of evaluations induced by the $d-\gamma$ sets \\ $\{f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)\}_{i=0}^{n'_{u_j}-1}$, 
+\item[$\bullet$] $2 \ n'_{\max}=2 \ \max \limits_{j \in \mathcal{D}} \ (n'_{u_j})$, is the number of evaluations induced by the $2$ sets $\{f\left(\vx_{i}\right)\}_{i=0}^{n'_{\max}-1}$ and $\{f\left({\vx'}_{i}\right)\}_{i=0}^{n'_{\max}-1}$.
+\end{itemize}
+At the opposite, the cost of Variant $A$ excluding ``Correlation 2" writes: 
+\begin{equation}
+\sum \limits_{j \in \mathcal{D}} n_{u_j} + 2 \ n_{\max}.
+\label{cost.non.improvement}
+\end{equation}
+The comparison between (\ref{cost.improvement}) and (\ref{cost.non.improvement}) is driven by whether or not total effect indices require more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than their respective first-order indices.
+We distinguish two extreme cases :
+\begin{itemize}
+\item[1)] $\forall j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$.
+As a result, the difference (\ref{cost.improvement}) - (\ref{cost.non.improvement}) is always positive.
+Thus, using ``Correlation 2" results in a cost regression.
+\item[2)] $\forall j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires less evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$.
+As a result, the difference (\ref{cost.improvement}) - (\ref{cost.non.improvement}) is always negative.
+Thus, using ``Correlation 2" results in a cost improvement.
+\end{itemize}
+The standard case varies between these two.
+That is a portion of indices $\ov{$S$}_j$ require more evaluations and another portion of $\ov{$S$}_j$ require less.
+Illustrations of this potential improvement are addressed in Section \ref{appli}.
+\bigskip
+
+In pratice, one does not know which are the small Sobol' indices. To overcome this issue, we proceed as follows in Variant $A$:
+... etc ...
+
 %The second improvement focus on the choice of the $2d$ generating matrices that generate the two Sobol' sequences $\mathcal{P}_\ell$  and ${\mathcal{P}'}_\ell$ in procedure $B$.
@@
 \label{appli}
-\subsection{Classical test functions}
 \subsection{Real case model}
@@
 Thus, in order to estimate the expected value on a continuous time Browninan motion, one could either use a multilevel method, or a multivariate decomposition method to estimate this infinite dimensional integral.
+
+\subsection{Classical test functions}
 

### 2016-08-09 article.tex
changes L, sections 4.1 4.2

@@
 \begin{align*}
-S_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
+\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
 \overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
 \end{align*}
-Therefore, we can define $S_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
+Therefore, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
 If we can estimate $\vI$ such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$, then we can define the following estimators for the Sobol' indices:
@@
 Namely, Saltelli's strategy and the one based on replicated designs.
-The form of the error bound is the same for both strategies and is given by equation \ref{}.
+The form of the stopping criterion is the same for both strategies.
+It is defined as $\abs{\varepsilon_{S_u}} \leq \epsilon$, where $\epsilon$ is the desired precision on the Sobol' indices.
 
 We start be detailing our recursive procedure in the form of an algorithm.
-Then, we discuss a possible improvement by considering an estimator recently introduced by Owen improving the estimation of small first-order indices.
+Then, we discuss a possible improvement by considering a new estimator recently introduced in \cite{Owen} for first-order indices.
 
-\subsection{Main algorithm}
-%
-%$\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can either be used with procedure $A$ to estimate all first-order and all total effect Sobol' indices or with procedure $B$ to estimate all first-order Sobol' indices.
-Algorithms \ref{procedureA} and \ref{procedureB} summarize the main steps of each procedure.
-%\begin{algorithm}[!ht]
-%\caption{Procedure $A$}
-%\begin{algorithmic}[1]
-%\vspace*{0.2cm}
-%\State Set: $\ell \leftarrow 1$, $\mathcal{P}_{0} \leftarrow B_0$, ${\mathcal{P}'}_{0} \leftarrow {B'}_0$
-%\While {stopping criterion}
-%\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
-%
-%\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
-%\State Compute $\{f(\vx_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$
-%\For {$u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$}
-%\State Construct design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=2^{\ell-1}}^{2^{\ell}-1}$
-%\State Compute  $\{f(\vx_{i,u},{\vx'}_{i,-u})\}_{i=2^{\ell-1}}^{2^\ell-1}$
-%\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ with formula (\ref{first.order.est.rec}) and (\ref{total.effect.est.rec})
-%\EndFor
-%\State $\ell \leftarrow \ell + 1$
-%\EndWhile
-%\State Return $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ for all $u \in \mathcal{D}$.
-%\end{algorithmic}
-%\label{procedureA}
-%\end{algorithm}
-%\begin{algorithm}[!ht]
-%\caption{Procedure $B$}
-%\begin{algorithmic}[1]
-%\vspace*{0.2cm}
-%\State Set: $\ell \leftarrow 1$, $\mathcal{P}_{0} \leftarrow B_0$, ${\mathcal{P}'}_{0} \leftarrow {B'}_0$
-%\While {stopping criterion}
-%\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
-%
-%\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
-%\State Compute $\{f(\vx_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$
-%\For {$u \in \mathcal{D}$}
-%\State  order $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ into $\{\pi_u(f({\vx'}_i))\}_{i=2^{\ell-1}}^{2^\ell-1}$
-%\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ with formula (\ref{first.order.est.rec})
-%\EndFor
-%\State $\ell \leftarrow \ell + 1$
-%\EndWhile
-%\State Return $\widehat{\underline{\tau}_u^2}^{(\ell)}$ for all $u \in \mathcal{D}$.
-%\end{algorithmic}
-%\label{procedureB}
-%\end{algorithm}
-%
+\subsection{Recursive procedure algorithm}
+
+Algorithm \ref{recursive.algorithm} summarizes the main steps of our recursive procedure.
+First, choose the target tolerance $\epsilon >0$.
+Choose $r \in \mathbb{N}$ large enough to satisfy the cone conditions (\ref{}) and balance the inflation factor $a(r,\ell)$.
+Set $\ell=r-1$ and construct the two starting designs $\mathcal{P}_{\ell}=\{\vx_i\}_{i=0}^{2^\ell-1}$ and $\mathcal{P}'_{\ell}=\{\vx'_i\}_{i=0}^{2^\ell-1}$ accordingly to the multiplicative approach detailed in \cite{crass}.
+
+With this construction, at each step $\ell$, $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ correspond to the first $2^\ell$ points of two Sobol' sequences.
+Furthermore, they possess the structure of two replicated designs of order $1$.
+\bigskip
+
+Then, $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can either be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices.
+This option is referred as Variant $A$ in Algorithm \ref{recursive.algorithm}.
+Or $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can be used with the replication procedure to estimate all first-order Sobol' indices.
+This option is referred as Variant $B$ in Algorithm \ref{recursive.algorithm}.
+
+If the stopping criterion is satisfied, the algorithm stops and Sobol' estimates are returned.
+Otherwise, $\ell$ is incremented by one and a new set of $2^{\ell}$ points is added to each design $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$.
+
+\begin{algorithm}[!ht]
+\caption{Recursive estimation of Sobol' indices}
+\begin{algorithmic}[1]
+\vspace*{0.2cm}
+\State Choose $\epsilon >0$ and $r \in \mathbb{N}$
+\State Set: $\ell \leftarrow r-1$, 
+\While {$\abs{\varepsilon_{S_u}} \leq \epsilon$}
+\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
+
+\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
+\For {$u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$}
+\If {Variant $A$}
+\State Estimate $\widehat{\underline{S}_u}^{(\ell)}$ and $\widehat{\ov{$S$}_u}^{(\ell)}$ with formula \ref{} and Saltelli's strategy
+\EndIf
+\If {Variant $B$}
+\State Estimate $\widehat{\underline{S}_u}^{(\ell)}$ with formula \ref{} and the replication procedure
+\EndIf
+\EndFor
+\State $\ell \leftarrow \ell + 1$
+\EndWhile
+\State Return the Sobol' estimates.
+\end{algorithmic}
+\label{recursive.algorithm}
+\end{algorithm}
+
+The cost of our algorithm varies whether Variant $A$ or Variant $B$ is selected.
+To discuss this cost we note by $\ell^\star$ the ending iteration.
+If Variant $A$ is selected the cost of our algorithm writes:
+\begin{equation*}
+\sum \limits_{j \in \mathcal{D}} 2^{\ell_j} + 2 \times 2^{\ell^{\star}},
+\end{equation*}
+where: 
+\begin{itemize}
+\item[$\bullet$] $2^{\ell_j}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ used to estimate both $\underline{S}_j$ and $\overline{S}_j$.
+\item[$\bullet$] $2 \times 2^{\ell^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
+\end{itemize}
+This cost can be seen as a generalisation of the one specified in Theorem \ref{saltelli.theorem}.
+If all $\ell_j$ are equal, the cost of Variant $A$ becomes $2^{\ell^\star}(d+2)$ and we recover the cost of Theorem \ref{saltelli.theorem} with $n=2^{\ell^\star}$.
+
+If Variant $B$ is selected the cost of our algorithm equals $2 \times 2^{\ell^{\star}}$. This cost corresponds to the one specified in the replication procedure with $n=2^{\ell^{\star}}$.
+
 \subsection{Improvements}
@@
 \end{equation}
-It uses an extra set of $n$ model evaluations to estimate $\widehat{\underline{\tau}_u^2}$.
-%Owen explains the effectiveness of (\ref{correlation2}) as follows.
-If the main effect of $\vx_u$ is small then $f(\vx)$ will be almost entirely explained by $\vx_{-u}$.
-The two terms $(f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))$ and $(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i))$ should then be small quantities as well as (\ref{correlation2}).
+where $(\vx_i,{\vx'}_i, \vz_i) \iid [0,1)^{3d}$. It uses an extra set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.
 \bigskip
@@
 We denote by $u_1,\dots,u_{\gamma}$ the indexes of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$.
-The cost of Variant $A$ including ``Correlation 2" writes:
+The cost of Variant $A$ including ``Correlation 2" rewrites:
 \begin{equation}
-2 \sum \limits_{j \in \Gamma} n'_{u_j} + \sum \limits_{j \in \mathcal{D}/\Gamma} n'_{u_j} + 2 \ n'_{\max},
+\sum \limits_{j \in \Gamma} 2 \times 2^{\ell'_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{\ell_{u_j}} + 2 \times 2^{\ell^\star}, \qquad \ell'_{u_j}\leq \ell^{\star}, \ \ell_{u_j} \leq \ell^{\star},
 \label{cost.improvement}
@@
 where: \begin{itemize}
-\item[$\bullet$] $2 \sum \limits_{j \in \Gamma} n'_{u_j}$ is the number of evaluations induces by the $\gamma$ sets \\ $\{f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)\}_{i=0}^{n'_{u_j}-1}$ and $\gamma$ sets $\{f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)\}_{i=0}^{n'_{u_j}-1}$,
-\item[$\bullet$] $\sum \limits_{j \in \mathcal{D}/\Gamma} n'_{u_j}$ is the number of evaluations induced by the $d-\gamma$ sets \\ $\{f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)\}_{i=0}^{n'_{u_j}-1}$, 
-\item[$\bullet$] $2 \ n'_{\max}=2 \ \max \limits_{j \in \mathcal{D}} \ (n'_{u_j})$, is the number of evaluations induced by the $2$ sets $\{f\left(\vx_{i}\right)\}_{i=0}^{n'_{\max}-1}$ and $\{f\left({\vx'}_{i}\right)\}_{i=0}^{n'_{\max}-1}$.
+\item[$\bullet$] for $j\in \Gamma$, $2 \times 2^{\ell'_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ and $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate small first-order indices,
+\item[$\bullet$] for $j\in \mathcal{D}/\Gamma$, $ 2^{\ell_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate non small first-order indices,
+\item[$\bullet$] $2 \times 2^{\ell^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
 \end{itemize}
-At the opposite, the cost of Variant $A$ excluding ``Correlation 2" writes: 
+At the opposite the cost of Variant $A$ without  ``Correlation 2" writes:
 \begin{equation}
-\sum \limits_{j \in \mathcal{D}} n_{u_j} + 2 \ n_{\max}.
+\sum \limits_{j \in \Gamma} 2^{\ell_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{\ell_{u_j}} + 2 \times 2^{\ell^{\star}}, \qquad \ell_{u_j} \leq \ell^{\star}.
 \label{cost.non.improvement}
 \end{equation}
-The comparison between (\ref{cost.improvement}) and (\ref{cost.non.improvement}) is driven by whether or not total effect indices require more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than their respective first-order indices.
-We distinguish two extreme cases :
+
+The difference between costs (\ref{cost.improvement}) and (\ref{cost.non.improvement}) equals:
+\begin{equation}
+ \sum \limits_{j \in \Gamma} 2^{\ell'_{u_j}+1} - 2^{\ell_{u_j}}.
+\label{cost.comparison}
+\end{equation}
+Hence, the sign of this difference indicates whether or not using ``Correlation 2" bring an improvement to Variant $A$. We distinguish two extreme cases :
 \begin{itemize}
-\item[1)] $\forall j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$.
-As a result, the difference (\ref{cost.improvement}) - (\ref{cost.non.improvement}) is always positive.
-Thus, using ``Correlation 2" results in a cost regression.
+\item[1)] $\forall j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires as much or more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$.
+As a result, the difference (\ref{cost.comparison}) is always positive and using ``Correlation 2" leads to a cost regression.
 \item[2)] $\forall j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires less evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$.
-As a result, the difference (\ref{cost.improvement}) - (\ref{cost.non.improvement}) is always negative.
-Thus, using ``Correlation 2" results in a cost improvement.
+As a result, the difference (\ref{cost.comparison}) is always negative or null and using ``Correlation 2" may provide a cost improvement.
 \end{itemize}
-The standard case varies between these two.
-That is a portion of indices $\ov{$S$}_j$ require more evaluations and another portion of $\ov{$S$}_j$ require less.
+Other cases vary between these two.
+That is, some indices $\ov{$S$}_j$ require more evaluations than $\underline{S}_j$ and others require less.
 Illustrations of this potential improvement are addressed in Section \ref{appli}.
@@
 
-In pratice, one does not know which are the small Sobol' indices. To overcome this issue, we proceed as follows in Variant $A$:
-... etc ...
-
-%The second improvement focus on the choice of the $2d$ generating matrices that generate the two Sobol' sequences $\mathcal{P}_\ell$  and ${\mathcal{P}'}_\ell$ in procedure $B$.
-%
-%We note by $C_1,\dots,C_d$ the matrices generating $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and ${C'}_1,\dots,{C'}_d$ those generating $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$.
-%In the multiplicative approach \cite{crass}, these $2d$ matrices are selected as the first $2d$ elements of the set found by Kuo and Joe in \cite{Kuo}.
-This set is composed of generating matrices that optimize the $2$-dimensional projection $t$-values.
-%
-%%In procedure $A$, each design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i\geq0}$ constructed in step $6$ of Algorithm \ref{procedureA} is a $d$-dimensional Sobol' sequence generated by the $d$-subset: $${C'}_1,\dots,{C'}_{u-1},C_u,{C'}_{u+1},\dots,C_d.$$ Therefore, $2$-dimensional projection $t$-values are still optimized.
-%
-%In procedure $B$, each permutation $\pi_u$ applied in step $6$ of Algorithm \ref{procedureB} results in a design $\{\vx_{i,u}:{\vx'}_{\pi_u(i),-u}\}_{i=0}^{2^\ell-1}$.
-The $d$ generating matrices corresponding to this design are:
-%$${C'}_1U_u,\dots,{C'}_{u-1}U_u,C_u,{C'}_{u+1}U_u,{C'}_dU_u$$ where $U_u$ is a a full rank upper triangular matrix verifying $C_u={C'}_uU_u$.
-The right multiplication by $U_u$ is the digital representation of the ordering by $\pi_u$.
-
-%\section{Estimators: Correlation 2 Oracle 2}
-%\subsection{Choice and parameters (threshold small?)}
-%\subsection{Cost discussion: for first-order Consider or not total order}
+In pratice, one does not know which are the small Sobol' indices.
+To overcome this issue, we propose the following alternative for Variant $A$.
+Assume that there exists one or multiple  $u \in \mathcal{D}$ such that estimates $\widehat{\underline{S}_u}^{(\ell)}$ are smaller than a specified threshold at the end of the first iteration.
+Then, for these indices, at the next iteration estimator (\ref{first.order.est}) is switched for (\ref{correlation2}) and a third Sobol' sequence $\mathcal{P''}_{\ell}=\{\vz_i\}_{i=0}^{2^\ell-1}$ is constructed for the evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
 

### 2016-08-10 article.tex
Last changes in article.tex

--- 2016-08-06 article.tex
@@
 \label{section.error}
-\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
-In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$.
-In both cases, regular and normalized indices can be approximated by estimating some integrals,
-\begin{align*}
-S_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
-\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
-\end{align*}
-Therefore, we can define $S_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
-If we can estimate $\vI$ such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$, then we can define the following estimators for the Sobol' indices:
-\begin{align*}
-\widehat{S}_u & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right) \\
-\varepsilon_{S_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right)
-\end{align*}
-where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
 
-\subsection{Reliable Estimation Using Quasi-Monte Carlo}
+\subsection{Reliable Estimation Using Quasi-Monte Carlo}\label{sec_reliable_error}
 
-We assume we have an embedded sequence of digital nets in base $b$,
+Consider an embedded sequence of digital nets in base $b$,
 \[
@@
 \]
+One example that will be particularly useful for our application is the Sobol' sequence \cite{•}.
 
@@
 
-An important property is that for any Walsh basis $\phi_{\vk}(\vx)$
-\[
+An important property for the error estimation using digital nets is that for any Walsh basis $\phi_{\vk}(\vx)$
+\begin{equation}\label{basis_prop}
 \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\phi_{\vk}(\vx)=
@@
 1,\quad \vk\in\mathcal{P}_m^\perp, \\
-0,\quad \vk\notin\mathcal{P}_m^\perp
+0,\quad \vk\notin\mathcal{P}_m^\perp.
 \end{cases}
-\]
+\end{equation}
 
-Therefore,
+For any function $f\in L^2(\cube)$, one may use its Walsh series $f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\phi_{\vk}(\vx)$ and equation \eqref{basis_prop} to rewrite the error as,
+
 \[
@@
 \end{itemize}
+
+\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
+The aim of our algorithm is to estimate the normalized Sobol' indices, $\underline{S}_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$.
+In both cases, regular and normalized indices can be approximated by estimating integrals,
+\begin{align}\label{indices_integ_1}
+\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
+\label{indices_integ_2}
+\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
+\end{align}
+However, to guarantee the error in our $\underline{S}_u$ and $\overline{S}_u$ approximations we need to proceed with an estimator different than the usual.
+Given equations \eqref{indices_integ_1} and \eqref{indices_integ_2}, one may write $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
+According to section \ref{sec_reliable_error}, integrals can be estimated such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
+Thus, the following estimator
+\begin{align*}
+\widehat{S}_u & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right) \\
+\varepsilon_{S_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right)
+\end{align*}
+ensures that the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
 

### 2016-08-10 article.tex
Changes in article.tex

--- 2016-08-09 article.tex
@@
 
-\subsection{Reliable Estimation Using Quasi-Monte Carlo}
+\subsection{Reliable Estimation Using Quasi-Monte Carlo}\label{sec_reliable_error}
 
-We assume we have an embedded sequence of digital nets in base $b$,
+Consider an embedded sequence of digital nets in base $b$,
 \[
@@
 \subsection{Definition of $\widehat{S}$ (fix it with max and min)}
-In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$.
-In both cases, regular and normalized indices can be approximated by estimating some integrals,
-\begin{align*}
+
+The aim of our algorithm is to estimate the normalized Sobol' indices, $\underline{S}_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$.
+In both cases, regular and normalized indices can be approximated by estimating integrals,
+\begin{align}\label{indices_integ_1}
 \underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
+\label{indices_integ_2}
 \overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
-\end{align*}
-Therefore, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
-If we can estimate $\vI$ such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$, then we can define the following estimators for the Sobol' indices:
+\end{align}
+However, to guarantee the error in our $\underline{S}_u$ and $\overline{S}_u$ approximations we need to proceed with an estimator different than the usual.
+Given equations \eqref{indices_integ_1} and \eqref{indices_integ_2}, one may write $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
+According to section \ref{sec_reliable_error}, integrals can be estimated such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
+Thus, the following estimator
 \begin{align*}
@@
 \end{align*}
-where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
+ensures that the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
 

### 2016-08-10 Images/article_scheme_S.m
Adding figure to estimator S in article.tex

@@ -1,0 +1,34 @@
+    set(0,'defaultaxesfontsize',24,'defaulttextfontsize',24) %make font larger
+    set(0,'defaultLineLineWidth',3) %thick lines
+    set(0,'defaultTextInterpreter','latex') %latex axis labels
+    set(0,'defaultLegendInterpreter','latex') %latex axis labels
+    set(0,'defaultLineMarkerSize',40) %latex axis labels
+
+S = @(x) exp(-(x-1).^2) + 1;
+
+I = 0.90;
+err = 0.2;
+Smax = S(1); xmax = 1;
+Smin = S(I - err); xmin = I - err;
+
+
+x = I - err - 0.06:0.02:I + err + 0.06;
+ymin = min(S(x));
+ymax = max(S(x));
+
+plot(x,S(x))
+ax = gca;
+set(ax,'TickLabelInterpreter', 'Latex');
+ax.XTick = [I-err I I+err];
+ax.YTick = [Smin (Smin+Smax)/2 S(I) Smax];
+ax.XTickLabel = {'$\hat{I}-err$','$\hat{I}$','$\hat{I}+err$'};
+ax.YTickLabel = {'$S_{\min}$', '$(S_{\min}+S_{\max})/2$', '$S(\hat{I})$', '$S_{\max}$'};
+hold on
+plot([xmin xmin], [ymin Smin], 'k--')
+plot([x(1) xmin], [Smin Smin], 'k--')
+plot([I I], [ymin S(I)], 'k--')
+plot([x(1) I], [S(I) S(I)], 'k--')
+plot([xmax xmax], [ymin Smax], 'k--')
+plot([x(1) xmax], [Smax Smax], 'k--')
+hold off
+axis([x(1) x(end) ymin ymax*1.01])

### 2016-08-10 article.tex
Adding figure to estimator S in article.tex
More changes in article.tex

@@
 \newcommand{\vx}{\bvec{x}}
+\newcommand{\vt}{\bvec{t}}
 \newcommand{\vI}{\bvec{I}}
@@
 
-Each $\mathcal{P}_m$ has a group structure under the digit wise addition.
+Each $\mathcal{P}_m$ has a group structure under the digit-wise addition:
+\[
+\vx\oplus\vt = \left(\sum_{\ell=1}^{\infty} [(x_{j\ell} + t_{j\ell}) \bmod b] b^{-\ell} \pmod{1} \right)_{j=1}^d.
+\]
+where $x_{j\ell}$ and $t_{j\ell}$ are the binary decompositions of $x_j$ and $t_j$.
+
  Analogously, we can also define the dual nets as $\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vx}{\vk}=0,\, \vx\in\mathcal{P}_m\}$,
@@
 
-In \cite{HicJim} we proposed an algorithm based on digital nets that estimates hight dimensional integrals whose error lies within a user-input error tolerance.
-This algorithm finds the number of data points automatically.
-We will refer to it as $\widehat{I}(f;\varepsilon)$, where $f$ is the function to integrate and $\varepsilon$ the user-input error tolerance.
+In \cite{HicJim} we proposed an ordering of the wavenumbers $\vk\in\naturals_0^d$ that led to the data-based upper bound below,
 
@@
 
+ algorithm based on digital nets that estimates hight dimensional integrals whose error lies within a user-input error tolerance.
+This algorithm finds the number of data points automatically.
+We will refer to it as $\widehat{I}(f;\varepsilon)$, where $f$ is the function to integrate and $\varepsilon$ the user-input error tolerance.
+
 \subsection{Definition of $\widehat{S}$ (fix it with max and min)}
@@
 \begin{align}\label{indices_integ_1}
-\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
+\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} \left(f(\vx)-
+f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'} }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_3-(I_4)^2}, \\
 \label{indices_integ_2}
-\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
+\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_2}{I_3-(I_4)^2}.
 \end{align}
@@
 \begin{align*}
-\widehat{S}_u & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right) \\
-\varepsilon_{S_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right)
+\widehat{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right) \\
+\varepsilon_{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right)
 \end{align*}
-ensures that the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
+\begin{align*}
+\widehat{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right) \\
+\varepsilon_{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right)
+\end{align*}
+ensures that the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$. Explain why max min 0, 1.............
+
+\begin{figure}\centering
+\includegraphics[width=1.\textwidth]{Images/scheme_S.eps}
+%\caption*{Representation of estimators.}
+\end{figure}
 

### 2016-08-11 article.tex
changes L, section 4.1, 4.2

--- 2016-08-10 article.tex
@@
 
-The two estimation procedures reviewed in the previous section can be rendered recursive.
 In \cite{Gilquin16}, the authors propose a recursive version of the replication procedure.
@@
 
-The construction of our stopping criterion is the subject of the next section \ref{section.error}. Our recursive estimation procedure is presented in section \ref{section.recursive.procedure}.
+The construction of the error bound is the subject of the next section \ref{section.error}. Our recursive estimation procedure is presented in section \ref{section.recursive.procedure}.
 
@@
 
-\subsection{Reliable Estimation Using Quasi-Monte Carlo}\label{sec_reliable_error}
+\subsection{Reliable Estimation Using Quasi-Monte Carlo}
 
-Consider an embedded sequence of digital nets in base $b$,
+We assume we have an embedded sequence of digital nets in base $b$,
 \[
@@
 \]
-One example that will be particularly useful for our application is the Sobol' sequence \cite{•}.
 
@@
 
-An important property for the error estimation using digital nets is that for any Walsh basis $\phi_{\vk}(\vx)$
-\begin{equation}\label{basis_prop}
+An important property is that for any Walsh basis $\phi_{\vk}(\vx)$
+\[
 \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\phi_{\vk}(\vx)=
@@
 1,\quad \vk\in\mathcal{P}_m^\perp, \\
-0,\quad \vk\notin\mathcal{P}_m^\perp.
+0,\quad \vk\notin\mathcal{P}_m^\perp
 \end{cases}
-\end{equation}
+\]
 
-For any function $f\in L^2(\cube)$, one may use its Walsh series $f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\phi_{\vk}(\vx)$ and equation \eqref{basis_prop} to rewrite the error as,
-
+Therefore,
 \[
@@
 \subsection{Definition of $\widehat{S}$ (fix it with max and min)}
-
-The aim of our algorithm is to estimate the normalized Sobol' indices, $\underline{S}_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$.
-In both cases, regular and normalized indices can be approximated by estimating integrals,
-\begin{align}\label{indices_integ_1}
+In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$.
+In both cases, regular and normalized indices can be approximated by estimating some integrals,
+\begin{align*}
 \underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
-\label{indices_integ_2}
 \overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
-\end{align}
-However, to guarantee the error in our $\underline{S}_u$ and $\overline{S}_u$ approximations we need to proceed with an estimator different than the usual.
-Given equations \eqref{indices_integ_1} and \eqref{indices_integ_2}, one may write $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
-According to section \ref{sec_reliable_error}, integrals can be estimated such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
-Thus, the following estimator
+\end{align*}
+Therefore, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
+If we can estimate $\vI$ such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$, then we can define the following estimators for the Sobol' indices:
 \begin{align*}
@@
 \end{align*}
-ensures that the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
+where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
 
@@
 
-The recursive estimation procedure we propose combine the error bound presented in the previous section with one of the two estimation strategies of section \ref{estimation.strategies}.
-Namely, Saltelli's strategy and the one based on replicated designs.
+The recursive estimation procedure we propose combine the error bound presented in the previous section with one of the two estimation strategies of section \ref{estimation.strategies}, namely Saltelli's strategy and the replication procedure.
 The form of the stopping criterion is the same for both strategies.
@@
 Algorithm \ref{recursive.algorithm} summarizes the main steps of our recursive procedure.
-First, choose the target tolerance $\epsilon >0$.
-Choose $r \in \mathbb{N}$ large enough to satisfy the cone conditions (\ref{}) and balance the inflation factor $a(r,\ell)$.
-Set $\ell=r-1$ and construct the two starting designs $\mathcal{P}_{\ell}=\{\vx_i\}_{i=0}^{2^\ell-1}$ and $\mathcal{P}'_{\ell}=\{\vx'_i\}_{i=0}^{2^\ell-1}$ accordingly to the multiplicative approach detailed in \cite{crass}.
-
-With this construction, at each step $\ell$, $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ correspond to the first $2^\ell$ points of two Sobol' sequences.
+First, fix the target precision $\epsilon >0$.
+Set $m=m_0$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ accordingly to the multiplicative approach detailed in \cite{crass}.
+With this construction, $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two Sobol' sequences.
 Furthermore, they possess the structure of two replicated designs of order $1$.
@@
 
-Then, $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can either be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices.
+Then, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can either be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices.
 This option is referred as Variant $A$ in Algorithm \ref{recursive.algorithm}.
-Or $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can be used with the replication procedure to estimate all first-order Sobol' indices.
+Or $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can be used with the replication procedure to estimate all first-order Sobol' indices.
 This option is referred as Variant $B$ in Algorithm \ref{recursive.algorithm}.
 
-If the stopping criterion is satisfied, the algorithm stops and Sobol' estimates are returned.
-Otherwise, $\ell$ is incremented by one and a new set of $2^{\ell}$ points is added to each design $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$.
+If the stopping criterion is satisfied, the algorithm stops and Sobol' estimates are returned. Otherwise, $m$ is incremented by one to perform a new estimation.
 
@@
 \vspace*{0.2cm}
-\State Choose $\epsilon >0$ and $r \in \mathbb{N}$
-\State Set: $\ell \leftarrow r-1$, 
+\State choose $\epsilon >0$
+\State set: $m \leftarrow m_0$
 \While {$\abs{\varepsilon_{S_u}} \leq \epsilon$}
-\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
+\State $\mathcal{P}_m \leftarrow \mathcal{P}_{m-1} \cup B_m$
 
-\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
+\hspace*{-0.3cm} $\mathcal{P}'_m \leftarrow \mathcal{P}'_{m-1} \cup {B'}_m$
 \For {$u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$}
 \If {Variant $A$}
-\State Estimate $\widehat{\underline{S}_u}^{(\ell)}$ and $\widehat{\ov{$S$}_u}^{(\ell)}$ with formula \ref{} and Saltelli's strategy
+\State estimate $\widehat{\underline{S}_u}^{(m)}$ and $\widehat{\ov{$S$}_u}^{(m)}$ with formula \ref{} and Saltelli's strategy
 \EndIf
 \If {Variant $B$}
-\State Estimate $\widehat{\underline{S}_u}^{(\ell)}$ with formula \ref{} and the replication procedure
+\State estimate $\widehat{\underline{S}_u}^{(m)}$ with formula \ref{} and the replication procedure
 \EndIf
 \EndFor
-\State $\ell \leftarrow \ell + 1$
+\State $m \leftarrow m + 1$
 \EndWhile
-\State Return the Sobol' estimates.
+\State return the Sobol' estimates.
 \end{algorithmic}
@@
 The cost of our algorithm varies whether Variant $A$ or Variant $B$ is selected.
-To discuss this cost we note by $\ell^\star$ the ending iteration.
-If Variant $A$ is selected the cost of our algorithm writes:
+To discuss this cost we note by $m^\star$ the ending iteration.
+If Variant $A$ is selected, the cost of our algorithm writes:
 \begin{equation*}
-\sum \limits_{j \in \mathcal{D}} 2^{\ell_j} + 2 \times 2^{\ell^{\star}},
+\sum \limits_{u \in \mathcal{D}} 2^{m_u} + 2 \times 2^{m^{\star}}, \qquad m^\star= \max \limits_{u \in \mathcal{D}} \ m_u,
 \end{equation*}
@@
 \begin{itemize}
-\item[$\bullet$] $2^{\ell_j}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ used to estimate both $\underline{S}_j$ and $\overline{S}_j$.
-\item[$\bullet$] $2 \times 2^{\ell^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
+\item[$\bullet$] $2^{m_u}$ is the number of evaluations $f\left(\vx_{i,u}:{\vx'}_{i,-u}\right)$ used to estimate both $\underline{S}_u$ and $\overline{S}_u$.
+\item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
 \end{itemize}
 This cost can be seen as a generalisation of the one specified in Theorem \ref{saltelli.theorem}.
-If all $\ell_j$ are equal, the cost of Variant $A$ becomes $2^{\ell^\star}(d+2)$ and we recover the cost of Theorem \ref{saltelli.theorem} with $n=2^{\ell^\star}$.
+If all $m_u$ are equal, the cost of Variant $A$ becomes $2^{m^\star}(d+2)$ and we recover the cost of Theorem \ref{saltelli.theorem} with $n=2^{m^\star}$.
 
-If Variant $B$ is selected the cost of our algorithm equals $2 \times 2^{\ell^{\star}}$. This cost corresponds to the one specified in the replication procedure with $n=2^{\ell^{\star}}$.
+If Variant $B$ is selected the cost of our algorithm equals $2 \times 2^{m^{\star}}$. This cost corresponds to the one specified in the replication procedure with $n=2^{m^{\star}}$.
 
-\subsection{Improvements}
+\subsection{Improvement}
 
@@
 
-We discuss now the potential improvement brought by the use of ``Correlation 2" in Variant $A$.
+We discuss below the potential improvement brought by the use of ``Correlation 2" in Variant $A$.
 The idea is to replace the current estimator (\ref{first.order.est}) by (\ref{correlation2}) for each small first-order index.
@@
 We denote by $u_1,\dots,u_{\gamma}$ the indexes of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$.
-The cost of Variant $A$ including ``Correlation 2" rewrites:
+
+The cost of Variant $A$ including ``Correlation 2" writes: 
 \begin{equation}
-\sum \limits_{j \in \Gamma} 2 \times 2^{\ell'_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{\ell_{u_j}} + 2 \times 2^{\ell^\star}, \qquad \ell'_{u_j}\leq \ell^{\star}, \ \ell_{u_j} \leq \ell^{\star},
+\sum \limits_{j \in \Gamma} 2^{m''_{u_j}} + \sum \limits_{j \in \Gamma} 2^{m'_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{m_{u_j}} + 2 \times 2^{m^\star}, \qquad m'_{u_j}\leq m^{\star}, \ m_{u_j} \leq m^{\star},
 \label{cost.improvement}
@@
 where: \begin{itemize}
-\item[$\bullet$] for $j\in \Gamma$, $2 \times 2^{\ell'_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ and $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate small first-order indices,
-\item[$\bullet$] for $j\in \mathcal{D}/\Gamma$, $ 2^{\ell_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate non small first-order indices,
-\item[$\bullet$] $2 \times 2^{\ell^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
+\item[$\bullet$] for $j\in \Gamma$, $2^{m''_{u_j}}$ is the number of evaluations $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate small first-order indices,
+\item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate both small first-order and total effect indices,
+\item[$\bullet$] for $j\in \mathcal{D}/\Gamma$, $ 2^{m_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate non small first-order indices,
+\item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
 \end{itemize}
-At the opposite the cost of Variant $A$ without  ``Correlation 2" writes:
+Recall that the cost of Variant $A$ without  ``Correlation 2" writes:
 \begin{equation}
-\sum \limits_{j \in \Gamma} 2^{\ell_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{\ell_{u_j}} + 2 \times 2^{\ell^{\star}}, \qquad \ell_{u_j} \leq \ell^{\star}.
+\sum \limits_{j \in \Gamma} 2^{m_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{m_{u_j}} + 2 \times 2^{m^{\star}}, \qquad m_{u_j} \leq m^{\star}.
 \label{cost.non.improvement}
 \end{equation}
-
 The difference between costs (\ref{cost.improvement}) and (\ref{cost.non.improvement}) equals:
 \begin{equation}
- \sum \limits_{j \in \Gamma} 2^{\ell'_{u_j}+1} - 2^{\ell_{u_j}}.
+ \sum \limits_{j \in \Gamma} 2^{m_{u_j}} \left(2^{m''_{u_j}-m_{u_j}}  + 2^{m'_{u_j}-m_{u_j}} - 1 \right) = \sum \limits_{j \in \Gamma} c_j.
 \label{cost.comparison}
 \end{equation}
-Hence, the sign of this difference indicates whether or not using ``Correlation 2" bring an improvement to Variant $A$. We distinguish two extreme cases :
+Hence, the sign of this difference indicates whether or not using ``Correlation 2" bring an improvement to Variant $A$. We distinguish two cases :
 \begin{itemize}
-\item[1)] $\forall j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires as much or more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$.
-As a result, the difference (\ref{cost.comparison}) is always positive and using ``Correlation 2" leads to a cost regression.
-\item[2)] $\forall j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires less evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$.
-As a result, the difference (\ref{cost.comparison}) is always negative or null and using ``Correlation 2" may provide a cost improvement.
+\item[1)] for $j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires as much or more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$.
+Since the total effect estimator is the same, as a consequence we have $m'_{u_j}=m_{u_j}$ and $c_j >0$.
+\item[2)] for $j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires less evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$.
+In this case, if both $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ then $c_j \leq 0$.
 \end{itemize}
-Other cases vary between these two.
-That is, some indices $\ov{$S$}_j$ require more evaluations than $\underline{S}_j$ and others require less.
-Illustrations of this potential improvement are addressed in Section \ref{appli}.
+We can write $\Gamma = \Gamma_1 \cup \Gamma_2$, $\Gamma_1 \cap \Gamma_2=\varnothing$, to separate the number of times case $1)$ or case $2)$ are verified.
+We expect to have more case $2)$ than case $1)$.
+The reason is that the numerator of the first-order index (\ref{}) requires to estimate $2d-1$ integrals against only $d+1$ integrals for the numerator of the total effect index (\ref{}).
+Thus, it seems reasonable to suppose that it takes less points to evaluate (\ref{}) than (\ref{}).
+Furthermore, in case $2$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to be often satisfied as ``Correlation 2" has been shown 
+to perform the best.
+
+To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{appli}. 
 \bigskip
@@
 To overcome this issue, we propose the following alternative for Variant $A$.
-Assume that there exists one or multiple  $u \in \mathcal{D}$ such that estimates $\widehat{\underline{S}_u}^{(\ell)}$ are smaller than a specified threshold at the end of the first iteration.
-Then, for these indices, at the next iteration estimator (\ref{first.order.est}) is switched for (\ref{correlation2}) and a third Sobol' sequence $\mathcal{P''}_{\ell}=\{\vz_i\}_{i=0}^{2^\ell-1}$ is constructed for the evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+Assume that there exists one or multiple  $u \in \mathcal{D}$ such that estimates $\widehat{\underline{S}_u}^{(m)}$ are smaller than a specified threshold at the end of the first iteration of Algorithm \ref{recursive.algorithm}.
+Then, for these indices, at the next iteration estimator (\ref{first.order.est}) is switched for (\ref{correlation2}) and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed for the evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
 
@@
 %
-%Let $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$ be the two points sets constructed with the recursive scheme (\ref{rec.scheme}).  
+%Let $\mathcal{P}_m=\{\vx_i\}_{i=0}^{2^m-1}$ and $\mathcal{P}'_m=\{{\vx'}_i\}_{i=0}^{2^m-1}$ be the two points sets constructed with the recursive scheme (\ref{rec.scheme}).  
 %
@@
 %\\
-%\hat{\mu}^{(\ell+1)} = \dfrac{1}{2} \Big{(} \hat{\mu}^{(\ell)} + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}
+%\hat{\mu}^{(m+1)} = \dfrac{1}{2} \Big{(} \hat{\mu}^{(m)} + \dfrac{1}{2^{m+1}} \sum \limits_{i=2^{m}}^{2^{m+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}
 %\end{array}\right.\]
 %\begin{proof}
-%By developing $\hat{\mu}^{(\ell+1)}$:
+%By developing $\hat{\mu}^{(m+1)}$:
 %\begin{align*}
-%\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \\
-%\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \Big{(} \sum \limits_{i=0}^{2^{\ell}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
-%\hat{\mu}^{(\ell+1)} &= \dfrac{1}{2} \dfrac{1}{2^{\ell+1}} \Big{(} 2 \times 2^{\ell}\hat{\mu}^{(\ell)} + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
+%\hat{\mu}^{(m+1)} &= \dfrac{1}{2} \dfrac{1}{2^{m+1}} \sum \limits_{i=0}^{2^{m+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \\
+%\hat{\mu}^{(m+1)} &= \dfrac{1}{2} \dfrac{1}{2^{m+1}} \Big{(} \sum \limits_{i=0}^{2^{m}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{m}}^{2^{m+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
+%\hat{\mu}^{(m+1)} &= \dfrac{1}{2} \dfrac{1}{2^{m+1}} \Big{(} 2 \times 2^{m}\hat{\mu}^{(m)} + \sum \limits_{i=2^{m}}^{2^{m+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
 %\end{align*}
@@
 %\\
-%\widehat{\underline{\tau}_u^2}^{(\ell+1)} =  \dfrac{1}{2} \widehat{\underline{\tau}_u^2}^{(\ell)} - \dfrac{1}{2} (\hat{\mu}^{(\ell)})^2 - (\hat{\mu}^{(\ell+1)})^2 + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}+1}^{2^{\ell+1}-1} f(\vx_i) f(\vx_{i,u}:{\vx'}_{i,-u})
+%\widehat{\underline{\tau}_u^2}^{(m+1)} =  \dfrac{1}{2} \widehat{\underline{\tau}_u^2}^{(m)} - \dfrac{1}{2} (\hat{\mu}^{(m)})^2 - (\hat{\mu}^{(m+1)})^2 + \dfrac{1}{2^{m+1}} \sum \limits_{i=2^{m}+1}^{2^{m+1}-1} f(\vx_i) f(\vx_{i,u}:{\vx'}_{i,-u})
 %\end{array}\right.
@@
 %\begin{proof}
-%By developing $\widehat{\underline{\tau}_u^2}^{(\ell+1)}$:
+%By developing $\widehat{\underline{\tau}_u^2}^{(m+1)}$:
 %\begin{align*}
-%\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} (f(\vx_i)-\hat{\mu}^{(\ell+1)})(f(\vx_{i,u}:{\vx'}_{i,-u})-\hat{\mu}^{(\ell+1)}) \\
-%\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \sum \limits_{i=0}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(\ell+1)})^2 \\
-%\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \frac{1}{2^{\ell+1}} \Big{(}\sum \limits_{i=0}^{2^{\ell}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})\Big{)} -(\hat{\mu}^{(\ell+1)})^2 \\
-%\widehat{\underline{\tau}_u^2}^{(\ell+1)} &= \dfrac{1}{2}\Big{(}\widehat{\underline{\tau}_u^2}^{(\ell)}-(\hat{\mu}^{(\ell)})^2\Big{)} + \frac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}}^{2^{\ell+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(\ell+1)})^2 \\
+%\widehat{\underline{\tau}_u^2}^{(m+1)} &= \frac{1}{2^{m+1}} \sum \limits_{i=0}^{2^{m+1}-1} (f(\vx_i)-\hat{\mu}^{(m+1)})(f(\vx_{i,u}:{\vx'}_{i,-u})-\hat{\mu}^{(m+1)}) \\
+%\widehat{\underline{\tau}_u^2}^{(m+1)} &= \frac{1}{2^{m+1}} \sum \limits_{i=0}^{2^{m+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(m+1)})^2 \\
+%\widehat{\underline{\tau}_u^2}^{(m+1)} &= \frac{1}{2^{m+1}} \Big{(}\sum \limits_{i=0}^{2^{m}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{m}}^{2^{m+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})\Big{)} -(\hat{\mu}^{(m+1)})^2 \\
+%\widehat{\underline{\tau}_u^2}^{(m+1)} &= \dfrac{1}{2}\Big{(}\widehat{\underline{\tau}_u^2}^{(m)}-(\hat{\mu}^{(m)})^2\Big{)} + \frac{1}{2^{m+1}} \sum \limits_{i=2^{m}}^{2^{m+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(m+1)})^2 \\
 %\end{align*}
@@
 %\\
-%\widehat{\ov{$\tau$}_u^2}^{(\ell+1)} = \dfrac{1}{2} \widehat{\ov{$\tau$}_u^2}^{(\ell)} + \dfrac{1}{2^{\ell+1}} \sum \limits_{i=2^{\ell}+1}^{2^{\ell+1}-1} \Big{(}f(\vx_i)- f({\vx'}_{i,u}:\vx_{i,-u})\Big{)}^2
+%\widehat{\ov{$\tau$}_u^2}^{(m+1)} = \dfrac{1}{2} \widehat{\ov{$\tau$}_u^2}^{(m)} + \dfrac{1}{2^{m+1}} \sum \limits_{i=2^{m}+1}^{2^{m+1}-1} \Big{(}f(\vx_i)- f({\vx'}_{i,u}:\vx_{i,-u})\Big{)}^2 
 %\end{array}\right.
@@
 %\begin{proof}
-%Straightforward by developing $\widehat{\ov{$\tau$}_u^2}^{(\ell+1)}$.
+%Straightforward by developing $\widehat{\ov{$\tau$}_u^2}^{(m+1)}$.
 %\end{proof}

### 2016-08-12 article.tex
changes L

@@
-% !TEX TS-program = PDFLatexBibtex
-%&LaTeX
 \documentclass[]{elsarticle}
@@
 where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
+\begin{figure}[!ht]
+\centering
+\includegraphics{scheme_S.eps}
+\end{figure}
 
@@
 Set $m=m_0$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ accordingly to the multiplicative approach detailed in \cite{crass}.
-With this construction, $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two Sobol' sequences.
+With this construction, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two Sobol' sequences.
 Furthermore, they possess the structure of two replicated designs of order $1$.
@@
 
-Then, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can either be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices.
+$\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can either be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices.
 This option is referred as Variant $A$ in Algorithm \ref{recursive.algorithm}.
@@
 \begin{itemize}
-\item[$\bullet$] $2^{m_u}$ is the number of evaluations $f\left(\vx_{i,u}:{\vx'}_{i,-u}\right)$ used to estimate both $\underline{S}_u$ and $\overline{S}_u$.
+\item[$\bullet$] $2^{m_u}$ is the number of evaluations $f\left(\vx_{i,u}:{\vx'}_{i,-u}\right)$ used to estimate both the first-order index $\underline{S}_u$ and the total effect index $\overline{S}_u$.
 \item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
@@
 This cost can be seen as a generalisation of the one specified in Theorem \ref{saltelli.theorem}.
-If all $m_u$ are equal, the cost of Variant $A$ becomes $2^{m^\star}(d+2)$ and we recover the cost of Theorem \ref{saltelli.theorem} with $n=2^{m^\star}$.
+If all $m_u$ are equal, the cost of Variant $A$ becomes $2^{m^\star}(d+2)$ and we recover the cost in Theorem \ref{saltelli.theorem} with $n=2^{m^\star}$.
 
@@
 where: \begin{itemize}
-\item[$\bullet$] for $j\in \Gamma$, $2^{m''_{u_j}}$ is the number of evaluations $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate small first-order indices,
-\item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate both small first-order and total effect indices,
-\item[$\bullet$] for $j\in \mathcal{D}/\Gamma$, $ 2^{m_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate non small first-order indices,
+\item[$\bullet$] for $j\in \Gamma$, $2^{m''_{u_j}}$ is the number of evaluations $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate $\underline{S}_{u_j}$,
+\item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
+\item[$\bullet$] likewise, for $j\in \mathcal{D}/\Gamma$, $ 2^{m_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
 \item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
@@
 \begin{itemize}
-\item[1)] for $j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires as much or more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$.
+\item[1)] for $j \in \Gamma$, the total effect index $\ov{$S$}_{u_j}$ requires as much or more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_{u_j}$.
 Since the total effect estimator is the same, as a consequence we have $m'_{u_j}=m_{u_j}$ and $c_j >0$.
-\item[2)] for $j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires less evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$.
+\item[2)] for $j \in \Gamma$, the total effect index $\ov{$S$}_{u_j}$ requires less evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_{u_j}$.
 In this case, if both $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ then $c_j \leq 0$.
@@
 We expect to have more case $2)$ than case $1)$.
-The reason is that the numerator of the first-order index (\ref{}) requires to estimate $2d-1$ integrals against only $d+1$ integrals for the numerator of the total effect index (\ref{}).
-Thus, it seems reasonable to suppose that it takes less points to evaluate (\ref{}) than (\ref{}).
-Furthermore, in case $2$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to be often satisfied as ``Correlation 2" has been shown 
-to perform the best.
+Indeed, the numerator of the first-order index $\underline{S}_u$ requires to estimate $2d-1$ integrals against only $d+1$ integrals for the numerator of the total effect index $\ov{$S$}_u$.
+It seems reasonable to suppose that it takes less points to evaluate $\ov{$S$}_u$ than $\underline{S}_u$.
 
-To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{appli}. 
+Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to be often satisfied as ``Correlation 2" has been shown 
+to perform the best for small first-order indices. To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{appli}. 
 \bigskip
@@
 To overcome this issue, we propose the following alternative for Variant $A$.
-Assume that there exists one or multiple  $u \in \mathcal{D}$ such that estimates $\widehat{\underline{S}_u}^{(m)}$ are smaller than a specified threshold at the end of the first iteration of Algorithm \ref{recursive.algorithm}.
-Then, for these indices, at the next iteration estimator (\ref{first.order.est}) is switched for (\ref{correlation2}) and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed for the evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+If at the end of the first iteration, the estimate $\widehat{\underline{S}_u}^{(m)}$, $u \in \mathcal{D}$, is smaller than a specified threshold, then at the next iteration estimator (\ref{first.order.est}) is switched for (\ref{correlation2}) and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed for the evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
 

### 2016-08-12 article.tex
Completing information in section "Reliable cubatures" in article.tex

@@
 \newcommand{\fudge}{\fC}
+\newcommand{\cc}{\mathcal{C}}
 \newcommand{\dtf}{\textit{\doubletilde{f}}}
@@
 \newcommand{\vz}{\bvec{z}}
+\newcommand{\vt}{\bvec{t}}
 \newcommand{\dif}{\mathsf{d}}
@@
 
-We assume we have an embedded sequence of digital nets in base $b$,
+We assume we have an embedded sequence of digital nets in base $b$ as in \cite[Sec. 2-3]{HicJim},
 \[
@@
 \]
+Each $\mathcal{P}_m$ has a group structure under the digit wise addition:
+\[
+\vx \oplus \vt = \left(\sum_{\ell=1}^{\infty} [(x_{j\ell} + t_{j\ell}) \bmod b] b^{-\ell} \pmod{1} \right)_{j=1}^d,
+\]
+where $x_{j\ell}$ and $t_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ component of points $\vx$ and $\vt$.
 
-Each $\mathcal{P}_m$ has a group structure under the digit wise addition.
-Analogously, we can also define the dual nets as $\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vx}{\vk}=0,\, \vx\in\mathcal{P}_m\}$,
+In order to relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the relationship between any digital net and the \emph{wavenumber} space $\mathbb{N}_0^d$.
+Hence, a dual net is
 \[
+\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vx}{\vk}=0,\, \vx\in\mathcal{P}_m\},
+\]
+and inherits the same embedded structure as for the digital nets,
+\begin{equation}\label{dual_net_structure}
 \mathcal{P}_0^\perp=\left\{\mathbb{N}_0^d\right\}\supset\dots\supset\mathcal{P}_\infty=\{\bvec{0}\}.
-\]
+\end{equation}
 
-An important property is that for any Walsh basis $\phi_{\vk}(\vx)$
-\[
+As shown in \cite[Sec. 3]{HicJim}, the group structure of the digital nets guarantees the property below affecting any Walsh basis $\phi_{\vk}(\vx)$,
+\begin{equation}\label{basis_integ_prop}
 \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\phi_{\vk}(\vx)=
@@
 \end{cases}
-\]
+\end{equation}
+Therefore, considering the Walsh decomposition $f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)$ for any $f\in L^2([0,1]^d)$ and property \eqref{basis_integ_prop},
+\begin{align*}
+\abs{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} & = \abs{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}\\
+& = \abs{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}}
+\end{align*}
 
-Therefore,
-\[
-\abs{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}=\abs{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}}
-\]
+Based on the size of $\abs{\hf_{\vk}}$ and the structure of the dual nets \eqref{dual_net_structure}, in \cite[Sec.
+4.1]{HicJim} we proposed an ordering of the wavenumbers $\vk(\cdot):\naturals_0\rightarrow\naturals_0^d$.
+To simplify notation, $\hf_{\kappa}:=\hf_{\vk(\kappa)}$.
+This mapping leads to the following error bound,
+\begin{equation}
+\abs{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
+\end{equation}
 
-In \cite{HicJim} we proposed an algorithm based on digital nets that estimates hight dimensional integrals whose error lies within a user-input error tolerance.
-This algorithm finds the number of data points automatically.
-We will refer to it as $\widehat{I}(f;\varepsilon)$, where $f$ is the function to integrate and $\varepsilon$ the user-input error tolerance.
+However, because the knowledge of the Walsh coefficients $\hf_{\kappa}$ is not assumed, we will estimate them using $\mathcal{P}_m$ instead, and refer to them as $\tf_{m,\kappa}$.
 
-The main result from the article if that for all $f\in\mathcal{C}$,
-\[
-\abs{\int_{\cube} f(\vx)\,d\vx - \widehat{I}(f;\varepsilon)}\leq a(r,m)\sum_{\kappa=\left \lfloor 2^{m-r-1}\right \rfloor}^{2^{m-r}-1} \abs{\tf_{m,\kappa}}\leq \varepsilon.
-\]
-\begin{itemize}
-\item $\tf_{m,\kappa}=$ discrete Fourier Walsh coefficients of $f$.
-\item $a(r,m)=$ inflation factor that depends on $\mathcal{C}$.
-\end{itemize}
+For $\ell,m \in \mathbb{N}_0$ and $\ell \le m$ we introduce the following notation,
+\begin{gather*}
+S_m(f) =  \sum_{\kappa=\left \lfloor b^{m-1} \right \rfloor}^{b^{m}-1} \abs{\hf_{\kappa}}, \qquad 
+\hS_{\ell,m}(f)  = \sum_{\kappa=\left \lfloor b^{\ell-1} \right \rfloor}^{b^{\ell}-1} \sum_{\lambda=1}^{\infty} \abs{ \hf_{\kappa+\lambda b^{m}}}, \\
+\wcS_m(f)=\hS_{0,m}(f) + \cdots + \hS_{m,m}(f)=
+\sum_{\kappa=b^{m}}^{\infty} \abs{\hf_{\kappa}}, \qquad
+\tS_{\ell,m}(f) = \sum_{\kappa=\left \lfloor b^{\ell-1}\right \rfloor}^{b^{\ell}-1} \abs{\tf_{m,\kappa}}.
+\end{gather*}
+
+Finally, we define the set of functions $\cc$,
+\begin{multline} \label{conecond}
+\cc:=\{f \in L^2(\cube) : \hS_{\ell,m}(f) \le \homega(m-\ell) \wcS_m(f),\ \ \ell \le m, \\
+\wcS_m(f) \le \wcomega(m-\ell) S_{\ell}(f),\ \  \ell_* \le \ell \le m\}.
+\end{multline}
+for $\ell_* \in \mathbb{N}$, $\homega$ and $\wcomega$ two non-negative valued functions with $\lim_{m \to \infty} \wcomega(m) = 0$ and such that $\homega(r)\wcomega(r)<1$ for some $r\in\mathbb{N}$.
+
+Hence, in \cite[Sec. 4.2]{HicJim} we prove that for any $f\in\cc$,
+\begin{equation}
+\abs{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
+\le \frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}. \label{errbd}
+\end{equation}
+where one may increase $m$ until the error bound is small enough.
+
+The details about the algorithm, mapping of the wavenumber space, or meaning and properties of $\cc$, are discussed in \cite{HicJim}.
 
@@
 where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
-\begin{figure}[!ht]
+\begin{figure}[H]
 \centering
-\includegraphics{scheme_S.eps}
+\includegraphics[width=\textwidth]{Images/scheme_S.eps}
 \end{figure}

### 2016-08-12 article.tex
Modifying the description of the estimators in article.tex

@@
 \subsection{Reliable Estimation Using Quasi-Monte Carlo}
+\label{section.error.algo}
 
@@
 \begin{align*}
-\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
-\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
+\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} \left(f(\vx)-
+f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_3-(I_4)^2}, \\
+\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_2}{I_3-(I_4)^2}.
 \end{align*}
-Therefore, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
-If we can estimate $\vI$ such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$, then we can define the following estimators for the Sobol' indices:
+If $\vI:=(I_1,I_2,I_3,I_4)$, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
+If we estimate $\vI$ by $\widehat{\vI}$ and error bound $\varepsilon_{\vI}$ according to \ref{section.error.algo}, then $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
+
+Alternatively to the common estimators $\widehat{\underline{S}_u}=\underline{S}_u(\widehat{\vI})$ and $\widehat{\overline{S}_u}=\overline{S}_u(\widehat{\vI})$, we propose the following estimators:
 \begin{align*}
-\widehat{S}_u & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right) \\
-\varepsilon_{S_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right)
+\widehat{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right), \\
+\varepsilon_{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right),
 \end{align*}
-where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
+and,
+\begin{align*}
+\widehat{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right), \\
+\varepsilon_{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right).
+\end{align*}
+These new estimators allow us to say that $\underline{S}_u\in [\widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u}]$ and $\overline{S}_u\in [\widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u}]$.
+
+For a better understanding of these estimators, we provide and example in dimension 1 below,
 \begin{figure}[H]

### 2016-08-12 Images/article_scheme_S.m

@@ -1,4 +1,4 @@
-    set(0,'defaultaxesfontsize',24,'defaulttextfontsize',24) %make font larger
+    set(0,'defaultaxesfontsize',28,'defaulttextfontsize',28) %make font larger
     set(0,'defaultLineLineWidth',3) %thick lines
     set(0,'defaultTextInterpreter','latex') %latex axis labels
     set(0,'defaultLegendInterpreter','latex') %latex axis labels
@@ -6,6 +6,7 @@
 
 S = @(x) exp(-(x-1).^2) + 1;
 
+Ireal = I - err + 0.03;
 I = 0.90;
 err = 0.2;
 Smax = S(1); xmax = 1;
@@ -16,19 +17,22 @@ x = I - err - 0.06:0.02:I + err + 0.06;
 ymin = min(S(x));
 ymax = max(S(x));
 
-plot(x,S(x))
+plot(x, S(x), 'k')
 ax = gca;
 set(ax,'TickLabelInterpreter', 'Latex');
-ax.XTick = [I-err I I+err];
-ax.YTick = [Smin (Smin+Smax)/2 S(I) Smax];
-ax.XTickLabel = {'$\hat{I}-err$','$\hat{I}$','$\hat{I}+err$'};
-ax.YTickLabel = {'$S_{\min}$', '$(S_{\min}+S_{\max})/2$', '$S(\hat{I})$', '$S_{\max}$'};
+ax.XTick = [I-err Ireal I I+err];
+ax.YTick = [Smin S(Ireal) (Smin+Smax)/2 S(I) Smax];
+ax.XTickLabel = {'$\hat{I}-\varepsilon_{I}$','$I$','$\hat{I}$','$\hat{I}+\varepsilon_{I}$'};
+ax.YTickLabel = {'$S_{\min}$', '$S(I)$','$(S_{\min}+S_{\max})/2$', '$S(\hat{I})$', '$S_{\max}$'};
 hold on
+area(I - err:0.02:I + err, S(I - err:0.02:I + err))
 plot([xmin xmin], [ymin Smin], 'k--')
 plot([x(1) xmin], [Smin Smin], 'k--')
 plot([I I], [ymin S(I)], 'k--')
 plot([x(1) I], [S(I) S(I)], 'k--')
 plot([xmax xmax], [ymin Smax], 'k--')
 plot([x(1) xmax], [Smax Smax], 'k--')
[…]

### 2016-08-18 article/article.tex
added template journal and aux. files

--- 2016-08-12 article.tex
@@
 Denote by $f$ a numerical model, by $\vx=(x_1,\dots,x_d)$ its vector of inputs and set $\mathcal{D}=\{1,\dots,d\}$.
-The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
+%The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
 Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality.
@@
 \begin{equation}
-f(\vx)=\mu+\sum \limits_{u \subseteq \mathcal{D}} f_u(\vx),
+f(\vx)=\mu+\sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} f_u(\vx),
 \label{anova}
@@
 Due to orthogonality, taking the variance of each side in equation (\ref{anova}) leads to the variance decomposition of $f$:
-\[ \sigma^2 = \sum \limits_{u \subseteq \{1,\dots,d\}} \sigma_v^2, \ \text{ with } \ \sigma_v^2=\int_{[0,1)^{|v|}} f_v(\vx)^2 d{\vx}.\]
+\[ \sigma^2 = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1)^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
 From the variance decomposition of $f$, on can express the following two quantities:
@@
 $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ satisfy the following relations: $ 0 \leq  \underline{\tau}_u^2 \leq \ov{$\tau$}_u^2$ and $\underline{\tau}_u^2 = \sigma^2 - \ov{$\tau$}_{-u}^2$.
-These two measure are commonly found in the litterature in their normalized form: $\underline{S}_u = \underline{\tau}_u^2 / \sigma^2$ is the closed $|u|$-order Sobol' index for the set $u$, while $\ov{$S$}_u = \ov{$\tau$}_u^2 / \sigma^2$ is the total effect Sobol' index for the set $u$.
+These two measure are commonly found in the litterature in their normalized form: $\underline{S}_u = \underline{\tau}_u^2 / \sigma^2$ is the closed $|u|$-order Sobol' index for the set $u$, while $\ov{$S$}_u = \ov{$\tau$}_u^2 / \sigma^2$ is the total effect Sobol' index.
 \bigskip
@@
 The problem of interest here is the evaluation of first-order and total effect Sobol' indices.
-The computation of these indices is performed based on the following integral formula for their numerators:
+The computation of these indices is performed based on the following integral formulas for their numerators:
 \begin{align}
@@
 \underline{\tau}_u^2  &= \int_{[0,1)^{2d-1}} \left(f(\vx)-
-f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}, \\
+f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'_{-u}}, \\
 \label{total.effect}
-\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}, \qquad u \in \mathcal{D},
+\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2 d{\vx'} d\vx_u, \qquad u \in \mathcal{D},
 \end{align}
 The variance of $f$ is evaluated by:
-\[ \sigma^2 = \int_{[0,1)^{d}} f(\vx)^2d{\vx} - \mu^2, \text{ with } \ \mu = \int_{[0,1)^{d}} f(\vx) d{\vx}.\]
-Most of the time, the complexity of $f$ causes the computation of $\mu$, $\sigma^2$ and integrals (\ref{first.order}) and (\ref{total.effect}) to be intractable.
+\begin{equation}
+\sigma^2 = \int_{[0,1)^{d}} f(\vx)^2d{\vx} - \mu^2, \text{ with } \ \mu = \int_{[0,1)^{d}} f(\vx) d{\vx}.
+\label{eq.sigma.mu}
+\end{equation} 
+Most of the time, the complexity of $f$ causes the computation of integrals (\ref{first.order}), (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable.
 In such case, one needs to rely on an estimation of these quantities.
@@
 \end{equation}
-The estimation of a single pair ($\underline{\tau}_u^2$, $\ov{$\tau$}_u^2$) requires $3n$ evaluations of the model $f$.
+The Sobol' indices estimators are defined by:
+\begin{equation*}
+\widehat{\underline{S}_u} = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
+\widehat{\overline{S}_u} = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
+\end{equation*}
+The estimation of a single pair ($\widehat{\underline{S}_u}$, $\widehat{\overline{S}_u}$) requires $3n$ evaluations of the model $f$.
 Using a combinatorial formalism, in \cite[Theorem 1]{Saltelli} Saltelli proposes the following estimation strategy:
@@
 $\mathcal{P}'$) indexed by $u$.
-We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if $\forall \ u \subsetneq \mathcal{D}$ of cardinality $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1)^a$.
-We note $\pi_u$ the permutation reordering the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
+We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if $\forall \ u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1)^a$.
+We note $\pi_u$ the permutation arranging the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
 \end{definition}
@@
 
-More specifically, let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$.
+More precisely, let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$.
 Denote by $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$.
@@
 Then, remark that $\forall i \in \{0,\dots,n-1\}$:
-\[\pi_u(f({\vx'}_i))=f({\vx'}_{\pi_u(i)})=f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u})=f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u})\]
-%\pi_u(f({\vx'}_{i,u}:{\vx'}_{i,-u}))
-Each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) with $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{\pi_u(f({\vx'}_i))\}_{i=0}^{n-1}$ without requiring further model evaluations.
+\[\pi_u(f({\vx'}_i))=f({\vx'}_{\pi_u(i)})=f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u})=f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).\]
+Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) with $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{\pi_u(f({\vx'}_i))\}_{i=0}^{n-1}$ without requiring further model evaluations.
 This estimation method has been deeply studied and generalized in Tissot et al.
@@
 In the following we refer to this method as replication procedure.
+
+\subsection{Towards a reliable estimation}
+The aim of this paper is to propose a recursive procedure to estimate first-order and total effect Sobol' indices.
+The choice of the stopping criterion is the key point of this paper.
+In \cite{Gilquin16}, the authors propose a recursive version of the replication procedure.
+In this recursive version, the stopping criterion is an absolute difference between estimates computed on consecutive steps.
+
+More generally, in most recursive approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly upon the estimates.
+Such stopping criteria often involve hyper-parameters hard to tweak but above all fail to guarantee any error bound on the estimates.
 \bigskip
 
-\subsection{Towards a reliable estimation}
-The aim of this paper is to propose a recursive estimation procedure to estimate Sobol' indices. The choice of the stopping criterion is the key point of this paper.
-
-In \cite{Gilquin16}, the authors propose a recursive version of the replication procedure.
-In this recursive version, the stopping criterion is an absolute difference between estimates computed on consecutive steps.
-More generally, in most recursive approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly upon the estimates.
-Such stopping criteria often involved hyperparameters hard to tweak but above all fail to guarantee any error bound on the estimation.
-\bigskip
-
-Our recursive procedure stands apart from others approaches by the construction of a robust stopping criterion.
+Our recursive procedure stands apart from others approaches with the construction of a robust stopping criterion.
 This criterion is an error bound based on the discrete Walsh decomposition of integrals (\ref{first.order}) and (\ref{total.effect}).
 This decomposition use the close set property of digital sequences.
-As such, our recursive procedure relies on the iterative construction of Sobol' sequences.
-The iterative construction of the Sobol' sequences is performed accordingly to the multiplicative  approach presented in \cite{crass}.
+As such, our recursive procedure relies on an iterative construction of Sobol' sequences.
+This construction is performed accordingly to the multiplicative  approach presented in \cite{crass}.
 
-The construction of the error bound is the subject of the next section \ref{section.error}. Our recursive estimation procedure is presented in section \ref{section.recursive.procedure}.
+The construction of the error bound is the subject of the next section. Our recursive estimation procedure is presented in section \ref{section.recursive.procedure}.
 
-\section{Reliable Error Estimation for Cubatures}
+\section{Reliable error bound for Sobol' indices}
 \label{section.error}
 
-\subsection{Reliable Estimation Using Quasi-Monte Carlo}
+\subsection{Reliable integral estimation using quasi-Monte Carlo}
 \label{section.error.algo}
@@
 
-The details about the algorithm, mapping of the wavenumber space, or meaning and properties of $\cc$, are discussed in \cite{HicJim}.
+Details concerning the algorithm, mapping of the wavenumber space, or meaning and properties of $\cc$, are provided in \cite{HicJim}.
+For the rest of the paper we only consider Sobol' sequences.
+These sequences are digital sequences in based $b=2$.
+Their major interests come from their fast and easy implementation as well as their slow growing size rate.
+Further details concerning these sequences can be found in \cite{Lemieuxbook,Niederreiter92}.
 
-\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
-In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$.
+\subsection{Generalization to Sobol' indices}
+The idea here is to extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To do so, we consider the two integral formulas of the first-order and total effect Sobol' indices:
+%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
+%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$.
 In both cases, regular and normalized indices can be approximated by estimating some integrals,
+
 \begin{align*}
-\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} \left(f(\vx)-
-f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_3-(I_4)^2}, \\
-\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_2}{I_3-(I_4)^2}.
+\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d-1}} \left(f(\vx)-
+f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2} = \frac{I_1}{I_3-(I_4)^2}, \\
+\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2} = \frac{I_2}{I_3-(I_4)^2},
 \end{align*}
-If $\vI:=(I_1,I_2,I_3,I_4)$, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
+where $\vI=(I_1,I_2,I_3,I_4)$.
+Thus, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
 If we estimate $\vI$ by $\widehat{\vI}$ and error bound $\varepsilon_{\vI}$ according to \ref{section.error.algo}, then $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
+\bigskip
 
-Alternatively to the common estimators $\widehat{\underline{S}_u}=\underline{S}_u(\widehat{\vI})$ and $\widehat{\overline{S}_u}=\overline{S}_u(\widehat{\vI})$, we propose the following estimators:
-\begin{align*}
+Alternatively to the common estimators $\widehat{\underline{S}_u}=\underline{S}_u(\widehat{\vI})$ and $\widehat{\overline{S}_u}=\overline{S}_u(\widehat{\vI})$, we consider here the following estimators with their respective error bounds:
+\begin{gather}
+\begin{aligned}
 \widehat{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right), \\
 \varepsilon_{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right),
-\end{align*}
+\end{aligned}
+\label{formula_undersu}
+\end{gather}
 and,
-\begin{align*}
+\begin{gather}
+\begin{aligned}
 \widehat{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right), \\
 \varepsilon_{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right).
-\end{align*}
-These new estimators allow us to say that $\underline{S}_u\in [\widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u}]$ and $\overline{S}_u\in [\widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u}]$.
-
-For a better understanding of these estimators, we provide and example in dimension 1 below,
+\end{aligned}
+\label{formula_oversu}
+\end{gather}
+These new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u} \right] ;\] This property is illustrated below in dimension one.
 \begin{figure}[H]
 \centering
-\includegraphics[width=\textwidth]{Images/scheme_S.eps}
+\includegraphics[width=0.5\textwidth]{Images/scheme_S.eps}
 \end{figure}
@@
 
-The recursive estimation procedure we propose combine the error bound presented in the previous section with one of the two estimation strategies of section \ref{estimation.strategies}, namely Saltelli's strategy and the replication procedure.
-The form of the stopping criterion is the same for both strategies.
-It is defined as $\abs{\varepsilon_{S_u}} \leq \epsilon$, where $\epsilon$ is the desired precision on the Sobol' indices.
+The recursive estimation procedure we propose combine the error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ presented in the previous section with one of the two estimation strategies of section \ref{estimation.strategies}, namely Saltelli's strategy and the replication procedure.
 
 We start be detailing our recursive procedure in the form of an algorithm.
-Then, we discuss a possible improvement by considering a new estimator recently introduced in \cite{Owen} for first-order indices.
+Then, we discuss a possible improvement by considering a new estimator recently introduced in \cite{Owen} for the first-order indices.
 
@@
 Algorithm \ref{recursive.algorithm} summarizes the main steps of our recursive procedure.
-First, fix the target precision $\epsilon >0$.
-Set $m=m_0$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ accordingly to the multiplicative approach detailed in \cite{crass}.
+First, one must fix the target precision $\epsilon >0$ for the Sobol' estimates.
+The stopping criterion is initialized with $\zeta=\epsilon+1$.
+Then, we set $m=m_0$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ accordingly to the multiplicative approach detailed in \cite{crass}.
 With this construction, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two Sobol' sequences.
-Furthermore, they possess the structure of two replicated designs of order $1$.
+Furthermore, they possess the structure of two replicated designs of order $1$ (Definition \ref{rep.designs}).
 \bigskip
 
-$\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can either be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices.
+$\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices.
 This option is referred as Variant $A$ in Algorithm \ref{recursive.algorithm}.
-Or $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can be used with the replication procedure to estimate all first-order Sobol' indices.
+
+Alternatively, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can be used with the replication procedure to estimate all first-order Sobol' indices.
 This option is referred as Variant $B$ in Algorithm \ref{recursive.algorithm}.
 
-If the stopping criterion is satisfied, the algorithm stops and Sobol' estimates are returned. Otherwise, $m$ is incremented by one to perform a new estimation.
+In both case we test if the respective error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ are lower than the target precision $\epsilon$.
+\bigskip
+
+If the stopping criterion is satisfied, that is if $bool$ is true, the algorithm stops and Sobol' estimates are returned. Otherwise, $m$ is incremented by one to perform a new estimation.
 
@@
 \State set: $m \leftarrow m_0$
-\While {$\abs{\varepsilon_{S_u}} \leq \epsilon$}
+\State $bool \leftarrow false$
+\While {$! bool$}
 \State $\mathcal{P}_m \leftarrow \mathcal{P}_{m-1} \cup B_m$
@@
 \hspace*{-0.3cm} $\mathcal{P}'_m \leftarrow \mathcal{P}'_{m-1} \cup {B'}_m$
-\For {$u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$}
+\For {$u =1,\dots,d$}
 \If {Variant $A$}
-\State estimate $\widehat{\underline{S}_u}^{(m)}$ and $\widehat{\ov{$S$}_u}^{(m)}$ with formula \ref{} and Saltelli's strategy
+\State estimate $\widehat{\underline{S}_u}^{(m)}$ and $\widehat{\ov{$S$}_u}^{(m)}$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}) and Saltelli's strategy
+\State $bool_u \leftarrow \abs{\varepsilon_{\underline{S}_u}} \leq \epsilon \ \& \ \abs{\varepsilon_{\overline{S}_u}} \leq \epsilon$
 \EndIf
 \If {Variant $B$}
-\State estimate $\widehat{\underline{S}_u}^{(m)}$ with formula \ref{} and the replication procedure
+\State estimate $\widehat{\underline{S}_u}^{(m)}$ with formula (\ref{formula_undersu}) and the replication procedure
+\State $bool_u \leftarrow \abs{\varepsilon_{\underline{S}_u}} \leq \epsilon$
 \EndIf
 \EndFor
+\State $bool \leftarrow \forall u: \ bool_u$
 \State $m \leftarrow m + 1$
@@
 \begin{itemize}
-\item[$\bullet$] $2^{m_u}$ is the number of evaluations $f\left(\vx_{i,u}:{\vx'}_{i,-u}\right)$ used to estimate both the first-order index $\underline{S}_u$ and the total effect index $\overline{S}_u$.
+\item[$\bullet$] $2^{m_u}$ is the number of evaluations $f\left(\vx_{i,u}:{\vx'}_{i,-u}\right)$ used to estimate both the first-order index $\underline{S}_u$ and the total effect index $\overline{S}_u$,
 \item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
@@
 
-We focus on the use of a better estimator to evaluate small first-order Sobol' indices in Variant $A$.
+We focus on the use of a recent estimator to evaluate small first-order Sobol' indices in Variant $A$.
 This estimator is called ``Correlation 2" and was introduced by Owen in \cite{Owen}.
-Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small closed Sobol' indices.
-Our aim is to show that using ``Correlation 2" in procedure $A$ may reduce the total number of model evaluations.
+Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices.
+Our aim is to show that using ``Correlation 2" in Variant $A$ may reduce the total number of model evaluations.
 Its formula writes as follows:
@@
 The idea is to replace the current estimator (\ref{first.order.est}) by (\ref{correlation2}) for each small first-order index.
+
 Assume that the number of small first-order indices is known and equals $\gamma$.
 We denote by $u_1,\dots,u_{\gamma}$ the indexes of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$.
-
 The cost of Variant $A$ including ``Correlation 2" writes:
@@
 \begin{itemize}
-\item[1)] for $j \in \Gamma$, the total effect index $\ov{$S$}_{u_j}$ requires as much or more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_{u_j}$.
+\item[1)] for $j \in \Gamma$, the total effect index $\ov{$S$}_{u_j}$ requires as much or more evaluations than the first-order index $\underline{S}_{u_j}$.
 Since the total effect estimator is the same, as a consequence we have $m'_{u_j}=m_{u_j}$ and $c_j >0$.
-\item[2)] for $j \in \Gamma$, the total effect index $\ov{$S$}_{u_j}$ requires less evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_{u_j}$.
+\item[2)] for $j \in \Gamma$, the total effect index $\ov{$S$}_{u_j}$ requires less evaluations than the first-order index $\underline{S}_{u_j}$.
 In this case, if both $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ then $c_j \leq 0$.
 \end{itemize}
-We can write $\Gamma = \Gamma_1 \cup \Gamma_2$, $\Gamma_1 \cap \Gamma_2=\varnothing$, to separate the number of times case $1)$ or case $2)$ are verified.
-We expect to have more case $2)$ than case $1)$.
-Indeed, the numerator of the first-order index $\underline{S}_u$ requires to estimate $2d-1$ integrals against only $d+1$ integrals for the numerator of the total effect index $\ov{$S$}_u$.
-It seems reasonable to suppose that it takes less points to evaluate $\ov{$S$}_u$ than $\underline{S}_u$.
+Overall we expect to have more case $2)$ than case $1)$.
+Indeed, the numerator of $\underline{S}_u$ requires to estimate $2d-1$ integrals against only $d+1$ integrals for the numerator of $\ov{$S$}_u$.
+Hence, it seems reasonable to suppose that it takes less points to evaluate $\ov{$S$}_u$ than $\underline{S}_u$.
 
-Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to be often satisfied as ``Correlation 2" has been shown 
-to perform the best for small first-order indices. To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{appli}. 
+Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to be always satisfied as ``Correlation 2" has been shown 
+to perform the best for small first-order indices.
+
+To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{appli}. 
 \bigskip

### 2016-08-18 article/template.tex
added template journal and aux. files

--- 2016-08-18 article/article.tex
@@
-\documentclass[]{elsarticle}
-\setlength{\marginparwidth}{0.5in}
-\usepackage{amsmath,amssymb,amsthm,natbib,
-mathtools,bbm,extraipa,mathabx,graphicx,algorithm}
+%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% This is a general template file for the LaTeX package SVJour3
+% for Springer journals.          Springer Heidelberg 2010/09/16
+%
+% Copy it to a new file with a new name and use it as the basis
+% for your article. Delete % signs as needed.
+%
+% This template includes a few options for different layouts and
+% content for various journals. Please consult a previous issue of
+% your journal as needed.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% First comes an example EPS file -- just ignore it and
+% proceed on the \documentclass line
+% your LaTeX will extract the file if required
+%\begin{filecontents*}{example.eps}
+%!PS-Adobe-3.0 EPSF-3.0
+%%BoundingBox: 19 19 221 221
+%%CreationDate: Mon Sep 29 1997
+%%Creator: programmed by hand (JK)
+%%EndComments
+%gsave
+%newpath
+%  20 20 moveto
+%  20 220 lineto
+%  220 220 lineto
+%  220 20 lineto
+%closepath
+%2 setlinewidth
+%gsave
+%  .4 setgray fill
+%grestore
+%stroke
+%grestore
+%\end{filecontents*}
+%
+\RequirePackage{fix-cm}
+\RequirePackage{amsmath}
+%
+%\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+\smartqed  % flush right qed marks, e.g. at end of proof
+%
+\usepackage{graphicx}
+%
+\usepackage{mathptmx}      % use Times fonts if available on your TeX system
+%
+% insert here the call for the packages your document requires
+\let\amalg\relax
+\usepackage{amssymb,
+mathtools,bm,extraipa,mathabx,graphicx,algorithm}
 \usepackage{algpseudocode}
-%accents,
+\usepackage{url}
 
-\newtheorem{lem}{Lemma}
-\newtheorem{remark}{Remark}
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}{Proposition}
-\theoremstyle{definition}
-\newtheorem{algo}{Algorithm}
+%\usepackage{latexsym}
+% etc.
+%
+% please place your own definitions here and don't use \def but
+% \newcommand{}{}
 
@@
 \newcommand{\cube}{[0,1)^d}
-%\renewcommand{\bbK}{\natzero^d}
 \newcommand{\rf}{\mathring{f}}
@@
 \newcommand{\e}{\text{e}}
-\newcommand{\bvec}[1]{\boldsymbol{#1}}
-\newcommand{\vx}{\bvec{x}}
-\newcommand{\vI}{\bvec{I}}
-\newcommand{\vk}{\bvec{k}}
-\newcommand{\vw}{\bvec{w}}
-\newcommand{\vz}{\bvec{z}}
-\newcommand{\vt}{\bvec{t}}
+%\newcommand{\bvec}[1]{\boldsymbol{#1}}
+\newcommand{\vect}[1]{\boldsymbol{\mathbf{#1}}}
+\newcommand{\vx}{\vect{x}}
+\newcommand{\vI}{\vect{I}}
+\newcommand{\vk}{\vect{k}}
+\newcommand{\vw}{\vect{w}}
+\newcommand{\vz}{\vect{z}}
+\newcommand{\vt}{\vect{t}}
 \newcommand{\dif}{\mathsf{d}}
@@
 \newcommand{\wcomega}{\mathring{\omega}}
-\newcommand{\vzero}{\bvec{0}}
+\newcommand{\vzero}{\vect{0}}
 \newcommand{\integers}{\mathbb{Z}}
@@
 \makeatletter
-\newcommand*{\ov}[1]{
+\newcommand{\ov}[1]{
   \m@th\overline{\mbox{#1}\raisebox{2mm}{}}
 }
-
-\def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}
-
+\newcommand{\absolute}[1]{\left\lvert#1\right\rvert}
 \let\oldemptyset\emptyset
@@
 
+% Insert the name of "your journal" with
+% \journalname{myjournal}
+%
 \begin{document}
 
-\begin{frontmatter}
+\title{Reliable error estimation for Sobol' indices%\thanks{Grants or other notes
+%about the article that should go on the front page should be
+%placed here. General acknowledgments should be placed at the end of the article.}
+}
+%\subtitle{Do you have a subtitle?\\ If so, write it here}
 
-\title{Reliable error estimation for Sobol' indices}
+%\titlerunning{Short form of title}        % if too long for running head
 
-\author{Cl\'ementine Prieur, Elise Arnaud, Laurent Gilquin, Fred J. Hickernell, Llu\'{i}s Antoni Jim\'{e}nez Rugama}
-\address{U. Josef Fourier, Illinois Institute of Technology}
+\author{Laurent Gilquin \and
+        Llu\'{i}s Antoni Jim\'{e}nez Rugama %etc.
+}
+
+%\authorrunning{Short form of author list} % if too long for running head
+
+\institute{Laurent Gilquin \at
+              Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 655 avenue de l'Europe, 38330 Montbonnot \\
+              %Tel.: +123-45-678910\\
+              %Fax: +123-45-678910\\
+              \email{gilquin.laurent@inria.fr}           %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+           \and
+           Llu\'{i}s Antoni Jim\'{e}nez Rugama \at
+              Illinois Institute of Technology, Rettaliata Engineering Center, 10 W 32st, Chicago, IL 60616 \\
+\email{ljimene1@hawk.iit.edu}
+}
+
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
+
+\maketitle
+
 \begin{abstract}
+Insert your abstract here. Include keywords, PACS and mathematical
+subject classification numbers as needed.
+\keywords{First keyword \and Second keyword \and More}
+% \PACS{PACS code1 \and PACS code2 \and more}
+% \subclass{MSC code1 \and MSC code2 \and more}
 \end{abstract}
 
-\end{frontmatter}
+%\section{Introduction}
+%\label{intro}
+%Your text comes here. Separate text sections with
+%\section{Section title}
+%\label{sec:1}
+%Text with citations \cite{RefB} and \cite{RefJ}.
+%\subsection{Subsection title}
+%\label{sec:2}
+%as required. Don't forget to give each section
+%and subsection a unique label (see Sect.~\ref{sec:1}).
+%\paragraph{Paragraph headings} Use paragraph headings as needed.
+%\begin{equation}
+%a^2+b^2=c^2
+%\end{equation}
+
+% For one-column wide figures use
+%\begin{figure}
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+%  \includegraphics{example.eps}
+% figure caption is below the figure
+%\caption{Please write your figure caption here}
+%\label{fig:1}       % Give a unique label
+%\end{figure}
+%
+% For two-column wide figures use
+%\begin{figure*}
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+%  \includegraphics[width=0.75\textwidth]{example.eps}
+% figure caption is below the figure
+%\caption{Please write your figure caption here}
+%\label{fig:2}       % Give a unique label
+%\end{figure*}
+%
+% For tables use
+%\begin{table}
+%% table caption is above the table
+%\caption{Please write your table caption here}
+%\label{tab:1}       % Give a unique label
+%% For LaTeX tables use
+%\begin{tabular}{lll}
+%\hline\noalign{\smallskip}
+%first & second & third  \\
+%\noalign{\smallskip}\hline\noalign{\smallskip}
+%number & number & number \\
+%number & number & number \\
+%\noalign{\smallskip}\hline
+%\end{tabular}
+%\end{table}
 
 \section{Introduction}
+\label{sec:1}
 
@@
 \section{Backgrounds on Sobol' indices}
+\label{sec:2}
 
 \subsection{Definition of Sobol' indices}
+\label{sec:2.1}
 %We adopt the same notations introduced by Owen in \cite{Owen}. 
@@
 Let $f$ be the symbol representing the numerical model studied. We assume $f \in \mathcal{L}^2[0,1)^d$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
-The uncertainty on $\vx$ is modeled by random variables such that $\vx \iid \mathcal{U}[0,1)^d$. Recall the Hoeffding decomposition \cite{Hoeffding} of $f$:
+The uncertainty on $\vx$ is modeled by random variables such that $\vx \iid \mathcal{U}[0,1)^d$. Recall the Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$:
 \begin{equation}
@@
 \label{total.effect}
-\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2 d{\vx'} d\vx_u, \qquad u \in \mathcal{D},
+\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2 d\vx_u d{\vx'}, \ u \in \mathcal{D},
 \end{align}
@@
 \subsection{Estimation of Sobol' indices}
-\label{estimation.strategies}
+\label{sec:2.2}
 In this section we review two Monte Carlo procedures for the estimation of Sobol' indices.
@@
 Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid [0,1)^{2d}$.
-\bigskip
-
 One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
@@
 \label{first.order.est}
-\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_i)-f(\vx_{i,u}:{\vx'}_{i,-u}\right)f(\vx'_i),\\
+\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_i)-f(\vx_{i,u}:{\vx'}_{i,-u})\right)f(\vx'_i),\\
 \label{total.effect.est}
-\widehat{\ov{$\tau$}_u^2} & = \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
+\widehat{\ov{$\tau$}_u^2} & = \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \ u \in \mathcal{D},
 \end{align}
@@
 The Sobol' indices estimators are defined by:
-\begin{equation*}
+\begin{equation}
 \widehat{\underline{S}_u} = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
 \widehat{\overline{S}_u} = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
-\end{equation*}
+\label{common.sobol.est}
+\end{equation}
 The estimation of a single pair ($\widehat{\underline{S}_u}$, $\widehat{\overline{S}_u}$) requires $3n$ evaluations of the model $f$.
-Using a combinatorial formalism, in \cite[Theorem 1]{Saltelli} Saltelli proposes the following estimation strategy:
+Using a combinatorial formalism, in \cite{Saltelli} Saltelli proposes the following estimation strategy:
 \begin{theorem}
@@
 
-An efficient alternative to evaluate all first-order indices was proposed by Mara \textit{et al.} \cite{Mara}  requiring only $2n$ model evaluations.
+An efficient alternative to evaluate all first-order indices was proposed by \cite{Mara} requiring only $2n$ model evaluations.
 This alternative relies on the construction of two replicated designs.
-The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes in \cite{Mckay}.
+The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes \cite{McKay}.
 The definition we give here introduce the structure in a wider context:
@@
 Then, remark that $\forall i \in \{0,\dots,n-1\}$:
-\[\pi_u(f({\vx'}_i))=f({\vx'}_{\pi_u(i)})=f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u})=f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).\]
-Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) with $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{\pi_u(f({\vx'}_i))\}_{i=0}^{n-1}$ without requiring further model evaluations.
+\begin{align*}
+\pi_u(f({\vx'}_i))&=f({\vx'}_{\pi_u(i)}), \\
+\pi_u(f({\vx'}_i))&=f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u}), \\
+\pi_u(f({\vx'}_i))&=f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).
+\end{align*}
+Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) with \\ $\pi_u(f({\vx'}_i))$ in place of $f(\vx_{i,u}:{\vx'}_{i,-u})$ without requiring further model evaluations.
 This estimation method has been deeply studied and generalized in Tissot et al.
-\cite{Mara} to the case of closed second-order indices.
+\cite{Tissot} to the case of closed second-order indices.
 In the following we refer to this method as replication procedure.
@@
 \subsection{Towards a reliable estimation}
+\label{sec:2.3}
 The aim of this paper is to propose a recursive procedure to estimate first-order and total effect Sobol' indices.
 The choice of the stopping criterion is the key point of this paper.
-In \cite{Gilquin16}, the authors propose a recursive version of the replication procedure.
+%A recursive version of the replication procedure has recently been proposed by Gilquin et al.
+(2016) (preprint available at \url{https://hal.inria.fr/hal-01291769}).
 In this recursive version, the stopping criterion is an absolute difference between estimates computed on consecutive steps.
-
-More generally, in most recursive approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly upon the estimates.
+Generally, in most recursive approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly upon the estimates.
 Such stopping criteria often involve hyper-parameters hard to tweak but above all fail to guarantee any error bound on the estimates.
@@
 As such, our recursive procedure relies on an iterative construction of Sobol' sequences.
-This construction is performed accordingly to the multiplicative  approach presented in \cite{crass}.
+This construction is performed accordingly to the multiplicative approach presented in (Gilquin et al., 2016, preprint available at \url{https://hal.inria.fr/hal-01349444}).
 
-The construction of the error bound is the subject of the next section. Our recursive estimation procedure is presented in section \ref{section.recursive.procedure}.
+The construction of the error bound is the subject of the next section. Our recursive estimation procedure is detailed in section \ref{sec:4}.
 
 \section{Reliable error bound for Sobol' indices}
-\label{section.error}
+\label{sec:3} 
+We start by reviewing the construction of an error bound for the estimation of a multidimensional integral proposed in \cite{HicJim}.
+This construction is based on the Walsh decomposition of the integrand and relies on quasi-Monte Carlo points sets.
+Then, we present an extension of this error bound for the case of Sobol' indices.
+This extension exploits the integral formula of a Sobol' index.
 
 \subsection{Reliable integral estimation using quasi-Monte Carlo}
-\label{section.error.algo}
+\label{sec:3.1}
 
@@
 \[
-\mathcal{P}_0=\{\bvec{0}\}\subset\dots\subset\mathcal{P}_m=\{\vx_i\}_{i=0}^{b^m-1}\subset\dots\subset\mathcal{P}_\infty=\{\vx_i\}_{i=0}^{\infty}.
+\mathcal{P}_0=\{\vect{0}\}\subset\dots\subset\mathcal{P}_m=\{\vx_i\}_{i=0}^{b^m-1}\subset\dots\subset\mathcal{P}_\infty=\{\vx_i\}_{i=0}^{\infty}.
 \]
@@
 \begin{equation}\label{dual_net_structure}
-\mathcal{P}_0^\perp=\left\{\mathbb{N}_0^d\right\}\supset\dots\supset\mathcal{P}_\infty=\{\bvec{0}\}.
+\mathcal{P}_0^\perp=\left\{\mathbb{N}_0^d\right\}\supset\dots\supset\mathcal{P}_\infty=\{\vect{0}\}.
 \end{equation}
-
 As shown in \cite[Sec. 3]{HicJim}, the group structure of the digital nets guarantees the property below affecting any Walsh basis $\phi_{\vk}(\vx)$,
@@
 \end{equation}
-Therefore, considering the Walsh decomposition $f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)$ for any $f\in L^2([0,1]^d)$ and property \eqref{basis_integ_prop},
+Therefore, considering the Walsh decomposition: \[
+f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
+for any $f\in L^2([0,1]^d)$ and property \eqref{basis_integ_prop},
 \begin{align*}
-\abs{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} & = \abs{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}\\
-& = \abs{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}}
+\absolute{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
+\absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)} \\
+&= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}}
 \end{align*}
-
-Based on the size of $\abs{\hf_{\vk}}$ and the structure of the dual nets \eqref{dual_net_structure}, in \cite[Sec.
+Based on the size of $\absolute{\hf_{\vk}}$ and the structure of the dual nets \eqref{dual_net_structure}, in \cite[Sec.
 4.1]{HicJim} we proposed an ordering of the wavenumbers $\vk(\cdot):\naturals_0\rightarrow\naturals_0^d$.
@@
 \begin{equation}
-\abs{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
+\absolute{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
 \end{equation}
-
 However, because the knowledge of the Walsh coefficients $\hf_{\kappa}$ is not assumed, we will estimate them using $\mathcal{P}_m$ instead, and refer to them as $\tf_{m,\kappa}$.
@@
 For $\ell,m \in \mathbb{N}_0$ and $\ell \le m$ we introduce the following notation,
-\begin{gather*}
-S_m(f) =  \sum_{\kappa=\left \lfloor b^{m-1} \right \rfloor}^{b^{m}-1} \abs{\hf_{\kappa}}, \qquad 
-\hS_{\ell,m}(f)  = \sum_{\kappa=\left \lfloor b^{\ell-1} \right \rfloor}^{b^{\ell}-1} \sum_{\lambda=1}^{\infty} \abs{ \hf_{\kappa+\lambda b^{m}}}, \\
-\wcS_m(f)=\hS_{0,m}(f) + \cdots + \hS_{m,m}(f)=
-\sum_{\kappa=b^{m}}^{\infty} \abs{\hf_{\kappa}}, \qquad
-\tS_{\ell,m}(f) = \sum_{\kappa=\left \lfloor b^{\ell-1}\right \rfloor}^{b^{\ell}-1} \abs{\tf_{m,\kappa}}.
-\end{gather*}
-
+\begin{align*}
+S_m(f) &=  \sum_{\kappa=\left \lfloor b^{m-1} \right \rfloor}^{b^{m}-1} \absolute{\hf_{\kappa}}, \ 
+\hS_{\ell,m}(f)  = \sum_{\kappa=\left \lfloor b^{\ell-1} \right \rfloor}^{b^{\ell}-1} \sum_{\lambda=1}^{\infty} \absolute{ \hf_{\kappa+\lambda b^{m}}}, \\
+\wcS_m(f)&=\hS_{0,m}(f) + \cdots + \hS_{m,m}(f)=
+\sum_{\kappa=b^{m}}^{\infty} \absolute{\hf_{\kappa}},\\ 
+\tS_{\ell,m}(f) &= \sum_{\kappa=\left \lfloor b^{\ell-1}\right \rfloor}^{b^{\ell}-1} \absolute{\tf_{m,\kappa}}.
+\end{align*}
 Finally, we define the set of functions $\cc$,
@@
 \begin{equation}
-\abs{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
+\absolute{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
 \le \frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}. \label{errbd}
@@
 where one may increase $m$ until the error bound is small enough.
+\bigskip
 
-Details concerning the algorithm, mapping of the wavenumber space, or meaning and properties of $\cc$, are provided in \cite{HicJim}.
-For the rest of the paper we only consider Sobol' sequences.
-These sequences are digital sequences in based $b=2$.
-Their major interests come from their fast and easy implementation as well as their slow growing size rate.
-Further details concerning these sequences can be found in \cite{Lemieuxbook,Niederreiter92}.
+Details concerning the algorithm, the mapping of the wavenumber space, or the meaning and properties of $\cc$, are provided in \cite{HicJim}.
 
-\subsection{Generalization to Sobol' indices}
+For our problem, only Sobol' sequences have been considered.
+These sequences are digital defined in based $b=2$.
+Their major interests come from their fast and easy implementation as well as their relatively slow growing size rate.
+Further details concerning Sobol' sequences can be found in \cite{Lemieuxbook,Niederreiter}.
+
+\subsection{Extension to Sobol' indices}
+\label{sec:3.2}
 The idea here is to extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To do so, we consider the two integral formulas of the first-order and total effect Sobol' indices:
@@
 In both cases, regular and normalized indices can be approximated by estimating some integrals,
-
 \begin{align*}
 \underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d-1}} \left(f(\vx)-
-f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2} = \frac{I_1}{I_3-(I_4)^2}, \\
-\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2} = \frac{I_2}{I_3-(I_4)^2},
+f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'_{-u}}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
+\underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
+\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\
+\overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
 \end{align*}
 where $\vI=(I_1,I_2,I_3,I_4)$.
-Thus, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$.
-If we estimate $\vI$ by $\widehat{\vI}$ and error bound $\varepsilon_{\vI}$ according to \ref{section.error.algo}, then $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
-\bigskip
+$\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over a vector of integrals $\vI$.
+If we estimate $\vI$ by $\widehat{\vI}$ with the error bound $\varepsilon_{\vI}$ according to \ref{sec:3.1}, then $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
 
-Alternatively to the common estimators $\widehat{\underline{S}_u}=\underline{S}_u(\widehat{\vI})$ and $\widehat{\overline{S}_u}=\overline{S}_u(\widehat{\vI})$, we consider here the following estimators with their respective error bounds:
+Then, alternatively to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the two following estimators with their respective error bounds:
 \begin{gather}
@@
 \end{gather}
-These new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u} \right] ;\] This property is illustrated below in dimension one.
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\textwidth]{Images/scheme_S.eps}
-\end{figure}
+%This property is illustrated in Figure \ref{fig:1} below.
+%\begin{figure*}
+%\centering
+%\includegraphics[width=0.75\textwidth]{scheme_S.eps}
+% figure caption is below the figure
+%\caption{Estimator property.}
+%\label{fig:1}       % Give a unique label
+%\end{figure*} 
+Under the condition that each integrand of $\vI$ are in $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u} \right] .\]
+For the rest of the paper, $\widehat{\underline{S}_u}$ and $\widehat{\overline{S}_u}$ will refer to formula (\ref{formula_undersu}) and (\ref{formula_oversu}).
 
 \section{Recursive estimation procedure}
-\label{section.recursive.procedure}
-
-The recursive estimation procedure we propose combine the error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ presented in the previous section with one of the two estimation strategies of section \ref{estimation.strategies}, namely Saltelli's strategy and the replication procedure.
+\label{sec:4}
+The recursive estimation procedure we propose combine the error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ presented in the previous section with one of the two estimation strategies of section \ref{sec:2.2}, that is Saltelli's strategy and the replication procedure.
 
@@
 \subsection{Recursive procedure algorithm}
+\label{sec:4.1}
 
 Algorithm \ref{recursive.algorithm} summarizes the main steps of our recursive procedure.
-First, one must fix the target precision $\epsilon >0$ for the Sobol' estimates.
-The stopping criterion is initialized with $\zeta=\epsilon+1$.
+First, one must fix the tolerance $\epsilon >0$ for the Sobol' estimates.
 Then, we set $m=m_0$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ accordingly to the multiplicative approach detailed in \cite{crass}.
@@
 Furthermore, they possess the structure of two replicated designs of order $1$ (Definition \ref{rep.designs}).
+The choice of $m_0$ must be large enough to insure that each integrand of $\vI$ (Section \ref{sec:3.2}) is in $\cc$ .
 \bigskip
@@
 
-In both case we test if the respective error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ are lower than the target precision $\epsilon$.
+In both case we test if the respective error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ are lower than the user tolerance $\epsilon$.
+The stopping criterion checks if all Sobol' estimates satisfy the test.
+For Variant $A$ it writes: $ \forall u \in \mathcal{D}, \absolute{\varepsilon_{\underline{S}_u}} \leq \epsilon \text{ and } \absolute{\varepsilon_{\overline{S}_u}} \leq \epsilon$,
+for Variant $B$:
+$ \forall u \in \mathcal{D}, \absolute{\varepsilon_{\underline{S}_u}} \leq \epsilon.$ 
 \bigskip
@@
 \State estimate $\widehat{\underline{S}_u}^{(m)}$ and $\widehat{\ov{$S$}_u}^{(m)}$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}) and Saltelli's strategy
-\State $bool_u \leftarrow \abs{\varepsilon_{\underline{S}_u}} \leq \epsilon \ \& \ \abs{\varepsilon_{\overline{S}_u}} \leq \epsilon$
+\State $bool_u \leftarrow \absolute{\varepsilon_{\underline{S}_u}} \leq \epsilon \ \& \ \absolute{\varepsilon_{\overline{S}_u}} \leq \epsilon$
 \EndIf
@@
 \State estimate $\widehat{\underline{S}_u}^{(m)}$ with formula (\ref{formula_undersu}) and the replication procedure
-\State $bool_u \leftarrow \abs{\varepsilon_{\underline{S}_u}} \leq \epsilon$
+\State $bool_u \leftarrow \absolute{\varepsilon_{\underline{S}_u}} \leq \epsilon$
 \EndIf
@@
 If Variant $A$ is selected, the cost of our algorithm writes:
-\begin{equation*}
-\sum \limits_{u \in \mathcal{D}} 2^{m_u} + 2 \times 2^{m^{\star}}, \qquad m^\star= \max \limits_{u \in \mathcal{D}} \ m_u,
-\end{equation*}
+\[\sum \limits_{u \in \mathcal{D}} 2^{m_u} + 2 \times 2^{m^{\star}}, \qquad m^\star= \max \limits_{u \in \mathcal{D}} \ m_u,\]
 where: 
@@
 \subsection{Improvement}
+\label{sec:4.2}
 
 We focus on the use of a recent estimator to evaluate small first-order Sobol' indices in Variant $A$.
-This estimator is called ``Correlation 2" and was introduced by Owen in \cite{Owen}.
+This estimator was introduced by Owen in \cite{Owen} and is called ``Correlation 2".
 Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices.
@@
 \begin{equation}
-\sum \limits_{j \in \Gamma} 2^{m''_{u_j}} + \sum \limits_{j \in \Gamma} 2^{m'_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{m_{u_j}} + 2 \times 2^{m^\star}, \qquad m'_{u_j}\leq m^{\star}, \ m_{u_j} \leq m^{\star},
+\sum \limits_{j \in \Gamma} 2^{m''_{u_j}} + \sum \limits_{j \in \Gamma} 2^{m'_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{m_{u_j}} + 2 \times 2^{m^\star},
 \label{cost.improvement}
 \end{equation}
-where: \begin{itemize}
-\item[$\bullet$] for $j\in \Gamma$, $2^{m''_{u_j}}$ is the number of evaluations $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate $\underline{S}_{u_j}$,
+where $m'_{u_j}\leq m^{\star}$, $\ m_{u_j} \leq m^{\star}$, and: 
+\begin{itemize}
+\item[$\bullet$] for $j\in \Gamma$, $2^{m''_{u_j}}$ is the number of evaluations \\ $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate $\underline{S}_{u_j}$,
 \item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
@@
 Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to be always satisfied as ``Correlation 2" has been shown 
-to perform the best for small first-order indices.
-
-To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{appli}. 
+to perform the best for small first-order indices. To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{sec:5}. 
 \bigskip
@@
 To overcome this issue, we propose the following alternative for Variant $A$.
-If at the end of the first iteration, the estimate $\widehat{\underline{S}_u}^{(m)}$, $u \in \mathcal{D}$, is smaller than a specified threshold, then at the next iteration estimator (\ref{first.order.est}) is switched for (\ref{correlation2}) and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed for the evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+If at the end of the first iteration, the estimate $\widehat{\underline{S}_u}^{(m)}$, $u \in \mathcal{D}$, is smaller than a specified threshold, then at the next iteration estimator (\ref{first.order.est}) is switched for (\ref{correlation2}) and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to perform the evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
 
 \section{Applications}
-\label{appli}
+\label{sec:5}
 \subsection{Real case model}
-The Brownian motion is widely used in many applications.
+\label{sec:5.1}
+%The Brownian motion is widely used in many applications.
 Thus, the following example might be interesting to understand what Sobol' indices can explain in some of these applications.
 For instance, if we want to estimate the expected value of the maximum of a discretized Brownian motion whose covariance matrix is $\Sigma$, our goal is to estimate
-\begin{align*}
-\mathbb{E} \left[\max(\bvec{B}_t)\right] &= \int_{\mathbb{R}^d} \max(\bvec{B}_t) \frac{{\rm e}^{\bvec{B}_t^T\Sigma^{-1}\bvec{B}_t}}{(2\pi)^{d/2}|\Sigma|^{1/2}}\,d\bvec{B}_t \\
-&= \int_{[0,1]^d} \max(f_{\rm Chol}(\vx)) \,d\vx \\
-&= \int_{[0,1]^d} \max(f_{\rm PCA}(\vx)) \,d\vx.
-\end{align*}
-The last two equalities are obtained through two different subsitutions corresponding to the \textit{Cholesky} construction of the Brownian motion, and the \textit{PCA} construction.
+%\begin{align*}
+%\mathbb{E} \left[\max(\vect{B}_t)\right] &= \int_{\mathbb{R}^d} \max(\vect{B}_t) \frac{{\rm e}^{\vect{B}_t^T\Sigma^{-1}\vect{B}_t}}{(2\pi)^{d/2}|\Sigma|^{1/2}}\,d\vect{B}_t \\
+%&= \int_{[0,1]^d} \max(f_{\rm Chol}(\vx)) \,d\vx \\
+%&= \int_{[0,1]^d} \max(f_{\rm PCA}(\vx)) \,d\vx.
+%\end{align*}
+%The last two equalities are obtained through two different subsitutions corresponding to the \textit{Cholesky} construction of the Brownian motion, and the \textit{PCA} construction.
 For instance, if we take 10 dimensions and $t_i=i/10$, using the Cholesky construction $S_{1} = 24\%$, $S_{2} = 16\%$, $S_{3} = 13\%$, $S_{4} = 10\%$, and $\overline{S}_{1}=24\%$, $\overline{S}_{2}=18\%$, $\overline{S}_{3}=15\%$, $\overline{S}_{4} = 13\%$.
@@
 This shows that the PCA construction will be better to estimate the above expectation using quasi-Monte Carlo methods since it has a lower effective dimensionality.
-
-For those who were curious about the actual value of $\mathbb{E} \left[\max(\bvec{B}_t)\right]$, it is approximately 0.5935.
+%
+%For those who were curious about the actual value of $\mathbb{E} \left[\max(\vect{B}_t)\right]$, it is approximately 0.5935.
 Nevertheless, the Brownian Motion is a continuous time process.
@@
 \subsection{Classical test functions}
+\label{sec:5.2}
 
-%\newpage
-%\section{Annexes}
+\begin{acknowledgements}
+This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-\newline MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).
+\end{acknowledgements}
 
-%\subsection{recursive formulas}
-%\label{recursive.formulas}
+% BibTeX users please use one of
+%\bibliographystyle{spbasic}      % basic style, author-year citations
+%\bibliographystyle{spmpsci}      % mathematics and physical sciences
+%\bibliographystyle{spphys}       % APS-like style for physics
+%\bibliography{}   % name your BibTeX data base
+
+% Non-BibTeX users please use
+\begin{thebibliography}{99}
 %
-%Let $\mathcal{P}_m=\{\vx_i\}_{i=0}^{2^m-1}$ and $\mathcal{P}'_m=\{{\vx'}_i\}_{i=0}^{2^m-1}$ be the two points sets constructed with the recursive scheme (\ref{rec.scheme}).  
+% and use \bibitem to create references. Consult the Instructions
+% for authors for reference list style.
 %
-%\subsection{Recursive formula for $\hat{\mu}$}
-%
-%The quantity $\hat{\mu}$ defined by formula (\ref{mu.est}) can be recursively estimated by:
-%\[\left \lbrace\begin{array}{l}
-%\hat{\mu}^{(0)} = \dfrac{1}{2} \Big{(} f(\vx_0)+f(\vx_{0,u}:{\vx'}_{0,-u}) \Big{)} \\
-%\\
-%\hat{\mu}^{(m+1)} = \dfrac{1}{2} \Big{(} \hat{\mu}^{(m)} + \dfrac{1}{2^{m+1}} \sum \limits_{i=2^{m}}^{2^{m+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}
-%\end{array}\right.\]
-%\begin{proof}
-%By developing $\hat{\mu}^{(m+1)}$:
-%\begin{align*}
-%\hat{\mu}^{(m+1)} &= \dfrac{1}{2} \dfrac{1}{2^{m+1}} \sum \limits_{i=0}^{2^{m+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \\
-%\hat{\mu}^{(m+1)} &= \dfrac{1}{2} \dfrac{1}{2^{m+1}} \Big{(} \sum \limits_{i=0}^{2^{m}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{m}}^{2^{m+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
-%\hat{\mu}^{(m+1)} &= \dfrac{1}{2} \dfrac{1}{2^{m+1}} \Big{(} 2 \times 2^{m}\hat{\mu}^{(m)} + \sum \limits_{i=2^{m}}^{2^{m+1}-1} f(\vx_i) + f(\vx_{i,u}:{\vx'}_{i,-u}) \Big{)}\\
-%\end{align*}
-%\end{proof}
-%
-%
-%\subsection{Recursive formula for $\widehat{\underline{\tau}_u^2}$}
-%
-%The quantity $\widehat{\underline{\tau}_u^2}$ defined by formula (\ref{first.order.est}) can be recursively estimated by:
-%\begin{equation}
-%\left\lbrace \begin{array}{l}
-%\widehat{\underline{\tau}_u^2}^{(0)}= (f(\vx_0)-\hat{\mu}^{(0)})(f(\vx_{0,u}:{\vx'}_{0,-u})-\hat{\mu}^{(0)}) \\
-%\\
-%\widehat{\underline{\tau}_u^2}^{(m+1)} =  \dfrac{1}{2} \widehat{\underline{\tau}_u^2}^{(m)} - \dfrac{1}{2} (\hat{\mu}^{(m)})^2 - (\hat{\mu}^{(m+1)})^2 + \dfrac{1}{2^{m+1}} \sum \limits_{i=2^{m}+1}^{2^{m+1}-1} f(\vx_i) f(\vx_{i,u}:{\vx'}_{i,-u})
-%\end{array}\right.
-%\label{first.order.est.rec}
-%\end{equation}
-%\begin{proof}
-%By developing $\widehat{\underline{\tau}_u^2}^{(m+1)}$:
-%\begin{align*}
-%\widehat{\underline{\tau}_u^2}^{(m+1)} &= \frac{1}{2^{m+1}} \sum \limits_{i=0}^{2^{m+1}-1} (f(\vx_i)-\hat{\mu}^{(m+1)})(f(\vx_{i,u}:{\vx'}_{i,-u})-\hat{\mu}^{(m+1)}) \\
-%\widehat{\underline{\tau}_u^2}^{(m+1)} &= \frac{1}{2^{m+1}} \sum \limits_{i=0}^{2^{m+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(m+1)})^2 \\
-%\widehat{\underline{\tau}_u^2}^{(m+1)} &= \frac{1}{2^{m+1}} \Big{(}\sum \limits_{i=0}^{2^{m}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u}) + \sum \limits_{i=2^{m}}^{2^{m+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})\Big{)} -(\hat{\mu}^{(m+1)})^2 \\
-%\widehat{\underline{\tau}_u^2}^{(m+1)} &= \dfrac{1}{2}\Big{(}\widehat{\underline{\tau}_u^2}^{(m)}-(\hat{\mu}^{(m)})^2\Big{)} + \frac{1}{2^{m+1}} \sum \limits_{i=2^{m}}^{2^{m+1}-1} f(\vx_i)f(\vx_{i,u}:{\vx'}_{i,-u})-(\hat{\mu}^{(m+1)})^2 \\
-%\end{align*}
-%\end{proof}
-%
-%\subsection{Recursive formula for} 
-%%$\widehat{\ov{$\tau$}_u^2}$}
-%
-%The quantity $\widehat{\underline{\tau}_u^2}$ defined by formula (\ref{total.effect.est}) can be recursively estimated by:
-%\begin{equation}
-%\left\lbrace \begin{array}{l}
-%\widehat{\ov{$\tau$}_u^2}^{(0)}= \dfrac{1}{2} \Big{(} f(\vx_0)-(f({\vx'}_{0,u}:\vx_{0,-u}) \Big{)}^2 \\
-%\\
-%\widehat{\ov{$\tau$}_u^2}^{(m+1)} = \dfrac{1}{2} \widehat{\ov{$\tau$}_u^2}^{(m)} + \dfrac{1}{2^{m+1}} \sum \limits_{i=2^{m}+1}^{2^{m+1}-1} \Big{(}f(\vx_i)- f({\vx'}_{i,u}:\vx_{i,-u})\Big{)}^2 
-%\end{array}\right.
-%\label{total.effect.est.rec}
-%\end{equation}
-%\begin{proof}
-%Straightforward by developing $\widehat{\ov{$\tau$}_u^2}^{(m+1)}$.
-%\end{proof}
-%
-%\subsection{Proof proposition \ref{right.multi}}
-%\label{proof.prop}
-%
+\bibitem{HicJim}
+Hickernell, F.J, Jim\'enez Rugama, L.A.: Reliable Adaptative Cubature Using Digital Sequences: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 367-383 (2016)
+\bibitem{Hoeffding}
+Hoeffding, W.F.: A class of statistics with asymptotically normal distribution, Ann. Math. Stat. \textbf{19}(3), 293-325 (1948)
+\bibitem{Lemieuxbook}
+Lemieux,C.: Monte Carlo and Quasi-Monte Carlo Sampling, Springer, New-York (2009)
+\bibitem{Mara}
+Mara, T.A., Rakoto Joseph, 0.: Comparison of some efficient methods to evaluate the main effect of computer model factors, J. Statist. Comput. Simulation \textbf{78}(2), 167-178 (2008)
+\bibitem{McKay}
+McKay, M.D.: Evaluating prediction uncertainty, Los Alamos National Laboratory Report NUREG/CR- 6311, LA-12915-MS. (1995)
+\bibitem{Niederreiter} 
+Niederreiter, H.: Random Number Generation and Quasi-Monte Carlo Methods: CBMS-NSF Regional Conference Series in Applied Math., vol. 63, SIAM, Philadelphia (1992)
+\bibitem{Owen}
+Owen, A.B.: Better estimation of small Sobol' sensitivity indices, ACM Trans. Model. Comput. Simul. \textbf{23}(2), :11 (2013)
+\bibitem{Sobol'}
+Sobol', I.M.: Sensitivity indices for nonlinear mathematical models, Mathematical Modeling and Computational Experiment \textbf{1}, 407-414 (1993)
+\bibitem{Tissot}
+Tissot, J.Y., Prieur, C.: A randomized Orthogonal Array-based procedure for the estimation of first- and second-order Sobol' indices, J. Statist. Comput. Simulation \textbf{85}(7), 1358-1381 (2014)
+
+\end{thebibliography}
 \end{document}

### 2016-08-22 article/template.tex
global changes L

@@
 \begin{abstract}
-Insert your abstract here. Include keywords, PACS and mathematical
+Insert your abstract here. Include keywords,\\ PACS and mathematical
 subject classification numbers as needed.
@@
 
-\begin{itemize}
-\item[$\bullet$] introduction sensitivity analysis + estimation methods
-\item[$\bullet$] importance of sampling $\rightarrow$ sobol' sequences
-\item[$\bullet$] problem: when to stop? $\rightarrow$ reliable error estimation 
-\end{itemize}
+Let $f$ represents a deterministic numerical model on $[0,1)^d$, $d \geq 1$.
+Sensitivity measures known as Sobol' indices are used to assess which inputs of $f$ are influential on the output.
+These indices are scalar between $0$ and $1$ whose values are interpreted as follows: the closer to $1$ the more influential the index.
+Among all Sobol' indices one can distinguish first-order and total effect indices.
+The former measure the effect of an input, the latter measure the effect of an input and its interactions.
+
+When dealing with complex numerical models, analytical expressions of Sobol' indices are often inaccessible.
+In such cases, one must rely on an estimation of these indices.
+The original estimation procedure is due to Sobol' \cite{Sobol'}.
+Later on, Saltelli \cite{Saltelli} proposed strategies to estimate sets of Sobol' indices in one go through the use of a combinatorial formalism.
+While elegant, these strategies require a large number of model evaluations.
+A cost efficient alternative was introduced in \cite{Mara} to estimate first-order indices.
+This alternative called replication procedure has recently been further studied  in \cite{Tissot} and generalized to the estimation of closed second-order indices.
+
+A practical problem concerning the use of these methods is how large to chose the number of model evaluations to ensure that Sobol' estimates are accurate enough.
+This paper addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences.
+The error bound is constructed based on the discrete Walsh decomposition of the Sobol' indices integrals.
+We propose a sequential estimation procedure of Sobol' indices using the error bound as stopping criterion.
+The procedure operates under the assumption that all integrands satisfy a cone condition (see \cite{HicJim}).
+
+The next section introduces Sobol' indices and reviews both Saltelli's strategy to estimate first-order and total effect Sobol' indices and the replication procedure.
+Our main contribution is detailed in  Section \ref{sec:3}.
+We first review the construction of the error bound for the estimation of an integral then generalize it for Sobol' indices.
+Section \ref{sec:4} is devoted to our sequential estimation procedure in the form of an algorithm.
+It combines the error bound of Section \ref{sec:3} and one of the two estimation procedure of Section \ref{sec:2}.
+We also discuss a potential improvement to estimate small first-order indices.
+Illustrations of our procedure are presented in Section \ref{sec:5}.
 
@@
 %We adopt the same notations introduced by Owen in \cite{Owen}. 
-Denote by $f$ a numerical model, by $\vx=(x_1,\dots,x_d)$ its vector of inputs and set $\mathcal{D}=\{1,\dots,d\}$.
-%The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
+Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of $f$ and $\mathcal{D}=\{1,\dots,d\}$. %The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
 Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality.
@@
 
-Let $f$ be the symbol representing the numerical model studied. We assume $f \in \mathcal{L}^2[0,1)^d$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
+We assume $f \in \mathcal{L}^2[0,1)^d$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
 The uncertainty on $\vx$ is modeled by random variables such that $\vx \iid \mathcal{U}[0,1)^d$. Recall the Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$:
@@
 \[ \sigma^2 = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1)^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
-From the variance decomposition of $f$, on can express the following two quantities:
+From this decomposition, one can express the following two quantities:
 \[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
@@
 $\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$ that is the effect of all interactions between variables in $\vx_u$.
-$\ov{$\tau$}_u^2$ quantifies the main effect of $\vx_u$ plus all interactions between variables in $\vx_u$ and variables in $\vx_{-u}$.
+$\ov{$\tau$}_u^2$ quantifies the main effect of $\vx_u$ plus the effect of all interactions between variables in $\vx_u$ and variables in $\vx_{-u}$.
 
@@
 \end{align}
-The variance of $f$ is evaluated by:
+while the variance of $f$ is evaluated by:
 \begin{equation}
@@
 \label{first.order.est}
-\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_i)-f(\vx_{i,u}:{\vx'}_{i,-u})\right)f(\vx'_i),\\
+\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_i)-f(\vx_{i,u}:{\vx'}_{i,-u})\right)f(\vx'_i),\\
 \label{total.effect.est}
-\widehat{\ov{$\tau$}_u^2} & = \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \ u \in \mathcal{D},
+\widehat{\ov{$\tau$}_u^2} &= \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
 \end{align}
@@
 The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ accordingly to $u$.
-While elegant, this approach still requires a number of model evaluations that grows linearly with respect to the input space dimension.
+While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input space dimension.
 
@@
 \begin{align*}
-\pi_u(f({\vx'}_i))&=f({\vx'}_{\pi_u(i)}), \\
-\pi_u(f({\vx'}_i))&=f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u}), \\
-\pi_u(f({\vx'}_i))&=f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).
+\pi_u(f({\vx'}_i))&= f({\vx'}_{\pi_u(i)}), \\
+&= f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u}), \\
+&= f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).
 \end{align*}
@@
 \label{sec:2.3}
-The aim of this paper is to propose a recursive procedure to estimate first-order and total effect Sobol' indices.
-The choice of the stopping criterion is the key point of this paper.
-%A recursive version of the replication procedure has recently been proposed by Gilquin et al.
-(2016) (preprint available at \url{https://hal.inria.fr/hal-01291769}).
-In this recursive version, the stopping criterion is an absolute difference between estimates computed on consecutive steps.
-Generally, in most recursive approaches that estimate Sobol' indices, the stopping criterion is a quantity of interest build directly upon the estimates.
+The aim of this paper is to propose a sequential procedure to estimate first-order and total effect Sobol' indices.
+Generally, in most sequential procedures that estimate Sobol' indices, the stopping criterion is a quantity of interest built directly upon the estimates.
 Such stopping criteria often involve hyper-parameters hard to tweak but above all fail to guarantee any error bound on the estimates.
-\bigskip
 
-Our recursive procedure stands apart from others approaches with the construction of a robust stopping criterion.
-This criterion is an error bound based on the discrete Walsh decomposition of integrals (\ref{first.order}) and (\ref{total.effect}).
+Our sequential procedure stands apart from others with the construction of a robust stopping criterion.
+This criterion is an error bound based on the discrete Walsh decomposition of integrals (\ref{first.order}), (\ref{total.effect}) and (\ref{eq.sigma.mu}).
 This decomposition use the close set property of digital sequences.
-As such, our recursive procedure relies on an iterative construction of Sobol' sequences.
-This construction is performed accordingly to the multiplicative approach presented in (Gilquin et al., 2016, preprint available at \url{https://hal.inria.fr/hal-01349444}).
+As such, our procedure relies on an iterative construction of Sobol' sequences.
+This construction is performed accordingly to the multiplicative approach presented in \cite{GJAHMP}.
 
-The construction of the error bound is the subject of the next section. Our recursive estimation procedure is detailed in section \ref{sec:4}.
+The construction of the error bound is the subject of the next section. Our sequential procedure is detailed in section \ref{sec:4}.
 
@@
 \label{sec:3} 
-We start by reviewing the construction of an error bound for the estimation of a multidimensional integral proposed in \cite{HicJim}.
-This construction is based on the Walsh decomposition of the integrand and relies on quasi-Monte Carlo points sets.
-Then, we present an extension of this error bound for the case of Sobol' indices.
+We start by reviewing the construction of the error bound proposed in \cite{HicJim} for the estimation of a $d$-dimensional integral.
+Then, we present an extension of this error bound for Sobol' indices.
 This extension exploits the integral formula of a Sobol' index.
 
-\subsection{Reliable integral estimation using quasi-Monte Carlo}
+\subsection{Reliable integral estimation using digital sequences}
 \label{sec:3.1}
@@
 1,\quad \vk\in\mathcal{P}_m^\perp, \\
-0,\quad \vk\notin\mathcal{P}_m^\perp
+0,\quad \vk\notin\mathcal{P}_m^\perp.
 \end{cases}
@@
 f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
+and:
+\[ I = \int_{\cube} f(\vx)\,d\vx,\]
 for any $f\in L^2([0,1]^d)$ and property \eqref{basis_integ_prop},
 \begin{align*}
-\absolute{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
-\absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)} \\
-&= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}}
+\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
+\absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}, \\
+&= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}}.
 \end{align*}
 Based on the size of $\absolute{\hf_{\vk}}$ and the structure of the dual nets \eqref{dual_net_structure}, in \cite[Sec.
-4.1]{HicJim} we proposed an ordering of the wavenumbers $\vk(\cdot):\naturals_0\rightarrow\naturals_0^d$.
+4.1]{HicJim} we proposed an ordering of the wave-numbers $\vk(\cdot):\naturals_0\rightarrow\naturals_0^d$.
 To simplify notation, $\hf_{\kappa}:=\hf_{\vk(\kappa)}$.
@@
 \begin{equation}
-\absolute{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
+\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
 \end{equation}
@@
 \begin{equation}
-\absolute{\int_{\cube} f(\vx)\,d\vx - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
-\le \frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}. \label{errbd}
+\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
+\le \frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)} = \epsilon_I, \label{errbd}
 \end{equation}
-where one may increase $m$ until the error bound is small enough.
-\bigskip
+where one may increase $m$ until the error bound $\epsilon_I$ is small enough.
 
@@
 
-For our problem, only Sobol' sequences have been considered.
-These sequences are digital defined in based $b=2$.
-Their major interests come from their fast and easy implementation as well as their relatively slow growing size rate.
+For our problem, only Sobol' sequences \cite{Sobol'seq} have been considered.
+These sequences are digital defined in base $b=2$.
+Their major interest comes from their fast and easy implementation as well as their relatively slow growing size rate.
 Further details concerning Sobol' sequences can be found in \cite{Lemieuxbook,Niederreiter}.
@@
 where $\vI=(I_1,I_2,I_3,I_4)$.
-$\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over a vector of integrals $\vI$.
-If we estimate $\vI$ by $\widehat{\vI}$ with the error bound $\varepsilon_{\vI}$ according to \ref{sec:3.1}, then $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
+$\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector of integrals $\vI$.
+If we estimate $\vI$ by $\widehat{\vI}$ with the vector of error bounds $\varepsilon_{\vI}=(\epsilon_{I_1},\epsilon_{I_2},\epsilon_{I_3},\epsilon_{I_4})$ according to \ref{sec:3.1}, we obtain $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
 
-Then, alternatively to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the two following estimators with their respective error bounds:
+Then, alternatively to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the two following estimators with the respective error bounds:
 \begin{gather}
 \begin{aligned}
-\widehat{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right), \\
-\varepsilon_{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right),
+\widehat{\underline{S}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
+\varepsilon_{\underline{S}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
 \end{aligned}
@@
 \begin{aligned}
-\widehat{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right), \\
-\varepsilon_{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right).
+\widehat{\overline{S}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
+\varepsilon_{\overline{S}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
 \end{aligned}
@@
 \end{gather}
-%This property is illustrated in Figure \ref{fig:1} below.
+Maximizing $\underline{S}_u(\vI)$ (resp.
+$\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp.
+$I_2$) and minimizing the denominator $I_3-I_4^2$.
+At the opposite, minimizing $\underline{S}_u(\vI)$ (resp.
+$\overline{S}_u(\vI)$) is done through minimizing the numerator $I_1$ (resp.
+$I_2$) and maximizing the denominator $I_3-I_4^2$.
+%As an example, Figure \ref{fig:1} below illustrate the maximization process for $\vI$ unidimensional.
 %\begin{figure*}
@@
 %\end{figure*}
+
 Under the condition that each integrand of $\vI$ are in $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u} \right] .\]
-For the rest of the paper, $\widehat{\underline{S}_u}$ and $\widehat{\overline{S}_u}$ will refer to formula (\ref{formula_undersu}) and (\ref{formula_oversu}).
+For the rest of the paper, we will consider $\widehat{\underline{S}_u}$ and $\widehat{\overline{S}_u}$   as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).
 
-\section{Recursive estimation procedure}
+\section{Sequential estimation procedure}
 \label{sec:4}
-The recursive estimation procedure we propose combine the error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ presented in the previous section with one of the two estimation strategies of section \ref{sec:2.2}, that is Saltelli's strategy and the replication procedure.
+The sequential estimation procedure we propose combine the error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ presented in the previous section with one of the two estimation strategies of section \ref{sec:2.2}: Saltelli's strategy and the replication procedure.
 
-We start be detailing our recursive procedure in the form of an algorithm.
-Then, we discuss a possible improvement by considering a new estimator recently introduced in \cite{Owen} for the first-order indices.
+We start be detailing our procedure in the form of an algorithm.
+Then, we discuss a possible improvement by considering a new estimator recently introduced in \cite{Owen} for the estimation of first-order indices.
 
-\subsection{Recursive procedure algorithm}
+\subsection{Sequential algorithm and its cost}
 \label{sec:4.1}
 
-Algorithm \ref{recursive.algorithm} summarizes the main steps of our recursive procedure.
+Algorithm \ref{recursive.algorithm} summarizes the main steps of our sequential procedure.
 First, one must fix the tolerance $\epsilon >0$ for the Sobol' estimates.
-Then, we set $m=m_0$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ accordingly to the multiplicative approach detailed in \cite{crass}.
+Then, we set $m=m_0$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ accordingly to the multiplicative approach detailed in \cite{GJAHMP}.
+Step $5$ corresponds to the recursive scheme of this approach.
+The choice of $m_0$ must be large enough to insure that each integrand of $\vI$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).
+
 With this construction, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two Sobol' sequences.
 Furthermore, they possess the structure of two replicated designs of order $1$ (Definition \ref{rep.designs}).
-The choice of $m_0$ must be large enough to insure that each integrand of $\vI$ (Section \ref{sec:3.2}) is in $\cc$ .
 \bigskip
@@
 
-In both case we test if the respective error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ are lower than the user tolerance $\epsilon$.
-The stopping criterion checks if all Sobol' estimates satisfy the test.
-For Variant $A$ it writes: $ \forall u \in \mathcal{D}, \absolute{\varepsilon_{\underline{S}_u}} \leq \epsilon \text{ and } \absolute{\varepsilon_{\overline{S}_u}} \leq \epsilon$,
-for Variant $B$:
-$ \forall u \in \mathcal{D}, \absolute{\varepsilon_{\underline{S}_u}} \leq \epsilon.$ 
-\bigskip
+In both case we test if the respective error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ are lower than the tolerance $\epsilon$.
+For Variant $A$ the stopping criterion writes: $ \forall u \in \mathcal{D}, \varepsilon_{\underline{S}_u} \leq \epsilon \text{ and } \varepsilon_{\overline{S}_u} \leq \epsilon$,
+for Variant $B$ it writes:
+$ \forall u \in \mathcal{D}, \varepsilon_{\underline{S}_u} \leq \epsilon.$
 
-If the stopping criterion is satisfied, that is if $bool$ is true, the algorithm stops and Sobol' estimates are returned. Otherwise, $m$ is incremented by one to perform a new estimation.
-
+If the stopping criterion is satisfied, the algorithm stops and Sobol' estimates are returned. Otherwise, $m$ is incremented by one to perform a new estimation. 
 \begin{algorithm}[!ht]
-\caption{Recursive estimation of Sobol' indices}
+\caption{Sequential estimation of Sobol' indices}
 \begin{algorithmic}[1]
@@
 \If {Variant $A$}
-\State estimate $\widehat{\underline{S}_u}^{(m)}$ and $\widehat{\ov{$S$}_u}^{(m)}$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}) and Saltelli's strategy
-\State $bool_u \leftarrow \absolute{\varepsilon_{\underline{S}_u}} \leq \epsilon \ \& \ \absolute{\varepsilon_{\overline{S}_u}} \leq \epsilon$
+\State estimate $\widehat{\underline{S}_u}$ and $\widehat{\ov{$S$}_u}$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}) and Saltelli's strategy
+\State $bool_u \leftarrow \varepsilon_{\underline{S}_u} \leq \epsilon \ \& \ \varepsilon_{\overline{S}_u} \leq \epsilon$
 \EndIf
 \If {Variant $B$}
-\State estimate $\widehat{\underline{S}_u}^{(m)}$ with formula (\ref{formula_undersu}) and the replication procedure
-\State $bool_u \leftarrow \absolute{\varepsilon_{\underline{S}_u}} \leq \epsilon$
+\State estimate $\widehat{\underline{S}_u}$ with formula (\ref{formula_undersu}) and the replication procedure
+\State $bool_u \leftarrow \varepsilon_{\underline{S}_u} \leq \epsilon$
 \EndIf
@@
 \end{algorithm}
+\bigskip
 
@@
 \end{itemize}
-This cost can be seen as a generalisation of the one specified in Theorem \ref{saltelli.theorem}.
-If all $m_u$ are equal, the cost of Variant $A$ becomes $2^{m^\star}(d+2)$ and we recover the cost in Theorem \ref{saltelli.theorem} with $n=2^{m^\star}$.
+If all $m_u$ are equal, the cost of Variant $A$ becomes $2^{m^\star}(d+2)$ and we recover the cost specified in Theorem \ref{saltelli.theorem} with $n=2^{m^\star}$.
 
-If Variant $B$ is selected the cost of our algorithm equals $2 \times 2^{m^{\star}}$. This cost corresponds to the one specified in the replication procedure with $n=2^{m^{\star}}$.
+If Variant $B$ is selected the cost of our algorithm equals $2 \times 2^{m^{\star}}$. This cost corresponds to the one of the replication procedure with $n=2^{m^{\star}}$.
 
@@
 
-We focus on the use of a recent estimator to evaluate small first-order Sobol' indices in Variant $A$.
-This estimator was introduced by Owen in \cite{Owen} and is called ``Correlation 2".
+We focus on the use of a new estimator to evaluate small first-order Sobol' indices in Variant $A$.
+This estimator has recently been introduced by Owen in \cite{Owen} and is called ``Correlation 2".
 Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices.
@@
 Its formula writes as follows:
-\begin{equation}
+\begin{equation*}
 \widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)),
-\label{correlation2}
-\end{equation}
+\end{equation*}
 where $(\vx_i,{\vx'}_i, \vz_i) \iid [0,1)^{3d}$. It uses an extra set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.
@@
 We discuss below the potential improvement brought by the use of ``Correlation 2" in Variant $A$.
-The idea is to replace the current estimator (\ref{first.order.est}) by (\ref{correlation2}) for each small first-order index.
+The idea is to replace the current estimator (\ref{first.order.est}) by  ``Correlation 2" for each small first-order index.
 
 Assume that the number of small first-order indices is known and equals $\gamma$.
-We denote by $u_1,\dots,u_{\gamma}$ the indexes of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$.
+We denote by $u_1,\dots,u_{\gamma}$ the indices of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$.
 The cost of Variant $A$ including ``Correlation 2" writes:
 \begin{equation}
-\sum \limits_{j \in \Gamma} 2^{m''_{u_j}} + \sum \limits_{j \in \Gamma} 2^{m'_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{m_{u_j}} + 2 \times 2^{m^\star},
+\sum \limits_{j \in \Gamma} 2^{m''_{u_j}} + \sum \limits_{j \in \Gamma} 2^{m'_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^\star},
 \label{cost.improvement}
@@
 \item[$\bullet$] for $j\in \Gamma$, $2^{m''_{u_j}}$ is the number of evaluations \\ $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate $\underline{S}_{u_j}$,
-\item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
-\item[$\bullet$] likewise, for $j\in \mathcal{D}/\Gamma$, $ 2^{m_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
+\item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations \\ $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
+\item[$\bullet$] likewise, for $j\in \mathcal{D}\setminus{\Gamma}$, $ 2^{m_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
 \item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
@@
 \begin{equation}
-\sum \limits_{j \in \Gamma} 2^{m_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{m_{u_j}} + 2 \times 2^{m^{\star}}, \qquad m_{u_j} \leq m^{\star}.
+\sum \limits_{j \in \Gamma} 2^{m_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^{\star}}, \qquad m_{u_j} \leq m^{\star}.
 \label{cost.non.improvement}
@@
 to perform the best for small first-order indices. To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{sec:5}.
-\bigskip
 
@@
 To overcome this issue, we propose the following alternative for Variant $A$.
-If at the end of the first iteration, the estimate $\widehat{\underline{S}_u}^{(m)}$, $u \in \mathcal{D}$, is smaller than a specified threshold, then at the next iteration estimator (\ref{first.order.est}) is switched for (\ref{correlation2}) and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to perform the evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+If at the end of the first iteration, the estimate $\widehat{\underline{S}_u}$, $u \in \mathcal{D}$, is smaller than a specified threshold, then at the next iteration estimator (\ref{first.order.est}) is switched for ``Correlation 2" and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
 
@@
 This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-\newline MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).
+The authors thank Stephen Joe, Frances Y.
+Kuo and Art B.
+Owen for helpful answers and suggestions.
 \end{acknowledgements}
@@
 %
+\bibitem{GJAHMP}
+Gilquin, L., Jim\'enez Rugama, L.A., Arnaud, E., Hickernell, F.J., Monod, H., Prieur, C.: Iterative construction of replicated designs based on Sobol' sequences, preprint available at \url{https://hal.inria.fr/hal-01349444} (2016)
 \bibitem{HicJim}
-Hickernell, F.J, Jim\'enez Rugama, L.A.: Reliable Adaptative Cubature Using Digital Sequences: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 367-383 (2016)
+Hickernell, F.J., Jim\'enez Rugama, L.A.: Reliable Adaptative Cubature Using Digital Sequences: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 367-383 (2016)
 \bibitem{Hoeffding}
 Hoeffding, W.F.: A class of statistics with asymptotically normal distribution, Ann. Math. Stat. \textbf{19}(3), 293-325 (1948)
+%\bibitem{Janon}
+%Janon, A., Klein, T., Lagnoux A., Nodet, M., Prieur C.: Asymptotic normality and efficiency of two {S}obol' index estimators, ESAIM Probab. Stat. \textbf{18}, 342-364 (2014)
 \bibitem{Lemieuxbook}
@@
 Owen, A.B.: Better estimation of small Sobol' sensitivity indices, ACM Trans. Model. Comput. Simul. \textbf{23}(2), :11 (2013)
+\bibitem{Saltelli}
+Sobol', I.M.: On the distribution of points in a cube and the approximate evaluation of integrals, USSR Comput. Math. Math. Phys. \textbf{7}(4), 86-112 (1967)
+\bibitem{Sobol'seq}
+Saltelli, A.: Making best use of models evaluations to compute sensitivity indices, Comput. Phys. Commun. \textbf{145}(2), 280-297 (2002)
 \bibitem{Sobol'}

### 2016-08-29 article/template.tex
Changes in templatex.tex

@@
 \newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
-\newcommand\iid{\stackrel{iid}{\sim}}
+\newcommand\iid{\stackrel{{\rm iid}}{\sim}}
 
@@
 
-Let $f$ represents a deterministic numerical model on $[0,1)^d$, $d \geq 1$.
-Sensitivity measures known as Sobol' indices are used to assess which inputs of $f$ are influential on the output.
-These indices are scalar between $0$ and $1$ whose values are interpreted as follows: the closer to $1$ the more influential the index.
-Among all Sobol' indices one can distinguish first-order and total effect indices.
-The former measure the effect of an input, the latter measure the effect of an input and its interactions.
+Let $f$ represent a deterministic numerical model in $[0,1)^d$, $d \geq 1$.
+Sensitivity measures, also known as Sobol' indices, are used to assess which inputs of $f$ are influential for the output.
+The normalized indices are scalars between $0$ and $1$ whose values are interpreted as follows: the closer to $1$ the more influential the index.
+Alternatively, they can be interpreted as the percentage of the variance explained by the inputs.
+Among all Sobol' indices one can distinguish \emph{first-order} and \emph{total effect} indices.
+The first measures the effect of a single input, while the latter measures this same effect and includes all its interactions with other inputs.
 
@@
 The original estimation procedure is due to Sobol' \cite{Sobol'}.
-Later on, Saltelli \cite{Saltelli} proposed strategies to estimate sets of Sobol' indices in one go through the use of a combinatorial formalism.
-While elegant, these strategies require a large number of model evaluations.
-A cost efficient alternative was introduced in \cite{Mara} to estimate first-order indices.
-This alternative called replication procedure has recently been further studied  in \cite{Tissot} and generalized to the estimation of closed second-order indices.
+However, this procedure requires several model evaluations which are usually expensive.
+Later on, Saltelli \cite{Saltelli} proposed strategies to estimate sets of Sobol' indices at once through the use of a combinatorial formalisms.
+While elegant, these strategies still require a large number of model evaluations.
+A cost efficient alternative to estimate first-order indices was introduced in \cite{Mara}.
+This alternative, called replication procedure, has recently been further studied  in \cite{Tissot} and generalized to the estimation of closed second-order indices.
 
-A practical problem concerning the use of these methods is how large to chose the number of model evaluations to ensure that Sobol' estimates are accurate enough.
+A practical problem concerning the use of these methods is how to quantify the number of model evaluations to ensure that Sobol' estimates are accurate enough.
 This paper addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences.
-The error bound is constructed based on the discrete Walsh decomposition of the Sobol' indices integrals.
+The error bound is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition.
 We propose a sequential estimation procedure of Sobol' indices using the error bound as stopping criterion.
-The procedure operates under the assumption that all integrands satisfy a cone condition (see \cite{HicJim}).
+The procedure operates under the assumption that all integrands lie inside a particular cone of functions (see \cite{HicJim}).
 
-The next section introduces Sobol' indices and reviews both Saltelli's strategy to estimate first-order and total effect Sobol' indices and the replication procedure.
+Firstly, section \ref{sec:2} introduces Sobol' indices and reviews both Saltelli's strategy to estimate first-order and total effect Sobol' indices, and the replication procedure.
 Our main contribution is detailed in  Section \ref{sec:3}.
-We first review the construction of the error bound for the estimation of an integral then generalize it for Sobol' indices.
-Section \ref{sec:4} is devoted to our sequential estimation procedure in the form of an algorithm.
-It combines the error bound of Section \ref{sec:3} and one of the two estimation procedure of Section \ref{sec:2}.
-We also discuss a potential improvement to estimate small first-order indices.
-Illustrations of our procedure are presented in Section \ref{sec:5}.
+There we review the construction of the error bound for the estimation of integrals based on digital nets, and then generalize it for Sobol' indices.
+Section \ref{sec:4} is devoted to analyze the cost in terms of model evaluations of our sequential estimation algorithm.
+It combines the error bound in Section \ref{sec:3} and one of the two estimation procedures of Section \ref{sec:2}.
+We also discuss a potential improvement to estimate small first-order indices according to \cite{Owen}.
+Finally, examples and illustrations of our procedure are presented in Section \ref{sec:5}.
 
@@
 %We adopt the same notations introduced by Owen in \cite{Owen}. 
-Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of $f$ and $\mathcal{D}=\{1,\dots,d\}$. %The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
+Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of $f$ and $\mathcal{D}=\{1,\dots,d\}$ the set of dimensions indexes.
+%The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
 Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality.
-$\vx_u$ represents a point in $[0,1)^u$ with components $x_j, j \in u$.
+$\vx_u$ represents a point in $[0,1)^{|u|}$ with components $x_j, j \in u$.
 Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j={x'}_j$ if $j \notin u$.
 
-We assume $f \in \mathcal{L}^2[0,1)^d$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
-The uncertainty on $\vx$ is modeled by random variables such that $\vx \iid \mathcal{U}[0,1)^d$. Recall the Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$:
+We assume that $f \in \mathcal{L}^2\left([0,1]^d\right)$ and denote by $\mu$ and $\sigma^2$ the mean $\int_{\cube}f(\vx)d{\vx}$ and variance $\int_{\cube}(f(\vx)-\mu)^2d{\vx}$ of $f$.
+The uncertainty on $\vx$ is modeled as a uniform random variable, namely $\vx \iid \mathcal{U}\left([0,1)^d\right)$. The Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$ is:
 \begin{equation}
@@
 \[f_u(\vx)= \int_{[0,1)^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).\]
-Due to orthogonality, taking the variance of each side in equation (\ref{anova}) leads to the variance decomposition of $f$:
+Due to orthogonality, applying the variance to equation \eqref{anova} leads to the variance decomposition of $f$:
 \[ \sigma^2 = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1)^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
@@
 
-For $u \subsetneq \mathcal{D}$, the two quantities $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ both measure the importance of the variables in $\vx_u$.
-$\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$ that is the effect of all interactions between variables in $\vx_u$.
+For $u \subsetneq \mathcal{D}$, the two quantities $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ measure the importance of variables in $\vx_u$.
+$\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$, that is the effect of all interactions between variables in $\vx_u$.
 $\ov{$\tau$}_u^2$ quantifies the main effect of $\vx_u$ plus the effect of all interactions between variables in $\vx_u$ and variables in $\vx_{-u}$.
@@
 $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ satisfy the following relations: $ 0 \leq  \underline{\tau}_u^2 \leq \ov{$\tau$}_u^2$ and $\underline{\tau}_u^2 = \sigma^2 - \ov{$\tau$}_{-u}^2$.
-These two measure are commonly found in the litterature in their normalized form: $\underline{S}_u = \underline{\tau}_u^2 / \sigma^2$ is the closed $|u|$-order Sobol' index for the set $u$, while $\ov{$S$}_u = \ov{$\tau$}_u^2 / \sigma^2$ is the total effect Sobol' index.
+These two measures are commonly found in the literature in their normalized form: $\underline{S}_u = \underline{\tau}_u^2 / \sigma^2$ is the closed $|u|$-order Sobol' index for inputs $u$, while $\ov{$S$}_u = \ov{$\tau$}_u^2 / \sigma^2$ is the total effect Sobol' index of order $|u|$.
 \bigskip
 
-The problem of interest here is the evaluation of first-order and total effect Sobol' indices.
-The computation of these indices is performed based on the following integral formulas for their numerators:
+The problem of interest is the evaluation of first-order and total effect Sobol' indices of order 1.
+The computation of the normalized indices is performed based on the following integral formulas for their numerators:
 \begin{align}
@@
 \end{align}
-while the variance of $f$ is evaluated by:
+while the variance of $f$ is evaluated as:
 \begin{equation}
@@
 \end{equation} 
-Most of the time, the complexity of $f$ causes the computation of integrals (\ref{first.order}), (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable.
-In such case, one needs to rely on an estimation of these quantities.
+Usually the complexity of $f$ causes the computation of integrals \eqref{first.order}, (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable.
+In such cases, one can estimate these quantities instead.
 
@@
 In this section we review two Monte Carlo procedures for the estimation of Sobol' indices.
-We define by design a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ obtained by sampling each variable $x_j$ $n$ times.
-Each row of the design is a point $\vx_i$ in $[0,1)^d$.
-Each column of the design refers to a variable $x_j$.
+A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times.
+Each row of the design is a point $\vx_i$ in $[0,1)^d$ and each column of the design refers to a variable $x_j$.
 Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid [0,1)^{2d}$.
@@
 \end{align}
-using for $\sigma^2$ the classic estimator:
+using for $\sigma^2$:
 \begin{equation}
@@
 \end{equation}
-The Sobol' indices estimators are defined by:
+Then, the normalized Sobol' indices estimators are:
 \begin{equation}
@@
 The estimation of a single pair ($\widehat{\underline{S}_u}$, $\widehat{\overline{S}_u}$) requires $3n$ evaluations of the model $f$.
-Using a combinatorial formalism, in \cite{Saltelli} Saltelli proposes the following estimation strategy:
+Thus, for first order indices, one would need $3nd$ model evaluations.
+Using a combinatorial formalism, in \cite{Saltelli}, Saltelli proposes the following estimation strategy:
 \begin{theorem}
 \label{saltelli.theorem}
-The $d+2$ designs $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allows to estimate all first-order and all total effect Sobol' indices at a cost of $n(d+2)$ evaluations of the model.
+The $d+2$ designs $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allows to estimate all first-order and total effect Sobol' indices of order 1 at a cost of $n(d+2)$ evaluations of the model.
 \end{theorem}
 The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ accordingly to $u$.
+Indeed, there is no need of reevaluating $f({\vx}_i$ and $f({\vx'}_i$ for each $u$.
 While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input space dimension.
@@
 This alternative relies on the construction of two replicated designs.
-The notion of replicated designs was first introduced by McKay through its introduction of replicated Latin Hypercubes \cite{McKay}.
-The definition we give here introduce the structure in a wider context:
+The notion of replicated designs was first introduced by McKay through its replicated Latin Hypercubes in \cite{McKay}.
+The definition we provide below generalizes the notion of replicated designs:
 \begin{definition}
@@
 We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if $\forall \ u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1)^a$.
-We note $\pi_u$ the permutation arranging the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
+We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
 \end{definition}
@@
 Denote by $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$.
-Consider $u \in \mathcal{D}$, from Definition \ref{rep.designs} there exists a permutation $\pi_u$ such that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$.
-Then, remark that $\forall i \in \{0,\dots,n-1\}$:
+From Definition \ref{rep.designs}, ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$.
+Then, for all $i \in \{0,\dots,n-1\}$:
 \begin{align*}
@@
 Our sequential procedure stands apart from others with the construction of a robust stopping criterion.
-This criterion is an error bound based on the discrete Walsh decomposition of integrals (\ref{first.order}), (\ref{total.effect}) and (\ref{eq.sigma.mu}).
-This decomposition use the close set property of digital sequences.
+This criterion is an error bound based on the Walsh series decomposition of the integrands in (\ref{first.order}), (\ref{total.effect}) and (\ref{eq.sigma.mu}).
+This decomposition uses the group properties of digital nets.
 As such, our procedure relies on an iterative construction of Sobol' sequences.
@@
 
-The construction of the error bound is the subject of the next section. Our sequential procedure is detailed in section \ref{sec:4}.
+The description of the error bound is introduced in the following section and our sequential procedure is detailed in section \ref{sec:4}.
 
@@
 \label{sec:3} 
-We start by reviewing the construction of the error bound proposed in \cite{HicJim} for the estimation of a $d$-dimensional integral.
-Then, we present an extension of this error bound for Sobol' indices.
+We start by reviewing the construction of the error bound proposed in \cite{HicJim} for the estimation of $d$-dimensional integrals.
+Then, we present an extension of this error bound for normalized Sobol' indices.
 This extension exploits the integral formula of a Sobol' index.
@@
 \begin{equation}\label{dual_net_structure}
-\mathcal{P}_0^\perp=\left\{\mathbb{N}_0^d\right\}\supset\dots\supset\mathcal{P}_\infty=\{\vect{0}\}.
+\mathcal{P}_0^\perp=\mathbb{N}_0^d\supset\dots\supset\mathcal{P}_\infty=\{\vect{0}\}.
 \end{equation}
@@
 \end{equation}
-Therefore, considering the Walsh decomposition: \[
+Therefore, considering the Walsh decomposition for any $f\in L^2([0,1]^d)$: \[
 f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
-and:
-\[ I = \int_{\cube} f(\vx)\,d\vx,\]
-for any $f\in L^2([0,1]^d)$ and property \eqref{basis_integ_prop},
+and,
+\[ I(f) = \int_{\cube} f(\vx)\,d\vx,\]
+property \eqref{basis_integ_prop} leads to
 \begin{align*}
-\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
+\absolute{I(f) - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
 \absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}, \\
-&= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}}.
+&= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}} \\
+& \leq \sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\absolute{\hf_{\vk}}.
 \end{align*}
@@
 \begin{equation}
-\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
+\absolute{I(f) - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
 \end{equation}
-However, because the knowledge of the Walsh coefficients $\hf_{\kappa}$ is not assumed, we will estimate them using $\mathcal{P}_m$ instead, and refer to them as $\tf_{m,\kappa}$.
+However, because the knowledge of the Walsh coefficients $\hf_{\kappa}$ is not assumed, we will estimate them using the precomputed function values instead, and refer to them as $\tf_{m,\kappa}$.
 
@@
 \begin{equation}
-\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
-\le \frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)} = \epsilon_I, \label{errbd}
+\absolute{I(f) - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
+\le \overbrace{\frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}}^{\epsilon_I:=}, \label{errbd}
 \end{equation}
@@
 For our problem, only Sobol' sequences \cite{Sobol'seq} have been considered.
-These sequences are digital defined in base $b=2$.
+These are digital sequences defined in base $b=2$.
 Their major interest comes from their fast and easy implementation as well as their relatively slow growing size rate.
@@
 \end{align*}
-where $\vI=(I_1,I_2,I_3,I_4)$.
-$\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector of integrals $\vI$.
-If we estimate $\vI$ by $\widehat{\vI}$ with the vector of error bounds $\varepsilon_{\vI}=(\epsilon_{I_1},\epsilon_{I_2},\epsilon_{I_3},\epsilon_{I_4})$ according to \ref{sec:3.1}, we obtain $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
+where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values.
+$\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$.
+If we estimate $\vI$ by $\widehat{\vI}$ with the vector of error bounds $\varepsilon_{\vI}=(\epsilon_{I_1},\epsilon_{I_2},\epsilon_{I_3},\epsilon_{I_4})$ according to \ref{sec:3.1}, we know that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
 
@@
 \end{gather}
-Maximizing $\underline{S}_u(\vI)$ (resp.
+Because numerator and denominator are known to be positive, maximizing $\underline{S}_u(\vI)$ (resp.
 $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp.
 $I_2$) and minimizing the denominator $I_3-I_4^2$.
-At the opposite, minimizing $\underline{S}_u(\vI)$ (resp.
-$\overline{S}_u(\vI)$) is done through minimizing the numerator $I_1$ (resp.
-$I_2$) and maximizing the denominator $I_3-I_4^2$.
+Analogously, to minimize $\underline{S}_u(\vI)$ (resp.
+$\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp.
+$I_2$) and maximizes the denominator $I_3-I_4^2$.
 %As an example, Figure \ref{fig:1} below illustrate the maximization process for $\vI$ unidimensional.
@@
 
-Under the condition that each integrand of $\vI$ are in $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u} \right] .\]
+Under the assumption that each integrand of $\vI$ is in $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u} \right] .\]
 For the rest of the paper, we will consider $\widehat{\underline{S}_u}$ and $\widehat{\overline{S}_u}$   as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).

### 2016-08-30 article/template.tex
changes L., corrections C.P

@@
 \newcommand{\dtf}{\textit{\doubletilde{f}}}
-\newcommand{\cube}{[0,1)^d}
+\newcommand{\cube}{[0,1]^d}
 \newcommand{\rf}{\mathring{f}}
@@
 Section \ref{sec:4} is devoted to analyze the cost in terms of model evaluations of our sequential estimation algorithm.
-It combines the error bound in Section \ref{sec:3} and one of the two estimation procedures of Section \ref{sec:2}.
+It combines the error bound in Section \ref{sec:3} and either one of the two estimation procedures of Section \ref{sec:2}.
 We also discuss a potential improvement to estimate small first-order indices according to \cite{Owen}.
@@
 Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j={x'}_j$ if $j \notin u$.
+We assume that $f \in \mathbb{L}^2(\cube)$.% and denote by $\mu$ and $\sigma^2$ the mean $\int_{\cube}f(\vx)d{\vx}$ and variance $\int_{\cube}(f(\vx)-\mu)^2d{\vx}$ of $f$.
 
-We assume that $f \in \mathcal{L}^2\left([0,1]^d\right)$ and denote by $\mu$ and $\sigma^2$ the mean $\int_{\cube}f(\vx)d{\vx}$ and variance $\int_{\cube}(f(\vx)-\mu)^2d{\vx}$ of $f$.
-The uncertainty on $\vx$ is modeled as a uniform random variable, namely $\vx \iid \mathcal{U}\left([0,1)^d\right)$. The Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$ is:
+The uncertainty on $\vx$ is modeled by a uniform random vector, namely $\vx \iid \mathcal{U}(\cube)$. The Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$ is:
 \begin{equation}
-f(\vx)=\mu+\sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} f_u(\vx),
+f(\vx)=f_{\varnothing}+\sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} f_u(\vx),
 \label{anova}
@@
 where:
-\[f_u(\vx)= \int_{[0,1)^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).\]
+\begin{align*}
+f_{\varnothing} &= \mathrm{E}[\vx]= \mu, \\
+f_u(\vx) &= \int_{[0,1)^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).
+\end{align*}
 Due to orthogonality, applying the variance to equation \eqref{anova} leads to the variance decomposition of $f$:
-\[ \sigma^2 = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1)^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
+\[ \sigma^2 = \mathrm{Var}[\vx] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1)^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
 From this decomposition, one can express the following two quantities:
@@
 
-The problem of interest is the evaluation of first-order and total effect Sobol' indices of order 1.
+The problem of interest is the evaluation of first-order and total effect Sobol' indices.
+In our framework, we are only interested in single input indices.
+To this effect we restrain $u \in \mathcal{D}$.
 The computation of the normalized indices is performed based on the following integral formulas for their numerators:
@@
 \end{align}
-while the variance of $f$ is evaluated as:
-\begin{equation}
-\sigma^2 = \int_{[0,1)^{d}} f(\vx)^2d{\vx} - \mu^2, \text{ with } \ \mu = \int_{[0,1)^{d}} f(\vx) d{\vx}.
+while variance and mean of $f$ are evaluated by:
+\begin{gather}
+\begin{aligned}
+\sigma^2 &= \int_{[0,1)^{d}} f(\vx)^2d{\vx} - \mu^2, \\
+ \mu &= \int_{[0,1)^{d}} f(\vx) d{\vx},
 \label{eq.sigma.mu}
-\end{equation} 
+\end{aligned}
+\end{gather}
 Usually the complexity of $f$ causes the computation of integrals \eqref{first.order}, (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable.
@@
 \end{equation}
-Then, the normalized Sobol' indices estimators are:
+Then, the Sobol' indices estimators are:
 \begin{equation}
-\widehat{\underline{S}_u} = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
-\widehat{\overline{S}_u} = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
+\widehat{\underline{S}}_u = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
+\widehat{\overline{S}}_u = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
 \label{common.sobol.est}
 \end{equation}
-The estimation of a single pair ($\widehat{\underline{S}_u}$, $\widehat{\overline{S}_u}$) requires $3n$ evaluations of the model $f$.
+The estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$.
 Thus, for first order indices, one would need $3nd$ model evaluations.
@@
 \label{saltelli.theorem}
-The $d+2$ designs $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allows to estimate all first-order and total effect Sobol' indices of order 1 at a cost of $n(d+2)$ evaluations of the model.
+The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allows to estimate all first-order and total effect Sobol' indices of order 1 at a cost of $n(d+2)$ evaluations of the model.
 \end{theorem}
 The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ accordingly to $u$.
-Indeed, there is no need of reevaluating $f({\vx}_i$ and $f({\vx'}_i$ for each $u$.
+Indeed, there is no need of reevaluating $f({\vx}_i)$ and $f({\vx'}_i)$ for each $u$.
 While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input space dimension.
@@
 From Definition \ref{rep.designs}, ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$.
-Then, for all $i \in \{0,\dots,n-1\}$:
+We define:
+\[\pi_u(f({\vx'}_i)) = f({\vx'}_{\pi_u(i)}), \qquad  i \in \{0,\dots,n-1\},\]
+then remark:
 \begin{align*}
-\pi_u(f({\vx'}_i))&= f({\vx'}_{\pi_u(i)}), \\
-&= f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u}), \\
+\pi_u(f({\vx'}_i))&= f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u}), \\
 &= f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).
@@
 The aim of this paper is to propose a sequential procedure to estimate first-order and total effect Sobol' indices.
-Generally, in most sequential procedures that estimate Sobol' indices, the stopping criterion is a quantity of interest built directly upon the estimates.
-Such stopping criteria often involve hyper-parameters hard to tweak but above all fail to guarantee any error bound on the estimates.
+A practical problem concerning the estimation of these indices is how large to choose the number of evaluations to ensure that Sobol' estimates are accurate enough.
+Asymptotical results show that Sobol' estimates are normally distributed (\cite[Proposition 2.2]{Janon}, \cite[Proposition 3.5]{Tissot}).
+As a consequence, confidence intervals can be use.
+
+An alternative to address this problematic is the use of sequential procedures.
+As examples, sequential versions of the replication procedure and McKay's procedure are respectively proposed in \cite{Gilquin.rec} and \cite{Tong}.
+However, in those two latter procedures, the stopping criterion is a quantity of interest purely empirical, built directly upon the estimates.
+Such stopping criteria often involve hyper-parameters difficult to tweak but more importantly fail to guarantee any error bound on the estimates.
 
@@
 
-In order to relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the relationship between any digital net and the \emph{wavenumber} space $\mathbb{N}_0^d$.
+In order to relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the relationship between any digital net and the \emph{wavenumber} space $\mathbb{N}_0^d$ of non-negative integers.
 Hence, a dual net is
@@
 \begin{equation}\label{dual_net_structure}
-\mathcal{P}_0^\perp=\mathbb{N}_0^d\supset\dots\supset\mathcal{P}_\infty=\{\vect{0}\}.
+\mathcal{P}_0^\perp=\mathbb{N}_0^d\supset\dots\supset\mathcal{P}_\infty^\perp=\{\vect{0}\}.
 \end{equation}
-As shown in \cite[Sec. 3]{HicJim}, the group structure of the digital nets guarantees the property below affecting any Walsh basis $\phi_{\vk}(\vx)$,
+As shown in \cite[Sec. 3]{HicJim}, the group structure of the digital nets guarantees the property below affecting any Walsh basis $\varphi_{\vk}(\vx)$,
 \begin{equation}\label{basis_integ_prop}
-\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\phi_{\vk}(\vx)=
+\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\varphi_{\vk}(\vx)=
 \begin{cases}
@@
 \end{equation}
-Therefore, considering the Walsh decomposition for any $f\in L^2([0,1]^d)$: \[
+Therefore, considering the Walsh decomposition for any $f\in \mathbb{L}^2([0,1]^d)$: \[
 f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
@@
 \begin{multline} \label{conecond}
-\cc:=\{f \in L^2(\cube) : \hS_{\ell,m}(f) \le \homega(m-\ell) \wcS_m(f),\ \ \ell \le m, \\
+\cc:=\{f \in \mathbb{L}^2(\cube) : \hS_{\ell,m}(f) \le \homega(m-\ell) \wcS_m(f),\ \ \ell \le m, \\
 \wcS_m(f) \le \wcomega(m-\ell) S_{\ell}(f),\ \  \ell_* \le \ell \le m\}.
@@
 
-Hence, in \cite[Sec. 4.2]{HicJim} we prove that for any $f\in\cc$,
+Hence, in \cite[Sec. 4.2]{HicJim} it is proved that for any $f\in\cc$,
 \begin{equation}
@@
 $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$.
-If we estimate $\vI$ by $\widehat{\vI}$ with the vector of error bounds $\varepsilon_{\vI}=(\epsilon_{I_1},\epsilon_{I_2},\epsilon_{I_3},\epsilon_{I_4})$ according to \ref{sec:3.1}, we know that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
+If we estimate $\vI$ by $\widehat{\vI}$ with the vector of error bounds $\varepsilon_{\vI}=(\epsilon_{I_1},\epsilon_{I_2},\epsilon_{I_3}$,\\ $\epsilon_{I_4})$ according to \ref{sec:3.1}, we know that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
 
@@
 \begin{aligned}
-\widehat{\underline{S}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
+\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
 \varepsilon_{\underline{S}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
@@
 \begin{aligned}
-\widehat{\overline{S}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
+\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
 \varepsilon_{\overline{S}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
@@
 
-Under the assumption that each integrand of $\vI$ is in $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u} \right] .\]
-For the rest of the paper, we will consider $\widehat{\underline{S}_u}$ and $\widehat{\overline{S}_u}$   as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).
+Under the assumption that each integrand of $\vI$ is in $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}}_u + \varepsilon_{\underline{S}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}}_u + \varepsilon_{\overline{S}_u} \right] .\]
+For the rest of the paper, we will consider $\widehat{\underline{S}}_u$ and $\widehat{\overline{S}}_u$   as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).
 
@@
 
-We start be detailing our procedure in the form of an algorithm.
+We start by detailing our procedure in the form of an algorithm.
 Then, we discuss a possible improvement by considering a new estimator recently introduced in \cite{Owen} for the estimation of first-order indices.
@@
 
-In both case we test if the respective error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ are lower than the tolerance $\epsilon$.
+In both cases we test if the respective error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ are lower than the tolerance $\epsilon$.
 For Variant $A$ the stopping criterion writes: $ \forall u \in \mathcal{D}, \varepsilon_{\underline{S}_u} \leq \epsilon \text{ and } \varepsilon_{\overline{S}_u} \leq \epsilon$,
@@
 \If {Variant $A$}
-\State estimate $\widehat{\underline{S}_u}$ and $\widehat{\ov{$S$}_u}$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}) and Saltelli's strategy
+\State estimate $\widehat{\underline{S}}_u$ and $\widehat{\ov{$S$}}_u$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}) and Saltelli's strategy
 \State $bool_u \leftarrow \varepsilon_{\underline{S}_u} \leq \epsilon \ \& \ \varepsilon_{\overline{S}_u} \leq \epsilon$
@@
 \If {Variant $B$}
-\State estimate $\widehat{\underline{S}_u}$ with formula (\ref{formula_undersu}) and the replication procedure
+\State estimate $\widehat{\underline{S}}_u$ with formula (\ref{formula_undersu}) and the replication procedure
 \State $bool_u \leftarrow \varepsilon_{\underline{S}_u} \leq \epsilon$
@@
 \item[$\bullet$] for $j\in \Gamma$, $2^{m''_{u_j}}$ is the number of evaluations \\ $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate $\underline{S}_{u_j}$,
-\item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations \\ $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
-\item[$\bullet$] likewise, for $j\in \mathcal{D}\setminus{\Gamma}$, $ 2^{m_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
+\item[$\bullet$] for $j\in \Gamma$, $2^{m'_{u_j}}$ is the number of evaluations \\ $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
+\item[$\bullet$] likewise, for $j\in \mathcal{D}\setminus{\Gamma}$, $ 2^{m_{u_j}}$ is the number of evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ to estimate both $\underline{S}_{u_j}$ and  $\overline{S}_{u_j}$,
 \item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
@@
 \end{equation}
-Hence, the sign of this difference indicates whether or not using ``Correlation 2" bring an improvement to Variant $A$. We distinguish two cases :
+Hence, the sign of this difference indicates whether or not using ``Correlation 2" brings an improvement to Variant $A$. We distinguish two cases :
 \begin{itemize}
@@
 To overcome this issue, we propose the following alternative for Variant $A$.
-If at the end of the first iteration, the estimate $\widehat{\underline{S}_u}$, $u \in \mathcal{D}$, is smaller than a specified threshold, then at the next iteration estimator (\ref{first.order.est}) is switched for ``Correlation 2" and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+If at the end of the first iteration, the estimate $\widehat{\underline{S}}_u$, $u \in \mathcal{D}$, is smaller than a specified threshold, then at the next iteration estimator (\ref{first.order.est}) is switched for ``Correlation 2" and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
 
@@
 This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-\newline MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).
-The authors thank Stephen Joe, Frances Y.
+
+The authors thank Fred J.
+Hickernell and Cl\'ementine Prieur for initiating this collaborative work and Elise Arnaud for her proofreading.
+The authors are grateful to Stephen Joe, Frances Y.
 Kuo and Art B.
@@
 %
+\bibitem{Gilquin.rec}
+Gilquin, L., Arnaud, E., Monod, H., Prieur, C.: Recursive estimation procedure of Sobol' indices based on replicated designs, preprint available at \url{https://hal.inria.fr/hal-01291769}, (2016).
 \bibitem{GJAHMP}
@@
 \bibitem{Saltelli}
+Saltelli, A.: Making best use of models evaluations to compute sensitivity indices, Comput. Phys. Commun. \textbf{145}(2), 280-297 (2002)
+\bibitem{Sobol'seq}
 Sobol', I.M.: On the distribution of points in a cube and the approximate evaluation of integrals, USSR Comput. Math. Math. Phys. \textbf{7}(4), 86-112 (1967)
-\bibitem{Sobol'seq}
-Saltelli, A.: Making best use of models evaluations to compute sensitivity indices, Comput. Phys. Commun. \textbf{145}(2), 280-297 (2002)
 \bibitem{Sobol'}
@@
 \bibitem{Tissot}
-Tissot, J.Y., Prieur, C.: A randomized Orthogonal Array-based procedure for the estimation of first- and second-order Sobol' indices, J. Statist. Comput. Simulation \textbf{85}(7), 1358-1381 (2014)
+Tissot, J.Y., Prieur, C.: A randomized Orthogonal Array-based procedure for the estimation of first- and second-order Sobol' indices, J. Statist. Comput. Simulation \textbf{85}(7), 1358-1381 (2015)
+\bibitem{Tong}
+Tong C.: Self-validated variance-based methods for sensitivity analysis of model outputs, Reliab. Eng. Syst. Saf. \textbf{95}(3), 301-309 (2010)
 

### 2016-08-30 article/template.tex
Last changes in template.tex

@@
 \begin{align*}
-f_{\varnothing} &= \mathrm{E}[\vx]= \mu, \\
+f_{\varnothing} &= \mathrm{E}[f(\vx)]= \mu, \\
 f_u(\vx) &= \int_{[0,1)^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).
@@
 Due to orthogonality, applying the variance to equation \eqref{anova} leads to the variance decomposition of $f$:
-\[ \sigma^2 = \mathrm{Var}[\vx] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1)^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
+\[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1)^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
 From this decomposition, one can express the following two quantities:
@@
 The problem of interest is the evaluation of first-order and total effect Sobol' indices.
-In our framework, we are only interested in single input indices.
+In our framework, we are only interested in single input indices, $|u|=1$.
 To this effect we restrain $u \in \mathcal{D}$.
@@
 \end{align}
-while variance and mean of $f$ are evaluated by:
+while variance and mean of $f$ are evaluated as:
 \begin{gather}
@@
 Usually the complexity of $f$ causes the computation of integrals \eqref{first.order}, (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable.
-In such cases, one can estimate these quantities instead.
+In such cases, one can instead estimate these quantities.
 
@@
 Denote by $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$.
-From Definition \ref{rep.designs}, ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$.
-We define:
+From Definition \ref{rep.designs}, we know that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$.
+In addition, we define:
 \[\pi_u(f({\vx'}_i)) = f({\vx'}_{\pi_u(i)}), \qquad  i \in \{0,\dots,n-1\},\]
@@
 \end{align*}
-Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) with \\ $\pi_u(f({\vx'}_i))$ in place of $f(\vx_{i,u}:{\vx'}_{i,-u})$ without requiring further model evaluations.
+Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) where \\ $\pi_u(f({\vx'}_i))$ is exactly $f(\vx_{i,u}:{\vx'}_{i,-u})$ without requiring further model evaluations.
 This estimation method has been deeply studied and generalized in Tissot et al.
@@
 Asymptotical results show that Sobol' estimates are normally distributed (\cite[Proposition 2.2]{Janon}, \cite[Proposition 3.5]{Tissot}).
-As a consequence, confidence intervals can be use.
+As a consequence, confidence intervals can be used.
 
@@
 As examples, sequential versions of the replication procedure and McKay's procedure are respectively proposed in \cite{Gilquin.rec} and \cite{Tong}.
-However, in those two latter procedures, the stopping criterion is a quantity of interest purely empirical, built directly upon the estimates.
-Such stopping criteria often involve hyper-parameters difficult to tweak but more importantly fail to guarantee any error bound on the estimates.
+However, in those two cases, the stopping criterion is a quantity of interest purely empirical, built directly upon the estimates.
+Such stopping criteria often involve hyper-parameters difficult to tweak but more importantly, fail to guarantee any error bound on the estimates.
 
 Our sequential procedure stands apart from others with the construction of a robust stopping criterion.
-This criterion is an error bound based on the Walsh series decomposition of the integrands in (\ref{first.order}), (\ref{total.effect}) and (\ref{eq.sigma.mu}).
-This decomposition uses the group properties of digital nets.
+This criterion is an error bound based on the Walsh series decomposition of the integrands in (\ref{first.order}), (\ref{total.effect}) and (\ref{eq.sigma.mu}), and exploits the group properties of digital nets.
 As such, our procedure relies on an iterative construction of Sobol' sequences.
@@
 Then, we present an extension of this error bound for normalized Sobol' indices.
-This extension exploits the integral formula of a Sobol' index.
+This extension is built upon the integral formula of a Sobol' index.
 
@@
 
-In order to relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the relationship between any digital net and the \emph{wavenumber} space $\mathbb{N}_0^d$ of non-negative integers.
+In order to relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the relationship between any digital net and the \emph{wavenumber} space of non-negative integers $\mathbb{N}_0^d$.
 Hence, a dual net is
-\[
-\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vx}{\vk}=0,\, \vx\in\mathcal{P}_m\},
-\]
+\begin{align*}
+\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vk}{\vx}=0,\, \vx\in\mathcal{P}_m\}, \\
+\ip{\vk}{\vx} = \sum_{j=1}^{d} \sum_{\ell=0}^{\infty} k_{j\ell}x_{j,\ell+1}  \pmod b.
+\end{align*}
 and inherits the same embedded structure as for the digital nets,
@@
 \end{equation}
-As shown in \cite[Sec. 3]{HicJim}, the group structure of the digital nets guarantees the property below affecting any Walsh basis $\varphi_{\vk}(\vx)$,
+As shown in \cite[Sec. 3]{HicJim}, the group structure of the digital nets guarantees the property below affecting any Walsh basis $\varphi_{\vk}(\vx)=\e^{2 \pi \sqrt{-1} \ip{\vk}{\vx}/b}$,
 \begin{equation}\label{basis_integ_prop}
@@
 property \eqref{basis_integ_prop} leads to
-\begin{align*}
+\begin{align}
+\nonumber
 \absolute{I(f) - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
 \absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}, \\
+\nonumber
 &= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}} \\
-& \leq \sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\absolute{\hf_{\vk}}.
-\end{align*}
+& \leq \sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\absolute{\hf_{\vk}}. \label{3.1.err_bound}
+\end{align}
 Based on the size of $\absolute{\hf_{\vk}}$ and the structure of the dual nets \eqref{dual_net_structure}, in \cite[Sec.
 4.1]{HicJim} we proposed an ordering of the wave-numbers $\vk(\cdot):\naturals_0\rightarrow\naturals_0^d$.
-To simplify notation, $\hf_{\kappa}:=\hf_{\vk(\kappa)}$.
+This ordering will be helpful to address the summation in \eqref{3.1.err_bound}.
+To simplify notation, $\hf_{\kappa}=\hf_{\vk(\kappa)}$.
 This mapping leads to the following error bound,
@@
 \end{equation}
-However, because the knowledge of the Walsh coefficients $\hf_{\kappa}$ is not assumed, we will estimate them using the precomputed function values instead, and refer to them as $\tf_{m,\kappa}$.
+However, because the knowledge of the Walsh coefficients $\hf_{\kappa}$ is not assumed, we will estimate them using the fast transform obtained with the precomputed function values, and refer to them as $\tf_{m,\kappa}$.
+Note that for function values evaluated at $\mathcal{P}_m$, one only generates $b^m$ discrete Walsh coefficients $\tf_{m,\kappa}$.
 
@@
 \absolute{I(f) - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
-\le \overbrace{\frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}}^{\epsilon_I:=}, \label{errbd}
+\le \overbrace{\frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}}^{\epsilon_{I(f)}=}, \label{errbd}
 \end{equation}
-where one may increase $m$ until the error bound $\epsilon_I$ is small enough.
+where one may increase $m$ until the error bound $\epsilon_{I(f)}$ is small enough.
 
@@
 where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values.
-$\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$.
-If we estimate $\vI$ by $\widehat{\vI}$ with the vector of error bounds $\varepsilon_{\vI}=(\epsilon_{I_1},\epsilon_{I_2},\epsilon_{I_3}$,\\ $\epsilon_{I_4})$ according to \ref{sec:3.1}, we know that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
+$\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over vector $\vI$.
+If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\vI}=(\epsilon_{I_1},\epsilon_{I_2},\epsilon_{I_3}$,\\ $\epsilon_{I_4})$ according to \ref{sec:3.1}, we know that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
 
-Then, alternatively to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the two following estimators with the respective error bounds:
+Then, alternatively to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
 \begin{gather}
@@
 \label{sec:4}
-The sequential estimation procedure we propose combine the error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ presented in the previous section with one of the two estimation strategies of section \ref{sec:2.2}: Saltelli's strategy and the replication procedure.
+The sequential estimation procedure we propose combines the error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ presented in the previous section with either one of the two estimation strategies of section \ref{sec:2.2}: Saltelli's strategy and the replication procedure.
 
@@
 Step $5$ corresponds to the recursive scheme of this approach.
-The choice of $m_0$ must be large enough to insure that each integrand of $\vI$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).
+The choice of $m_0$ must be large enough to ensure that each integrand of $\vI$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).
 
-With this construction, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two Sobol' sequences.
+With this construction, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two independent Sobol' sequences.
 Furthermore, they possess the structure of two replicated designs of order $1$ (Definition \ref{rep.designs}).
@@
 \item[$\bullet$] $2^{m_u}$ is the number of evaluations $f\left(\vx_{i,u}:{\vx'}_{i,-u}\right)$ used to estimate both the first-order index $\underline{S}_u$ and the total effect index $\overline{S}_u$,
-\item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
+\item[$\bullet$] $2 \times 2^{m^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect indices.
 \end{itemize}
@@
 
-If Variant $B$ is selected the cost of our algorithm equals $2 \times 2^{m^{\star}}$. This cost corresponds to the one of the replication procedure with $n=2^{m^{\star}}$.
+If Variant $B$ is selected the cost of our algorithm equals $2 \times 2^{m^{\star}}$.
+This cost corresponds to the one of the replication procedure claimed in the introduction, where $2n=2\times 2^{m^{\star}}$ independent of $d$.
 
@@
 
-We discuss below the potential improvement brought by the use of ``Correlation 2" in Variant $A$.
-The idea is to replace the current estimator (\ref{first.order.est}) by  ``Correlation 2" for each small first-order index.
+We discuss below the potential improvement brought by using ``Correlation 2" in Variant $A$.
+The idea is to replace the current estimator (\ref{first.order.est}) by  ``Correlation 2" for each small first-order indices.
 
@@
 \end{itemize}
-Overall we expect to have more case $2)$ than case $1)$.
-Indeed, the numerator of $\underline{S}_u$ requires to estimate $2d-1$ integrals against only $d+1$ integrals for the numerator of $\ov{$S$}_u$.
-Hence, it seems reasonable to suppose that it takes less points to evaluate $\ov{$S$}_u$ than $\underline{S}_u$.
+Overall we expect to observe case $2)$ more often than case $1)$.
+Indeed, the numerator of $\underline{S}_u$ requires to estimate $2d-1$ dimensional integrals against only $d+1$ dimensional integrals for the numerator of $\ov{$S$}_u$.
+Hence, it seems reasonable to expect that it will take less points to estimate $\ov{$S$}_u$ than $\underline{S}_u$.
 
-Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to be always satisfied as ``Correlation 2" has been shown 
-to perform the best for small first-order indices. To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{sec:5}.
+Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to always hold as ``Correlation 2" is shown 
+to perform better for small first-order indices. To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{sec:5}.
 
-In pratice, one does not know which are the small Sobol' indices.
+In practice, one does not know which are the small Sobol' indices.
 To overcome this issue, we propose the following alternative for Variant $A$.
-If at the end of the first iteration, the estimate $\widehat{\underline{S}}_u$, $u \in \mathcal{D}$, is smaller than a specified threshold, then at the next iteration estimator (\ref{first.order.est}) is switched for ``Correlation 2" and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+If at the end of the first iteration, the estimate $\widehat{\underline{S}}_u$, $u \in \mathcal{D}$, is smaller than a threshold, then at the next iteration estimator (\ref{first.order.est}) is switched for ``Correlation 2" and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
 
@@
 Kuo and Art B.
-Owen for helpful answers and suggestions.
+Owen for their helpful answers and suggestions.
 \end{acknowledgements}
@@
 \bibitem{GJAHMP}
-Gilquin, L., Jim\'enez Rugama, L.A., Arnaud, E., Hickernell, F.J., Monod, H., Prieur, C.: Iterative construction of replicated designs based on Sobol' sequences, preprint available at \url{https://hal.inria.fr/hal-01349444} (2016)
+Gilquin, L., Jim\'enez Rugama, Ll.A., Arnaud, E., Hickernell, F.J., Monod, H., Prieur, C.: Iterative construction of replicated designs based on Sobol' sequences, preprint available at \url{https://hal.inria.fr/hal-01349444} (2016)
 \bibitem{HicJim}
-Hickernell, F.J., Jim\'enez Rugama, L.A.: Reliable Adaptative Cubature Using Digital Sequences: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 367-383 (2016)
+Hickernell, F.J., Jim\'enez Rugama, Ll.A.: Reliable Adaptative Cubature Using Digital Sequences: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 367-383 (2016)
 \bibitem{Hoeffding}

### 2016-08-30 article/template.tex
last check

@@
 \newcommand{\tS}{\widetilde{S}}
-\newcommand{\tf}{\tilde{f}}
+\newcommand{\tf}{\widetilde{f}}
 \newcommand{\fC}{\mathfrak{C}}
@@
 The problem of interest is the evaluation of first-order and total effect Sobol' indices.
-In our framework, we are only interested in single input indices, $|u|=1$.
-To this effect we restrain $u \in \mathcal{D}$.
+In our framework, we are only interested in single input indices, namely $|u|=1$.
 The computation of the normalized indices is performed based on the following integral formulas for their numerators:
@@
 \absolute{I(f) - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
-\le \overbrace{\frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}}^{\epsilon_{I(f)}=}, \label{errbd}
+\le \frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}=\epsilon_{I(f)}, \label{errbd}
 \end{equation}
@@
 If Variant $B$ is selected the cost of our algorithm equals $2 \times 2^{m^{\star}}$.
-This cost corresponds to the one of the replication procedure claimed in the introduction, where $2n=2\times 2^{m^{\star}}$ independent of $d$.
+This cost corresponds to the one of the replication procedure introduced in Section \ref{sec:2.2}, where $2n=2\times 2^{m^{\star}}$ independent of $d$.
 
@@
 \end{equation}
-where $m'_{u_j}\leq m^{\star}$, $\ m_{u_j} \leq m^{\star}$, and: 
+where: %$m'_{u_j}\leq m^{\star}$, $\ m_{u_j} \leq m^{\star}$, and: 
 \begin{itemize}
@@
 \begin{equation}
-\sum \limits_{j \in \Gamma} 2^{m_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^{\star}}, \qquad m_{u_j} \leq m^{\star}.
+\sum \limits_{j \in \Gamma} 2^{m_{u_j}} + \sum \limits_{j \in \mathcal{D}\setminus{\Gamma}} 2^{m_{u_j}} + 2 \times 2^{m^{\star}}. 
+%\qquad m_{u_j} \leq m^{\star}.
 \label{cost.non.improvement}
 \end{equation}
-The difference between costs (\ref{cost.improvement}) and (\ref{cost.non.improvement}) equals:
+The difference (\ref{cost.improvement}) $-$ (\ref{cost.non.improvement}) equals:
 \begin{equation}
@@
 
-Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to always hold as ``Correlation 2" is shown 
-to perform better for small first-order indices. To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{sec:5}.
+Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to always hold as ``Correlation 2" is shown in \cite{Owen} to perform better for small first-order indices.
+To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{sec:5}.
 
-In practice, one does not know which are the small Sobol' indices.
+In practice, one does not know which are the small Sobol' indices ($u_1,\dots,u_\gamma)$.
 To overcome this issue, we propose the following alternative for Variant $A$.
-If at the end of the first iteration, the estimate $\widehat{\underline{S}}_u$, $u \in \mathcal{D}$, is smaller than a threshold, then at the next iteration estimator (\ref{first.order.est}) is switched for ``Correlation 2" and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+If at the end of the first iteration, the estimate $\widehat{\underline{S}}_u$, $u \in \mathcal{D}$, is smaller than a threshold (here $0.1$), then at the next iteration estimator (\ref{first.order.est}) is switched for ``Correlation 2" and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
 
@@
 Hoeffding, W.F.: A class of statistics with asymptotically normal distribution, Ann. Math. Stat. \textbf{19}(3), 293-325 (1948)
-%\bibitem{Janon}
-%Janon, A., Klein, T., Lagnoux A., Nodet, M., Prieur C.: Asymptotic normality and efficiency of two {S}obol' index estimators, ESAIM Probab. Stat. \textbf{18}, 342-364 (2014)
+\bibitem{Janon}
+Janon, A., Klein, T., Lagnoux A., Nodet, M., Prieur C.: Asymptotic normality and efficiency of two {S}obol' index estimators, ESAIM Probab. Stat. \textbf{18}, 342-364 (2014)
 \bibitem{Lemieuxbook}

### 2016-09-20 FunctionsTest/SI_all_example.m
Adding examples and plot for article

@@ -1,14 +1,14 @@
 clearvars
 
-abstol = 1*1e-3;
+abstol = 5*1e-3;
 reltol = 0e-2; % Pure absolute tolerance
-mmin = 10;
+mmin = 9;
 mmax = 24; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
 wronga = 0; % Wrong estimates with all indices method
 wrong = 0; % Wrong estimates using the one by one algo
 s = .0; %time in seconds used delay each function evaluation
 
-fudge = @(m,d) 5*2.^-(m);
+fudge = @(m,d) 5*2.^-(1.*m);
 
 %% Ishigami
 disp('Running Ishigami example ...')
@@ -25,8 +25,9 @@ SI_s = out_param.small;
 disp(SI)
 % disp(out_param.bound_err)
 disp(SI_n)
+disp(abs(R - SI))
 % disp(SI_s)
-% disp(abs(R-SI) > max(abstol,R*reltol))
+disp(abs(R-SI) > max(abstol,R*reltol))
 % disp(out_param.exitflag)
 % wronga = wronga + sum(sum(abs(R-SI) > max(abstol,R*reltol)));
 % disp(['Time:' num2str(SI_t)])
@@ -74,8 +75,9 @@ SI_s = out_param.small;
 disp(SI)
 % disp(out_param.bound_err)
 disp(SI_n)
+disp(abs(R - SI))
 % disp(SI_s)
-% disp(abs(R-SI) > max(abstol,R*reltol))
+disp(abs(R-SI) > max(abstol,R*reltol))
 % wronga = wronga + sum(sum(abs(R-SI) > max(abstol,R*reltol)));
 % disp(['Time:' num2str(SI_t)])
 
@@ -99,7 +101,6 @@ disp(SI_n)
 % disp(SI)
 % disp(SI_n)
 % disp(SI_s)
-% disp(abs(R-SI) > abstol)
 % wrong = wrong + sum(sum(abs(R-SI) > abstol));
 % if any(sum(exitflag) > 0) || any(sum(exitflagt) > 0)
 %     warning('Results cannot be guaranteed due to reaching maximum budget or failing necessary conditions.')
@@ -124,8 +125,9 @@ SI_s = out_param.small;
 disp(SI)
 % disp(out_param.bound_err)
 disp(SI_n)
+disp(abs(R - SI))
 % disp(SI_s)
[…]

### 2016-09-20 FunctionsTest/cubSobol_SI_all_g.m

@@ -255,12 +255,12 @@ numerator_size = 1;
 % Sfo_max = @(down, up) estimate_max(down, up); % S function for first order
 % ffo1 = @(xpts,u,fx,fy,fxy,fzx) fx.*fxy;
 % ffo2 = @(xpts,u,fx,fy,fxy,fzx) 1/2*(fx + fxy);
-Sfo_min = @(down, up) estimate_min([down(1) down(end) down(2:end)], [up(1) up(end) up(2:end)]); % S function for first order
-Sfo_max = @(down, up) estimate_max([down(1) down(end) down(2:end)], [up(1) up(end) up(2:end)]); % S function for first order
-ffo = @(xpts,u,fx,fy,fxy,fzx) fx.*fxy;
-% Sfo_min = @(down, up) estimate_min([down(1) 0 down(2:end)], [up(1) 0 up(2:end)]); % S function for first order
-% Sfo_max = @(down, up) estimate_max([down(1) 0 down(2:end)], [up(1) 0 up(2:end)]); % S function for first order
-% ffo = @(xpts,u,fx,fy,fxy,fzx) fx.*(fxy - fy); % ffo = @(xpts,u,fx,fy,fxy,fzx) (fx - 1/2*mean(fx + fxy)).*(fxy - 1/2*mean(fx + fxy));
+% Sfo_min = @(down, up) estimate_min([down(1) down(end) down(2:end)], [up(1) up(end) up(2:end)]); % S function for first order
+% Sfo_max = @(down, up) estimate_max([down(1) down(end) down(2:end)], [up(1) up(end) up(2:end)]); % S function for first order
+% ffo = @(xpts,u,fx,fy,fxy,fzx) fx.*fxy;
+Sfo_min = @(down, up) estimate_min([down(1) 0 down(2:end)], [up(1) 0 up(2:end)]); % S function for first order
+Sfo_max = @(down, up) estimate_max([down(1) 0 down(2:end)], [up(1) 0 up(2:end)]); % S function for first order
+ffo = @(xpts,u,fx,fy,fxy,fzx) fx.*(fxy - fy); % ffo = @(xpts,u,fx,fy,fxy,fzx) (fx - 1/2*mean(fx + fxy)).*(fxy - 1/2*mean(fx + fxy));
 
 Sfo_s_min = @(down,up) estimate_min([down(1) 0 down(2:end)], [up(1) 0 up(2:end)]); % S function for first order small
[…]

### 2016-09-20 article/Images/article_scheme_S.m

@@ -6,9 +6,9 @@
 
 S = @(x) exp(-(x-1).^2) + 1;
 
-Ireal = I - err + 0.03;
 I = 0.90;
 err = 0.2;
+Ireal = I - err + 0.03;
 Smax = S(1); xmax = 1;
 Smin = S(I - err); xmin = I - err;
 

### 2016-09-20 article/Images/article_scheme_S_3D.m

@@ -1,0 +1,153 @@
+set(0,'defaultaxesfontsize',16,'defaulttextfontsize',16) %make font larger
+set(0,'defaultLineLineWidth',3) %thick lines
+set(0,'defaultTextInterpreter','latex') %latex axis labels
+set(0,'defaultLegendInterpreter','latex') %latex axis labels
+set(0,'defaultLineMarkerSize',5) %latex axis labels
+
+% Bratley d=6 S_2 first order
+sigma2 = 164143/2985984;
+indice = 0.1791303924*sigma2;
+S = @(I3, I4) min(indice./max(I3-I4.^2, eps), 1);
+
+mu = -21/64;
+I = [(sigma2 + (mu)^2) -mu];
+err = [.05 .1]; 
+Ireal = I - .35*err.*[1 -1];
+Smax = S(I(1) - err(1), I(2) + err(2));
+Smin = S(I(1) + err(1), I(2) - err(2));
+
+
+step = 0.0025;
+width = 0.02;
+[X,Y] = meshgrid(I(1) - err(1) - width:step:I(1) + err(1) + width,...
+    I(2) - err(2) - width:step:I(2) + err(2) + width);
+mesh(X, Y, S(X, Y))
+axis tight
+xmin = min(min(X)); xmax = max(max(X));
+ymin = min(min(Y)); ymax = max(max(Y));
+zmin = min(min(S(X, Y))); zmax = max(max(S(X, Y)));
+
+ax = gca;
+set(ax,'TickLabelInterpreter', 'Latex');
+ax.XTick = sort([I(1)-err(1) Ireal(1) I(1) I(1)+err(1)]);
+ax.YTick = sort([I(2)-err(2) Ireal(2) I(2) I(2)+err(2)]);
+if S(Ireal(1),Ireal(2)) < Smax & S(Ireal(1),Ireal(2)) > Smin % Not the...
+    % same value as Smax and Smin for the Zaxis
+    ax.ZTick = sort([Smin S(Ireal(1),Ireal(2)) (Smin+Smax)/2 S(I(1),I(2)) Smax]);
+else
+    ax.ZTick = sort([Smin (Smin+Smax)/2 S(I(1),I(2)) Smax]);
+end
[…]

### 2016-09-22 article/template.tex
Adding examples and plot for article
Adding all changes and new files for examples in template.tex. There is still no scrambled replicated code (cubSobol_fo_all_g)

@@
 $I_2$) and maximizes the denominator $I_3-I_4^2$.
-%As an example, Figure \ref{fig:1} below illustrate the maximization process for $\vI$ unidimensional.
-%\begin{figure*}
-%\centering
-%\includegraphics[width=0.75\textwidth]{scheme_S.eps}
-% figure caption is below the figure
-%\caption{Estimator property.}
-%\label{fig:1}       % Give a unique label
-%\end{figure*}
+As an example, Figure \ref{fig:1} below illustrate the maximization process for $\vI$ unidimensional.
+\begin{figure*}
+\centering
+\includegraphics[width=1\textwidth]{Images/estimator_3d_small.eps}
+ figure caption is below the figure
+\caption{Estimator property.}
+\label{fig:1}       % Give a unique label
+\end{figure*}
 
@@
 \label{sec:5}
+
+\subsection{Classical test functions}
+\label{sec:5.1}
+
+$\varepsilon=10^{-3}$, initial $1024$ points, $fudge = @(m,d) 10*2.^-(.9*m)$, run $100$ samples to estimate the mean:
+
+\subsubsection{With small indices estimator}
+Bratley et al. example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.6530  &  0.1790  &  0.0370  &  0.0134  &  0.0016  &  0.0015 \\ \hline
+ n & 521667  &    262144  &     65536  &  17039  &   1055  &      1096 \\ \hline
+ \text{error } 10^{-3} & 0.0211  &  0.0520  &  0.1160  &  0.1550  &  0.3220  &  0.3210 \\ \hline
+ \widehat{\overline{S}}_u & 0.7400  &  0.2660  &  0.0764  &  0.0343  &  0.0060  &  0.0061 \\  \hline
+ n & 262144  &    131072  &   65536  &   40960  &  4936  &      6031 \\ \hline
+ \text{error } 10^{-3} & 0.0578  &  0.0374  &  0.0761  &  0.1820  &  0.5530  &  0.2740 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     100  & 100  & 100  & 100  &  99  & 100 \\
+     100  & 100  & 100  &  99  &  84  &  90
+\end{array}
+\]
+
+Sobol g-function example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.5870  &  0.2610  &  0.0365 &   0.0059  &  0.0001  &  0.0001 \\ \hline
+ n & 131072   &  130417  &  17695  &  1987  &  1024  &   1024 \\ \hline
+ \text{error } 10^{-3} & 0.0235  &  0.0228  &  0.2140 & 0.1560  &  0.0026  &  0.0023 \\ \hline
+ \widehat{\overline{S}}_u & 0.6900  &  0.3560  &  0.0563 &   0.0092  &  0.0001  &  0.0001 \\  \hline
+ n & 110756  &  65536  &  16056  &  2550  &  1024  &  1024 \\ \hline
+ \text{error } 10^{-3} & 0.0366 &  0.0413  &  0.0856 & 0.0838  &  0.0022  &  0.0028 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     100  & 100  & 93  & 100  &  100  & 100 \\
+     98  &  99  &  98 &  100  & 100 &  100
+\end{array}
+\]
+
+\subsubsection{Without small indices estimator}
+Bratley et al. example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.6530 & 0.1790 & 0.0370 & 0.0133 & 0.0014 & 0.0015 \\ \hline
+ n & 524288 & 262144  &  222822 & 131072 & 57190 & 64901 \\ \hline
+ \text{error } 10^{-3} & 0.0275 & 0.0592 & 0.0536 & 0.0667 &  0.2030 & 0.1180 \\ \hline
+ \widehat{\overline{S}}_u & 0.7400 & 0.2660 & 0.0764 & 0.0343 & 0.0060 & 0.0062 \\  \hline
+ n & 262144 & 131072 &  65536 &  39322 & 4710 & 6339 \\ \hline
+ \text{error } 10^{-3} & 0.0781 & 0.0371 & 0.1090 & 0.2150 &  0.4850 & 0.1740 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     100  & 100  & 100  & 100  &  97  & 99 \\
+     100  & 100  & 100  &  99  &  88  &  98
+\end{array}
+\]
+
+Sobol g-function example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.5870 & 0.2610 & 0.0367 &  0.0059 & 0.0004 & 0.0004 \\ \hline
+ n & 131072 & 131072 & 63898 & 19825 & 1024 & 1024 \\ \hline
+ \text{error } 10^{-3} & 0.0280 & 0.0262 & 0.0476 & 0.0736 & 0.3390 & 0.3440 \\ \hline
+ \widehat{\overline{S}}_u & 0.6900 & 0.3560 & 0.0563 & 0.0092 & 0.0001 &  0.0001 \\  \hline
+ n & 105513 & 65536 & 16056 & 2703 & 1024 & 1024 \\ \hline
+ \text{error } 10^{-3} & 0.0507 & 0.0442 & 0.1270 & 0.0703 & 0.0022 & 0.0027 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     100  & 100  & 99  & 100  &  100  & 100 \\
+     98  &  99  &  97 &  100  & 100 &  100
+\end{array}
+\]
+
+\subsubsection{Replicated method}
+Bratley et al. example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.6530 & 0.1790 & 0.0370 & 0.0133 & 0.0014 & 0.0015 \\ \hline
+ n & 524288 & 262144  &  222822 & 131072 & 57190 & 64901 \\ \hline
+ \text{error } 10^{-3} & 0.0275 & 0.0592 & 0.0536 & 0.0667 &  0.2030 & 0.1180 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     100  & 100  & 100  & 100  &  97  & 99
+\end{array}
+\]
+
+Sobol g-function example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.5870 & 0.2610 & 0.0367 &  0.0059 & 0.0004 & 0.0004 \\ \hline
+ n & 131072 & 131072 & 63898 & 19825 & 1024 & 1024 \\ \hline
+ \text{error } 10^{-3} & 0.0280 & 0.0262 & 0.0476 & 0.0736 & 0.3390 & 0.3440 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     100  & 100  & 99  & 100  &  100  & 100
+\end{array}
+\]
+
 \subsection{Real case model}
-\label{sec:5.1}
+\label{sec:5.2}
 %The Brownian motion is widely used in many applications.
@@
 Thus, in order to estimate the expected value on a continuous time Browninan motion, one could either use a multilevel method, or a multivariate decomposition method to estimate this infinite dimensional integral.
-
-\subsection{Classical test functions}
-\label{sec:5.2}
 

### 2016-09-22 FunctionsTest/SI_all_example.m

@@ -1,8 +1,8 @@
 clearvars
 
-abstol = 5*1e-3;
+abstol = 1*1e-3;
 reltol = 0e-2; % Pure absolute tolerance
-mmin = 9;
+mmin = 10;
 mmax = 24; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
 wronga = 0; % Wrong estimates with all indices method
 wrong = 0; % Wrong estimates using the one by one algo

### 2016-09-22 FunctionsTest/SI_all_example_percentage.m

@@ -1,0 +1,66 @@
+clearvars
+
+abstol = 1*1e-3;
+pre = 3; % Precision to display according to 1*1e-3 (3 digits)
+reltol = 0e-2; % Pure absolute tolerance
+mmin = 10;
+mmax = 24; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
+wronga = 0; % Wrong estimates with all indices method
+wrong = 0; % Wrong estimates using the one by one algo
+s = .0; %time in seconds used delay each function evaluation
+samples = 100;
+
+fudge = @(m,d) 10*2.^-(.9*m);
+
+%% Bratley et al.
+disp('Running Bratley et al. example ...')
+d = 6;
+f = @(x) sum(bsxfun(@times, cumprod(x,2), (-1).^(1:d)),2) +  pause_t(s);
+hyperbox = [-zeros(1,d) ; ones(1,d)];
+
+R = [.6528636616, .1791303924, 0.3701041165e-1, 0.1332374820e-1, 0.1480416466e-2, 0.1480416466e-2; .7396477462, .2659144770, 0.764211693e-1, 0.343115454e-1, 0.62384628e-2, 0.62384628e-2];
+SI = zeros(2, d);
+SI_n = SI;
+error = SI;
+reliability = SI;
+for k = 1:samples
+    [q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d));
+    SI = SI + q;
+    SI_n = SI_n + out_param.n;
+    error = error + abs(R-q);
+    reliability = reliability + 1*(abs(R-q) > max(abstol,R*reltol));
+end
+SI = SI/samples; SI_n = SI_n/samples; reliability = 1 - reliability/samples; error = error/samples;
+round(SI, pre, 'significant')
+round(SI_n)
+round(error, pre, 'significant')
+round(reliability*100)
+
+
+%% Sobol' g-function
+disp('Running Sobol g-function example ...')
+d = 6;
+a = [0 1/2 3 9 99 99];
+f = @(x) prod(bsxfun(@(x,a) (abs(4*x-2)+a)./(1+a), x , a),2) +  pause_t(s);
+hyperbox = [zeros(1,d) ; ones(1,d)];
+
[…]

### 2016-09-22 FunctionsTest/SI_fo_example_percentage.m

@@ -1,0 +1,66 @@
+clearvars
+
+abstol = 1*1e-3;
+pre = 3; % Precision to display according to 1*1e-3 (3 digits)
+reltol = 0e-2; % Pure absolute tolerance
+mmin = 10;
+mmax = 24; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
+wronga = 0; % Wrong estimates with all indices method
+wrong = 0; % Wrong estimates using the one by one algo
+s = .0; %time in seconds used delay each function evaluation
+samples = 1;
+
+fudge = @(m,d) 10*2.^-(1.*m);
+
+%% Bratley et al.
+disp('Running Bratley et al. example ...')
+d = 6;
+f = @(x) sum(bsxfun(@times, cumprod(x,2), (-1).^(1:d)),2) +  pause_t(s);
+hyperbox = [-zeros(1,d) ; ones(1,d)];
+
+R = [.6528636616, .1791303924, 0.3701041165e-1, 0.1332374820e-1, 0.1480416466e-2, 0.1480416466e-2];
+SI = zeros(1, d);
+SI_n = SI;
+error = SI;
+reliability = SI;
+for k = 1:samples
+    [q,app_int,out_param] = cubSobol_SI_fo_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d));
+    SI = SI + q;
+    SI_n = SI_n + out_param.n;
+    error = error + abs(R-q);
+    reliability = reliability + 1*(abs(R-q) > max(abstol,R*reltol));
+end
+SI = SI/samples; SI_n = SI_n/samples; reliability = 1 - reliability/samples; error = error/samples;
+round(SI, pre, 'significant')
+round(SI_n)
+round(error, pre, 'significant')
+round(reliability*100)
+
+
+%% Sobol' g-function
+disp('Running Sobol g-function example ...')
+d = 6;
+a = [0 1/2 3 9 99 99];
+f = @(x) prod(bsxfun(@(x,a) (abs(4*x-2)+a)./(1+a), x , a),2) +  pause_t(s);
+hyperbox = [zeros(1,d) ; ones(1,d)];
+
+R = [.5867811893, .2607916397, 0.3667382378e-1, 0.5867811312e-2, 0.5867753221e-4, 0.5867753221e-4];
+SI = zeros(1, d);
+SI_n = SI;
[…]

### 2016-09-22 FunctionsTest/cubSobol_SI_all_g.m

@@ -361,6 +361,7 @@ for u = 1:out_param.d
         INDICES(1,u).err_bound_int = err_bound_int_fx2_fx(:,1); %initialize error estimates for each integral in the numerator
         INDICES(1,u).y = INDICES(1,u).f{1}(xpts,u,fx,fy,fxy,fzx); % We reevaluate the points if we change the estimator
         out_param.small(1,u) = 1;
+        fzx = [];
     end
     INDICES(2,u).y = INDICES(2,u).f{1}(xpts,u,fx,fy,fxy,0);
     INDICES(1,u).est_int = mean(INDICES(1,u).y, 1); % Estimate the integral
@@ -627,6 +628,7 @@ for m = out_param.mmin+1:out_param.mmax
                 for func = 1:size(INDICES(r,u).f, 2)
                     ynext = [ynext INDICES(r,u).f{func}(xnext,u,fxval(end/2 + 1:end),fy,fxy,fzx)];
                 end
+                fzx = [];
                 INDICES(r,u).est_int(meff, :) = 1/2*(INDICES(r,u).est_int(meff-1, :) + mean(ynext, 1)); % Estimate the integral
 
                %% Compute initial FWT on next points only for y

### 2016-09-23 article/template.tex
Adding the new tables with results including csv files with errors.

--- 2016-08-30 article/template.tex
@@
 \label{sec:5}
+
+\subsection{Classical test functions}
+\label{sec:5.1}
+
+$\varepsilon=0.005$, initial $512$ points, $fudge = @(m,d) 10*2.^{-m}$, run $100$ samples and show the average values for the whole set of samples:
+
+(We use the scrambled replicated points, should we mention that somewhere and explain the requirement? Replicated points should share the same scrambling, u and u+d)
+
+\subsubsection{Without small indices estimator}
+Bratley et al. example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.6500 & 0.1800 & 0.0370 & 0.0120 & 0.0034 & 0.0033 \\ \hline
+ n & 17531 & 8438 & 4137 & 3686 & 625 & 650\\ \hline
+ \text{error } & 0.0004 & 0.0006 & 0.0058 & 0.0022 & 0.0024 & 0.0021 \\ \hline
+ \widehat{\overline{S}}_u & 0.7400 & 0.2700 & 0.0760 & 0.0340 & 0.0065 & 0.0064 \\  \hline
+ n & 16384 & 8192 & 3113 & 1060 & 512 & 512 \\ \hline
+ \text{error } & 0.0003 & 0.0004 & 0.0012 & 0.0020 & 0.0014 & 0.0010 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     100  & 100  & 29  & 88  &  89  & 94 \\
+     100  & 100  & 98  &  93  &  97  &  100
+\end{array}
+\]
+
+Sobol g-function example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.5900 & 0.2600 & 0.0370 & 0.0060 & 0.0003 & 0.0003 \\ \hline
+ n & 16138 & 9011 & 3748 & 891 & 512 & 512 \\ \hline
+ \text{error } & 0.0004 & 0.0006 & 0.0011 & 0.0012 & 0.0003 & 0.0003 \\ \hline
+ \widehat{\overline{S}}_u & 0.6900 & 0.3600 & 0.0560 & 0.0093 & 0.0001 & 0.0001 \\  \hline
+ n & 11796 & 7496 & 1475 & 512 & 512 & 512 \\ \hline
+ \text{error } & 0.0005 & 0.0004 & 0.0008 & 0.0003 & 0.0000 & 0.0000 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     98  & 98  & 97  & 98  &  100  & 100 \\
+     98  &  100  &  100 &  100  & 100 &  100
+\end{array}
+\]
+
+\subsubsection{With small indices estimator (threshold $0.1$)}
+Bratley et al. example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.6500 & 0.1800 & 0.0380 & 0.0140 & 0.0014 & 0.0016 \\ \hline
+ n & 17203 & 8520 & 1362 & 517 & 512 & 512 \\ \hline
+ \text{error } & 0.0004 & 0.0006 & 0.0019 & 0.0016 & 0.0003 & 0.0004 \\ \hline
+ \widehat{\overline{S}}_u & 0.7400 & 0.2700 & 0.0760 & 0.0340 & 0.0063 & 0.0065 \\  \hline
+ n & 16384 & 8192 & 2847 & 1142 & 512 & 512 \\ \hline
+ \text{error } & 0.0003 & 0.0005 & 0.0013 & 0.0017 & 0.0015 & 0.0011 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     100  & 100  & 96  & 99  &  100  & 100 \\
+     100  & 100  & 99  &  98  &  96  &  100
+\end{array}
+\]
+
+Sobol g-function example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.5900 & 0.2600 & 0.0370 & 0.0060 & 0.0001 & 0.0001 \\ \hline
+ n & 16056 & 8929 & 1070 & 512 & 512 & 512 \\ \hline
+ \text{error } & 0.0005 & 0.0007 & 0.0015 & 0.0003 & 0.0000 & 0.0000 \\ \hline
+ \widehat{\overline{S}}_u & 0.6900 & 0.3600 & 0.0560 & 0.0093 & 0.0001 & 0.0001 \\  \hline
+ n & 11551 & 7741 & 1464 & 512 & 512 & 512 \\ \hline
+ \text{error } & 0.0006 & 0.0003 & 0.0009 & 0.0003 & 0.0000 & 0.0000 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     97  & 97  & 95  & 100  &  100  & 100 \\
+     98  &  100  &  100 &  100  & 100 &  100
+\end{array}
+\]
+
+\subsubsection{Replicated method}
+Bratley et al. example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.6500 & 0.1800 & 0.0370 & 0.0100 & 0.0038 & 0.0040 \\ \hline
+ n & 32768 & 16384 & 16384 & 12447 & 8637 & 9196 \\ \hline
+ \text{error } & 0.0003 & 0.0006 & 0.0010 & 0.0038 & 0.0024 & 0.0026 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     100  & 100  & 100  & 75  &  100  & 100
+\end{array}
+\]
+
+Sobol g-function example:
+
+\[
+\begin{array}{lcccccc}
+   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+ \widehat{\underline{S}}_u & 0.5900 & 0.2600 & 0.0360 & 0.0059 & 0.0031 & 0.0036 \\ \hline
+ n & 16384 & 16384 & 16225 & 14612 & 7086 & 6661 \\ \hline
+ \text{error } & 0.0011 & 0.0013 & 0.0018 & 0.0013 & 0.0031 & 0.0036 \\ \hline
+\end{array}
+\]
+Reliability on the results,
+\[
+\begin{array}{ cccccc }
+     93  & 92  & 91  & 90  &  96  & 95
+\end{array}
+\]
+
 \subsection{Real case model}
-\label{sec:5.1}
+\label{sec:5.2}
 %The Brownian motion is widely used in many applications.
@@
 
-\subsection{Classical test functions}
-\label{sec:5.2}
+\section{Conclusions}
 

### 2016-09-23 FunctionsTest/SI_all_example_percentage.m

@@ -1,16 +1,17 @@
 clearvars
 
-abstol = 1*1e-3;
-pre = 3; % Precision to display according to 1*1e-3 (3 digits)
+abstol = 5*1e-3;
+pre = 2; % Precision to display according to 1*1e-3 (3 digits)
 reltol = 0e-2; % Pure absolute tolerance
-mmin = 10;
+mmin = 9;
 mmax = 24; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
+threshold_small = 0.; % Below which sizes do we use correl2 estimator
 wronga = 0; % Wrong estimates with all indices method
 wrong = 0; % Wrong estimates using the one by one algo
 s = .0; %time in seconds used delay each function evaluation
 samples = 100;
 
-fudge = @(m,d) 10*2.^-(.9*m);
+fudge = @(m,d) 10*2.^-(1.*m);
 
 %% Bratley et al.
 disp('Running Bratley et al. example ...')
@@ -23,11 +24,13 @@ SI = zeros(2, d);
 SI_n = SI;
 error = SI;
 reliability = SI;
+error_all = [];
 for k = 1:samples
-    [q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d));
+    [q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d), 'threshold_small', threshold_small);
     SI = SI + q;
     SI_n = SI_n + out_param.n;
     error = error + abs(R-q);
+    error_all = [error_all; abs(R-q)];
     reliability = reliability + 1*(abs(R-q) > max(abstol,R*reltol));
 end
 SI = SI/samples; SI_n = SI_n/samples; reliability = 1 - reliability/samples; error = error/samples;
@@ -36,6 +39,11 @@ round(SI_n)
 round(error, pre, 'significant')
 round(reliability*100)
 
+% if threshold_small == 0
+%     csvwrite('bratley_non_small.csv', error_all)
+% else
+%     csvwrite('bratley_with_small.csv', error_all)
+% end
 
 %% Sobol' g-function
 disp('Running Sobol g-function example ...')
[…]

### 2016-09-23 FunctionsTest/SI_fo_example_percentage.m

@@ -1,14 +1,14 @@
 clearvars
 
-abstol = 1*1e-3;
-pre = 3; % Precision to display according to 1*1e-3 (3 digits)
+abstol = 5*1e-3;
+pre = 2; % Precision to display according to 1*1e-3 (3 digits)
 reltol = 0e-2; % Pure absolute tolerance
-mmin = 10;
+mmin = 9;
 mmax = 24; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
 wronga = 0; % Wrong estimates with all indices method
 wrong = 0; % Wrong estimates using the one by one algo
 s = .0; %time in seconds used delay each function evaluation
-samples = 1;
+samples = 100;
 
 fudge = @(m,d) 10*2.^-(1.*m);
 
@@ -23,11 +23,13 @@ SI = zeros(1, d);
 SI_n = SI;
 error = SI;
 reliability = SI;
+error_all = [];
 for k = 1:samples
     [q,app_int,out_param] = cubSobol_SI_fo_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d));
     SI = SI + q;
     SI_n = SI_n + out_param.n;
     error = error + abs(R-q);
+    error_all = [error_all; abs(R-q)];
     reliability = reliability + 1*(abs(R-q) > max(abstol,R*reltol));
 end
 SI = SI/samples; SI_n = SI_n/samples; reliability = 1 - reliability/samples; error = error/samples;
@@ -35,6 +37,9 @@ round(SI, pre, 'significant')
 round(SI_n)
 round(error, pre, 'significant')
 round(reliability*100)
+
+% csvwrite('bratley_replicated.csv', error_all)
+
 
 
 %% Sobol' g-function
@@ -49,11 +54,13 @@ SI = zeros(1, d);
 SI_n = SI;
 error = SI;
 reliability = SI;
+error_all = [];
 for k = 1:samples
     [q,app_int,out_param] = cubSobol_SI_fo_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d));
     SI = SI + q;
     SI_n = SI_n + out_param.n;
     error = error + abs(R-q);
+    error_all = [error_all; abs(R-q)];
[…]

### 2016-09-23 FunctionsTest/cubSobol_SI_all_g.m

@@ -99,6 +99,9 @@ function [q,int,out_param] = cubSobol_SI_all_g(varargin)
 %     theta*abstol+(1-theta)*reltol*| integral(f) |. Note that for theta = 1, 
 %     we have pure absolute tolerance while for theta = 0, we have pure 
 %     relative tolerance. By default, theta=1.
+% 
+%     in_param.threshold_small --- this input is the size at which we use
+%     the small indices estimator instead of the usual. By default is 0.1.
 %
 %   Output Arguments
 %
@@ -227,7 +230,6 @@ function [q,int,out_param] = cubSobol_SI_all_g(varargin)
 t_start = tic;
 %% Initial important cone factors and Check-initialize parameters
 r_lag = 4; %distance between coefficients summed and those computed
-threshold_small = 0.1; % Threshold for changing the estimators for small indices
 [f,hyperbox,out_param] = cubSobol_SI_all_g_param(r_lag,varargin{:});
 out_param.small = false(2, out_param.d); % Boolean that states whether we are dealing with small indices estimators
 converged = false(2, out_param.d); % We flag the indices that converged
@@ -346,7 +348,7 @@ for u = 1:out_param.d
         INDICES(1,u).y = [INDICES(1,u).y INDICES(1,u).f{p}(xpts,u,fx,fy,fxy,0)];
     end
     aux_double = INDICES(1,u).Smin([mean(INDICES(1,u).y, 1) mean(fx2) mean(fx)],[mean(INDICES(1,u).y, 1) mean(fx2) mean(fx)]);
-    if aux_double < threshold_small % If the normalized first order index is small, we change to a better estimator estimator
+    if aux_double < out_param.threshold_small % If the normalized first order index is small, we change to a better estimator estimator
         if isempty(fzx)
             fzx = f([xpts(:,1:u-1) xpts(:,2*out_param.d + u) xpts(:,u+1:out_param.d)]);
         end
@@ -763,6 +765,7 @@ default.mmax  = 24;
 default.fudge = @(m) 5*2.^-m;
 default.toltype  = 'max';
 default.theta  = 1;
+default.threshold_small = 0.1;
 
 if numel(varargin)<2
     help cubSobol_SI_all_g
@@ -821,6 +824,7 @@ if ~validvarargin
     out_param.fudge = default.fudge;
     out_param.toltype = default.toltype;
     out_param.theta = default.theta;
+    out_param.threshold_small = default.threshold_small;
 else
[…]

### 2016-09-23 FunctionsTest/cubSobol_SI_fo_g.m

@@ -250,8 +250,10 @@ Sfo_max = @(down, up) estimate_max([down(1) 0 down(2:end)], [up(1) 0 up(2:end)])
 ffo = @(fx,fy,fxy) fx.*(fxy - fy);
 
 %% Main algorithm (we added 2xd dimensions for each index and and additional 2 for mean of f and f^2)
-sobstr = sobolset(2*out_param.d); %generate a Sobol' sequence 3*d to consider the changing to the estimator for some smaller size indices
-% sobstr = scramble(sobstr,'MatousekAffineOwen'); %scramble it
+sobstr = sobolset(2*out_param.d); %generate a Sobol' sequence 2*d
+sobstr_scr = sobolset(out_param.d); % This will be the first scrambled sequence...
+    % The replicated sequence will have to use the same scrambling
+sobstr_scr = scramble(sobstr_scr,'MatousekAffineOwen'); %scramble it
 kappanumap_fx2_fx = bsxfun(@times,(1:2^out_param.mmin)', [1 1]); %initialize map
 Stilde_fx2_fx = zeros(out_param.mmax-out_param.mmin+1, 2); %initialize sum of DFWT terms for fx2 and fx
 CStilde_low_fx2_fx = -inf(out_param.mmax-l_star+1, 2); %initialize various sums of DFWT terms for necessary conditions for fx2 and fx
@@ -282,36 +284,47 @@ end
 
 
 %% Initial points and FWT
-out_param.n = 2^out_param.mmin*ones(1,out_param.d); %total number of points to start with
-n0 = out_param.n(1); %initial number of points
-xpts = sobstr(1:n0,1:2*out_param.d); %grab Sobol' points
-fx = f(xpts(:,1:out_param.d)); %evaluate integrands y3
-fx2 = fx.^2; %evaluate integrands y2
-fxval = fx; % We store fx because fx will later contain the fast transform
-fx2val = fx2; % We store fx2 because fx2 will later contain the fast transform
-% We only need fy if we use the estimator that includes ffo
-fy = [];
-if numerator_size == 1
-    fy = f(xpts(:,out_param.d+1:2*out_param.d)); % We evaluate the f at the replicated points
-end
 
 %% In this section we apply the replicated method
 % For the replication method, we want to sort dimension u+d with the same
 % order as dimension u. In other words, if dimension u is sorted according
 % to permutation tau and u+d according to sigma, we want to find psi such
[…]

### 2016-09-23 article/Images/article_scheme_S_3D.m

@@ -106,6 +106,11 @@ yy = ones(n,1)*(I(2)+err(2)+width);
 zz = ones(n,1)*(Smin+Smax)/2; %S(I(1)-err(1), I(2)-err(2))
 plot3(xx, yy, zz, 'k.', 'Linewidth', .5)
 
+xx = linspace(I(1)-err(1)-width, I(1)+err(1)+width, n)'; % Axis line for (Smin+Smax)/2 line
+yy = ones(n,1)*(I(2)+err(2)+width); 
+zz = ones(n,1)*(Smin+Smax)/2; %S(I(1)-err(1), I(2)-err(2))
+plot3(xx, yy, zz, 'k.', 'Linewidth', .5)
+
 axis([xmin xmax ymin ymax zmin zmax*1.01 ])
 
 %area(I - err:0.02:I + err, S(I - err:0.02:I + err))

### 2016-09-27 article/template.tex
changes L, section 5

--- 2016-08-30 article/template.tex
@@
 \usepackage{algpseudocode}
+\usepackage{booktabs}
+\usepackage{multirow}
 \usepackage{url}
@@
 To overcome this issue, we propose the following alternative for Variant $A$.
-If at the end of the first iteration, the estimate $\widehat{\underline{S}}_u$, $u \in \mathcal{D}$, is smaller than a threshold (here $0.1$), then at the next iteration estimator (\ref{first.order.est}) is switched for ``Correlation 2" and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+If at the end of the first iteration, the estimate $\widehat{\underline{S}}_u$, $u \in \mathcal{D}$, is smaller than a threshold (here $0.1$), then estimator (\ref{first.order.est}) is switched for ``Correlation 2" and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
 
@@
 \label{sec:5}
+
+We propose to illustrate our sequential estimation procedure on two classical test functions and one real model. For each case, we compare results obtained with each of the three methods:
+\begin{itemize}
+\item[$\bullet$] Variant $A$ without using ``Correlation 2'', refers as Variant $A.a$, 
+\item[$\bullet$] Variant $A$ using ``Correlation 2'', refers as Variant $A.b$,
+\item[$\bullet$] Variant $B$.
+\end{itemize}
+The threshold to decide whether or not a first-order index is small is set to $0.1$.
+
+The comparison is based on error bounds, namely $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$, and total number of evaluations.
+Boxplots of error bounds are provided to support tables of results.
+Results are averaged over $r=100$ repeats.
+For each repeat, we fix the tolerance $\varepsilon$ to $5.10^{-3}$ and set the starting size $m_0$ to $2^9$ (the Sobol' sequences are initiated with $512$ points).
+
+We also evaluate the failure rate over the $100$ repeats that is the ratio of error bounds failing to satisfy respectively $\varepsilon_{\underline{S}_u} \leq \varepsilon$ and $\varepsilon_{\underline{S}_u} \leq \varepsilon$.
+Failure rates are denoted by ${err}_{\varepsilon_{\underline{S}_u}}$ and  ${err}_{\varepsilon_{\overline{S}_u}}$.
+
+%$\varepsilon=0.005$, initial $512$ points, $fudge = @(m,d) 10*2.^{-m}$, run $100$ samples and show the average values for the whole set of samples:
+%
+%(We use the scrambled replicated points, should we mention that somewhere and explain the requirement? Replicated points should share the same scrambling, u and u+d)
+
+\subsection{Classical test functions}
+\label{sec:5.1}
+
+The two classical test functions considered are the g-function introduced by Sobol' \cite{Sobol'} and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
+The idea is to test our method over two categories of functions: additive (g-function) and multiplicative (Bratley \textit{et al.} function).
+
+\subsubsection{Sobol' g-function}
+
+The g-function is defined as follows:
+\begin{equation*}
+f(\vx)= \prod \limits_{i=1}^{d}g_i(x_i), \qquad g_i(x_i)=\frac{\left |4x_i-2 \right | + a_i}{1 + a_i}, \ a_i \geq 0.
+\end{equation*}
+Each value $a_i$ determines the relative importance of the $x_i$.
+When the value of $a_i$ gets closer to zero the variable $x_i$ becomes more influential.
+Here, the dimension is $d=6$ and values chosen for the $a_i$ are given by the following vector $(a_1=0,=a_2=0.5, a_3=3, a_4=9, a_5=99$, $a_6=99)$.
+
+Table \ref{res.gfunc.Aa} shows the averaged error bounds obtained with Variant $A.a$ as well as the averaged total number of evaluations performed.
+Table \ref{res.gfunc.Ab} shows the same results obtained with Variant $A.b$.
+\renewcommand{\arraystretch}{1.3}
+\begin{table}[!ht]
+\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ obtained with Variant $A.a$ over $100$ repeats.
+Failure rates are denoted by ${err}_{\varepsilon_{\underline{S}_u}}$ and  ${err}_{\varepsilon_{\overline{S}_u}}$.}
+\centering
+\begin{tabular}{ccccccc}
+\hline
+ input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ & $\overline{S}_u$ & $\varepsilon_{\overline{S}_u}$ &$err_{\varepsilon_{\overline{S}_u}}$ \\ \hline
+ $x_1$ & $0.5868$ &  $0.0004$ & $0.02$ & $0.6901$ & $0.0005$ & $0.02$ \\ \hline
+ $x_2$ & $0.2608$ &  $0.0006$ & $0.02$ & $0.3562$ & $0.0004$ & $0$ \\ \hline
+ $x_3$ & $0.0367$ &  $0.0011$ & $0.03$ & $0.0563$ & $0.0008$ & $0$ \\ \hline
+ $x_4$ & $0.0058$ &  $0.0012$ & $0.02$ & $0.0092$ & $0.0003$ & $0$ \\ \hline
+ $x_5$ & $5.10^{-5}$ & $0.0003$ & $0$ & $9.10^{-5}$ & $0.0000$ & $0$ \\ \hline
+ $x_6$ & $5.10^{-5}$ & $0.0003$ & $0$  & $9.10^{-5}$ & $0.0000$ & $0$ \\ \hline \hline
+\multicolumn{4}{l}{Total number of evaluations: $63 \ 088$} & & &\\ \hline 
+\end{tabular}
+\label{res.gfunc.Aa}
+\end{table}
+\begin{table}[!ht]
+\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ obtained with Variant $A.b$ over $100$ repeats.
+Failure rates are denoted by ${err}_{\varepsilon_{\underline{S}_u}}$ and  ${err}_{\varepsilon_{\overline{S}_u}}$.}
+\centering
+\begin{tabular}{ccccccc}
+\hline
+ input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ & $\overline{S}_u$ & $\varepsilon_{\overline{S}_u}$ &$err_{\varepsilon_{\overline{S}_u}}$ \\ \hline
+ $x_1$ & $0.5868$ &  $0.0005$ & $0.03$ & $0.6901$ & $0.0006$ & $0.02$ \\ \hline
+ $x_2$ & $0.2608$ &  $0.0007$ & $0.03$ & $0.3562$ & $0.0003$ & $0$ \\ \hline
+ $x_3$ & $0.0367$ &  $0.0015$ & $0.05$ & $0.0563$ & $0.0009$ & $0$ \\ \hline
+ $x_4$ & $0.0058$ &  $0.0003$ & $0$ & $0.0092$ & $0.0003$ & $0$ \\ \hline
+ $x_5$ & $5.10^{-5}$ & $0.0000$ & $0$ & $9.10^{-5}$ & $0.0000$ & $0$ \\ \hline
+ $x_6$ & $5.10^{-5}$ & $0.0000$ & $0$  & $9.10^{-5}$ & $0.0000$ & $0$ \\ \hline \hline
+\multicolumn{4}{l}{Total number of evaluations: $62 \ 703$} & & &\\ \hline 
+\end{tabular}
+\label{res.gfunc.Ab}
+\end{table}
+
+The main observation is that both approaches give similar results both in terms of error bounds and total number of evaluations.
+Looking at those averaged results, the use of ``Correlation 2'' to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ does not seems to bring any improvements.
+We propose to draw boxplots to further investigate the results.
+
+Figure \ref{boxplots.gfunc} shows boxplots of the $100$ error bounds $\varepsilon_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and $A.b$.
+\begin{figure}[!ht]
+\caption{Boxplots of error bounds $\varepsilon_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and $A.b$.}
+\centering
+\includegraphics[width=0.45\textwidth]{Images/boxplots.pdf}
+\label{boxplots.gfunc}
+\end{figure}
+As expected, the use of ``Correlation 2'' in Variant $A.b$ allows to obtain better error bounds.
+The discrepancy observed does not show off in Table \ref{res.gfunc.Ab} due to its low magnitude varying between $10^{-4}$ and $10^{-5}$.
+\bigskip
+
+Table \ref{res.gfunc.B} shows the averaged error bounds $\varepsilon_{\underline{S}_u}$ obtained with Variant $B$ and the averaged total number of evaluations performed. 
+\begin{table}[!ht]
+\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$  obtained with Variant $B$ over $100$ repeats. Failure rate is denoted by ${err}_{\varepsilon_{\underline{S}_u}}$.}
+\centering
+\begin{tabular}{cccc}
+\hline
+ input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ \\ \hline
+ $x_1$ & $0.5868$ &  $0.0011$ & $0.07$ \\ \hline
+ $x_2$ & $0.2608$ &  $0.0013$ & $0.08$ \\ \hline
+ $x_3$ & $0.0367$ &  $0.0018$ & $0.09$ \\ \hline
+ $x_4$ & $0.0058$ &  $0.0013$ & $0.1$    \\ \hline
+ $x_5$ & $5.10^{-5}$ & $0.0031$ & $0.04$  \\ \hline
+ $x_6$ & $5.10^{-5}$ & $0.0036$ & $0.05$  \\ \hline \hline
+\multicolumn{4}{l}{Total number of evaluations: $32 \ 768$}\\ \hline 
+\end{tabular}
+\label{res.gfunc.B}
+\end{table}
+Looking at the results, using Variant $B$ leads to higher failure rates than those obtained with Variant $A.a$ or $A.b$.
+The compromise is a total number of evaluations twice as small as the others two variants.
+As such, this approach remains interesting when one want to estimate only first-order indices.
+
+\subsubsection{Bratley et al. function}
+%
+%\subsubsection{Without small indices estimator}
+%Bratley et al. example:
+%
+%\[
+%\begin{array}{lcccccc}
+%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+% \widehat{\underline{S}}_u & 0.6500 & 0.1800 & 0.0370 & 0.0120 & 0.0034 & 0.0033 \\ \hline
+% n & 17531 & 8438 & 4137 & 3686 & 625 & 650\\ \hline
+% \text{error } & 0.0004 & 0.0006 & 0.0058 & 0.0022 & 0.0024 & 0.0021 \\ \hline
+% \widehat{\overline{S}}_u & 0.7400 & 0.2700 & 0.0760 & 0.0340 & 0.0065 & 0.0064 \\  \hline
+% n & 16384 & 8192 & 3113 & 1060 & 512 & 512 \\ \hline
+% \text{error } & 0.0003 & 0.0004 & 0.0012 & 0.0020 & 0.0014 & 0.0010 \\ \hline
+%\end{array}
+%\]
+%Reliability on the results,
+%\[
+%\begin{array}{ cccccc }
+%     100  & 100  & 29  & 88  &  89  & 94 \\
+%     100  & 100  & 98  &  93  &  97  &  100
+%\end{array}
+%\]
+%
+%
+%Sobol g-function example:
+%
+%\[
+%\begin{array}{lcccccc}
+%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+% \widehat{\underline{S}}_u & 0.5900 & 0.2600 & 0.0370 & 0.0060 & 0.0003 & 0.0003 \\ \hline
+% n & 16138 & 9011 & 3748 & 891 & 512 & 512 \\ \hline
+% \text{error } & 0.0004 & 0.0006 & 0.0011 & 0.0012 & 0.0003 & 0.0003 \\ \hline
+% \widehat{\overline{S}}_u & 0.6900 & 0.3600 & 0.0560 & 0.0093 & 0.0001 & 0.0001 \\  \hline
+% n & 11796 & 7496 & 1475 & 512 & 512 & 512 \\ \hline
+% \text{error } & 0.0005 & 0.0004 & 0.0008 & 0.0003 & 0.0000 & 0.0000 \\ \hline
+%\end{array}
+%\]
+%Reliability on the results,
+%\[
+%\begin{array}{ cccccc }
+%     98  & 98  & 97  & 98  &  100  & 100 \\
+%     98  &  100  &  100 &  100  & 100 &  100
+%\end{array}
+%\]
+%
+%\subsubsection{With small indices estimator (threshold $0.1$)}
+%Bratley et al. example:
+%
+%\[
+%\begin{array}{lcccccc}
+%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+% \widehat{\underline{S}}_u & 0.6500 & 0.1800 & 0.0380 & 0.0140 & 0.0014 & 0.0016 \\ \hline
+% n & 17203 & 8520 & 1362 & 517 & 512 & 512 \\ \hline
+% \text{error } & 0.0004 & 0.0006 & 0.0019 & 0.0016 & 0.0003 & 0.0004 \\ \hline
+% \widehat{\overline{S}}_u & 0.7400 & 0.2700 & 0.0760 & 0.0340 & 0.0063 & 0.0065 \\  \hline
+% n & 16384 & 8192 & 2847 & 1142 & 512 & 512 \\ \hline
+% \text{error } & 0.0003 & 0.0005 & 0.0013 & 0.0017 & 0.0015 & 0.0011 \\ \hline
+%\end{array}
+%\]
+%Reliability on the results,
+%\[
+%\begin{array}{ cccccc }
+%     100  & 100  & 96  & 99  &  100  & 100 \\
+%     100  & 100  & 99  &  98  &  96  &  100
+%\end{array}
+%\]
+%
+%
+%Sobol g-function example:
+%
+%\[
+%\begin{array}{lcccccc}
+%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+% \widehat{\underline{S}}_u & 0.5900 & 0.2600 & 0.0370 & 0.0060 & 0.0001 & 0.0001 \\ \hline
+% n & 16056 & 8929 & 1070 & 512 & 512 & 512 \\ \hline
+% \text{error } & 0.0005 & 0.0007 & 0.0015 & 0.0003 & 0.0000 & 0.0000 \\ \hline
+% \widehat{\overline{S}}_u & 0.6900 & 0.3600 & 0.0560 & 0.0093 & 0.0001 & 0.0001 \\  \hline
+% n & 11551 & 7741 & 1464 & 512 & 512 & 512 \\ \hline
+% \text{error } & 0.0006 & 0.0003 & 0.0009 & 0.0003 & 0.0000 & 0.0000 \\ \hline
+%\end{array}
+%\]
+%Reliability on the results,
+%\[
+%\begin{array}{ cccccc }
+%     97  & 97  & 95  & 100  &  100  & 100 \\
+%     98  &  100  &  100 &  100  & 100 &  100
+%\end{array}
+%\]
+%
+%\subsubsection{Replicated method}
+%Bratley et al. example:
+%
+%\[
+%\begin{array}{lcccccc}
+%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+% \widehat{\underline{S}}_u & 0.6500 & 0.1800 & 0.0370 & 0.0100 & 0.0038 & 0.0040 \\ \hline
+% n & 32768 & 16384 & 16384 & 12447 & 8637 & 9196 \\ \hline
+% \text{error } & 0.0003 & 0.0006 & 0.0010 & 0.0038 & 0.0024 & 0.0026 \\ \hline
+%\end{array}
+%\]
+%Reliability on the results,
+%\[
+%\begin{array}{ cccccc }
+%     100  & 100  & 100  & 75  &  100  & 100
+%\end{array}
+%\]
+%
+%
+%Sobol g-function example:
+%
+%\[
+%\begin{array}{lcccccc}
+%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+% \widehat{\underline{S}}_u & 0.5900 & 0.2600 & 0.0360 & 0.0059 & 0.0031 & 0.0036 \\ \hline
+% n & 16384 & 16384 & 16225 & 14612 & 7086 & 6661 \\ \hline
+% \text{error } & 0.0011 & 0.0013 & 0.0018 & 0.0013 & 0.0031 & 0.0036 \\ \hline
+%\end{array}
+%\]
+%Reliability on the results,
+%\[
+%\begin{array}{ cccccc }
+%     93  & 92  & 91  & 90  &  96  & 95
+%\end{array}
+%\]
+
 \subsection{Real case model}
-\label{sec:5.1}
+\label{sec:5.2}
 %The Brownian motion is widely used in many applications.
@@
 %
+
+\bibitem{Bratley}
+Bratley, P., Fox, B.L., Niederreiter, H.: Implementation and tests of low-discrepancy sequences, ACM Trans. Model. Comput. Simul. \textbf{2}(3), 195-213 (1992)
+Hickernell, F.J., Jim\'enez Rugama, Ll.A.: Reliable Adaptative Cubature Using Digital Sequences: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 367-383 (2016)
 \bibitem{Gilquin.rec}

### 2016-09-27 article/article_for_submission.tex
Changes to add the Asian option example in the article

--- 2016-09-27 article/template.tex
@@
 \label{sec:5.2}
-%The Brownian motion is widely used in many applications.
+As a real case example, we will study the payoff function of an arithmetic mean Asian call option.
+
+For a discretized Brownian motion $\vect{B}=(B_{t_1}, B_{t_2},\dots, B_{t_d})$ at given times $t_1,\dots,t_d$, the payoff of the option is:
+
+\[
+f_{\rm payoff}(\vect{B}) = \max\left(\frac{1}{d}\sum_{i=1}^d S_0\e^{(r-\sigma^2/2)t_i+\sigma B_{t_i}}-K, 0\right)
+\]
+
+The Brownian motion is widely used in many applications.
 Thus, the following example might be interesting to understand what Sobol' indices can explain in some of these applications.
 For instance, if we want to estimate the expected value of the maximum of a discretized Brownian motion whose covariance matrix is $\Sigma$, our goal is to estimate
-%\begin{align*}
-%\mathbb{E} \left[\max(\vect{B}_t)\right] &= \int_{\mathbb{R}^d} \max(\vect{B}_t) \frac{{\rm e}^{\vect{B}_t^T\Sigma^{-1}\vect{B}_t}}{(2\pi)^{d/2}|\Sigma|^{1/2}}\,d\vect{B}_t \\
-%&= \int_{[0,1]^d} \max(f_{\rm Chol}(\vx)) \,d\vx \\
-%&= \int_{[0,1]^d} \max(f_{\rm PCA}(\vx)) \,d\vx.
-%\end{align*}
-%The last two equalities are obtained through two different subsitutions corresponding to the \textit{Cholesky} construction of the Brownian motion, and the \textit{PCA} construction.
+\begin{align*}
+\mathbb{E} \left[\max(\vect{B}_t)\right] &= \int_{\mathbb{R}^d} \max(\vect{B}_t) \frac{{\rm e}^{\vect{B}_t^T\Sigma^{-1}\vect{B}_t}}{(2\pi)^{d/2}|\Sigma|^{1/2}}\,d\vect{B}_t \\
+&= \int_{[0,1]^d} \max(f_{\rm Chol}(\vx)) \,d\vx \\
+&= \int_{[0,1]^d} \max(f_{\rm PCA}(\vx)) \,d\vx.
+\end{align*}
+The last two equalities are obtained through two different subsitutions corresponding to the \textit{Cholesky} construction of the Brownian motion, and the \textit{PCA} construction.
 For instance, if we take 10 dimensions and $t_i=i/10$, using the Cholesky construction $S_{1} = 24\%$, $S_{2} = 16\%$, $S_{3} = 13\%$, $S_{4} = 10\%$, and $\overline{S}_{1}=24\%$, $\overline{S}_{2}=18\%$, $\overline{S}_{3}=15\%$, $\overline{S}_{4} = 13\%$.
@@
 This shows that the PCA construction will be better to estimate the above expectation using quasi-Monte Carlo methods since it has a lower effective dimensionality.
-%
-%For those who were curious about the actual value of $\mathbb{E} \left[\max(\vect{B}_t)\right]$, it is approximately 0.5935.
+
+For those who were curious about the actual value of $\mathbb{E} \left[\max(\vect{B}_t)\right]$, it is approximately 0.5935.
 Nevertheless, the Brownian Motion is a continuous time process.

### 2016-09-27 article/Images/article_scheme_S_3D.m

@@ -102,12 +102,13 @@ a = I(1) + err(1)/2; b = I(2) + err(2)/2;
 % text(a, b, (Smin+Smax)/2, '$(S_{\min}+S_{\max})/2$')
 
 xx = linspace(I(1)-err(1)-width, I(1)+err(1)+width, n)'; % Axis line for (Smin+Smax)/2 line
-yy = ones(n,1)*(I(2)+err(2)+width); 
+yy = ones(n,1)*(ymax); 
 zz = ones(n,1)*(Smin+Smax)/2; %S(I(1)-err(1), I(2)-err(2))
 plot3(xx, yy, zz, 'k.', 'Linewidth', .5)
 
-xx = linspace(I(1)-err(1)-width, I(1)+err(1)+width, n)'; % Axis line for (Smin+Smax)/2 line
-yy = ones(n,1)*(I(2)+err(2)+width); 
+aux = sqrt(abs(xmin - indice/((Smin+Smax)/2)));
+yy = linspace(aux, I(2)+err(2)+width, n)'; % Axis line for (Smin+Smax)/2 line
+xx = ones(n,1)*(xmin);
 zz = ones(n,1)*(Smin+Smax)/2; %S(I(1)-err(1), I(2)-err(2))
 plot3(xx, yy, zz, 'k.', 'Linewidth', .5)
 
@@ -154,5 +155,4 @@ az = -15.5; e1 = 30;
 view(az,e1)
 
 colormap autumn
-set(gcf, 'Renderer', 'painters'); 
 print '-depsc2' -opengl  'estimator_3d_small.eps'

### 2016-09-28 article/Images/boxplots.tex
changes L, section 5, abstract, conclusion, MSC codes

% Created by tikzDevice version 0.10.1 on 2016-09-27 19:09:28
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,361.35);
\begin{scope}
\path[clip] ( 52.08, 52.08) rectangle (416.82,344.55);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round] ( 81.18,261.99) -- (101.96,261.99);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 91.57,135.21) -- ( 91.57,249.68);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 91.57,299.79) -- ( 91.57,283.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.37,135.21) -- ( 96.76,135.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.37,299.79) -- ( 96.76,299.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.18,249.68) --
	(101.96,249.68) --
	(101.96,283.05) --
	( 81.18,283.05) --
	( 81.18,249.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,310.32) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,305.59) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,333.72) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,309.85) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,303.48) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,308.16) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,301.46) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,309.43) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,313.31) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,313.68) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,328.71) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,322.14) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (159.11,282.34) -- (179.89,282.34);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.50,206.32) -- (169.50,259.43);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.50,307.99) -- (169.50,291.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.31,206.32) -- (174.70,206.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.31,307.99) -- (174.70,307.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.11,259.43) --
	(179.89,259.43) --
	(179.89,291.80) --
	(159.11,291.80) --
	(159.11,259.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,316.59) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,316.53) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (237.05,248.35) -- (257.83,248.35);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (247.44,145.15) -- (247.44,230.90);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (247.44,273.76) -- (247.44,258.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.24,145.15) -- (252.64,145.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.24,273.76) -- (252.64,273.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,230.90) --
	(257.83,230.90) --
	(257.83,258.23) --
	(237.05,258.23) --
	(237.05,230.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,285.84) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,276.97) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,277.81) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,275.10) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (340.96,244.14) -- (361.75,244.14);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (351.35,184.73) -- (351.35,235.68);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (351.35,264.95) -- (351.35,252.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (346.16,184.73) -- (356.55,184.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (346.16,264.95) -- (356.55,264.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.96,235.68) --
	(361.75,235.68) --
	(361.75,252.92) --
	(340.96,252.92) --
	(340.96,235.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.35,277.50) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.35,272.29) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.35,273.68) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.35,269.61) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.35,274.89) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.35,271.79) circle (  4.41);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08, 70.00) -- ( 52.08,279.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08, 70.00) -- ( 43.68, 70.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,174.65) -- ( 43.68,174.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,279.31) -- ( 43.68,279.31);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 40.32, 70.00) {1e-07};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 40.32,174.65) {1e-05};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at (13,210) {$\varepsilon_{\underline{S}_u}$};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 40.32,279.31) {1e-03};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at (234.45, 10.08) {inputs};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 20.16,198.31) { };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08, 52.08) --
	(416.82, 52.08) --
	(416.82,344.55) --
	( 52.08,344.55) --
	( 52.08, 52.08);
\end{scope}
\begin{scope}
\path[clip] ( 52.08, 52.08) rectangle (416.82,344.55);
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 1.2pt,line join=round] (107.15,280.40) -- (127.94,280.40);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.55,198.54) -- (117.55,263.82);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.55,313.05) -- (117.55,296.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.35,198.54) -- (122.74,198.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.35,313.05) -- (122.74,313.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.15,263.82) --
	(127.94,263.82) --
	(127.94,296.88) --
	(107.15,296.88) --
	(107.15,263.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.55,322.21) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.55,318.08) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.55,324.66) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.55,328.89) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.55,317.19) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (185.09,247.91) -- (205.87,247.91);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (195.48,180.39) -- (195.48,231.77);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (195.48,277.51) -- (195.48,260.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.29,180.39) -- (200.68,180.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.29,277.51) -- (200.68,277.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.09,231.77) --
	(205.87,231.77) --
	(205.87,260.90) --
	(185.09,260.90) --
	(185.09,231.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.48,278.43) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.48,281.93) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.48,282.68) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (263.03,145.96) -- (283.81,145.96);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (273.42, 62.91) -- (273.42,129.15);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (273.42,172.18) -- (273.42,157.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.22, 62.91) -- (278.61, 62.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.22,172.18) -- (278.61,172.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.03,129.15) --
	(283.81,129.15) --
	(283.81,157.95) --
	(263.03,157.95) --
	(263.03,129.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,187.97) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,177.67) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,175.37) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,177.46) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,177.40) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,181.20) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (366.94,147.77) -- (387.72,147.77);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (377.33, 64.25) -- (377.33,127.04);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (377.33,177.11) -- (377.33,159.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.14, 64.25) -- (382.53, 64.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.14,177.11) -- (382.53,177.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (366.94,127.04) --
	(387.72,127.04) --
	(387.72,159.91) --
	(366.94,159.91) --
	(366.94,127.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.33,179.32) circle (  4.41);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.56, 52.08) -- (364.34, 52.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.56, 52.08) -- (104.56, 43.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.49, 52.08) -- (182.49, 43.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (260.43, 52.08) -- (260.43, 43.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.34, 52.08) -- (364.34, 43.68);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 97.19, 32.77) {x};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.18] at (106.05, 30.24) {3};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at (175.12, 32.77) {x};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.18] at (183.99, 30.24) {4};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at (253.06, 32.77) {x};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.18] at (261.92, 30.24) {5};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at (356.97, 32.77) {x};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.18] at (365.84, 30.24) {6};
\end{scope}
\begin{scope}
\path[clip] ( 52.08, 52.08) rectangle (416.82,344.55);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,102.48) rectangle (170.41, 52.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.53, 82.53) rectangle ( 67.83, 88.83);
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.53, 65.73) rectangle ( 67.83, 72.03);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 77.28, 79.89) {Variant A.a};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 77.28, 63.09) {Variant A.b};
\definecolor{drawColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,315.89) -- (416.82,315.89);
\end{scope}
\end{tikzpicture}

\end{document}

### 2016-09-28 article/Images/boxplots_bis.tex
changes L, section 5, abstract, conclusion, MSC codes

% Created by tikzDevice version 0.10.1 on 2016-09-28 10:42:51
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,361.35);
\begin{scope}
\path[clip] ( 52.08, 52.08) rectangle (416.82,344.55);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round] ( 81.18,306.99) -- (101.96,306.99);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 91.57,276.20) -- ( 91.57,299.28);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 91.57,323.16) -- ( 91.57,311.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.37,276.20) -- ( 96.76,276.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.37,323.16) -- ( 96.76,323.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.18,299.28) --
	(101.96,299.28) --
	(101.96,311.51) --
	( 81.18,311.51) --
	( 81.18,299.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.57,211.08) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (159.11,244.65) -- (179.89,244.65);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.50,116.49) -- (169.50,220.17);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.50,281.05) -- (169.50,265.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.31,116.49) -- (174.70,116.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.31,281.05) -- (174.70,281.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.11,220.17) --
	(179.89,220.17) --
	(179.89,265.88) --
	(159.11,265.88) --
	(159.11,220.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,320.13) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,321.58) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,321.64) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,327.86) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,320.52) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,333.72) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,322.23) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,320.78) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,333.62) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,332.53) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,324.25) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.50,329.22) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (237.05,262.88) -- (257.83,262.88);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (247.44,115.74) -- (247.44,254.43);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (247.44,302.17) -- (247.44,281.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.24,115.74) -- (252.64,115.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.24,302.17) -- (252.64,302.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,254.43) --
	(257.83,254.43) --
	(257.83,281.63) --
	(237.05,281.63) --
	(237.05,254.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,310.30) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,307.71) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,310.68) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,309.44) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,326.37) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,314.83) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,306.55) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.44,319.47) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (340.96,264.78) -- (361.75,264.78);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (351.35, 66.01) -- (351.35,239.90);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (351.35,301.24) -- (351.35,276.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (346.16, 66.01) -- (356.55, 66.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (346.16,301.24) -- (356.55,301.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.96,239.90) --
	(361.75,239.90) --
	(361.75,276.83) --
	(340.96,276.83) --
	(340.96,239.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.35,305.41) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.35,308.76) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.35,306.75) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.35,314.02) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (351.35,316.83) circle (  4.41);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08, 66.54) -- ( 52.08,326.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08, 66.54) -- ( 43.68, 66.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,127.15) -- ( 43.68,127.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,153.25) -- ( 43.68,153.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,213.85) -- ( 43.68,213.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,239.95) -- ( 43.68,239.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,300.56) -- ( 43.68,300.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,326.66) -- ( 43.68,326.66);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 40.32, 66.54) {1e-05};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 40.32,127.15) {5e-05};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at (13,175) {$\varepsilon_{\underline{S}_u}$};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 40.32,213.85) {5e-04};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 40.32,300.56) {5e-03};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at (234.45, 10.08) {inputs};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 20.16,198.31) { };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08, 52.08) --
	(416.82, 52.08) --
	(416.82,344.55) --
	( 52.08,344.55) --
	( 52.08, 52.08);
\end{scope}
\begin{scope}
\path[clip] ( 52.08, 52.08) rectangle (416.82,344.55);
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 1.2pt,line join=round] (107.15,261.10) -- (127.94,261.10);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.55, 62.91) -- (117.55,236.24);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.55,302.05) -- (117.55,276.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.35, 62.91) -- (122.74, 62.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.35,302.05) -- (122.74,302.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.15,236.24) --
	(127.94,236.24) --
	(127.94,276.57) --
	(107.15,276.57) --
	(107.15,236.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.55,303.09) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.55,307.34) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.55,314.20) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (185.09,248.49) -- (205.87,248.49);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (195.48, 75.27) -- (195.48,227.29);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (195.48,297.89) -- (195.48,271.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.29, 75.27) -- (200.68, 75.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.29,297.89) -- (200.68,297.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.09,227.29) --
	(205.87,227.29) --
	(205.87,271.55) --
	(185.09,271.55) --
	(185.09,227.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.48,301.86) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (263.03,195.72) -- (283.81,195.72);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (273.42, 76.18) -- (273.42,169.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (273.42,230.87) -- (273.42,207.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.22, 76.18) -- (278.61, 76.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.22,230.87) -- (278.61,230.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.03,169.85) --
	(283.81,169.85) --
	(283.81,207.60) --
	(263.03,207.60) --
	(263.03,169.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,243.30) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,245.14) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,251.06) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,235.07) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,243.94) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.42,232.91) circle (  4.41);

\path[draw=drawColor,line width= 1.2pt,line join=round] (366.94,193.08) -- (387.72,193.08);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (377.33, 73.03) -- (377.33,172.11);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (377.33,239.43) -- (377.33,216.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.14, 73.03) -- (382.53, 73.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.14,239.43) -- (382.53,239.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (366.94,172.11) --
	(387.72,172.11) --
	(387.72,216.80) --
	(366.94,216.80) --
	(366.94,172.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.33,253.83) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.33,253.84) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.33,262.95) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.33,270.28) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.33,247.69) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.33,254.87) circle (  4.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.33,251.83) circle (  4.41);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,361.35);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.56, 52.08) -- (364.34, 52.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.56, 52.08) -- (104.56, 43.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.49, 52.08) -- (182.49, 43.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (260.43, 52.08) -- (260.43, 43.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (364.34, 52.08) -- (364.34, 43.68);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 97.19, 32.77) {x};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.18] at (106.05, 30.24) {3};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at (175.12, 32.77) {x};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.18] at (183.99, 30.24) {4};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at (253.06, 32.77) {x};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.18] at (261.92, 30.24) {5};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at (356.97, 32.77) {x};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.18] at (365.84, 30.24) {6};
\end{scope}
\begin{scope}
\path[clip] ( 52.08, 52.08) rectangle (416.82,344.55);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,102.48) rectangle (170.41, 52.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.53, 82.53) rectangle ( 67.83, 88.83);
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.53, 65.73) rectangle ( 67.83, 72.03);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 77.28, 79.89) {Variant A.a};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.68] at ( 77.28, 63.09) {Variant A.b};
\definecolor{drawColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.08,300.56) -- (416.82,300.56);
\end{scope}
\end{tikzpicture}

\end{document}

### 2016-09-28 article/article_for_submission.tex
changes L, section 5, abstract, conclusion, MSC codes

@@
 
-\title{Reliable error estimation for Sobol' indices%\thanks{Grants or other notes
-%about the article that should go on the front page should be
-%placed here. General acknowledgments should be placed at the end of the article.}
+\title{Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}
 }
@@
 
-\author{Laurent Gilquin \and
-        Llu\'{i}s Antoni Jim\'{e}nez Rugama %etc.
-}
+\author{
+        Llu\'{i}s Antoni Jim\'{e}nez Rugama \and  Laurent Gilquin}
 
@@
 
-\institute{Laurent Gilquin \at
-              Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 655 avenue de l'Europe, 38330 Montbonnot \\
-              %Tel.: +123-45-678910\\
-              %Fax: +123-45-678910\\
-              \email{gilquin.laurent@inria.fr}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           Llu\'{i}s Antoni Jim\'{e}nez Rugama \at
+\institute{Llu\'{i}s Antoni Jim\'{e}nez Rugama \at
               Illinois Institute of Technology, Rettaliata Engineering Center, 10 W 32st, Chicago, IL 60616 \\
 \email{ljimene1@hawk.iit.edu}
+           \and
+           Laurent Gilquin \at
+              Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 655 avenue de l'Europe, 38330 Montbonnot \\
+\email{gilquin.laurent@inria.fr}   
 }
@@
 \begin{abstract}
-Insert your abstract here. Include keywords,\\ PACS and mathematical
-subject classification numbers as needed.
-\keywords{First keyword \and Second keyword \and More}
+In the field of sensitivity analysis, Sobol' indices are sensitivity measures widely used to assess the importance of inputs of a model on its output.
+The estimation of these indices is often performed trough Monte Carlo or quasi-Monte Carlo methods.
+A notable method is the replication procedure that estimate first-order indices at a reduced cost.
+
+An inherent practical problem is how to quantity the number of model evaluations to ensure that estimates satisfy a desired tolerance.
+This paper addresses this challenge by proposing a reliable error bound for first-order and total effect Sobol' indices.
+Starting from the integral formula of the indices, the error bound is defined in terms of the discrete Walsh coefficients of the different integrands.
+
+We propose a sequential estimation procedure of Sobol' indices using the latter error bound as stopping criterion.
+The sequential procedure combines Sobol' sequences with either Saltelli's strategy to estimate both first-order and total effect indices, or the replication procedure to estimate only first-order indices.
+
+\keywords{Sobol' indices \and error bound \and sequential method \and Sobol' sequences}
 % \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
+\subclass{49Q12 \and 62L10 \and 65R10}
 \end{abstract}
@@
 Our main contribution is detailed in  Section \ref{sec:3}.
-There we review the construction of the error bound for the estimation of integrals based on digital nets, and then generalize it for Sobol' indices.
+There, we review the construction of the error bound proposed in \cite{HicJim} for the estimation of integrals based on digital sequences, then generalize it for Sobol' indices.
 Section \ref{sec:4} is devoted to analyze the cost in terms of model evaluations of our sequential estimation algorithm.
@@
 $I_2$) and maximizes the denominator $I_3-I_4^2$.
-As an example, Figure \ref{fig:1} below illustrate the maximization process for $\vI$ unidimensional.
-\begin{figure*}
-\centering
-\includegraphics[width=1\textwidth]{Images/estimator_3d_small.eps}
- figure caption is below the figure
-\caption{Estimator property.}
-\label{fig:1}       % Give a unique label
-\end{figure*}
+%As an example, Figure \ref{fig:1} below illustrate the maximization of $\underline{S}_u(\vI)$.
+%\begin{figure*}
+%\centering
+%\textbf{•}\includegraphics[width=1\textwidth]{Images/%estimator_3d_small.eps}
+% figure caption is below the figure
+%\caption{Estimator property.}
+%\label{fig:1}       % Give a unique label
+%\end{figure*}
 
@@
 The comparison is based on error bounds, namely $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$, and total number of evaluations.
-Boxplots of error bounds are provided to support tables of results.
+Boxplots of error bounds are drawn to support table of results.
 Results are averaged over $r=100$ repeats.
@@
 
-We also evaluate the failure rate over the $100$ repeats that is the ratio of error bounds failing to satisfy respectively $\varepsilon_{\underline{S}_u} \leq \varepsilon$ and $\varepsilon_{\underline{S}_u} \leq \varepsilon$.
+We also evaluate the failure rate of each variant over the $100$ repeats.
+The failure rate corresponds to the ratio of error bounds failing to satisfy respectively $\varepsilon_{\underline{S}_u} \leq \varepsilon$ and $\varepsilon_{\underline{S}_u} \leq \varepsilon$.
 Failure rates are denoted by ${err}_{\varepsilon_{\underline{S}_u}}$ and  ${err}_{\varepsilon_{\overline{S}_u}}$.
@@
 The two classical test functions considered are the g-function introduced by Sobol' \cite{Sobol'} and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
-The idea is to test our method over two categories of functions: additive (g-function) and multiplicative (Bratley \textit{et al.} function).
+The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.} function) and multiplicative (g-function).
 
@@
 \begin{equation*}
-f(\vx)= \prod \limits_{i=1}^{d}g_i(x_i), \qquad g_i(x_i)=\frac{\left |4x_i-2 \right | + a_i}{1 + a_i}, \ a_i \geq 0.
+f(\vx)= \prod \limits_{j=1}^{d}g_j(x_j), \qquad g_j(x_j)=\frac{\left |4x_j-2 \right | + a_j}{1 + a_j}, \ a_j \geq 0.
 \end{equation*}
-Each value $a_i$ determines the relative importance of the $x_i$.
-When the value of $a_i$ gets closer to zero the variable $x_i$ becomes more influential.
-Here, the dimension is $d=6$ and values chosen for the $a_i$ are given by the following vector $(a_1=0,=a_2=0.5, a_3=3, a_4=9, a_5=99$, $a_6=99)$.
+Each value $a_j$ determines the relative importance of the $x_j$.
+When the value of $a_j$ gets closer to zero the variable $x_i$ becomes more influent.
+Here, the dimension is $d=6$ and values chosen for the $a_j$ are given by the following vector $(a_1=0,=a_2=0.5, a_3=3, a_4=9, a_5=99$, $a_6=99)$.
 
@@
 Table \ref{res.gfunc.Ab} shows the same results obtained with Variant $A.b$.
-\renewcommand{\arraystretch}{1.3}
+\renewcommand{\arraystretch}{1.25}
 \begin{table}[!ht]
-\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ obtained with Variant $A.a$ over $100$ repeats.
-Failure rates are denoted by ${err}_{\varepsilon_{\underline{S}_u}}$ and  ${err}_{\varepsilon_{\overline{S}_u}}$.}
+\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$ , $\varepsilon_{\overline{S}_u}$ and total number of evaluations of Variant $A.a$.}
 \centering
@@
  $x_4$ & $0.0058$ &  $0.0012$ & $0.02$ & $0.0092$ & $0.0003$ & $0$ \\ \hline
- $x_5$ & $5.10^{-5}$ & $0.0003$ & $0$ & $9.10^{-5}$ & $0.0000$ & $0$ \\ \hline
- $x_6$ & $5.10^{-5}$ & $0.0003$ & $0$  & $9.10^{-5}$ & $0.0000$ & $0$ \\ \hline \hline
+ $x_5$ & $5.10^{-5}$ & $0.0003$ & $0$ & $9.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
+ $x_6$ & $5.10^{-5}$ & $0.0003$ & $0$  & $9.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
 \multicolumn{4}{l}{Total number of evaluations: $63 \ 088$} & & &\\ \hline 
@@
 \begin{table}[!ht]
-\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ obtained with Variant $A.b$ over $100$ repeats.
-Failure rates are denoted by ${err}_{\varepsilon_{\underline{S}_u}}$ and  ${err}_{\varepsilon_{\overline{S}_u}}$.}
+\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$ , $\varepsilon_{\overline{S}_u}$ and total number of evaluations of Variant $A.b$.}
 \centering
@@
  $x_4$ & $0.0058$ &  $0.0003$ & $0$ & $0.0092$ & $0.0003$ & $0$ \\ \hline
- $x_5$ & $5.10^{-5}$ & $0.0000$ & $0$ & $9.10^{-5}$ & $0.0000$ & $0$ \\ \hline
- $x_6$ & $5.10^{-5}$ & $0.0000$ & $0$  & $9.10^{-5}$ & $0.0000$ & $0$ \\ \hline \hline
+ $x_5$ & $5.10^{-5}$ & $< 10^{-4}$ & $0$ & $9.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
+ $x_6$ & $5.10^{-5}$ & $< 10^{-4}$ & $0$  & $9.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
 \multicolumn{4}{l}{Total number of evaluations: $62 \ 703$} & & &\\ \hline 
@@
 \end{table}
-
-The main observation is that both approaches give similar results both in terms of error bounds and total number of evaluations.
-Looking at those averaged results, the use of ``Correlation 2'' to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ does not seems to bring any improvements.
-We propose to draw boxplots to further investigate the results.
-
-Figure \ref{boxplots.gfunc} shows boxplots of the $100$ error bounds $\varepsilon_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and $A.b$.
+The main observation is that both approaches give similar results both in terms of error bounds, failure rates and total number of evaluations.
+The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ does not seem to bring any improvement.
+We propose to draw boxplots of error bounds to further investigate the results.
+
+Figure \ref{boxplots.gfunc} shows boxplots of the $100$ error bounds $\varepsilon_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$.
+The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.
 \begin{figure}[!ht]
-\caption{Boxplots of error bounds $\varepsilon_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and $A.b$.}
+\caption{Boxplots of error bounds $\varepsilon_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$.
+The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
 \centering
@@
 \end{figure}
-As expected, the use of ``Correlation 2'' in Variant $A.b$ allows to obtain better error bounds.
-The discrepancy observed does not show off in Table \ref{res.gfunc.Ab} due to its low magnitude varying between $10^{-4}$ and $10^{-5}$.
+As expected, we observe that the use of ``Correlation 2'' in Variant $A.b$ results in lower error bounds for these four inputs.
+The discrepancy observed does not stand out in Table \ref{res.gfunc.Ab} due to its low magnitude ($10^{-4} \sim 10^{-5}$).
 \bigskip
 
-Table \ref{res.gfunc.B} shows the averaged error bounds $\varepsilon_{\underline{S}_u}$ obtained with Variant $B$ and the averaged total number of evaluations performed. 
+Table \ref{res.gfunc.B} shows averaged error bounds $\varepsilon_{\underline{S}_u}$ and total number of evaluations of Variant $B$. 
 \begin{table}[!ht]
-\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$  obtained with Variant $B$ over $100$ repeats. Failure rate is denoted by ${err}_{\varepsilon_{\underline{S}_u}}$.}
+\caption{Averaged error bound $\varepsilon_{\underline{S}_u}$ and total number of evaluations of Variant $B$.}
 \centering
@@
 \end{table}
-Looking at the results, using Variant $B$ leads to higher failure rates than those obtained with Variant $A.a$ or $A.b$.
-The compromise is a total number of evaluations twice as small as the others two variants.
-As such, this approach remains interesting when one want to estimate only first-order indices.
+Looking at the results, using Variant $B$ leads to smaller error bounds and higher failure rates than those obtained with Variant $A.a$ or Variant $A.b$.
+The compromise is a total number of evaluations twice as small.
+As such, this approach remains interesting when one wants to estimate only first-order indices.
 
 \subsubsection{Bratley et al. function}
+
+For the second example, we consider the Bratley \textit{et al.} function defined by:
+$$f(x_1,\dots,x_d)=\sum \limits_{i=1}^{d} (-1)^i \prod \limits_{j=1}^{i} x_j \ .$$
+The importance of each variable $x_j$ depends on their own rank. More explicitly, $x_1$ is more influent than $x_2$ that is respectively more influent than $x_3$ and so on.
+
+As for the g-function, Tables \ref{res.bratley.Aa} and \ref{res.bratley.Ab} show averaged error bounds and averaged total number of evaluations for Variant $A.a$ and Variant $A.b$.
+\begin{table}[!ht]
+\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$, $\varepsilon_{\overline{S}_u}$ and total number of evaluations of Variant $A.a$.}
+\centering
+\begin{tabular}{ccccccc}
+\hline
+ input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ & $\overline{S}_u$ & $\varepsilon_{\overline{S}_u}$ &$err_{\varepsilon_{\overline{S}_u}}$ \\ \hline
+ $x_1$ & $0.6529$ &  $0.0004$ & $0$ & $0.7396$ & $0.0003$ & $0.$ \\ \hline
+ $x_2$ & $0.1791$ &  $0.0006$ & $0$ & $0.2659$ & $0.0004$ & $0$ \\ \hline
+ $x_3$ & $0.0370$ &  $0.0058$ & $0.71$ & $0.0764$ & $0.0012$ & $0.02$ \\ \hline
+ $x_4$ & $0.0133$ &  $0.0022$ & $0.12$ & $0.0343$ & $0.0020$ & $0.07$ \\ \hline
+ $x_5$ & $0.0015$ &  $0.0024$ & $0.11$ & $0.0062$ & $0.0014$ & $0$ \\ \hline
+ $x_6$ & $0.0015$ & $0.0021$ & $0.06$  & $0.0062$ & $0.0010$ & $0.03$ \\ \hline \hline
+\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} & & &\\ \hline 
+\end{tabular}
+\label{res.bratley.Aa}
+\end{table}
+\begin{table}[!ht]
+\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$, $\varepsilon_{\overline{S}_u}$ and total number of evaluations of Variant $A.b$.}
+\centering
+\begin{tabular}{ccccccc}
+\hline
+ input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ & $\overline{S}_u$ & $\varepsilon_{\overline{S}_u}$ &$err_{\varepsilon_{\overline{S}_u}}$ \\ \hline
+ $x_1$ & $0.6529$ &  $0.0004$ & $0$ & $0.7396$ & $0.0003$ & $0$ \\ \hline
+ $x_2$ & $0.1791$ &  $0.0006$ & $0$ & $0.2659$ & $0.0005$ & $0$ \\ \hline
+ $x_3$ & $0.0370$ &  $0.0019$ & $0.04$ & $0.0764$ & $0.0013$ & $0.01$ \\ \hline
+ $x_4$ & $0.0133$ &  $0.0016$ & $0.01$ & $0.0343$ & $0.0017$ & $0.02$ \\ \hline
+ $x_5$ & $0.0015$ &  $0.0003$ & $0$ & $0.0062$ & $0.0015$ & $0.04$ \\ \hline
+ $x_6$ & $0.0015$ &  $0.0004$ & $0$  & $0.0062$ & $0.0011$ & $0$ \\ \hline \hline
+\multicolumn{4}{l}{Total number of evaluations: $68 \ 045$} & & &\\ \hline 
+\end{tabular}
+\label{res.bratley.Ab}
+\end{table}
+Variant $A.b$ provides better error bounds than Variant $A.a$ on the four small first-indices $\underline{S}_3,\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''.
+The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $71\%$ against only $4\%$ for Variant $A.b$.
+Furthermore, Variant $A.b$ requires less evaluations than Variant $A.a$.
+\begin{figure}[!ht]
+\caption{Boxplots of error bounds $\varepsilon_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$.
+The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
+\centering
+\includegraphics[width=0.45\textwidth]{Images/boxplots_bis.pdf}
+\label{boxplots.bratley}
+\end{figure}
+The boxplots represented in Figure \ref{boxplots.bratley} emphasize the latter observations and remarks.
+
+Table \ref{res.bratley.B} shows averaged error bounds $\varepsilon_{\underline{S}_u}$ and total number of evaluations of Variant $B$. 
+\begin{table}[!ht]
+\caption{Averaged error bound $\varepsilon_{\underline{S}_u}$ and averaged total number of evaluations for Variant $B$.}
+\centering
+\begin{tabular}{cccc}
+\hline
+ input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ \\ \hline
+ $x_1$ & $0.6529$ &  $0.0003$ & $0$ \\ \hline
+ $x_2$ & $0.1791$ &  $0.0006$ & $0$ \\ \hline
+ $x_3$ & $0.0370$ &  $0.0010$ & $0$ \\ \hline
+ $x_4$ & $0.0133$ &  $0.0038$ & $0.25$    \\ \hline
+ $x_5$ & $0.0015$ & $0.0024$ & $0$  \\ \hline
+ $x_6$ & $0.0015$ & $0.0026$ & $0$  \\ \hline \hline
+\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
+\end{tabular}
+\label{res.bratley.B}
+\end{table}
+The error bounds are better than those of Variant $A.a$ but worse than those of Variant $A.b$.
+Since the total number of evaluations is close to the one of Variant $A.b$, the conclusion is that Variant $B$ does not bring any improvement for this example.
+\bigskip
+
+From the results on these two functions test, the main conclusion is that Variant $A.b$ performs the best.
+This highlights the efficiency of ``Correlation 2'' to estimate small first-order indices.
+Even if ``Correlation 2'' estimator originally requires more samples, this drawback is completely overridden when this estimator is included into a sequential procedure such as ours.
+
+%\[
+%\begin{array}{lcccccc}
+%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
+% \widehat{\underline{S}}_u & 0.6500 & 0.1800 & 0.0370 & 0.0100 & 0.0038 & 0.0040 \\ \hline
+% n & 32768 & 16384 & 16384 & 12447 & 8637 & 9196 \\ \hline
+% \text{error } & 0.0003 & 0.0006 & 0.0010 & 0.0038 & 0.0024 & 0.0026 \\ \hline
+%\end{array}
+%\]
+%Reliability on the results,
+%\[
+%\begin{array}{ cccccc }
+%     100  & 100  & 100  & 75  &  100  & 100
+%\end{array}
+%\]
+
 %
@@
 
-\section{Conclusions}
+\section{Conclusion}
+When estimating Sobol' indices, the question of how much evaluations must be performed to reach a desired precision is often raised by practitioners.
+This question is difficult to address mostly because the number of evaluations needed depends on the complexity of the model studied.
+As such, it is hard to bring out a general rule of thumb.
+
+The sequential estimation procedure proposed in this paper offers a practical solution with the construction of an error bound for the Sobol' indices.
+The number of points is progressively augmented until the error bound becomes lower than a user specified tolerance.
+The procedure presented combines Sobol' sequences with either Saltelli's strategy to estimate both first-order and total effect indices, or the replication procedure to estimate only first-order indices.
+Furthermore, we investigated the use of a recent estimator well-suited to the estimation of small first-order indices.
+The efficiency of this estimator was assessed and highlighted on two test functions and a real case model.
+More generally, our estimation procedure gave good results in term of precision of the error bounds with low failure rates observed across the indices.
 
 \begin{acknowledgements}
-This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-\newline MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).
-
 The authors thank Fred J.
@@
 Bratley, P., Fox, B.L., Niederreiter, H.: Implementation and tests of low-discrepancy sequences, ACM Trans. Model. Comput. Simul. \textbf{2}(3), 195-213 (1992)
-Hickernell, F.J., Jim\'enez Rugama, Ll.A.: Reliable Adaptative Cubature Using Digital Sequences: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 367-383 (2016)
 \bibitem{Gilquin.rec}

### 2016-09-28 article/article_for_submission.tex
Last changes for article

@@
 
-As for the g-function, Tables \ref{res.bratley.Aa} and \ref{res.bratley.Ab} show averaged error bounds and averaged total number of evaluations for Variant $A.a$ and Variant $A.b$.
+As for the g-function, Tables \ref{res.bratley.Aa} and \ref{res.bratley.Ab} show averaged error bounds and averaged total number of evaluations of Variant $A.a$ and Variant $A.b$.
 \begin{table}[!ht]
@@
 This highlights the efficiency of ``Correlation 2'' to estimate small first-order indices.
-Even if ``Correlation 2'' estimator originally requires more samples, this drawback is completely overridden when this estimator is included into a sequential procedure such as ours.
+Even if ``Correlation 2'' originally requires more samples, this drawback is completely overridden when this estimator is included into a sequential procedure such as ours.
 
@@
 Furthermore, we investigated the use of a recent estimator well-suited to the estimation of small first-order indices.
-The efficiency of this estimator was assessed and highlighted on two test functions and a real case model.
-More generally, our estimation procedure gave good results in term of precision of the error bounds with low failure rates observed across the indices.
+The efficiency of this estimator, called ``Correlation 2'', was assessed and highlighted on two test functions and a real case model.
+The variant combining Saltelli's strategy and ``Correlation 2'' gave the best results in term of precision of the error bounds with low failure rates observed across the indices.
 

### 2016-09-28 article/article_for_submission.tex
Little changes
changes L section 5

@@
 
-We propose to illustrate our sequential estimation procedure on two classical test functions and one real model. For each case, we compare results obtained with each of the three methods:
+We propose to illustrate our sequential estimation procedure on two classical test functions and one real model. In each case, Sobol' indices are estimated with the following three variants:
 \begin{itemize}
@@
 
-The comparison is based on error bounds, namely $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$, and total number of evaluations.
-Boxplots of error bounds are drawn to support table of results.
+For the two test functions, results of the three variants are compared based on estimation errors.
+These errors correspond to absolute difference between true values of indices and estimates.
+They are defined as follows:
+$$\delta_{\underline{S}_u} = \absolute{\underline{S}_u - \widehat{\underline{S}_u}}, \qquad \delta_{\overline{S}_u} = \absolute{\overline{S}_u - \widehat{\overline{S}_u}}.$$
+We also compare the total number of evaluations of each variant.
 Results are averaged over $r=100$ repeats.
@@
 
-We also evaluate the failure rate of each variant over the $100$ repeats.
-The failure rate corresponds to the ratio of error bounds failing to satisfy respectively $\varepsilon_{\underline{S}_u} \leq \varepsilon$ and $\varepsilon_{\underline{S}_u} \leq \varepsilon$.
-Failure rates are denoted by ${err}_{\varepsilon_{\underline{S}_u}}$ and  ${err}_{\varepsilon_{\overline{S}_u}}$.
+The failure rate of each variant is evaluated over the $100$ repeats.
+The failure rate is defined as the ratio of estimation errors failing to satisfy respectively $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$.
+Failure rates are denoted by $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$.
 
@@
 
-Table \ref{res.gfunc.Aa} shows the averaged error bounds obtained with Variant $A.a$ as well as the averaged total number of evaluations performed.
+Table \ref{res.gfunc.Aa} shows the averaged estimation errors obtained with Variant $A.a$ as well as the averaged total number of evaluations performed.
 Table \ref{res.gfunc.Ab} shows the same results obtained with Variant $A.b$.
@@
 \begin{table}[!ht]
-\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$ , $\varepsilon_{\overline{S}_u}$ and total number of evaluations of Variant $A.a$.}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ , $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.a$.}
 \centering
@@
 \hline
- input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ & $\overline{S}_u$ & $\varepsilon_{\overline{S}_u}$ &$err_{\varepsilon_{\overline{S}_u}}$ \\ \hline
+ input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
  $x_1$ & $0.5868$ &  $0.0004$ & $0.02$ & $0.6901$ & $0.0005$ & $0.02$ \\ \hline
@@
 \begin{table}[!ht]
-\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$ , $\varepsilon_{\overline{S}_u}$ and total number of evaluations of Variant $A.b$.}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ , $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.b$.}
 \centering
@@
 \hline
- input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ & $\overline{S}_u$ & $\varepsilon_{\overline{S}_u}$ &$err_{\varepsilon_{\overline{S}_u}}$ \\ \hline
+ input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
  $x_1$ & $0.5868$ &  $0.0005$ & $0.03$ & $0.6901$ & $0.0006$ & $0.02$ \\ \hline
@@
 \end{table}
-The main observation is that both approaches give similar results both in terms of error bounds, failure rates and total number of evaluations.
+The main observation is that both approaches give similar results both in terms of estimation errors, failure rates and total number of evaluations.
 The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ does not seem to bring any improvement.
-We propose to draw boxplots of error bounds to further investigate the results.
-
-Figure \ref{boxplots.gfunc} shows boxplots of the $100$ error bounds $\varepsilon_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$.
+We propose to draw boxplots of estimation errors to further investigate the results.
+
+Figure \ref{boxplots.gfunc} shows boxplots of the $100$ estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$.
 The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.
 \begin{figure}[!ht]
-\caption{Boxplots of error bounds $\varepsilon_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$.
+\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$.
 The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
@@
 \end{figure}
-As expected, we observe that the use of ``Correlation 2'' in Variant $A.b$ results in lower error bounds for these four inputs.
+As expected, we observe that the use of ``Correlation 2'' in Variant $A.b$ results in lower estimation errors for these four inputs.
 The discrepancy observed does not stand out in Table \ref{res.gfunc.Ab} due to its low magnitude ($10^{-4} \sim 10^{-5}$).
@@
 
-Table \ref{res.gfunc.B} shows averaged error bounds $\varepsilon_{\underline{S}_u}$ and total number of evaluations of Variant $B$. 
+Table \ref{res.gfunc.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$. 
 \begin{table}[!ht]
-\caption{Averaged error bound $\varepsilon_{\underline{S}_u}$ and total number of evaluations of Variant $B$.}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
 \centering
@@
 \hline
- input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ \\ \hline
+ input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
  $x_1$ & $0.5868$ &  $0.0011$ & $0.07$ \\ \hline
@@
 \end{table}
-Looking at the results, using Variant $B$ leads to smaller error bounds and higher failure rates than those obtained with Variant $A.a$ or Variant $A.b$.
+Looking at the results, using Variant $B$ leads to higher estimation errors and higher failure rates than those obtained with Variant $A.a$ or Variant $A.b$.
 The compromise is a total number of evaluations twice as small.
@@
 
-As for the g-function, Tables \ref{res.bratley.Aa} and \ref{res.bratley.Ab} show averaged error bounds and averaged total number of evaluations of Variant $A.a$ and Variant $A.b$.
+As for the g-function, Tables \ref{res.bratley.Aa} and \ref{res.bratley.Ab} show averaged estimation errors and averaged total number of evaluations for Variant $A.a$ and Variant $A.b$.
 \begin{table}[!ht]
-\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$, $\varepsilon_{\overline{S}_u}$ and total number of evaluations of Variant $A.a$.}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.a$.}
 \centering
@@
 \hline
- input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ & $\overline{S}_u$ & $\varepsilon_{\overline{S}_u}$ &$err_{\varepsilon_{\overline{S}_u}}$ \\ \hline
+ input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
  $x_1$ & $0.6529$ &  $0.0004$ & $0$ & $0.7396$ & $0.0003$ & $0.$ \\ \hline
@@
 \begin{table}[!ht]
-\caption{Averaged error bounds $\varepsilon_{\underline{S}_u}$, $\varepsilon_{\overline{S}_u}$ and total number of evaluations of Variant $A.b$.}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.b$.}
 \centering
@@
 \hline
- input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ & $\overline{S}_u$ & $\varepsilon_{\overline{S}_u}$ &$err_{\varepsilon_{\overline{S}_u}}$ \\ \hline
+ input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ & $r_{\delta_{\overline{S}_u}}$ \\ \hline
  $x_1$ & $0.6529$ &  $0.0004$ & $0$ & $0.7396$ & $0.0003$ & $0$ \\ \hline
@@
 \end{table}
-Variant $A.b$ provides better error bounds than Variant $A.a$ on the four small first-indices $\underline{S}_3,\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''.
+Variant $A.b$ gives lower estimation errors and fewer failures than Variant $A.a$ on the four small first-indices $\underline{S}_3,\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''.
 The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $71\%$ against only $4\%$ for Variant $A.b$.
 Furthermore, Variant $A.b$ requires less evaluations than Variant $A.a$.
+The boxplots represented in Figure \ref{boxplots.bratley} emphasize the latter observations.
 \begin{figure}[!ht]
-\caption{Boxplots of error bounds $\varepsilon_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$.
+\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$.
 The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
@@
 \end{figure}
-The boxplots represented in Figure \ref{boxplots.bratley} emphasize the latter observations and remarks.
-
-Table \ref{res.bratley.B} shows averaged error bounds $\varepsilon_{\underline{S}_u}$ and total number of evaluations of Variant $B$. 
+
+Table \ref{res.bratley.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$. 
 \begin{table}[!ht]
-\caption{Averaged error bound $\varepsilon_{\underline{S}_u}$ and averaged total number of evaluations for Variant $B$.}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and averaged total number of evaluations for Variant $B$.}
 \centering
@@
 \hline
- input & $\underline{S}_u$ & $\varepsilon_{\underline{S}_u}$ & ${err}_{\varepsilon_{\underline{S}_u}}$ \\ \hline
+ input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
  $x_1$ & $0.6529$ &  $0.0003$ & $0$ \\ \hline
@@
 \end{table}
-The error bounds are better than those of Variant $A.a$ but worse than those of Variant $A.b$.
+The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$.
+Failure rates are similar to those of Variant $A.a$.
 Since the total number of evaluations is close to the one of Variant $A.b$, the conclusion is that Variant $B$ does not bring any improvement for this example.
@@
 Even if ``Correlation 2'' originally requires more samples, this drawback is completely overridden when this estimator is included into a sequential procedure such as ours.
-
-%\[
-%\begin{array}{lcccccc}
-%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
-% \widehat{\underline{S}}_u & 0.6500 & 0.1800 & 0.0370 & 0.0100 & 0.0038 & 0.0040 \\ \hline
-% n & 32768 & 16384 & 16384 & 12447 & 8637 & 9196 \\ \hline
-% \text{error } & 0.0003 & 0.0006 & 0.0010 & 0.0038 & 0.0024 & 0.0026 \\ \hline
-%\end{array}
-%\]
-%Reliability on the results,
-%\[
-%\begin{array}{ cccccc }
-%     100  & 100  & 100  & 75  &  100  & 100
-%\end{array}
-%\]
-
-%
-%\subsubsection{Without small indices estimator}
-%Bratley et al. example:
-%
-%\[
-%\begin{array}{lcccccc}
-%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
-% \widehat{\underline{S}}_u & 0.6500 & 0.1800 & 0.0370 & 0.0120 & 0.0034 & 0.0033 \\ \hline
-% n & 17531 & 8438 & 4137 & 3686 & 625 & 650\\ \hline
-% \text{error } & 0.0004 & 0.0006 & 0.0058 & 0.0022 & 0.0024 & 0.0021 \\ \hline
-% \widehat{\overline{S}}_u & 0.7400 & 0.2700 & 0.0760 & 0.0340 & 0.0065 & 0.0064 \\  \hline
-% n & 16384 & 8192 & 3113 & 1060 & 512 & 512 \\ \hline
-% \text{error } & 0.0003 & 0.0004 & 0.0012 & 0.0020 & 0.0014 & 0.0010 \\ \hline
-%\end{array}
-%\]
-%Reliability on the results,
-%\[
-%\begin{array}{ cccccc }
-%     100  & 100  & 29  & 88  &  89  & 94 \\
-%     100  & 100  & 98  &  93  &  97  &  100
-%\end{array}
-%\]
-%
-%
-%Sobol g-function example:
-%
-%\[
-%\begin{array}{lcccccc}
-%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
-% \widehat{\underline{S}}_u & 0.5900 & 0.2600 & 0.0370 & 0.0060 & 0.0003 & 0.0003 \\ \hline
-% n & 16138 & 9011 & 3748 & 891 & 512 & 512 \\ \hline
-% \text{error } & 0.0004 & 0.0006 & 0.0011 & 0.0012 & 0.0003 & 0.0003 \\ \hline
-% \widehat{\overline{S}}_u & 0.6900 & 0.3600 & 0.0560 & 0.0093 & 0.0001 & 0.0001 \\  \hline
-% n & 11796 & 7496 & 1475 & 512 & 512 & 512 \\ \hline
-% \text{error } & 0.0005 & 0.0004 & 0.0008 & 0.0003 & 0.0000 & 0.0000 \\ \hline
-%\end{array}
-%\]
-%Reliability on the results,
-%\[
-%\begin{array}{ cccccc }
-%     98  & 98  & 97  & 98  &  100  & 100 \\
-%     98  &  100  &  100 &  100  & 100 &  100
-%\end{array}
-%\]
-%
-%\subsubsection{With small indices estimator (threshold $0.1$)}
-%Bratley et al. example:
-%
-%\[
-%\begin{array}{lcccccc}
-%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
-% \widehat{\underline{S}}_u & 0.6500 & 0.1800 & 0.0380 & 0.0140 & 0.0014 & 0.0016 \\ \hline
-% n & 17203 & 8520 & 1362 & 517 & 512 & 512 \\ \hline
-% \text{error } & 0.0004 & 0.0006 & 0.0019 & 0.0016 & 0.0003 & 0.0004 \\ \hline
-% \widehat{\overline{S}}_u & 0.7400 & 0.2700 & 0.0760 & 0.0340 & 0.0063 & 0.0065 \\  \hline
-% n & 16384 & 8192 & 2847 & 1142 & 512 & 512 \\ \hline
-% \text{error } & 0.0003 & 0.0005 & 0.0013 & 0.0017 & 0.0015 & 0.0011 \\ \hline
-%\end{array}
-%\]
-%Reliability on the results,
-%\[
-%\begin{array}{ cccccc }
-%     100  & 100  & 96  & 99  &  100  & 100 \\
-%     100  & 100  & 99  &  98  &  96  &  100
-%\end{array}
-%\]
-%
-%
-%Sobol g-function example:
-%
-%\[
-%\begin{array}{lcccccc}
-%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
-% \widehat{\underline{S}}_u & 0.5900 & 0.2600 & 0.0370 & 0.0060 & 0.0001 & 0.0001 \\ \hline
-% n & 16056 & 8929 & 1070 & 512 & 512 & 512 \\ \hline
-% \text{error } & 0.0005 & 0.0007 & 0.0015 & 0.0003 & 0.0000 & 0.0000 \\ \hline
-% \widehat{\overline{S}}_u & 0.6900 & 0.3600 & 0.0560 & 0.0093 & 0.0001 & 0.0001 \\  \hline
-% n & 11551 & 7741 & 1464 & 512 & 512 & 512 \\ \hline
-% \text{error } & 0.0006 & 0.0003 & 0.0009 & 0.0003 & 0.0000 & 0.0000 \\ \hline
-%\end{array}
-%\]
-%Reliability on the results,
-%\[
-%\begin{array}{ cccccc }
-%     97  & 97  & 95  & 100  &  100  & 100 \\
-%     98  &  100  &  100 &  100  & 100 &  100
-%\end{array}
-%\]
-%
-%\subsubsection{Replicated method}
-%Bratley et al. example:
-%
-%\[
-%\begin{array}{lcccccc}
-%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
-% \widehat{\underline{S}}_u & 0.6500 & 0.1800 & 0.0370 & 0.0100 & 0.0038 & 0.0040 \\ \hline
-% n & 32768 & 16384 & 16384 & 12447 & 8637 & 9196 \\ \hline
-% \text{error } & 0.0003 & 0.0006 & 0.0010 & 0.0038 & 0.0024 & 0.0026 \\ \hline
-%\end{array}
-%\]
-%Reliability on the results,
-%\[
-%\begin{array}{ cccccc }
-%     100  & 100  & 100  & 75  &  100  & 100
-%\end{array}
-%\]
-%
-%
-%Sobol g-function example:
-%
-%\[
-%\begin{array}{lcccccc}
-%   & u=\{1\} & u=\{2\} & u=\{3\} & u=\{4\} & u=\{5\} & u=\{6\} \\ \hline \hline
-% \widehat{\underline{S}}_u & 0.5900 & 0.2600 & 0.0360 & 0.0059 & 0.0031 & 0.0036 \\ \hline
-% n & 16384 & 16384 & 16225 & 14612 & 7086 & 6661 \\ \hline
-% \text{error } & 0.0011 & 0.0013 & 0.0018 & 0.0013 & 0.0031 & 0.0036 \\ \hline
-%\end{array}
-%\]
-%Reliability on the results,
-%\[
-%\begin{array}{ cccccc }
-%     93  & 92  & 91  & 90  &  96  & 95
-%\end{array}
-%\]
 
@@
 The efficiency of this estimator, called ``Correlation 2'', was assessed and highlighted on two test functions and a real case model.
-The variant combining Saltelli's strategy and ``Correlation 2'' gave the best results in term of precision of the error bounds with low failure rates observed across the indices.
+The variant combining Saltelli's strategy and ``Correlation 2'' gave the best results with low failure rates across all indices.
 

### 2016-09-29 article/article_for_submission.tex
Minor changes article for submission

--- 2016-09-28 article/article_for_submission.tex
@@
 % \PACS{PACS code1 \and PACS code2 \and more}
-\subclass{49Q12 \and 62L10 \and 65R10}
+\subclass{49Q12 \and 62L12 \and 65R10}
 \end{abstract}
@@
 \nonumber
-\absolute{I(f) - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
+\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
 \absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}, \\
@@
 \begin{equation}
-\absolute{I(f) - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
+\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
 \end{equation}
@@
 \begin{equation}
-\absolute{I(f) - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
-\le \frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}=\epsilon_{I(f)}, \label{errbd}
+\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
+\le \frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}=\epsilon_{I}, \label{errbd}
 \end{equation}
-where one may increase $m$ until the error bound $\epsilon_{I(f)}$ is small enough.
+where one may increase $m$ until the error bound $\epsilon_{I}$ is small enough.
 
@@
 Each value $a_j$ determines the relative importance of the $x_j$.
-When the value of $a_j$ gets closer to zero the variable $x_i$ becomes more influent.
+When the value of $a_j$ gets closer to zero the variable $x_j$ becomes more influent.
 Here, the dimension is $d=6$ and values chosen for the $a_j$ are given by the following vector $(a_1=0,=a_2=0.5, a_3=3, a_4=9, a_5=99$, $a_6=99)$.

### 2016-09-30 article/article_for_submission.tex
Last changes to article for submission

--- 2016-09-28 article/article_for_submission.tex
@@
 \begin{abstract}
-In the field of sensitivity analysis, Sobol' indices are sensitivity measures widely used to assess the importance of inputs of a model on its output.
+In the field of sensitivity analysis, Sobol' indices are sensitivity measures widely used to assess the importance of inputs of a model to its output.
 The estimation of these indices is often performed trough Monte Carlo or quasi-Monte Carlo methods.
-A notable method is the replication procedure that estimate first-order indices at a reduced cost.
+A notable method is the replication procedure that estimates first-order indices at a reduced cost in terms of number of model evaluations.
 
-An inherent practical problem is how to quantity the number of model evaluations to ensure that estimates satisfy a desired tolerance.
+An inherent practical problem of this estimation is how to quantify the number of model evaluations to ensure that estimates satisfy a desired error tolerance.
 This paper addresses this challenge by proposing a reliable error bound for first-order and total effect Sobol' indices.
@@
 
-We propose a sequential estimation procedure of Sobol' indices using the latter error bound as stopping criterion.
+We propose a sequential estimation procedure of Sobol' indices using the error bound as a stopping criterion.
 The sequential procedure combines Sobol' sequences with either Saltelli's strategy to estimate both first-order and total effect indices, or the replication procedure to estimate only first-order indices.
 
-\keywords{Sobol' indices \and error bound \and sequential method \and Sobol' sequences}
+\keywords{Sobol' indices \and error bound \and sequential method \and quasi-Monte Carlo}
 % \PACS{PACS code1 \and PACS code2 \and more}
-\subclass{49Q12 \and 62L10 \and 65R10}
+\subclass{49Q12 \and 62L12 \and 65R10}
 \end{abstract}
@@
 
-Let $f$ represent a deterministic numerical model in $[0,1)^d$, $d \geq 1$.
+Let $f$ represent a deterministic numerical model in $[0,1]^d$, $d \geq 1$.
 Sensitivity measures, also known as Sobol' indices, are used to assess which inputs of $f$ are influential for the output.
@@
 Among all Sobol' indices one can distinguish \emph{first-order} and \emph{total effect} indices.
-The first measures the effect of a single input, while the latter measures this same effect and includes all its interactions with other inputs.
+The first measure the effect of a single input, while the second measure this same effect and includes all its interactions with other inputs.
 
@@
 A cost efficient alternative to estimate first-order indices was introduced in \cite{Mara}.
-This alternative, called replication procedure, has recently been further studied  in \cite{Tissot} and generalized to the estimation of closed second-order indices.
+This alternative, called the replication procedure, has recently been further studied  in \cite{Tissot} and generalized to the estimation of closed second-order indices.
 
 A practical problem concerning the use of these methods is how to quantify the number of model evaluations to ensure that Sobol' estimates are accurate enough.
-This paper addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences.
+This article addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences.
 The error bound is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition.
-We propose a sequential estimation procedure of Sobol' indices using the error bound as stopping criterion.
+We propose a sequential estimation procedure of Sobol' indices using the error bound as our stopping criterion.
 The procedure operates under the assumption that all integrands lie inside a particular cone of functions (see \cite{HicJim}).
@@
 Our main contribution is detailed in  Section \ref{sec:3}.
-There, we review the construction of the error bound proposed in \cite{HicJim} for the estimation of integrals based on digital sequences, then generalize it for Sobol' indices.
+There, we review the construction of the error bound proposed in \cite{HicJim} for the estimation of integrals based on digital sequences, and then we generalize it for Sobol' indices.
 Section \ref{sec:4} is devoted to analyze the cost in terms of model evaluations of our sequential estimation algorithm.
@@
 
-\section{Backgrounds on Sobol' indices}
+\section{Background on Sobol' indices}
 \label{sec:2}
@@
 %We adopt the same notations introduced by Owen in \cite{Owen}. 
-Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of $f$ and $\mathcal{D}=\{1,\dots,d\}$ the set of dimensions indexes.
+Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of\\$f\in \mathbb{L}^2(\cube)$, and $\mathcal{D}=\{1,\dots,d\}$ the set of dimension indexes.
 %The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
 Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality.
-$\vx_u$ represents a point in $[0,1)^{|u|}$ with components $x_j, j \in u$.
-Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j={x'}_j$ if $j \notin u$.
-We assume that $f \in \mathbb{L}^2(\cube)$.% and denote by $\mu$ and $\sigma^2$ the mean $\int_{\cube}f(\vx)d{\vx}$ and variance $\int_{\cube}(f(\vx)-\mu)^2d{\vx}$ of $f$.
+$\vx_u$ represents a point in $[0,1]^{|u|}$ with components $x_j, j \in u$.
+Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j={x'}_j$ if $j \notin u$.% and denote by $\mu$ and $\sigma^2$ the mean $\int_{\cube}f(\vx)d{\vx}$ and variance $\int_{\cube}(f(\vx)-\mu)^2d{\vx}$ of $f$.
 
@@
 \begin{align*}
-f_{\varnothing} &= \mathrm{E}[f(\vx)]= \mu, \\
-f_u(\vx) &= \int_{[0,1)^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).
+f_{\varnothing} &= \mathbb{E}[f(\vx)]= \mu, \\
+f_u(\vx) &= \int_{[0,1]^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).
 \end{align*}
-Due to orthogonality, applying the variance to equation \eqref{anova} leads to the variance decomposition of $f$:
-\[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1)^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
+Due to orthogonality, the variance of equation \eqref{anova} leads to the variance decomposition of $f$:
+\[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1]^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
 From this decomposition, one can express the following two quantities:
@@
 
-For $u \subsetneq \mathcal{D}$, the two quantities $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ measure the importance of variables in $\vx_u$.
-$\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$, that is the effect of all interactions between variables in $\vx_u$.
-$\ov{$\tau$}_u^2$ quantifies the main effect of $\vx_u$ plus the effect of all interactions between variables in $\vx_u$ and variables in $\vx_{-u}$.
+These two quantities $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ measure the importance of variables $\vx_u$.
+$\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$, that is the effect of all interactions between variables in $\vx_u$, and $\ov{$\tau$}_u^2$ quantifies the main effect of $\vx_u$ plus the effect of all interactions between variables in $\vx_u$ and variables in $\vx_{-u}$.
 
@@
 
-The problem of interest is the evaluation of first-order and total effect Sobol' indices.
-In our framework, we are only interested in single input indices, namely $|u|=1$.
-The computation of the normalized indices is performed based on the following integral formulas for their numerators:
+%The problem of interest is the evaluation of first-order and total effect Sobol' indices.
+In our framework, we are only interested in single input indices, namely $|u|=1$. The computation of the normalized indices is performed based on the following integral formulas for their numerators:
 \begin{align}
 \label{first.order}
-\underline{\tau}_u^2  &= \int_{[0,1)^{2d-1}} \left(f(\vx)-
-f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'_{-u}}, \\
+\underline{\tau}_u^2  &= \int_{[0,1]^{2d}} \left(f(\vx)-
+f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}, \\
 \label{total.effect}
-\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2 d\vx_u d{\vx'}, \ u \in \mathcal{D},
+\ov{$\tau$}_u^2 &= \frac{1}{2}\int_{[0,1]^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2 d\vx_u d{\vx'}, \ u \in \mathcal{D},
 \end{align}
@@
 \begin{aligned}
-\sigma^2 &= \int_{[0,1)^{d}} f(\vx)^2d{\vx} - \mu^2, \\
- \mu &= \int_{[0,1)^{d}} f(\vx) d{\vx},
+\sigma^2 &= \int_{[0,1]^{d}} f(\vx)^2d{\vx} - \mu^2, \\
+ \mu &= \int_{[0,1]^{d}} f(\vx) d{\vx},
 \label{eq.sigma.mu}
@@
 \end{gather}
-Usually the complexity of $f$ causes the computation of integrals \eqref{first.order}, (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable.
+Usually the complexity of $f$ causes the solution of integrals \eqref{first.order}, (\ref{total.effect}) and (\ref{eq.sigma.mu}) to be intractable.
 In such cases, one can instead estimate these quantities.
@@
 A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times.
-Each row of the design is a point $\vx_i$ in $[0,1)^d$ and each column of the design refers to a variable $x_j$.
-Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid [0,1)^{2d}$.
+Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to a variable $x_j$.
+Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$.
 One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
@@
 \end{equation}
-The estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$.
-Thus, for first order indices, one would need $3nd$ model evaluations.
-Using a combinatorial formalism, in \cite{Saltelli}, Saltelli proposes the following estimation strategy:
+Using this method, the estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$.
+Thus, for all first order and total effect indices, one would need $3nd$ model evaluations.
+Using a combinatorial formalism, in \cite{Saltelli} Saltelli proposes the following estimation strategy:
 \begin{theorem}
 \label{saltelli.theorem}
-The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allows to estimate all first-order and total effect Sobol' indices of order 1 at a cost of $n(d+2)$ evaluations of the model.
+The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allow to estimate all first-order and total effect Sobol' indices of order 1 at a cost of $n(d+2)$ evaluations of the model.
 \end{theorem}
+The main idea of the theorem is that there is no need to reevaluate $f({\vx}_i)$ and $f({\vx'}_i)$ for each $u$.
+Hence, we can simply evaluate $f({\vx}_i)$ $n$ times, $f({\vx'}_i)$ $n$ times, and $f(\vx_{i,u}:{\vx'}_{i,-u})$ $nd$ times, which accounts for the $n(d+2)$ evaluations.
+
 The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ accordingly to $u$.
-Indeed, there is no need of reevaluating $f({\vx}_i)$ and $f({\vx'}_i)$ for each $u$.
 While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input space dimension.
 
-An efficient alternative to evaluate all first-order indices was proposed by \cite{Mara} requiring only $2n$ model evaluations.
+A more efficient alternative to evaluate all first-order indices was proposed in \cite{Mara} and only requires $2n$ model evaluations.
 This alternative relies on the construction of two replicated designs.
 The notion of replicated designs was first introduced by McKay through its replicated Latin Hypercubes in \cite{McKay}.
-The definition we provide below generalizes the notion of replicated designs:
+In order to apply this definition to other types of points, in \cite{GJAHMP} we generalized this notion to:
 \begin{definition}
@@
 Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
-$[0,1)^{d}$.
+$[0,1]^{d}$.
 Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp.
@@
 $\mathcal{P}'$) indexed by $u$.
-We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if $\forall \ u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1)^a$.
+We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if for any $u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1]^a$.
 We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
@@
 The method introduced in \cite{Mara} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$.
-The key point of this method is to use the permutations resulting from the structure of the two replicated designs to mimic the hybrid points in formula (\ref{first.order.est}).
+The key point of this method is to use the permutations resulting from the structure of the two replicated designs to mimic the hybrid points in equation (\ref{first.order.est}).
 
 More precisely, let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$.
-Denote by $\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$.
+Denote by $\{y_i\}_{i=0}^{n-1}=$\\$\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{y'_i\}_{i=0}^{n-1}=\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$.
 From Definition \ref{rep.designs}, we know that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$.
-In addition, we define:
-\[\pi_u(f({\vx'}_i)) = f({\vx'}_{\pi_u(i)}), \qquad  i \in \{0,\dots,n-1\},\]
-then remark:
+Then,
 \begin{align*}
-\pi_u(f({\vx'}_i))&= f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u}), \\
+y'_{\pi_u(i)}&= f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u}) \\
 &= f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).
 \end{align*}
-Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) where \\ $\pi_u(f({\vx'}_i))$ is exactly $f(\vx_{i,u}:{\vx'}_{i,-u})$ without requiring further model evaluations.
+Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) by using $y'_{\pi_u(i)}$ instead of $f(\vx_{i,u}:{\vx'}_{i,-u})$ without requiring further model evaluations for each $u$.
 This estimation method has been deeply studied and generalized in Tissot et al.
 \cite{Tissot} to the case of closed second-order indices.
-In the following we refer to this method as replication procedure.
+In the following we will refer to this method as the replication procedure.
 
@@
 \label{sec:2.3}
-The aim of this paper is to propose a sequential procedure to estimate first-order and total effect Sobol' indices.
+The aim of this article is to propose a sequential procedure to estimate first-order and total effect Sobol' indices.
 A practical problem concerning the estimation of these indices is how large to choose the number of evaluations to ensure that Sobol' estimates are accurate enough.
 Asymptotical results show that Sobol' estimates are normally distributed (\cite[Proposition 2.2]{Janon}, \cite[Proposition 3.5]{Tissot}).
-As a consequence, confidence intervals can be used.
+As a consequence, errors can be estimated through confidence intervals.
+However, these error estimates are only guaranteed asymptotically as the number of model evaluations goes to infinity.
 
-An alternative to address this problematic is the use of sequential procedures.
-As examples, sequential versions of the replication procedure and McKay's procedure are respectively proposed in \cite{Gilquin.rec} and \cite{Tong}.
-However, in those two cases, the stopping criterion is a quantity of interest purely empirical, built directly upon the estimates.
+Additional sequential procedures are the replicated procedure and McKay's procedure respectively proposed in \cite{Gilquin.rec} and \cite{Tong}.
+Nevertheless, in those two cases, the stopping criterion is a quantity of interest purely empirical, built directly upon the estimates.
 Such stopping criteria often involve hyper-parameters difficult to tweak but more importantly, fail to guarantee any error bound on the estimates.
 
-Our sequential procedure stands apart from others with the construction of a robust stopping criterion.
+Our sequential procedure stands apart from others since it proposes a robust stopping criterion, not costly to compute.
 This criterion is an error bound based on the Walsh series decomposition of the integrands in (\ref{first.order}), (\ref{total.effect}) and (\ref{eq.sigma.mu}), and exploits the group properties of digital nets.
@@
 \]
-Each $\mathcal{P}_m$ has a group structure under the digit wise addition:
+Each $\mathcal{P}_m$ has a group structure under the digitwise addition:
 \[
@@
 
-In order to relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the relationship between any digital net and the \emph{wavenumber} space of non-negative integers $\mathbb{N}_0^d$.
-Hence, a dual net is
+To relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the relationship between any digital net and the \emph{wavenumber} space of non-negative integers $\mathbb{N}_0^d$.
+A dual net is
 \begin{align*}
 \mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vk}{\vx}=0,\, \vx\in\mathcal{P}_m\}, \\
-\ip{\vk}{\vx} = \sum_{j=1}^{d} \sum_{\ell=0}^{\infty} k_{j\ell}x_{j,\ell+1}  \pmod b.
+\ip{\vk}{\vx} = \sum_{j=1}^{d} \sum_{\ell=0}^{\infty} k_{j\ell}x_{j,\ell+1}  \pmod b,
 \end{align*}
-and inherits the same embedded structure as for the digital nets,
+and inherits the same embedded structure as for digital nets,
 \begin{equation}\label{dual_net_structure}
@@
 \end{equation}
-As shown in \cite[Sec. 3]{HicJim}, the group structure of the digital nets guarantees the property below affecting any Walsh basis $\varphi_{\vk}(\vx)=\e^{2 \pi \sqrt{-1} \ip{\vk}{\vx}/b}$,
+As shown in \cite[Sec. 3]{HicJim}, the group structure of digital nets guarantees the property below affecting any Walsh basis \\$\varphi_{\vk}(\vx)=\e^{2 \pi \sqrt{-1} \ip{\vk}{\vx}/b}$,
 \begin{equation}\label{basis_integ_prop}
@@
 \end{equation}
-Therefore, considering the Walsh decomposition for any $f\in \mathbb{L}^2([0,1]^d)$: \[
+
+Therefore, considering the Walsh decomposition of any $f\in \mathbb{L}^2([0,1]^d)$: \[
 f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
 and,
-\[ I(f) = \int_{\cube} f(\vx)\,d\vx,\]
+\[ I = \int_{\cube} f(\vx)\,d\vx,\]
 property \eqref{basis_integ_prop} leads to
@@
 \end{align}
-Based on the size of $\absolute{\hf_{\vk}}$ and the structure of the dual nets \eqref{dual_net_structure}, in \cite[Sec.
+Based on the size of $\absolute{\hf_{\vk}}$ and the structure of dual nets \eqref{dual_net_structure}, in \cite[Sec.
 4.1]{HicJim} we proposed an ordering of the wave-numbers $\vk(\cdot):\naturals_0\rightarrow\naturals_0^d$.
-This ordering will be helpful to address the summation in \eqref{3.1.err_bound}.
-To simplify notation, $\hf_{\kappa}=\hf_{\vk(\kappa)}$.
-This mapping leads to the following error bound,
+Defining $\hf_{\kappa}=\hf_{\vk(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,
 \begin{equation}
-\absolute{I(f) - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
+\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
 \end{equation}
-However, because the knowledge of the Walsh coefficients $\hf_{\kappa}$ is not assumed, we will estimate them using the fast transform obtained with the precomputed function values, and refer to them as $\tf_{m,\kappa}$.
+Nonetheless, because the knowledge of the Walsh coefficients $\hf_{\kappa}$ is not assumed, we will estimate them using the fast transform obtained with the precomputed function values, and refer to them as $\tf_{m,\kappa}$,
+\[
+\tf_{m,\kappa}=\tf_{m,\vk(\kappa)}=\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)\overline{\varphi_{\vk(\kappa)}(\vx)}.
+\]
 Note that for function values evaluated at $\mathcal{P}_m$, one only generates $b^m$ discrete Walsh coefficients $\tf_{m,\kappa}$.
@@
 \end{multline}
-for $\ell_* \in \mathbb{N}$, $\homega$ and $\wcomega$ two non-negative valued functions with $\lim_{m \to \infty} \wcomega(m) = 0$ and such that $\homega(r)\wcomega(r)<1$ for some $r\in\mathbb{N}$.
+for $\ell_* \in \mathbb{N}$, $\homega$ and $\wcomega$ two non-negative valued functions with $\lim_{m \to \infty} \wcomega(m) = 0$, and such that $\homega(r)\wcomega(r)<1$ for some fixed $r\in\mathbb{N}$.
 
-Hence, in \cite[Sec. 4.2]{HicJim} it is proved that for any $f\in\cc$,
+In \cite[Sec. 4.2]{HicJim} it is shown that for any $f\in\cc$,
 \begin{equation}
-\absolute{I(f) - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
-\le \frac{\tS_{\ell,m}(f)\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}=\epsilon_{I(f)}, \label{errbd}
+\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
+\le \tS_{\ell,m}(f)\underbrace{\frac{\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}}_{\mathfrak{C}(m)}=\epsilon_{I}, \label{errbd}
 \end{equation}
-where one may increase $m$ until the error bound $\epsilon_{I(f)}$ is small enough.
+where one may increase $m$ until the error bound $\epsilon_{I}$ is small enough.
 
@@
 For our problem, only Sobol' sequences \cite{Sobol'seq} have been considered.
-These are digital sequences defined in base $b=2$.
-Their major interest comes from their fast and easy implementation as well as their relatively slow growing size rate.
+Their major interest comes from their fast and easy implementation.
 Further details concerning Sobol' sequences can be found in \cite{Lemieuxbook,Niederreiter}.
@@
 \begin{align*}
-\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d-1}} \left(f(\vx)-
-f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'_{-u}}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
+\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d}} \left(f(\vx)-
+f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
 \underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
@@
 where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values.
-$\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over vector $\vI$.
-If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\vI}=(\epsilon_{I_1},\epsilon_{I_2},\epsilon_{I_3}$,\\ $\epsilon_{I_4})$ according to \ref{sec:3.1}, we know that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.
+$\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$.
+If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$,\\ $\epsilon_{\widehat{I}_4})$ according to \ref{sec:3.1}, we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.
 
-Then, alternatively to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
+Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
 \begin{gather}
 \begin{aligned}
-\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
-\varepsilon_{\underline{S}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
+\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
+\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
 \end{aligned}
@@
 \begin{aligned}
-\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
-\varepsilon_{\overline{S}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
+\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
+\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
 \end{aligned}
@@
 \end{gather}
-Because numerator and denominator are known to be positive, maximizing $\underline{S}_u(\vI)$ (resp.
+Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp.
 $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp.
@@
 $I_2$) and maximizes the denominator $I_3-I_4^2$.
-%As an example, Figure \ref{fig:1} below illustrate the maximization of $\underline{S}_u(\vI)$.
-%\begin{figure*}
-%\centering
-%\textbf{•}\includegraphics[width=1\textwidth]{Images/%estimator_3d_small.eps}
-% figure caption is below the figure
-%\caption{Estimator property.}
-%\label{fig:1}       % Give a unique label
-%\end{figure*}
+As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_u(\vI)$.
+\begin{figure}[!ht]
+\caption{Given the true value of $I_1$, the figure shows in blue the region of all possible values of $\underline{S}_u(\vI)$.
+There, $\underline{S}_u^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)}$ and $\underline{S}_u^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)}$.}
+\centering
+\includegraphics[width=.5\textwidth]{Images/estimator_3d_small.eps}
+\label{fig:1}       % Give a unique label
+\end{figure}
 
-Under the assumption that each integrand of $\vI$ is in $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}}_u + \varepsilon_{\underline{S}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}}_u + \varepsilon_{\overline{S}_u} \right] .\]
+Under the assumption that each integrand in $\underline{S}_u$ and $\overline{S}_u$ lies inside $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\widehat{\underline{S}}_u}, \widehat{\underline{S}}_u + \varepsilon_{\widehat{\underline{S}}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\widehat{\overline{S}}_u}, \widehat{\overline{S}}_u + \varepsilon_{\widehat{\overline{S}}_u} \right] .\]
 For the rest of the paper, we will consider $\widehat{\underline{S}}_u$ and $\widehat{\overline{S}}_u$   as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).
@@
 \label{sec:4}
-The sequential estimation procedure we propose combines the error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ presented in the previous section with either one of the two estimation strategies of section \ref{sec:2.2}: Saltelli's strategy and the replication procedure.
+The sequential estimation procedure we propose combines error bounds $\varepsilon_{\widehat{\underline{S}}_u}$ and $\varepsilon_{\widehat{\overline{S}}_u}$ presented in the previous section with either one of the two estimation strategies of section \ref{sec:2.2}: Saltelli's strategy and the replication procedure.
 
-We start by detailing our procedure in the form of an algorithm.
-Then, we discuss a possible improvement by considering a new estimator recently introduced in \cite{Owen} for the estimation of first-order indices.
+We start by detailing our procedure under the form of an algorithm.
+Then, we discuss a possible improvement by considering a new estimator introduced in \cite{Owen} for the estimation of first-order indices.
 
-\subsection{Sequential algorithm and its cost}
+\subsection{Sequential algorithm and cost}
 \label{sec:4.1}
@@
 Algorithm \ref{recursive.algorithm} summarizes the main steps of our sequential procedure.
-First, one must fix the tolerance $\epsilon >0$ for the Sobol' estimates.
-Then, we set $m=m_0$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ accordingly to the multiplicative approach detailed in \cite{GJAHMP}.
-Step $5$ corresponds to the recursive scheme of this approach.
-The choice of $m_0$ must be large enough to ensure that each integrand of $\vI$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).
+First, one must fix the tolerance $\epsilon >0$ at which Sobol' indices must be estimated.
+Then, we set $m=\ell_*+r$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}.
+The choice of $\ell_*$ must be large enough to ensure that each integrand of $\underline{S}_u$ and $\overline{S}_u$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).
 
-With this construction, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two independent Sobol' sequences.
-Furthermore, they possess the structure of two replicated designs of order $1$ (Definition \ref{rep.designs}).
+Under this construction, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two independent Sobol' sequences.
+Furthermore, they possess the structure of two replicated designs of order $1$, as shown in \cite{GJAHMP}.
+$\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can also be scrambled as long as both point sets share the same scrambling dimensionwise.
 \bigskip
@@
 
-In both cases we test if the respective error bounds $\varepsilon_{\underline{S}_u}$ and $\varepsilon_{\overline{S}_u}$ are lower than the tolerance $\epsilon$.
-For Variant $A$ the stopping criterion writes: $ \forall u \in \mathcal{D}, \varepsilon_{\underline{S}_u} \leq \epsilon \text{ and } \varepsilon_{\overline{S}_u} \leq \epsilon$,
-for Variant $B$ it writes:
-$ \forall u \in \mathcal{D}, \varepsilon_{\underline{S}_u} \leq \epsilon.$
+In both cases we always check if the respective error bounds $\varepsilon_{\widehat{\underline{S}}_u}$ and $\varepsilon_{\widehat{\overline{S}}_u}$ are lower than the tolerance $\epsilon$.
+For Variant $A$ the stopping criterion is $\varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon \text{ and } \varepsilon_{\widehat{\overline{S}}_u} \leq \epsilon$ for all $ u \in \mathcal{D}$.
+For Variant $B$ it is $\varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon$ for all $ u \in \mathcal{D}$.
 
@@
 \State choose $\epsilon >0$
-\State set: $m \leftarrow m_0$
+\State set: $m \leftarrow \ell_*+r$
 \State $bool \leftarrow false$
@@
 \If {Variant $A$}
-\State estimate $\widehat{\underline{S}}_u$ and $\widehat{\ov{$S$}}_u$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}) and Saltelli's strategy
-\State $bool_u \leftarrow \varepsilon_{\underline{S}_u} \leq \epsilon \ \& \ \varepsilon_{\overline{S}_u} \leq \epsilon$
+\State compute $\widehat{\underline{S}}_u$ and $\widehat{\ov{$S$}}_u$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}), and Saltelli's strategy
+\State $bool_u \leftarrow \varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon \ \& \ \varepsilon_{\widehat{\widehat{\overline{S}}}_u} \leq \epsilon$
 \EndIf
@@
 \State estimate $\widehat{\underline{S}}_u$ with formula (\ref{formula_undersu}) and the replication procedure
-\State $bool_u \leftarrow \varepsilon_{\underline{S}_u} \leq \epsilon$
+\State $bool_u \leftarrow \varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon$
 \EndIf
@@
 
-The cost of our algorithm varies whether Variant $A$ or Variant $B$ is selected.
+The cost of our algorithm, in terms of model evaluations, varies whether Variant $A$ or Variant $B$ is selected.
 To discuss this cost we note by $m^\star$ the ending iteration.
-If Variant $A$ is selected, the cost of our algorithm writes:
+If Variant $A$ is selected, the cost of our algorithm is:
 \[\sum \limits_{u \in \mathcal{D}} 2^{m_u} + 2 \times 2^{m^{\star}}, \qquad m^\star= \max \limits_{u \in \mathcal{D}} \ m_u,\]
@@
 
-If Variant $B$ is selected the cost of our algorithm equals $2 \times 2^{m^{\star}}$.
+If Variant $B$ is selected, the cost of our algorithm equals $2 \times 2^{m^{\star}}$.
 This cost corresponds to the one of the replication procedure introduced in Section \ref{sec:2.2}, where $2n=2\times 2^{m^{\star}}$ independent of $d$.
@@
 
-We focus on the use of a new estimator to evaluate small first-order Sobol' indices in Variant $A$.
-This estimator has recently been introduced by Owen in \cite{Owen} and is called ``Correlation 2".
-Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices.
-Our aim is to show that using ``Correlation 2" in Variant $A$ may reduce the total number of model evaluations.
-Its formula writes as follows:
+When $\underline{S}_u$ is small, it usually becomes harder to estimate.
+For this reason, we consider the use of a new estimator to evaluate small first-order Sobol' indices in Variant $A$.
+This estimator called ``Correlation 2" has been introduced by Owen in \cite{Owen}.
+In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices.
+Our aim is to show that the use of ``Correlation 2" in Variant $A$ may reduce the total number of model evaluations.
+This new estimator is,
 \begin{equation*}
@@
 \end{equation*}
-where $(\vx_i,{\vx'}_i, \vz_i) \iid [0,1)^{3d}$. It uses an extra set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.
+where $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$. It requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.
 \bigskip
@@
 We discuss below the potential improvement brought by using ``Correlation 2" in Variant $A$.
-The idea is to replace the current estimator (\ref{first.order.est}) by  ``Correlation 2" for each small first-order indices.
+The idea is to replace the current estimator (\ref{first.order.est}) by  ``Correlation 2" for each small first-order index.
 
@@
 We denote by $u_1,\dots,u_{\gamma}$ the indices of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$.
-The cost of Variant $A$ including ``Correlation 2" writes:
+The cost of Variant $A$ including ``Correlation 2" becomes,
 \begin{equation}
@@
 \end{itemize}
-Recall that the cost of Variant $A$ without  ``Correlation 2" writes:
+We recall the cost of Variant $A$ without  ``Correlation 2",
 \begin{equation}
@@
 \begin{itemize}
-\item[1)] for $j \in \Gamma$, the total effect index $\ov{$S$}_{u_j}$ requires as much or more evaluations than the first-order index $\underline{S}_{u_j}$.
+\item[1)] for $j \in \Gamma$, if the total effect index $\ov{$S$}_{u_j}$ requires as much or more evaluations than the first-order index $\underline{S}_{u_j}$.
 Since the total effect estimator is the same, as a consequence we have $m'_{u_j}=m_{u_j}$ and $c_j >0$.
-\item[2)] for $j \in \Gamma$, the total effect index $\ov{$S$}_{u_j}$ requires less evaluations than the first-order index $\underline{S}_{u_j}$.
+\item[2)] for $j \in \Gamma$, if the total effect index $\ov{$S$}_{u_j}$ requires less evaluations than the first-order index $\underline{S}_{u_j}$.
 In this case, if both $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ then $c_j \leq 0$.
@@
 Overall we expect to observe case $2)$ more often than case $1)$.
-Indeed, the numerator of $\underline{S}_u$ requires to estimate $2d-1$ dimensional integrals against only $d+1$ dimensional integrals for the numerator of $\ov{$S$}_u$.
+Indeed, the numerator of $\underline{S}_u$ requires to estimate $2d$ dimensional integrals against only $d+1$ dimensional integrals for the numerator of $\ov{$S$}_u$.
 Hence, it seems reasonable to expect that it will take less points to estimate $\ov{$S$}_u$ than $\underline{S}_u$.
 
-Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to always hold as ``Correlation 2" is shown in \cite{Owen} to perform better for small first-order indices.
-To support this discussion, illustrations of the use of ``Correlation 2" are presented in Section \ref{sec:5}.
+Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to usually hold as in \cite{Owen}, ``Correlation 2" is shown to perform better for small first-order indices.
+To support this discussion, numerical examples are presented in Section \ref{sec:5}.
 
@@
 To overcome this issue, we propose the following alternative for Variant $A$.
-If at the end of the first iteration, the estimate $\widehat{\underline{S}}_u$, $u \in \mathcal{D}$, is smaller than a threshold (here $0.1$), then estimator (\ref{first.order.est}) is switched for ``Correlation 2" and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+If at the end of the first iteration $\widehat{\underline{S}}_u$ is smaller than a threshold (in our case $0.1$, as suggested by Owen), then the estimator (\ref{first.order.est}) is switched to ``Correlation 2" for this particular $u$ and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
 
@@
 
-We propose to illustrate our sequential estimation procedure on two classical test functions and one real model. In each case, Sobol' indices are estimated with the following three variants:
+We illustrate our sequential estimation procedure with two classical test functions and one real example. In each case, Sobol' indices are estimated with the following three variants:
 \begin{itemize}
-\item[$\bullet$] Variant $A$ without using ``Correlation 2'', refers as Variant $A.a$, 
-\item[$\bullet$] Variant $A$ using ``Correlation 2'', refers as Variant $A.b$,
+\item[$\bullet$] Variant $A.a$ as Variant $A$ without using ``Correlation 2''. 
+\item[$\bullet$] Variant $A.b$ as Variant $A$ using ``Correlation 2''.
 \item[$\bullet$] Variant $B$.
@@
 
-For the two test functions, results of the three variants are compared based on estimation errors.
-These errors correspond to absolute difference between true values of indices and estimates.
-They are defined as follows:
+For the two test functions, results of the three variants are compared based on the true estimation errors.
+These errors correspond to the absolute difference between the true values and their estimates:
 $$\delta_{\underline{S}_u} = \absolute{\underline{S}_u - \widehat{\underline{S}_u}}, \qquad \delta_{\overline{S}_u} = \absolute{\overline{S}_u - \widehat{\overline{S}_u}}.$$
 We also compare the total number of evaluations of each variant.
-Results are averaged over $r=100$ repeats.
-For each repeat, we fix the tolerance $\varepsilon$ to $5.10^{-3}$ and set the starting size $m_0$ to $2^9$ (the Sobol' sequences are initiated with $512$ points).
+Results are averaged over $r=100$ repetitions using Owen's scrambled Sobol' sequences \cite{HonHic00a,Owe95}.
+For each repetition, we fix the tolerance $\varepsilon=5.10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points).
+The algorithm error bound factor is set to $\mathfrak{C}(m)=10\times 2^{-m}$.
 
-The failure rate of each variant is evaluated over the $100$ repeats.
-The failure rate is defined as the ratio of estimation errors failing to satisfy respectively $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$.
-Failure rates are denoted by $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$.
+The failure rates $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$ of each estimate are evaluated over the $100$ repetitions.
+These rates are the proportion of the repetitions in which the real errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$.
 
@@
 
-The two classical test functions considered are the g-function introduced by Sobol' \cite{Sobol'} and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
+The two classical test functions considered in this article are the g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
 The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.} function) and multiplicative (g-function).
@@
 When the value of $a_j$ gets closer to zero the variable $x_i$ becomes more influent.
-Here, the dimension is $d=6$ and values chosen for the $a_j$ are given by the following vector $(a_1=0,=a_2=0.5, a_3=3, a_4=9, a_5=99$, $a_6=99)$.
+For this example, we chose $d=6$ and $a_1=0,a_2=0.5, a_3=3, a_4=9, a_5=99$, and $a_6=99$.
 
@@
 The main observation is that both approaches give similar results both in terms of estimation errors, failure rates and total number of evaluations.
-The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ does not seem to bring any improvement.
-We propose to draw boxplots of estimation errors to further investigate the results.
+The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ does not seem to bring much improvement.
+We propose to draw boxplots of the estimation errors to further investigate the results.
 
@@
 \end{table}
-Looking at the results, using Variant $B$ leads to higher estimation errors and higher failure rates than those obtained with Variant $A.a$ or Variant $A.b$.
-The compromise is a total number of evaluations twice as small.
+The results show that the use of Variant $B$ leads to slightly higher estimation errors and higher failure rates than those obtained with Variant $A.a$ or Variant $A.b$.
+However, the total number of evaluations is twice as small.
 As such, this approach remains interesting when one wants to estimate only first-order indices.
@@
 
-For the second example, we consider the Bratley \textit{et al.} function defined by:
+In this second example, we consider the Bratley \textit{et al.} function defined by,
 $$f(x_1,\dots,x_d)=\sum \limits_{i=1}^{d} (-1)^i \prod \limits_{j=1}^{i} x_j \ .$$
@@
 
-As for the g-function, Tables \ref{res.bratley.Aa} and \ref{res.bratley.Ab} show averaged estimation errors and averaged total number of evaluations for Variant $A.a$ and Variant $A.b$.
+As for the g-function, Tables \ref{res.bratley.Aa} and \ref{res.bratley.Ab} show averaged estimation errors and total number of evaluations for Variant $A.a$ and Variant $A.b$.
 \begin{table}[!ht]
@@
 \end{table}
-Variant $A.b$ gives lower estimation errors and fewer failures than Variant $A.a$ on the four small first-indices $\underline{S}_3,\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''.
+Variant $A.b$ gives lower estimation errors and fewer failure rates than Variant $A.a$ on the four small first-indices $\underline{S}_3,\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''.
 The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $71\%$ against only $4\%$ for Variant $A.b$.
@@
 The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$.
-Failure rates are similar to those of Variant $A.a$.
-Since the total number of evaluations is close to the one of Variant $A.b$, the conclusion is that Variant $B$ does not bring any improvement for this example.
+Failure rates are similar to those of Variant $A.b$.
+Since the total number of evaluations is close to the one of Variant $A.b$, the conclusion is that Variant $B$ does not bring much improvement for this example.
 \bigskip
 
-From the results on these two functions test, the main conclusion is that Variant $A.b$ performs the best.
-This highlights the efficiency of ``Correlation 2'' to estimate small first-order indices.
-Even if ``Correlation 2'' originally requires more samples, this drawback is completely overridden when this estimator is included into a sequential procedure such as ours.
+From the results on these two test functions, the main conclusion is that Variant $A.b$ performs the best.
+This highlights the efficiency of ``Correlation 2'' to estimate small first-order indices with quasi-Monte Carlo methods.
+Even if ``Correlation 2'' originally requires more model evaluations, this drawback is completely overridden when this estimator is included into a sequential procedure such as ours.
 
@@
 \label{sec:5.2}
+
 As a real case example, we will study the payoff function of an arithmetic mean Asian call option.
-
-For a discretized Brownian motion $\vect{B}=(B_{t_1}, B_{t_2},\dots, B_{t_d})$ at given times $t_1,\dots,t_d$, the payoff of the option is:
+For a discretized Brownian motion $\vect{B}=(B_{t_1}, B_{t_2},\dots, B_{t_d})$ at times $t_i=T\times i/d$, the payoff of the option is:
 
 \[
-f_{\rm payoff}(\vect{B}) = \max\left(\frac{1}{d}\sum_{i=1}^d S_0\e^{(r-\sigma^2/2)t_i+\sigma B_{t_i}}-K, 0\right)
+f_{\rm payoff}(\vect{B}) = \e^{-rT}\max\left(\frac{1}{d}\sum_{i=1}^d S_0\e^{(r-\sigma^2/2)t_i+\sigma B_{t_i}}-K, 0\right)
 \]
+where $T$ is the maturity of the option, $S_0$ is the initial stock price, $\sigma$ the volatility of the stock, $r$ the interest rate, and $K$ the strike price.
 
-The Brownian motion is widely used in many applications.
-Thus, the following example might be interesting to understand what Sobol' indices can explain in some of these applications.
-For instance, if we want to estimate the expected value of the maximum of a discretized Brownian motion whose covariance matrix is $\Sigma$, our goal is to estimate
-\begin{align*}
-\mathbb{E} \left[\max(\vect{B}_t)\right] &= \int_{\mathbb{R}^d} \max(\vect{B}_t) \frac{{\rm e}^{\vect{B}_t^T\Sigma^{-1}\vect{B}_t}}{(2\pi)^{d/2}|\Sigma|^{1/2}}\,d\vect{B}_t \\
-&= \int_{[0,1]^d} \max(f_{\rm Chol}(\vx)) \,d\vx \\
-&= \int_{[0,1]^d} \max(f_{\rm PCA}(\vx)) \,d\vx.
-\end{align*}
-The last two equalities are obtained through two different subsitutions corresponding to the \textit{Cholesky} construction of the Brownian motion, and the \textit{PCA} construction.
-For instance, if we take 10 dimensions and $t_i=i/10$, using the Cholesky construction $S_{1} = 24\%$, $S_{2} = 16\%$, $S_{3} = 13\%$, $S_{4} = 10\%$, and $\overline{S}_{1}=24\%$, $\overline{S}_{2}=18\%$, $\overline{S}_{3}=15\%$, $\overline{S}_{4} = 13\%$.
-However, using the PCA construction, $S_{1} = 89\%$, $S_{2} = 2\%$, $S_{3} = 1\%$, $S_{4} = 0\%$, and $\overline{S}_{1}=94\%$, $\overline{S}_{2}=7\%$, $\overline{S}_{3}=3\%$, $\overline{S}_{4} = 2\%$.
-This shows that the PCA construction will be better to estimate the above expectation using quasi-Monte Carlo methods since it has a lower effective dimensionality.
+The discretized Brownian motion $\vect{B}$ follows a multivariate normal distribution with mean $\vzero$ and covariance matrix $\mathsf{\Sigma}$, with $\mathsf{\Sigma}_{ij}=\min(t_i,t_j)$.
+If $\vect{Y}\sim N(\vzero,I_d)$, given a matrix $M$ such that $\mathsf{\Sigma}=MM^t$, then $M\vect{Y}\sim N(\vzero,\mathsf{\Sigma})$.
+Hence, we can generate the discretized Brownian motion using the inverse normal cumulative distribution function $\phi^{-1}$: $\vect{B}\sim M\phi^{-1}(\vect{X})$ with $\phi^{-1}(\vect{X})=(\phi^{-1}(X_1),\dots,\phi^{-1}(X_d))^t$ and $\vect{X}\sim \mathcal{U}([0,1]^d)$.
+Thus, we can estimate the Sobol' indices over $f_{\rm payoff}(M\phi^{-1}(\vect{X}))$.
 
-For those who were curious about the actual value of $\mathbb{E} \left[\max(\vect{B}_t)\right]$, it is approximately 0.5935.
-Nevertheless, the Brownian Motion is a continuous time process.
-Thus, in order to estimate the expected value on a continuous time Browninan motion, one could either use a multilevel method, or a multivariate decomposition method to estimate this infinite dimensional integral.
+Tables \ref{res.AsianChol.Aa}, \ref{res.AsianChol.Ab}, and \ref{res.AsianChol.B} show the results when $M$ corresponds to the Cholesky decomposition of $\mathsf{\Sigma}$.
+
+\begin{table}[!ht]
+\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and number of evaluations of Variant $A.a$ with Cholesky decomposition.}
+\centering
+\begin{tabular}{ccccc}
+\hline
+ input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
+ $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
+ $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
+ $x_3$ & $0.0820$ & $37356$ & $0.3150$ & $65536$ \\ \hline
+ $x_4$ & $0.0408$ & $16742$ & $0.1950$ & $33096$ \\ \hline
+ $x_5$ & $0.0142$ & $5980$ & $0.0944$ & $16384$ \\ \hline
+ $x_6$ & $0.0048$ & $1106$ & $0.0257$ & $1654$ \\ \hline \hline
+%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
+\end{tabular}
+\label{res.AsianChol.Aa}
+\end{table}
+
+\begin{table}[!ht]
+\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and number of evaluations of Variant $A.b$ with Cholesky decomposition.}
+\centering
+\begin{tabular}{ccccc}
+\hline
+ input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
+ $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
+ $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
+ $x_3$ & $0.0822$ & $34406$ & $0.3150$ & $65536$ \\ \hline
+ $x_4$ & $0.0434$ & $13107$ & $0.1950$ & $33423$ \\ \hline
+ $x_5$ & $0.0169$ & $2371$ & $0.0944$ & $16384$ \\ \hline
+ $x_6$ & $0.0049$ & $532$ & $0.0259$ & $1577$ \\ \hline \hline
+%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
+\end{tabular}
+\label{res.AsianChol.Ab}
+\end{table}
+
+\begin{table}[!ht]
+\caption{Averaged values of $\widehat{\underline{S}}_u$ and number of evaluations of Variant $B$ with Cholesky decomposition.}
+\centering
+\begin{tabular}{ccc}
+\hline
+ input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
+ $x_1$ & $0.2120$ & $131072$ \\ \hline
+ $x_2$ & $0.1350$ & $129766$ \\ \hline
+ $x_3$ & $0.0774$ & $62290$ \\ \hline
+ $x_4$ & $0.0338$ & $49961$ \\ \hline
+ $x_5$ & $0.0149$ & $48845$ \\ \hline
+ $x_6$ & $0.0028$ & $17905$ \\ \hline \hline
+%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
+\end{tabular}
+\label{res.AsianChol.B}
+\end{table}
+
+Variant $A.b$ is the best because the total number of evaluations.................
+
+It is also interesting to see the Sobol' indices estimates when $M$ is constructed with the PCA decomposition. For this case, we only show the results for Variant $A.b$ in table \ref{res.AsianPCA.Ab}.
+
+\begin{table}[!ht]
+\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and number of evaluations of Variant $A.b$ with PCA decomposition.}
+\centering
+\begin{tabular}{ccccc}
+\hline
+ input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
+ $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
+ $x_2$ & $0.0034$ & $512$ & $0.0172$ & $824$ \\ \hline
+ $x_3$ & $0.0004$ & $512$ & $0.0023$ & $512$ \\ \hline
+ $x_4$ & $0.0001$ & $512$ & $0.0005$ & $512$ \\ \hline
+ $x_5$ & $0.0000$ & $512$ & $0.0001$ & $512$ \\ \hline
+ $x_6$ & $0.0000$ & $512$ & $0.0000$ & $512$ \\ \hline \hline
+%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
+\end{tabular}
+\label{res.AsianPCA.Ab}
+\end{table}
+
+One may conclude that these estimates explain how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.
 
@@
 
-The sequential estimation procedure proposed in this paper offers a practical solution with the construction of an error bound for the Sobol' indices.
+The sequential estimation procedure proposed in this article offers a practical solution with the construction of an estimator and error bound for Sobol' indices.
 The number of points is progressively augmented until the error bound becomes lower than a user specified tolerance.
 The procedure presented combines Sobol' sequences with either Saltelli's strategy to estimate both first-order and total effect indices, or the replication procedure to estimate only first-order indices.
-Furthermore, we investigated the use of a recent estimator well-suited to the estimation of small first-order indices.
+Furthermore, we investigated the use of a recent estimator well-suited to the estimation of small first-order indices using quasi-Monte Carlo methods.
 The efficiency of this estimator, called ``Correlation 2'', was assessed and highlighted on two test functions and a real case model.
 The variant combining Saltelli's strategy and ``Correlation 2'' gave the best results with low failure rates across all indices.
+
+As a future project, the same estimators and algorithms can be designed for rank-1 lattices using the results in \cite{JimHic}, and noticing that rank-1 lattices of the same size are also replicated designs of order 1.
 
@@
 Hickernell, F.J., Jim\'enez Rugama, Ll.A.: Reliable Adaptative Cubature Using Digital Sequences: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 367-383 (2016)
+\bibitem{HonHic00a}
+H.S. Hong, F.J. Hickernell.: Algorithm 823: Implementing scrambled digital nets, ACM Trans. Math. Software, vol. 29, 95-109, (2003)
 \bibitem{Hoeffding}
@@
 Janon, A., Klein, T., Lagnoux A., Nodet, M., Prieur C.: Asymptotic normality and efficiency of two {S}obol' index estimators, ESAIM Probab. Stat. \textbf{18}, 342-364 (2014)
+\bibitem{JimHic}
+Jim\'enez Rugama, Ll.A., Hickernell, F.J.: Adaptive Multidimensional Integration Based on Rank-1 Lattices: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 407-422 (2016)
 \bibitem{Lemieuxbook}
@@
 Niederreiter, H.: Random Number Generation and Quasi-Monte Carlo Methods: CBMS-NSF Regional Conference Series in Applied Math., vol. 63, SIAM, Philadelphia (1992)
+\bibitem{Owe95}
+A.B. Owen.: Randomly permuted $(t,m,s)$-nets and $(t,s)$-sequences: Monte Carlo and Quasi-Monte Carlo Methods in Scientific Computing, vol. 106, 299-317 (1995)
 \bibitem{Owen}

### 2016-09-30 FunctionsTest/SI_all_example_percentage.m

@@ -9,7 +9,7 @@ threshold_small = 0.; % Below which sizes do we use correl2 estimator
 wronga = 0; % Wrong estimates with all indices method
 wrong = 0; % Wrong estimates using the one by one algo
 s = .0; %time in seconds used delay each function evaluation
-samples = 100;
+samples = 1;
 
 fudge = @(m,d) 10*2.^-(1.*m);
 

### 2016-09-30 FunctionsTest/testing_sobInd_arit_asian.m

@@ -1,0 +1,65 @@
+abstol = 5*1e-3;
+pre = 3; % Precision to display according to 1*1e-3 (3 digits)
+reltol = 0e-2; % Pure absolute tolerance
+mmin = 9;
+mmax = 24; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
+samples = 100;
+fudge = @(m,d) 10*2.^-(1.*m);
+d = 6;
+
+inp.timeDim.timeVector = 1/52:1/52:d*1/52; %weekly monitoring for 1 year
+inp.assetParam.initPrice = 36; %initial stock price
+inp.assetParam.interest = 0.06; %risk-free interest rate
+inp.assetParam.volatility = 0.5; %volatility
+inp.payoffParam.strike = 40; %strike price
+inp.priceParam.cubMethod = 'Sobol'; %Sobol sampling
+inp.bmParam.assembleType = 'PCA';
+EuroCall = optPrice(inp); %construct an optPrice object 
+
+opt = optPayoff(EuroCall); %make a copy
+opt.payoffParam = struct('optType',{{'amean'}}, 'putCallType',{{'call'}}); 
+
+f =@(x) genOptPayoffs(opt,x);
+hyperbox = [zeros(1,d) ; ones(1,d)];
+
+%% Testing without small indices estimator
+SI = zeros(2, d);
+SI_n = SI;
+tic
+for k = 1:samples
+    [q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d), 'threshold_small', 0);
+    SI = SI + q;
+    SI_n = SI_n + out_param.n;
+end
+toc
+SI = SI/samples; SI_n = SI_n/samples;
+round(SI, pre, 'significant')
+round(SI_n)
+
+%% Testing with small indices estimator
+SI = zeros(2, d);
+SI_n = SI;
+tic
+for k = 1:samples
+    [q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d), 'threshold_small', 0.1);
+    SI = SI + q;
+    SI_n = SI_n + out_param.n;
+end
+toc
[…]

### 2016-09-30 article/Images/article_scheme_S_3D.m

@@ -1,4 +1,4 @@
-set(0,'defaultaxesfontsize',16,'defaulttextfontsize',16) %make font larger
+set(0,'defaultaxesfontsize',20,'defaulttextfontsize',20) %make font larger
 set(0,'defaultLineLineWidth',3) %thick lines
 set(0,'defaultTextInterpreter','latex') %latex axis labels
 set(0,'defaultLegendInterpreter','latex') %latex axis labels
@@ -29,102 +29,85 @@ zmin = min(min(S(X, Y))); zmax = max(max(S(X, Y)));
 
 ax = gca;
 set(ax,'TickLabelInterpreter', 'Latex');
-ax.XTick = sort([I(1)-err(1) Ireal(1) I(1) I(1)+err(1)]);
-ax.YTick = sort([I(2)-err(2) Ireal(2) I(2) I(2)+err(2)]);
+% ax.XTick = sort([I(1)-err(1) Ireal(1) I(1) I(1)+err(1)]);
+ax.XTick = sort([I(1)-err(1) Ireal(1) I(1)+err(1)]);
+% ax.YTick = sort([I(2)-err(2) Ireal(2) I(2) I(2)+err(2)]);
+ax.YTick = sort([I(2)-err(2) Ireal(2) I(2)+err(2)]);
 if S(Ireal(1),Ireal(2)) < Smax & S(Ireal(1),Ireal(2)) > Smin % Not the...
     % same value as Smax and Smin for the Zaxis
-    ax.ZTick = sort([Smin S(Ireal(1),Ireal(2)) (Smin+Smax)/2 S(I(1),I(2)) Smax]);
+%     ax.ZTick = sort([Smin S(Ireal(1),Ireal(2)) (Smin+Smax)/2 S(I(1),I(2)) Smax]);
+    ax.ZTick = sort([Smin (Smin+Smax)/2 Smax]);
 else
-    ax.ZTick = sort([Smin (Smin+Smax)/2 S(I(1),I(2)) Smax]);
+%     ax.ZTick = sort([Smin (Smin+Smax)/2 S(I(1),I(2)) Smax]);
+    ax.ZTick = sort([Smin (Smin+Smax)/2 Smax]);
 end
 if Ireal(1) < I(1) % Ireal is indeed I, and variable I corresponds to I hat
[…]

### 2016-09-30 kuo_code/generating_C_Sobol.m
Old material to commit

@@ -1,9 +1,8 @@
 %% Construction of C generating matrices
 s = 28; % Number of matrices for which we generate the Sobol' seq generator
-m = 12; % Number of digits used to generate the seq up to 2^m points
+m = 20; % Number of digits used to generate the seq up to 2^m points
 entry_file = 'new-joe-kuo-6.21201'; % joe-kuo-old.1111 new-joe-kuo-6.21201
 A = txt2mat(entry_file);
-
 
 %% We take the generator values to the struct C
 for k = 1:size(A,1)
@@ -54,7 +53,7 @@ end
 % end
 % dlmwrite('C_matrices_R.txt',C_text,'delimiter',' ');
 
-%% Checking the points generated by Matlab and ours
+% %% Checking the points generated by Matlab and ours
 % x = zeros(2^m,s);
 % for n = 1:2^m-1
 %     vec_n = (dec2bin(n)- '0');
@@ -65,27 +64,49 @@ end
 % end
 % sob = sobolset(s);
 % x_check = net(sob,2^m);
-% disp(x-x_check)
+% disp(norm(x-x_check))
 
 %% Evaluating t-values and creating the t-values table
-t_table(1).t = [];
-for dim = 2:s
-    t_table(dim).t = [];
-    for j = 1:dim - 1
-        t_table(dim).t = [t_table(dim).t, t_value(C(j).C,C(dim).C,m)];
+t_values_table = zeros(s,s);
+% t_table(1).t = [];
+for dim = 1:s
+    disp(dim)
+    for dim2 = 1:s
+        if dim <= dim2;
+            t_values_table(dim,dim2) = 0;
+        else
+            t_values_table(dim,dim2) = t_value(C(dim).C,C(dim2).C,m);
+        end
+    %     t_table(dim).t = [];
+    %     for j = 1:dim - 1
+    %         t_table(dim).t = [t_table(dim).t, t_value(C(j).C,C(dim).C,m)];
+    %     end
+    %     disp(t_table(dim).t)
     end
-    disp(t_table(dim).t)
 end
 
-% dim1 = 14;
-% dim2 = 28;
-% x = zeros(2^m,2);
-% for n = 1:2^m-1
-%     vec_n = (dec2bin(n)- '0');
-%     vec_n = fliplr(vec_n)';
-%     for j = [dim1 dim2]
[…]

### 2016-09-30 kuo_code/optimizing_dim.m

@@ -1,0 +1,54 @@
+s = 25; % Number of matrices for which we generate the Sobol' seq generator
+m = 20; % Number of digits used to generate the seq up to 2^m points
+
+weight_matrix = (s-1)*ones(2*s,2*s);
+weight_matrix(1:s,1:s) = s;
+weight_matrix(s+1:end,s+1:end) = s-2;
+weight_matrix(1:2*s+1:4*s*s) = 0;
+% for i = 1:2*s
+%     for j = 1:2*s
+%         if j >= i
+%             weight_matrix(i,j) = 0;
+%         end
+%     end
+% end
+
+table_t_values_file = sprintf('tval_table_s%d_m%d.mat',2*s,m);
+if exist(table_t_values_file)
+    load(table_t_values_file)
+else
+    error('No t-values table found to optimize.')
+end
+
+initial_value = sum(sum(t_values_table.*weight_matrix));
+fname1 = sprintf('better_permutations_s%d_m%d.mat',s,m);
+fname2 = sprintf('weight_values_s%d_m%d.mat',s,m);
+if exist(fname1)
+    load(fname1)
+end
+if exist(fname2)
+    load(fname2)
+end
+better_values = [];
+new_permutations = [];
+fraction = 1/2; % fraction of s dimensions that we keep their order at the beginning
+tic
+parfor i = 1:20000000
+    p = [1:floor(s*fraction) floor(s*fraction)+randperm(s+ceil(s*(1-fraction)))];
+    new_value = sum(sum(t_values_table(p,p).*weight_matrix));
+    if initial_value > new_value;
+        disp(new_value)
+        better_values = [better_values; new_value];
+        new_permutations = [new_permutations; p];
+    end
+end
+toc
+
+values = [values; better_values];
+permutations = [permutations; new_permutations];
+[~,I] = sort(values); % we only keep the best n weighted values
+n = min(size(values,1),5); % we keep the best 5 values or less if we have less
+values = values(I(1:n));
+permutations = permutations(I(1:n),:);
+save(fname1, 'permutations')
+save(fname2, 'values')

### 2016-09-30 kuo_code/test_t_values_replicated.m

@@ -1,0 +1,88 @@
+% %% Construction of C generating matrices
+% s = 28; % Number of matrices for which we generate the Sobol' seq generator
+% m = 12; % Number of digits used to generate the seq up to 2^m points
+% entry_file = 'new-joe-kuo-6.21201'; % joe-kuo-old.1111 new-joe-kuo-6.21201
+% A = txt2mat(entry_file);
+% 
+% %% We take the generator values to the struct C and generate matrices Cs
+% for k = 1:size(A,1)
+%     C(k + 1).d = A(k,1); % Dimension
+%     C(k + 1).s = A(k,2); % Polynomial degree
+%     C(k + 1).a = A(k,3); % Polynomial coefficients assuming a = a_d-1 * 2^0 + a_d-2 * 2^1 + ... + a_1 2^d-2
+%     aa = find(isnan(A(k,:))==1);
+%     if ~isempty(aa)
+%         C(k + 1).m = A(k,4:aa(1) - 1); % Initial directional numbers m_i
+%     else
+%         C(k + 1).m = A(k,4:end);
+%     end
+% end
+% 
+% C(1).C = eye(m); C(1).d = 1; C(1).s = 0; C(1).a = []; C(1).m = 1;
+% C(2).C = C(1).C;
+% % I generate C(2).C manually
+% for i = 2:m
+%     C(2).m = [C(2).m bitxor(2*C(2).m(end),C(2).m(end))];
+%     aa = (dec2bin(C(2).m(i))- '0')';
+%     empty = i - size(aa,1);
+%     C(2).C(1:i,i) = [zeros(empty,1); aa];
+% end
+% 
+% % Generate C(j).C matrices for j = 3:s
+% for j = 3:s % For each dimension
+%     C(j).C = C(1).C;
+%     for i = 2:m % for each column of C(j).C
+%         if i > size(C(j).m,2)
+%             vec_a = dec2bin(C(j).a)- '0';
+%             if size(vec_a,2) < C(j).s - 1
+%                 vec_a = [zeros(1,C(j).s-size(vec_a,2)-1), vec_a];
+%             end
+%             vec_a = [(vec_a), 1, 1].*[2.^(1:C(j).s), 1]; % Matlab mistake: [fliplr(vec_a), 1, 1].*[2.^(1:C(j).s), 1]
[…]

### 2016-09-30 article/article_for_submission.tex
Little typo
Laurent last changes before advisors review

@@
 \absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
-\le \tS_{\ell,m}(f)\underbrace{\frac{\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}}_{\mathfrak{C}(m)}=\epsilon_{I}, \label{errbd}
+\le \tS_{\ell,m}(f)\underbrace{\frac{\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}}_{\mathfrak{C}(m)}=\epsilon_{\widehat{I}}, \label{errbd}
 \end{equation}
@@
 $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$.
-If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$,\\ $\epsilon_{\widehat{I}_4})$ according to \ref{sec:3.1}, we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.
+If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$,\\ $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.
 
@@
 $I_2$) and maximizes the denominator $I_3-I_4^2$.
-As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_u(\vI)$.
+As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_u(\vI)$ given the true value of $I_1$.
 \begin{figure}[!ht]
@@
 \centering
-\includegraphics[width=.5\textwidth]{Images/estimator_3d_small.eps}
+\includegraphics[width=.5\textwidth]{Images/estimator_3d_small.pdf}
 \label{fig:1}       % Give a unique label
@@
 We also compare the total number of evaluations of each variant.
-Results are averaged over $r=100$ repetitions using Owen's scrambled Sobol' sequences \cite{HonHic00a,Owe95}.
+Results are averaged over $100$ repetitions using Owen's scrambled Sobol' sequences \cite{HonHic00a,Owe95}.
 For each repetition, we fix the tolerance $\varepsilon=5.10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points).
@@
 \begin{table}[!ht]
-\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and averaged total number of evaluations for Variant $B$.}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
 \centering
@@
 Thus, we can estimate the Sobol' indices over $f_{\rm payoff}(M\phi^{-1}(\vect{X}))$.
+We propose to analyze the results with averaged Sobol' estimates and averaged total number of evaluations over $100$ repetitions.
+The tolerance $\varepsilon$ and parameters $\ell^*$, $r$ and $\mathfrak{C}(m)$ are set as previously.
 
 Tables \ref{res.AsianChol.Aa}, \ref{res.AsianChol.Ab}, and \ref{res.AsianChol.B} show the results when $M$ corresponds to the Cholesky decomposition of $\mathsf{\Sigma}$. 
-
 \begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and number of evaluations of Variant $A.a$ with Cholesky decomposition.}
-\centering
-\begin{tabular}{ccccc}
+\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and total number of evaluations of Variant $A.a$ with Cholesky decomposition.}
+%\centering
+%\begin{tabular}{ccccc}
+%\hline
+% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
+% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
+% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
+% $x_3$ & $0.0820$ & $37356$ & $0.3150$ & $65536$ \\ \hline
+% $x_4$ & $0.0408$ & $16742$ & $0.1950$ & $33096$ \\ \hline
+% $x_5$ & $0.0142$ & $5980$ & $0.0944$ & $16384$ \\ \hline
+% $x_6$ & $0.0048$ & $1106$ & $0.0257$ & $1654$ \\ \hline \hline
+\centering
+\begin{tabular}{ccc}
 \hline
- input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
- $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
- $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
- $x_3$ & $0.0820$ & $37356$ & $0.3150$ & $65536$ \\ \hline
- $x_4$ & $0.0408$ & $16742$ & $0.1950$ & $33096$ \\ \hline
- $x_5$ & $0.0142$ & $5980$ & $0.0944$ & $16384$ \\ \hline
- $x_6$ & $0.0048$ & $1106$ & $0.0257$ & $1654$ \\ \hline \hline
-%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
+ input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
+ $x_1$ & $0.2120$ & $0.5650$  \\ \hline
+ $x_2$ & $0.1370$ & $0.4420$  \\ \hline
+ $x_3$ & $0.0820$ & $0.3150$  \\ \hline
+ $x_4$ & $0.0408$ & $0.1950$  \\ \hline
+ $x_5$ & $0.0142$ & $0.0944$  \\ \hline
+ $x_6$ & $0.0048$ & $0.0257$  \\ \hline \hline
+\multicolumn{3}{l}{Total number of evaluations: $648 \ 821$} \\ \hline 
 \end{tabular}
@@
 \end{table}
-
 \begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and number of evaluations of Variant $A.b$ with Cholesky decomposition.}
-\centering
-\begin{tabular}{ccccc}
+\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with Cholesky decomposition.}
+%\centering
+%\begin{tabular}{ccccc}
+%\hline
+% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
+% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
+% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
+% $x_3$ & $0.0822$ & $34406$ & $0.3150$ & $65536$ \\ \hline
+% $x_4$ & $0.0434$ & $13107$ & $0.1950$ & $33423$ \\ \hline
+% $x_5$ & $0.0169$ & $2371$ & $0.0944$ & $16384$ \\ \hline
+% $x_6$ & $0.0049$ & $532$ & $0.0259$ & $1577$ \\ \hline \hline
+ \centering
+\begin{tabular}{ccc}
 \hline
- input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
- $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
- $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
- $x_3$ & $0.0822$ & $34406$ & $0.3150$ & $65536$ \\ \hline
- $x_4$ & $0.0434$ & $13107$ & $0.1950$ & $33423$ \\ \hline
- $x_5$ & $0.0169$ & $2371$ & $0.0944$ & $16384$ \\ \hline
- $x_6$ & $0.0049$ & $532$ & $0.0259$ & $1577$ \\ \hline \hline
-%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
+ input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$  \\ \hline
+ $x_1$ & $0.2120$ & $0.5650$  \\ \hline
+ $x_2$ & $0.1370$ & $0.4420$ \\ \hline
+ $x_3$ & $0.0822$ & $0.3150$  \\ \hline
+ $x_4$ & $0.0434$ & $0.1950$  \\ \hline
+ $x_5$ & $0.0169$ & $0.0944$  \\ \hline
+ $x_6$ & $0.0049$ & $0.0259$  \\ \hline \hline
+\multicolumn{3}{l}{Total number of evaluations: $699 \ 487$}\\ \hline 
 \end{tabular}
@@
 \end{table}
-
 \begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$ and number of evaluations of Variant $B$ with Cholesky decomposition.}
-\centering
-\begin{tabular}{ccc}
+\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with Cholesky decomposition.}
+%\centering
+%\begin{tabular}{ccc}
+%\hline
+% input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
+% $x_1$ & $0.2120$ & $131072$ \\ \hline
+% $x_2$ & $0.1350$ & $129766$ \\ \hline
+% $x_3$ & $0.0774$ & $62290$ \\ \hline
+% $x_4$ & $0.0338$ & $49961$ \\ \hline
+% $x_5$ & $0.0149$ & $48845$ \\ \hline
+% $x_6$ & $0.0028$ & $17905$ \\ \hline \hline
+ \centering
+\begin{tabular}{cc}
 \hline
- input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
- $x_1$ & $0.2120$ & $131072$ \\ \hline
- $x_2$ & $0.1350$ & $129766$ \\ \hline
- $x_3$ & $0.0774$ & $62290$ \\ \hline
- $x_4$ & $0.0338$ & $49961$ \\ \hline
- $x_5$ & $0.0149$ & $48845$ \\ \hline
- $x_6$ & $0.0028$ & $17905$ \\ \hline \hline
-%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
+ input & $\widehat{\underline{S}}_u$ \\ \hline
+ $x_1$ & $0.2120$ \\ \hline
+ $x_2$ & $0.1350$ \\ \hline
+ $x_3$ & $0.0774$ \\ \hline
+ $x_4$ & $0.0338$ \\ \hline
+ $x_5$ & $0.0149$ \\ \hline
+ $x_6$ & $0.0028$ \\ \hline \hline
+\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
 \end{tabular}
@@
 \end{table}
-
-Variant $A.b$ is the best because the total number of evaluations.................
+It turns out that Variant $A.b$ does not better than Variant $A.a$.
+Averaged Sobol' estimates are similar while the averaged number of model evaluations is slightly worse.
+The explanation is that total effect Sobol' indices require more evaluations than their corresponding first-order indices.
+As such, ``Correlation 2'' falls into case 1) explained in Section \ref{sec:4.2}.
+Variant $B$ shows a drastic improvement on the total number of evaluations with the drawback of a false estimation for input $x_4$.
+Indeed, the discrepancy is higher than $\epsilon$ when comparing with the other two variants.
 
@@
 \begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and number of evaluations of Variant $A.b$ with PCA decomposition.}
-\centering
-\begin{tabular}{ccccc}
+\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with PCA decomposition.}
+%\centering
+%\begin{tabular}{ccccc}
+%\hline
+% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
+% $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
+% $x_2$ & $0.0034$ & $512$ & $0.0172$ & $824$ \\ \hline
+% $x_3$ & $0.0004$ & $512$ & $0.0023$ & $512$ \\ \hline
+% $x_4$ & $0.0001$ & $512$ & $0.0005$ & $512$ \\ \hline
+% $x_5$ & $0.0000$ & $512$ & $0.0001$ & $512$ \\ \hline
+% $x_6$ & $0.0000$ & $512$ & $0.0000$ & $512$ \\ \hline \hline
+ \centering
+\begin{tabular}{ccc}
 \hline
- input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
- $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
- $x_2$ & $0.0034$ & $512$ & $0.0172$ & $824$ \\ \hline
- $x_3$ & $0.0004$ & $512$ & $0.0023$ & $512$ \\ \hline
- $x_4$ & $0.0001$ & $512$ & $0.0005$ & $512$ \\ \hline
- $x_5$ & $0.0000$ & $512$ & $0.0001$ & $512$ \\ \hline
- $x_6$ & $0.0000$ & $512$ & $0.0000$ & $512$ \\ \hline \hline
-%\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} &\\ \hline 
+ input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
+ $x_1$ & $0.9800$ &  $0.9960$  \\ \hline
+ $x_2$ & $0.0034$ &  $0.0172$  \\ \hline
+ $x_3$ & $0.0004$ &  $0.0023$  \\ \hline
+ $x_4$ & $0.0001$ &  $0.0005$  \\ \hline
+ $x_5$ & $0.0000$ &  $0.0001$  \\ \hline
+ $x_6$ & $0.0000$ &  $0.0000$  \\ \hline \hline
+\multicolumn{3}{l}{Total number of evaluations: $398 \ 648$} \\ \hline 
 \end{tabular}
@@
 \end{table}
-
 One may conclude that these estimates explain how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.
@@
 Furthermore, we investigated the use of a recent estimator well-suited to the estimation of small first-order indices using quasi-Monte Carlo methods.
-The efficiency of this estimator, called ``Correlation 2'', was assessed and highlighted on two test functions and a real case model.
-The variant combining Saltelli's strategy and ``Correlation 2'' gave the best results with low failure rates across all indices.
+The efficiency of this estimator, called ``Correlation 2'', was assessed and highlighted on two test functions.
+Overall, the variant combining Saltelli's strategy and ``Correlation 2'' gave the best results, with low failure rates across all indices.
 

### 2016-09-30 article/article_for_submission.tex
Adding all changes according to Clementine's review (article for submission)

@@
 \begin{figure}[!ht]
-\caption{Given the true value of $I_1$, the figure shows in blue the region of all possible values of $\underline{S}_u(\vI)$.
-There, $\underline{S}_u^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)}$ and $\underline{S}_u^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)}$.}
-\centering
-\includegraphics[width=.5\textwidth]{Images/estimator_3d_small.pdf}
+\caption{The delimited region on the figure represents the values $\underline{S}_2$ in $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ for the Bratley \textit{et al.} function.
+There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$ and $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
+\centering
+\includegraphics[width=.5\textwidth]{Images/estimator_3d_small.eps}
 \label{fig:1}       % Give a unique label
@@
 The failure rates $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$ of each estimate are evaluated over the $100$ repetitions.
-These rates are the proportion of the repetitions in which the real errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$.
+These rates are the proportion of the repetitions in which the true estimation errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$.
+When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our integration parameters are not conservative enough and the integrands fell outside the cone \eqref{errbd}.
 
@@
 Even if ``Correlation 2'' originally requires more model evaluations, this drawback is completely overridden when this estimator is included into a sequential procedure such as ours.
+For the case where we are only interested in estimating first-order indices, Variant $B$ should be the best choice as illustrated with the g-function.
 
@@
 Thus, we can estimate the Sobol' indices over $f_{\rm payoff}(M\phi^{-1}(\vect{X}))$.
+In this particular application, the choice of $M$ is pivotal to reduce the effective dimensionality of the model.
+In this regard, Sobol' indices can help us assess whether we reduce the effective dimensionality.
+We will compare the case with either the Cholesky decomposition and the PCA construction.
+
 We propose to analyze the results with averaged Sobol' estimates and averaged total number of evaluations over $100$ repetitions.
@@
 \end{table}
-It turns out that Variant $A.b$ does not better than Variant $A.a$.
-Averaged Sobol' estimates are similar while the averaged number of model evaluations is slightly worse.
+It turns out that Variant $A.b$ does not perform better than Variant $A.a$.
+Averaged Sobol' estimates are similar but the average total number of model evaluations is slightly worse.
 The explanation is that total effect Sobol' indices require more evaluations than their corresponding first-order indices.
@@
 Variant $B$ shows a drastic improvement on the total number of evaluations with the drawback of a false estimation for input $x_4$.
-Indeed, the discrepancy is higher than $\epsilon$ when comparing with the other two variants.
-
-It is also interesting to see the Sobol' indices estimates when $M$ is constructed with the PCA decomposition. For this case, we only show the results for Variant $A.b$ in table \ref{res.AsianPCA.Ab}.
+Its discrepancy is higher than $\epsilon$ when comparing to the other two variants.
+
+Table \ref{res.AsianPCA.Ab}, shows the results for Variant $A.b$ when $M$ is constructed with the PCA decomposition.
+
+\begin{table}[!ht]
+\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.a$ with PCA decomposition.}
+\centering
+\begin{tabular}{ccccc}
+\hline
+ input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
+ $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
+ $x_2$ & $0.0037$ & $952$ & $0.0172$ & $824$ \\ \hline
+ $x_3$ & $0.0016$ & $517$ & $0.0023$ & $512$ \\ \hline
+ $x_4$ & $0.0014$ & $512$ & $0.0005$ & $512$ \\ \hline
+ $x_5$ & $0.0005$ & $512$ & $0.0001$ & $512$ \\ \hline
+ $x_6$ & $0.0002$ & $512$ & $0.0000$ & $512$ \\ \hline
+ \multicolumn{3}{l}{Total number of evaluations: }
+ \\ \hline
+\end{tabular}
+\label{res.AsianPCA.Aa}
+\end{table}
 
@@
 \end{table}
+
+\begin{table}[!ht]
+\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with PCA decomposition.}
+\centering
+\begin{tabular}{ccc}
+\hline
+ input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
+ $x_1$ & $0.9800$ & $131072$ \\ \hline
+ $x_2$ & $0.0037$ & $18422$ \\ \hline
+ $x_3$ & $0.0028$ & $7834$ \\ \hline
+ $x_4$ & $0.0029$ & $10486$ \\ \hline
+ $x_5$ & $0.0017$ & $4613$ \\ \hline
+ $x_6$ & $0.0029$ & $9467$ \\ \hline \hline
+\multicolumn{2}{l}{Total number of evaluations: } \\ \hline 
+\end{tabular}
+\label{res.AsianChol.B}
+\end{table}
+
 One may conclude that these estimates explain how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.

### 2016-09-30 article/Images/article_scheme_S_3D.m

@@ -1,4 +1,4 @@
-set(0,'defaultaxesfontsize',20,'defaulttextfontsize',20) %make font larger
+set(0,'defaultaxesfontsize',18,'defaulttextfontsize',18) %make font larger
 set(0,'defaultLineLineWidth',3) %thick lines
 set(0,'defaultTextInterpreter','latex') %latex axis labels
 set(0,'defaultLegendInterpreter','latex') %latex axis labels
@@ -10,9 +10,9 @@ indice = 0.1791303924*sigma2;
 S = @(I3, I4) min(indice./max(I3-I4.^2, eps), 1);
 
 mu = -21/64;
-I = [(sigma2 + (mu)^2) -mu];
+Ireal = [(sigma2 + (mu)^2) -mu];
 err = [.05 .1]; 
-Ireal = I - .35*err.*[1 -1];
+I = Ireal + .2*err.*[1 -1];
 Smax = S(I(1) - err(1), I(2) + err(2));
 Smin = S(I(1) + err(1), I(2) - err(2));
 
@@ -59,18 +59,18 @@ if S(Ireal(1),Ireal(2)) < Smax & S(Ireal(1),Ireal(2)) > Smin % Not the...
     % same value as Smax and Smin for the Zaxis
     if S(Ireal(1),Ireal(2)) < S(I(1),I(2))
 %         ax.ZTickLabel = {'$S_{\min}$', '$S(I)$','$(S_{\min}+S_{\max})/2$', '$S(\hat{I})$', '$S_{\max}$'};
-        ax.ZTickLabel = {'$\underline{S}_{n,\min}$', '$\widehat{\underline{S}}_u=(\underline{S}_{u}^{\min}+\underline{S}_{u}^{\max})/2$', '$\underline{S}_{u}^{\max}$'};
+        ax.ZTickLabel = {'$\underline{S}_{2}^{\min}$', '$(\underline{S}_{2}^{\min}+\underline{S}_{2}^{\max})/2$', '$\underline{S}_{2}^{\max}$'};
     else
 %         ax.ZTickLabel = {'$S_{\min}$', '$S(\hat{I})$', '$(S_{\min}+S_{\max})/2$', '$S(I)$', '$S_{\max}$'};
[…]

### 2016-10-02 article/article_for_submission.tex
changes L, PCA + comm fig1

@@
 $I_2$) and maximizes the denominator $I_3-I_4^2$.
-As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_u(\vI)$ given the true value of $I_1$.
+As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_2(\vI)$ given the true value of $I_1$ for the test function of Bratley \textit{et al.} \cite{Bratley}.
+This function is further described in section \ref{sec:5}.
 \begin{figure}[!ht]
@@
 In this regard, Sobol' indices can help us assess whether we reduce the effective dimensionality.
-We will compare the case with either the Cholesky decomposition and the PCA construction.
+We will compare the case with either the Cholesky decomposition or the PCA construction.
 
@@
 
-Table \ref{res.AsianPCA.Ab}, shows the results for Variant $A.b$ when $M$ is constructed with the PCA decomposition.
+Tables \ref{res.AsianPCA.Aa}, \ref{res.AsianPCA.Ab}, and \ref{res.AsianPCA.B} show the results when $M$ corresponds to the PCA decomposition of $\mathsf{\Sigma}$.
 
@@
 \hline
- input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
- $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
- $x_2$ & $0.0037$ & $952$ & $0.0172$ & $824$ \\ \hline
- $x_3$ & $0.0016$ & $517$ & $0.0023$ & $512$ \\ \hline
- $x_4$ & $0.0014$ & $512$ & $0.0005$ & $512$ \\ \hline
- $x_5$ & $0.0005$ & $512$ & $0.0001$ & $512$ \\ \hline
- $x_6$ & $0.0002$ & $512$ & $0.0000$ & $512$ \\ \hline
- \multicolumn{3}{l}{Total number of evaluations: }
+ input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
+ $x_1$ & $0.9800$ & $0.9960$  \\ \hline
+ $x_2$ & $0.0037$ & $0.0172$  \\ \hline
+ $x_3$ & $0.0016$ & $0.0023$  \\ \hline
+ $x_4$ & $0.0014$ & $0.0005$  \\ \hline
+ $x_5$ & $0.0005$ & $0.0001$  \\ \hline
+ $x_6$ & $0.0002$ & $0.0000$ \\ \hline
+ \multicolumn{3}{l}{Total number of evaluations: $396 \ 221$}
  \\ \hline
@@
 \hline
- input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
- $x_1$ & $0.9800$ & $131072$ \\ \hline
- $x_2$ & $0.0037$ & $18422$ \\ \hline
- $x_3$ & $0.0028$ & $7834$ \\ \hline
- $x_4$ & $0.0029$ & $10486$ \\ \hline
- $x_5$ & $0.0017$ & $4613$ \\ \hline
- $x_6$ & $0.0029$ & $9467$ \\ \hline \hline
-\multicolumn{2}{l}{Total number of evaluations: } \\ \hline 
+ input & $\widehat{\underline{S}}_u$  \\ \hline
+ $x_1$ & $0.9800$ \\ \hline
+ $x_2$ & $0.0037$ \\ \hline
+ $x_3$ & $0.0028$ \\ \hline
+ $x_4$ & $0.0029$ \\ \hline
+ $x_5$ & $0.0017$ \\ \hline
+ $x_6$ & $0.0029$ \\ \hline \hline
+\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
 \end{tabular}
-\label{res.AsianChol.B}
+\label{res.AsianPCA.B}
 \end{table}
-
-One may conclude that these estimates explain how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.
+Variant $A.b$ performs equally well as Variant $A.a$ in terms of average total number of evaluations while most probably giving better estimates for the small first-order indices.
+Once 	again, variant $B$ shows an improvement on the total number of evaluations with the drawback of slightly overestimating the small first-order indices.
+
+Overall, each variant captures well how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.
 

### 2016-10-02 article/article_for_submission.tex
changes L, boxplot legend dashed line instead of line
Small changes in comments for PCA example in section 5.2 (article for submission)

@@
 \caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$.
-The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
+The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
 \centering
@@
 \end{table}
-Variant $A.b$ performs equally well as Variant $A.a$ in terms of average total number of evaluations while most probably giving better estimates for the small first-order indices.
+Variant $A.a$ performs as well as Variant $A.b$ in terms of average total number of evaluations.
+However, Variant $A.a$ is most probably giving worse estimates for the small first-order indices.
+Table \ref{res.AsianPCA.Aa} shows that averaged $\widehat{\underline{S}}_4$ is greater than $\widehat{\overline{S}}_4$, $\widehat{\underline{S}}_5$ greater than $\widehat{\overline{S}}_5$, and $\widehat{\underline{S}}_6$ greater than $\widehat{\overline{S}}_6$, which is inconsistent with the property ${\underline{S}}_u\leq{\overline{S}}_u$.
 Once again, variant $B$ shows an improvement on the total number of evaluations with the drawback of slightly overestimating the small first-order indices.

### 2016-10-06 article/article_for_submission.tex
Corrections for the article_for_submission.tex

@@
 \institute{Llu\'{i}s Antoni Jim\'{e}nez Rugama \at
-              Illinois Institute of Technology, Rettaliata Engineering Center, 10 W 32st, Chicago, IL 60616 \\
+              Illinois Institute of Technology, Rettaliata Engineering Center, Room 208, 10 W 32st, Chicago, IL 60616 \\
 \email{ljimene1@hawk.iit.edu}
@@
 
-An inherent practical problem of this estimation is how to quantify the number of model evaluations to ensure that estimates satisfy a desired error tolerance.
+An inherent practical problem of this estimation is how to quantify the number of model evaluations needed to ensure that estimates satisfy a desired error tolerance.
 This paper addresses this challenge by proposing a reliable error bound for first-order and total effect Sobol' indices.
@@
 Among all Sobol' indices one can distinguish \emph{first-order} and \emph{total effect} indices.
-The first measure the effect of a single input, while the second measure this same effect and includes all its interactions with other inputs.
+The first measure the effect of a single input, while the second measure the effect of a single input plus all its interactions with other inputs.
 
@@
 
-A practical problem concerning the use of these methods is how to quantify the number of model evaluations to ensure that Sobol' estimates are accurate enough.
+A practical problem concerning the use of these methods is how to quantify the number of model evaluations required to ensure that Sobol' estimates are accurate enough.
 This article addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences.
@@
 
-Firstly, section \ref{sec:2} introduces Sobol' indices and reviews both Saltelli's strategy to estimate first-order and total effect Sobol' indices, and the replication procedure.
+Firstly, Section \ref{sec:2} introduces Sobol' indices and reviews both Saltelli's strategy to estimate first-order and total effect Sobol' indices, and the replication procedure.
 Our main contribution is detailed in  Section \ref{sec:3}.
@@
 %We adopt the same notations introduced by Owen in \cite{Owen}. 
-Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of\\$f\in \mathbb{L}^2(\cube)$, and $\mathcal{D}=\{1,\dots,d\}$ the set of dimension indexes.
+Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of $f$.
+We assume that $f$ is in some subset of $\in \mathbb{L}^2(\cube)$ for which $f(\vx)$ is defined for all $\vx\in\cube$, and $\mathcal{D}=\{1,\dots,d\}$ the set of dimension indexes.
 %The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
 Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality.
-$\vx_u$ represents a point in $[0,1]^{|u|}$ with components $x_j, j \in u$.
-Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j={x'}_j$ if $j \notin u$.% and denote by $\mu$ and $\sigma^2$ the mean $\int_{\cube}f(\vx)d{\vx}$ and variance $\int_{\cube}(f(\vx)-\mu)^2d{\vx}$ of $f$.
+Then, $\vx_u$ represents a point in $[0,1]^{|u|}$ with components $x_j, j \in u$.
+Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j=x'_j$ if $j \notin u$.% and denote by $\mu$ and $\sigma^2$ the mean $\int_{\cube}f(\vx)d{\vx}$ and variance $\int_{\cube}(f(\vx)-\mu)^2d{\vx}$ of $f$.
 
@@
 \[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1]^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
-From this decomposition, one can express the following two quantities:
+From this decomposition, one can define the following two quantities:
 \[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
@@
 
-These two quantities $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ measure the importance of variables $\vx_u$.
-$\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$, that is the effect of all interactions between variables in $\vx_u$, and $\ov{$\tau$}_u^2$ quantifies the main effect of $\vx_u$ plus the effect of all interactions between variables in $\vx_u$ and variables in $\vx_{-u}$.
-
-$\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ satisfy the following relations: $ 0 \leq  \underline{\tau}_u^2 \leq \ov{$\tau$}_u^2$ and $\underline{\tau}_u^2 = \sigma^2 - \ov{$\tau$}_{-u}^2$.
+These two quantities $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ measure the importance of variables $\vx_u$: $\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$, that is the effect of all interactions between variables in $\vx_u$, and $\ov{$\tau$}_u^2$ quantifies the main effect of $\vx_u$ plus the effect of all interactions between variables in $\vx_u$ and variables in $\vx_{-u}$.
+
+Both $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ satisfy the following relations: $ 0 \leq  \underline{\tau}_u^2 \leq \ov{$\tau$}_u^2$ and $\underline{\tau}_u^2 = \sigma^2 - \ov{$\tau$}_{-u}^2$.
 These two measures are commonly found in the literature in their normalized form: $\underline{S}_u = \underline{\tau}_u^2 / \sigma^2$ is the closed $|u|$-order Sobol' index for inputs $u$, while $\ov{$S$}_u = \ov{$\tau$}_u^2 / \sigma^2$ is the total effect Sobol' index of order $|u|$.
@@
 A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times.
-Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to a variable $x_j$.
+Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to samples of a variable $x_j$.
 Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$.
@@
 This alternative relies on the construction of two replicated designs.
-The notion of replicated designs was first introduced by McKay through its replicated Latin Hypercubes in \cite{McKay}.
-In order to apply this definition to other types of points, in \cite{GJAHMP} we generalized this notion to:
+The notion of replicated designs was first introduced by McKay through his replicated Latin Hypercubes in \cite{McKay}.
+In order to apply this definition to other types of points, in \cite{GJAHMP} we generalized this notion to the following.
 \begin{definition}
@@
 Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) by using $y'_{\pi_u(i)}$ instead of $f(\vx_{i,u}:{\vx'}_{i,-u})$ without requiring further model evaluations for each $u$.
-This estimation method has been deeply studied and generalized in Tissot et al.
+This estimation method has been studied deeply and generalized in Tissot et al.
 \cite{Tissot} to the case of closed second-order indices.
@@
 Additional sequential procedures are the replicated procedure and McKay's procedure respectively proposed in \cite{Gilquin.rec} and \cite{Tong}.
-Nevertheless, in those two cases, the stopping criterion is a quantity of interest purely empirical, built directly upon the estimates.
-Such stopping criteria often involve hyper-parameters difficult to tweak but more importantly, fail to guarantee any error bound on the estimates.
+Nevertheless, in those two cases, the stopping criterion is a purely empirical quantity of interest, built directly upon the estimates.
+Such stopping criteria often involve hyper-parameters that are difficult to tweak but more importantly, fail to guarantee any error bound on the estimates.
 
@@
 
-The description of the error bound is introduced in the following section and our sequential procedure is detailed in section \ref{sec:4}.
+The description of the error bound is introduced in the following section and our sequential procedure is detailed in Section \ref{sec:4}.
 
@@
 Based on the size of $\absolute{\hf_{\vk}}$ and the structure of dual nets \eqref{dual_net_structure}, in \cite[Sec.
-4.1]{HicJim} we proposed an ordering of the wave-numbers $\vk(\cdot):\naturals_0\rightarrow\naturals_0^d$.
+4.1]{HicJim} we proposed an ordering of the \emph{wavenumbers} $\vk(\cdot):\naturals_0\rightarrow\naturals_0^d$.
 Defining $\hf_{\kappa}=\hf_{\vk(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,
@@
 
-Details concerning the algorithm, the mapping of the wavenumber space, or the meaning and properties of $\cc$, are provided in \cite{HicJim}.
+Details concerning the algorithm, the mapping of the \emph{wavenumber} space, or the meaning and properties of $\cc$, are provided in \cite{HicJim}.
 
@@
 \label{sec:3.2}
-The idea here is to extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To do so, we consider the two integral formulas of the first-order and total effect Sobol' indices:
+The idea here is to extend the definition of the error bound (\ref{errbd}) to Sobol' indices.
+To achieve this goal, we consider the two integral formulas of the first-order and total effect Sobol' indices with $|u|=1$:
 %\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
@@
 where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values.
-$\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$.
+Indices $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$.
 If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$,\\ $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.
@@
 As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_2(\vI)$ given the true value of $I_1$ for the test function of Bratley \textit{et al.} \cite{Bratley}.
-This function is further described in section \ref{sec:5}.
+This function is further described in Section \ref{sec:5}.
 \begin{figure}[!ht]
@@
 \label{sec:4}
-The sequential estimation procedure we propose combines error bounds $\varepsilon_{\widehat{\underline{S}}_u}$ and $\varepsilon_{\widehat{\overline{S}}_u}$ presented in the previous section with either one of the two estimation strategies of section \ref{sec:2.2}: Saltelli's strategy and the replication procedure.
+The sequential estimation procedure we propose combines error bounds $\varepsilon_{\widehat{\underline{S}}_u}$ and $\varepsilon_{\widehat{\overline{S}}_u}$ presented in the previous section with either one of the two estimation strategies of Section \ref{sec:2.2}: Saltelli's strategy and the replication procedure.
 
@@
 Algorithm \ref{recursive.algorithm} summarizes the main steps of our sequential procedure.
-First, one must fix the tolerance $\epsilon >0$ at which Sobol' indices must be estimated.
-Then, we set $m=\ell_*+r$ and construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}.
+First, one must fix the tolerance $\epsilon >0$ at which Sobol' indices must be estimated, and set $m=\ell_*+r$, where $\ell_*$ and $r$ are the two hyper-parameters defined in \eqref{conecond}.
+Then, one must construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}.
 The choice of $\ell_*$ must be large enough to ensure that each integrand of $\underline{S}_u$ and $\overline{S}_u$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).
@@
 Furthermore, they possess the structure of two replicated designs of order $1$, as shown in \cite{GJAHMP}.
-$\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can also be scrambled as long as both point sets share the same scrambling dimensionwise.
+In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can also be scrambled as long as both point sets share the same scrambling dimensionwise.
 \bigskip
 
-$\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices.
+The sets $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ can be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices.
 This option is referred as Variant $A$ in Algorithm \ref{recursive.algorithm}.
@@
 For each repetition, we fix the tolerance $\varepsilon=5.10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points).
-The algorithm error bound factor is set to $\mathfrak{C}(m)=10\times 2^{-m}$.
+The algorithm error bound factor described in \eqref{errbd} is set to $\mathfrak{C}(m)=10\times 2^{-m}$.
 
@@
 These rates are the proportion of the repetitions in which the true estimation errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$.
-When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our integration parameters are not conservative enough and the integrands fell outside the cone \eqref{errbd}.
+When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and the integrands fall outside the cone \eqref{conecond}.
 
@@
 Each value $a_j$ determines the relative importance of the $x_j$.
-When the value of $a_j$ gets closer to zero the variable $x_i$ becomes more influent.
+When the value of $a_j$ gets closer to zero the variable $x_j$ becomes more influent.
 For this example, we chose $d=6$ and $a_1=0,a_2=0.5, a_3=3, a_4=9, a_5=99$, and $a_6=99$.
@@
 \[
-f_{\rm payoff}(\vect{B}) = \e^{-rT}\max\left(\frac{1}{d}\sum_{i=1}^d S_0\e^{(r-\sigma^2/2)t_i+\sigma B_{t_i}}-K, 0\right)
+f_{\rm payoff}(\vect{B}) = \e^{-\rho T}\max\left(\frac{1}{d}\sum_{i=1}^d S_0\e^{(\rho-\sigma^2/2)t_i+\sigma B_{t_i}}-K, 0\right)
 \]
-where $T$ is the maturity of the option, $S_0$ is the initial stock price, $\sigma$ the volatility of the stock, $r$ the interest rate, and $K$ the strike price.
+where $T$ is the maturity of the option, $S_0$ is the initial stock price, $\sigma$ the volatility of the stock, $\rho$ the interest rate, and $K$ the strike price.
 
 The discretized Brownian motion $\vect{B}$ follows a multivariate normal distribution with mean $\vzero$ and covariance matrix $\mathsf{\Sigma}$, with $\mathsf{\Sigma}_{ij}=\min(t_i,t_j)$.
-If $\vect{Y}\sim N(\vzero,I_d)$, given a matrix $M$ such that $\mathsf{\Sigma}=MM^t$, then $M\vect{Y}\sim N(\vzero,\mathsf{\Sigma})$.
+If $\vect{Y}\sim N(\vzero,I_d)$, then for any matrix $M$, $M\vect{Y}\sim N(\vzero,\mathsf{\Sigma})$ where $\mathsf{\Sigma}=MM^t$.
 Hence, we can generate the discretized Brownian motion using the inverse normal cumulative distribution function $\phi^{-1}$: $\vect{B}\sim M\phi^{-1}(\vect{X})$ with $\phi^{-1}(\vect{X})=(\phi^{-1}(X_1),\dots,\phi^{-1}(X_d))^t$ and $\vect{X}\sim \mathcal{U}([0,1]^d)$.
@@
 \section{Conclusion}
-When estimating Sobol' indices, the question of how much evaluations must be performed to reach a desired precision is often raised by practitioners.
+When estimating Sobol' indices, the question of how many evaluations must be performed to reach a desired precision is often raised by practitioners.
 This question is difficult to address mostly because the number of evaluations needed depends on the complexity of the model studied.

### 2016-10-06 article/article_for_submission.tex
changes last? L

@@
 Alternatively, they can be interpreted as the percentage of the variance explained by the inputs.
-Among all Sobol' indices one can distinguish \emph{first-order} and \emph{total effect} indices.
+Among all Sobol' indices one can distinguish first-order and total effect indices.
 The first measure the effect of a single input, while the second measure the effect of a single input plus all its interactions with other inputs.
@@
 \label{saltelli.theorem}
-The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allow to estimate all first-order and total effect Sobol' indices of order 1 at a cost of $n(d+2)$ evaluations of the model.
+The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allow to estimate all first-order and total effect Sobol' indices at a cost of $n(d+2)$ evaluations of the model.
 \end{theorem}
@@
 \If {Variant $A$}
+\If {$! bool_u$}
 \State compute $\widehat{\underline{S}}_u$ and $\widehat{\ov{$S$}}_u$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}), and Saltelli's strategy
 \State $bool_u \leftarrow \varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon \ \& \ \varepsilon_{\widehat{\widehat{\overline{S}}}_u} \leq \epsilon$
+\State $m_u \leftarrow m$
+\EndIf
 \EndIf
 \If {Variant $B$}
+\If {$! bool_u$}
 \State estimate $\widehat{\underline{S}}_u$ with formula (\ref{formula_undersu}) and the replication procedure
 \State $bool_u \leftarrow \varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon$
+\State $m_u \leftarrow m$
+\EndIf
 \EndIf
@@
 \end{table}
+
 The main observation is that both approaches give similar results both in terms of estimation errors, failure rates and total number of evaluations.
@@
 Figure \ref{boxplots.gfunc} shows boxplots of the $100$ estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$.
-The horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.
+The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.
 \begin{figure}[!ht]
@@
 \end{figure}
+
 As expected, we observe that the use of ``Correlation 2'' in Variant $A.b$ results in lower estimation errors for these four inputs.
@@
 \end{table}
-Variant $A.b$ gives lower estimation errors and fewer failure rates than Variant $A.a$ on the four small first-indices $\underline{S}_3,\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''.
+
+Variant $A.b$ gives lower estimation errors and fewer failure rates than Variant $A.a$ on the four small first-indices $\underline{S}_3$, $\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''.
 The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $71\%$ against only $4\%$ for Variant $A.b$.
@@
 \end{table}
+
 The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$.
@@
 \end{table}
+
 It turns out that Variant $A.b$ does not perform better than Variant $A.a$.

### 2016-11-23 crass/crassnew.tex
final changes (for real this time)
tex crass
Adding letter to review for CRASS and adding CRASS new lines in blue for reviewer

@@
 \usepackage{graphicx}
+
+\usepackage{color} % TO REMOVE AFTER REVIEW APPROVES COMMENTS IN BLUE
 
@@
 The definition of these constructions is recursive, therefore one can iteratively refine each replicated design by adding the corresponding new set of points.
-
 We first provide a brief introduction on digital sequences and then present two iterative approaches to construct the two replicated point sets.
@@
 \begin{equation*}
+\renewcommand{\arraystretch}{1.3}
 \begin{pmatrix}
@@
 \end{lemma}
-\textit{Proof}: For each $\ell\geq 1$, digital shift and scrambling operations carried out in equations (\ref{linear.scrambl}) and (\ref{dig.shift}) are bijections from $\mathbb{F}_2^r$ and $\left(\mathbb{F}_2^{r}\right)^{s}$.
+\textit{Proof}: For each $\ell\geq 1$, digital shift and scrambling operations carried out in (\ref{linear.scrambl}) and (\ref{dig.shift}) are bijections from $\mathbb{F}_2^r$ and $\left(\mathbb{F}_2^{r}\right)^{s}$.
 Hence, the same coordinates of $B_\ell$ and ${B'}_\ell$ will contain the same set of $2^r$ values.
@@
 While each of the $100$ designs $M$ is independently randomized applying Owen's scrambling \cite{OwenScrambling}, designs $A$ are constructed by randomly selecting matrix $L$ (uniformly among all $2^{r(r-1)/2}$ choices) and vectors $\ve_\ell$ used in equation (\ref{dig.shift}).
-In addition, we also show in Figure \ref{results.crit} the results obtained with a Latin Hypercube design (LH design) with an equal number of points as in design $A$.
-LH designs are the standard designs used in the replication procedure to estimate first-order indices.
-The x-axis corresponds to the number of design points $N$ and the y-axis to the value of the criterion.
+\textcolor{blue}{In addition, we also show in Figure \ref{results.crit} the results obtained with an optimized Latin Hypercube design (LH design) according to each criterion for an equal number of points as in design $A$.} The x-axis corresponds to the number of design points $N$ and the y-axis to the value of the criterion.
+\textcolor{blue}{Although LH designs are the standard designs used in the replication procedure to estimate first-order indices, the replicated LH design of an optimized LH design is not guaranteed to be optimal.}
 
 As expected, design $M$ performs the best and the estimated slope of the discrepancy curve ($-0.72$) falls within the expected range for Sobol' sequences \cite{Morokoff}.
-Although design $A$ does not perform as well as design $M$, it outperforms a classic LH design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $M$.
+\textcolor{blue}{Although design $A$ does not perform as well as design $M$, it outperforms an optimized LH design for the discrepancy criterion.
+However for the maximin criterion, design $A$ shows slightly worse results.
+Concerning the number of steps, design $A$ allows $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $M$.}
 \begin{figure}
@@
 % The Acknowledgements are an un-numbered section
-%\section*{Acknowledgements}
-% Acknowledgements text here
+\section*{Acknowledgements}
+This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020).
 
@@
 
-\bibitem{Matousek} J. Matou$\check{s}$ek, On the $L2$-discrepancy for anchored boxes, \emph{Journal of Complexity} 14, 1998, pp. 527?-556.
+\bibitem{Matousek} J. Matou$\check{s}$ek, On the $L2$-discrepancy for anchored boxes, \emph{Journal of Complexity} 14, 1998, pp. 527-556.
 

### 2017-02-09 article_review/Manuscript.tex
added revised manuscript files

--- 2016-10-06 article/article_for_submission.tex
@@
 \usepackage{url}
+
+\usepackage{xcolor} % for colors
 
@@
 In the field of sensitivity analysis, Sobol' indices are sensitivity measures widely used to assess the importance of inputs of a model to its output.
-The estimation of these indices is often performed trough Monte Carlo or quasi-Monte Carlo methods.
+The estimation of these indices is often performed {\color{purple}through} Monte Carlo or quasi-Monte Carlo methods.
 A notable method is the replication procedure that estimates first-order indices at a reduced cost in terms of number of model evaluations.
@@
 
-\keywords{Sobol' indices \and error bound \and sequential method \and quasi-Monte Carlo}
+\keywords{Sobol' index \and error bound \and sequential method \and quasi-Monte Carlo}
 % \PACS{PACS code1 \and PACS code2 \and more}
@@
 f_{\varnothing} &= \mathbb{E}[f(\vx)]= \mu, \\
-f_u(\vx) &= \int_{[0,1]^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).
+f_u(\vx) &= \int_{[0,1]^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subsetneq u} f_v(\vx).
 \end{align*}
@@
 \[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
-\ov{$\tau$}_u^2 = \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2, \qquad u \subsetneq \mathcal{D}.\]
+\ov{$\tau$}_u^2 = \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2, \qquad u \subseteq \mathcal{D}.\]
 
@@
 \begin{equation}
- \widehat{\sigma}^2 = \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i)^2 - \widehat{\mu}^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
+ \widehat{\sigma}^2 = \frac{1}{n-1} \sum \limits_{i=0}^{n-1} \left( f(\vx_i) - \widehat{\mu}\right)^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
 \label{mu.est}
@@
 
-The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ accordingly to $u$.
+The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ {\color{purple}according} to $u$.
 While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input space dimension.
@@
 \end{equation}
-where one may increase $m$ until the error bound $\epsilon_{I}$ is small enough.
+where one may increase $m$ until the error bound $\epsilon_{\widehat{I}}$ is small enough.
 
@@
 \centering
-\includegraphics[width=.5\textwidth]{Images/estimator_3d_small.eps}
+\includegraphics[width=.5\textwidth]{Fig1.pdf}
 \label{fig:1}       % Give a unique label
@@
 \centering
-\includegraphics[width=0.45\textwidth]{Images/boxplots.pdf}
+\includegraphics[width=0.45\textwidth]{Fig2.pdf}
 \label{boxplots.gfunc}
@@
 The results show that the use of Variant $B$ leads to slightly higher estimation errors and higher failure rates than those obtained with Variant $A.a$ or Variant $A.b$.
-However, the total number of evaluations is twice as small.
+However, the total number of evaluations is {\color{purple}half as large}.
 As such, this approach remains interesting when one wants to estimate only first-order indices.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{Images/boxplots_bis.pdf}
+\includegraphics[width=0.45\textwidth]{Fig3.pdf}
 \label{boxplots.bratley}

### 2017-02-10 levelEmodel/levelE.R
levelE model

@@ -1,0 +1,61 @@
+modelE <- function(X){
+  
+  # distribution transformations
+  X[,1] <- (1000-100)*X[,1]+100
+  X[,2] <- exp((log(10^(-2))-log(10^(-3)))*X[,2]+log(10^-(3)))
+  X[,3] <- exp((log(10^(-5))-log(10^(-6)))*X[,3]+log(10^-(6)))
+  X[,4] <- exp((log(10^(-1))-log(10^(-3)))*X[,4]+log(10^-(3)))
+  X[,5] <- (500-100)*X[,5]+100
+  X[,6] <- (5-1)*X[,6]+1
+  X[,7] <- (30-3)*X[,7]+3
+  X[,8] <- exp((log(10^(-1))-log(10^(-2)))*X[,8]+log(10^-(2)))
+  X[,9] <- (200-50)*X[,9]+50
+  X[,10] <- (5-1)*X[,10]+1
+  X[,11] <- (30-3)*X[,11]+3
+  X[,12] <- exp((log(10^(7))-log(10^(5)))*X[,12]+log(10^-(5)))
+  
+  # call to level E model
+  path = "/Users/Laurent/Desktop/levelEmodel/src"
+  write.table(x=nrow(X),file = paste(path,"/try.txt",sep=""),col.names = FALSE,row.names = FALSE)
+  write.table(x=X,file = paste(path,"/try.txt",sep=""),append=TRUE,col.names = FALSE,row.names = FALSE)
+  system(paste(paste("cd", path,sep=" "),"; ./levele.out",sep=""),intern=TRUE)
+  
+  # retrieve the outputs
+  y <- read.table(file = paste(path,"/LevelE.txt",sep=""))
+  y <- as.matrix(y)
+  
+  return(y)
+}
+
+library(boot)
+# designs of experiments
+n <- 14350
+d <- 12
+X1 <- data.frame(matrix(runif(d * n), nrow = n))
+X2 <- data.frame(matrix(runif(d * n), nrow = n))
+
+# sensitivity analysis : sobolSalt
+x <- sobolSalt(model = NULL, X1, X2, scheme="A", nboot = 100)
+y_modelE <- modelE(X = x$X)
+
+AS1 <- x
+tell(x = AS1,y=y_modelE[,1])
+
+AS26 <- x
+tell(x = AS26,y=y_modelE[,26])
+
+
+# sensitivity analysis : sobolowen
+
+library(boot)
+n <- 14350
[…]

### 2017-02-10 levelEmodel/src/batman.f

@@ -1,0 +1,105 @@
+      SUBROUTINE BATMAN(T,NELCHN,ALAMB,C0,RLEACH,TSLEAC,CIN)
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C                                                                      C
+C SUBROUTINE BATMAN                                                    C
+C A. SALTELLI, JOINT RESEARCH CENTRE OF ISPRA                          C
+C DIVISION OF RADIOCHEMISTRY                                           C
+C OCTOBER 30, 1988                                                     C
+C                                                                      C
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C                                                                      C
+C DESCRIPTION:                                                         C
+C                                                                      C
+C SUBROUTINE TO COMPUTE ACTIVITIES (MOL/KG OF CONCRETE) AFTER          C
+C CHAIN DECAY USING BATEMAN EQUATIONS . SUBROUTINE FOR BATMAN          C
+C EQUATIONS INCLUDING A EXPONENTIAL LEACHING RATE(RLEACH) STARTING     C
+C AT 'CONTIM' TIME.                                                    C
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C                                                                      C
+C DICTIONARY:                                                          C
+C                                                                      C
+C T               = TIME PINT CONSIDERD                                C
+C NELCHN          = NUMBER OF ELEMENT                                  C
+C ALAMB(I)        = DECAY CONSTANT (1/A)                               C
+C RLEACH(I)       = LEACHING RATE                                      C
+C TSLEACH         = TIME WHEN LEACHING START                           C
+C C0(I)           = NUCLIDE CONCENTRATION IN THE MATRIX AT TIME        C
+C                   OF VAULT CLOSURE (MOL/KG)                          C
[…]

### 2017-02-10 levelEmodel/src/bios.f

@@ -1,0 +1,65 @@
+      SUBROUTINE BIOS
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C                                                                      C
+C     BIOS                                                             C
+C                                                                      C
+C     DESCRIPTION                                                      C
+C         THIS BIOSPHERE MODEL IS VERY SIMPLE. THE FULL GEOSPHERE FLUX C
+C         IS ASSUMED TO ENTER A STREAM WHICH IS USED FOR DRINKING      C
+C         WATER.                                                       C
+C                                                                      C
+C     CALLED BY MAIN                                                   C
+C                                                                      C
+C     USES WRDOSE                                                      C
+C                                                                      C
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C                                                                      C
+C     DICTIONARY                                                       C
+C         DOSRT(1,N,I,K) --- INGESTION DOSE FROM N-TH CHAIN, I-TH      C
+C                            ELEMENT AT K-TH TIME                      C
+C         ADOS1(I,K,L)   --- GEOSPHERE FLUX                            C
+C         TTC(N,I)       --- DOSE CONVERSION FACTOR OF N-TH CHAIN,     C
+C                            I-TH ELEMENT                              C
+C                                                                      C
+C                                                                      C
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C
+      INCLUDE  'par.h'
+      INCLUDE  'cparam.h'
+      INCLUDE  'cnucld.h'
+      INCLUDE  'cbios.h'
+      INCLUDE  'ctime.h'
+      INCLUDE  'coutp.h'
+      INCLUDE  'cspop.h'
+C
+C
+      NELCHN = NEL(NCHAIN)
+      DO  20  K = 1, NTIME
+          DO  10  I = 1, NELCHN
+C
[…]

### 2017-02-10 levelEmodel/src/block.h

@@ -1,0 +1,11 @@
+      COMMON /CONST/
+     & C0(I129)       ,C0(NP237)      ,C0(U233)       ,C0(TH229)      
+     &,DISPC(1)       ,RETC(NP,1)     ,RETC(U,1)      ,RETC(TH,1)     
+     &,DISPC(2)       ,RETC(NP,2)     ,RETC(U,2)      ,RETC(TH,2)     
+     &,DIFFM          ,DSF(I129)      ,DSF(NP237)     ,DSF(U233)      
+     &,DSF(TH229)     
+     &,RMW            
+      COMMON /VARIA/
+     & CONTIM         ,RLI            ,RLC            ,VREAL(1)       
+     &,XPATH(1)       ,RET(I,1)       ,FC(1)          ,VREAL(2)       
+     &,XPATH(2)       ,RET(I,2)       ,FC(2)          ,STFLOW         

### 2017-02-10 levelEmodel/src/calass.h

@@ -1,0 +1,5 @@
+      CALL ASSIGN ( 
+     & CONTIM         ,RLI            ,RLC            ,VREAL(1)       
+     &,XPATH(1)       ,RET(I,1)       ,FC(1)          ,VREAL(2)       
+     &,XPATH(2)       ,RET(I,2)       ,FC(2)          ,STFLOW         
+     &   ) 

### 2017-02-10 levelEmodel/src/calcon.h

@@ -1,0 +1,8 @@
+      CALL ASSCON ( 
+     & C0(I129)       ,C0(NP237)      ,C0(U233)       ,C0(TH229)      
+     &,DISPC(1)       ,RETC(NP,1)     ,RETC(U,1)      ,RETC(TH,1)     
+     &,DISPC(2)       ,RETC(NP,2)     ,RETC(U,2)      ,RETC(TH,2)     
+     &,DIFFM          ,DSF(I129)      ,DSF(NP237)     ,DSF(U233)      
+     &,DSF(TH229)     
+     &,RMW            
+     &   ) 

### 2017-02-10 levelEmodel/src/cbios.h

@@ -1,0 +1,3 @@
+C
+      COMMON /CBIOS /
+     &  TTC(MXNCHN,MXNELM)    , DSF(MXNCHN,MXNELM)    , STFLOW, RMW

### 2017-02-10 levelEmodel/src/cchara.h

@@ -1,0 +1,11 @@
+C                                                                               
+      COMMON  /CCHARA/                                                          
+     &  VNAME(MXNVAR,2)       , ENAME(MXNVAR,2)       ,                         
+     &  FVFLD(MXNVAR,2)       , RELANM(2*MXNVAR), XRELA(2*MXNVAR)               
+                                                                                
+C                                      **               **                      
+C    &  FVFLD(MXNVAR,2)       , RELANM(MXNVAR), XRELA(MXNVAR)                   
+C    CHANGED FOR MODIFIED KIM - ANDREA AUGUST 1993                              
+                                                                                
+      CHARACTER  VNAME*6, ENAME*6, FVFLD*15, RELANM*15, XRELA*40                
+C                                                                               

### 2017-02-10 levelEmodel/src/cfarf.h

@@ -1,0 +1,7 @@
+C
+      COMMON /CFARF /
+     &  DEN(MXNLYS)   , POR(MXNLYS)   ,
+     &  DIFFM         , DISPC(MXNLYS) , DISPH(MXNLYS) , VREAL(MXNLYS) ,
+     &  XPATH(MXNLYS) , RET(MXNCHN,MXNELM,MXNLYS)     ,
+     &  RETC(MXNCHN,MXNELM,MXNLYS)    , FC(MXNLYS)    ,
+     &  DXL(MXNLYS)   , NPX(MXNLYS)   , NXTOT

### 2017-02-10 levelEmodel/src/cfast.h

@@ -1,0 +1,5 @@
+C                                                                      
+      REAL  VTEMP                                                       
+      COMMON  /CFAST/                                                   
+     &  VTEMP(MXNVAR,MXNRUN)                                           
+C                                                                 

### 2017-02-10 levelEmodel/src/cname.h

@@ -1,0 +1,6 @@
+C
+      COMMON /CNAME /
+     &  CNAME(MXNCON) , VNAME(MXNVAR)
+      CHARACTER*15  CNAME, VNAME
+      COMMON /CHIM  /
+     &  IFHIM(MXNVAR)

### 2017-02-10 levelEmodel/src/coutp.h

@@ -1,0 +1,6 @@
+C
+      PARAMETER ( NPTH   =     1 )
+      COMMON /COUTP /
+     &  DOSRT(NPTH,MXNCHN,MXNELM,MXNTPT)      ,
+     &  ADOS(MXNELM,MXNTPT)   , ADOS1(MXNELM,MXNTPT,MXNLYS)   ,
+     &  ISAVE(MXNCHN)         , KSAVE(MXNCHN)

### 2017-02-10 levelEmodel/src/csobol.h

@@ -1,0 +1,5 @@
+C                                                                       00000100
+      REAL*8  VTEMP                                                     00000110
+      COMMON  /CSOBOL/                                                  00000200
+     &  VTEMP(2*MXNVAR,MXNRUN)                                          00000410
+C                                                                       00000500

### 2017-02-10 levelEmodel/src/cvaria.h

@@ -1,0 +1,8 @@
+C                                                                               
+       COMMON  /CVARIA/                                                          
+     &  DITR  , ITYPE(MXNVAR) , NINT(MXNVAR)  ,                                 
+     &  RANGE(MXNVAR,MXNINT+1), WEIGHT(MXNVAR,MXNINT+1),
+     &  XX(MXNVAR,MXNRUN+1)   , XVAR(MXNVAR)    ,                              
+     &  XBASE(MXNVAR,MXNRUN)  , XDASH(MXNVAR,MXNRUN)                            
+C    &  IFHIM(MXNVAR)                                                           
+C                                                                               

### 2017-02-10 levelEmodel/src/gtm1.f

@@ -1,0 +1,183 @@
+      SUBROUTINE  GTM1
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C                                                                      C
+C  SUBROUTINE GTM1 (FAR-FIELD MODULE)                                  C
+C                                                                      C
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C
+      INCLUDE 'par.h'
+      INCLUDE 'cparam.h'
+      INCLUDE 'cnucld.h'
+      INCLUDE 'cfarf.h'
+      INCLUDE 'cbios.h'
+      INCLUDE 'ctime.h'
+      INCLUDE 'coutp.h'
+C
+      DIMENSION AF1(MXNELM,MXNLYS),AF2(MXNELM,MXNLYS)
+      DIMENSION AF3(MXNELM,MXNLYS),AF4(MXNELM,MXNLYS)
+      DIMENSION AF5(MXNELM,MXNLYS),AF6(MXNELM,MXNLYS)
+      DIMENSION AF7(MXNELM,MXNLYS),AF8(MXNELM,MXNLYS)
+      DIMENSION CBEF(MXNELM,MXNSPT),CATEMP(MXNSPT)
+      DIMENSION CBB(MXNSPT),DECAF(MXNSPT),CPAR(MXNSPT)
+      DIMENSION ISIGN(MXNELM)
+C
+C
+C                   TSV = TRUNCATION DOSE (SV)
+C                   ==========================
+C
+      TSV = 1.E-15
+      NELCHN = NEL(NCHAIN)
+      NPXL1 = NXTOT - 1
+      NPXL2 = NXTOT - 2
+
+C
+C
+C                   INITIALIZE
+C                   ==========
+C
+      DO  20  J = 1, NPXL2
+          DO  10  I = 1, NELCHN
+              CBEF(I,J) = 0.
+   10     CONTINUE
+   20 CONTINUE
+      NXF=0
+      DXF=0.
+      DO  22  N = 1, NLAYER-1
+          NXF=NXF + NPX(N)
+          DXF=DXF + NPX(N)*DXL(N)
+   22 CONTINUE
+      NNN=XPATH(NLAYER)/DXL(NLAYER)
+      NXF=NXF + NNN
[…]

### 2017-02-10 levelEmodel/src/levele.f

@@ -1,0 +1,103 @@
+       program levele
+          
+C
+C       THE LEVELE MODEL.
+C       
+C       for the SIMLAB software
+C-----------------------------------------------------------------------
+C     INPUT:   
+C		 ..\LevelE.sam 
+C
+C	OUTPUT:
+C		 ..\LevelE.out 
+C                (total dose at a number of time points)
+C
+C-----------------------------------------------------------------------
+C
+      IMPLICIT REAL (A-H,P-Z)
+
+      INCLUDE 'par.h'
+      INCLUDE 'cparam.h'                                                        
+      INCLUDE 'cvaria.h' 
+      INCLUDE 'cfast.h'
+      include 'ctime.h'                                                      
+      INCLUDE 'cspop.h'                                                            
+
+      DIMENSION VAR(MXNVAR),U(MXNRUN)
+
+      IOUT=MXNTIM
+
+       DATA (TOUT(j), j=1,MXNTIM)  /
+     *  2.000E04,  3.000E04,  4.000E04,  5.000E04,  6.000E04,  7.000E04,  
+     *  8.000E04,  9.000E04,  1.000E05,  2.000E05,  3.000E05,  4.000E05,   
+     *  5.000E05,  6.000E05,  7.000E05,  8.000E05,  9.000E05,  1.000E06,
+     *  2.000E06,  3.000E06,  4.000E06,  5.000E06,  6.000E06,  7.000E06,   
+     *  8.000E06,  9.000E06 /
+
+c      Open Input sample file
+
+	 open(55,file='.\LevelE.sam')
+
+c      Open Model output file
+
+c       open(66,file='.\LevelEsimlab.out')
+       open(77,file='.\LevelE.out')
+
+c     read dummy variable
+c	read(55,*) ndum0
+
+C     read number of runs of the model
+c	read(55,*) nrunmax
+
+C     read number of parameters in the model
+c	read(55,*) nvars
+
+c     read dummy variable
+c	read(55,*) dum0
+
+      nrunmax=57344
+	nvars=12
+
+C     write header on the output file
+
+c      write(66,*)	'3'
+c      write(66,'(A11)')	'IODINE_DOSE'
+c      write(66,'(A14)')	'NEPTUNIUM_DOSE'
+c      write(66,'(A10)')	'TOTAL_DOSE'
+c      write(66,'(A10)')	'time = yes'      
+c	 write(66,*) nrunmax
+
[…]

### 2017-02-10 levelEmodel/src/levele_model.f

@@ -1,0 +1,124 @@
+      SUBROUTINE levele_model
+            
+      REAL*4  ELAPS,USRTIM,SYSTIM
+      
+      INTEGER L,I
+      INCLUDE 'par.h'
+      INCLUDE 'cparam.h'
+      INCLUDE 'cvaria.h'
+      INCLUDE 'cname.h'
+      INCLUDE 'cnucld.h'
+      INCLUDE 'cnearf.h'
+      INCLUDE 'cfarf.h'
+      INCLUDE 'ctime.h'
+      INCLUDE 'cbios.h'
+      INCLUDE 'coutp.h'
+      INCLUDE 'cspop.h'
+      INCLUDE 'const.h'
+      INCLUDE 'var.h'
+      INCLUDE 'rel.h'
+
+	DO   I = 1, NDC
+	  NELCHN = NEL(I)
+	  DO   J = 1, NELCHN
+	    AM(I,J)=ALAMB(I,J)*6.02252E+23/3.1536E+07
+	  enddo	  
+	enddo
+		
+C                   CHECK IF ANY CHAIN IS EMPTY
+C                    => KSAVE(NCHAIN)=0
+C                   ===========================
+C
+      DO  20  N = 1, NDC
+          NELCHN = NEL(N)
+          KSAVE(N) = 0
+          DO  10  I = 1, NELCHN
+              IF( C0(N,I).NE.0. )  THEN
+                  KSAVE(N) = 1
+              ENDIF
+   10     CONTINUE
+   20 CONTINUE
+	
+C
+C                   SET TOTAL DOSE TO ZERO
+C                   ================
+C
+          DO  30  I = 1, IOUT
+              TDOSE(I) = 0.
+   30     CONTINUE
+	
+C                   START CHAINS LOOP
+C                   =================
+C
+          DO  80  NCHAIN = 1, NDC
+	
+	    NELCHN = NEL(NCHAIN)
+            ISAVE(NCHAIN) = 1
+C
+C                   SET DOSRT, ADOS AND ADOS1 TO ZERO
+C                   =================================
+C
+              C A L L   S E T Z E R
+C
+C
+C                   JUMP CHAINS WITH NO SOURCE TERM
+C                   ===============================
+C
+              IF( KSAVE(NCHAIN).EQ.0 )  GO TO 80
+C
+
+              C A L L   M G S P A C
+C
+              C A L L   M G T I M E
+C
+              C A L L   N E A R F
+C
+C                   NO OUTPUT FROM NEAR FIELD
[…]

### 2017-02-10 levelEmodel/src/mgspac.f

@@ -1,0 +1,68 @@
+      SUBROUTINE  MGSPAC
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C                                                                      C
+C     MGSPAC                                                           C
+C                                                                      C
+C     DESCRIPTION                                                      C
+C         MANAGE SPACE STEPS FOR DIFFERENTIAL EQUATION OF CONTAMINATE  C
+C         TRANSPORT IN THE GEOSPHERE                                   C
+C                                                                      C
+C     DESCRIPTION OF ARGUMENTS                                         C
+C         INPUT                                                        C
+C           MXNSPT - MAXIMUM NUMBER OF SPACE POINTS                    C
+C           NLAYER - NUMBER OF GEOSPHERE LAYERS                        C
+C           XPATH(N) - GEOSPHERE PATH LENGTH OF EACH LAYER (M)         C
+C           DISPC(N) - DISPERSION LENGTH OF EACH LAYER (M)             C
+C                                                                      C
+C         OUTPUT                                                       C
+C           DXL(N) - SPACE LENGTH OF EACH LAYER (M)                    C
+C           NPX(N) - NUMBER OF SPACE POINTS OF EACH LAYER              C
+C           NXTOT  - TOTAL NUMBER OF SPACE POINTS                      C
+C                                                                      C
+C     CALLED BY MAIN                                                   C
+C                                                                      C
+C                                                                      C
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C
+      INCLUDE  'par.h'
+      INCLUDE  'cparam.h'
+      INCLUDE  'cfarf.h'
+      INCLUDE 'cvaria.h'
+      INCLUDE 'var.h'
+C
+C
+      NXTIN = 0
+      DO  10  N = 1,NLAYER
+          DXL(N) = 1.5*DISPC(N)
[…]

### 2017-02-10 levelEmodel/src/mgtime.f

@@ -1,0 +1,160 @@
+      SUBROUTINE  MGTIME
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C                                                                      C
+C     MGSPAC                                                           C
+C                                                                      C
+C     DESCRIPTION                                                      C
+C         MANAGE TIME STEPS FOR DIFFERENTIAL EQUATION OF CONTAMINATE   C
+C         TRANSPORT IN THE GEOSPHERE                                   C
+C                                                                      C
+C     DESCRIPTION OF VARIABLES                                         C
+C           NXTOT  - TOTAL NUMBER OF SPACE POINTS                      C
+C                                                                      C
+C     CALLED BY MAIN                                                   C
+C                                                                      C
+C                                                                      C
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C
+      INCLUDE  'par.h'
+      INCLUDE  'cparam.h'
+      INCLUDE  'cnucld.h'
+      INCLUDE  'cnearf.h'
+      INCLUDE  'cfarf.h'
+      INCLUDE  'ctime.h'
+C
+C
+      XUPPER=ALOG(2.)*2.**13.
+      NELCHN = NEL(NCHAIN)
+C
+C
+C                   MAXIMUN TRAVEL TIME
+C                   ===================
+C
+      TRTMP = 0.
+      DO  20  I =1, NELCHN
+          TRVL = 0.
+          DO  10  N = 1,NLAYER
+              RV = VREAL(N)/RET(NCHAIN,I,N)
+              TRVL = TRVL + (XPATH(N)/RV)
+   10     CONTINUE
+          IF( TRVL.GT.TRTMP )  TRTMP = TRVL
+   20 CONTINUE
+      TTMAX = (TRTMP + CONTIM)*1.5
+C
+C
+C                   DTS < TRAVEL TIME OF ONE SPACE STEP
+C                   ===================================
+C
[…]

### 2017-02-10 levelEmodel/src/nearf.f

@@ -1,0 +1,59 @@
+      SUBROUTINE NEARF
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C                                                                      C
+C      NEARF                                                           C
+C                                                                      C
+CCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCCC
+C
+      INCLUDE 'par.h'
+      INCLUDE 'cparam.h'
+      INCLUDE 'cnucld.h'
+      INCLUDE 'cnearf.h'
+      INCLUDE 'ctime.h'
+      INCLUDE 'coutp.h'
+C
+      DIMENSION  AL(MXNELM), CC(MXNELM), RL(MXNELM)
+      DIMENSION  CIN(MXNELM)
+C
+C
+      NELCHN = NEL(NCHAIN)
+      DO  10  I = 1, NELCHN
+          AL(I)=ALAMB(NCHAIN,I)
+          CC(I)=C0(NCHAIN,I)
+          RL(I)=RLEACH(NCHAIN,I)
+   10 CONTINUE
+      TSLEAC = TOCC
+      IF( CONTIM.GT.TOCC )  TSLEAC = CONTIM
+C
+C
+      NTNF=NTIME
+      KDOS=0
+      DO  30  J = 1, NTIME
+          T = TSTEP(J)
+C
+C                   BATEMAN EQUATION
+C                   ================
+C
+          C A L L  B A T M A N (T,NELCHN,AL,CC,RL,TSLEAC,CIN)
+C
+          IFLAG=0
+          DO  20  I = 1, NELCHN
+              IF( CIN(I).NE.0. )  THEN
+                  KDOS=KDOS+1
+                  ADOS(I,J) = CIN(I)*RL(I)
+                  IFLAG=1
+              ENDIF
+   20     CONTINUE
+          IF( IFLAG.EQ. 0 )  THEN
+              NTNF=J
+              GO TO 40
+          ENDIF
+   30 CONTINUE
+C
+   40 CONTINUE
+      IF(KDOS.EQ.0)  THEN
+          ISAVE(NCHAIN)=0
+      ENDIF
+C
+      RETURN
+      END

### 2017-02-10 levelEmodel/src/sift.f

@@ -1,0 +1,27 @@
+      SUBROUTINE SIFT(N,XV)
+C*****PERFORM ASCENDING SORT ON ARRAY XV
+      DIMENSION  XV(N)
+      M=N
+ 1000 CONTINUE
+      M=M/2
+      IF(M) 3000, 9000, 3000
+ 3000 CONTINUE
+      K=N-M
+      J=1
+ 4000 CONTINUE
+      I=J
+ 5000 CONTINUE
+      L=I+M
+      IF(XV(L)-XV(I)) 6000, 7000, 7000
+ 6000 CONTINUE
+      A=XV(I)
+      XV(I)=XV(L)
+      XV(L)=A
+      I=I-M
+      IF(I) 7000, 7000, 5000
+ 7000 CONTINUE
+      J=J + 1
+      IF(J-K) 4000, 4000, 1000
+ 9000 CONTINUE
+      RETURN
+      END

### 2017-02-10 levelEmodel/src/spopinc.h

@@ -1,0 +1,75 @@
+                                                                                
+C>>>>>>>>>>>>>>INCLUDED COMMONS>>>>>>>>>>>>>                                    
+                                                                                
+      PARAMETER (NRUNSM=16384,NVARSM=50,NTPM=500,                                
+     &          NTIMEM=44,NESTM=14,NVMOSM=10,                                   
+     &          NCMBMX=100)                                                     
+                                                                                
+                                                                                
+      COMMON /CONST/                                                            
+     &            EPSI,ALPHA,BETA,GAMMA,YTRUN,IOPT                              
+                                                                                
+      COMMON /VARIAB/                                                           
+     &            TIMES(NTIMEM),PTIME(NTPM),                                    
+     &            XINP(NRUNSM,NVARSM+1),YVAR(NTPM),                             
+     &            JTIME(NTIMEM)                                                 
+                                                                                
+      COMMON /HIMARR/                                                           
+     &            VHIM(NCMBMX,NTIMEM),VHIMR(NCMBMX,NTIMEM),                     
+     &            DHAT(NCMBMX,NTIMEM),DHATR(NCMBMX,NTIMEM),                     
+     &            DHATER(NCMBMX,NTIMEM,2),                                        
+     &            DHARER(NCMBMX,NTIMEM,2),                                        
+     &            SCHIM(NTIMEM,3),SCHIMR(NTIMEM,3),                             
+     &            NV(NCMBMX,NVARSM),KEL(NCMBMX),                                
+     &            HIMCMB,NCMB,HIMS                                              
+                                                                                
+      COMMON /RUNCON/                                                           
+     &            ISELVA(NVARSM),VALNOR,                              
+     &            NRUNS,NVARS,NVARP1,NVMP1,NTP,NTIMES,NEST,NVMOST,              
+     &            NOUTVA,NVAOUT,ISEL,                                           
+     &            SELKEY(NVARSM),                                               
+     &            SWPEA,SWSMI,SWTTS,SWSHI,SWHIM,SWPOIN,YESNOT(NESTM),           
+     &            SWINTP,WORD,SWTIME,SWNORM,SWREGR                                  
+                                                                                
+      COMMON /ANAMES/                                                           
+     &            VARNAM(NVARSM)                                                
+     &           ,ESTNAM(NESTM)                                                 
[…]

### 2017-02-10 levelEmodel/src/subass.h

@@ -1,0 +1,5 @@
+      SUBROUTINE ASSIGN ( 
+     & CONTIM         ,RLI            ,RLC            ,VREAL(1)       
+     &,XPATH(1)       ,RET(I,1)       ,FC(1)          ,VREAL(2)       
+     &,XPATH(2)       ,RET(I,2)       ,FC(2)          ,STFLOW         
+     &   ) 

### 2017-02-10 levelEmodel/src/subcon.h

@@ -1,0 +1,8 @@
+      SUBROUTINE ASSCON ( 
+     & C0(I129)       ,C0(NP237)      ,C0(U233)       ,C0(TH229)      
+     &,DISPC(1)       ,RETC(NP,1)     ,RETC(U,1)      ,RETC(TH,1)     
+     &,DISPC(2)       ,RETC(NP,2)     ,RETC(U,2)      ,RETC(TH,2)     
+     &,DIFFM          ,DSF(I129)      ,DSF(NP237)     ,DSF(U233)      
+     &,DSF(TH229)     
+     &,RMW            
+     &   ) 

### 2017-02-10 levelEmodel/src/var.h

@@ -1,0 +1,13 @@
+C
+       CONTIM         = XVAR( 1)
+       RLI            = XVAR( 2)
+       RLC            = XVAR( 3)
+       VREAL (1)      = XVAR( 4)
+       XPATH (1)      = XVAR( 5)
+       RET   ( 1,1,1) = XVAR( 6)
+       FC    (1)      = XVAR( 7)
+       VREAL (2)      = XVAR( 8)
+       XPATH (2)      = XVAR( 9)
+       RET   ( 1,1,2) = XVAR(10)
+       FC    (2)      = XVAR(11)
+       STFLOW         = XVAR(12)

### 2017-02-13 article_review/matlab_code_revision/SI_all_example_percentage.m
Rerunning results for wingweight function and adding the SI estimates

@@ -125,6 +125,8 @@ hyperbox = [150 220 6  -1/18*pi 16 0.5 0.08 2.5 1700 0.025;
             200 300 10  1/18*pi 45 1   0.18 6   2500 0.08 ];
 
 SI = zeros(2, d);
+SI_estimates = [];
+SI_estimates_small = [];
 SI_small = zeros(2, d);
 SI_n = SI;
 SI_n_small = SI_small;
@@ -136,10 +138,12 @@ for k = 1:samples
     sobstr = scramble(sobstr,'MatousekAffineOwen'); %scramble it
     [q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,sobstr,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d), 'threshold_small', 0);
     SI = SI + q;
+    SI_estimates = [SI_estimates; q];
     SI_n_print = [SI_n_print; out_param.n];
     SI_n = SI_n + out_param.n;
     [q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,sobstr,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d), 'threshold_small', threshold_small);
     SI_small = SI_small + q;
+    SI_estimates_small = [SI_estimates_small; q];
     SI_n_print_small = [SI_n_print_small; out_param.n];
     SI_n_small = SI_n_small + out_param.n;
     small = [small; out_param.small];
@@ -148,5 +152,7 @@ SI = SI/samples; SI_n = SI_n/samples;
 SI_small = SI_small/samples; SI_n_small = SI_n_small/samples;
 
 csvwrite('wingweight_variantAa_nvalues.csv', SI_n_print)
+csvwrite('wingweight_variantAa_SIvalues.csv', SI_estimates)
+csvwrite('wingweight_variantAb_SIvalues.csv', SI_estimates_small)
 csvwrite('wingweight_variantAb_nvalues.csv', SI_n_print_small)
 csvwrite('wingweight_variantAb_small_estimates.csv', small)

### 2017-02-13 article_review/matlab_code_revision/SI_fo_example_percentage.m

@@ -1,7 +1,6 @@
 clearvars
 
 abstol = 5*1e-3;
-pre = 2; % Precision to display according to 1*1e-3 (3 digits)
 reltol = 0e-2; % Pure absolute tolerance
 mmin = 9;
 mmax = 24; % I adjust that not to run out of memory. It can go up to 54. Type help cubSobol_SI_g for more information.
@@ -94,14 +93,15 @@ hyperbox = [150 220 6  -1/18*pi 16 0.5 0.08 2.5 1700 0.025;
 SI = zeros(1, d);
 SI_n = SI;
 SI_n_print = [];
+SI_estimates = [];
 for k = 1:samples
     [q,app_int,out_param] = cubSobol_SI_fo_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d));
     SI = SI + q;
+    SI_estimates = [SI_estimates; q];
     SI_n_print = [SI_n_print; out_param.n];
     SI_n = SI_n + out_param.n;
 end
 SI = SI/samples; SI_n = SI_n/samples;
-% round(SI, pre,'significant')
-% round(SI_n)
 
 csvwrite('wingweight_variantB_replicated_nvalues.csv', SI_n_print)
+csvwrite('wingweight_variantB_replicated_SIvalues.csv', SI_estimates)

### 2017-02-13 article_review/matlab_code_revision/SI_all_example_percentage.m
Adding results for the Sobol-g function

@@ -11,62 +11,62 @@ samples = 100;
 
 fudge = @(m,d) 10*2.^-(1.*m);
 
-%% Bratley et al.
-disp('Running Bratley et al. example ...')
-d = 6;
-f = @(x) sum(bsxfun(@times, cumprod(x,2), (-1).^(1:d)),2) +  pause_t(s);
-hyperbox = [-zeros(1,d) ; ones(1,d)];
-
-R = [.6528636616, .1791303924, 0.3701041165e-1, 0.1332374820e-1, 0.1480416466e-2, 0.1480416466e-2; .7396477462, .2659144770, 0.764211693e-1, 0.343115454e-1, 0.62384628e-2, 0.62384628e-2];
-SI = zeros(2, d);
-SI_small = zeros(2, d);
-SI_n = SI;
-SI_n_small = SI_small;
-error = SI;
-error_small = SI_small;
-reliability = SI;
-reliability_small = SI_small;
-error_all = [];
-error_all_small = [];
-SI_n_print = [];
-SI_n_print_small = [];
-small = [];
-for k = 1:samples
-    sobstr = sobolset(3*d); %generate a Sobol' sequence 3*d to consider the changing to the estimator for some smaller size indices
-    sobstr = scramble(sobstr,'MatousekAffineOwen'); %scramble it
-    [q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,sobstr,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d), 'threshold_small', 0);
-    SI = SI + q;
-    SI_n_print = [SI_n_print; out_param.n];
-    SI_n = SI_n + out_param.n;
-    error = error + abs(R-q);
-    error_all = [error_all; abs(R-q)];
-    reliability = reliability + 1*(abs(R-q) > max(abstol,R*reltol));
-    [q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,sobstr,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d), 'threshold_small', threshold_small);
-    SI_small = SI_small + q;
-    SI_n_print_small = [SI_n_print_small; out_param.n];
-    SI_n_small = SI_n_small + out_param.n;
-    error_small = error_small + abs(R-q);
-    error_all_small = [error_all_small; abs(R-q)];
[…]

### 2017-02-13 article_review/matlab_code_revision/SI_fo_example_percentage.m

@@ -11,45 +11,45 @@ samples = 100;
 
 fudge = @(m,d) 10*2.^-(1.*m);
 
-%% Bratley et al.
-disp('Running Bratley et al. example ...')
-d = 6;
-f = @(x) sum(bsxfun(@times, cumprod(x,2), (-1).^(1:d)),2) +  pause_t(s);
-hyperbox = [-zeros(1,d) ; ones(1,d)];
-
-R = [.6528636616, .1791303924, 0.3701041165e-1, 0.1332374820e-1, 0.1480416466e-2, 0.1480416466e-2];
-SI = zeros(1, d);
-SI_n = SI;
-error = SI;
-reliability = SI;
-error_all = [];
-SI_n_print = [];
-for k = 1:samples
-    [q,app_int,out_param] = cubSobol_SI_fo_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d));
-    SI = SI + q;
-    SI_n_print = [SI_n_print; out_param.n];
-    SI_n = SI_n + out_param.n;
-    error = error + abs(R-q);
-    error_all = [error_all; abs(R-q)];
-    reliability = reliability + 1*(abs(R-q) > max(abstol,R*reltol));
-end
-SI = SI/samples; SI_n = SI_n/samples; reliability = 1 - reliability/samples; error = error/samples;
-% round(SI, pre, 'significant')
-% round(SI_n)
-% round(error, pre, 'significant')
-% round(reliability*100)
-
-csvwrite('bratley_variantB_replicated_reliability.csv', reliability)
-csvwrite('bratley_variantB_replicated_errors.csv', error_all)
-csvwrite('bratley_variantB_replicated_nvalues.csv', SI_n_print)
-
-
+% %% Bratley et al.
+% disp('Running Bratley et al. example ...')
+% d = 6;
+% f = @(x) sum(bsxfun(@times, cumprod(x,2), (-1).^(1:d)),2) +  pause_t(s);
+% hyperbox = [-zeros(1,d) ; ones(1,d)];
+% 
+% R = [.6528636616, .1791303924, 0.3701041165e-1, 0.1332374820e-1, 0.1480416466e-2, 0.1480416466e-2];
+% SI = zeros(1, d);
+% SI_n = SI;
+% error = SI;
[…]

### 2017-02-14 article_review/reviewer_letter.tex
added tex for review letter

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb,
mathtools,bm,extraipa,mathabx,graphicx,algorithm}
\usepackage{color}

\newcommand{\vect}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\vk}{\vect{k}}
\newcommand{\vx}{\vect{x}}
\newcommand{\vI}{\vect{I}}
\newcommand{\hS}{\widehat{S}}
\newcommand{\tS}{\widetilde{S}}
\newcommand{\wcS}{\widecheck{S}}
\def\dashfill{\cleaders\hbox to 2em{-}\hfill}

\makeatletter
\newcommand{\ov}[1]{
  \m@th\overline{\mbox{#1}\raisebox{2mm}{}}
}

\begin{document}

\textcolor{blue}{Dear associated editor and reviewers,\\
we would like to thank you for the positive and constructive feedback. Below we have
compiled a detailed list of answers (blue text) to the issues raised in the review reports. In particular, in light of reviewer's two remark, the Asian option problem was deleted and replaced with a new ``real function''.\\
Best regards,\\
Laurent Gilquin and Llu\'{i}s Antoni Jim\'{e}nez Rugama}

\section*{Report on ``Reliable error estimation for Sobol' indices''}

\textbf{\large{Associate Editor comments}}
\vspace*{0.5cm}

\begin{itemize}
\item[1.] Page 4, left, line 52: What are $\kappa$ and $\vk(\kappa)$ there? They seem undefined, and then many readers will not understand what follows.
\item[2.] Page 4, right, line 30: Remove the period before (13).
\item[3.] Page 4, right, lines 38--42: We find $\epsilon_{\hat I}$ in (14) and $\epsilon_{I}$ below (seems inconsistent).
\item[4.] Section 5.2: These empirical results are for what parameters $d$, $T$, $S_0$, $\sigma$, $\rho$, $K$? I expect the behavior to depend strongly on the values of these parameters. E.g., large $d$ vs small $d$, large $T$ vs small $T$, large $\sigma$ vs small $\sigma$, etc. Also, this example is largely academic and not based on real-life data; I would not call it a "real-life" example. 
\item[5.] The given examples are only in small dimensions. What about higher-dimensional "real-life" examples?-- Pierre L'Ecuyer
\end{itemize}

\textbf{\large{Reviewer $1$}}
\vspace*{0.5cm}

\textbf{Major comments}:

\begin{itemize}
\item[1.] Advantages of using this method: The proposed method seems to work well in that with enough function evaluations, in most case the Sobol' indices can be estimated with good accuracy. In Section 2.3, the authors discuss a few alternative approaches and their disadvantages. They argue the main advantages of their approach are that 1) it guarantees the desired error threshold is met and 2) is not costly to compute. A concern with 1) is that we see later that sometimes the error threshold looks like it is not met (see item (3) below on the topic of the set C). A concern with 2) is that later in the paper, the discussion of the cost only focuses on the evaluation of the function f and seems to ignore the cost of constructing the error threshold (see item (2) below about "complete assessment of the cost"). In light of these concerns, simpler methods based on random sampling and straightforward confidence intervals become more attractive, as they have no extra cost and potentially a better assessment of how likely it is that the error is met (i.e., they provide a probabilistic statement about the error vs hoping parameters have been chosen so that the threshold is valid). I think this point should be discussed more thoroughly -- perhaps in the conclusion, or in Section 5 -- by the authors in order to convince the readers that the proposed method is indeed better.

\item[2.] Complete assessment of the cost: Since only the different variants of this method are compared in the numerical results, it is fair to focus on the number of function evaluations to compare their respective costs. However, and as discussed in paper [4] from the list of references (in particular toward the end of Theorem 1 in [4]), the overall cost of this method should also include the Walsh function evaluations required to determine the quantity $\widetilde{S}_{l,m}$ used in the error calculation via (14). The authors should mention this and discuss this impact of this cost on comparisons that are made with other methods.

\item[3.]The set C: In the section describing numerical results, choices are made for the parameters $\ell^*$ and $r$ which in turn define the set (cone) of functions C for which the error threshold formula (14) used to derive the algorithm holds. There should be some information in the paper on whether or not the functions considered in this section can be shown to be in this cone. This is especially important in light of the results obtained on page 10 (column 1, lines 36-38), where it looks like the error threshold was not met by the algorithm. Is it because the function is not in C?
\end{itemize}

\textbf{Minor comments}:
\begin{itemize}
\item[a.] page 1, column 1, lines 23-24: "through" instead of "trough"
\item[b.] page 2, column 2, equation (7): why use a biased estimator for $\sigma^2$ ?
\item[c.] page 4, column 2, equation (14): it is not clear how $\ell$ is chosen on the RHS, and whether or not the inequality holds for all $\ell \leq m$ or for some specific value of $\ell$ ? Please clarify.
\item[d.] page 4, column 2, line 42: is it not instead "...the error bound $\epsilon_{\hat{I}}$" (hat on subscript I?)?
\item[e.] page 5, column 2 line 55: not clear what you mean by "independent" in "two independent Sobol' sequences", especially if the designs are not randomized. From [4] it looks like you are using a 2d-dimensional Sobol' sequence and assign the first d coordinates to the first design and the next d ones to the second design. Please explain this more and state what properties you need for these sequences.
\item[f.] page 6, column 2, line 32: is the "iid" property valid across the indices i, i.e., the n vectors have to be independent? If so, this would invalidate the use of a Sobol' sequence to create these vectors, so please clarify this point.
\item[g.] page 9, column 2 , "real case model". There are some imprecisions in this part: lines 15-16, it should be the "discounted payoff" and not just "payoff", rho is the risk-free interest rate (not just interest rate). More importantly, the authors directly give the discounted payoff in terms of the Brownian motion without stating what model is used for the stock price and without stating that for the purpose of pricing one should work under the risk-neutral measure. Please clarify this so that the financial motivation for this problem is properly done.
\end{itemize}

\textbf{\large{Reviewer $2$}}
\vspace*{0.5cm}

\textbf{Major comments}:
\begin{itemize}
\item[1.] Definition 1 is not enough to get good points. Additional criteria should be attached to it, either by making the definition stricter or requiring some
other conditions to hold.

To illustrate, suppose that $u_0,\dots,u_{n-1} \in [0,1]$ are chosen. Then let $\vx_i = (u_i, u_i, \dots,u_i) \in \mathbb{R}^d$ and choose $\vx'_i= \vx_{\pi(i)}$ where $\pi$ is a permutation
of $0$ through $n-1$. Now we have replicated designs of order $a$ for any $a = 1,\dots,d-1$. In fact simply taking $n = 1$ and $\vx'=\vx \in [0,1]^d$ will do.

Also, how is $\pi_u$ defined when there is more than one permutation that rearranges the rows $\vx'_i$ into $\vx_i$? Maybe it should say ``to be any permutation
that rearranges the rows ... ''.

{\color{blue} Thank you for this remark. The definition was intended to include only point sets where all points are coordinate-wise different. Namely, consider a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and two points $\vx_{i_1}$, $\vx_{i_2}$, $i_1 \neq i_2$. Then $\vx_{i_1}$ and $\vx_{i_2}$ are coordinate-wise different if: 
$$ x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
Definition 1 has been reworked to include this property. This also tackles the issue of having more than one permutation that would rearranges the rows $\vx'_i$ into $\vx_i$. Now, the permutation is unique.

Furthermore, a remark was added to specify that in this paper $\mathcal{P}$ and $\mathcal{P}'$ are constructed to avoid the degenerate case $\forall i, \ \vx'_i=\vx_i$.}

\item[2.] Section $3.1$ needs more detail for readers not already familiar with the approach. For instance on page $4$ line $16$ a little should be said about what $k_{j\ell}$ is. It should also briefly say in words what $S_m$, $\hS_{\ell,m}$, $\wcS_m$ and $\tS_{\ell,m}$ all mean.

\item[3.] Page $5$ line $56$ presents some bounds that the Sobol' indices must satisfy. Sometimes they won't satisfy those bounds. When do they fail, how that
be detectable, and what can we do in the face of bounds that might or might not hold? Presumably these issues have been discussed in simpler contexts. The paper should address this issue.

\item[4.]If we replace $f$ by $f-c$ for some constant shift $c$, then the Sobol' indices do not change. But the bounds for $\underline{S}_u$ and $\overline{S}_u$ do change because $\vI_3$ is affected. What could/should we do about this?

\item[5.] Page $7$ lines $22:27$. The discussion here is saying that the higher dimensional integrand is likely to be the one that needs more evaluations. That is not in line with the last couple of decades of QMC theory. The nominal dimension might not be very telling. Maybe only a few of the inputs are important in the higher dimensional integrand, or maybe the higher order variable interactions are less important for that integrand.

So, can you give a better reason for why that integrand might need larger $n$? Alternatively, in the numerical examples, which integrands required the most evaluations?
(This point touches on the circular issue, perhaps best avoided, of finding which variables are important when you're estimating a Sobol' index.)

\item[6.] In Section $5.1.1$, the Sobol' g-function looks like a potentially misleading choice. It is completely smooth except when one of the inputs is $1/2$.
That makes it a particularly favorable problem for Sobol' points or any points in base $2$. The problem might just be too QMC-friendly. It would be better to use $g_j(x_j) = (|3x_j-2| + a_j)/(1 + a_j)$ which has issues when
$x_j = 2/3$ which is not dyadic. The QMC friendly version might still work exactly the same as the unfriendly version, but changing $g$ just removes that issue from consideration.

\item[7.] The Asian option is very over used in QMC problems. We already know that BB and PC make the first component most important. It might be interesting to compare these two, although the answer might depend on
the strike price and volatility.

For the same amount of work, the authors could use a real function where the answer would be interesting. Derek Bingham maintains a site of test functions for computer experiments. Some of those would be more suitable.

\item[8.] Sobol' indices are often motivated by the need to identify important variables when $f$ is expensive to evaluate; perhaps half a day for $n = 1$. Estimates that require $n$ to be several hundred thousand do not fitthat motivating context. If the authors can describe a context where it would be worth having $n = 400000$ to get a Sobol' estimate, that would be great. Nobody else has properly addressed this issue, so this point is a
suggestion, not a requirement.
\end{itemize}

\textbf{Minor comments}:
\begin{itemize}
\item[a.] page $2$ line $48$: it should be clear that $v \subset $u excludes $v = u$.

\item[b.] page $2$ line $59$: it is not clear why $u = \mathcal{D}$ is ruled out. In that case both $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ equal $\sigma^2$.

\item[c.] equation (7) is a numerically poor way to estimate $\sigma^2$ (roundoff errors).

\item[d.] page $3$ line $37$: accordingly $\rightarrow$ according

\item[e.] page $4$: there is a symbol class of $S$ for Sobol' indices with $S_m(f)$ and related quantities. The paper could note the distinction or possibly use a
new letter.

\item[f.] page $8$ line $16$: twice as small  $\rightarrow$ half as large
\end{itemize}
\end{document}

### 2017-02-14 article_review/reviewer_letter.tex
modifs in reviewer's letter

@@
 
-{\color{blue} Thank you for this remark.
-The definition was intended to include only point sets where all points are coordinate-wise different.
-Namely, consider a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and two points $\vx_{i_1}$, $\vx_{i_2}$, $i_1 \neq i_2$.
+{\color{blue} We thank the reviewer for this remark.
+The definition was intended for point sets where all points are coordinate-wise different.
+More precisely, consider a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and two points $\vx_{i_1}$, $\vx_{i_2}$, $i_1 \neq i_2$.
 Then $\vx_{i_1}$ and $\vx_{i_2}$ are coordinate-wise different if:
@@
 Definition 1 has been reworked to include this property.
-This also tackles the issue of having more than one permutation that would rearranges the rows $\vx'_i$ into $\vx_i$.
+This also tackles the issue of having more than one permutation that would rearrange the rows $\vx'_i$ into $\vx_i$.
 Now, the permutation is unique.
 
-Furthermore, a remark was added to specify that in this paper $\mathcal{P}$ and $\mathcal{P}'$ are constructed to avoid the degenerate case $\forall i, \ \vx'_i=\vx_i$.}
+Furthermore, a remark was added to specify that in this paper $\mathcal{P}$ and $\mathcal{P}'$ are constructed to avoid the degenerate case: $\forall i, \ \vx'_i=\vx_i$.}
 
@@
 What could/should we do about this?
+
+{\color {blue} We acknowledge that Sobol' indices are theoretically invariant by adding a constant shift $c$ to the studied function.
+As underlined by the reviewer, the addition of a constant shift $c$ modifies the error bound for $\vI_3$ but also the errors bounds for the others integrands ($\vI_1$, $\vI_2$ and $\vI_4$).
+More generally, our algorithm depends on the analytical expression of the Sobol' index estimator considered.
+
+However, that is not a concerns since error bounds for any estimator can be calculated.
+That is, our algorithm can be adapted to any Sobol' index estimator.
+In particular, this is done when ``Correlation 2'' is used in Variant A.b instead of (5).}
 
@@
 
+{\color{blue} The Sobol' g-function has been modified according to the reviewer remark. Corresponding tables and figures have changed.}
+
 \item[7.] The Asian option is very over used in QMC problems.
@@
 
+{\color{blue} The Asian option problem has been replaced by the wing weight test function taken from the suggested database.
+Section $5.2$ has been reworked to introduce this new test function.
+Our results are compared to formers obtained by screening approaches.}
+
 \item[8.] Sobol' indices are often motivated by the need to identify important variables when $f$ is expensive to evaluate; perhaps half a day for $n = 1$.
@@
 suggestion, not a requirement.
+
+{\color{blue} We understand and agree with the issue raised by the reviewer.
+A possible solution is to choose a higher target precision $\epsilon$ when dealing with time-expensive function.
+In the proposed examples, $\epsilon$ was intentionally fixed small to put forward the performance of our algorithm.
+To cover both situations (small and high value of $\epsilon$), the bratley example has been reworked.
+
+On another hand, if one has to deal with a function where one day is required to obtain one evaluation, perhaps the use of Sobol' indices should be dropped for a screening method (less accurate but less greedy).
+Or if available, one could make use of a cluster to perform multiple model evaluations in parallel.}
 \end{itemize}
@@
 \end{itemize}
+
+{\color{blue} All minors points have been dealt with.
+For point c., equation (7) was replaced with the unbiased estimator of $\sigma^2$.
+For point e., the distinction has been noted in the paper given that notations cannot be changed (they need to match those of the sourced paper).
 \end{document}

### 2017-02-14 article_review/matlab_code_revision/SI_all_example_percentage.m
Adding results for new Sobol gfunction

@@ -69,7 +69,8 @@ a = [0 1/2 3 9 99 99];
 f = @(x) prod(bsxfun(@(x,a) (abs(3*x-2)+a)./(1+a), x , a),2) +  pause_t(s);
 hyperbox = [zeros(1,d) ; ones(1,d)];
 
-R = [.5867811893, .2607916397, 0.3667382378e-1, 0.5867811312e-2, 0.5867753221e-4, 0.5867753221e-4; .6900858920, .3561733634, 0.563335432e-1, 0.91705767e-2, 0.920079e-4, 0.920079e-4];
+% R = [.5867811893, .2607916397, 0.3667382378e-1, 0.5867811312e-2, 0.5867753221e-4, 0.5867753221e-4; .6900858920, .3561733634, 0.563335432e-1, 0.91705767e-2, 0.920079e-4, 0.920079e-4]; % If abs(4x-2)
+R = [.6042800971, .2360469148, 0.2855765831e-1, 0.4339846615e-2, 0.4210460219e-4, 0.4210460219e-4; .7251945137, .3480933667, 0.483463013e-1, 0.74762327e-2, 0.727601e-4, 0.727601e-4]; % If abs(3x-2)
 SI = zeros(2, d);
 SI_small = zeros(2, d);
 SI_n = SI;
@@ -84,6 +85,7 @@ SI_n_print = [];
 SI_n_print_small = [];
 small = [];
 for k = 1:samples
+    disp(k)
     sobstr = sobolset(3*d); %generate a Sobol' sequence 3*d to consider the changing to the estimator for some smaller size indices
     sobstr = scramble(sobstr,'MatousekAffineOwen'); %scramble it
     [q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,sobstr,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d), 'threshold_small', 0);

### 2017-02-14 article_review/matlab_code_revision/SI_fo_example_percentage.m

@@ -52,7 +52,8 @@ a = [0 1/2 3 9 99 99];
 f = @(x) prod(bsxfun(@(x,a) (abs(3*x-2)+a)./(1+a), x , a),2) +  pause_t(s);
 hyperbox = [zeros(1,d) ; ones(1,d)];
 
-R = [.5867811893, .2607916397, 0.3667382378e-1, 0.5867811312e-2, 0.5867753221e-4, 0.5867753221e-4];
+% R = [.5867811893, .2607916397, 0.3667382378e-1, 0.5867811312e-2, 0.5867753221e-4, 0.5867753221e-4]; % If abs(4x-2)
+R = [.6042800971, .2360469148, 0.2855765831e-1, 0.4339846615e-2, 0.4210460219e-4, 0.4210460219e-4]; % If abs(3x-2)
 SI = zeros(1, d);
 SI_n = SI;
 error = SI;

### 2017-02-16 article_review/Manuscript.tex
Adding changes on manuscript

@@
 \newcommand{\vx}{\vect{x}}
+\newcommand{\vl}{\vect{l}}
 \newcommand{\vI}{\vect{I}}
@@
 
+\newcommand{\comment}[1]{{\color{cyan} (Toni) #1 }}
 % Insert the name of "your journal" with
@@
 
-We assume we have an embedded sequence of digital nets in base $b$ as in \cite[Sec. 2-3]{HicJim},
-\[
+We will assume that we have an embedded sequence of digital nets \comment{in $\cube$, base $b$ and dimension d} as described in \cite[Sec. 2-3]{HicJim},
+\begin{equation}\label{embedded_digital}
 \mathcal{P}_0=\{\vect{0}\}\subset\dots\subset\mathcal{P}_m=\{\vx_i\}_{i=0}^{b^m-1}\subset\dots\subset\mathcal{P}_\infty=\{\vx_i\}_{i=0}^{\infty}.
-\]
-Each $\mathcal{P}_m$ has a group structure under the digitwise addition:
+\end{equation}
+\comment{The Sobol' sequence is an example of a digital net in base two satisfying \eqref{embedded_digital}, which in dimension one corresponds to: $\mathcal{P}_0=\{0\}$, $\mathcal{P}_1=\{0,0.5\}$, $\mathcal{P}_2=\{0,0.5,0.25,0.75\}$, $\mathcal{P}_3=\{0,0.5,0.25,0.75,0.125,0.625,0.375,0.875\}$,...}
+
+\comment{For this sequence of digital nets,} each $\mathcal{P}_m$ has a group structure under the digitwise addition:
 \[
@@
 \]
-where $x_{j\ell}$ and $t_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ component of points $\vx$ and $\vt$.
-
-To relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the relationship between any digital net and the \emph{wavenumber} space of non-negative integers $\mathbb{N}_0^d$.
-A dual net is
+where $x_{j\ell}$ and $t_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ component of points $\vx$ and $\vt$,\comment{ i.e.
+\[
+x_{j} = \sum_{\ell=1}^{\infty} x_{j\ell}b^{-\ell},\qquad t_{j} = \sum_{\ell=1}^{\infty} t_{j\ell}b^{-\ell}.
+\]
+For $b=2$, the digitwise addition is equivalent to the XOR operation.
+
+In addition, we consider the \emph{wavenumber} space of non-negative integers $\mathbb{N}_0^d$.
+These non-negative integers will index the frequencies in which we decompose our integrand as a Fourier series.
+The space $\mathbb{N}_0^d$ is also a group under the digitwise addition:
+\[
+\vk \oplus \vl = \left(\sum_{\ell=0}^{\infty} [(k_{j\ell} + l_{j\ell}) \bmod b] b^{\ell} \right)_{j=1}^d,
+\]
+where $k_{j\ell}$ and $l_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ components,
+\[
+k_{j} = \sum_{\ell=0}^{\infty} k_{j\ell}b^{\ell},\qquad l_{j} = \sum_{\ell=0}^{\infty} l_{j\ell}b^{\ell}.
+\]
+}
+To relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the link between any digital net and the \emph{wavenumber} space.
+A dual net $\mathcal{P}_m^\perp$ is
 \begin{align*}
-\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vk}{\vx}=0,\, \vx\in\mathcal{P}_m\}, \\
-\ip{\vk}{\vx} = \sum_{j=1}^{d} \sum_{\ell=0}^{\infty} k_{j\ell}x_{j,\ell+1}  \pmod b,
+\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vk}{\vx}=0,\, \text{ for all } \vx\in\mathcal{P}_m\}, \\
+\ip{\vk}{\vx} = \left(\sum_{j=1}^{d} \sum_{\ell=0}^{\infty} k_{j\ell}x_{j,\ell+1}  \pmod b \right)/b,
 \end{align*}
-and inherits the same embedded structure as for digital nets,
+and inherits the inverted embedded structure \eqref{embedded_digital},
 \begin{equation}\label{dual_net_structure}
@@
 \end{equation}
-As shown in \cite[Sec. 3]{HicJim}, the group structure of digital nets guarantees the property below affecting any Walsh basis \\$\varphi_{\vk}(\vx)=\e^{2 \pi \sqrt{-1} \ip{\vk}{\vx}/b}$,
+
+As shown in \cite[Sec. 3]{HicJim}, the group structure of digital nets guarantees the property below affecting any Walsh basis function $\varphi_{\vk}(\vx)=\e^{2 \pi \sqrt{-1} \ip{\vk}{\vx}}$,
 \begin{equation}\label{basis_integ_prop}
@@
 \end{equation}
-
-Therefore, considering the Walsh decomposition of any $f\in \mathbb{L}^2([0,1]^d)$: \[
+Therefore, using the Walsh decomposition of $f\in \mathbb{L}^2([0,1]^d)$: \[
 f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
-and,
+and defining the value of the integral,
 \[ I = \int_{\cube} f(\vx)\,d\vx,\]
@@
 Based on the size of $\absolute{\hf_{\vk}}$ and the structure of dual nets \eqref{dual_net_structure}, in \cite[Sec.
-4.1]{HicJim} we proposed an ordering of the \emph{wavenumbers} $\vk(\cdot):\naturals_0\rightarrow\naturals_0^d$.
-Defining $\hf_{\kappa}=\hf_{\vk(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,
-\begin{equation}
+4.1]{HicJim} we proposed an ordering of the \emph{wavenumbers} $\tilde{\vk}(\cdot):\naturals_0\rightarrow\naturals_0^d$.
+\comment{This ordering $\tilde{\vk}$ is a one-to-one and onto mapping between $\naturals_0$ and $\naturals_0^d$.
+Thus, we can identify each $\vk\in\naturals_0^d$ with one $\kappa\in\naturals_0$ such that $\tilde{\vk}(\kappa)=\vk$.
+This ordering ensures that $\mathcal{P}_m^\perp\setminus\{\vzero\}=\{\tilde{\vk}(\lambda b^m)\}_{\lambda=1}^\infty$.
+If we identify $\hf_{\kappa}=\hf_{\tilde{\vk}(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,}
+\begin{equation}\label{mapped_error_bound}
 \absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
 \end{equation}
-Nonetheless, because the knowledge of the Walsh coefficients $\hf_{\kappa}$ is not assumed, we will estimate them using the fast transform obtained with the precomputed function values, and refer to them as $\tf_{m,\kappa}$,
+\comment{To use the error bound \eqref{mapped_error_bound} to design and automatic algorithm would require the knowledge of the Walsh coefficients.
+To avoid this assumption, we will estimate them via the fast transform obtained using the precomputed function values.
+We will refer to the discrete coefficients as $\tf_{m,\kappa}$,}
 \[
-\tf_{m,\kappa}=\tf_{m,\vk(\kappa)}=\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)\overline{\varphi_{\vk(\kappa)}(\vx)}.
+\tf_{m,\kappa}=\tf_{m,\tilde{\vk}(\kappa)}=\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)\overline{\varphi_{\tilde{\vk}(\kappa)}(\vx)}.
 \]
-Note that for function values evaluated at $\mathcal{P}_m$, one only generates $b^m$ discrete Walsh coefficients $\tf_{m,\kappa}$.
+\comment{As shown in \cite[Sec. 3]{HicJim}, the error of estimating the true coefficients using the discrete coefficients can be measured,
+\begin{equation}\label{discrite_true_relationship}
+\tf_{m,\kappa} = \hf_\kappa + \sum_{\lambda=1}^{\infty} \hf_{\kappa + \lambda b^m}, \qquad \text{ for all } \kappa\in\naturals_0,
+\end{equation}
+However, since there are at most $b^m$ distinct values of $\tf_{m,\kappa}$, we require some assumptions on the decay rate of $\hf_{\kappa}$ to transform \eqref{mapped_error_bound} into a new error bound in terms of the discrete coefficients.}
 
@@
 \end{align*}
+\comment{Among these sums, one should notice that $\hS_{0,m}(f)$ corresponds to the error bound appearing in \eqref{mapped_error_bound}.
+Thus, $\wcS_m(f)$ is an infinite sum of Walsh coefficients that contain the error bound coefficients.
+To have a control on the decay rate of the coefficients, we also define the finite sum of true coefficients $S_m(f)$.
+Note that from these sums, we can only observe $\tS_{\ell,m}(f)$.
+}
+
 Finally, we define the set of functions $\cc$,
@@
 \end{multline}
-for $\ell_* \in \mathbb{N}$, $\homega$ and $\wcomega$ two non-negative valued functions with $\lim_{m \to \infty} \wcomega(m) = 0$, and such that $\homega(r)\wcomega(r)<1$ for some fixed $r\in\mathbb{N}$.
-
-In \cite[Sec. 4.2]{HicJim} it is shown that for any $f\in\cc$,
+for a fixed $\ell_* \in \mathbb{N}$, $\homega$ and $\wcomega$ two non-negative valued functions with $\lim_{m \to \infty} \wcomega(m) = 0$.
+\comment{The decay rate assumptions on the Walsh coefficients are encoded in $\cc$ and controlled by $\homega$ and $\wcomega$.
+First, we assume that $\wcS_m(f)$ bounds $\hS_{\ell,m}(f)$ in some sense, in particular it bounds $\hS_{0,m}(f)$.
+This means that we can use $\wcS_m(f)$ as a good indicator for the error bound.
+Then, we also need $S_{\ell}(f)$ to bound $\wcS_m(f)$ which helps transforming the infinite sum into a finite sum.
+In this step, we are assuming that if $S_{\ell}(f)$ is small enough, we expect the high frequency coefficients, i.e.
+$\wcS_m(f)$, to also be small.
+By defining $r=m-\ell$, and assuming that $\homega(r)\wcomega(r)<1$ with $r\in\mathbb{N}$, one may see $r$ as a distance between $S_{\ell}(f)$ and $\wcS_m(f)$: larger values of $r$ will imply a smaller error bound but more dependence on smaller Walsh coefficients.
+Finally, we can write the error bound in terms of $\tS_{\ell,m}(f)$ instead of $\wcS_m(f)$ by using \eqref{discrite_true_relationship}.} In \cite[Sec.
+4.2]{HicJim} it is shown that for any $f\in\cc$,
 \begin{equation}
 \absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
-\le \tS_{\ell,m}(f)\underbrace{\frac{\homega(m) \wcomega(m-\ell)}{1 - \homega(m-\ell) \wcomega(m-\ell)}}_{\mathfrak{C}(m)}=\epsilon_{\widehat{I}}, \label{errbd}
+\le \tS_{\ell,m}(f)\underbrace{\frac{\homega(m) \wcomega(r)}{1 - \homega(r) \wcomega(r)}}_{\mathfrak{C}(m)}=\epsilon_{\widehat{I}}, \label{errbd}
 \end{equation}
@@
 Indices $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$.
-If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$,\\ $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.
+If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$, $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.
 

### 2017-02-16 article/Images/article_scheme_S_3D.m

@@ -43,17 +43,17 @@ else
 end
 if Ireal(1) < I(1) % Ireal is indeed I, and variable I corresponds to I hat
 %     ax.XTickLabel = {'$\hat{I_3}-\varepsilon_{I_3}$','$I_3$','$\hat{I_3}$','$\hat{I_3}+\varepsilon_{I_3}$'};
-    ax.XTickLabel = {'$\hat{I_3}-\varepsilon_{I_3}$','$I_3$','$\hat{I_3}+\varepsilon_{I_3}$'};
+    ax.XTickLabel = {'$\hat{I_3}-\varepsilon_{\hat{I_3}}$','$I_3$','$\hat{I_3}+\varepsilon_{\hat{I_3}}$'};
 else
 %     ax.XTickLabel = {'$\hat{I_3}-\varepsilon_{I_3}$','$\hat{I_3}$','$I_3$','$\hat{I_3}+\varepsilon_{I_3}$'};
-    ax.XTickLabel = {'$\hat{I_3}-\varepsilon_{I_3}$','$I_3$','$\hat{I_3}+\varepsilon_{I_3}$'};
+    ax.XTickLabel = {'$\hat{I_3}-\varepsilon_{\hat{I_3}}$','$I_3$','$\hat{I_3}+\varepsilon_{\hat{I_3}}$'};
 end
 if Ireal(2) < I(2)
 %     ax.YTickLabel = {'$\hat{I_4}-\varepsilon_{I_4}$','$I_4$','$\hat{I_4}$','$\hat{I_4}+\varepsilon_{I_4}$'};
-    ax.YTickLabel = {'$\hat{I_4}-\varepsilon_{I_4}$','$I_4$','$\hat{I_4}+\varepsilon_{I_4}$'};
+    ax.YTickLabel = {'$\hat{I_4}-\varepsilon_{\hat{I_4}}$','$I_4$','$\hat{I_4}+\varepsilon_{\hat{I_4}}$'};
 else
 %     ax.YTickLabel = {'$\hat{I_4}-\varepsilon_{I_4}$','$\hat{I_4}$','$I_4$','$\hat{I_4}+\varepsilon_{I_4}$'};
-    ax.YTickLabel = {'$\hat{I_4}-\varepsilon_{I_4}$','$I_4$','$\hat{I_4}+\varepsilon_{I_4}$'};
[…]

### 2017-02-16 article_review/Manuscript.tex
changes manuscript

@@
 using for $\sigma^2$:
+{\color{purple} (Lolo)
 \begin{equation}
@@
 \label{mu.est}
-\end{equation}
+\end{equation}}
 Then, the Sobol' indices estimators are:
@@
 In order to apply this definition to other types of points, in \cite{GJAHMP} we generalized this notion to the following.
+
+{\color{purple} (Lolo) 
 \begin{definition}
 \label{rep.designs}
-Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
-$[0,1]^{d}$.
+Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1]^{d}$.
+Assume that the points $\vx_i$ (resp.
+$\vx'_i$) are all coordinate-wise different; that is $\forall (i_1,i_2) \in \{0,,n-1\}^2$, such that $i_1 \neq i_2$: $$x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
 Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp.
@@
 \end{definition}
+
+\begin{remark}
+In the following, the two replicated designs $\mathcal{P}$, $\mathcal{P}'$ are constructed to avoid the degenerate case $\forall i \ \vx_i = \vx'_i$. 
+\end{remark}}
+
 The method introduced in \cite{Mara} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$.
@@
 \end{equation}
-where one may increase $m$ until the error bound $\epsilon_{\widehat{I}}$ is small enough.
+where one may increase $m$ until the error bound {\color{purple}$\epsilon_{\widehat{I}}$} is small enough.
 
@@
 First, one must fix the tolerance $\epsilon >0$ at which Sobol' indices must be estimated, and set $m=\ell_*+r$, where $\ell_*$ and $r$ are the two hyper-parameters defined in \eqref{conecond}.
+{\color{purple} (Lolo) The choice of $\ell_*$ must be large enough to ensure that each integrand of $\underline{S}_u$ and $\overline{S}_u$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).}
+
 Then, one must construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}.
-The choice of $\ell_*$ must be large enough to ensure that each integrand of $\underline{S}_u$ and $\overline{S}_u$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).
-
-Under this construction, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two independent Sobol' sequences.
+{\color{purple} (Lolo) This approach iteratively constructs a $2d$-dimensional Sobol' sequence then assigns its first $d$ coordinates to $\mathcal{P}_{m}$ and its last $d$ coordinates to $\mathcal{P}'_{m}$.
+The $2d$-dimension Sobol' sequence is generated based on the directional numbers found in \cite{Kuo}.
+These directional numbers insure better two-dimensional projections of the resulting Sobol' sequence.
+In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling scheme \cite{HonHic00a,Owe95}.}
+
+%Under this construction, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ correspond to the first $2^{m}$ points of two independent Sobol' sequences.
 Furthermore, they possess the structure of two replicated designs of order $1$, as shown in \cite{GJAHMP}.
@@
 This option is referred as Variant $B$ in Algorithm \ref{recursive.algorithm}.
+{\color{purple} (Lolo) However, in this case, the scrambling applied to both designs must be identical to insure that $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are replicated designs of order one.}
 
@@
 \end{equation}
-Hence, the sign of this difference indicates whether or not using ``Correlation 2" brings an improvement to Variant $A$. We distinguish two cases :
+{\color{purple} (Lolo) The sign of \eqref{cost.comparison}} indicates whether or not using ``Correlation 2" brings an improvement to Variant $A$. We distinguish two cases :
 \begin{itemize}
@@
 \end{itemize}
-Overall we expect to observe case $2)$ more often than case $1)$.
+{\color{purple}(Lolo) We assume that the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$.
+If this assumption holds, we expect to observe case $2)$ more often than case $1)$ and the sign of \eqref{cost.comparison} should be negative or equal to $0$.
+The validity of this assumption is tested on the numerical examples presented in Section \ref{sec:5}.
+%Overall we expect to observe case $2)$ more often than case $1)$.
 Indeed, the numerator of $\underline{S}_u$ requires to estimate $2d$ dimensional integrals against only $d+1$ dimensional integrals for the numerator of $\ov{$S$}_u$.
 Hence, it seems reasonable to expect that it will take less points to estimate $\ov{$S$}_u$ than $\underline{S}_u$.
-
-Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to usually hold as in \cite{Owen}, ``Correlation 2" is shown to perform better for small first-order indices.
-To support this discussion, numerical examples are presented in Section \ref{sec:5}.
+Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to usually hold as ``Correlation 2" is shown to perform better for small first-order indices (\textit c.f.
+\cite{Owen}).}
 
@@
 To overcome this issue, we propose the following alternative for Variant $A$.
-If at the end of the first iteration $\widehat{\underline{S}}_u$ is smaller than a threshold (in our case $0.1$, as suggested by Owen), then the estimator (\ref{first.order.est}) is switched to ``Correlation 2" for this particular $u$ and a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+{\color{purple}(Lolo) If at the end of the first iteration $\widehat{\underline{S}}_u$ is smaller than a threshold (in our case $0.1$, as suggested by Owen), the estimator (\ref{first.order.est}) is switched to ``Correlation 2" for this particular $u$.
+Then, a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+$\mathcal{P''}$ is obtained by assigning and scrambling the next $d$ coordinates of the starting $2d$-dimensional Sobol' sequence.}
 
@@
 $$\delta_{\underline{S}_u} = \absolute{\underline{S}_u - \widehat{\underline{S}_u}}, \qquad \delta_{\overline{S}_u} = \absolute{\overline{S}_u - \widehat{\overline{S}_u}}.$$
+{\color{purple} (Lolo) True values of Sobol' indices are estimated with a precision of $10$ digits. For clarity concern, they are rounded in the tables presenting the results.}
+
 We also compare the total number of evaluations of each variant.
-Results are averaged over $100$ repetitions using Owen's scrambled Sobol' sequences \cite{HonHic00a,Owe95}.
+{\color{purple} (Lolo) Results are averaged over $100$ repetitions by applying different scrambling}.
 For each repetition, we fix the tolerance $\varepsilon=5.10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points).
@@
 
+{\color{purple} (Lolo) To verify the validity of our  assumption saying that the sign of \eqref{cost.comparison} is negative, the sum of the $c_j$ is evaluated for each repetition and barplots of its values are drawn.}
+
 %$\varepsilon=0.005$, initial $512$ points, $fudge = @(m,d) 10*2.^{-m}$, run $100$ samples and show the average values for the whole set of samples:
@@
 
-The two classical test functions considered in this article are the g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
+The two classical test functions considered in this article are {\color{purple} (Lolo) a non QMC friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
 The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.} function) and multiplicative (g-function).
@@
 
-The g-function is defined as follows:
+{\color{purple} (Lolo)
+The non QMC friendly version of the g-function is defined as follows:
 \begin{equation*}
-f(\vx)= \prod \limits_{j=1}^{d}g_j(x_j), \qquad g_j(x_j)=\frac{\left |4x_j-2 \right | + a_j}{1 + a_j}, \ a_j \geq 0.
-\end{equation*}
+f(\vx)= \prod \limits_{j=1}^{d}g_j(x_j), \qquad g_j(x_j)=\frac{\left |3x_j-2 \right | + a_j}{1 + a_j}, \ a_j \geq 0.
+\end{equation*}}
 Each value $a_j$ determines the relative importance of the $x_j$.
@@
 \renewcommand{\arraystretch}{1.25}
+{\color{purple}(Lolo) (nouvelles tables et figures)
 \begin{table}[!ht]
@@
  input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
- $x_1$ & $0.5868$ &  $0.0004$ & $0.02$ & $0.6901$ & $0.0005$ & $0.02$ \\ \hline
- $x_2$ & $0.2608$ &  $0.0006$ & $0.02$ & $0.3562$ & $0.0004$ & $0$ \\ \hline
- $x_3$ & $0.0367$ &  $0.0011$ & $0.03$ & $0.0563$ & $0.0008$ & $0$ \\ \hline
- $x_4$ & $0.0058$ &  $0.0012$ & $0.02$ & $0.0092$ & $0.0003$ & $0$ \\ \hline
- $x_5$ & $5.10^{-5}$ & $0.0003$ & $0$ & $9.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
- $x_6$ & $5.10^{-5}$ & $0.0003$ & $0$  & $9.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
-\multicolumn{4}{l}{Total number of evaluations: $63 \ 088$} & & &\\ \hline 
+ $x_1$ & $0.6043$ &  $0.0005$ & $0$ & $0.7252$ & $0.0001$ & $0$ \\ \hline
+ $x_2$ & $0.2360$ &  $0.0006$ & $0$ & $0.3481$ & $0.0007$ & $0$ \\ \hline
+ $x_3$ & $0.0286$ &  $0.0007$ & $0$ & $0.0483$ & $0.0005$ & $0$ \\ \hline
+ $x_4$ & $0.0043$ &  $0.0025$ & $0.11$ & $0.0075$ & $0.0004$ & $0$ \\ \hline
+ $x_5$ & $4.10^{-5}$ & $0.0003$ & $0$ & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
+ $x_6$ & $4.10^{-5}$ & $0.0003$ & $0$  & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
+\multicolumn{4}{l}{Total number of evaluations: $120 \ 638$} & & &\\ \hline 
 \end{tabular}
@@
  input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
- $x_1$ & $0.5868$ &  $0.0005$ & $0.03$ & $0.6901$ & $0.0006$ & $0.02$ \\ \hline
- $x_2$ & $0.2608$ &  $0.0007$ & $0.03$ & $0.3562$ & $0.0003$ & $0$ \\ \hline
- $x_3$ & $0.0367$ &  $0.0015$ & $0.05$ & $0.0563$ & $0.0009$ & $0$ \\ \hline
- $x_4$ & $0.0058$ &  $0.0003$ & $0$ & $0.0092$ & $0.0003$ & $0$ \\ \hline
- $x_5$ & $5.10^{-5}$ & $< 10^{-4}$ & $0$ & $9.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
- $x_6$ & $5.10^{-5}$ & $< 10^{-4}$ & $0$  & $9.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
-\multicolumn{4}{l}{Total number of evaluations: $62 \ 703$} & & &\\ \hline 
+ $x_1$ & $0.6043$ &  $0.0005$ & $0$ & $0.7252$ & $0.0001$ & $0$ \\ \hline
+ $x_2$ & $0.2360$ &  $0.0006$ & $0$ & $0.3481$ & $0.0007$ & $0$ \\ \hline
+ $x_3$ & $0.0286$ &  $0.0013$ & $0$ & $0.0483$ & $0.0005$ & $0$ \\ \hline
+ $x_4$ & $0.0043$ &  $0.0003$ & $0$ & $0.0075$ & $0.0004$ & $0$ \\ \hline
+ $x_5$ & $4.10^{-5}$ & $< 10^{-4}$ & $0$ & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
+ $x_6$ & $4.10^{-5}$ & $< 10^{-4}$ & $0$  & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
+\multicolumn{4}{l}{Total number of evaluations: $120 \ 832$} & & &\\ \hline 
 \end{tabular}
 \label{res.gfunc.Ab}
-\end{table}
+\end{table}}
 
 The main observation is that both approaches give similar results both in terms of estimation errors, failure rates and total number of evaluations.
-The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ does not seem to bring much improvement.
-We propose to draw boxplots of the estimation errors to further investigate the results.
+The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ {\color{purple} (Lolo) does seem to bring an improvement.
+In particular, the failure rate for input $x_3$ is reduced to $0$.} We propose to draw boxplots of the estimation errors to further investigate the results.
 
@@
 The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
-\centering
-\includegraphics[width=0.45\textwidth]{Fig2.pdf}
+\vspace*{0.2cm}
+\centering
+\includegraphics[width=0.45\textwidth]{sobolg_box.eps}
 \label{boxplots.gfunc}
@@
 The discrepancy observed does not stand out in Table \ref{res.gfunc.Ab} due to its low magnitude ($10^{-4} \sim 10^{-5}$).
+
+{\color{purple} (Lolo) (REFAIRE BARPLOT MOINS HAUT) 
+\begin{figure}[!ht]
+\caption{Barplots of the $100$ values taken by the sum of the $c_j$. The distribution is bimodal with $60\%$ values equal to $0$.}
+\vspace*{0.2cm}
+\centering
+\includegraphics[width=0.45\textwidth]{sobolg_cj.eps}
+\label{cj.gfunc}
+\end{figure}
+Figure \ref{cj.gfunc} shows barplots of the $100$ values of the sum of the $c_j$.
+The distribution is bimodal with around $60\%$ of the values equal to $0$ and $40\%$ equal to $512$.
+As a result, the assumption is validated $60\%$ of the times and Variant A.b does not cost more (or slightly more) than Variant A.a.}
 \bigskip
@@
  input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
- $x_1$ & $0.5868$ &  $0.0011$ & $0.07$ \\ \hline
- $x_2$ & $0.2608$ &  $0.0013$ & $0.08$ \\ \hline
- $x_3$ & $0.0367$ &  $0.0018$ & $0.09$ \\ \hline
- $x_4$ & $0.0058$ &  $0.0013$ & $0.1$    \\ \hline
- $x_5$ & $5.10^{-5}$ & $0.0031$ & $0.04$  \\ \hline
- $x_6$ & $5.10^{-5}$ & $0.0036$ & $0.05$  \\ \hline \hline
-\multicolumn{4}{l}{Total number of evaluations: $32 \ 768$}\\ \hline 
+ $x_1$ & $0.6043$ &  $0.0005$ & $0$ \\ \hline
+ $x_2$ & $0.2360$ &  $0.0010$ & $0$ \\ \hline
+ $x_3$ & $0.0286$ &  $0.0018$ & $0.02$ \\ \hline
+ $x_4$ & $0.0043$ &  $0.0016$ & $0$    \\ \hline
+ $x_5$ & $4.10^{-5}$ & $0.0034$ & $0$  \\ \hline
+ $x_6$ & $4.10^{-5}$ & $0.0035$ & $0$  \\ \hline \hline
+\multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
 \end{tabular}
@@
 \end{table}
-The results show that the use of Variant $B$ leads to slightly higher estimation errors and higher failure rates than those obtained with Variant $A.a$ or Variant $A.b$.
+The results show that the use of Variant $B$ leads to slightly higher estimation errors than those obtained with Variant $A.a$ or Variant $A.b$.
 However, the total number of evaluations is {\color{purple}half as large}.
@@
 Jim\'enez Rugama, Ll.A., Hickernell, F.J.: Adaptive Multidimensional Integration Based on Rank-1 Lattices: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 407-422 (2016)
+\bibitem{Kuo} S. Joe, F. Y. Kuo, Constructing Sobol Sequences with Better Two-Dimensional Projections, \emph{SIAM J. Sci. Comput.} 30(8), 2008, pp. 2635--2654.
 \bibitem{Lemieuxbook}

### 2017-02-16 article_review/reviewer_letter.tex
Adding changes on manuscript
changes manuscript

@@
 \item[a.] page 1, column 1, lines 23-24: "through" instead of "trough"
+
+{\color{blue} The typo has been corrected.}
 \item[b.] page 2, column 2, equation (7): why use a biased estimator for $\sigma^2$ ?
+
+{\color{blue} The biased estimator has been replaced by the unbiased one.}
 \item[c.] page 4, column 2, equation (14): it is not clear how $\ell$ is chosen on the RHS, and whether or not the inequality holds for all $\ell \leq m$ or for some specific value of $\ell$ ?
@@
 \item[d.] page 4, column 2, line 42: is it not instead "...the error bound $\epsilon_{\hat{I}}$" (hat on subscript I?)?
+
+{\color{blue} The typo has been corrected.}
 \item[e.] page 5, column 2 line 55: not clear what you mean by "independent" in "two independent Sobol' sequences", especially if the designs are not randomized.
@@
 Please explain this more and state what properties you need for these sequences.
+
+{\color{blue} The paragraph has been reworked.
+The reviewer guessed right.
+We use a 2d-dimensional Sobol' sequence and assign its first d dimensions to the first design and the remaining ones to the second design.
+Then, each Sobol' sequence is scrambled independently; except in Variant B where the scrambling is the same to insure that the two designs are replicated designs of order one.
+
+As for the properties of the Sobol' sequences, the ones used in this paper are generated with the directional numbers found by S.
+Joe and F.
+Y.
+Kuo (2008).
+These directional numbers insure better two-dimensional projections of the resulting Sobol' sequences.}
+
 \item[f.] page 6, column 2, line 32: is the "iid" property valid across the indices i, i.e., the n vectors have to be independent?
@@
 Please clarify this so that the financial motivation for this problem is properly done.
+
+{\color{blue} The ``real case model'' has been replaced with a new one as suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections.} 
 \end{itemize}
@@
 
-{\color {blue} We acknowledge that Sobol' indices are theoretically invariant by adding a constant shift $c$ to the studied function.
-As underlined by the reviewer, the addition of a constant shift $c$ modifies the error bound for $\vI_3$ but also the errors bounds for the others integrands ($\vI_1$, $\vI_2$ and $\vI_4$).
+{\color {blue} We acknowledge that analytical formulas of Sobol' indices are invariant by adding a constant shift $c$ to the function $f$.
+As underlined by the reviewer, in our algorithm the addition of a constant shift $c$ modifies the error bound for $\vI_3$ but also the errors bounds for the others integrands ($\vI_1$, $\vI_2$ and $\vI_4$).
 More generally, our algorithm depends on the analytical expression of the Sobol' index estimator considered.
@@
 
+{\color{blue} We agree with the reviewer that the effective dimension of the higher dimensions integrand might be lower than its lower dimensions counterpart.
+However, evaluating the effective dimension of each integrands already requires a large number of model evaluations itself (\textit{c.f.} Wang.
+X and Fang.
+K.-T., 2003).
+
+Since evaluating the effective dimension is not in the scope of this paper, we propose the following.
+The original statement has been replaced with the assumption that the higher dimensions integrand possesses a higher effective dimension.
+Then, this assumption is tested on each example by plotting the repartition of the sum of the $c_j$ (equation (19)) over the $100$ repeats.
+The sign of the sum tells us if, in average, this assumption is validated across the Sobol' indices.}
+
 \item[6.] In Section $5.1.1$, the Sobol' g-function looks like a potentially misleading choice. It is completely smooth except when one of the inputs is $1/2$.
@@
 
-{\color{blue} The Sobol' g-function has been modified according to the reviewer remark. Corresponding tables and figures have changed.}
+{\color{blue} The Sobol' g-function has been modified according to the reviewer remark.
+There were no drastic changes observed.
+As a matter of fact, the failure rates have improved for all three approaches (Variant A.a, A.b and B).}
 
@@
 Section $5.2$ has been reworked to introduce this new test function.
-Our results are compared to formers obtained by screening approaches.}
+Our results are compared to formers obtained by screening approaches (Moon, H.
+(2010)).}
 

### 2017-02-16 article_review/Manuscript.tex
changes manuscript

@@
 In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices.
-Our aim is to show that the use of ``Correlation 2" in Variant $A$ may reduce the total number of model evaluations.
-This new estimator is,
+Our aim is to show that the use of ``Correlation 2" in Variant $A$ {\color{purple} (Lolo) improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.} This new estimator is,
 \begin{equation*}

### 2017-02-16 article_review/Manuscript.tex
Adding real case example

@@
 First, we assume that $\wcS_m(f)$ bounds $\hS_{\ell,m}(f)$ in some sense, in particular it bounds $\hS_{0,m}(f)$.
-This means that we can use $\wcS_m(f)$ as a good indicator for the error bound.
+This means that we can use $\wcS_m(f)$ as an indicator of the error bound.
 Then, we also need $S_{\ell}(f)$ to bound $\wcS_m(f)$ which helps transforming the infinite sum into a finite sum.
@@
 $\wcS_m(f)$, to also be small.
-By defining $r=m-\ell$, and assuming that $\homega(r)\wcomega(r)<1$ with $r\in\mathbb{N}$, one may see $r$ as a distance between $S_{\ell}(f)$ and $\wcS_m(f)$: larger values of $r$ will imply a smaller error bound but more dependence on smaller Walsh coefficients.
-Finally, we can write the error bound in terms of $\tS_{\ell,m}(f)$ instead of $\wcS_m(f)$ by using \eqref{discrite_true_relationship}.} In \cite[Sec.
-4.2]{HicJim} it is shown that for any $f\in\cc$,
+By defining $r=m-\ell$, and assuming that $\homega(r)\wcomega(r)<1$ with $r\in\mathbb{N}$, one may intuitively see $r$ as a distance between $S_{\ell}(f)$ and $\wcS_m(f)$ to tune: larger values of $r$ will imply a smaller error bound but more dependence on smaller Walsh coefficients.
+Finally, we can write the error bound in terms of $\tS_{\ell,m}(f)$ instead of $\wcS_m(f)$ by using \eqref{discrite_true_relationship}.} With this reasoning, in \cite[Sec.
+4.2]{HicJim} we showed that for any $f\in\cc$,
 \begin{equation}
@@
 \label{sec:5.2}
+\comment{As a real case example, we will study the wing weight function:
+\begin{align*}
+f(\vx)=0.036 x_1^{0.758} & x_2^{0.0035} \left(\frac{x_3}{\cos(x_4)^2}\right)^{0.6} x_5^{0.006} x_6^{0.04}\times \\
+ & \times\left(\frac{100 x_7}{\cos(x_4)}\right)^{-0.3} (x_8 x_9)^{0.49} + x_1 x_10
+\end{align*}
+\begin{tabular}{|l|l|}
+\hline
+$x_1\in[150, 200]$ & wing area (ft$^2$) \\
+$x_2\in[220, 300]$ & weight of fuel in the wing (lb) \\
+$x_3\in[6, 10]$ & aspect ratio \\
+$x_4\in[-10, 10]$ & quarter-chord sweep (degrees) \\
+$x_5\in[16, 45]$ & dynamic pressure at cruise (lb/ft$^2$) \\
+$x_6\in[0.5, 1]$ & taper ratio \\
+$x_7\in[0.08, 0.18]$ & aerofoil thickness to chord ratio \\
+$x_8\in[2.5, 6]$ & ultimate load factor \\
+$x_9\in[1700, 2500]$ & flight design gross weight (lb) \\
+$x_{10}\in[0.025, 0.08]$ & paint weight (lb/ft$^2$) \\
+\hline
+\end{tabular}
+}
 

### 2017-02-17 article_review/Manuscript.tex
changes figures + application

@@
 \centering
-\includegraphics[width=.5\textwidth]{Fig1.pdf}
+\includegraphics[width=.5\textwidth]{estimator_3d_small.eps}
 \label{fig:1}       % Give a unique label
@@
 {\color{purple}(Lolo) We assume that the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$.
-If this assumption holds, we expect to observe case $2)$ more often than case $1)$ and the sign of \eqref{cost.comparison} should be negative or equal to $0$.
+If this assumption holds, we expect to observe case $2)$ more often than case $1)$ and \eqref{cost.comparison} verifies the following inequality:
+\begin{equation}
+\sum \limits_{j \in \Gamma} c_j \leq 0 \ .
+\label{assumption}
+\end{equation}
 The validity of this assumption is tested on the numerical examples presented in Section \ref{sec:5}.
@@
 
-{\color{purple} (Lolo) To verify the validity of our  assumption saying that the sign of \eqref{cost.comparison} is negative, the sum of the $c_j$ is evaluated for each repetition and barplots of its values are drawn.}
+{\color{purple} (Lolo) To verify the validity of assumption \eqref{assumption}, the sum of the $c_j$ is evaluated for each repetition and barplots of its values are drawn.}
 
@@
 {\color{purple}(Lolo) (nouvelles tables et figures)
-\begin{table}[!ht]
+\begin{table}[t]
 \caption{Averaged estimation errors $\delta_{\underline{S}_u}$ , $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.a$.}
@@
 \end{table}
-\begin{table}[!ht]
+\begin{table}[t]
 \caption{Averaged estimation errors $\delta_{\underline{S}_u}$ , $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.b$.}
@@
 The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.
-\begin{figure}[!ht]
+\begin{figure}[t]
 \caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$.
@@
 
-{\color{purple} (Lolo) (REFAIRE BARPLOT MOINS HAUT) 
-\begin{figure}[!ht]
+{\color{purple} (Lolo)
+\begin{figure}[t]
 \caption{Barplots of the $100$ values taken by the sum of the $c_j$. The distribution is bimodal with $60\%$ values equal to $0$.}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{sobolg_cj.eps}
+\includegraphics[width=0.25\textwidth]{sobolg_cj.eps}
 \label{cj.gfunc}
@@
 The distribution is bimodal with around $60\%$ of the values equal to $0$ and $40\%$ equal to $512$.
-As a result, the assumption is validated $60\%$ of the times and Variant A.b does not cost more (or slightly more) than Variant A.a.}
+As a result, assumption \eqref{assumption} is validated $60\%$ of the times and Variant A.b does not cost more (or slightly more) than Variant A.a.}
 \bigskip
 
-Table \ref{res.gfunc.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$. 
-\begin{table}[!ht]
+\begin{table}[t]
 \caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
@@
 \end{table}
+Table \ref{res.gfunc.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.
 The results show that the use of Variant $B$ leads to slightly higher estimation errors than those obtained with Variant $A.a$ or Variant $A.b$.
@@
  input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ \\ \hline
- $x_1$ & $0.6529$ &  $0.0004$ & $0$ & $0.7396$ & $0.0003$ & $0.$ \\ \hline
- $x_2$ & $0.1791$ &  $0.0006$ & $0$ & $0.2659$ & $0.0004$ & $0$ \\ \hline
- $x_3$ & $0.0370$ &  $0.0058$ & $0.71$ & $0.0764$ & $0.0012$ & $0.02$ \\ \hline
- $x_4$ & $0.0133$ &  $0.0022$ & $0.12$ & $0.0343$ & $0.0020$ & $0.07$ \\ \hline
- $x_5$ & $0.0015$ &  $0.0024$ & $0.11$ & $0.0062$ & $0.0014$ & $0$ \\ \hline
- $x_6$ & $0.0015$ & $0.0021$ & $0.06$  & $0.0062$ & $0.0010$ & $0.03$ \\ \hline \hline
-\multicolumn{4}{l}{Total number of evaluations: $70 \ 129$} & & &\\ \hline 
+ $x_1$ & $0.6529$ &  $0.0005$ & $0$ & $0.7396$ & $0.0002$ & $0.$ \\ \hline
+ $x_2$ & $0.1791$ &  $0.0006$ & $0$ & $0.2659$ & $0.0005$ & $0$ \\ \hline
+ $x_3$ & $0.0370$ &  $0.0058$ & $0.78$ & $0.0764$ & $0.0015$ & $0.01$ \\ \hline
+ $x_4$ & $0.0133$ &  $0.0019$ & $0.09$ & $0.0343$ & $0.0018$ & $0.02$ \\ \hline
+ $x_5$ & $0.0015$ &  $0.0024$ & $0.13$ & $0.0062$ & $0.0016$ & $0.05$ \\ \hline
+ $x_6$ & $0.0015$ & $0.0023$ & $0.09$  & $0.0062$ & $0.0011$ & $0$ \\ \hline \hline
+\multicolumn{4}{l}{Total number of evaluations: $68 \ 404$} & & &\\ \hline 
 \end{tabular}
@@
  input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\overline{S}_u$ & $\delta_{\overline{S}_u}$ & $r_{\delta_{\overline{S}_u}}$ \\ \hline
- $x_1$ & $0.6529$ &  $0.0004$ & $0$ & $0.7396$ & $0.0003$ & $0$ \\ \hline
+ $x_1$ & $0.6529$ &  $0.0005$ & $0$ & $0.7396$ & $0.0002$ & $0$ \\ \hline
  $x_2$ & $0.1791$ &  $0.0006$ & $0$ & $0.2659$ & $0.0005$ & $0$ \\ \hline
- $x_3$ & $0.0370$ &  $0.0019$ & $0.04$ & $0.0764$ & $0.0013$ & $0.01$ \\ \hline
- $x_4$ & $0.0133$ &  $0.0016$ & $0.01$ & $0.0343$ & $0.0017$ & $0.02$ \\ \hline
- $x_5$ & $0.0015$ &  $0.0003$ & $0$ & $0.0062$ & $0.0015$ & $0.04$ \\ \hline
+ $x_3$ & $0.0370$ &  $0.0017$ & $0.02$ & $0.0764$ & $0.0015$ & $0.01$ \\ \hline
+ $x_4$ & $0.0133$ &  $0.0017$ & $0$ & $0.0343$ & $0.0018$ & $0.02$ \\ \hline
+ $x_5$ & $0.0015$ &  $0.0003$ & $0$ & $0.0062$ & $0.0016$ & $0.05$ \\ \hline
  $x_6$ & $0.0015$ &  $0.0004$ & $0$  & $0.0062$ & $0.0011$ & $0$ \\ \hline \hline
-\multicolumn{4}{l}{Total number of evaluations: $68 \ 045$} & & &\\ \hline 
+\multicolumn{4}{l}{Total number of evaluations: $66 \ 821$} & & &\\ \hline 
 \end{tabular}
@@
 Variant $A.b$ gives lower estimation errors and fewer failure rates than Variant $A.a$ on the four small first-indices $\underline{S}_3$, $\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''.
-The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $71\%$ against only $4\%$ for Variant $A.b$.
+The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $71\%$ against only $2\%$ for Variant $A.b$.
 Furthermore, Variant $A.b$ requires less evaluations than Variant $A.a$.
 The boxplots represented in Figure \ref{boxplots.bratley} emphasize the latter observations.
-\begin{figure}[!ht]
+\begin{figure}[t]
 \caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$.
 The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
-\centering
-\includegraphics[width=0.45\textwidth]{Fig3.pdf}
+\vspace*{0.2cm}
+\centering
+\includegraphics[width=0.45\textwidth]{bratley_box.eps}
 \label{boxplots.bratley}
@@
 
+{\color{purple} (Lolo)
+\begin{figure}[t]
+\caption{Barplots of the $100$ values taken by the sum of the $c_j$. $88\%$ of the values are lower or equal to zero. The maximal value equal $3072$.}
+\vspace*{0.2cm}
+\centering
+\includegraphics[width=0.45\textwidth]{bratley_cj.eps}
+\label{cj.bratley}
+\end{figure}
+
+Figure \ref{cj.bratley} shows barplots of the $100$ values of the sum of the $c_j$.
+$88\%$ of the values are lower of equal to zero, that is assumption \eqref{assumption} is validated most of the times.}
+\bigskip
+
 Table \ref{res.bratley.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.
+The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$.
+Failure rates are similar to those of Variant $A.b$.
+Since the total number of evaluations is close to the one of Variant $A.b$ at the exception of input $x_4$.
+As a conclusion, Variant $B$ does not bring much improvement for this example.
 \begin{table}[!ht]
@@
  input & $\underline{S}_u$ & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ \\ \hline
- $x_1$ & $0.6529$ &  $0.0003$ & $0$ \\ \hline
+ $x_1$ & $0.6529$ &  $0.0004$ & $0$ \\ \hline
  $x_2$ & $0.1791$ &  $0.0006$ & $0$ \\ \hline
- $x_3$ & $0.0370$ &  $0.0010$ & $0$ \\ \hline
- $x_4$ & $0.0133$ &  $0.0038$ & $0.25$    \\ \hline
- $x_5$ & $0.0015$ & $0.0024$ & $0$  \\ \hline
- $x_6$ & $0.0015$ & $0.0026$ & $0$  \\ \hline \hline
+ $x_3$ & $0.0370$ &  $0.0007$ & $0$ \\ \hline
+ $x_4$ & $0.0133$ &  $0.0037$ & $0.25$    \\ \hline
+ $x_5$ & $0.0015$ & $0.0023$ & $0$  \\ \hline
+ $x_6$ & $0.0015$ & $0.0025$ & $0$  \\ \hline \hline
 \multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
@@
 \end{table}
-
-The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$.
-Failure rates are similar to those of Variant $A.b$.
-Since the total number of evaluations is close to the one of Variant $A.b$, the conclusion is that Variant $B$ does not bring much improvement for this example.
 \bigskip
@@
 This highlights the efficiency of ``Correlation 2'' to estimate small first-order indices with quasi-Monte Carlo methods.
-Even if ``Correlation 2'' originally requires more model evaluations, this drawback is completely overridden when this estimator is included into a sequential procedure such as ours.
+Even if ``Correlation 2'' originally requires more model evaluations, this drawback is overridden when this estimator is included into a sequential procedure such as ours.
+
 For the case where we are only interested in estimating first-order indices, Variant $B$ should be the best choice as illustrated with the g-function.
 
-\subsection{Real case model}
+{\color{purple}
+\subsection{Application}
 \label{sec:5.2}
-\comment{As a real case example, we will study the wing weight function:
+
+(Lolo) As an application, we will study the wing weight function introduced by Forrester \textit{et al.} \cite{Forrester} and defined as follows:
 \begin{align*}
 f(\vx)=0.036 x_1^{0.758} & x_2^{0.0035} \left(\frac{x_3}{\cos(x_4)^2}\right)^{0.6} x_5^{0.006} x_6^{0.04}\times \\
- & \times\left(\frac{100 x_7}{\cos(x_4)}\right)^{-0.3} (x_8 x_9)^{0.49} + x_1 x_10
+ & \times\left(\frac{100 x_7}{\cos(x_4)}\right)^{-0.3} (x_8 x_9)^{0.49} + x_1 x_{10}
 \end{align*}
-\begin{tabular}{|l|l|}
+Table \ref{wing_inputs_table} gives the range of variation of each input and their physical representation.  All inputs are independent and uniformly distributed in their respective ranges.
+\begin{table}[!ht]
+\caption{Inputs and their ranges of variation. All inputs are independent and uniformly distributed in their respective ranges.}
+\centering
+\begin{tabular}{ccc}
 \hline
-$x_1\in[150, 200]$ & wing area (ft$^2$) \\
-$x_2\in[220, 300]$ & weight of fuel in the wing (lb) \\
-$x_3\in[6, 10]$ & aspect ratio \\
-$x_4\in[-10, 10]$ & quarter-chord sweep (degrees) \\
-$x_5\in[16, 45]$ & dynamic pressure at cruise (lb/ft$^2$) \\
-$x_6\in[0.5, 1]$ & taper ratio \\
-$x_7\in[0.08, 0.18]$ & aerofoil thickness to chord ratio \\
-$x_8\in[2.5, 6]$ & ultimate load factor \\
-$x_9\in[1700, 2500]$ & flight design gross weight (lb) \\
-$x_{10}\in[0.025, 0.08]$ & paint weight (lb/ft$^2$) \\
+ inputs & range & description \\ \hline
+$x_1$ & $[150, 200]$ & wing area (ft$^2$) \\
+$x_2$ & $[220, 300]$ & weight of fuel in the wing (lb) \\
+$x_3$ & $[6, 10]$ & aspect ratio \\
+$x_4$ & $[-10, 10]$ & quarter-chord sweep (degrees) \\
+$x_5$ & $[16, 45]$ & dynamic pressure at cruise (lb/ft$^2$) \\
+$x_6$ & $[0.5, 1]$ & taper ratio \\
+$x_7$ & $[0.08, 0.18]$ & aerofoil thickness to chord ratio \\
+$x_8$ & $[2.5, 6]$ & ultimate load factor \\
+$x_9$ & $[1700, 2500]$ & flight design gross weight (lb) \\
+$x_{10}$ & $[0.025, 0.08]$ & paint weight (lb/ft$^2$) \\
 \hline
 \end{tabular}
+\label{wing_inputs_table}
+\end{table}
+
+(TABLES OF RESULTS)
+\begin{table}[!ht]
+\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and total number of evaluations of Variant $A.a$.}
+\centering
+\begin{tabular}{ccc}
+\hline
+ input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
+ $x_1$ & $0.1245$ & $0.1280$  \\ \hline
+ $x_2$ & $0.0001$ & $< 10^{-4}$  \\ \hline
+ $x_3$ & $0.2203$ & $0.2261$  \\ \hline
+ $x_4$ & $0.0025$ & $0.0006$  \\ \hline
+ $x_5$ & $0.0007$ & $0.0001$  \\ \hline
+ $x_6$ & $0.0034$ & $0.0024$  \\ \hline 
+ $x_7$ & $0.1410$ & $0.1451$  \\ \hline
+ $x_8$ & $0.4116$ & $0.4197$  \\ \hline
+ $x_9$ & $0.0851$ & $0.0876$  \\ \hline
+ $x_{10}$ & $0.0031$ & $0.0042$  \\ \hline
+\hline
+\multicolumn{3}{l}{Total number of evaluations: $84 \ 792$} \\ \hline 
+\end{tabular}
+\label{res.wing.Aa}
+\end{table}
+\begin{table}[!ht]
+\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$.}
+ \centering
+\begin{tabular}{ccc}
+\hline
+  input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
+ $x_1$ & $0.1245$ & $0.1280$  \\ \hline
+ $x_2$ & $< 10^{-4}$ & $< 10^{-4}$  \\ \hline
+ $x_3$ & $0.2203$ & $0.2261$  \\ \hline
+ $x_4$ & $0.0006$ & $0.0006$  \\ \hline
+ $x_5$ & $0.0001$ & $0.0001$  \\ \hline
+ $x_6$ & $0.0023$ & $0.0024$  \\ \hline 
+ $x_7$ & $0.1410$ & $0.1451$  \\ \hline
+ $x_8$ & $0.4116$ & $0.4197$  \\ \hline
+ $x_9$ & $0.0850$ & $0.0876$  \\ \hline
+ $x_{10}$ & $0.0042$ & $0.0042$  \\ \hline
+\hline
+\multicolumn{3}{l}{Total number of evaluations: $88 \ 269$} \\ \hline 
+\end{tabular}
+\label{res.wing.Ab}
+\end{table}
+\begin{table}[!ht]
+\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$.}
+ \centering
+\begin{tabular}{cc}
+\hline
+ input & $\widehat{\underline{S}}_u$ \\ \hline
+ $x_1$ & $0.1245$ \\ \hline
+ $x_2$ & $0.0042$ \\ \hline
+ $x_3$ & $0.2201$ \\ \hline
+ $x_4$ & $0.0039$ \\ \hline
+ $x_5$ & $0.0035$ \\ \hline
+ $x_6$ & $0.0045$ \\ \hline 
+ $x_7$ & $0.1410$ \\ \hline
+ $x_8$ & $0.4116$ \\ \hline
+ $x_9$ & $0.0850$ \\ \hline
+ $x_{10}$ & $0.0042$ \\ \hline
+ \hline
+\multicolumn{2}{l}{Total number of evaluations: $65 \ 536$} \\ \hline 
+\end{tabular}
+\label{res.wing.B}
+\end{table}
+(FIGURES)
+\begin{figure}[!ht]
+\caption{Boxplots of first-order indices $\underline{S}_u$ for inputs $x_2,x_4,x_5,x_6,x_{10}$ obtained with both Variant $A.a$ and Variant $A.b$.}
+\vspace*{0.2cm}
+\centering
+\includegraphics[width=0.45\textwidth]{wingweight_box.eps}
+\label{boxplots.wing}
+\end{figure}
+\begin{figure}[t]
+\caption{Barplots of the $100$ values taken by the sum of the $c_j$. All values are higher than zero.}
+\vspace*{0.2cm}
+\centering
+\includegraphics[width=0.45\textwidth]{wingweight_cj.eps}
+\label{cj.wing}
+\end{figure}
+
+Comments: Variant A.b is more expansive but guarantee that first-order indices are lower or equal to total-effect indices. At the opposite, Variant A.a fails to guarantee this property.
+
+Variant B requires less evaluations but estimates of small first-order indices are less accurate.
+(TO COMPLETE)
+
+(ALSO TRY LEVEL E MODEL ?)
 }
 
-As a real case example, we will study the payoff function of an arithmetic mean Asian call option.
+%\comment{As a real case example, we will study the wing weight function:
+%\begin{align*}
+%f(\vx)=0.036 x_1^{0.758} & x_2^{0.0035} \left(\frac{x_3}{\cos(x_4)^2}\right)^{0.6} x_5^{0.006} x_6^{0.04}\times \\
+% & \times\left(\frac{100 x_7}{\cos(x_4)}\right)^{-0.3} (x_8 x_9)^{0.49} + x_1 x_10
+%\end{align*}
+%\begin{tabular}{|l|l|}
+%\hline
+%$x_1\in[150, 200]$ & wing area (ft$^2$) \\
+%$x_2\in[220, 300]$ & weight of fuel in the wing (lb) \\
+%$x_3\in[6, 10]$ & aspect ratio \\
+%$x_4\in[-10, 10]$ & quarter-chord sweep (degrees) \\
+%$x_5\in[16, 45]$ & dynamic pressure at cruise (lb/ft$^2$) \\
+%$x_6\in[0.5, 1]$ & taper ratio \\
+%$x_7\in[0.08, 0.18]$ & aerofoil thickness to chord ratio \\
+%$x_8\in[2.5, 6]$ & ultimate load factor \\
+%$x_9\in[1700, 2500]$ & flight design gross weight (lb) \\
+%$x_{10}\in[0.025, 0.08]$ & paint weight (lb/ft$^2$) \\
+%\hline
+%\end{tabular}
+
+%\subsection{Real case model}
+%As a real case example, we will study the payoff function of an arithmetic mean Asian call option.
 For a discretized Brownian motion $\vect{B}=(B_{t_1}, B_{t_2},\dots, B_{t_d})$ at times $t_i=T\times i/d$, the payoff of the option is:
-
-\[
-f_{\rm payoff}(\vect{B}) = \e^{-\rho T}\max\left(\frac{1}{d}\sum_{i=1}^d S_0\e^{(\rho-\sigma^2/2)t_i+\sigma B_{t_i}}-K, 0\right)
-\]
-where $T$ is the maturity of the option, $S_0$ is the initial stock price, $\sigma$ the volatility of the stock, $\rho$ the interest rate, and $K$ the strike price.
-
-The discretized Brownian motion $\vect{B}$ follows a multivariate normal distribution with mean $\vzero$ and covariance matrix $\mathsf{\Sigma}$, with $\mathsf{\Sigma}_{ij}=\min(t_i,t_j)$.
+%
+%\[
+%f_{\rm payoff}(\vect{B}) = \e^{-\rho T}\max\left(\frac{1}{d}\sum_{i=1}^d S_0\e^{(\rho-\sigma^2/2)t_i+\sigma B_{t_i}}-K, 0\right)
+%\]
+%where $T$ is the maturity of the option, $S_0$ is the initial stock price, $\sigma$ the volatility of the stock, $\rho$ the interest rate, and $K$ the strike price.
+%
+%The discretized Brownian motion $\vect{B}$ follows a multivariate normal distribution with mean $\vzero$ and covariance matrix $\mathsf{\Sigma}$, with $\mathsf{\Sigma}_{ij}=\min(t_i,t_j)$.
 If $\vect{Y}\sim N(\vzero,I_d)$, then for any matrix $M$, $M\vect{Y}\sim N(\vzero,\mathsf{\Sigma})$ where $\mathsf{\Sigma}=MM^t$.
@@
 We will compare the case with either the Cholesky decomposition or the PCA construction.
-
-We propose to analyze the results with averaged Sobol' estimates and averaged total number of evaluations over $100$ repetitions.
+%
+%We propose to analyze the results with averaged Sobol' estimates and averaged total number of evaluations over $100$ repetitions.
 The tolerance $\varepsilon$ and parameters $\ell^*$, $r$ and $\mathfrak{C}(m)$ are set as previously.
-
-Tables \ref{res.AsianChol.Aa}, \ref{res.AsianChol.Ab}, and \ref{res.AsianChol.B} show the results when $M$ corresponds to the Cholesky decomposition of $\mathsf{\Sigma}$. 
-\begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and total number of evaluations of Variant $A.a$ with Cholesky decomposition.}
-%\centering
-%\begin{tabular}{ccccc}
-%\hline
-% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
-% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
-% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
-% $x_3$ & $0.0820$ & $37356$ & $0.3150$ & $65536$ \\ \hline
-% $x_4$ & $0.0408$ & $16742$ & $0.1950$ & $33096$ \\ \hline
-% $x_5$ & $0.0142$ & $5980$ & $0.0944$ & $16384$ \\ \hline
-% $x_6$ & $0.0048$ & $1106$ & $0.0257$ & $1654$ \\ \hline \hline
-\centering
-\begin{tabular}{ccc}
-\hline
- input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
- $x_1$ & $0.2120$ & $0.5650$  \\ \hline
- $x_2$ & $0.1370$ & $0.4420$  \\ \hline
- $x_3$ & $0.0820$ & $0.3150$  \\ \hline
- $x_4$ & $0.0408$ & $0.1950$  \\ \hline
- $x_5$ & $0.0142$ & $0.0944$  \\ \hline
- $x_6$ & $0.0048$ & $0.0257$  \\ \hline \hline
-\multicolumn{3}{l}{Total number of evaluations: $648 \ 821$} \\ \hline 
-\end{tabular}
-\label{res.AsianChol.Aa}
-\end{table}
-\begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with Cholesky decomposition.}
-%\centering
-%\begin{tabular}{ccccc}
-%\hline
-% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
-% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
-% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
-% $x_3$ & $0.0822$ & $34406$ & $0.3150$ & $65536$ \\ \hline
-% $x_4$ & $0.0434$ & $13107$ & $0.1950$ & $33423$ \\ \hline
-% $x_5$ & $0.0169$ & $2371$ & $0.0944$ & $16384$ \\ \hline
-% $x_6$ & $0.0049$ & $532$ & $0.0259$ & $1577$ \\ \hline \hline
- \centering
-\begin{tabular}{ccc}
-\hline
- input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$  \\ \hline
- $x_1$ & $0.2120$ & $0.5650$  \\ \hline
- $x_2$ & $0.1370$ & $0.4420$ \\ \hline
- $x_3$ & $0.0822$ & $0.3150$  \\ \hline
- $x_4$ & $0.0434$ & $0.1950$  \\ \hline
- $x_5$ & $0.0169$ & $0.0944$  \\ \hline
- $x_6$ & $0.0049$ & $0.0259$  \\ \hline \hline
-\multicolumn{3}{l}{Total number of evaluations: $699 \ 487$}\\ \hline 
-\end{tabular}
-\label{res.AsianChol.Ab}
-\end{table}
-\begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with Cholesky decomposition.}
+%
+%Tables \ref{res.AsianChol.Aa}, \ref{res.AsianChol.Ab}, and \ref{res.AsianChol.B} show the results when $M$ corresponds to the Cholesky decomposition of $\mathsf{\Sigma}$. 
+%\begin{table}[!ht]
+%\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and total number of evaluations of Variant $A.a$ with Cholesky decomposition.}
+%%\centering
+%%\begin{tabular}{ccccc}
+%%\hline
+%% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
+%% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
+%% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
+%% $x_3$ & $0.0820$ & $37356$ & $0.3150$ & $65536$ \\ \hline
+%% $x_4$ & $0.0408$ & $16742$ & $0.1950$ & $33096$ \\ \hline
+%% $x_5$ & $0.0142$ & $5980$ & $0.0944$ & $16384$ \\ \hline
+%% $x_6$ & $0.0048$ & $1106$ & $0.0257$ & $1654$ \\ \hline \hline
 %\centering
@@
 %\hline
-% input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
-% $x_1$ & $0.2120$ & $131072$ \\ \hline
-% $x_2$ & $0.1350$ & $129766$ \\ \hline
-% $x_3$ & $0.0774$ & $62290$ \\ \hline
-% $x_4$ & $0.0338$ & $49961$ \\ \hline
-% $x_5$ & $0.0149$ & $48845$ \\ \hline
-% $x_6$ & $0.0028$ & $17905$ \\ \hline \hline
- \centering
-\begin{tabular}{cc}
-\hline
- input & $\widehat{\underline{S}}_u$ \\ \hline
- $x_1$ & $0.2120$ \\ \hline
- $x_2$ & $0.1350$ \\ \hline
- $x_3$ & $0.0774$ \\ \hline
- $x_4$ & $0.0338$ \\ \hline
- $x_5$ & $0.0149$ \\ \hline
- $x_6$ & $0.0028$ \\ \hline \hline
-\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
-\end{tabular}
-\label{res.AsianChol.B}
-\end{table}
-
-It turns out that Variant $A.b$ does not perform better than Variant $A.a$.
+% input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
+% $x_1$ & $0.2120$ & $0.5650$  \\ \hline
+% $x_2$ & $0.1370$ & $0.4420$  \\ \hline
+% $x_3$ & $0.0820$ & $0.3150$  \\ \hline
+% $x_4$ & $0.0408$ & $0.1950$  \\ \hline
+% $x_5$ & $0.0142$ & $0.0944$  \\ \hline
+% $x_6$ & $0.0048$ & $0.0257$  \\ \hline \hline
+%\multicolumn{3}{l}{Total number of evaluations: $648 \ 821$} \\ \hline 
+%\end{tabular}
+%\label{res.AsianChol.Aa}
+%\end{table}
+%\begin{table}[!ht]
+%\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with Cholesky decomposition.}
+%%\centering
+%%\begin{tabular}{ccccc}
+%%\hline
+%% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
+%% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
+%% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
+%% $x_3$ & $0.0822$ & $34406$ & $0.3150$ & $65536$ \\ \hline
+%% $x_4$ & $0.0434$ & $13107$ & $0.1950$ & $33423$ \\ \hline
+%% $x_5$ & $0.0169$ & $2371$ & $0.0944$ & $16384$ \\ \hline
+%% $x_6$ & $0.0049$ & $532$ & $0.0259$ & $1577$ \\ \hline \hline
+% \centering
+%\begin{tabular}{ccc}
+%\hline
+% input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$  \\ \hline
+% $x_1$ & $0.2120$ & $0.5650$  \\ \hline
+% $x_2$ & $0.1370$ & $0.4420$ \\ \hline
+% $x_3$ & $0.0822$ & $0.3150$  \\ \hline
+% $x_4$ & $0.0434$ & $0.1950$  \\ \hline
+% $x_5$ & $0.0169$ & $0.0944$  \\ \hline
+% $x_6$ & $0.0049$ & $0.0259$  \\ \hline \hline
+%\multicolumn{3}{l}{Total number of evaluations: $699 \ 487$}\\ \hline 
+%\end{tabular}
+%\label{res.AsianChol.Ab}
+%\end{table}
+%\begin{table}[!ht]
+%\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with Cholesky decomposition.}
+%%\centering
+%%\begin{tabular}{ccc}
+%%\hline
+%% input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
+%% $x_1$ & $0.2120$ & $131072$ \\ \hline
+%% $x_2$ & $0.1350$ & $129766$ \\ \hline
+%% $x_3$ & $0.0774$ & $62290$ \\ \hline
+%% $x_4$ & $0.0338$ & $49961$ \\ \hline
+%% $x_5$ & $0.0149$ & $48845$ \\ \hline
+%% $x_6$ & $0.0028$ & $17905$ \\ \hline \hline
+% \centering
+%\begin{tabular}{cc}
+%\hline
+% input & $\widehat{\underline{S}}_u$ \\ \hline
+% $x_1$ & $0.2120$ \\ \hline
+% $x_2$ & $0.1350$ \\ \hline
+% $x_3$ & $0.0774$ \\ \hline
+% $x_4$ & $0.0338$ \\ \hline
+% $x_5$ & $0.0149$ \\ \hline
+% $x_6$ & $0.0028$ \\ \hline \hline
+%\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
+%\end{tabular}
+%\label{res.AsianChol.B}
+%\end{table}
+%
+%It turns out that Variant $A.b$ does not perform better than Variant $A.a$.
 Averaged Sobol' estimates are similar but the average total number of model evaluations is slightly worse.
@@
 Its discrepancy is higher than $\epsilon$ when comparing to the other two variants.
-
-Tables \ref{res.AsianPCA.Aa}, \ref{res.AsianPCA.Ab}, and \ref{res.AsianPCA.B} show the results when $M$ corresponds to the PCA decomposition of $\mathsf{\Sigma}$.
-
-\begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.a$ with PCA decomposition.}
-\centering
-\begin{tabular}{ccccc}
-\hline
- input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
- $x_1$ & $0.9800$ & $0.9960$  \\ \hline
- $x_2$ & $0.0037$ & $0.0172$  \\ \hline
- $x_3$ & $0.0016$ & $0.0023$  \\ \hline
- $x_4$ & $0.0014$ & $0.0005$  \\ \hline
- $x_5$ & $0.0005$ & $0.0001$  \\ \hline
- $x_6$ & $0.0002$ & $0.0000$ \\ \hline
- \multicolumn{3}{l}{Total number of evaluations: $396 \ 221$}
- \\ \hline
-\end{tabular}
-\label{res.AsianPCA.Aa}
-\end{table}
-
-\begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with PCA decomposition.}
+%
+%
+%Tables \ref{res.AsianPCA.Aa}, \ref{res.AsianPCA.Ab}, and \ref{res.AsianPCA.B} show the results when $M$ corresponds to the PCA decomposition of $\mathsf{\Sigma}$. 
+%
+%\begin{table}[!ht]
+%\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.a$ with PCA decomposition.}
 %\centering
@@
 %\hline
-% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
-% $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
-% $x_2$ & $0.0034$ & $512$ & $0.0172$ & $824$ \\ \hline
-% $x_3$ & $0.0004$ & $512$ & $0.0023$ & $512$ \\ \hline
-% $x_4$ & $0.0001$ & $512$ & $0.0005$ & $512$ \\ \hline
-% $x_5$ & $0.0000$ & $512$ & $0.0001$ & $512$ \\ \hline
-% $x_6$ & $0.0000$ & $512$ & $0.0000$ & $512$ \\ \hline \hline
- \centering
-\begin{tabular}{ccc}
-\hline
- input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
- $x_1$ & $0.9800$ &  $0.9960$  \\ \hline
- $x_2$ & $0.0034$ &  $0.0172$  \\ \hline
- $x_3$ & $0.0004$ &  $0.0023$  \\ \hline
- $x_4$ & $0.0001$ &  $0.0005$  \\ \hline
- $x_5$ & $0.0000$ &  $0.0001$  \\ \hline
- $x_6$ & $0.0000$ &  $0.0000$  \\ \hline \hline
-\multicolumn{3}{l}{Total number of evaluations: $398 \ 648$} \\ \hline 
-\end{tabular}
-\label{res.AsianPCA.Ab}
-\end{table}
-
-\begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with PCA decomposition.}
-\centering
-\begin{tabular}{ccc}
-\hline
- input & $\widehat{\underline{S}}_u$  \\ \hline
- $x_1$ & $0.9800$ \\ \hline
- $x_2$ & $0.0037$ \\ \hline
- $x_3$ & $0.0028$ \\ \hline
- $x_4$ & $0.0029$ \\ \hline
- $x_5$ & $0.0017$ \\ \hline
- $x_6$ & $0.0029$ \\ \hline \hline
-\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
-\end{tabular}
-\label{res.AsianPCA.B}
-\end{table}
-Variant $A.a$ performs as well as Variant $A.b$ in terms of average total number of evaluations.
+% input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
+% $x_1$ & $0.9800$ & $0.9960$  \\ \hline
+% $x_2$ & $0.0037$ & $0.0172$  \\ \hline
+% $x_3$ & $0.0016$ & $0.0023$  \\ \hline
+% $x_4$ & $0.0014$ & $0.0005$  \\ \hline
+% $x_5$ & $0.0005$ & $0.0001$  \\ \hline
+% $x_6$ & $0.0002$ & $0.0000$ \\ \hline
+% \multicolumn{3}{l}{Total number of evaluations: $396 \ 221$}
+% \\ \hline
+%\end{tabular}
+%\label{res.AsianPCA.Aa}
+%\end{table}
+%
+%\begin{table}[!ht]
+%\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with PCA decomposition.}
+%%\centering
+%%\begin{tabular}{ccccc}
+%%\hline
+%% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
+%% $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
+%% $x_2$ & $0.0034$ & $512$ & $0.0172$ & $824$ \\ \hline
+%% $x_3$ & $0.0004$ & $512$ & $0.0023$ & $512$ \\ \hline
+%% $x_4$ & $0.0001$ & $512$ & $0.0005$ & $512$ \\ \hline
+%% $x_5$ & $0.0000$ & $512$ & $0.0001$ & $512$ \\ \hline
+%% $x_6$ & $0.0000$ & $512$ & $0.0000$ & $512$ \\ \hline \hline
+% \centering
+%\begin{tabular}{ccc}
+%\hline
+% input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
+% $x_1$ & $0.9800$ &  $0.9960$  \\ \hline
+% $x_2$ & $0.0034$ &  $0.0172$  \\ \hline
+% $x_3$ & $0.0004$ &  $0.0023$  \\ \hline
+% $x_4$ & $0.0001$ &  $0.0005$  \\ \hline
+% $x_5$ & $0.0000$ &  $0.0001$  \\ \hline
+% $x_6$ & $0.0000$ &  $0.0000$  \\ \hline \hline
+%\multicolumn{3}{l}{Total number of evaluations: $398 \ 648$} \\ \hline 
+%\end{tabular}
+%\label{res.AsianPCA.Ab}
+%\end{table}
+%
+%\begin{table}[!ht]
+%\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with PCA decomposition.}
+%\centering
+%\begin{tabular}{ccc}
+%\hline
+% input & $\widehat{\underline{S}}_u$  \\ \hline
+% $x_1$ & $0.9800$ \\ \hline
+% $x_2$ & $0.0037$ \\ \hline
+% $x_3$ & $0.0028$ \\ \hline
+% $x_4$ & $0.0029$ \\ \hline
+% $x_5$ & $0.0017$ \\ \hline
+% $x_6$ & $0.0029$ \\ \hline \hline
+%\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
+%\end{tabular}
+%\label{res.AsianPCA.B}
+%\end{table}
+%Variant $A.a$ performs as well as Variant $A.b$ in terms of average total number of evaluations.
 However, Variant $A.a$ is most probably giving worse estimates for the small first-order indices.
@@
 Once again, variant $B$ shows an improvement on the total number of evaluations with the drawback of slightly overestimating the small first-order indices.
-
-Overall, each variant captures well how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.
+%
+%Overall, each variant captures well how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.
 
@@
 Bratley, P., Fox, B.L., Niederreiter, H.: Implementation and tests of low-discrepancy sequences, ACM Trans. Model. Comput. Simul. \textbf{2}(3), 195-213 (1992)
+\bibitem{Forrester}
+Forrester, A., S\'obester, A., Keane, A.: Engineering Design via Surrogate Modelling, Chichester: Wiley (2008)
 \bibitem{Gilquin.rec}
@@
 \bibitem{GJAHMP}
-Gilquin, L., Jim\'enez Rugama, Ll.A., Arnaud, E., Hickernell, F.J., Monod, H., Prieur, C.: Iterative construction of replicated designs based on Sobol' sequences, preprint available at \url{https://hal.inria.fr/hal-01349444} (2016)
+Gilquin, L., Jim\'enez Rugama, Ll.A., Arnaud, E., Hickernell, F.J., Monod, H., Prieur, C.: Iterative construction of replicated designs based on Sobol' sequences, C. R. Math., vol. 355, 10-14 (2017)
 \bibitem{HicJim}

### 2017-02-18 article_review/Manuscript.tex
More reviewer changes

@@
 An inherent practical problem of this estimation is how to quantify the number of model evaluations needed to ensure that estimates satisfy a desired error tolerance.
-This paper addresses this challenge by proposing a reliable error bound for first-order and total effect Sobol' indices.
+This article addresses this challenge by proposing a reliable error bound for first-order and total effect Sobol' indices.
 Starting from the integral formula of the indices, the error bound is defined in terms of the discrete Walsh coefficients of the different integrands.
@@
 
-The uncertainty on $\vx$ is modeled by a uniform random vector, namely $\vx \iid \mathcal{U}(\cube)$. The Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$ is:
+The uncertainty on $\vx$ is modeled by a uniform random vector, namely $\vx \sim \mathcal{U}(\cube)$. The Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$ is:
 \begin{equation}
@@
 \end{align*}
-\comment{Among these sums, one should notice that $\hS_{0,m}(f)$ corresponds to the error bound appearing in \eqref{mapped_error_bound}.
+\comment{The sums $S_m(f)$, $\hS_{\ell,m}(f)$, $\wcS_m(f)$, and $\tS_{\ell,m}(f)$ are different from the normalized Sobol' indices $\underline{S}_u$ and $\ov{$S$}_u$.
+Unfortunately, the notation in articles \cite{HicJim,HicJimLi,JimHic} uses these symbols for the sums which should not be confused with the normalized Sobol' indices.
+
+Among these sums, one should notice that $\hS_{0,m}(f)$ corresponds to the error bound appearing in \eqref{mapped_error_bound}.
 Thus, $\wcS_m(f)$ is an infinite sum of Walsh coefficients that contain the error bound coefficients.
@@
 $\wcS_m(f)$, to also be small.
-By defining $r=m-\ell$, and assuming that $\homega(r)\wcomega(r)<1$ with $r\in\mathbb{N}$, one may intuitively see $r$ as a distance between $S_{\ell}(f)$ and $\wcS_m(f)$ to tune: larger values of $r$ will imply a smaller error bound but more dependence on smaller Walsh coefficients.
+By defining $r=m-\ell$ with $\homega(r)\wcomega(r)<1$ and $r\in\mathbb{N}$, one may intuitively see $r$ as the distance between $S_{\ell}(f)$ and $\wcS_m(f)$.
+One only needs to choose the appropriate $r$: larger values of $r$ will imply a smaller error bound but more dependence on smaller Walsh coefficients.
 Finally, we can write the error bound in terms of $\tS_{\ell,m}(f)$ instead of $\wcS_m(f)$ by using \eqref{discrite_true_relationship}.} With this reasoning, in \cite[Sec.
@@
 \absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)}
-\le \tS_{\ell,m}(f)\underbrace{\frac{\homega(m) \wcomega(r)}{1 - \homega(r) \wcomega(r)}}_{\mathfrak{C}(m)}=\epsilon_{\widehat{I}}, \label{errbd}
+\le \tS_{m-r,m}(f)\underbrace{\frac{\homega(m) \wcomega(r)}{1 - \homega(r) \wcomega(r)}}_{\mathfrak{C}(m)}=\epsilon_{\widehat{I}}, \label{errbd}
 \end{equation}
@@
 Under the assumption that each integrand in $\underline{S}_u$ and $\overline{S}_u$ lies inside $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\widehat{\underline{S}}_u}, \widehat{\underline{S}}_u + \varepsilon_{\widehat{\underline{S}}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\widehat{\overline{S}}_u}, \widehat{\overline{S}}_u + \varepsilon_{\widehat{\overline{S}}_u} \right] .\]
-For the rest of the paper, we will consider $\widehat{\underline{S}}_u$ and $\widehat{\overline{S}}_u$   as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).
+\comment{Because we do not assume the knowledge of the Walsh coefficients, it is hard to verify whether all the integrands lie in $\cc$.
+Nevertheless, some data-based necessary conditions are provided in \cite{HicJimLi}.
+These conditions can be used to automatically enlarge the cone according to each integrand.} For the rest of the article, we will consider $\widehat{\underline{S}}_u$ and $\widehat{\overline{S}}_u$ as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).
 
@@
 These directional numbers insure better two-dimensional projections of the resulting Sobol' sequence.
-In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling scheme \cite{HonHic00a,Owe95}.}
+In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling scheme \cite{HonHic00a,Owe95}.......}
 
@@
 \begin{equation*}
-\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)),
+\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)).
 \end{equation*}
-where $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$. It requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.
+\comment{As proposed by Owen in \cite{Owen}, the sample points are $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$.
+For our algorithm, we extend Owen's estimator by replacing the uniform points with a Sobol' sequence in dimension $3d$.
+In either case, this estimator requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.}
 \bigskip
@@
 
-The failure rates $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$ of each estimate are evaluated over the $100$ repetitions.
+\comment{For the following examples we do not know the true Walsh coefficients of the integrands.
+Therefore, we cannot say whether they lie inside the cone defined.
+}The failure rates $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$ of each estimate are evaluated over the $100$ repetitions.
 These rates are the proportion of the repetitions in which the true estimation errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$.
@@
 
-The two classical test functions considered in this article are {\color{purple} (Lolo) a non QMC friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
+The two classical test functions considered in this article are {\color{purple} (Lolo) a non qMC friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
 The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.} function) and multiplicative (g-function).
@@
 {\color{purple} (Lolo)
-The non QMC friendly version of the g-function is defined as follows:
+The non qMC friendly version of the g-function is defined as follows:
 \begin{equation*}
@@
 Overall, the variant combining Saltelli's strategy and ``Correlation 2'' gave the best results, with low failure rates across all indices.
+\comment{Add that we can consider relative errors and reference ...}
 
@@
 \bibitem{Bratley}
-Bratley, P., Fox, B.L., Niederreiter, H.: Implementation and tests of low-discrepancy sequences, ACM Trans. Model. Comput. Simul. \textbf{2}(3), 195-213 (1992)
+Bratley, P., Fox, B. L., Niederreiter, H.: Implementation and tests of low-discrepancy sequences, ACM Trans. Model. Comput. Simul. \textbf{2}(3), 195-213 (1992)
 \bibitem{Forrester}
-Forrester, A., S\'obester, A., Keane, A.: Engineering Design via Surrogate Modelling, Chichester: Wiley (2008)
+Forrester, A., S\'obester, A., Keane, A.: Engineering design via surrogate modelling, Chichester: Wiley (2008)
 \bibitem{Gilquin.rec}
@@
 \bibitem{GJAHMP}
-Gilquin, L., Jim\'enez Rugama, Ll.A., Arnaud, E., Hickernell, F.J., Monod, H., Prieur, C.: Iterative construction of replicated designs based on Sobol' sequences, C. R. Math., vol. 355, 10-14 (2017)
+Gilquin, L., Jim\'enez Rugama, Ll. A., Arnaud, E., Hickernell, F. J., Monod, H., Prieur, C.: Iterative construction of replicated designs based on Sobol' sequences, C. R. Math., vol. 355, 10-14 (2017)
 \bibitem{HicJim}
-Hickernell, F.J., Jim\'enez Rugama, Ll.A.: Reliable Adaptative Cubature Using Digital Sequences: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 367-383 (2016)
+Hickernell, F. J., Jim\'enez Rugama, Ll. A.: Reliable adaptive cubature using digital sequences: Monte Carlo and Quasi-Monte Carlo Methods 2014, vol. 163, 367-383 (2016)
+\bibitem{HicJimLi}
+Hickernell, F. J., Jim\'enez Rugama, Ll. A., Li, D.: Adaptive quasi-Monte Carlo methods for cubature, preprint available at \url{https://arxiv.org/pdf/1702.01491.pdf}, (2017).
 \bibitem{HonHic00a}
-H.S. Hong, F.J. Hickernell.: Algorithm 823: Implementing scrambled digital nets, ACM Trans. Math. Software, vol. 29, 95-109, (2003)
+Hong, H. S., Hickernell, F. J.: Algorithm 823: Implementing scrambled digital nets, ACM Trans. Math. Software, vol. 29, 95-109, (2003)
 \bibitem{Hoeffding}
-Hoeffding, W.F.: A class of statistics with asymptotically normal distribution, Ann. Math. Stat. \textbf{19}(3), 293-325 (1948)
+Hoeffding, W. F.: A class of statistics with asymptotically normal distribution, Ann. Math. Stat. \textbf{19}(3), 293-325 (1948)
 \bibitem{Janon}
@@
 \bibitem{JimHic}
-Jim\'enez Rugama, Ll.A., Hickernell, F.J.: Adaptive Multidimensional Integration Based on Rank-1 Lattices: Monte Carlo and Quasi-Monte Carlo Methods, vol. 163, 407-422 (2016)
-\bibitem{Kuo} S. Joe, F. Y. Kuo, Constructing Sobol Sequences with Better Two-Dimensional Projections, \emph{SIAM J. Sci. Comput.} 30(8), 2008, pp. 2635--2654.
+Jim\'enez Rugama, Ll. A., Hickernell, F. J.: Adaptive multidimensional integration based on rank-1 lattices: Monte Carlo and Quasi-Monte Carlo Methods 2014, vol. 163, 407-422 (2016)
+\bibitem{Kuo} Joe, S., Kuo, F. Y., Constructing Sobol sequences with better two-dimensional projections, \emph{SIAM J. Sci. Comput.} 30(8), 2008, pp. 2635--2654.
 \bibitem{Lemieuxbook}
-Lemieux,C.: Monte Carlo and Quasi-Monte Carlo Sampling, Springer, New-York (2009)
+Lemieux, C.: Monte Carlo and quasi-Monte Carlo sampling, Springer, New-York (2009)
 \bibitem{Mara}
-Mara, T.A., Rakoto Joseph, 0.: Comparison of some efficient methods to evaluate the main effect of computer model factors, J. Statist. Comput. Simulation \textbf{78}(2), 167-178 (2008)
+Mara, T. A., Rakoto Joseph, O.: Comparison of some efficient methods to evaluate the main effect of computer model factors, J. Statist. Comput. Simulation \textbf{78}(2), 167-178 (2008)
 \bibitem{McKay}
-McKay, M.D.: Evaluating prediction uncertainty, Los Alamos National Laboratory Report NUREG/CR- 6311, LA-12915-MS. (1995)
+McKay, M. D.: Evaluating prediction uncertainty, Los Alamos National Laboratory Report NUREG/CR- 6311, LA-12915-MS. (1995)
 \bibitem{Niederreiter} 
-Niederreiter, H.: Random Number Generation and Quasi-Monte Carlo Methods: CBMS-NSF Regional Conference Series in Applied Math., vol. 63, SIAM, Philadelphia (1992)
+Niederreiter, H.: Random number generation and quasi-Monte carlo methods: CBMS-NSF Regional Conference Series in Applied Math., vol. 63, SIAM, Philadelphia (1992)
 \bibitem{Owe95}
-A.B. Owen.: Randomly permuted $(t,m,s)$-nets and $(t,s)$-sequences: Monte Carlo and Quasi-Monte Carlo Methods in Scientific Computing, vol. 106, 299-317 (1995)
+Owen, A. B.: Randomly permuted $(t,m,s)$-nets and $(t,s)$-sequences: Monte Carlo and Quasi-Monte Carlo Methods in Scientific Computing, vol. 106, 299-317 (1995)
 \bibitem{Owen}
@@
 \bibitem{Sobol'seq}
-Sobol', I.M.: On the distribution of points in a cube and the approximate evaluation of integrals, USSR Comput. Math. Math. Phys. \textbf{7}(4), 86-112 (1967)
+Sobol', I. M.: On the distribution of points in a cube and the approximate evaluation of integrals, USSR Comput. Math. Math. Phys. \textbf{7}(4), 86-112 (1967)
 \bibitem{Sobol'}
-Sobol', I.M.: Sensitivity indices for nonlinear mathematical models, Mathematical Modeling and Computational Experiment \textbf{1}, 407-414 (1993)
+Sobol', I. M.: Sensitivity indices for nonlinear mathematical models, Mathematical Modeling and Computational Experiment \textbf{1}, 407-414 (1993)
 \bibitem{Tissot}
-Tissot, J.Y., Prieur, C.: A randomized Orthogonal Array-based procedure for the estimation of first- and second-order Sobol' indices, J. Statist. Comput. Simulation \textbf{85}(7), 1358-1381 (2015)
+Tissot, J. Y., Prieur, C.: A randomized Orthogonal Array-based procedure for the estimation of first- and second-order Sobol' indices, J. Statist. Comput. Simulation \textbf{85}(7), 1358-1381 (2015)
 \bibitem{Tong}
-Tong C.: Self-validated variance-based methods for sensitivity analysis of model outputs, Reliab. Eng. Syst. Saf. \textbf{95}(3), 301-309 (2010)
+Tong, C.: Self-validated variance-based methods for sensitivity analysis of model outputs, Reliab. Eng. Syst. Saf. \textbf{95}(3), 301-309 (2010)
 

### 2017-02-18 article_review/reviewer_letter.tex
Adding real case example
More reviewer changes

@@
 \def\dashfill{\cleaders\hbox to 2em{-}\hfill}
+\newcommand{\answer}[1]{{\color{blue} #1 }}
 
@@
 Is it because the function is not in C?
+
+\answer{End of section 3 and beginning of section 5}
 \end{itemize}
@@
 
-{\color{blue} The biased estimator has been replaced by the unbiased one.}
+{\color{blue} The biased estimator has been replaced with the unbiased one.}
 \item[c.] page 4, column 2, equation (14): it is not clear how $\ell$ is chosen on the RHS, and whether or not the inequality holds for all $\ell \leq m$ or for some specific value of $\ell$ ?
 Please clarify.
+
+\answer{While the RHS holds for any $\ell_*\leq\ell\leq m$, it is definitely not clear how to proceed with the information given in the article.
+We added more detailed information explaining that one only needs to fix $r=m-\ell$.
+Once $r$ is chosen, the RHS only depends on $m$.}
+
 \item[d.] page 4, column 2, line 42: is it not instead "...the error bound $\epsilon_{\hat{I}}$" (hat on subscript I?)?
@@
 If so, this would invalidate the use of a Sobol' sequence to create these vectors, so please clarify this point.
+
+\answer{As pointed out by the reviewer, some clarification was needed in this paragraph. We added the missing explanation indicating that we replace Owen's iid uniform points by a Sobol' sequence.}
+
 \item[g.] page 9, column 2 , "real case model".
@@
 
-{\color{blue} The ``real case model'' has been replaced with a new one as suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections.} 
+{\color{blue} The ``real case model'' has been replaced with a new one as suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections that we agreed with.} 
 \end{itemize}
@@
 
+\answer{More details have been provided in Section 3.1 to help readers follow the ideas behind the approach.
+Among all additions, $k_{j\ell}$ has been defined and the sums $S_m$, $\hS_{\ell,m}$, $\wcS_m$, $\tS_{\ell,m}$ have been briefly described in conjunction with the cone conditions.}
+
 \item[3.] Page $5$ line $56$ presents some bounds that the Sobol' indices must satisfy. Sometimes they won't satisfy those bounds. When do they fail, how that
 be detectable, and what can we do in the face of bounds that might or might not hold? Presumably these issues have been discussed in simpler contexts. The paper should address this issue.
+
+\answer{
+As proposed in this point, we added more information that might be useful for this issue.
+
+If $I_1, I_2, I_3, I_4$ are all in $\mathcal{C}$, by construction we know that
+\[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\widehat{\underline{S}}_u}, \widehat{\underline{S}}_u + \varepsilon_{\widehat{\underline{S}}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\widehat{\overline{S}}_u}, \widehat{\overline{S}}_u + \varepsilon_{\widehat{\overline{S}}_u} \right] .\]
+However, since we do not assume the knowledge of the Walsh coefficients of our integrands, it is hard to verify whether each of them lie inside $\mathcal{C}$.
+Instead, we suggest and refer to some data-based necessary conditions discussed in another article.
+If these necessary conditions are not satisfied, one should consider enlarging the cone.}
 
@@
 
-However, that is not a concerns since error bounds for any estimator can be calculated.
+However, that is not a concern since error bounds for any estimator can be calculated.
 That is, our algorithm can be adapted to any Sobol' index estimator.
-In particular, this is done when ``Correlation 2'' is used in Variant A.b instead of (5).}
+In particular, this is done when ``Correlation 2'' is used in Variant A.b instead of (5).
+Our goal was to design an automatic algorithm that does not ac...}
 
@@
 {\color{blue} We agree with the reviewer that the effective dimension of the higher dimensions integrand might be lower than its lower dimensions counterpart.
-However, evaluating the effective dimension of each integrands already requires a large number of model evaluations itself (\textit{c.f.} Wang.
+However, evaluating the effective dimension of each integrands already requires a large number of model evaluations (\textit{c.f.} Wang.
 X and Fang.
@@
 {\color{blue} The Sobol' g-function has been modified according to the reviewer remark.
-There were no drastic changes observed.
-As a matter of fact, the failure rates have improved for all three approaches (Variant A.a, A.b and B).}
+There were no drastic changes observed, perhaps since the scrambling might remove most of the anchoring.
+Indeed, the new results show that failure rates have improved for all three approaches (Variant A.a, A.b and B).}
 
@@
 {\color{blue} We understand and agree with the issue raised by the reviewer.
-A possible solution is to choose a higher target precision $\epsilon$ when dealing with time-expensive function.
-In the proposed examples, $\epsilon$ was intentionally fixed small to put forward the performance of our algorithm.
-To cover both situations (small and high value of $\epsilon$), the bratley example has been reworked.
+A possible solution is to choose a less conservative precision $\epsilon$ when dealing with time-expensive functions.
+In the proposed examples, $\epsilon$ was intentionally fixed small to push forward the performance of our algorithm.
+That shows the difference in function evaluations cost ....
 
-On another hand, if one has to deal with a function where one day is required to obtain one evaluation, perhaps the use of Sobol' indices should be dropped for a screening method (less accurate but less greedy).
+On another hand, if one has to deal with a function where one day is required to obtain one evaluation, perhaps the use of a screening method is more adequate (less accurate but less greedy).
 Or if available, one could make use of a cluster to perform multiple model evaluations in parallel.}
@@
 For point c., equation (7) was replaced with the unbiased estimator of $\sigma^2$.
-For point e., the distinction has been noted in the paper given that notations cannot be changed (they need to match those of the sourced paper).
+For point e., the distinction has been noted in the paper.
+The authors preferred to keep the notations from previous cited articles.
 \end{document}

### 2017-02-19 article_review/Manuscript.tex
corrected error in formula first-order Sobol' index

@@
 In our framework, we are only interested in single input indices, namely $|u|=1$. The computation of the normalized indices is performed based on the following integral formulas for their numerators:
+{\color{purple}(Lolo)
 \begin{align}
 \label{first.order}
-\underline{\tau}_u^2  &= \int_{[0,1]^{2d}} \left(f(\vx)-
-f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}, \\
+\underline{\tau}_u^2  &= \int_{[0,1]^{2d}} \left(
+f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}, \\
 \label{total.effect}
@@
 \end{align}
+}
 while variance and mean of $f$ are evaluated as:
@@
 One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
+{\color{purple}(Lolo)
 \begin{align}
 \label{first.order.est}
-\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_i)-f(\vx_{i,u}:{\vx'}_{i,-u})\right)f(\vx'_i),\\
+\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_{i,u}:{\vx'}_{i,-u})-f(\vx'_i)\right)f(\vx_i),\\
 \label{total.effect.est}
@@
 \end{align}
+}
 using for $\sigma^2$:
@@
 \label{mu.est}
-\end{equation}}
+\end{equation}
+}
 Then, the Sobol' indices estimators are:
@@
 In both cases, regular and normalized indices can be approximated by estimating some integrals,
+{\color{purple}(Lolo)
 \begin{align*}
-\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d}} \left(f(\vx)-
-f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
+\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d}} \left(f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
 \underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
@@
 \end{align*}
+}
 where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values.

### 2017-02-19 article_review/reviewer_letter.tex
corrected error in formula first-order Sobol' index

@@
 \item[1.] Page 4, left, line 52: What are $\kappa$ and $\vk(\kappa)$ there? They seem undefined, and then many readers will not understand what follows.
+
+{\color{blue} The notations $\kappa$ and $\vk(\kappa)$ are now properly defined.}
 \item[2.] Page 4, right, line 30: Remove the period before (13).
+
+{\color{blue} The typo has been fixed.}
 \item[3.] Page 4, right, lines 38--42: We find $\epsilon_{\hat I}$ in (14) and $\epsilon_{I}$ below (seems inconsistent).
+
+{\color{blue} The typo has been fixed.}
 \item[4.] Section 5.2: These empirical results are for what parameters $d$, $T$, $S_0$, $\sigma$, $\rho$, $K$?
@@
 Also, this example is largely academic and not based on real-life data; I would not call it a "real-life" example.
+
+{\color{blue} The ``real case model'' has been replaced with another academic application as suggested by the second reviewer.
+Nonetheless, we thank the associate editor for pointing out these corrections.}
 \item[5.] The given examples are only in small dimensions. What about higher-dimensional "real-life" examples?-- Pierre L'Ecuyer
+
+{\color{blue} The new academic application is in dimension $10$.
+For higher-dimensional "real-life" examples, our procedure should still work well given that the effective dimension of a model is often way smaller than its nominal dimension.
+Furthermore, the estimator ``Correlation 2'' is really efficient at revealing inputs with small main effects.}
 \end{itemize}
@@
 I think this point should be discussed more thoroughly -- perhaps in the conclusion, or in Section 5 -- by the authors in order to convince the readers that the proposed method is indeed better.
+
+{\color{blue} We address here the remark saying that ``simpler methods based on random sampling and straightforward confidence intervals become more attractive, as they have no extra cost and potentially a better assessment of how likely it is that the error is met''.
+
+First, the cost of constructing the error threshold is a computational cost and not a numerical cost.
+That is, it does not require extra model evaluations.
+This specificity is further discussed in the answer to point 2.
+
+Secondly, we claim that the precision of our procedure should be better than those based on confidence intervals (asymptotic or bootstrap based) obtained with random sampling methods.
+In our approach, the construction of the error bounds makes use of the analytical expression of the Sobol' indices.
+At the opposite, errors bounds in confidence intervals are estimated entirely from the sampling points and are less accurate.
+
+To back up this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling.
+The comparison is carried out for the wing weight example.
+Results show that for an equivalent number of evaluations, the precision of bootstrap confidence intervals is far less accurate than the precision of our procedure.}
 
@@
 
-\answer{As pointed out by the reviewer, some clarification was needed in this paragraph. We added the missing explanation indicating that we replace Owen's iid uniform points by a Sobol' sequence.}
+\answer{As pointed out by the reviewer, some clarification was needed in this paragraph.
+We added the missing explanation indicating that we extend the use of  Owen's estimator by using Sobol' sequences instead of iid random points.}
 

### 2017-02-19 article_review/reviewer_letter.tex
minor changes in rewiever letter

@@
 For higher-dimensional "real-life" examples, our procedure should still work well given that the effective dimension of a model is often way smaller than its nominal dimension.
-Furthermore, the estimator ``Correlation 2'' is really efficient at revealing inputs with small main effects.}
+Furthermore, the estimator ``Correlation 2'' is really efficient at identifying inputs with small main effects.}
 \end{itemize}
@@
 That is, it does not require extra model evaluations.
-This specificity is further discussed in the answer to point 2.
+This specificity is further discussed in the answer to comment 2.
+below.
 
-Secondly, we claim that the precision of our procedure should be better than those based on confidence intervals (asymptotic or bootstrap based) obtained with random sampling methods.
+Secondly, we claim that the precision of our procedure should be better than those of random sampling methods using confidence intervals (asymptotic or bootstrap based).
 In our approach, the construction of the error bounds makes use of the analytical expression of the Sobol' indices.
@@
 To back up this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling.
-The comparison is carried out for the wing weight example.
-Results show that for an equivalent number of evaluations, the precision of bootstrap confidence intervals is far less accurate than the precision of our procedure.}
+The comparison is carried out for the bratley test function in Section 5.3.
+Results show that for an equivalent number of evaluations, random methods using confidence intervals are less accurate than our procedure.}
 

### 2017-02-19 article_review/Manuscript.tex
More changes

--- 2017-02-18 article_review/Manuscript.tex
@@
 Thus, we can identify each $\vk\in\naturals_0^d$ with one $\kappa\in\naturals_0$ such that $\tilde{\vk}(\kappa)=\vk$.
-This ordering ensures that $\mathcal{P}_m^\perp\setminus\{\vzero\}=\{\tilde{\vk}(\lambda b^m)\}_{\lambda=1}^\infty$.
+The ordering is not unique and one should choose it such that large values of $\kappa$ are mapped to smaller values of $\absolute{\hf_{\tilde{\vk}(\kappa)}}$.
+It also ensures that $\mathcal{P}_m^\perp\setminus\{\vzero\}=\{\tilde{\vk}(\lambda b^m)\}_{\lambda=1}^\infty$.
 If we identify $\hf_{\kappa}=\hf_{\tilde{\vk}(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,}
@@
 \comment{To use the error bound \eqref{mapped_error_bound} to design and automatic algorithm would require the knowledge of the Walsh coefficients.
-To avoid this assumption, we will estimate them via the fast transform obtained using the precomputed function values.
+To avoid this assumption, we will estimate them via the fast transform obtained using the precomputed function values already used to estimate the mean.
 We will refer to the discrete coefficients as $\tf_{m,\kappa}$,}
@@
 Then, we discuss a possible improvement by considering a new estimator introduced in \cite{Owen} for the estimation of first-order indices.
+
+\comment{We assumed that evaluating our model is expensive.
+Thus, we will focus our cost study on the number of function evaluations needed to estimate the indices.
+The function evaluations used to estimate the indices are the same as the ones used to compute the discrete Walsh coefficients.
+The only computation cost that could be expensive is the fast transform algorithm.
+However, on a regular laptop computing the discrete coefficients of $2^{20}$ points takes around $0.5$ seconds while evaluating these points at an average evaluation time of $1$ microsecond, takes a total of around $1$ second.}
 
@@
 {\color{purple} (Lolo) Results are averaged over $100$ repetitions by applying different scrambling}.
-For each repetition, we fix the tolerance $\varepsilon=5.10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points).
+For each repetition, we fix the tolerance $\varepsilon=5\cdot10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points).
 The algorithm error bound factor described in \eqref{errbd} is set to $\mathfrak{C}(m)=10\times 2^{-m}$.
 
-\comment{For the following examples we do not know the true Walsh coefficients of the integrands.
-Therefore, we cannot say whether they lie inside the cone defined.
-}The failure rates $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$ of each estimate are evaluated over the $100$ repetitions.
+\comment{For the examples in this section we do not know the true Walsh coefficients of the integrands.
+Indeed, since the mapping $\tilde{\vk}$ is chosen heuristically, the cone conditions will also depend on each scrambling.
+Therefore, we cannot say whether the integrands lie inside the cone.
+For this reason, we define the failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$ over the $100$ repetitions.
 These rates are the proportion of the repetitions in which the true estimation errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$.
-When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and the integrands fall outside the cone \eqref{conecond}.
+When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and at least one integrand ($I_1$, $I_2$, $I_3$, or $I_4$) falls outside the cone \eqref{conecond}.}
 
@@
 Figure \ref{boxplots.gfunc} shows boxplots of the $100$ estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$.
-The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.
+The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.
 \begin{figure}[t]
 \caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$.
-The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
+The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
 \vspace*{0.2cm}
@@
 \caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$.
-The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
+The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
 \vspace*{0.2cm}

### 2017-02-19 article_review/reviewer_letter.tex
More changes

--- 2017-02-18 article_review/reviewer_letter.tex
@@
 
+\answer{The function values used to estimate the Sobol' indices are the same to compute the discrite Walsh coefficients.
+Thus, there are no additional function evaluations needed to compute $\widetilde{S}_{l,m}$.
+}
+
 \item[3.]The set C: In the section describing numerical results, choices are made for the parameters $\ell^*$ and $r$ which in turn define the set (cone) of functions C for which the error threshold formula (14) used to derive the algorithm holds.
@@
 
-\answer{End of section 3 and beginning of section 5}
+\answer{As the reviewer claims, this is a key point that we revised and explained with more detail.
+It is really hard to verify whether an integrand satisfies the cone condition.
+Indeed, because we choose our mapping $\tilde{\vk}$ heuristically, the cone conditions will also depend on the scrambling.
+At the end of section 3 we cited some data-based necessary conditions that can help identify when integrands are not in the cone.
+In addition, also at the beginning of section 5, we note that if the error bound is not satisfied it is certain that the integrand is not in the cone.}
 \end{itemize}

### 2017-02-20 article_review/Manuscript.tex
More changes for the review

@@
 
-\newcommand{\comment}[1]{{\color{cyan} (Toni) #1 }}
+\newcommand{\comment}[1]{{\color{cyan} #1 }}
 % Insert the name of "your journal" with
@@
 Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1]^{d}$.
-Assume that the points $\vx_i$ (resp.
-$\vx'_i$) are all coordinate-wise different; that is $\forall (i_1,i_2) \in \{0,,n-1\}^2$, such that $i_1 \neq i_2$: $$x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
+In these sets, all points $\vx_i$ (resp.
+$\vx'_i$) are coordinate-wise different, i.e.
+for all $(i_1,i_2) \in \{0,\dots,n-1\}^2$ such that $i_1 \neq i_2$: $$x_{i_1,j} \neq x_{i_2,j}, \qquad \text{for any  } j=1,\dots,d .$$
 Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp.
@@
 We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if for any $u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1]^a$.
-We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
+We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$ and exclude the trivial case $\vx_i = \vx'_i$ for all $i\in\{0,\dots,n-1\}$.
 \end{definition}
-
-\begin{remark}
-In the following, the two replicated designs $\mathcal{P}$, $\mathcal{P}'$ are constructed to avoid the degenerate case $\forall i \ \vx_i = \vx'_i$. 
-\end{remark}}
+}
 
@@
 
-\comment{We assumed that evaluating our model is expensive.
-Thus, we will focus our cost study on the number of function evaluations needed to estimate the indices.
-The function evaluations used to estimate the indices are the same as the ones used to compute the discrete Walsh coefficients.
-The only computation cost that could be expensive is the fast transform algorithm.
-However, on a regular laptop computing the discrete coefficients of $2^{20}$ points takes around $0.5$ seconds while evaluating these points at an average evaluation time of $1$ microsecond, takes a total of around $1$ second.}
+\comment{For this article, we assumed that evaluating the model is expensive.
+Hence, to study the cost we will focus on the number of function evaluations needed to estimate the indices.
+The function values used to estimate the indices are also used to compute the discrete Walsh coefficients.
+Thus, there are no additional evaluations needed to compute the error bound.
+The only computation cost that could be expensive is the fast Walsh transform.
+However, on a regular laptop, if we consider an extreme case of obtaining $2^{20}$ model values ($\approx$ one million points):
+\begin{itemize}
+\item At an average evaluation time of $1$ microsecond per point, the total evaluation time is about $1$ second.
+\item The fast transform on these values takes around $0.5$ seconds.
+\end{itemize}
+}
 
@@
 {\color{purple} (Lolo) This approach iteratively constructs a $2d$-dimensional Sobol' sequence then assigns its first $d$ coordinates to $\mathcal{P}_{m}$ and its last $d$ coordinates to $\mathcal{P}'_{m}$.
-The $2d$-dimension Sobol' sequence is generated based on the directional numbers found in \cite{Kuo}.
-These directional numbers insure better two-dimensional projections of the resulting Sobol' sequence.
-In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling scheme \cite{HonHic00a,Owe95}.......}
+The $2d$-dimensional Sobol' sequence is generated based on the direction numbers found in \cite{Kuo}.
+These direction numbers optimize the two-dimensional projections of the Sobol' sequence.
+Although this is the authors choice, one may choose any other Sobol' construction of $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ as long as the $2d$ dimensions are each generated with different primitive polynomials.
+In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling scheme \cite{HonHic00a,Owe95}.}
 
@@
 
-We illustrate our sequential estimation procedure with two classical test functions and one real example. In each case, Sobol' indices are estimated with the following three variants:
+We illustrate our sequential estimation procedure with two classical test functions and one academic example. In each case, Sobol' indices are estimated with the following three variants:
 \begin{itemize}
@@
 
-%\comment{As a real case example, we will study the wing weight function:
+%\comment{As an academic case example, we will study the wing weight function:
 %\begin{align*}
@@
 
-%\subsection{Real case model}
-%As a real case example, we will study the payoff function of an arithmetic mean Asian call option.
+%\subsection{Wing weight model}
+%As an academic case example, we will study the payoff function of an arithmetic mean Asian call option.
 For a discretized Brownian motion $\vect{B}=(B_{t_1}, B_{t_2},\dots, B_{t_d})$ at times $t_i=T\times i/d$, the payoff of the option is:

### 2017-02-20 article_review/reviewer_letter.tex
More changes for the review

--- 2017-02-19 article_review/reviewer_letter.tex
@@
 \textcolor{blue}{Dear associated editor and reviewers,\\
-we would like to thank you for the positive and constructive feedback. Below we have
-compiled a detailed list of answers (blue text) to the issues raised in the review reports.
-In particular, in light of reviewer's two remark, the Asian option problem was deleted and replaced with a new ``real function''.\\
+we would like to thank you for the positive and constructive feedback.
+Below we have compiled a detailed list of answers (blue text) to the issues raised in the review reports.
+In particular, in light of reviewer's two remark, the Asian option problem was replaced with a new ``real function''.\\
 Best regards,\\
@@
 \item[1.] Page 4, left, line 52: What are $\kappa$ and $\vk(\kappa)$ there? They seem undefined, and then many readers will not understand what follows.
+
+{\color{blue} The notations $\kappa$ and $\tilde{\vk}(\kappa)$ (former $\vk(\kappa)$) are now properly defined.}
 \item[2.] Page 4, right, line 30: Remove the period before (13).
+
+{\color{blue} The typo has been fixed.}
 \item[3.] Page 4, right, lines 38--42: We find $\epsilon_{\hat I}$ in (14) and $\epsilon_{I}$ below (seems inconsistent).
+
+{\color{blue} The typo has been fixed.}
 \item[4.] Section 5.2: These empirical results are for what parameters $d$, $T$, $S_0$, $\sigma$, $\rho$, $K$?
@@
 Also, this example is largely academic and not based on real-life data; I would not call it a "real-life" example.
+
+{\color{blue} The ``real case model'' has been replaced with another academic application as suggested by the second reviewer.
+Nonetheless, we thank the associate editor for pointing out these corrections.}
 \item[5.] The given examples are only in small dimensions. What about higher-dimensional "real-life" examples?-- Pierre L'Ecuyer
+
+{\color{blue} The new academic application is in dimension $10$.
+For higher-dimensional examples, we expect the effective dimension to be much smaller than its nominal dimension.
+Otherwise, a high dimensional problem with high effective dimension will be hard to deal with in most applications.
+In low effective dimensional problems, most Sobol' indices will have a small value.
+As shown in the examples, all the small value indices are very easily estimated.
+Furthermore, the estimator ``Correlation 2'' can (in some cases) reduce further the function values needed for inputs with small main effects.}
 \end{itemize}
@@
 
+{\color{blue} The points raised in this remark are crucial. We expect to have answered these questions with the information added the article.
+
+Below we address the remark: ``simpler methods based on random sampling and straightforward confidence intervals become more attractive, as they have no extra cost and potentially a better assessment of how likely it is that the error is met''.
+
+The cost of constructing the error bound is a computational cost and not a numerical cost. That is, it does not require extra model evaluations. This point is further discussed in question 2.
+
+For the estimation of the integrands, random sampling methods have convergence rates of $\mathcal{O}(n^{-1/2})$ instead of the quasi-Monte Carlo methods $\mathcal{O}(n^{-1+\delta})$.
+Hence, we expect the precision of our procedure to be better than those of random sampling methods that use confidence intervals (asymptotic or bootstrap based).
+In our approach, the construction of the error bounds is analytical even if the Sobol' sequence is randomly sampled.
+However, in other random sampling methods the confidence intervals are estimated entirely from the sampling points and are less accurate.
+
+To confirm this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling.
+The comparison is carried out for the Bratley test function in Section 5.3.
+Results show that for an equivalent number of evaluations, random methods using confidence intervals are less accurate than our procedure.}
+
 \item[2.] Complete assessment of the cost: Since only the different variants of this method are compared in the numerical results, it is fair to focus on the number of function evaluations to compare their respective costs.
@@
 
-\answer{The function values used to estimate the Sobol' indices are the same to compute the discrite Walsh coefficients.
-Thus, there are no additional function evaluations needed to compute $\widetilde{S}_{l,m}$.
-}
+\answer{We added an explanation at the beginning of Section 4.
+The function values used to estimate the Sobol' indices are the same ones used to compute the discrete Walsh coefficients.
+Thus, there are no additional function evaluations needed to compute $\widetilde{S}_{\ell,m}$.
+The only cost we should consider is the computational cost of calculating the fast transform.
+However, on a regular laptop, in the extreme case of $2^{20}$ model evaluations, the fast transform takes around $0.5$ seconds.}
 
@@
 At the end of section 3 we cited some data-based necessary conditions that can help identify when integrands are not in the cone.
-In addition, also at the beginning of section 5, we note that if the error bound is not satisfied it is certain that the integrand is not in the cone.}
+In addition, also at the beginning of section 5, we noted that if the error bound is not satisfied it is certain that the integrand is not in the cone.}
 \end{itemize}
@@
 \answer{While the RHS holds for any $\ell_*\leq\ell\leq m$, it is definitely not clear how to proceed with the information given in the article.
-We added more detailed information explaining that one only needs to fix $r=m-\ell$.
+We added more details clarifying that one only needs to fix $r=m-\ell$.
 Once $r$ is chosen, the RHS only depends on $m$.}
@@
 We use a 2d-dimensional Sobol' sequence and assign its first d dimensions to the first design and the remaining ones to the second design.
-Then, each Sobol' sequence is scrambled independently; except in Variant B where the scrambling is the same to insure that the two designs are replicated designs of order one.
+Although this is our choice, one may choose any other Sobol' construction of $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ as long as the $2d$ dimensions are each generated with different primitive polynomials.
+After that, each Sobol' sequence is scrambled independently; except in Variant B where the scrambling of both designs should be the same to ensure that both designs after the scrambling are replicated of order one.
 
-As for the properties of the Sobol' sequences, the ones used in this paper are generated with the directional numbers found by S.
-Joe and F.
-Y.
-Kuo (2008).
-These directional numbers insure better two-dimensional projections of the resulting Sobol' sequences.}
+As for the properties, in this paper we generate the sequences with the direction numbers found by S. Joe and F. Y. Kuo (2008) who optimized the two-dimensional projections.}
 
@@
 
-\answer{As pointed out by the reviewer, some clarification was needed in this paragraph. We added the missing explanation indicating that we replace Owen's iid uniform points by a Sobol' sequence.}
+\answer{As pointed out by the reviewer, some clarification was needed in this paragraph.
+We indicated that we extend the use of  Owen's estimator by using Sobol' sequences instead of iid random points.}
 
@@
 
-{\color{blue} The ``real case model'' has been replaced with a new one as suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections that we agreed with.} 
+{\color{blue} The ``real case model'' has been replaced with a new one suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections that we agreed with.} 
 \end{itemize}
@@
 {\color{blue} We thank the reviewer for this remark.
-The definition was intended for point sets where all points are coordinate-wise different.
-More precisely, consider a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and two points $\vx_{i_1}$, $\vx_{i_2}$, $i_1 \neq i_2$.
+Definition 1 is not intended to describe good points.
+It simply generalizes the definition of replicated designs to suggest the use of a bigger set of types of points.
+For instance, this definition clearly includes orthogonal arrays and Sobol' sequences, but rank-1 lattices are another type of points that could also generate replicated designs of order 1.
+Each of them are different types of points whose quality is measured with different tools.
+The authors think that at this point, the quality should be studied by type of points instead.
+
+Nonetheless, we modified the definition to only consider point sets whose points are coordinate-wise different.
+More precisely, consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\vx_{i_1}$, $\vx_{i_2}$, two different points from this set.
 Then $\vx_{i_1}$ and $\vx_{i_2}$ are coordinate-wise different if:
 $$ x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
-Definition 1 has been reworked to include this property.
-This also tackles the issue of having more than one permutation that would rearrange the rows $\vx'_i$ into $\vx_i$.
-Now, the permutation is unique.
+Definition 1 has been reworked to include this property. This solves the issue of having more than one permutation that would rearrange the rows $\vx'_i$ into $\vx_i$. Now, the permutation is unique.
 
@@
 
-\answer{More details have been provided in Section 3.1 to help readers follow the ideas behind the approach.
+\answer{More details have been provided in Section 3.1.
 Among all additions, $k_{j\ell}$ has been defined and the sums $S_m$, $\hS_{\ell,m}$, $\wcS_m$, $\tS_{\ell,m}$ have been briefly described in conjunction with the cone conditions.}
@@
 \answer{
-As proposed in this point, we added more information that might be useful for this issue.
+As proposed in this remark, we added more information at the end of Section 3 to clarify the issue.
 
@@
 {\color {blue} We acknowledge that analytical formulas of Sobol' indices are invariant by adding a constant shift $c$ to the function $f$.
-As underlined by the reviewer, in our algorithm the addition of a constant shift $c$ modifies the error bound for $\vI_3$ but also the errors bounds for the others integrands ($\vI_1$, $\vI_2$ and $\vI_4$).
-More generally, our algorithm depends on the analytical expression of the Sobol' index estimator considered.
+As underlined by the reviewer, in our algorithm the addition of a constant shift $c$ modifies the error bound for $\vI_3$ but also the error bounds for the integrands $\vI_1$ and $\vI_2$.
 
-However, that is not a concern since error bounds for any estimator can be calculated.
-That is, our algorithm can be adapted to any Sobol' index estimator.
-In particular, this is done when ``Correlation 2'' is used in Variant A.b instead of (5).
-Our goal was to design an automatic algorithm that does not ac...}
+However, our goal is to design an automatic (finds the number of points needed automatically) and adaptive (adapts to the difficulty of the problem) algorithm whose inputs are only:
+\begin{itemize}
+\item the absolute error tolerance.
+\item the black-box $f$ that only gives the value of $f(\vx)$ at any $\vx\in [0,1]^d$.
+\end{itemize}
+Without additional information and for the class of functions defined, the algorithm cannot distinguish whether a finite number of function values correspond to a shifted model or to another completely different model.
+We could restrict to a smaller class of functions to modify the algorithm and detect the shift case, but we preferred providing a more general algorithm.}
 
@@
 
-{\color{blue} We agree with the reviewer that the effective dimension of the higher dimensions integrand might be lower than its lower dimensions counterpart.
-However, evaluating the effective dimension of each integrands already requires a large number of model evaluations (\textit{c.f.} Wang.
+{\color{blue} We agree with the reviewer that the effective dimension of the $2d-1$ integrand might be lower than the $d+1$ integrand.
+However, estimating the effective dimension of each integrand already requires a large number of model evaluations (\textit{c.f.} Wang.
 X and Fang.
@@
 
-{\color{blue} The Sobol' g-function has been modified according to the reviewer remark.
-There were no drastic changes observed, perhaps since the scrambling might remove most of the anchoring.
+{\color{blue} The Sobol' g-function has been modified according to the reviewer's remark.
+There were no drastic changes observed, perhaps because the scrambling removes the anchoring.
 Indeed, the new results show that failure rates have improved for all three approaches (Variant A.a, A.b and B).}
@@
 Section $5.2$ has been reworked to introduce this new test function.
-Our results are compared to formers obtained by screening approaches (Moon, H.
+Our results are compared to older results obtained by screening approaches (Moon, H.
 (2010)).}
@@
 A possible solution is to choose a less conservative precision $\epsilon$ when dealing with time-expensive functions.
+The algorithm also allows to modify the maximum number of points allowed to estimate the indices.
 In the proposed examples, $\epsilon$ was intentionally fixed small to push forward the performance of our algorithm.
-That shows the difference in function evaluations cost ....
+That clearly shows the difference in number of function evaluations needed to estimate different indices for the same model.
 
-On another hand, if one has to deal with a function where one day is required to obtain one evaluation, perhaps the use of a screening method is more adequate (less accurate but less greedy).
+If one has to deal with a function where one day is required to obtain one evaluation, perhaps the use of a screening method is more adequate (less accurate but less greedy).
 Or if available, one could make use of a cluster to perform multiple model evaluations in parallel.}

### 2017-02-20 article_review/matlab_code_revision/SI_all_example_percentage.m

@@ -62,99 +62,99 @@ fudge = @(m,d) 10*2.^-(1.*m);
 % csvwrite('bratley_variantAb_small_estimates.csv', small)
 % 
 % 
-%% Sobol' g-function
-disp('Running Sobol g-function example ...')
-d = 6;
-a = [0 1/2 3 9 99 99];
-f = @(x) prod(bsxfun(@(x,a) (abs(3*x-2)+a)./(1+a), x , a),2) +  pause_t(s);
-hyperbox = [zeros(1,d) ; ones(1,d)];
-
-% R = [.5867811893, .2607916397, 0.3667382378e-1, 0.5867811312e-2, 0.5867753221e-4, 0.5867753221e-4; .6900858920, .3561733634, 0.563335432e-1, 0.91705767e-2, 0.920079e-4, 0.920079e-4]; % If abs(4x-2)
-R = [.6042800971, .2360469148, 0.2855765831e-1, 0.4339846615e-2, 0.4210460219e-4, 0.4210460219e-4; .7251945137, .3480933667, 0.483463013e-1, 0.74762327e-2, 0.727601e-4, 0.727601e-4]; % If abs(3x-2)
-SI = zeros(2, d);
-SI_small = zeros(2, d);
-SI_n = SI;
-SI_n_small = SI_small;
-error = SI;
-error_small = SI_small;
-reliability = SI;
-reliability_small = SI_small;
-error_all = [];
-error_all_small = [];
-SI_n_print = [];
-SI_n_print_small = [];
-small = [];
-for k = 1:samples
-    disp(k)
-    sobstr = sobolset(3*d); %generate a Sobol' sequence 3*d to consider the changing to the estimator for some smaller size indices
-    sobstr = scramble(sobstr,'MatousekAffineOwen'); %scramble it
-    [q,app_int,out_param] = cubSobol_SI_all_g(f,hyperbox,sobstr,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d), 'threshold_small', 0);
-    SI = SI + q;
-    SI_n_print = [SI_n_print; out_param.n];
-    SI_n = SI_n + out_param.n;
-    error = error + abs(R-q);
-    error_all = [error_all; abs(R-q)];
-    reliability = reliability + 1*(abs(R-q) > max(abstol,R*reltol));
[…]

### 2017-02-20 article_review/matlab_code_revision/SI_fo_example_percentage.m

@@ -45,64 +45,64 @@ fudge = @(m,d) 10*2.^-(1.*m);
 % 
 % 
 
-%% Sobol' g-function
-disp('Running Sobol g-function example ...')
-d = 6;
-a = [0 1/2 3 9 99 99];
-f = @(x) prod(bsxfun(@(x,a) (abs(3*x-2)+a)./(1+a), x , a),2) +  pause_t(s);
-hyperbox = [zeros(1,d) ; ones(1,d)];
-
-% R = [.5867811893, .2607916397, 0.3667382378e-1, 0.5867811312e-2, 0.5867753221e-4, 0.5867753221e-4]; % If abs(4x-2)
-R = [.6042800971, .2360469148, 0.2855765831e-1, 0.4339846615e-2, 0.4210460219e-4, 0.4210460219e-4]; % If abs(3x-2)
-SI = zeros(1, d);
-SI_n = SI;
-error = SI;
-reliability = SI;
-error_all = [];
-SI_n_print = [];
-for k = 1:samples
-    [q,app_int,out_param] = cubSobol_SI_fo_g(f,hyperbox,'abstol',abstol,'reltol',reltol,'mmin',mmin,'mmax',mmax,'fudge',@(m) fudge(m,d));
-    SI = SI + q;
-    SI_n_print = [SI_n_print; out_param.n];
-    SI_n = SI_n + out_param.n;
-    error = error + abs(R-q);
-    error_all = [error_all; abs(R-q)];
-    reliability = reliability + 1*(abs(R-q) > max(abstol,R*reltol));
-end
-SI = SI/samples; SI_n = SI_n/samples; reliability = 1 - reliability/samples; error = error/samples;
-% round(SI, pre,'significant')
-% round(SI_n)
-% round(error, pre, 'significant')
-% round(reliability*100)
-
-csvwrite('sobolg_variantB_replicated_reliability.csv', reliability)
-csvwrite('sobolg_variantB_replicated_errors.csv', error_all)
-csvwrite('sobolg_variantB_replicated_nvalues.csv', SI_n_print)
-
-
-
-% %% Wing weight function
-% disp('Running wing weight function example ...')
-% d = 10;
-% f = @(x) 0.036*x(:, 1).^0.758.*x(:, 2).^0.0035.*(x(:, 3)./ ...
[…]

### 2017-02-20 article_review/Manuscript.tex
added Section 5.3, reworked Section 5.2, deleted c_j figures

@@
 This function is further described in Section \ref{sec:5}.
-\begin{figure}[!ht]
+\begin{figure}[t]
 \caption{The delimited region on the figure represents the values $\underline{S}_2$ in $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ for the Bratley \textit{et al.} function.
@@
 If the stopping criterion is satisfied, the algorithm stops and Sobol' estimates are returned. Otherwise, $m$ is incremented by one to perform a new estimation. 
-\begin{algorithm}[!ht]
+\begin{algorithm}[t]
 \caption{Sequential estimation of Sobol' indices}
@@
 {\color{purple}(Lolo) We assume that the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$.
-If this assumption holds, we expect to observe case $2)$ more often than case $1)$ and \eqref{cost.comparison} verifies the following inequality:
-\begin{equation}
-\sum \limits_{j \in \Gamma} c_j \leq 0 \ .
-\label{assumption}
-\end{equation}
-The validity of this assumption is tested on the numerical examples presented in Section \ref{sec:5}.
-%Overall we expect to observe case $2)$ more often than case $1)$.
-Indeed, the numerator of $\underline{S}_u$ requires to estimate $2d$ dimensional integrals against only $d+1$ dimensional integrals for the numerator of $\ov{$S$}_u$.
-Hence, it seems reasonable to expect that it will take less points to estimate $\ov{$S$}_u$ than $\underline{S}_u$.
+This assumption is tested on the numerical examples presented in Section \ref{sec:5.1} by comparing the number of evaluations required by the two numerators.
+
+If this assumption holds, we expect to observe case $2)$ more often than case $1)$.
 Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to usually hold as ``Correlation 2" is shown to perform better for small first-order indices (\textit c.f.
 \cite{Owen}).}
+\bigskip
 
@@
 
-{\color{purple} (Lolo) To verify the validity of assumption \eqref{assumption}, the sum of the $c_j$ is evaluated for each repetition and barplots of its values are drawn.}
+%{\color{purple} (Lolo) To test if the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$,
+
+%To verify the validity of assumption \eqref{assumption}, the sum of the $c_j$ is evaluated for each repetition and barplots of its values are drawn.}
 
@@
 
-{\color{purple} (Lolo)
-\begin{figure}[t]
-\caption{Barplots of the $100$ values taken by the sum of the $c_j$. The distribution is bimodal with $60\%$ values equal to $0$.}
-\vspace*{0.2cm}
-\centering
-\includegraphics[width=0.25\textwidth]{sobolg_cj.eps}
-\label{cj.gfunc}
-\end{figure}
-Figure \ref{cj.gfunc} shows barplots of the $100$ values of the sum of the $c_j$.
-The distribution is bimodal with around $60\%$ of the values equal to $0$ and $40\%$ equal to $512$.
-As a result, assumption \eqref{assumption} is validated $60\%$ of the times and Variant A.b does not cost more (or slightly more) than Variant A.a.}
+{\color{purple}(Lolo) Table \ref{comparison.gfunc} shows the average number of evaluations performed in Variant $A.a$ to estimate $I_1$, the numerator of $\underline{S}_u$, and $I_2$, the numerator of $\ov{$S$}_u$.
+The column $I_2 > I_1$ indicates the number of times where $I_2$ required more evaluations than $I_1$.
+We observe that $I_2$ never requires more evaluations than $I_1$.
+This seems to indicate that the effective dimension of $I_1$ is higher than $I_2$ for this example.
+\begin{table}[t]
+\caption{Number of evaluations evaluations performed to estimate $I_1$ and $I_2$ in Variant $A.a$. $N$ is the number of times among the $100$ repeats where $I_2$ required more evaluations than $I_1$}
+\centering
+\begin{tabular}{cccc}
+\hline
+ input & $I_1$ & $I_2$ & $I_2 > I_1$ \\ \hline
+ $x_1$ & $32768$ & $32768$ & $0$ \\   \hline
+ $x_2$ & $16384$ & $16384$ & $0$ \\  \hline
+ $x_3$ & $4096$ & $2048$ & $0$ \\  \hline
+ $x_4$ & $830$ & $512$ & $0$ \\  \hline
+ $x_5$ & $512$ & $512$ & $0$ \\  \hline
+ $x_6$ & $512$ & $512$ & $0$ \\  \hline
+\end{tabular}
+\label{comparison.gfunc}
+\end{table}}
 \bigskip
 
+Table \ref{res.gfunc.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.
+The results show that the use of Variant $B$ leads to slightly higher estimation errors than those obtained with Variant $A.a$ or Variant $A.b$.
+However, the total number of evaluations is {\color{purple}half as large}.
+As such, this approach remains interesting when one wants to estimate only first-order indices.
 \begin{table}[t]
@@
 \end{table}
-Table \ref{res.gfunc.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.
-The results show that the use of Variant $B$ leads to slightly higher estimation errors than those obtained with Variant $A.a$ or Variant $A.b$.
-However, the total number of evaluations is {\color{purple}half as large}.
-As such, this approach remains interesting when one wants to estimate only first-order indices.
 
@@
 
-{\color{purple} (Lolo)
-\begin{figure}[t]
-\caption{Barplots of the $100$ values taken by the sum of the $c_j$. $88\%$ of the values are lower or equal to zero. The maximal value equal $3072$.}
-\vspace*{0.2cm}
-\centering
-\includegraphics[width=0.45\textwidth]{bratley_cj.eps}
-\label{cj.bratley}
-\end{figure}
-
-Figure \ref{cj.bratley} shows barplots of the $100$ values of the sum of the $c_j$.
-$88\%$ of the values are lower of equal to zero, that is assumption \eqref{assumption} is validated most of the times.}
-\bigskip
-
-Table \ref{res.bratley.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.
-The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$.
-Failure rates are similar to those of Variant $A.b$.
-Since the total number of evaluations is close to the one of Variant $A.b$ at the exception of input $x_4$.
-As a conclusion, Variant $B$ does not bring much improvement for this example.
-\begin{table}[!ht]
+{\color{purple}(Lolo) Table \ref{comparison.bratley} shows the average number of evaluations performed in Variant $A.a$ to estimate $I_1$, the numerator of $\underline{S}_u$, and $I_2$, the numerator of $\ov{$S$}_u$.
+The column $I_2 > I_1$ indicates the number of times among the $100$ repeats where $I_2$ required more evaluations than $I_1$.
+\begin{table}[t]
+\caption{Number of evaluations evaluations performed to estimate $I_1$ and $I_2$ in Variant $A.a$. $N$ is the number of times where $I_2$ required more evaluations than $I_1$}
+\centering
+\begin{tabular}{cccc}
+\hline
+ input & $I_1$ & $I_2$ & $I_2 > I_1$ \\ \hline
+ $x_1$ & $16876$ & $16384$ & $0$ \\  \hline
+ $x_2$ & $8520$ & $8192$ & $0$ \\  \hline
+ $x_3$ & $4096$ & $2786$ & $0$ \\  \hline
+ $x_4$ & $3794$ & $1096$ & $4$ \\  \hline
+ $x_5$ & $635$ & $512$ & $0$ \\  \hline
+ $x_6$ & $712$ & $512$ & $0$ \\ 
+\hline 
+\end{tabular}
+\label{comparison.bratley}
+\end{table}
+\begin{table}[t]
 \caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
@@
 \end{table}
+We observe that $I_2$ almost never requires more evaluations than $I_1$. This seems to indicate that the effective dimension of $I_1$ is also higher than $I_2$ for this example.}
+
+Table \ref{res.bratley.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.
+The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$.
+Failure rates are similar to those of Variant $A.b$.
+Since the total number of evaluations is close to the one of Variant $A.b$ at the exception of input $x_4$.
+As a conclusion, Variant $B$ does not bring much improvement for this example.
 \bigskip
@@
 \end{align*}
-Table \ref{wing_inputs_table} gives the range of variation of each input and their physical representation.  All inputs are independent and uniformly distributed in their respective ranges.
+Table \ref{wing_inputs_table} gives the range of variation of each input and their physical representation.
+All inputs are uniformly distributed in their respective ranges.
+To illustrate the performance of our procedure, five additional inert inputs $x_{11}$, $\dots$, $x_{15}$ are added which serve only to add ``noise'' to the sensitivity analysis.
+The inert inputs are all uniformly distributed in $[0,1]$.
 \begin{table}[!ht]
-\caption{Inputs and their ranges of variation. All inputs are independent and uniformly distributed in their respective ranges.}
+\caption{Inputs and their ranges of variation. All inputs are uniformly distributed in their respective ranges.}
 \centering
@@
 $x_{10}$ & $[0.025, 0.08]$ & paint weight (lb/ft$^2$) \\
+$x_{11},\dots,x_{15}$ & $[0,1]$ & ``noise'' \\
 \hline
@@
 
-(TABLES OF RESULTS)
+The motivation of this application is to test if our procedure capture the same set of influent inputs $(x_1,x_3,x_7,x_8,x_9)$ selected by the analysis of Forrester \textit{et al.}.
+
+A second motivation is to compare the performance of each variant ($A.a$, $A.b$ and $B$) on a function where true values of Sobol' indices cannot be computed.
+The comparison is based on averaged Sobol' estimates and averaged total number of evaluations over $100$ repetitions.
+\bigskip
+
+Tables \ref{res.wing.Aa}, \ref{res.wing.Ab} show the results obtained with Variant $A.a$ and  Variant $A.b$.
+Both variants capture well the presence of inert inputs.
+Variant A.b is more expansive but validates the property that first-order indices are lower or equal to total-effect indices.
+At the opposite, Variant A.a fails to guarantee this property for inputs with small main effects: $x_2$, $x_4$, $x_5$, $x_6$.
+This highlights once again the efficiency of ``Correlation 2''.
+The boxplots represented in Figure \ref{boxplots.wing} emphasize the latter observation, Variant $A.b$ provides less variance in the estimates.
+
 \begin{table}[!ht]
@@
  input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
- $x_1$ & $0.1245$ & $0.1280$  \\ \hline
+ $x_1$ & $0.1245$ & $0.1279$  \\ \hline
  $x_2$ & $0.0001$ & $< 10^{-4}$  \\ \hline
  $x_3$ & $0.2203$ & $0.2261$  \\ \hline
- $x_4$ & $0.0025$ & $0.0006$  \\ \hline
- $x_5$ & $0.0007$ & $0.0001$  \\ \hline
- $x_6$ & $0.0034$ & $0.0024$  \\ \hline 
- $x_7$ & $0.1410$ & $0.1451$  \\ \hline
- $x_8$ & $0.4116$ & $0.4197$  \\ \hline
- $x_9$ & $0.0851$ & $0.0876$  \\ \hline
- $x_{10}$ & $0.0031$ & $0.0042$  \\ \hline
-\hline
-\multicolumn{3}{l}{Total number of evaluations: $84 \ 792$} \\ \hline 
+ $x_4$ & $0.0022$ & $0.0006$  \\ \hline
+ $x_5$ & $0.0011$ & $0.0001$  \\ \hline
+ $x_6$ & $0.0037$ & $0.0024$  \\ \hline 
+ $x_7$ & $0.1410$ & $0.1452$  \\ \hline
+ $x_8$ & $0.4116$ & $0.4196$  \\ \hline
+ $x_9$ & $0.0851$ & $0.0877$  \\ \hline
+ $x_{10}$ & $0.0038$ & $0.0043$  \\ \hline
+ $x_{11},\dots,x_{15}$ & $0$ & $0$  \\ \hline
+\hline
+\multicolumn{3}{l}{Total number of evaluations: $87 \ 844$} \\ \hline 
 \end{tabular}
@@
   input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
- $x_1$ & $0.1245$ & $0.1280$  \\ \hline
+ $x_1$ & $0.1245$ & $0.1279$  \\ \hline
  $x_2$ & $< 10^{-4}$ & $< 10^{-4}$  \\ \hline
@@
  $x_6$ & $0.0023$ & $0.0024$  \\ \hline 
- $x_7$ & $0.1410$ & $0.1451$  \\ \hline
- $x_8$ & $0.4116$ & $0.4197$  \\ \hline
- $x_9$ & $0.0850$ & $0.0876$  \\ \hline
- $x_{10}$ & $0.0042$ & $0.0042$  \\ \hline
-\hline
-\multicolumn{3}{l}{Total number of evaluations: $88 \ 269$} \\ \hline 
+ $x_7$ & $0.1410$ & $0.1452$  \\ \hline
+ $x_8$ & $0.4116$ & $0.4196$  \\ \hline
+ $x_9$ & $0.0851$ & $0.0877$  \\ \hline
+ $x_{10}$ & $0.0043$ & $0.0043$  \\ \hline
+ $x_{11},\dots,x_{15}$ & $0$ & $0$  \\ \hline
+\hline
+\multicolumn{3}{l}{Total number of evaluations: $93 \ 881$} \\ \hline 
 \end{tabular}
@@
 \end{table}
-\begin{table}[!ht]
+
+\begin{figure}[!ht]
+\caption{Boxplots of first-order indices $\underline{S}_u$ for inputs $x_2,x_4,x_5,x_6,x_{10}$ obtained with both Variant $A.a$ and Variant $A.b$.}
+\vspace*{0.2cm}
+\centering
+\includegraphics[width=0.45\textwidth]{wingweight_box.eps}
+\label{boxplots.wing}
+\end{figure}
+
+Tables \ref{res.wing.B} show the results obtained with Variant $B$.
+Variant $B$ does not capture the presence of the inert inputs $x_{11}$, $\dots$, $x_{15}$.
+Their estimated main effects are confused with those of inputs $x_4$, $x_5$, $x_6$,$x_9$ and $x_{10}$.
+However, the drawback of overestimating small first-order indices is balanced by the improvement in terms of number of evaluations.
+
+Overall, each variant captures well the same set of influent inputs identified by Forrester \textit{et al.}
+\begin{table}[t]
 \caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$.}
@@
  input & $\widehat{\underline{S}}_u$ \\ \hline
- $x_1$ & $0.1245$ \\ \hline
- $x_2$ & $0.0042$ \\ \hline
- $x_3$ & $0.2201$ \\ \hline
- $x_4$ & $0.0039$ \\ \hline
- $x_5$ & $0.0035$ \\ \hline
- $x_6$ & $0.0045$ \\ \hline 
+ $x_1$ & $0.1243$ \\ \hline
+ $x_2$ & $0.0035$ \\ \hline
+ $x_3$ & $0.2202$ \\ \hline
+ $x_4$ & $0.0033$ \\ \hline
+ $x_5$ & $0.0021$ \\ \hline
+ $x_6$ & $0.0037$ \\ \hline 
  $x_7$ & $0.1410$ \\ \hline
- $x_8$ & $0.4116$ \\ \hline
- $x_9$ & $0.0850$ \\ \hline
- $x_{10}$ & $0.0042$ \\ \hline
+ $x_8$ & $0.4117$ \\ \hline
+ $x_9$ & $0.0673$ \\ \hline
+ $x_{10}$ & $0.0043$ \\ \hline
+ $x_{11},\dots,x_{15}$ & $\in [6.10^{-4},7.10^{-3}]$ \\ \hline
  \hline
@@
 \end{table}
-(FIGURES)
+
+\subsection{Comparison with Monte Carlo method}
+
+In this section, our procedure is compared to a simpler method based on random sampling and straightforward confidence intervals.
+The bratley \textit{et al.} function is used to compare both approaches.
+The random sampling method corresponds to Saltelli's procedure described in Section \ref{sec:2.2}.
+For a fair comparison, ``Correlation 2'' is used instead of \eqref{first.order.est} to estimate the small main effects of inputs $x_3$, $x_4$, $x_5$ and $x_6$.
+The random sampling method proceeds as follows: each Sobol' index is evaluated with the same number of evaluations used in Variant $A.b$.
+Then, bootstrap confidence intervals are computed.
+
+The results are averaged over $100$ repetitions and compared in Table \ref{compa_MC} to those obtained with Variant $A.b$.
+The comparison is made based on estimation errors and failures rates.
+The column precision corresponds to the average width of the bootstrap confidence interval for the random sampling method.
+
+The main observation is that our procedure performs the best.
+The random sapling method has high failure rates for inputs $x_1$, $x_2$ and slightly worse failure rates than Variant $A.b$ for inputs $x_3$, $x_4$.
+The average precision only falls below the tolerance $\varepsilon=5\cdot10^{-3}$ for inputs $x_5$ and $x_6$.
+Figures \ref{compa_MC_first} and \ref{compa_MC_tot} emphasize the latter observations.
+
+\begin{table}[!ht]
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, $\delta_{\overline{S}_u}$ and failure rates for the random sampling method (MC) and Variant $A.b$ (QMC).}
+\centering
+\begin{tabular}{ccccccc}
+\hline
+ input & procedure & $\delta_{\underline{S}_u}$ & $r_{\delta_{\underline{S}_u}}$ & $\delta_{\overline{S}_u}$ &$r_{\delta_{\overline{S}_u}}$ & precision \\
+\hline
+\multirow{2}{*}{$x_1$} & QMC & $0.0005$ & $0$ & $0.0002$ & $0$ & \multirow{2}{*}{$0.0344$} \\
+& MC & $0.0116$ & $0.75$ & $0.0086$ & $0.67$ & \\
+\hline
+\multirow{2}{*}{$x_2$} & QMC & $0.0006$ & $0$ & $0.0005$ & $0$ & \multirow{2}{*}{$0.0362$} \\
+& MC & $0.0122$ & $0.74$ & $0.0049$ & $0.37$ & \\
+\hline
+\multirow{2}{*}{$x_3$} & QMC & $0.0017$ & $0.02$ & $0.0015$ & $0.01$ & \multirow{2}{*}{$0.007$} \\
+& MC & $0.0020$ & $0.02$ & $0.0030$ & $0.18$ & \\
+\hline
+\multirow{2}{*}{$x_4$} & QMC & $0.0017$ & $0$ & $0.0018$ & $0.02$ & \multirow{2}{*}{$0.0052$} \\
+& MC & $0.0014$ & $0.01$ & $0.0027$ & $0.11$ & \\
+\hline
+\multirow{2}{*}{$x_5$} & QMC & $0.0003$ & $0$ & $0.0016$ & $0.05$ & \multirow{2}{*}{$0.0012$} \\
+& MC & $0.0003$ & $0$ & $0.0011$ & $0.01$ & \\
+\hline
+\multirow{2}{*}{$x_6$} & QMC & $0.0004$ & $0$ & $0.0011$ & $0$ & \multirow{2}{*}{$0.0012$} \\
+& MC & $0.0003$ & $0$ & $0.0010$ & $0$ & \\
+\hline
+\end{tabular}
+\label{compa_MC}
+\end{table}
+
 \begin{figure}[!ht]
-\caption{Boxplots of first-order indices $\underline{S}_u$ for inputs $x_2,x_4,x_5,x_6,x_{10}$ obtained with both Variant $A.a$ and Variant $A.b$.}
+\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method (MC).
+The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
+\centering
 \vspace*{0.2cm}
-\centering
-\includegraphics[width=0.45\textwidth]{wingweight_box.eps}
-\label{boxplots.wing}
+\includegraphics[width=0.4\textwidth]{comp_MC_first.eps}
+\label{compa_MC_first}
 \end{figure}
-\begin{figure}[t]
-\caption{Barplots of the $100$ values taken by the sum of the $c_j$. All values are higher than zero.}
+
+\begin{figure}[!ht]
+\caption{Boxplots of estimation errors $\delta_{\overline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method (MC).
+The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
+\centering
 \vspace*{0.2cm}
-\centering
-\includegraphics[width=0.45\textwidth]{wingweight_cj.eps}
-\label{cj.wing}
-\end{figure}
-
-Comments: Variant A.b is more expansive but guarantee that first-order indices are lower or equal to total-effect indices. At the opposite, Variant A.a fails to guarantee this property.
-
-Variant B requires less evaluations but estimates of small first-order indices are less accurate.
-(TO COMPLETE)
-
-(ALSO TRY LEVEL E MODEL ?)
-}
-
-%\comment{As an academic case example, we will study the wing weight function:
-%\begin{align*}
-%f(\vx)=0.036 x_1^{0.758} & x_2^{0.0035} \left(\frac{x_3}{\cos(x_4)^2}\right)^{0.6} x_5^{0.006} x_6^{0.04}\times \\
-% & \times\left(\frac{100 x_7}{\cos(x_4)}\right)^{-0.3} (x_8 x_9)^{0.49} + x_1 x_10
-%\end{align*}
-%\begin{tabular}{|l|l|}
-%\hline
-%$x_1\in[150, 200]$ & wing area (ft$^2$) \\
-%$x_2\in[220, 300]$ & weight of fuel in the wing (lb) \\
-%$x_3\in[6, 10]$ & aspect ratio \\
-%$x_4\in[-10, 10]$ & quarter-chord sweep (degrees) \\
-%$x_5\in[16, 45]$ & dynamic pressure at cruise (lb/ft$^2$) \\
-%$x_6\in[0.5, 1]$ & taper ratio \\
-%$x_7\in[0.08, 0.18]$ & aerofoil thickness to chord ratio \\
-%$x_8\in[2.5, 6]$ & ultimate load factor \\
-%$x_9\in[1700, 2500]$ & flight design gross weight (lb) \\
-%$x_{10}\in[0.025, 0.08]$ & paint weight (lb/ft$^2$) \\
-%\hline
-%\end{tabular}
-
-%\subsection{Wing weight model}
-%As an academic case example, we will study the payoff function of an arithmetic mean Asian call option.
-For a discretized Brownian motion $\vect{B}=(B_{t_1}, B_{t_2},\dots, B_{t_d})$ at times $t_i=T\times i/d$, the payoff of the option is:
-%
-%\[
-%f_{\rm payoff}(\vect{B}) = \e^{-\rho T}\max\left(\frac{1}{d}\sum_{i=1}^d S_0\e^{(\rho-\sigma^2/2)t_i+\sigma B_{t_i}}-K, 0\right)
-%\]
-%where $T$ is the maturity of the option, $S_0$ is the initial stock price, $\sigma$ the volatility of the stock, $\rho$ the interest rate, and $K$ the strike price.
-%
-%The discretized Brownian motion $\vect{B}$ follows a multivariate normal distribution with mean $\vzero$ and covariance matrix $\mathsf{\Sigma}$, with $\mathsf{\Sigma}_{ij}=\min(t_i,t_j)$.
-If $\vect{Y}\sim N(\vzero,I_d)$, then for any matrix $M$, $M\vect{Y}\sim N(\vzero,\mathsf{\Sigma})$ where $\mathsf{\Sigma}=MM^t$.
-Hence, we can generate the discretized Brownian motion using the inverse normal cumulative distribution function $\phi^{-1}$: $\vect{B}\sim M\phi^{-1}(\vect{X})$ with $\phi^{-1}(\vect{X})=(\phi^{-1}(X_1),\dots,\phi^{-1}(X_d))^t$ and $\vect{X}\sim \mathcal{U}([0,1]^d)$.
-Thus, we can estimate the Sobol' indices over $f_{\rm payoff}(M\phi^{-1}(\vect{X}))$.
-In this particular application, the choice of $M$ is pivotal to reduce the effective dimensionality of the model.
-In this regard, Sobol' indices can help us assess whether we reduce the effective dimensionality.
-We will compare the case with either the Cholesky decomposition or the PCA construction.
-%
-%We propose to analyze the results with averaged Sobol' estimates and averaged total number of evaluations over $100$ repetitions.
-The tolerance $\varepsilon$ and parameters $\ell^*$, $r$ and $\mathfrak{C}(m)$ are set as previously.
-%
-%Tables \ref{res.AsianChol.Aa}, \ref{res.AsianChol.Ab}, and \ref{res.AsianChol.B} show the results when $M$ corresponds to the Cholesky decomposition of $\mathsf{\Sigma}$. 
-%\begin{table}[!ht]
-%\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and total number of evaluations of Variant $A.a$ with Cholesky decomposition.}
-%%\centering
-%%\begin{tabular}{ccccc}
-%%\hline
-%% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
-%% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
-%% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
-%% $x_3$ & $0.0820$ & $37356$ & $0.3150$ & $65536$ \\ \hline
-%% $x_4$ & $0.0408$ & $16742$ & $0.1950$ & $33096$ \\ \hline
-%% $x_5$ & $0.0142$ & $5980$ & $0.0944$ & $16384$ \\ \hline
-%% $x_6$ & $0.0048$ & $1106$ & $0.0257$ & $1654$ \\ \hline \hline
-%\centering
-%\begin{tabular}{ccc}
-%\hline
-% input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
-% $x_1$ & $0.2120$ & $0.5650$  \\ \hline
-% $x_2$ & $0.1370$ & $0.4420$  \\ \hline
-% $x_3$ & $0.0820$ & $0.3150$  \\ \hline
-% $x_4$ & $0.0408$ & $0.1950$  \\ \hline
-% $x_5$ & $0.0142$ & $0.0944$  \\ \hline
-% $x_6$ & $0.0048$ & $0.0257$  \\ \hline \hline
-%\multicolumn{3}{l}{Total number of evaluations: $648 \ 821$} \\ \hline 
-%\end{tabular}
-%\label{res.AsianChol.Aa}
-%\end{table}
-%\begin{table}[!ht]
-%\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with Cholesky decomposition.}
-%%\centering
-%%\begin{tabular}{ccccc}
-%%\hline
-%% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
-%% $x_1$ & $0.2120$ & $131072$ & $0.5650$ & $133693$ \\ \hline
-%% $x_2$ & $0.1370$ & $65536$ & $0.4420$ & $131072$ \\ \hline
-%% $x_3$ & $0.0822$ & $34406$ & $0.3150$ & $65536$ \\ \hline
-%% $x_4$ & $0.0434$ & $13107$ & $0.1950$ & $33423$ \\ \hline
-%% $x_5$ & $0.0169$ & $2371$ & $0.0944$ & $16384$ \\ \hline
-%% $x_6$ & $0.0049$ & $532$ & $0.0259$ & $1577$ \\ \hline \hline
-% \centering
-%\begin{tabular}{ccc}
-%\hline
-% input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$  \\ \hline
-% $x_1$ & $0.2120$ & $0.5650$  \\ \hline
-% $x_2$ & $0.1370$ & $0.4420$ \\ \hline
-% $x_3$ & $0.0822$ & $0.3150$  \\ \hline
-% $x_4$ & $0.0434$ & $0.1950$  \\ \hline
-% $x_5$ & $0.0169$ & $0.0944$  \\ \hline
-% $x_6$ & $0.0049$ & $0.0259$  \\ \hline \hline
-%\multicolumn{3}{l}{Total number of evaluations: $699 \ 487$}\\ \hline 
-%\end{tabular}
-%\label{res.AsianChol.Ab}
-%\end{table}
-%\begin{table}[!ht]
-%\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with Cholesky decomposition.}
-%%\centering
-%%\begin{tabular}{ccc}
-%%\hline
-%% input & $\widehat{\underline{S}}_u$ & $n$ \\ \hline
-%% $x_1$ & $0.2120$ & $131072$ \\ \hline
-%% $x_2$ & $0.1350$ & $129766$ \\ \hline
-%% $x_3$ & $0.0774$ & $62290$ \\ \hline
-%% $x_4$ & $0.0338$ & $49961$ \\ \hline
-%% $x_5$ & $0.0149$ & $48845$ \\ \hline
-%% $x_6$ & $0.0028$ & $17905$ \\ \hline \hline
-% \centering
-%\begin{tabular}{cc}
-%\hline
-% input & $\widehat{\underline{S}}_u$ \\ \hline
-% $x_1$ & $0.2120$ \\ \hline
-% $x_2$ & $0.1350$ \\ \hline
-% $x_3$ & $0.0774$ \\ \hline
-% $x_4$ & $0.0338$ \\ \hline
-% $x_5$ & $0.0149$ \\ \hline
-% $x_6$ & $0.0028$ \\ \hline \hline
-%\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
-%\end{tabular}
-%\label{res.AsianChol.B}
-%\end{table}
-%
-%It turns out that Variant $A.b$ does not perform better than Variant $A.a$.
-Averaged Sobol' estimates are similar but the average total number of model evaluations is slightly worse.
-The explanation is that total effect Sobol' indices require more evaluations than their corresponding first-order indices.
-As such, ``Correlation 2'' falls into case 1) explained in Section \ref{sec:4.2}.
-Variant $B$ shows a drastic improvement on the total number of evaluations with the drawback of a false estimation for input $x_4$.
-Its discrepancy is higher than $\epsilon$ when comparing to the other two variants.
-%
-%
-%Tables \ref{res.AsianPCA.Aa}, \ref{res.AsianPCA.Ab}, and \ref{res.AsianPCA.B} show the results when $M$ corresponds to the PCA decomposition of $\mathsf{\Sigma}$. 
-%
-%\begin{table}[!ht]
-%\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.a$ with PCA decomposition.}
-%\centering
-%\begin{tabular}{ccccc}
-%\hline
-% input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
-% $x_1$ & $0.9800$ & $0.9960$  \\ \hline
-% $x_2$ & $0.0037$ & $0.0172$  \\ \hline
-% $x_3$ & $0.0016$ & $0.0023$  \\ \hline
-% $x_4$ & $0.0014$ & $0.0005$  \\ \hline
-% $x_5$ & $0.0005$ & $0.0001$  \\ \hline
-% $x_6$ & $0.0002$ & $0.0000$ \\ \hline
-% \multicolumn{3}{l}{Total number of evaluations: $396 \ 221$}
-% \\ \hline
-%\end{tabular}
-%\label{res.AsianPCA.Aa}
-%\end{table}
-%
-%\begin{table}[!ht]
-%\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$ with PCA decomposition.}
-%%\centering
-%%\begin{tabular}{ccccc}
-%%\hline
-%% input & $\widehat{\underline{S}}_u$ & $n$ & $\widehat{\overline{S}}_u$ & $n$ \\ \hline
-%% $x_1$ & $0.9800$ & $131072$ & $0.9960$ & $117309$ \\ \hline
-%% $x_2$ & $0.0034$ & $512$ & $0.0172$ & $824$ \\ \hline
-%% $x_3$ & $0.0004$ & $512$ & $0.0023$ & $512$ \\ \hline
-%% $x_4$ & $0.0001$ & $512$ & $0.0005$ & $512$ \\ \hline
-%% $x_5$ & $0.0000$ & $512$ & $0.0001$ & $512$ \\ \hline
-%% $x_6$ & $0.0000$ & $512$ & $0.0000$ & $512$ \\ \hline \hline
-% \centering
-%\begin{tabular}{ccc}
-%\hline
-% input & $\widehat{\underline{S}}_u$ & $\widehat{\overline{S}}_u$ \\ \hline
-% $x_1$ & $0.9800$ &  $0.9960$  \\ \hline
-% $x_2$ & $0.0034$ &  $0.0172$  \\ \hline
-% $x_3$ & $0.0004$ &  $0.0023$  \\ \hline
-% $x_4$ & $0.0001$ &  $0.0005$  \\ \hline
-% $x_5$ & $0.0000$ &  $0.0001$  \\ \hline
-% $x_6$ & $0.0000$ &  $0.0000$  \\ \hline \hline
-%\multicolumn{3}{l}{Total number of evaluations: $398 \ 648$} \\ \hline 
-%\end{tabular}
-%\label{res.AsianPCA.Ab}
-%\end{table}
-%
-%\begin{table}[!ht]
-%\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$ with PCA decomposition.}
-%\centering
-%\begin{tabular}{ccc}
-%\hline
-% input & $\widehat{\underline{S}}_u$  \\ \hline
-% $x_1$ & $0.9800$ \\ \hline
-% $x_2$ & $0.0037$ \\ \hline
-% $x_3$ & $0.0028$ \\ \hline
-% $x_4$ & $0.0029$ \\ \hline
-% $x_5$ & $0.0017$ \\ \hline
-% $x_6$ & $0.0029$ \\ \hline \hline
-%\multicolumn{2}{l}{Total number of evaluations: $262 \ 144$} \\ \hline 
-%\end{tabular}
-%\label{res.AsianPCA.B}
-%\end{table}
-%Variant $A.a$ performs as well as Variant $A.b$ in terms of average total number of evaluations.
-However, Variant $A.a$ is most probably giving worse estimates for the small first-order indices.
-Table \ref{res.AsianPCA.Aa} shows that averaged $\widehat{\underline{S}}_4$ is greater than $\widehat{\overline{S}}_4$, $\widehat{\underline{S}}_5$ greater than $\widehat{\overline{S}}_5$, and $\widehat{\underline{S}}_6$ greater than $\widehat{\overline{S}}_6$, which is inconsistent with the property ${\underline{S}}_u\leq{\overline{S}}_u$.
-Once again, variant $B$ shows an improvement on the total number of evaluations with the drawback of slightly overestimating the small first-order indices.
-%
-%Overall, each variant captures well how the PCA Brownian motion construction reduces the high effective dimensionality of the payoff function, in contrast to the initial Cholesky decomposition.
+\includegraphics[width=0.4\textwidth]{comp_MC_tot.eps}
+\label{compa_MC_tot}
+\end{figure}}
 
@@
 Furthermore, we investigated the use of a recent estimator well-suited to the estimation of small first-order indices using quasi-Monte Carlo methods.
-The efficiency of this estimator, called ``Correlation 2'', was assessed and highlighted on two test functions.
+The efficiency of this estimator, called ``Correlation 2'', was assessed and highlighted on two test functions and an application.
 Overall, the variant combining Saltelli's strategy and ``Correlation 2'' gave the best results, with low failure rates across all indices.
+
+{\color{purple}(Lolo) The precision of our procedure was also compared to a simpler method based on random sampling and straightforward confidence intervals.
+For an identical number of evaluations, our procedure was far more accurate than a random sampling method.
+The origin of the discrepancy observed lies in the use of a more robust error bound.}
+
 \comment{Add that we can consider relative errors and reference ...}

### 2017-02-20 article_review/reviewer_letter.tex
added Section 5.3, reworked Section 5.2, deleted c_j figures

@@
 
-{\color{blue} The new academic application is in dimension $10$.
+{\color{blue} The new academic application is in dimension $15$.
 For higher-dimensional examples, we expect the effective dimension to be much smaller than its nominal dimension.
@@
 To confirm this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling.
-The comparison is carried out for the Bratley test function in Section 5.3.
-Results show that for an equivalent number of evaluations, random methods using confidence intervals are less accurate than our procedure.}
+The comparison is carried out for the bratley \textit{et al.} test function in Section 5.3.
+Results show that for an equivalent number of evaluations, the random sampling method is less accurate than our procedure.}
 
@@
 
-{\color{blue} The ``real case model'' has been replaced with a new one suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections that we agreed with.} 
+{\color{blue} The ``real case model'' has been replaced with a new application as suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections that we agreed with.} 
 \end{itemize}
@@
 $$ x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
-Definition 1 has been reworked to include this property. This solves the issue of having more than one permutation that would rearrange the rows $\vx'_i$ into $\vx_i$. Now, the permutation is unique.
+Definition 1 has been reworked to include this property. This solves the issue of having more than one permutation that would rearrange the rows $\vx'_i$ into $\vx_i$. Now, the permutation is unique.}
 
-Furthermore, a remark was added to specify that in this paper $\mathcal{P}$ and $\mathcal{P}'$ are constructed to avoid the degenerate case: $\forall i, \ \vx'_i=\vx_i$.}
+%Furthermore, a remark was added to specify that in this paper $\mathcal{P}$ and $\mathcal{P}'$ are constructed to avoid the degenerate case: $\forall i, \ \vx'_i=\vx_i$.}
 
@@
 The original statement has been replaced with the assumption that the higher dimensions integrand possesses a higher effective dimension.
-Then, this assumption is tested on each example by plotting the repartition of the sum of the $c_j$ (equation (19)) over the $100$ repeats.
-The sign of the sum tells us if, in average, this assumption is validated across the Sobol' indices.}
+Then, this assumption is tested on each example by comparing the number of evaluations required by each integrand.}
+%plotting the repartition of the sum of the $c_j$ (equation (19)) over the $100$ repeats. The sign of the sum tells us if, in average, this assumption is validated across the Sobol' indices.}
 
@@
 {\color{blue} The Asian option problem has been replaced by the wing weight test function taken from the suggested database.
-Section $5.2$ has been reworked to introduce this new test function.
-Our results are compared to older results obtained by screening approaches (Moon, H.
+Section $5.2$ has been reworked to introduce this new test function.} %Our results are compared to older results obtained by screening approaches (Moon, H.
 (2010)).}

### 2017-02-20 article_review/Manuscript.tex
changes

@@
 However, this procedure requires several model evaluations which are usually expensive.
-Later on, Saltelli \cite{Saltelli} proposed strategies to estimate sets of Sobol' indices at once through the use of a combinatorial formalisms.
-While elegant, these strategies still require a large number of model evaluations.
+Later on, Saltelli \cite{Saltelli} proposed strat\-egies to estimate sets of Sobol' indices at once through the use of a combinatorial formalisms.
+While elegant, these strat\-egies still require a large number of model evaluations.
 A cost efficient alternative to estimate first-order indices was introduced in \cite{Mara}.
@@
 Due to orthogonality, the variance of equation \eqref{anova} leads to the variance decomposition of $f$:
-\[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1]^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
+\[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2,\]
+\[ \sigma_u^2=\int_{[0,1]^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
 From this decomposition, one can define the following two quantities:
@@
 \begin{figure}[!ht]
-\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method (MC).
+\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method.
 The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
@@
 \begin{figure}[!ht]
-\caption{Boxplots of estimation errors $\delta_{\overline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method (MC).
+\caption{Boxplots of estimation errors $\delta_{\overline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method.
 The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}

### 2017-02-20 article_review/Manuscript.tex
Changes on Manuscript

--- 2017-02-20 article_review/Manuscript.tex
@@
 In addition, we consider the \emph{wavenumber} space of non-negative integers $\mathbb{N}_0^d$.
-These non-negative integers will index the frequencies in which we decompose our integrand as a Fourier series.
+These non-negative integers will index the frequencies in which we decompose our integrand as a Walsh series.
 The space $\mathbb{N}_0^d$ is also a group under the digitwise addition:
@@
 \end{equation}
-\comment{To use the error bound \eqref{mapped_error_bound} to design and automatic algorithm would require the knowledge of the Walsh coefficients.
+\comment{The use of the error bound \eqref{mapped_error_bound} to design and automatic algorithm requires the knowledge of the Walsh coefficients.
 To avoid this assumption, we will estimate them via the fast transform obtained using the precomputed function values already used to estimate the mean.
@@
 \comment{The sums $S_m(f)$, $\hS_{\ell,m}(f)$, $\wcS_m(f)$, and $\tS_{\ell,m}(f)$ are different from the normalized Sobol' indices $\underline{S}_u$ and $\ov{$S$}_u$.
-Unfortunately, the notation in articles \cite{HicJim,HicJimLi,JimHic} uses these symbols for the sums which should not be confused with the normalized Sobol' indices.
+Unfortunately, the notation in articles \cite{HicJim,HicJimLi,JimHic} coincides and should not be confused with the normalized Sobol' indices notation.
 
@@
 \end{multline}
-for a fixed $\ell_* \in \mathbb{N}$, $\homega$ and $\wcomega$ two non-negative valued functions with $\lim_{m \to \infty} \wcomega(m) = 0$.
+for a fixed $\ell_* \in \mathbb{N}$, and $\homega$ and $\wcomega$ two non-negative valued functions with $\lim_{m \to \infty} \wcomega(m) = 0$.
 \comment{The decay rate assumptions on the Walsh coefficients are encoded in $\cc$ and controlled by $\homega$ and $\wcomega$.
-First, we assume that $\wcS_m(f)$ bounds $\hS_{\ell,m}(f)$ in some sense, in particular it bounds $\hS_{0,m}(f)$.
+First, we assume that $\wcS_m(f)$ bounds $\hS_{\ell,m}(f)$ through $\homega$, in particular it bounds $\hS_{0,m}(f)$.
 This means that we can use $\wcS_m(f)$ as an indicator of the error bound.
@@
 \label{sec:3.2}
-The idea here is to extend the definition of the error bound (\ref{errbd}) to Sobol' indices.
+In this section we will extend the definition of the error bound (\ref{errbd}) to Sobol' indices.
 To achieve this goal, we consider the two integral formulas of the first-order and total effect Sobol' indices with $|u|=1$:
@@
 Indices $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$.
-If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$, $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.
+If we estimate $\vI$ by $\widehat{\vI}$ with known error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$, $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.
 
@@
 \begin{figure}[!ht]
-\caption{The delimited region on the figure represents the values $\underline{S}_2$ in $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ for the Bratley \textit{et al.} function.
-There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$ and $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
+\caption{The delimited region in the figure represents the possible values of $\underline{S}_2$ for $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ (Bratley \textit{et al.} function).
+There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$, $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
 \centering
@@
 
-Under the assumption that each integrand in $\underline{S}_u$ and $\overline{S}_u$ lies inside $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\widehat{\underline{S}}_u}, \widehat{\underline{S}}_u + \varepsilon_{\widehat{\underline{S}}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\widehat{\overline{S}}_u}, \widehat{\overline{S}}_u + \varepsilon_{\widehat{\overline{S}}_u} \right] .\]
+By construction, under the assumption that each integrand in $\underline{S}_u$ and $\overline{S}_u$ lies inside $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\widehat{\underline{S}}_u}, \widehat{\underline{S}}_u + \varepsilon_{\widehat{\underline{S}}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\widehat{\overline{S}}_u}, \widehat{\overline{S}}_u + \varepsilon_{\widehat{\overline{S}}_u} \right] .\]
 \comment{Because we do not assume the knowledge of the Walsh coefficients, it is hard to verify whether all the integrands lie in $\cc$.
@@
 The function values used to estimate the indices are also used to compute the discrete Walsh coefficients.
-Thus, there are no additional evaluations needed to compute the error bound.
+Thus, there are no additional evaluations required to compute the error bound.
 The only computation cost that could be expensive is the fast Walsh transform.
@@
 \item At an average evaluation time of $1$ microsecond per point, the total evaluation time is about $1$ second.
-\item The fast transform on these values takes around $0.5$ seconds.
+\item The fast transform applied to these values takes around $0.5$ seconds.
 \end{itemize}
+In practice, we focus on models that will take much more than $1$ microsecond to evaluate and hence, the fast transform cost becomes inexpensive.
 }

### 2017-02-20 article_review/Manuscript.tex

--- 2017-02-20 article_review/Manuscript.tex
@@
 \begin{figure}[t]
-\caption{The delimited region on the figure represents the values $\underline{S}_2$ in $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ for the Bratley \textit{et al.} function.
-There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$ and $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
+\caption{The delimited region in the figure represents the possible values of $\underline{S}_2$ for $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ (Bratley \textit{et al.} function).
+There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$, $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
 \centering
@@
 \vspace*{0.2cm}
-\includegraphics[width=0.4\textwidth]{comp_MC_first.eps}
+\includegraphics[width=0.4\textwidth]{comp_mc_first.eps}
 \label{compa_MC_first}
@@
 \vspace*{0.2cm}
-\includegraphics[width=0.4\textwidth]{comp_MC_tot.eps}
+\includegraphics[width=0.4\textwidth]{comp_mc_tot.eps}
 \label{compa_MC_tot}

### 2017-02-20 article_review/reviewer_letter.tex

@@
 Below we have compiled a detailed list of answers (blue text) to the issues raised in the review reports.
-In particular, in light of reviewer's two remark, the Asian option problem was replaced with a new ``real function''.\\
+The corresponding modifications in the manuscript are colored in purple.
+In particular, in light of reviewer's two remark, the Asian option problem was replaced with a new application.\\
 Best regards,\\
@@
 
+\newpage
 \textbf{\large{Reviewer $1$}}
@@
 \end{itemize}
+\vspace*{0.5cm}
 
@@
 
+\newpage
 \textbf{\large{Reviewer $2$}}
@@
 
+\newpage
 \textbf{Minor comments}:

### 2017-02-21 article_review/Manuscript.tex
More changes

@@
 This article addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences.
-The error bound is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition.
+\comment{One reason to use digital sequences is that the numerical integration convergence rates are of $\mathcal{O}(n^{-1+\delta})$ ($n$ being the number of function values) instead of the usual $\mathcal{O}(n^{-1/2})$ for iid Monte Carlo methods.
+In addition,} the error bound in this article is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition.
 We propose a sequential estimation procedure of Sobol' indices using the error bound as our stopping criterion.
@@
 In our framework, we are only interested in single input indices, namely $|u|=1$. The computation of the normalized indices is performed based on the following integral formulas for their numerators:
-{\color{purple}(Lolo)
+{\color{purple}
 \begin{align}
@@
 One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
-{\color{purple}(Lolo)
+{\color{purple}
 \begin{align}
@@
 using for $\sigma^2$:
-{\color{purple} (Lolo)
+{\color{purple} 
 \begin{equation}
@@
 
-{\color{purple} (Lolo) 
+{\color{purple}  
 \begin{definition}
@@
 \]
-where $x_{j\ell}$ and $t_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ component of points $\vx$ and $\vt$,\comment{ i.e.
+where $x_{j\ell}$ and $t_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ component of points $\vx$ and $\vt$, \comment{ i.e.
 \[
@@
 In both cases, regular and normalized indices can be approximated by estimating some integrals,
-{\color{purple}(Lolo)
+{\color{purple}
 \begin{align*}
-\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d}} \left(f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
+\underline{S}_u(\vI) & = \frac{\int_{[0,1]^{2d}} \left(f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}}{\int_{[0,1]^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1]^{d}} f(\vx) d{\vx}\right)^2}, \\ 
 \underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
-\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\
+\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1]^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1]^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1]^{d}} f(\vx) d{\vx}\right)^2}, \\
 \overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
@@
 First, one must fix the tolerance $\epsilon >0$ at which Sobol' indices must be estimated, and set $m=\ell_*+r$, where $\ell_*$ and $r$ are the two hyper-parameters defined in \eqref{conecond}.
-{\color{purple} (Lolo) The choice of $\ell_*$ must be large enough to ensure that each integrand of $\underline{S}_u$ and $\overline{S}_u$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).}
+{\color{purple}  The choice of $\ell_*$ must be large enough to ensure that each integrand of $\underline{S}_u$ and $\overline{S}_u$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).
+Parameter $r$ should also be chosen carefully: larger values of $r$ will imply a smaller error bound and more dependence on smaller Walsh coefficients, while smaller of values of $r$ might incur in aliasing errors.}
 
 Then, one must construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}.
-{\color{purple} (Lolo) This approach iteratively constructs a $2d$-dimensional Sobol' sequence then assigns its first $d$ coordinates to $\mathcal{P}_{m}$ and its last $d$ coordinates to $\mathcal{P}'_{m}$.
+{\color{purple}  This approach iteratively constructs a $2d$-dimensional Sobol' sequence.
+Then, it assigns its first $d$ coordinates to $\mathcal{P}_{m}$ and its last $d$ coordinates to $\mathcal{P}'_{m}$.
 The $2d$-dimensional Sobol' sequence is generated based on the direction numbers found in \cite{Kuo}.
 These direction numbers optimize the two-dimensional projections of the Sobol' sequence.
-Although this is the authors choice, one may choose any other Sobol' construction of $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ as long as the $2d$ dimensions are each generated with different primitive polynomials.
-In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling scheme \cite{HonHic00a,Owe95}.}
+Although this is the authors choice, one may choose any other Sobol' construction for $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ as long as the $2d$ dimensions are each generated with different primitive polynomials.
+In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling \cite{HonHic00a,Owe95}.}
 
@@
 This option is referred as Variant $B$ in Algorithm \ref{recursive.algorithm}.
-{\color{purple} (Lolo) However, in this case, the scrambling applied to both designs must be identical to insure that $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are replicated designs of order one.}
+{\color{purple}  In this case, the scrambling applied to both designs must be identical to ensure that $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are replicated designs of order one.}
 
@@
 \State compute $\widehat{\underline{S}}_u$ and $\widehat{\ov{$S$}}_u$ with formulas (\ref{formula_undersu}) and (\ref{formula_oversu}), and Saltelli's strategy
-\State $bool_u \leftarrow \varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon \ \& \ \varepsilon_{\widehat{\widehat{\overline{S}}}_u} \leq \epsilon$
+\State $bool_u \leftarrow \varepsilon_{\widehat{\underline{S}}_u} \leq \epsilon \ \& \ \varepsilon_{\widehat{\overline{S}}_u} \leq \epsilon$
 \State $m_u \leftarrow m$
@@
 In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices.
-Our aim is to show that the use of ``Correlation 2" in Variant $A$ {\color{purple} (Lolo) improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.} This new estimator is,
+Our aim is to show that the use of ``Correlation 2" in Variant $A$ {\color{purple}  improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.} This new estimator is,
 \begin{equation*}
@@
 \comment{As proposed by Owen in \cite{Owen}, the sample points are $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$.
-For our algorithm, we extend Owen's estimator by replacing the uniform points with a Sobol' sequence in dimension $3d$.
+For our algorithm, we extend Owen's estimator by replacing the uniform points with a scrambled Sobol' sequence in dimension $3d$.
 In either case, this estimator requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.}
@@
 \end{equation}
-{\color{purple} (Lolo) The sign of \eqref{cost.comparison}} indicates whether or not using ``Correlation 2" brings an improvement to Variant $A$. We distinguish two cases :
+{\color{purple}  The sign of \eqref{cost.comparison} indicates whether or not using ``Correlation 2" brings an improvement to Variant $A$.
+A negative sign would mean an improvement.} We distinguish two cases :
 \begin{itemize}
@@
 \end{itemize}
-{\color{purple}(Lolo) We assume that the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$.
-This assumption is tested on the numerical examples presented in Section \ref{sec:5.1} by comparing the number of evaluations required by the two numerators.
+{\color{purple} We assume that the numerator in $\underline{S}_u$ is harder to estimate than the numerator in $\ov{$S$}_u$.
+This assumption is tested in the numerical examples presented in Section \ref{sec:5.1} by comparing the number of evaluations required by $\underline{S}_u$ and $\ov{$S$}_u$.
 
@@
 To overcome this issue, we propose the following alternative for Variant $A$.
-{\color{purple}(Lolo) If at the end of the first iteration $\widehat{\underline{S}}_u$ is smaller than a threshold (in our case $0.1$, as suggested by Owen), the estimator (\ref{first.order.est}) is switched to ``Correlation 2" for this particular $u$.
-Then, a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
-$\mathcal{P''}$ is obtained by assigning and scrambling the next $d$ coordinates of the starting $2d$-dimensional Sobol' sequence.}
+{\color{purple} If at the end of the first iteration $\widehat{\underline{S}}_u$ is smaller than a threshold (in our case $0.1$, as suggested by Owen), then the estimator (\ref{first.order.est}) is switched to ``Correlation 2" for this particular $u$.
+In this case, a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
+$\mathcal{P''}$ can be generated assigning and scrambling the last $d$ coordinates of a $3d$-dimensional Sobol' sequence.}
 
@@
 
-For the two test functions, results of the three variants are compared based on the true estimation errors.
+For the two test functions, the results of the three variants are compared based on the true estimation errors.
 These errors correspond to the absolute difference between the true values and their estimates:
 $$\delta_{\underline{S}_u} = \absolute{\underline{S}_u - \widehat{\underline{S}_u}}, \qquad \delta_{\overline{S}_u} = \absolute{\overline{S}_u - \widehat{\overline{S}_u}}.$$
-{\color{purple} (Lolo) True values of Sobol' indices are estimated with a precision of $10$ digits. For clarity concern, they are rounded in the tables presenting the results.}
-
-We also compare the total number of evaluations of each variant.
-{\color{purple} (Lolo) Results are averaged over $100$ repetitions by applying different scrambling}.
-For each repetition, we fix the tolerance $\varepsilon=5\cdot10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points).
-The algorithm error bound factor described in \eqref{errbd} is set to $\mathfrak{C}(m)=10\times 2^{-m}$.
-
-\comment{For the examples in this section we do not know the true Walsh coefficients of the integrands.
+{\color{purple} The true values of Sobol' indices are estimated with a precision of $10$ digits. For clarity purposes, in the following tables all results are rounded to $4$ digits.}
+
+We also compare the total number of evaluations of each variant to verify the assumption in Section \ref{sec:4.2}.
+{\color{purple}  Results are averaged over $100$ repetitions, each computed with different random scramblings}.
+For all repetitions, we fix the tolerance $\varepsilon=5\cdot 10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points).
+The error bound factor described in \eqref{errbd} is set to $\mathfrak{C}(m)=10\times 2^{-m}$.
+
+\comment{For these examples we do not know the true Walsh coefficients of the integrands.
 Indeed, since the mapping $\tilde{\vk}$ is chosen heuristically, the cone conditions will also depend on each scrambling.
@@
 For this reason, we define the failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$ over the $100$ repetitions.
-These rates are the proportion of the repetitions in which the true estimation errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$.
-When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and at least one integrand ($I_1$, $I_2$, $I_3$, or $I_4$) falls outside the cone \eqref{conecond}.}
-
-%{\color{purple} (Lolo) To test if the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$,
+These rates are the proportion of the repetitions in which the true errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\overline{S}_u} \leq \varepsilon$.
+When $\delta_{\underline{S}_u} > \varepsilon$ or $\delta_{\overline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and at least one integrand ($I_1$, $I_2$, $I_3$, or $I_4$) falls outside the cone \eqref{conecond}.}
+
+%{\color{purple}  To test if the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$,
 
@@
 
-The two classical test functions considered in this article are {\color{purple} (Lolo) a non qMC friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
+The two classical test functions considered in this article are {\color{purple} a non qMC (quasi-Monte Carlo) friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
 The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.} function) and multiplicative (g-function).
@@
 
-{\color{purple} (Lolo)
+{\color{purple} 
 The non qMC friendly version of the g-function is defined as follows:
@@
 \renewcommand{\arraystretch}{1.25}
-{\color{purple}(Lolo) (nouvelles tables et figures)
+{\color{purple} (nouvelles tables et figures)
 \begin{table}[t]
-\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ , $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.a$.}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and $\delta_{\overline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$, and averaged total number of evaluations for Variant $A.a$.}
 \centering
@@
  $x_4$ & $0.0043$ &  $0.0025$ & $0.11$ & $0.0075$ & $0.0004$ & $0$ \\ \hline
- $x_5$ & $4.10^{-5}$ & $0.0003$ & $0$ & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
- $x_6$ & $4.10^{-5}$ & $0.0003$ & $0$  & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
+ $x_5$ & $4\cdot 10^{-5}$ & $0.0003$ & $0$ & $7\cdot 10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
+ $x_6$ & $4\cdot 10^{-5}$ & $0.0003$ & $0$  & $7\cdot 10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
 \multicolumn{4}{l}{Total number of evaluations: $120 \ 638$} & & &\\ \hline 
@@
 \begin{table}[t]
-\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ , $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.b$.}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$  and $\delta_{\overline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$, and average total number of evaluations for Variant $A.b$.}
 \centering
@@
  $x_4$ & $0.0043$ &  $0.0003$ & $0$ & $0.0075$ & $0.0004$ & $0$ \\ \hline
- $x_5$ & $4.10^{-5}$ & $< 10^{-4}$ & $0$ & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
- $x_6$ & $4.10^{-5}$ & $< 10^{-4}$ & $0$  & $7.10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
+ $x_5$ & $4\cdot 10^{-5}$ & $< 10^{-4}$ & $0$ & $7\cdot 10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline
+ $x_6$ & $4\cdot 10^{-5}$ & $< 10^{-4}$ & $0$  & $7\cdot 10^{-5}$ & $< 10^{-4}$ & $0$ \\ \hline \hline
 \multicolumn{4}{l}{Total number of evaluations: $120 \ 832$} & & &\\ \hline 
@@
 
-The main observation is that both approaches give similar results both in terms of estimation errors, failure rates and total number of evaluations.
-The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ {\color{purple} (Lolo) does seem to bring an improvement.
+The main observation is that both approaches give similar results both in terms of estimation errors, failure rates and averaged total number of evaluations.
+The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ {\color{purple}  does seem to bring an improvement.
 In particular, the failure rate for input $x_3$ is reduced to $0$.} We propose to draw boxplots of the estimation errors to further investigate the results.
@@
 As expected, we observe that the use of ``Correlation 2'' in Variant $A.b$ results in lower estimation errors for these four inputs.
-The discrepancy observed does not stand out in Table \ref{res.gfunc.Ab} due to its low magnitude ($10^{-4} \sim 10^{-5}$).
-
-{\color{purple}(Lolo) Table \ref{comparison.gfunc} shows the average number of evaluations performed in Variant $A.a$ to estimate $I_1$, the numerator of $\underline{S}_u$, and $I_2$, the numerator of $\ov{$S$}_u$.
-The column $I_2 > I_1$ indicates the number of times where $I_2$ required more evaluations than $I_1$.
-We observe that $I_2$ never requires more evaluations than $I_1$.
-This seems to indicate that the effective dimension of $I_1$ is higher than $I_2$ for this example.
+The discrepancy observed does not stand out in Table \ref{res.gfunc.Ab} due to its low magnitude ($10^{-4}$ to $10^{-6}$).
+
+{\color{purple} Table \ref{comparison.gfunc} shows the average number of evaluations performed in Variant $A.a$ to estimate $\underline{S}_u$ and $\ov{$S$}_u$.
+The column $N$ indicates the number of times where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$.
+We observe that $\ov{$S$}_u$ never requires more evaluations than $\underline{S}_u$.
 \begin{table}[t]
-\caption{Number of evaluations evaluations performed to estimate $I_1$ and $I_2$ in Variant $A.a$. $N$ is the number of times among the $100$ repeats where $I_2$ required more evaluations than $I_1$}
+\caption{Average number of evaluations performed to estimate $\underline{S}_u$ and $\ov{$S$}_u$ in Variant $A.a$.
+Column $N$ shows the number of times among the $100$ repeats where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$.}
 \centering
@@
 \hline
- input & $I_1$ & $I_2$ & $I_2 > I_1$ \\ \hline
+ input & $\underline{S}_u$ & $\ov{$S$}_u$ & $N$ \\ \hline
  $x_1$ & $32768$ & $32768$ & $0$ \\   \hline
@@
 
-Table \ref{res.gfunc.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.
-The results show that the use of Variant $B$ leads to slightly higher estimation errors than those obtained with Variant $A.a$ or Variant $A.b$.
-However, the total number of evaluations is {\color{purple}half as large}.
+Table \ref{res.gfunc.B} shows the averaged estimation errors $\delta_{\underline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$, and averaged total number of evaluations for Variant $B$.
+Variant $B$ leads to slightly higher estimation errors than those obtained with Variant $A.a$ or Variant $A.b$.
+However, the averaged total number of evaluations is {\color{purple}half as large}.
 As such, this approach remains interesting when one wants to estimate only first-order indices.
 \begin{table}[t]
-\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$, and averaged total number of evaluations for Variant $B$.}
 \centering
@@
  $x_4$ & $0.0043$ &  $0.0016$ & $0$    \\ \hline
- $x_5$ & $4.10^{-5}$ & $0.0034$ & $0$  \\ \hline
- $x_6$ & $4.10^{-5}$ & $0.0035$ & $0$  \\ \hline \hline
+ $x_5$ & $4\cdot 10^{-5}$ & $0.0034$ & $0$  \\ \hline
+ $x_6$ & $4\cdot 10^{-5}$ & $0.0035$ & $0$  \\ \hline \hline
 \multicolumn{4}{l}{Total number of evaluations: $65 \ 536$}\\ \hline 
@@
 $$f(x_1,\dots,x_d)=\sum \limits_{i=1}^{d} (-1)^i \prod \limits_{j=1}^{i} x_j \ .$$
-The importance of each variable $x_j$ depends on their own rank. More explicitly, $x_1$ is more influent than $x_2$ that is respectively more influent than $x_3$ and so on.
-
-As for the g-function, Tables \ref{res.bratley.Aa} and \ref{res.bratley.Ab} show averaged estimation errors and total number of evaluations for Variant $A.a$ and Variant $A.b$.
-\begin{table}[!ht]
-\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.a$.}
+The importance of each variable $x_j$ depends on their own rank. More explicitly, $x_1$ is more influent than $x_2$ which is respectively more influent than $x_3$ and so on.
+
+As for the g-function, Tables \ref{res.bratley.Aa} and \ref{res.bratley.Ab} show averaged estimation errors, failure rates, and averaged total number of evaluations for Variant $A.a$ and Variant $A.b$.
+\begin{table}[t]
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and $\delta_{\overline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$, and averaged total number of evaluations for Variant $A.a$.}
 \centering
@@
 \end{table}
-\begin{table}[!ht]
-\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, $\delta_{\overline{S}_u}$ and total number of evaluations for Variant $A.b$.}
+\begin{table}[t]
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and $\delta_{\overline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$, and averaged total number of evaluations for Variant $A.b$.}
 \centering
@@
 
-Variant $A.b$ gives lower estimation errors and fewer failure rates than Variant $A.a$ on the four small first-indices $\underline{S}_3$, $\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''.
-The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $71\%$ against only $2\%$ for Variant $A.b$.
+Variant $A.b$ gives lower estimation errors and fewer failure rates than Variant $A.a$ on all four small first-indices $\underline{S}_3$, $\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the good performance of ``Correlation 2''.
+The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $78\%$ against only $2\%$ for Variant $A.b$.
 Furthermore, Variant $A.b$ requires less evaluations than Variant $A.a$.
-The boxplots represented in Figure \ref{boxplots.bratley} emphasize the latter observations.
+The boxplots presented in Figure \ref{boxplots.bratley} emphasize the latter observations.
 \begin{figure}[t]
@@
 
-{\color{purple}(Lolo) Table \ref{comparison.bratley} shows the average number of evaluations performed in Variant $A.a$ to estimate $I_1$, the numerator of $\underline{S}_u$, and $I_2$, the numerator of $\ov{$S$}_u$.
-The column $I_2 > I_1$ indicates the number of times among the $100$ repeats where $I_2$ required more evaluations than $I_1$.
+{\color{purple} Table \ref{comparison.bratley} shows the average number of evaluations performed in Variant $A.a$ to estimate $\underline{S}_u$ and $\ov{$S$}_u$.
+The column $N$ indicates the number of times where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$.
+In this case, we observe that $\ov{$S$}_u$ requires more evaluations than $\underline{S}_u$ in only $4$ of the $600$ estimations.
 \begin{table}[t]
-\caption{Number of evaluations evaluations performed to estimate $I_1$ and $I_2$ in Variant $A.a$. $N$ is the number of times where $I_2$ required more evaluations than $I_1$}
+\caption{Average number of evaluations performed to estimate $\underline{S}_u$ and $\ov{$S$}_u$ in Variant $A.a$.
+Column $N$ shows the number of times among the $100$ repeats where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$.}
 \centering
@@
 \hline
- input & $I_1$ & $I_2$ & $I_2 > I_1$ \\ \hline
+ input & $\underline{S}_u$ & $\ov{$S$}_u$ & $N$ \\ \hline
  $x_1$ & $16876$ & $16384$ & $0$ \\  \hline
@@
 \begin{table}[t]
-\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$, and averaged total number of evaluations for Variant $B$.}
 \centering
@@
 \label{res.bratley.B}
-\end{table}
-We observe that $I_2$ almost never requires more evaluations than $I_1$. This seems to indicate that the effective dimension of $I_1$ is also higher than $I_2$ for this example.}
-
-Table \ref{res.bratley.B} shows averaged estimation errors $\delta_{\underline{S}_u}$ and total number of evaluations for Variant $B$.
+\end{table}}
+
+Averaged estimation errors $\delta_{\underline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$, and averaged total number of evaluations for Variant $B$ are shwon in Table \ref{res.bratley.B}.
 The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$.
-Failure rates are similar to those of Variant $A.b$.
-Since the total number of evaluations is close to the one of Variant $A.b$ at the exception of input $x_4$.
-As a conclusion, Variant $B$ does not bring much improvement for this example.
+Failure rates are similar but slightly higher than those of Variant $A.b$.
+Since the averaged total number of evaluations is close to the one of Variant $A.b$,  Variant $B$ does not bring much improvement for this example.
 \bigskip
 
-From the results on these two test functions, the main conclusion is that Variant $A.b$ performs the best.
+From the results of these two test functions, the main conclusion is that Variant $A.b$ performs best.
 This highlights the efficiency of ``Correlation 2'' to estimate small first-order indices with quasi-Monte Carlo methods.
@@
 
-For the case where we are only interested in estimating first-order indices, Variant $B$ should be the best choice as illustrated with the g-function.
+For the case where we are only interested in estimating first-order indices, Variant $B$ could be the best choice as the number of function evaluations is less than for Variants $A.a$ and $A.b$.
 
@@
 
-(Lolo) As an application, we will study the wing weight function introduced by Forrester \textit{et al.} \cite{Forrester} and defined as follows:
+As an application, we will study the wing weight function introduced by Forrester \textit{et al.} \cite{Forrester} and defined as follows:
 \begin{align*}
 f(\vx)=0.036 x_1^{0.758} & x_2^{0.0035} \left(\frac{x_3}{\cos(x_4)^2}\right)^{0.6} x_5^{0.006} x_6^{0.04}\times \\
- & \times\left(\frac{100 x_7}{\cos(x_4)}\right)^{-0.3} (x_8 x_9)^{0.49} + x_1 x_{10}
+ & \times\left(\frac{100 x_7}{\cos(x_4)}\right)^{-0.3} (x_8 x_9)^{0.49} + x_1 x_{10}.
 \end{align*}
-Table \ref{wing_inputs_table} gives the range of variation of each input and their physical representation.
-All inputs are uniformly distributed in their respective ranges.
-To illustrate the performance of our procedure, five additional inert inputs $x_{11}$, $\dots$, $x_{15}$ are added which serve only to add ``noise'' to the sensitivity analysis.
-The inert inputs are all uniformly distributed in $[0,1]$.
-\begin{table}[!ht]
+All inputs are described in Table \ref{wing_inputs_table} including their distribution and their physical representation.
+To illustrate the performance of our procedure, five additional inert inputs $x_{11}$, $\dots$, $x_{15}$ are added to serve only as ``noise'' to the sensitivity analysis.
+\begin{table}[t]
 \caption{Inputs and their ranges of variation. All inputs are uniformly distributed in their respective ranges.}
 \centering
-\begin{tabular}{ccc}
+\begin{tabular}{cll}
 \hline
@@
 
-The motivation of this application is to test if our procedure capture the same set of influent inputs $(x_1,x_3,x_7,x_8,x_9)$ selected by the analysis of Forrester \textit{et al.}.
-
-A second motivation is to compare the performance of each variant ($A.a$, $A.b$ and $B$) on a function where true values of Sobol' indices cannot be computed.
-The comparison is based on averaged Sobol' estimates and averaged total number of evaluations over $100$ repetitions.
+The motivation of this application is to test if our procedure captures the same set of influent inputs $(x_1,x_3,x_7,x_8,x_9)$ selected by the analysis of Forrester \textit{et al.} which are those of value greater than $0.01$.
+
+A second motivation is to compare the performance of each variant ($A.a$, $A.b$ and $B$) on a function where the true values of Sobol' indices are unknown.
+The comparison is based on averaged Sobol' indices estimates and averaged total number of evaluations over $100$ repetitions.
 \bigskip
 
-Tables \ref{res.wing.Aa}, \ref{res.wing.Ab} show the results obtained with Variant $A.a$ and  Variant $A.b$.
+Tables \ref{res.wing.Aa} and \ref{res.wing.Ab} show the results obtained with Variant $A.a$ and  Variant $A.b$.
 Both variants capture well the presence of inert inputs.
-Variant A.b is more expansive but validates the property that first-order indices are lower or equal to total-effect indices.
-At the opposite, Variant A.a fails to guarantee this property for inputs with small main effects: $x_2$, $x_4$, $x_5$, $x_6$.
-This highlights once again the efficiency of ``Correlation 2''.
-The boxplots represented in Figure \ref{boxplots.wing} emphasize the latter observation, Variant $A.b$ provides less variance in the estimates.
-
-\begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and total number of evaluations of Variant $A.a$.}
+Variant $A.b$ is more expansive but validates the property that first-order indices are lower or equal to total-effect indices.
+Nonetheless, Variant A.a fails to guarantee this property for inputs with small main effects: $x_2$, $x_4$, $x_5$, $x_6$.
+Once again, this highlights the efficiency of ``Correlation 2''.
+The boxplots presented in Figure \ref{boxplots.wing} emphasize the latter observation where Variant $A.b$ shows less variance in the estimates.
+
+\begin{table}[t]
+\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$, and averaged total number of evaluations of Variant $A.a$.}
 \centering
@@
 \end{table}
-\begin{table}[!ht]
-\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and total number of evaluations of Variant $A.b$.}
+\begin{table}[t]
+\caption{Averaged values of $\widehat{\underline{S}}_u$, ${\widehat{\overline{S}}_u}$ and averaged total number of evaluations of Variant $A.b$.}
  \centering
@@
 
-\begin{figure}[!ht]
+\begin{figure}[t]
 \caption{Boxplots of first-order indices $\underline{S}_u$ for inputs $x_2,x_4,x_5,x_6,x_{10}$ obtained with both Variant $A.a$ and Variant $A.b$.}
@@
 
-Tables \ref{res.wing.B} show the results obtained with Variant $B$.
-Variant $B$ does not capture the presence of the inert inputs $x_{11}$, $\dots$, $x_{15}$.
-Their estimated main effects are confused with those of inputs $x_4$, $x_5$, $x_6$,$x_9$ and $x_{10}$.
-However, the drawback of overestimating small first-order indices is balanced by the improvement in terms of number of evaluations.
+Table \ref{res.wing.B} shows the results obtained with Variant $B$.
+Variant $B$ does not identify the inputs $x_{11}$, $\dots$, $x_{15}$ as inert inputs.
+However, all the estimated values for these inputs are smaller than the threshold $5\cdot 10^{-3}$.
+The overestimation of the first-order indices for the inert inputs is balanced by the improvement in terms of total number of evaluations.
 
@@
 \begin{table}[t]
-\caption{Averaged values of $\widehat{\underline{S}}_u$ and total number of evaluations of Variant $B$.}
+\caption{Averaged values of $\widehat{\underline{S}}_u$ and averaged total number of evaluations of Variant $B$.}
  \centering
@@
  $x_{10}$ & $0.0043$ \\ \hline
- $x_{11},\dots,x_{15}$ & $\in [6.10^{-4},7.10^{-3}]$ \\ \hline
+ $x_{11},\dots,x_{15}$ & $\in [0,\ 0.005)$ \\ \hline
  \hline
@@
 
-\subsection{Comparison with Monte Carlo method}
-
-In this section, our procedure is compared to a simpler method based on random sampling and straightforward confidence intervals.
-The bratley \textit{et al.} function is used to compare both approaches.
-The random sampling method corresponds to Saltelli's procedure described in Section \ref{sec:2.2}.
-For a fair comparison, ``Correlation 2'' is used instead of \eqref{first.order.est} to estimate the small main effects of inputs $x_3$, $x_4$, $x_5$ and $x_6$.
-The random sampling method proceeds as follows: each Sobol' index is evaluated with the same number of evaluations used in Variant $A.b$.
-Then, bootstrap confidence intervals are computed.
-
-The results are averaged over $100$ repetitions and compared in Table \ref{compa_MC} to those obtained with Variant $A.b$.
-The comparison is made based on estimation errors and failures rates.
-The column precision corresponds to the average width of the bootstrap confidence interval for the random sampling method.
+\subsection{Comparison with the iid Monte Carlo method}
+
+In this section, our procedure is compared to a simpler method based on iid sampling and straightforward confidence intervals.
+This method corresponds to Saltelli's procedure described in Section \ref{sec:2.2} using iid uniform points instead of Sobol' sequences.
+The Bratley \textit{et al.} function is used to compare the iid sampling approach with Variant $A.b$.
+The iid sampling method proceeds as follows: each Sobol' index is evaluated with the same number of evaluations used in Variant $A.b$.
+Then, we compute bootstrap confidence intervals to compare the error bounds.
+
+The results are averaged over $100$ repetitions and compared in Table \ref{compa_MC}.
+The comparison is made based on the estimation errors and failures rates.
+The column \textit{precision} corresponds to the average width of the bootstrap confidence interval for the iid sampling method.
 
@@
 The random sapling method has high failure rates for inputs $x_1$, $x_2$ and slightly worse failure rates than Variant $A.b$ for inputs $x_3$, $x_4$.
-The average precision only falls below the tolerance $\varepsilon=5\cdot10^{-3}$ for inputs $x_5$ and $x_6$.
+The average \textit{precision} values only fall below the tolerance $\varepsilon=5\cdot10^{-3}$ for inputs $x_5$ and $x_6$.
 Figures \ref{compa_MC_first} and \ref{compa_MC_tot} emphasize the latter observations.
 
-\begin{table}[!ht]
-\caption{Averaged estimation errors $\delta_{\underline{S}_u}$, $\delta_{\overline{S}_u}$ and failure rates for the random sampling method (MC) and Variant $A.b$ (QMC).}
+\begin{table}[t]
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and $\delta_{\overline{S}_u}$, and failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$ for the random sampling method (Monte Carlo as MC) and Variant $A.b$ (qMC).}
 \centering
@@
 \hline
-\multirow{2}{*}{$x_1$} & QMC & $0.0005$ & $0$ & $0.0002$ & $0$ & \multirow{2}{*}{$0.0344$} \\
+\multirow{2}{*}{$x_1$} & qMC & $0.0005$ & $0$ & $0.0002$ & $0$ & \multirow{2}{*}{$0.0344$} \\
 & MC & $0.0116$ & $0.75$ & $0.0086$ & $0.67$ & \\
 \hline
-\multirow{2}{*}{$x_2$} & QMC & $0.0006$ & $0$ & $0.0005$ & $0$ & \multirow{2}{*}{$0.0362$} \\
+\multirow{2}{*}{$x_2$} & qMC & $0.0006$ & $0$ & $0.0005$ & $0$ & \multirow{2}{*}{$0.0362$} \\
 & MC & $0.0122$ & $0.74$ & $0.0049$ & $0.37$ & \\
 \hline
-\multirow{2}{*}{$x_3$} & QMC & $0.0017$ & $0.02$ & $0.0015$ & $0.01$ & \multirow{2}{*}{$0.007$} \\
+\multirow{2}{*}{$x_3$} & qMC & $0.0017$ & $0.02$ & $0.0015$ & $0.01$ & \multirow{2}{*}{$0.007$} \\
 & MC & $0.0020$ & $0.02$ & $0.0030$ & $0.18$ & \\
 \hline
-\multirow{2}{*}{$x_4$} & QMC & $0.0017$ & $0$ & $0.0018$ & $0.02$ & \multirow{2}{*}{$0.0052$} \\
+\multirow{2}{*}{$x_4$} & qMC & $0.0017$ & $0$ & $0.0018$ & $0.02$ & \multirow{2}{*}{$0.0052$} \\
 & MC & $0.0014$ & $0.01$ & $0.0027$ & $0.11$ & \\
 \hline
-\multirow{2}{*}{$x_5$} & QMC & $0.0003$ & $0$ & $0.0016$ & $0.05$ & \multirow{2}{*}{$0.0012$} \\
+\multirow{2}{*}{$x_5$} & qMC & $0.0003$ & $0$ & $0.0016$ & $0.05$ & \multirow{2}{*}{$0.0012$} \\
 & MC & $0.0003$ & $0$ & $0.0011$ & $0.01$ & \\
 \hline
-\multirow{2}{*}{$x_6$} & QMC & $0.0004$ & $0$ & $0.0011$ & $0$ & \multirow{2}{*}{$0.0012$} \\
+\multirow{2}{*}{$x_6$} & qMC & $0.0004$ & $0$ & $0.0011$ & $0$ & \multirow{2}{*}{$0.0012$} \\
 & MC & $0.0003$ & $0$ & $0.0010$ & $0$ & \\
@@
 
-\begin{figure}[!ht]
+\begin{figure}[t]
 \caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method.
@@
 
-\begin{figure}[!ht]
+\begin{figure}[t]
 \caption{Boxplots of estimation errors $\delta_{\overline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method.
@@
 
-{\color{purple}(Lolo) The precision of our procedure was also compared to a simpler method based on random sampling and straightforward confidence intervals.
-For an identical number of evaluations, our procedure was far more accurate than a random sampling method.
+{\color{purple} The precision of our procedure was also compared to a simpler method based on random sampling and straightforward confidence intervals.
+For an identical number of evaluations, our procedure was far more accurate than an iid sampling method.
 The origin of the discrepancy observed lies in the use of a more robust error bound.}
 
-\comment{Add that we can consider relative errors and reference ...}
-
 As a future project, the same estimators and algorithms can be designed for rank-1 lattices using the results in \cite{JimHic}, and noticing that rank-1 lattices of the same size are also replicated designs of order 1.
+In addition, in view of the results from \cite{HicJimLi}, one can also include the hybrid error tolerance criterion in these algorithms.
 
@@
 The authors thank Fred J.
-Hickernell and Cl\'ementine Prieur for initiating this collaborative work and Elise Arnaud for her proofreading.
+Hickernell and Cl\'ementine Prieur for initiating this collaborative work, and Elise Arnaud for her proofreading.
 The authors are grateful to Stephen Joe, Frances Y.

### 2017-02-21 article_review/reviewer_letter.tex
More changes

@@
 To confirm this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling.
-The comparison is carried out for the bratley \textit{et al.} test function in Section 5.3.
+The comparison is carried out for the Bratley \textit{et al.} test function in Section 5.3.
 Results show that for an equivalent number of evaluations, the random sampling method is less accurate than our procedure.}
@@
 
-\answer{As pointed out by the reviewer, some clarification was needed in this paragraph.
-We indicated that we extend the use of  Owen's estimator by using Sobol' sequences instead of iid random points.}
+\answer{As pointed out by the reviewer, some clarification was needed in this paragraph. We indicated that we extend  Owen's estimator by using Sobol' sequences instead of iid random points.}
 
@@
 
-{\color{blue} We agree with the reviewer that the effective dimension of the $2d-1$ integrand might be lower than the $d+1$ integrand.
+{\color{blue} We agree with the reviewer that the effective dimension of the $2d$ integrand in $I_1$ might be lower than the $d+1$ integrand in $I_2$.
 However, estimating the effective dimension of each integrand already requires a large number of model evaluations (\textit{c.f.} Wang.
@@
 Since evaluating the effective dimension is not in the scope of this paper, we propose the following.
-The original statement has been replaced with the assumption that the higher dimensions integrand possesses a higher effective dimension.
-Then, this assumption is tested on each example by comparing the number of evaluations required by each integrand.}
+The original statement has been replaced with the assumption that the integrand in $I_1$ is harder to estimate than the integrand in $I_2$.
+Then, this assumption is tested on each example by comparing the number of evaluations required to estimate $I_1$ vs $I_2$.
+This is a reasonable assumption since $I_1$ contains a factor $f(\vx)f(\vx')$ (not appearing in $I_2$) which could increase the effective dimension of its homologous $f(\vx)$.
+While it is true that in QMC the nominal dimension might not be very telling, this happens in particular cases such as RKHS with dimension weights satisfying some specific properties.
+Since for Sobol' indices we consider integrands resulting from products of the same function with different independent inputs, considering the original RKHS might not be enough and the resulting effective dimension might increase.}
 %plotting the repartition of the sum of the $c_j$ (equation (19)) over the $100$ repeats. The sign of the sum tells us if, in average, this assumption is validated across the Sobol' indices.}

### 2017-02-21 article_review/Manuscript.tex
minor changes

@@
 
-\newcommand{\comment}[1]{{\color{cyan} #1 }}
+\newcommand{\comment}[1]{{\color{purple} #1 }}
 % Insert the name of "your journal" with
@@
 The original estimation procedure is due to Sobol' \cite{Sobol'}.
-However, this procedure requires several model evaluations which are usually expensive.
+\break However, this procedure requires several model evaluations which are usually expensive.
 Later on, Saltelli \cite{Saltelli} proposed strat\-egies to estimate sets of Sobol' indices at once through the use of a combinatorial formalisms.
@@
 In our framework, we are only interested in single input indices, namely $|u|=1$. The computation of the normalized indices is performed based on the following integral formulas for their numerators:
-{\color{purple}
 \begin{align}
@@
 \end{align}
-}
 while variance and mean of $f$ are evaluated as:
@@
 One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
-{\color{purple}
 \begin{align}
@@
 \end{align}
-}
 using for $\sigma^2$:
@@
 The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ {\color{purple}according} to $u$.
-While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input space dimension.
+While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input \break space dimension.
 
@@
 In both cases, regular and normalized indices can be approximated by estimating some integrals,
-{\color{purple}
 \begin{align*}
@@
 \end{align*}
-}
 where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values.
@@
 Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp.
-$\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp.
+$\overline{S}_u(\vI)$) is done through \break maximizing the numerator $I_1$ (resp.
 $I_2$) and minimizing the denominator $I_3-I_4^2$.
@@
 \centering
-\includegraphics[width=.5\textwidth]{estimator_3d_small.eps}
+\includegraphics[width=.45\textwidth]{estimator_3d_small.eps}
 \label{fig:1}       % Give a unique label
@@
 
-\comment{For this article, we assumed that evaluating the model is expensive.
+\comment{It is important to note that the function evaluations performed to estimate the Sobol' indices are also used to compute the discrete Walsh coefficients.
+As a result, no additional function evaluations is required to compute the error bound.
+The only computation cost that could be expensive is the fast Walsh transform.
+However, the fast transform cost becomes inexpensive when dealing with models that will take much more than $1$ microsecond to evaluate.}
+%For this article, we assumed that evaluating the model is expensive.
 Hence, to study the cost we will focus on the number of function evaluations needed to estimate the indices.
@@
 However, on a regular laptop, if we consider an extreme case of obtaining $2^{20}$ model values ($\approx$ one million points):
-\begin{itemize}
-\item At an average evaluation time of $1$ microsecond per point, the total evaluation time is about $1$ second.
-\item The fast transform applied to these values takes around $0.5$ seconds.
-\end{itemize}
-In practice, we focus on models that will take much more than $1$ microsecond to evaluate and hence, the fast transform cost becomes inexpensive.
-}
+%\begin{itemize}
+%\item At an average evaluation time of $1$ microsecond per point, the total evaluation time is about $1$ second.
+%\item The fast transform applied to these values takes around $0.5$ seconds.
+%\end{itemize}
+%In practice, we focus on models that will take much more than $1$ microsecond to evaluate and hence, the fast transform cost becomes inexpensive.
+%}
 
@@
 If all $m_u$ are equal, the cost of Variant $A$ becomes $2^{m^\star}(d+2)$ and we recover the cost specified in Theorem \ref{saltelli.theorem} with $n=2^{m^\star}$.
-
 If Variant $B$ is selected, the cost of our algorithm equals $2 \times 2^{m^{\star}}$.
@@
 \end{equation*}
-\comment{As proposed by Owen in \cite{Owen}, the sample points are $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$.
-For our algorithm, we extend Owen's estimator by replacing the uniform points with a scrambled Sobol' sequence in dimension $3d$.
+\comment{As proposed by Owen in \cite{Owen}, the sample points are \break $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$.
+For our algorithm, we extend \break Owen's estimator by replacing the uniform points with a scrambled Sobol' sequence in dimension $3d$.
 In either case, this estimator requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.}
@@
 The two classical test functions considered in this article are {\color{purple} a non qMC (quasi-Monte Carlo) friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
-The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.} function) and multiplicative (g-function).
+The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.}) and multiplicative (g-function).
 
@@
 Table \ref{res.gfunc.Ab} shows the same results obtained with Variant $A.b$.
+
+The main observation is that both approaches give similar results both in terms of estimation errors, failure rates and averaged total number of evaluations.
+The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ {\color{purple}  does seem to bring an improvement.
+In particular, the failure rate for input $x_3$ is reduced to $0$.} We propose to draw boxplots of the estimation errors to further investigate the results.
+\bigskip
+
+Figure \ref{boxplots.gfunc} shows boxplots of the $100$ estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$.
+The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.As expected, we observe that the use of ``Correlation 2'' in Variant $A.b$ results in lower estimation errors for these four inputs.
+The discrepancy observed does not stand out in Table \ref{res.gfunc.Ab} due to its low magnitude ($10^{-4}$ to $10^{-6}$).
+
+\setlength{\tabcolsep}{5.5pt}
 \renewcommand{\arraystretch}{1.25}
-{\color{purple} (nouvelles tables et figures)
 \begin{table}[t]
@@
 \label{res.gfunc.Ab}
-\end{table}}
-
-The main observation is that both approaches give similar results both in terms of estimation errors, failure rates and averaged total number of evaluations.
-The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ {\color{purple}  does seem to bring an improvement.
-In particular, the failure rate for input $x_3$ is reduced to $0$.} We propose to draw boxplots of the estimation errors to further investigate the results.
-
-Figure \ref{boxplots.gfunc} shows boxplots of the $100$ estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$.
-The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.
+\end{table}
 \begin{figure}[t]
@@
 
-As expected, we observe that the use of ``Correlation 2'' in Variant $A.b$ results in lower estimation errors for these four inputs.
-The discrepancy observed does not stand out in Table \ref{res.gfunc.Ab} due to its low magnitude ($10^{-4}$ to $10^{-6}$).
-
-{\color{purple} Table \ref{comparison.gfunc} shows the average number of evaluations performed in Variant $A.a$ to estimate $\underline{S}_u$ and $\ov{$S$}_u$.
-The column $N$ indicates the number of times where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$.
-We observe that $\ov{$S$}_u$ never requires more evaluations than $\underline{S}_u$.
+{\color{purple} Table \ref{comparison.gfunc} shows the average number of evaluations performed in Variant $A.a$ to estimate $\underline{S}_u$ and $\overline{S}_u$.
+The column $N$ indicates the number of times where $\overline{S}_u$ required more evaluations than $\underline{S}_u$.
+We observe that $\overline{S}_u$ never requires more evaluations than $\underline{S}_u$.
 \begin{table}[t]
-\caption{Average number of evaluations performed to estimate $\underline{S}_u$ and $\ov{$S$}_u$ in Variant $A.a$.
-Column $N$ shows the number of times among the $100$ repeats where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$.}
+\caption{Average number of evaluations performed to estimate $\underline{S}_u$ and $\overline{S}_u$ in Variant $A.a$.
+Column $N$ shows the number of times among the $100$ repeats where $\overline{S}_u$ required more evaluations than $\underline{S}_u$.}
 \centering
@@
 The column $N$ indicates the number of times where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$.
-In this case, we observe that $\ov{$S$}_u$ requires more evaluations than $\underline{S}_u$ in only $4$ of the $600$ estimations.
+In this case, we observe that $\ov{$S$}_u$ requires more evaluations than $\underline{S}_u$ in only $4$ of the $100$ estimations.
 \begin{table}[t]
-\caption{Average number of evaluations performed to estimate $\underline{S}_u$ and $\ov{$S$}_u$ in Variant $A.a$.
-Column $N$ shows the number of times among the $100$ repeats where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$.}
+\caption{Average number of evaluations performed to estimate $\underline{S}_u$ and $\overline{S}_u$ in Variant $A.a$.
+Column $N$ shows the number of times among the $100$ repeats where $\overline{S}_u$ required more evaluations than $\underline{S}_u$.}
 \centering
@@
 \hline
- input & $\underline{S}_u$ & $\ov{$S$}_u$ & $N$ \\ \hline
+ input & $\underline{S}_u$ & $\overline{S}_u$ & $N$ \\ \hline
  $x_1$ & $16876$ & $16384$ & $0$ \\  \hline
@@
 Variant $A.b$ is more expansive but validates the property that first-order indices are lower or equal to total-effect indices.
-Nonetheless, Variant A.a fails to guarantee this property for inputs with small main effects: $x_2$, $x_4$, $x_5$, $x_6$.
+On the other hand, Variant A.a fails to guarantee this property for inputs with small main effects: $x_2$, $x_4$, $x_5$, $x_6$.
 Once again, this highlights the efficiency of ``Correlation 2''.
@@
 
-In this section, our procedure is compared to a simpler method based on iid sampling and straightforward confidence intervals.
+In this section, our procedure is compared to a simpler \break method based on iid sampling and straightforward confidence intervals.
 This method corresponds to Saltelli's procedure described in Section \ref{sec:2.2} using iid uniform points instead of Sobol' sequences.
@@
 Then, we compute bootstrap confidence intervals to compare the error bounds.
+The confidence levels of the bootstrap intervals are set to $95\%$.
+The bounds are respectively the $2.5\%$ and $97.5\%$ quantile of the bootstrap sample.
 
@@
 The main observation is that our procedure performs the best.
-The random sapling method has high failure rates for inputs $x_1$, $x_2$ and slightly worse failure rates than Variant $A.b$ for inputs $x_3$, $x_4$.
+The random sampling method has high failure rates for inputs $x_1$, $x_2$ and slightly worse failure rates than Variant $A.b$ for inputs $x_3$, $x_4$.
 The average \textit{precision} values only fall below the tolerance $\varepsilon=5\cdot10^{-3}$ for inputs $x_5$ and $x_6$.
@@
 The authors thank Fred J.
-Hickernell and Cl\'ementine Prieur for initiating this collaborative work, and Elise Arnaud for her proofreading.
+Hickernell and \break Cl\'ementine Prieur for initiating this collaborative work, and Elise \break Arnaud for her proofreading.
 The authors are grateful to Stephen Joe, Frances Y.

### 2017-02-21 article_review/Manuscript.tex
Minor changes

--- 2017-02-21 article_review/Manuscript.tex
@@
 The comparison is made based on the estimation errors and failures rates.
-The column \textit{precision} corresponds to the average width of the bootstrap confidence interval for the iid sampling method.
+The column \textit{precision} corresponds to the width of the bootstrap confidence interval for the iid sampling method.
 
@@
 
-{\color{purple} The precision of our procedure was also compared to a simpler method based on random sampling and straightforward confidence intervals.
-For an identical number of evaluations, our procedure was far more accurate than an iid sampling method.
+{\color{purple} The precision of our procedure was also compared to a simpler method based on iid sampling and straightforward confidence intervals.
+For an identical number of evaluations, our procedure was far more accurate than the iid sampling method.
 The origin of the discrepancy observed lies in the use of a more robust error bound.}

### 2017-02-21 article_review/Manuscript.tex
Legend random->iid

@@
 \comment{It is important to note that the function evaluations performed to estimate the Sobol' indices are also used to compute the discrete Walsh coefficients.
-As a result, no additional function evaluations is required to compute the error bound.
+As a result, no additional function evaluations are required to compute the error bound.
 The only computation cost that could be expensive is the fast Walsh transform.
-However, the fast transform cost becomes inexpensive when dealing with models that will take much more than $1$ microsecond to evaluate.}
+However, the fast transform cost becomes inexpensive when dealing with time consuming models.}
 %For this article, we assumed that evaluating the model is expensive.
@@
 
-The motivation of this application is to test if our procedure captures the same set of influent inputs $(x_1,x_3,x_7,x_8,x_9)$ selected by the analysis of Forrester \textit{et al.} which are those of value greater than $0.01$.
+The motivation of this application is to test if our procedure captures the same set of influent inputs $(x_1,x_3,x_7,x_8,x_9)$ selected by the analysis of Forrester \textit{et al.} which are those of value greater than $0.05$.
 
@@
 Variant $A.b$ is more expansive but validates the property that first-order indices are lower or equal to total-effect indices.
-On the other hand, Variant A.a fails to guarantee this property for inputs with small main effects: $x_2$, $x_4$, $x_5$, $x_6$.
+Conversely, Variant A.a fails to guarantee this property for inputs with small main effects: $x_2$, $x_4$, $x_5$, $x_6$.
 Once again, this highlights the efficiency of ``Correlation 2''.
@@
 \begin{table}[t]
-\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and $\delta_{\overline{S}_u}$, and failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$ for the random sampling method (Monte Carlo as MC) and Variant $A.b$ (qMC).}
+\caption{Averaged estimation errors $\delta_{\underline{S}_u}$ and $\delta_{\overline{S}_u}$, and failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$ for the iid sampling method (Monte Carlo as MC) and Variant $A.b$ (qMC).}
 \centering
@@
 \begin{figure}[t]
-\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method.
+\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.b$ and the iid sampling method.
 The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
@@
 \begin{figure}[t]
-\caption{Boxplots of estimation errors $\delta_{\overline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method.
+\caption{Boxplots of estimation errors $\delta_{\overline{S}_u}$ obtained with both Variant $A.b$ and the iid sampling method.
 The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}

### 2017-05-16 article_review2.0/Manuscript.tex
new repo for revision

--- 2017-02-21 article_review/Manuscript.tex
@@
 In the field of sensitivity analysis, Sobol' indices are sensitivity measures widely used to assess the importance of inputs of a model to its output.
-The estimation of these indices is often performed {\color{purple}through} Monte Carlo or quasi-Monte Carlo methods.
+The estimation of these indices is often performed through Monte Carlo or quasi-Monte Carlo methods.
 A notable method is the replication procedure that estimates first-order indices at a reduced cost in terms of number of model evaluations.
@@
 This article addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences.
-\comment{One reason to use digital sequences is that the numerical integration convergence rates are of $\mathcal{O}(n^{-1+\delta})$ ($n$ being the number of function values) instead of the usual $\mathcal{O}(n^{-1/2})$ for iid Monte Carlo methods.
-In addition,} the error bound in this article is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition.
+One reason to use digital sequences is that the numerical integration convergence rates \comment{can be} $\mathcal{O}(n^{-1+\delta})$ ($n$ being the number of function values) instead of the usual $\mathcal{O}(n^{-1/2})$ for iid Monte Carlo methods.
+In addition, the error bound in this article is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition.
 We propose a sequential estimation procedure of Sobol' indices using the error bound as our stopping criterion.
@@
 Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of $f$.
-We assume that $f$ is in some subset of $\in \mathbb{L}^2(\cube)$ for which $f(\vx)$ is defined for all $\vx\in\cube$, and $\mathcal{D}=\{1,\dots,d\}$ the set of dimension indexes.
+We assume that $f$ is in some subset of $\mathbb{L}^2(\cube)$ for which $f(\vx)$ is defined for all $\vx\in\cube$, and $\mathcal{D}=\{1,\dots,d\}$ the set of dimension indexes.
 %The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
@@
 using for $\sigma^2$:
-{\color{purple} 
+\comment{\begin{equation}
+ \widehat{\sigma}^2 = \frac{1}{2(n-1)} \sum \limits_{i=0}^{n-1} \left[\left( f(\vx_i) - \widehat{\mu}\right)^2 + \left( f(\vx'_i) - \widehat{\mu}\right)^2\right],
+ \end{equation}
+with
 \begin{equation}
- \widehat{\sigma}^2 = \frac{1}{n-1} \sum \limits_{i=0}^{n-1} \left( f(\vx_i) - \widehat{\mu}\right)^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
+\widehat{\mu} =  \frac{1}{2n} \sum \limits_{i=0}^{n-1} \left[ f(\vx_i)+f(\vx'_i)\right].
 \label{mu.est}
-\end{equation}
-}
+\end{equation}}
+
 Then, the Sobol' indices estimators are:
@@
 
-The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ {\color{purple}according} to $u$.
+The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ according to $u$.
 While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input \break space dimension.
@@
 The notion of replicated designs was first introduced by McKay through his replicated Latin Hypercubes in \cite{McKay}.
-In order to apply this definition to other types of points, in \cite{GJAHMP} we generalized this notion to the following.
-
-{\color{purple}  
+In order to apply this definition to other types of points, \comment{we use the generalization from \cite{GJAHMP}.}
+
 \begin{definition}
@@
 \end{definition}
-}
 
@@
 Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) by using $y'_{\pi_u(i)}$ instead of $f(\vx_{i,u}:{\vx'}_{i,-u})$ without requiring further model evaluations for each $u$.
-This estimation method has been studied deeply and generalized in Tissot et al.
-\cite{Tissot} to the case of closed second-order indices.
+This estimation method has been studied deeply and generalized in \comment{Tissot and Prieur} \cite{Tissot} to the case of closed second-order indices.
 In the following we will refer to this method as the replication procedure.
@@
 A practical problem concerning the estimation of these indices is how large to choose the number of evaluations to ensure that Sobol' estimates are accurate enough.
-Asymptotical results show that Sobol' estimates are normally distributed (\cite[Proposition 2.2]{Janon}, \cite[Proposition 3.5]{Tissot}).
+\comment{Asymptotic} results show that Sobol' estimates are normally distributed (\cite[Proposition 2.2]{Janon}, \cite[Proposition 3.5]{Tissot}).
 As a consequence, errors can be estimated through confidence intervals.
@@
 
-We will assume that we have an embedded sequence of digital nets \comment{in $\cube$, base $b$ and dimension d} as described in \cite[Sec. 2-3]{HicJim},
+We will assume that we have an embedded sequence of digital nets in $\cube$, base $b$ and dimension \comment{$d$} as described in \cite[Sec. 2-3]{HicJim},
 \begin{equation}\label{embedded_digital}
@@
 \end{equation}
-\comment{The Sobol' sequence is an example of a digital net in base two satisfying \eqref{embedded_digital}, which in dimension one corresponds to: $\mathcal{P}_0=\{0\}$, $\mathcal{P}_1=\{0,0.5\}$, $\mathcal{P}_2=\{0,0.5,0.25,0.75\}$, $\mathcal{P}_3=\{0,0.5,0.25,0.75,0.125,0.625,0.375,0.875\}$,...}
-
-\comment{For this sequence of digital nets,} each $\mathcal{P}_m$ has a group structure under the digitwise addition:
+The Sobol' sequence is an example of a digital net in base two satisfying \eqref{embedded_digital}, which in dimension one corresponds to: $\mathcal{P}_0=\{0\}$, $\mathcal{P}_1=\{0,0.5\}$, $\mathcal{P}_2=\{0,0.5,0.25,0.75\}$, $\mathcal{P}_3=\{0,0.5,0.25,0.75,0.125,0.625,0.375,0.875\}$,...
+
+For this sequence of digital nets, each $\mathcal{P}_m$ has a group structure under the digitwise addition:
 \[
@@
 \]
-where $x_{j\ell}$ and $t_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ component of points $\vx$ and $\vt$, \comment{ i.e.
+where $x_{j\ell}$ and $t_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ component of points $\vx$ and $\vt$, i.e.
 \[
@@
 \]
-}
+
 To relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the link between any digital net and the \emph{wavenumber} space.
@@
 4.1]{HicJim} we proposed an ordering of the \emph{wavenumbers} $\tilde{\vk}(\cdot):\naturals_0\rightarrow\naturals_0^d$.
-\comment{This ordering $\tilde{\vk}$ is a one-to-one and onto mapping between $\naturals_0$ and $\naturals_0^d$.
+This ordering $\tilde{\vk}$ is a one-to-one and onto mapping between $\naturals_0$ and $\naturals_0^d$.
 Thus, we can identify each $\vk\in\naturals_0^d$ with one $\kappa\in\naturals_0$ such that $\tilde{\vk}(\kappa)=\vk$.
@@
 It also ensures that $\mathcal{P}_m^\perp\setminus\{\vzero\}=\{\tilde{\vk}(\lambda b^m)\}_{\lambda=1}^\infty$.
-If we identify $\hf_{\kappa}=\hf_{\tilde{\vk}(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,}
+If we identify $\hf_{\kappa}=\hf_{\tilde{\vk}(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,
 \begin{equation}\label{mapped_error_bound}
@@
 \end{equation}
-\comment{The use of the error bound \eqref{mapped_error_bound} to design and automatic algorithm requires the knowledge of the Walsh coefficients.
+The use of the error bound \eqref{mapped_error_bound} to design \comment{an} automatic algorithm requires the knowledge of the Walsh coefficients.
 To avoid this assumption, we will estimate them via the fast transform obtained using the precomputed function values already used to estimate the mean.
-We will refer to the discrete coefficients as $\tf_{m,\kappa}$,}
+We will refer to the discrete coefficients as $\tf_{m,\kappa}$,
 \[
@@
 \]
-\comment{As shown in \cite[Sec. 3]{HicJim}, the error of estimating the true coefficients using the discrete coefficients can be measured,
+As shown in \cite[Sec. 3]{HicJim}, the error of estimating the true coefficients using the discrete coefficients can be measured,
 \begin{equation}\label{discrite_true_relationship}
-\tf_{m,\kappa} = \hf_\kappa + \sum_{\lambda=1}^{\infty} \hf_{\kappa + \lambda b^m}, \qquad \text{ for all } \kappa\in\naturals_0,
+\tf_{m,\kappa} = \hf_\kappa + \sum_{\lambda=1}^{\infty} \hf_{\kappa + \lambda b^m}, \qquad \text{ for all } \kappa\in\naturals_0.
 \end{equation}
-However, since there are at most $b^m$ distinct values of $\tf_{m,\kappa}$, we require some assumptions on the decay rate of $\hf_{\kappa}$ to transform \eqref{mapped_error_bound} into a new error bound in terms of the discrete coefficients.}
+However, since there are at most $b^m$ distinct values of $\tf_{m,\kappa}$, we require some assumptions on the decay rate of $\hf_{\kappa}$ to transform \eqref{mapped_error_bound} into a new error bound in terms of the discrete coefficients.
 
@@
 \end{align*}
-\comment{The sums $S_m(f)$, $\hS_{\ell,m}(f)$, $\wcS_m(f)$, and $\tS_{\ell,m}(f)$ are different from the normalized Sobol' indices $\underline{S}_u$ and $\ov{$S$}_u$.
+The sums $S_m(f)$, $\hS_{\ell,m}(f)$, $\wcS_m(f)$, and $\tS_{\ell,m}(f)$ are different from the normalized Sobol' indices $\underline{S}_u$ and $\ov{$S$}_u$.
 Unfortunately, the notation in articles \cite{HicJim,HicJimLi,JimHic} coincides and should not be confused with the normalized Sobol' indices notation.
@@
 Note that from these sums, we can only observe $\tS_{\ell,m}(f)$.
-}
 
@@
 for a fixed $\ell_* \in \mathbb{N}$, and $\homega$ and $\wcomega$ two non-negative valued functions with $\lim_{m \to \infty} \wcomega(m) = 0$.
-\comment{The decay rate assumptions on the Walsh coefficients are encoded in $\cc$ and controlled by $\homega$ and $\wcomega$.
+The decay rate assumptions on the Walsh coefficients are encoded in $\cc$ and controlled by $\homega$ and $\wcomega$.
 First, we assume that $\wcS_m(f)$ bounds $\hS_{\ell,m}(f)$ through $\homega$, in particular it bounds $\hS_{0,m}(f)$.
@@
 One only needs to choose the appropriate $r$: larger values of $r$ will imply a smaller error bound but more dependence on smaller Walsh coefficients.
-Finally, we can write the error bound in terms of $\tS_{\ell,m}(f)$ instead of $\wcS_m(f)$ by using \eqref{discrite_true_relationship}.} With this reasoning, in \cite[Sec.
+Finally, we can write the error bound in terms of $\tS_{\ell,m}(f)$ instead of $\wcS_m(f)$ by using \eqref{discrite_true_relationship}.
+With this reasoning, in \cite[Sec.
 4.2]{HicJim} we showed that for any $f\in\cc$,
@@
 \end{equation}
-where one may increase $m$ until the error bound {\color{purple}$\epsilon_{\widehat{I}}$} is small enough.
+where one may increase $m$ until the error bound $\epsilon_{\widehat{I}}$ is small enough.
 
@@
 \centering
-\includegraphics[width=.45\textwidth]{estimator_3d_small.eps}
+\includegraphics[width=.45\textwidth]{Fig1.eps}
 \label{fig:1}       % Give a unique label
@@
 By construction, under the assumption that each integrand in $\underline{S}_u$ and $\overline{S}_u$ lies inside $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\widehat{\underline{S}}_u}, \widehat{\underline{S}}_u + \varepsilon_{\widehat{\underline{S}}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\widehat{\overline{S}}_u}, \widehat{\overline{S}}_u + \varepsilon_{\widehat{\overline{S}}_u} \right] .\]
-\comment{Because we do not assume the knowledge of the Walsh coefficients, it is hard to verify whether all the integrands lie in $\cc$.
+Because we do not assume the knowledge of the Walsh coefficients, it is hard to verify whether all the integrands lie in $\cc$.
 Nevertheless, some data-based necessary conditions are provided in \cite{HicJimLi}.
-These conditions can be used to automatically enlarge the cone according to each integrand.} For the rest of the article, we will consider $\widehat{\underline{S}}_u$ and $\widehat{\overline{S}}_u$ as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).
+These conditions can be used to automatically enlarge the cone according to each integrand.
+For the rest of the article, we will consider $\widehat{\underline{S}}_u$ and $\widehat{\overline{S}}_u$ as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).
 
@@
 
-\comment{It is important to note that the function evaluations performed to estimate the Sobol' indices are also used to compute the discrete Walsh coefficients.
+It is important to note that the function evaluations performed to estimate the Sobol' indices are also used to compute the discrete Walsh coefficients.
 As a result, no additional function evaluations are required to compute the error bound.
 The only computation cost that could be expensive is the fast Walsh transform.
-However, the fast transform cost becomes inexpensive when dealing with time consuming models.}
+However, the fast transform cost becomes inexpensive when dealing with time consuming models.
 %For this article, we assumed that evaluating the model is expensive.
@@
 First, one must fix the tolerance $\epsilon >0$ at which Sobol' indices must be estimated, and set $m=\ell_*+r$, where $\ell_*$ and $r$ are the two hyper-parameters defined in \eqref{conecond}.
-{\color{purple}  The choice of $\ell_*$ must be large enough to ensure that each integrand of $\underline{S}_u$ and $\overline{S}_u$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).
-Parameter $r$ should also be chosen carefully: larger values of $r$ will imply a smaller error bound and more dependence on smaller Walsh coefficients, while smaller of values of $r$ might incur in aliasing errors.}
+The choice of $\ell_*$ must be large enough to ensure that each integrand of $\underline{S}_u$ and $\overline{S}_u$ (Section \ref{sec:3.2}) is in $\cc$ (see  (\ref{conecond})).
+Parameter $r$ should also be chosen carefully: larger values of $r$ will imply a smaller error bound and more dependence on smaller Walsh coefficients, while smaller of values of $r$ might \comment{result} in aliasing errors.
 
 Then, one must construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}.
-{\color{purple}  This approach iteratively constructs a $2d$-dimensional Sobol' sequence.
+This approach iteratively constructs a $2d$-dimensional Sobol' sequence.
 Then, it assigns its first $d$ coordinates to $\mathcal{P}_{m}$ and its last $d$ coordinates to $\mathcal{P}'_{m}$.
@@
 Although this is the authors choice, one may choose any other Sobol' construction for $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ as long as the $2d$ dimensions are each generated with different primitive polynomials.
-In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling \cite{HonHic00a,Owe95}.}
+In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling \cite{HonHic00a,Owe95}.
 
@@
 This option is referred as Variant $B$ in Algorithm \ref{recursive.algorithm}.
-{\color{purple}  In this case, the scrambling applied to both designs must be identical to ensure that $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are replicated designs of order one.}
+In this case, the scrambling applied to both designs must be identical to ensure that $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are replicated designs of order one.
 
@@
 In this article, he discussed and highlighted the efficiency of ``Correlation 2" when estimating small first-order indices.
-Our aim is to show that the use of ``Correlation 2" in Variant $A$ {\color{purple}  improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.} This new estimator is,
+Our aim is to show that the use of ``Correlation 2" in Variant $A$ improves the estimation of small first-order indices while potentially reducing the total number of model evaluations required.
+This new estimator is,
 \begin{equation*}
@@
 \end{equation*}
-\comment{As proposed by Owen in \cite{Owen}, the sample points are \break $(\vx_i,{\vx'}_i, \vz_i) \iid \mathcal{U}([0,1])^{3d}$.
+As proposed by Owen in \cite{Owen}, the sample points are \break \comment{$(\vx_i,{\vx'}_i, \vz_i) \sim \mathcal{U}([0,1])^{3d}$}.
 For our algorithm, we extend \break Owen's estimator by replacing the uniform points with a scrambled Sobol' sequence in dimension $3d$.
-In either case, this estimator requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.}
+In either case, this estimator requires an additional set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.
 \bigskip
@@
 \end{equation}
-{\color{purple}  The sign of \eqref{cost.comparison} indicates whether or not using ``Correlation 2" brings an improvement to Variant $A$.
-A negative sign would mean an improvement.} We distinguish two cases :
+The sign of \eqref{cost.comparison} indicates whether or not using ``Correlation 2" brings an improvement to Variant $A$. A negative sign would mean an improvement. We distinguish two cases :
 \begin{itemize}
@@
 \end{itemize}
-{\color{purple} We assume that the numerator in $\underline{S}_u$ is harder to estimate than the numerator in $\ov{$S$}_u$.
+We assume that the numerator in $\underline{S}_u$ is harder to estimate than the numerator in $\ov{$S$}_u$.
 This assumption is tested in the numerical examples presented in Section \ref{sec:5.1} by comparing the number of evaluations required by $\underline{S}_u$ and $\ov{$S$}_u$.
@@
 Furthermore, in case $2)$, we expect the two conditions $m''_{u_j} < m_{u_j}$ and $m'_{u_j} < m_{u_j}$ to usually hold as ``Correlation 2" is shown to perform better for small first-order indices (\textit c.f.
-\cite{Owen}).}
+\cite{Owen}).
 \bigskip
@@
 To overcome this issue, we propose the following alternative for Variant $A$.
-{\color{purple} If at the end of the first iteration $\widehat{\underline{S}}_u$ is smaller than a threshold (in our case $0.1$, as suggested by Owen), then the estimator (\ref{first.order.est}) is switched to ``Correlation 2" for this particular $u$.
+If at the end of the first iteration $\widehat{\underline{S}}_u$ is smaller than a threshold (in our case $0.1$, as suggested by Owen), then the estimator (\ref{first.order.est}) is switched to ``Correlation 2" for this particular $u$.
 In this case, a third Sobol' sequence $\mathcal{P''}_{m}=\{\vz_i\}_{i=0}^{2^m-1}$ is constructed to obtain the corresponding evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
-$\mathcal{P''}$ can be generated assigning and scrambling the last $d$ coordinates of a $3d$-dimensional Sobol' sequence.}
+$\mathcal{P''}$ can be generated assigning and scrambling the last $d$ coordinates of a $3d$-dimensional Sobol' sequence.
 
@@
 
-We illustrate our sequential estimation procedure with two classical test functions and one academic example. In each case, Sobol' indices are estimated with the following three variants:
+We illustrate our sequential estimation procedure with two classical test functions and one \comment{application}. In each case, Sobol' indices are estimated with the following three variants:
 \begin{itemize}
@@
 $$\delta_{\underline{S}_u} = \absolute{\underline{S}_u - \widehat{\underline{S}_u}}, \qquad \delta_{\overline{S}_u} = \absolute{\overline{S}_u - \widehat{\overline{S}_u}}.$$
-{\color{purple} The true values of Sobol' indices are estimated with a precision of $10$ digits. For clarity purposes, in the following tables all results are rounded to $4$ digits.}
+The true values of Sobol' indices are estimated with a precision of $10$ digits. For clarity purposes, in the following tables all results are rounded to $4$ digits.
 
 We also compare the total number of evaluations of each variant to verify the assumption in Section \ref{sec:4.2}.
-{\color{purple}  Results are averaged over $100$ repetitions, each computed with different random scramblings}.
+Results are averaged over $100$ repetitions, each computed with different random scramblings.
 For all repetitions, we fix the tolerance $\varepsilon=5\cdot 10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points).
@@
 
-\comment{For these examples we do not know the true Walsh coefficients of the integrands.
+For these examples we do not know the true Walsh coefficients of the integrands.
 Indeed, since the mapping $\tilde{\vk}$ is chosen heuristically, the cone conditions will also depend on each scrambling.
@@
 These rates are the proportion of the repetitions in which the true errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\overline{S}_u} \leq \varepsilon$.
-When $\delta_{\underline{S}_u} > \varepsilon$ or $\delta_{\overline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and at least one integrand ($I_1$, $I_2$, $I_3$, or $I_4$) falls outside the cone \eqref{conecond}.}
-
-%{\color{purple}  To test if the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$,
-
-%To verify the validity of assumption \eqref{assumption}, the sum of the $c_j$ is evaluated for each repetition and barplots of its values are drawn.}
+When $\delta_{\underline{S}_u} > \varepsilon$ or $\delta_{\overline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and at least one integrand ($I_1$, $I_2$, $I_3$, or $I_4$) falls outside the cone \eqref{conecond}.
+
+%To test if the effective dimension of the numerator of $\underline{S}_u$ is higher than the one of the numerator of $\ov{$S$}_u$,
+
+%To verify the validity of assumption \eqref{assumption}, the sum of the $c_j$ is evaluated for each repetition and barplots of its values are drawn.
 
@@
 
-The two classical test functions considered in this article are {\color{purple} a non qMC (quasi-Monte Carlo) friendly version of the} g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
+The two classical test functions considered in this article are a non qMC (quasi-Monte Carlo) friendly version of the g-function introduced by Sobol' \cite{Sobol'}, and the function introduced by Bratley \textit{et al.} \cite{Bratley}.
 The idea is to test our method over two categories of functions: additive (Bratley \textit{et al.}) and multiplicative (g-function).
@@
 
-{\color{purple} 
 The non qMC friendly version of the g-function is defined as follows:
 \begin{equation*}
-f(\vx)= \prod \limits_{j=1}^{d}g_j(x_j), \qquad g_j(x_j)=\frac{\left |3x_j-2 \right | + a_j}{1 + a_j}, \ a_j \geq 0.
-\end{equation*}}
+f(\vx) = \prod \limits_{j=1}^{d}g_j(x_j), \qquad g_j(x_j)=\frac{\left |3x_j-2 \right | + a_j}{1 + a_j}, \ a_j \geq 0.
+\end{equation*}
+\comment{In many cases, qMC points are generated in base two.
+In addition, the derivative $\partial f(\vx)/\partial x_j$ is discontinuous at $x_j = 2/3$.
+Since $2/3$ does not have a finite binary representation, $f(\vx)$ does not benefit from the stratification properties of qMC points as well as the original Sobol' g-function}.
 Each value $a_j$ determines the relative importance of the $x_j$.
-When the value of $a_j$ gets closer to zero the variable $x_j$ becomes more influent.
+When the value of $a_j$ gets closer to zero the variable $x_j$ becomes more \comment{influential}.
 For this example, we chose $d=6$ and $a_1=0,a_2=0.5, a_3=3, a_4=9, a_5=99$, and $a_6=99$.
@@
 The main observation is that both approaches give similar results both in terms of estimation errors, failure rates and averaged total number of evaluations.
-The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ {\color{purple}  does seem to bring an improvement.
-In particular, the failure rate for input $x_3$ is reduced to $0$.} We propose to draw boxplots of the estimation errors to further investigate the results.
+The use of ``Correlation 2'' in Variant $A.b$ to estimate the four small first-order Sobol' indices $\underline{S}_3, \underline{S}_4, \underline{S}_5, \underline{S}_6$ does seem to bring an improvement.
+In particular, the failure rate for input $x_3$ is reduced to $0$.
+We \comment{draw boxplots} of the estimation errors to further investigate the results.
 \bigskip
@@
 \centering
-\includegraphics[width=0.45\textwidth]{sobolg_box.eps}
+\includegraphics[width=0.45\textwidth]{Fig2.eps}
 \label{boxplots.gfunc}
@@
 
-{\color{purple} Table \ref{comparison.gfunc} shows the average number of evaluations performed in Variant $A.a$ to estimate $\underline{S}_u$ and $\overline{S}_u$.
+Table \ref{comparison.gfunc} shows the average number of evaluations performed in Variant $A.a$ to estimate $\underline{S}_u$ and $\overline{S}_u$.
 The column $N$ indicates the number of times where $\overline{S}_u$ required more evaluations than $\underline{S}_u$.
@@
 \label{comparison.gfunc}
-\end{table}}
+\end{table}
 \bigskip
@@
 Variant $B$ leads to slightly higher estimation errors than those obtained with Variant $A.a$ or Variant $A.b$.
-However, the averaged total number of evaluations is {\color{purple}half as large}.
+However, the averaged total number of evaluations is half as large.
 As such, this approach remains interesting when one wants to estimate only first-order indices.
@@
 $$f(x_1,\dots,x_d)=\sum \limits_{i=1}^{d} (-1)^i \prod \limits_{j=1}^{i} x_j \ .$$
-The importance of each variable $x_j$ depends on their own rank. More explicitly, $x_1$ is more influent than $x_2$ which is respectively more influent than $x_3$ and so on.
+The importance of each variable $x_j$ depends on their own rank. More explicitly, $x_1$ is more \comment{influential} than $x_2$ which is respectively more \comment{influential} than $x_3$ and so on.
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{bratley_box.eps}
+\includegraphics[width=0.45\textwidth]{Fig3.eps}
 \label{boxplots.bratley}
@@
 
-{\color{purple} Table \ref{comparison.bratley} shows the average number of evaluations performed in Variant $A.a$ to estimate $\underline{S}_u$ and $\ov{$S$}_u$.
+Table \ref{comparison.bratley} shows the average number of evaluations performed in Variant $A.a$ to estimate $\underline{S}_u$ and $\ov{$S$}_u$.
 The column $N$ indicates the number of times where $\ov{$S$}_u$ required more evaluations than $\underline{S}_u$.
@@
 \label{res.bratley.B}
-\end{table}}
-
-Averaged estimation errors $\delta_{\underline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$, and averaged total number of evaluations for Variant $B$ are shwon in Table \ref{res.bratley.B}.
+\end{table}
+
+Averaged estimation errors $\delta_{\underline{S}_u}$, failure rates $r_{\delta_{\underline{S}_u}}$, and averaged total number of evaluations for Variant $B$ are \comment{shown} in Table \ref{res.bratley.B}.
 The estimation errors are lower than those of Variant $A.a$ but higher than those of Variant $A.b$.
@@
 Even if ``Correlation 2'' originally requires more model evaluations, this drawback is overridden when this estimator is included into a sequential procedure such as ours.
-
 For the case where we are only interested in estimating first-order indices, Variant $B$ could be the best choice as the number of function evaluations is less than for Variants $A.a$ and $A.b$.
 
-{\color{purple}
 \subsection{Application}
@@
 
-The motivation of this application is to test if our procedure captures the same set of influent inputs $(x_1,x_3,x_7,x_8,x_9)$ selected by the analysis of Forrester \textit{et al.} which are those of value greater than $0.05$.
+The motivation of this application is to test if our procedure captures the same set of \comment{influential} inputs $(x_1,x_3,x_7,x_8,x_9)$ selected by the analysis of Forrester \textit{et al.} which are those of value greater than $0.05$.
 
@@
 Both variants capture well the presence of inert inputs.
-Variant $A.b$ is more expansive but validates the property that first-order indices are lower or equal to total-effect indices.
+Variant $A.b$ is more \comment{expensive} but validates the property that first-order indices are lower or equal to total-effect indices.
 Conversely, Variant A.a fails to guarantee this property for inputs with small main effects: $x_2$, $x_4$, $x_5$, $x_6$.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{wingweight_box.eps}
+\includegraphics[width=0.45\textwidth]{Fig4.eps}
 \label{boxplots.wing}
@@
 
-Overall, each variant captures well the same set of influent inputs identified by Forrester \textit{et al.}
+Overall, each variant captures well the same set of \comment{influential} inputs identified by Forrester \textit{et al.}
 \begin{table}[t]
@@
 \vspace*{0.2cm}
-\includegraphics[width=0.4\textwidth]{comp_mc_first.eps}
+\includegraphics[width=0.4\textwidth]{Fig5.eps}
 \label{compa_MC_first}
@@
 \vspace*{0.2cm}
-\includegraphics[width=0.4\textwidth]{comp_mc_tot.eps}
+\includegraphics[width=0.4\textwidth]{Fig6.eps}
 \label{compa_MC_tot}
-\end{figure}}
+\end{figure}
 
@@
 
-{\color{purple} The precision of our procedure was also compared to a simpler method based on iid sampling and straightforward confidence intervals.
+The precision of our procedure was also compared to a simpler method based on iid sampling and straightforward confidence intervals.
 For an identical number of evaluations, our procedure was far more accurate than the iid sampling method.
-The origin of the discrepancy observed lies in the use of a more robust error bound.}
+The origin of the discrepancy observed lies in the use of a more robust error bound.
 

### 2017-05-20 article_review2.0/reviewer_letter.tex
added first draft of reviewer letter

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb,
mathtools,bm,extraipa,mathabx,graphicx,algorithm}
\usepackage{color}

\newcommand{\vect}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\vk}{\vect{k}}
\newcommand{\vx}{\vect{x}}
\newcommand{\vI}{\vect{I}}
\newcommand{\hS}{\widehat{S}}
\newcommand{\tS}{\widetilde{S}}
\newcommand{\wcS}{\widecheck{S}}
\def\dashfill{\cleaders\hbox to 2em{-}\hfill}
\newcommand{\answer}[1]{{\color{blue} #1 }}

\makeatletter
\newcommand{\ov}[1]{
  \m@th\overline{\mbox{#1}\raisebox{2mm}{}}
}

\begin{document}

\textcolor{blue}{Dear associated editor and reviewers,\\
we would like to thank you for the positive and constructive feedback. Below we have compiled a detailed list of answers (blue text) to the issues raised in the review reports. The corresponding modifications in the manuscript are colored in purple. \\
Further aknowledgments have been preemptively added to thank both the associate editor and the two reviewers work.\\
Best regards,\\
Laurent Gilquin and Llu\'{i}s Antoni Jim\'{e}nez Rugama}

\section*{Report on ``Reliable error estimation for Sobol' indices''}

\textbf{\large{Reviewer $1$}}
\vspace*{0.5cm}

\textbf{Minor comments}:

\begin{itemize}

\item[1.] page 2, column 1, line 1: replace "convergence rates are of" by "convergence rates can be", as these convergence rates only hold under some conditions, and the "are of" without any mention of conditions makes it sound as if these rates always held

\item[2.] page 4, column 1, line 9, italicize d in "dimension d"

\item[3.] page 4, column 2, lines 42-43: replace "and" by "an" before "automatic"

\item[4.] page 6, column 2, lines 22-23: replace "incur" by "result"

\item[5.] page 7, line 9 of column 2: regarding item f of the minor comments in my previous review, although it is now more clear how the points are constructed, the "iid" mention is still slightly confusing. I think you mean that the 3d coordinates are independent but not that the points themselves are independent (since even after scrambling the points of the scrambled sequence are dependent). I would remove the iid mention, assuming it is meant to describe the property of the 3d coordinates, as it is implicit when saying that each point follow a $\mathcal{U}([0,1)^{3d})$.

\item[6.] page 8, column 1, lines 32-33: "academic example": what does this mean? Why not just say "application" as indicated in the title of your Section 5.2 on page 10?

\item[7.] page 11, column 1, lines 51-52: should read "expensive"
\end{itemize}

\textcolor{blue}{
\begin{itemize}
\item[*]Points $1$, $2$, $3$, $4$ and $7$ have all been addressed accordingly.
\item[*]Concerning point $5$, we indeed intended to say that ``the 3d coordinates are independent but not that the points themselves''. As such, we have followed the suggested correction and removed the $iid$ mention.
\item[*]Concerning point $6$, we simply missed this correction during the first review. We thank the reviewer for catching it.
\end{itemize}}

\newpage
\textbf{\large{Reviewer $2$}}
\vspace*{0.5cm}

\textbf{Minor comments}:
\begin{itemize}
\item[1.] p2 line 33 Left: there is an extra $\in$

\item[2.] p3 eq (7): you can get a better estimate of $\sigma^2$ using all 2n observations, not just the first n.

\item[3.] p3 line 37 Left: `we generalized' is not quite precise, since ref [4] had 4 other authors

\item[4.] Rereading my original comment about definition 1, I see it was a bit ambiguous. Sorry about that. Something extra needed to be said to rule out bad point sets.  That could either be in the definition itself, or put in a comment right at the place where points satisfying the definition get used.  The revision puts it into the definition.  This is ok, but it leaves you with a longer definition than you might have wanted.

\item[5.] p3 line 14 Right: ref 21 has only two authors, so why not just say Tissot and Prieur instead of Tissot et al?

\item[6.] p3 line 26 Right: asymptotical $\rightarrow$ asymptotic

\item[7.] p5 eq (15) replace period by comma

\item[8.] sec 5.1.1  for readers who don't know a lot about QMC, it would help to explain why the new g function is not as qmc friendly as the previous one.

\item[9.] p5 line 51 Right: propose to draw boxplots $\rightarrow$ draw boxplots

\item[10.] p9 and elsewhere: influent $\rightarrow$ influential.  Influential means important. Influent refers to water flowing in: \\
http://www.dictionary.com/browse/influent?s=t

\item[11.] p10 55 Left shwon $\rightarrow$ shown

\item[12.] p11 52 Left expansive $\rightarrow$ expensive
\end{itemize}

\textcolor{blue}{
\begin{itemize}
\item[*]Points $1$, $5$, $6$, $7$, $9$, $10$, $11$ and $12$ have all been addressed accordingly.
\item[*]Concerning point $2$, $\sigma^2$ (along with $\mu$) has been rewritten to use all $2n$ observations.
\item[*]Concerning point $3$, `we generalized' has been replaced by `we use the generalization from' to answer the issue.
\item[*]Concerning point $4$, we decided to keep the modification in the definition to stress that bad point sets are ruled out.
\item[*]Concerning point $8$, further explainations were added on the new g-function (inspired from the reviewer's comments on the first review).
\end{itemize}}

\end{document}

### 2017-05-21 article_review2.0/Manuscript.tex
removed extra space in purple comments
Minor changes in Manuscript and reviewers letter

@@
 
-\newcommand{\comment}[1]{{\color{purple} #1 }}
+\newcommand{\comment}[1]{{\color{purple} #1}}
 % Insert the name of "your journal" with
@@
 using for $\sigma^2$:
-\comment{\begin{equation}
- \widehat{\sigma}^2 = \frac{1}{2(n-1)} \sum \limits_{i=0}^{n-1} \left[\left( f(\vx_i) - \widehat{\mu}\right)^2 + \left( f(\vx'_i) - \widehat{\mu}\right)^2\right],
+\begin{equation}\label{mu.est}
+\widehat{\sigma}^2 = \frac{1}{n-1} \sum \limits_{i=0}^{n-1} \left(f(\vx_i) - \widehat{\mu}\right)^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1}f(\vx_i).
 \end{equation}
-with
-\begin{equation}
-\widehat{\mu} =  \frac{1}{2n} \sum \limits_{i=0}^{n-1} \left[ f(\vx_i)+f(\vx'_i)\right].
-\label{mu.est}
-\end{equation}}
+\comment{Equation \eqref{mu.est} can be improved if we use the $2n$ evaluations $f(\vx_i)$ and $f(\vx'_i)$.
+While this would be an important improvement to estimate the indices' denominator, the error construction described in Section \ref{sec:3} would require additional computations.
+Because of the new computations in the algorithm, the additional benefit of using $2n$ evaluations could become more costly than beneficial.}
 

### 2017-05-21 article_review2.0/reviewer_letter.tex
Minor changes in Manuscript and reviewers letter

@@
 \item[*]Points $1$, $2$, $3$, $4$ and $7$ have all been addressed accordingly.
-\item[*]Concerning point $5$, we indeed intended to say that ``the 3d coordinates are independent but not that the points themselves''.
-As such, we have followed the suggested correction and removed the $iid$ mention.
+\item[*]Concerning point $5$, we intended to mention Owen's estimator in its original form, designed with uniform iid points.
+Since it uses iid uniform points, the integral (or expected value to be estimated) is defined over the uniform measure.
+Hence, because the integral is defined over the uniform measure, we can apply quasi-Monte Carlo points instead of uniform iid points.
+This does not imply that the quasi-Monte Carlo points need to be independent.
+As the reviewer mentions, since this is confusing, we have followed the suggested correction and removed the $iid$ mention.
 \item[*]Concerning point $6$, we simply missed this correction during the first review. We thank the reviewer for catching it.
@@
 \item[*]Points $1$, $5$, $6$, $7$, $9$, $10$, $11$ and $12$ have all been addressed accordingly.
-\item[*]Concerning point $2$, $\sigma^2$ (along with $\mu$) has been rewritten to use all $2n$ observations.
+\item[*]Concerning point $2$, although this is a great idea, this is not as convenient if we use the error estimation from Section 3.
+We could proceed by estimating $\mu$ (the same method for $\sigma^2$) with $f(\vx_i)$ and computing the error bound, estimating $\mu$ with $f(\vx'_i)$ and computing the error bound.
+Then, if $\mu\in[a,b]$ and $\mu'\in[a',b']$, the new estimator would be the mid point in $[a,b]\cap[a',b']$.
+This would require including the computation of the fast Fourier transform for the $f(\vx'_i)$ evaluations which could be too costly for the benefits it provides (given that the hard integral is in the numerator).
+As the reviewer suggests, it is important to consider that we have the $f(\vx'_i)$ evaluations and this could always be used.
+We added a comment after equation (7) explaining this point.
 \item[*]Concerning point $3$, `we generalized' has been replaced by `we use the generalization from' to answer the issue.

### 2017-05-21 article_review2.0/Manuscript.tex
added two changes

@@
 While this would be an important improvement to estimate the indices' denominator, the error construction described in Section \ref{sec:3} would require additional computations.
-Because of the new computations in the algorithm, the additional benefit of using $2n$ evaluations could become more costly than beneficial.}
-
-Then, the Sobol' indices estimators are:
+Because of these new computations in the algorithm, the additional benefit of using $2n$ evaluations could become more costly than beneficial.}
+
+The Sobol' indices estimators are:
 \begin{equation}
@@
 \end{equation}
-Using this method, the estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$.
+Based on equation \eqref{common.sobol.est}, the estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$.
 Thus, for all first order and total effect indices, one would need $3nd$ model evaluations.
@@
 \vspace*{0.2cm}
-\includegraphics[width=0.4\textwidth]{Fig5.eps}
+\includegraphics[width=0.45\textwidth]{Fig5.eps}
 \label{compa_MC_first}
@@
 \vspace*{0.2cm}
-\includegraphics[width=0.4\textwidth]{Fig6.eps}
+\includegraphics[width=0.45\textwidth]{Fig6.eps}
 \label{compa_MC_tot}
